---
title: "D7 connectivity analysis"
output: html_notebook
---

Load the functions
```{r}
library(neuprintr)
library(tidyverse)
library(cowplot)
library(neuprintrExtra)
library(reshape2)
library(patchwork)
source(file.path("..","PBFigures","PBAnalysisUtils.R"))
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))
```

Get the EPG and D7 connections
```{r}
EPGD7Bag <- neuronBag(getTypesTable(c("EPG","Delta7")))
```

Plot the type-to-type connections for the downstream partners of the EPGs and Delta7s in the PB
```{r, fig.width = 7, fig.height = 2}
EPGD7T2TConn <- plotConnectivityMatrix(EPGD7Bag$outputs %>% filter((roi=="PB") & !(type.to %in% c("1265399790","1283600055","2371497342"))), byGroup = "type") + 
  coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") + 
  theme_paper() + theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = 0)) +
  guides(fill = guide_colourbar(title = 'relative weight', direction = 'horizontal', title.position = 'top', barheight = 0.5))

EPGD7T2TConn
```

Plot the neuron-to-neuron connections between the EPGs and the Delta7s
```{r, fig.width=8, fig.height=8}
EPGD7ToSelf <- EPGD7Bag$outputs_raw %>% filter((roi=="PB") & (type.to %in% c("EPG","Delta7")))
EPGD7ToSelf$nameOrder.from <- PBRename(EPGD7ToSelf$name.from,EPGD7ToSelf$from)
EPGD7ToSelf$nameOrder.to <- PBRename(EPGD7ToSelf$name.to,EPGD7ToSelf$to)

cmax=50
EPGD7ToSelf_CM <- ggplot(EPGD7ToSelf) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = 0)) +
  coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") +
  guides(fill = guide_colourbar(title = '# of synapses', title.position = 'left', barwidth = 0.25, title.theme = element_text(angle=90)))
print(EPGD7ToSelf_CM)
```

Group the EPGs and D7s by name
```{r}
EPGToD7Gp <- EPGD7ToSelf %>% filter(type.from == 'EPG', type.to =='Delta7') %>% 
  group_by(name.from, nameOrder.to, name.to) %>% summarize(totalWeight = sum(ROIweight)) %>%
  group_by(name.from, name.to) %>% summarize(meanTotalWeight = mean(totalWeight))
EPGToD7Gp$nameOrder.from <- EPGToD7Gp$name.from %>% lapply(function(x) sub('\\(PB08\\)','',x)) %>% unlist()
EPGToD7Gp$nameOrder.from <- factor(EPGToD7Gp$nameOrder.from,
                                   levels = as.factor(c('EPG_L8','EPG_L7','EPG_L6','EPG_L5','EPG_L4','EPG_L3','EPG_L2','EPG_L1',
                                                        'EPG_R1','EPG_R2','EPG_R3','EPG_R4','EPG_R5','EPG_R6','EPG_R7','EPG_R8')))
EPGToD7Gp$nameOrder.to <- EPGToD7Gp$name.to %>% lapply(function(x) sub('elta','',sub('\\(PB15\\)','',x))) %>% unlist()
EPGToD7Gp$nameOrder.to <- factor(EPGToD7Gp$nameOrder.to, levels = as.factor(sort(unique(EPGToD7Gp$nameOrder.to),decreasing=TRUE)))

cmax=100
EPGToD7Gp_CM <- ggplot(EPGToD7Gp) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=meanTotalWeight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") +
  guides(fill = guide_colourbar(title = 'mean total # of synapses', title.position = 'left', barwidth = 0.25, title.theme = element_text(angle=90)))
print(EPGToD7Gp_CM)
```


```{r}
#Get the first L glomeruli for each D7
D7Gpids <- levels(EPGToD7Gp$nameOrder.to)
allD7LGlomsGp <- D7Gpids %>% lapply(function(x) sub('.*_(L[[:digit:]]).*','\\1',x)) %>% unlist()
```


```{r}
# Create a matrix of just the weights
colnames(EPGToD7Gp)[colnames(EPGToD7Gp) == 'meanTotalWeight'] <- 'ROIweight'
EPGToD7Gp_WM <- WMFromConTab(EPGToD7Gp,levels(EPGToD7Gp$nameOrder.from),D7Gpids) 

# Shift the entries to align the peaks
for (i in 1:length(D7Gpids)){
  # First, move the max so that the two peaks occur ~1/4 and ~3/4 of the way in
  wNow <- EPGToD7Gp_WM[,i]
  shift = 1-as.numeric(substr(allD7LGlomsGp[i],2,2))
  if (shift == 0){
    wNow
  } else {
    wNow <- c(tail(wNow, -shift), head(wNow, shift))
  }
  
  EPGToD7Gp_WM[,i] <- wNow
}

colnames(EPGToD7Gp_WM) <- D7Gpids
rownames(EPGToD7Gp_WM) <- seq(1:dim(EPGToD7Gp_WM)[1])
PBRegInputs <- melt(EPGToD7Gp_WM,value.name = 'regInput',varnames = c('position','D7id'))
PBRegInputs$D7id <- as.factor(PBRegInputs$D7id)
PBRegInputs <- PBRegInputs %>% filter(regInput != 0)

# Plot the connection matrix
conmatPlotGp <- ggplot(PBRegInputs) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(D7id,position,fill=regInput)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  coord_equal(ratio=1, ylim = c(1,16)) + xlab("postsynaptic D7 type") + ylab("shifted EPG input position") +
  guides(fill = guide_colourbar(title = 'mean total # of synapses', title.position = 'left', barwidth = 0.25, title.theme = element_text(angle=90)))

print(conmatPlotGp)
```

Plot the mean and SD with a cosine fit
```{r}
PBRegInputStats <- PBRegInputs %>% group_by(position) %>% summarize(mean = mean(regInput), sd = sd(regInput))

g_PBProf_Gp <- ggplot(PBRegInputStats) + geom_line(aes(x=position,y=mean,group=1, color='mean profile')) +
  geom_line(aes(x=position,y=mean-sd,group=1),color='gray') +
  geom_line(aes(x=position,y=mean+sd,group=1),color='gray')

# Fit a cosine to the entire profile and plot it
df = data.frame(pts = PBRegInputStats$position, wMean = PBRegInputStats$mean)
fit <- nls(wMean ~ (C1 * cos(-C2*(pts-theta))+C3), data=df,
  start=list(C1=20, C2=0.4, C3=10, theta=35), algorithm="port") 
pts = c(1:length(wNow)-1)
dffit <- data.frame(pts)
dffit$wMean <- predict(fit, newdata=dffit)

g_PBProf_Gp <- g_PBProf_Gp + geom_line(data=dffit,aes(x=pts,y=wMean,color='cosine fit'))

g_PBProf_Gp <- g_PBProf_Gp + theme_cowplot() + xlab('EPG input position') + ylab('# of synapses') + 
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = c('mean profile' = 'black',
                                'cosine fit' = 'red',
                                'cosine fit - R peak' = 'blue'))
print(g_PBProf_Gp)
```

Combine the plots
```{r}
design <- "
  12
  12
  12
  33
"
allPlts <- EPGToD7Gp_CM + conmatPlotGp + g_PBProf_Gp +
  plot_layout(design = design)
allPlts
```


Get the EPG activity given a von Mises profile
```{r}
# Use a von Mises bump profile
EBOrder <- c("R1","L8","R2","L7","R3","L6","R4","L5",
             "R5","L4","R6","L3","R7","L2","R8","L1")
actProfvM <- data.frame(act = vonMisesProf(),
                        glom = EBOrder)
```
```{r}
# Get the EPG to D7 connections
EPG_2_Delta7 <- getConnectionTable(
  unique(neuprint_search("EPG.*")$bodyid),
  "POST",
  "PB") %>% filter(type.from == "EPG" & type.to == "Delta7")
```
```{r}
# Get the EPG activity 
allEPGids <- PBRename(EPG_2_Delta7$name.from,EPG_2_Delta7$from) %>% unique() %>% as.character() %>% sort()
allD7ids <- PBRename(EPG_2_Delta7$name.to,EPG_2_Delta7$to) %>% unique()
allEPGGloms <-  allEPGids %>% as.character() %>% lapply(function(x) sub('.*_(L[1-9]|R[1-9]).*','\\1',x)) %>% unlist()
EPGact <-  numeric(length(allEPGids))
for (EPG in 1:length(allEPGids)){
  EPGact[EPG] <- actProfvM[which(actProfvM$glom == allEPGGloms[EPG]),]$act
}
EPGProf <- data.frame(nameid = allEPGids, act = EPGact, glom = allEPGGloms)
EPGProf$glom <- factor(EPGProf$glom, levels = rev(PBGlomSort(unique(EPGProf$glom))))
```
```{r, fig.width =3, fig.height = 2}
# Get the mean activity per EPG
EPGProfGlomAve <- EPGProf %>% group_by(glom) %>% summarize(meanAct = mean(act))

g_EPGact_in_PB_glomAve <- ggplot(EPGProfGlomAve) + geom_bar(aes(x = glom, weight = meanAct),fill='black') + 
  theme_paper() + coord_cartesian(expand=FALSE) + xlab('EPG glomerulus') + ylab('simulated output') +
  theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = 0))
print(g_EPGact_in_PB_glomAve)
```
```{r}
gloms_L <- c("L1","L2","L3","L4","L5","L6","L7","L8")
gloms_R <- c("R1","R2","R3","R4","R5","R6","R7","R8")
```
```{r, fig.width =3, fig.height = 2}
# Use activity only in one set of EPGs in a given glom.
actProf <- vector(mode="numeric",length = 16)
actProf[8] <- 1
actProfImp <- data.frame(act = actProf,
                         glom = c("R1","L8","R2","L7","R3","L6","R4","L5",
                                 "R5","L4","R6","L3","R7","L2","R8","L1"))
```
```{r}
actProfImpPlt <- actProfImp
actProfImpPlt$glom <- factor(actProfImpPlt$glom, levels = rev(PBGlomSort(actProfImpPlt$glom)))
g_EPGact_in_PB_imp <- ggplot(actProfImpPlt) + geom_bar(aes(x = glom, weight = act),fill = 'black') + 
  theme_paper() + coord_cartesian(expand=FALSE) + xlab('EPG glomerulus') + ylab('simulated activity') +
  theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = 0))
g_EPGact_in_PB_imp
```

```{r, fig.width = 4, fig.height = 2}
# Look at the mean profile for both the von mises and inpulse profile

# Save the figures for both conditions
EPGProfPlt <- list()

#Loop through both conditions
for (p in 1:2){
  if (p == 1)
    actProf <- actProfvM
  if (p == 2)
    actProf <- actProfImp
  
  # Get the EPG inputs from the D7s as a result of the given profile
  PBTpInputs_all <- EPGToD7OutputAct("EPG",actProf)

  # Align the bumps
  datToFit_L <- bumpAlign(PBTpInputs_all, gloms_L)
  datToFit_R <- bumpAlign(PBTpInputs_all, gloms_R)

  # Average the aligned profile across the glomeruli
  datStats_L <- datToFit_L %>% group_by(glom) %>% summarize(mean = mean(actAlign), sd = sd(act))
  datStats_R <- datToFit_R %>% group_by(glom) %>% summarize(mean = mean(actAlign), sd = sd(act))

  # Assign angles to the positions
  datStats_L$ang <- seq(from=-pi, to=pi, length.out=(1+nrow(datStats_L)))[1:nrow(datStats_L)]
  datStats_R$ang <- seq(from=-pi, to=pi, length.out=(1+nrow(datStats_R)))[1:nrow(datStats_R)]
  
  # Fit a cosine to the profiles
  datFit_L <- cosFit(datStats_L)
  datFit_R <- cosFit(datStats_R)
  datStats_L$fit <- coef(datFit_L)['C1']*cos(datStats_L$ang - coef(datFit_L)['theta']) + coef(datFit_L)['C2']
  datStats_R$fit <- coef(datFit_R)['C1']*cos(datStats_R$ang - coef(datFit_R)['theta']) + coef(datFit_R)['C2']
  
  # Move the gloms so that the valley falls at the profile peak (for display only)
  datStats_L$glom <- c(tail(datStats_L$glom, -5) %>% as.character, head(datStats_L$glom, 5) %>% as.character())
  datStats_R$glom <- c(tail(datStats_R$glom, -5) %>% as.character, head(datStats_R$glom, 5) %>% as.character())
  
  # Rearrange the order for plotting
  datStats_L$glom <- factor(datStats_L$glom, levels = c(rev(gloms_R),gloms_L))
  datStats_R$glom <- factor(datStats_R$glom, levels = c(rev(gloms_R),gloms_L))
  datStats_L <- datStats_L[order(datStats_L$glom),]
  datStats_R <- datStats_R[order(datStats_R$glom),]

  datStats_All <- rbind(datStats_L,datStats_R)

  meanPlt <- ggplot(datStats_All) + 
    geom_line(aes(x = glom, y = mean, group = 1 , color = 'mean')) +
    geom_line(aes(x = glom, y = fit, group = 1, color = 'fit')) +
    geom_line(aes(x = glom,y=mean-sd,group=1, color='sd')) +
    geom_line(aes(x = glom,y=mean+sd,group=1, color='sd')) +
    scale_color_manual(values = c('mean' = 'black',
                                  'fit' = 'red',
                                  'sd' = 'gray')) +
    xlab('EPG glomerulus') + ylab('simulated input') +
    ylim(-0.25,1.25) +
    theme_paper() + 
    theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = 0))
  
  EPGProfPlt[[p]] <- meanPlt
}

```

```{r}
design = "
 1
 2
 3
 4"

EPGActPlts <- g_EPGact_in_PB_glomAve + EPGProfPlt[[1]] + g_EPGact_in_PB_imp + EPGProfPlt[[2]] + plot_layout(design = design)
ggsave("old//EPGActPlts.pdf",EPGActPlts,
       width = 3, height = 4)
```


Find the RSS for a cosine fit for the outputs of D7s onto PE and PF neurons
```{r}
PBTps <- c("EPG","PFR_a",
           "PEN_a(PEN1)","PEN_b(PEN2)",
           "PFNa","PFNd","PFNm_a","PFNm_b","PFNp_a","PFNp_b","PFNp_c","PFNp_e","PFNv",
           "PEG","PFGs")
gloms_L_all <- list()
gloms_R_all <- list()
for (t in 1:2){
  gloms_L_all[[PBTps[t]]] <- c("L1","L2","L3","L4","L5","L6","L7","L8")
  gloms_R_all[[PBTps[t]]] <- c("R1","R2","R3","R4","R5","R6","R7","R8")
}
for (t in 3:13){
  gloms_L_all[[PBTps[t]]] <- c("L2","L3","L4","L5","L6","L7","L8","L9")
  gloms_R_all[[PBTps[t]]] <- c("R2","R3","R4","R5","R6","R7","R8","R9")
}
for (t in 14:15){
  gloms_L_all[[PBTps[t]]] <- c("L1","L2","L3","L4","L5","L6","L7","L8","L9")
  gloms_R_all[[PBTps[t]]] <- c("R1","R2","R3","R4","R5","R6","R7","R8","R9")
}
```

```{r}
for (t in 1:length(PBTps)){
  for (p in 1:2){
    if (p == 1){
      actProf <- actProfvM
      inpt <- "vonMises"
    }
    if (p == 2){
      actProf <- actProfImp
      inpt <- "impulse"
    }
      
    
    PBTpInputs_all <- EPGToD7OutputAct(PBTps[t],actProf)
  
    datToFit_L <- bumpAlign(PBTpInputs_all, gloms_L_all[[PBTps[t]]])
    datToFit_R <- bumpAlign(PBTpInputs_all, gloms_R_all[[PBTps[t]]])
  
    datStats_L <- datToFit_L %>% group_by(glom) %>% summarize(mean = mean(actAlign), sd = sd(act))
    datStats_R <- datToFit_R %>% group_by(glom) %>% summarize(mean = mean(actAlign), sd = sd(act))
  
    if (length(gloms_L_all[[PBTps[t]]]) == 8){
      datStats_L$ang <- seq(from=-pi, to=pi, length.out=(1+nrow(datStats_L)))[1:nrow(datStats_L)]
      datStats_R$ang <- seq(from=-pi, to=pi, length.out=(1+nrow(datStats_R)))[1:nrow(datStats_R)]
    }
    if (length(gloms_L_all[[PBTps[t]]]) == 9){
      datStats_L$ang <- seq(from=-pi, to=pi, length.out=nrow(datStats_L))
      datStats_R$ang <- seq(from=-pi, to=pi, length.out=nrow(datStats_R))
    }
    datFit_L <- cosFit(datStats_L)
    datFit_R <- cosFit(datStats_R)
    
    datNow <- data.frame(type = PBTps[t], inpt = inpt, 
                         RSE_L = deviance(datFit_L),
                         RSE_R = deviance(datFit_R))
    
    if ((t ==1) & (p==1)){
      allRSEs <- datNow
    } else {
      allRSEs <- rbind(allRSEs, datNow)
    }
  }
}

```
```{r}
allRSEs_melt <- melt(allRSEs, id.vars = c('type','inpt'), value.name = 'RSE', variable.name = 'side')
allRSEs_melt$inpt <- factor(allRSEs_melt$inpt, levels = c('vonMises','impulse'))
allRSEs_melt_RLave <- allRSEs_melt %>% group_by(type,inpt) %>% summarize(aveRSE = mean(RSE))
allRSEs_melt_RLave$type <- factor(allRSEs_melt_RLave$type, levels = PBTps)

gStats_all <- ggplot(allRSEs_melt_RLave,aes(x=type,y=aveRSE)) + geom_point(size=2, pch = 21, aes(fill = inpt)) +
  coord_cartesian(expand=FALSE,clip = 'off',ylim=c(0, 0.015)) + theme_paper() +
  xlab('neuron type') + ylab('residual sum of squares') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0)) + 
  scale_fill_manual(values = c('black','white'))
print(gStats_all)

ggsave("old//CosRSEAcrossTypes.pdf",gStats_all,
       width = 4, height = 2)
```




Plot the EPG input from D7s given a von Mises or Impulse input profile
```{r}
# Use a von Mises bump profile
actProfvM <- data.frame(act = vonMisesProf(),
                        glom = c("R1","L8","R2","L7","R3","L6","R4","L5",
                                 "R5","L4","R6","L3","R7","L2","R8","L1"))

# Transform the bump from EB coordinates to PB coordinates
vMOut <- EPGToD7Transform("EPG",actProfvM)

# Get the profile stats
D7OutputShape_stats_vM <- D7ShapeMeanSD(vMOut)
  
# Fit a cosine to the data
fit_vM <- D7CosFit(D7OutputShape_stats_vM) 

# Use activity only in one set of EPGs in a given glom.
actProf <- vector(mode="numeric",length = 16)
actProf[8] <- 1
actProfImp <- data.frame(act = actProf,
                         glom = c("R1","L8","R2","L7","R3","L6","R4","L5",
                                 "R5","L4","R6","L3","R7","L2","R8","L1"))
impOut <- EPGToD7Transform("EPG",actProfImp)

# Get the profile stats
D7OutputShape_stats_imp <- D7ShapeMeanSD(impOut)
  
# Fit a cosine to the data
fit_imp <- D7CosFit(D7OutputShape_stats_imp) 

# Plot
PBEPGToD7Prof_vM <- PBActPlot(D7OutputShape_stats_vM,fit_vM)
PBEPGToD7Prof_vM <- PBEPGToD7Prof_vM + ggtitle('von Mises E-PG input -> D7 -> E-PG') + theme_cowplot() +
  theme(legend.justification = c(0, 1), legend.position = c(0.1, 1))

# Plot
PBEPGToD7Prof_imp <- PBActPlot(D7OutputShape_stats_imp,fit_imp)
PBEPGToD7Prof_imp <- PBEPGToD7Prof_imp + ggtitle('impulse E-PG input -> D7 -> E-PG') + theme_cowplot() +
  theme(legend.justification = c(0, 1), legend.position = c(0.1, 1))

```

List the order of PB gloms
```{r}
PBGlomOrder <- c("R9","R8","R7","R6","R5","R4","R3","R2","R1",
                 "L1","L2","L3","L4","L5","L6","L7","L8","L9")
```

Create a von Mises profile in the EPGs - in the EB
```{r}
gloms = c("R1","L8","R2","L7","R3","L6","R4","L5",
         "R5","L4","R6","L3","R7","L2","R8","L1")
actProfvM <- data.frame(act = vonMisesProf(),glom = gloms)
actProfvM$glom <- factor(actProfvM$glom, levels = gloms)
g_EPGact_in_EB <- ggplot(actProfvM) + geom_bar(aes(x = glom, weight = act)) + 
  theme_paper() + coord_cartesian(expand=FALSE) + xlab('PB glom') + ylab('normalized activity')
print(g_EPGact_in_EB)
```

Propagate the profile into the PB


Get the EPG activity given an impulse profile
```{r}
allEPGids <- EPG_2_Delta7$nameid %>% unique()
allD7ids <- EPG_2_Delta7$partnerid %>% unique()
allEPGGloms = strsplit(allEPGids,"_") %>% lapply(function(x){tail(x,2)[1]}) %>% unlist()
EPGact_imp = numeric(length(allEPGids))
for (EPG in 1:length(allEPGids)){
  EPGact_imp[EPG] <- actProfImp[which(actProfImp$glom == allEPGGloms[EPG]),]$act
}
EPGProf_imp <- data.frame(nameid = PBRename(EPG_2_Delta7$name.from,EPG_2_Delta7$from) %>% unique(), act = EPGact_imp, glom = allEPGGloms)
EPGProf_imp$glom <- factor(EPGProf_imp$glom, levels = PBGlomOrder)
```

Get the mean activity per EPG
```{r}
EPGProfGlomAve_imp <- EPGProf_imp %>% group_by(glom) %>% summarize(meanAct = mean(act))

g_EPGact_in_PB_glomAve_imp <- ggplot(EPGProfGlomAve_imp) + geom_bar(aes(x = glom, weight = meanAct)) + 
  theme_paper() + coord_cartesian(expand=FALSE) + xlab('EPG neuron') + ylab('normalized activity')
print(g_EPGact_in_PB_glomAve_imp)
```



Print the inputs and average activity for the vonMises and impulse profiles
```{r}
EPGToD7TransPlt <- (g_EPGact_in_PB_glomAve + PBEPGToD7Prof_vM) /(g_EPGact_in_PB_glomAve_imp + PBEPGToD7Prof_imp)
EPGToD7TransPlt
```


Find the RSS for a cosine fit for the outputs of D7s onto PE and PF neurons
```{r}
# Use a von Mises bump profile
actProfvM <- data.frame(act = vonMisesProf(),
                        glom = c("R1","L8","R2","L7","R3","L6","R4","L5",
                                 "R5","L4","R6","L3","R7","L2","R8","L1"))
actProfvM$glom <- factor(actProfvM$glom,
                         levels = c("R8","R7","R6","R5","R4","R3","R2","R1",
                                    "L1","L2","L3","L4","L5","L6","L7","L8"))

# Use activity only in one set of EPGs in a given glom.
actProf <- vector(mode="numeric",length = 16)
actProf[8] <- 1
actProfImp <- data.frame(act = actProf,
                         glom = c("R1","L8","R2","L7","R3","L6","R4","L5",
                                 "R5","L4","R6","L3","R7","L2","R8","L1"))
actProfImp$glom <- factor(actProfImp$glom,
                         levels = c("R8","R7","R6","R5","R4","R3","R2","R1",
                                    "L1","L2","L3","L4","L5","L6","L7","L8"))

# Specify the search strings
PBTps <- c("EPG","PEN_a(PEN1)","PEN_b(PEN2)","PEG",
           "PFNa","PFNd","PFNm_a","PFNm_b","PFNp_a","PFNp_b","PFNp_c","PFNp_e","PFNv",
           "PFGs","PFL1","PFL3","PFR_a","PFR_b")
PBTpNames <- c("EPG","PEN1","PEN2","PEG",
               "PFNa","PFNd","PFNm_a","PFNm_b","PFNp_a","PFNp_b","PFNp_c","PFNp_e","PFNv",
               "PFG","PFL1","PFL3","PFR_a","PFR_b")
allvMDev <- c()
allimpDev <- c()
for (tp in 1:length(PBTps)){
  # Get the von Mises profiles
  vMOut <- EPGToD7Transform(PBTps[tp],actProfvM)

  # Get the profile stats
  D7OutputShape_stats <- D7ShapeMeanSD(vMOut)
  
  # Fit a cosine to the data
  fit <- D7CosFit(D7OutputShape_stats)
  allvMDev <- append(allvMDev,deviance(fit))
  
  # Get the impulse profiles
  impOut <- EPGToD7Transform(PBTps[tp],actProfImp)
  
  # Get the profile stats
  D7OutputShape_stats <- D7ShapeMeanSD(impOut)
  
  # Fit a cosine to the data
  fit <- D7CosFit(D7OutputShape_stats)
  allimpDev <- append(allimpDev,deviance(fit))
}
```

Plot the RSS
```{r}
plt_order = c("EPG","PEN1","PEN2","PEG","PFG",
              "PFNa","PFNd","PFNm_a","PFNm_b","PFNp_a","PFNp_b","PFNp_c","PFNp_e","PFNv",
              "PFL1","PFL3","PFR_a","PFR_b")

vM_stats <- data.frame(type = PBTpNames, resid = allvMDev, input = "von Mises input")
imp_stats <- data.frame(type = PBTpNames, resid = allimpDev, input = "impulse input")
all_stats = rbind(vM_stats,imp_stats)
all_stats$type = factor(all_stats$type, levels = as.factor(plt_order))

gStats_all <- ggplot(all_stats,aes(x=type,y=resid)) + geom_point(size=5, pch = 21, aes(fill = input)) +
  coord_cartesian(expand=FALSE,clip = 'off',ylim=c(0, 0.05)) + theme_paper() +
  xlab('neuron type') + ylab('residual sum of squares') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0)) + 
  scale_fill_manual(values = c('black','white'))
print(gStats_all)
```

Plot the neuron-to-neuron connections between the EPGs or Delta7s
```{r}
PBTpNames <- c("PEN_a(PEN1)","PEN_b(PEN2)","PEG",
               "PFNa","PFNd","PFNm_a","PFNm_b","PFNp_a","PFNp_b","PFNp_c","PFNp_e","PFNv",
               "PFGs","PFL1","PFL2","PFL3","PFR_a","PFR_b")

EPGD7ToPFX <- EPGD7Bag$outputs_raw %>% filter((roi=="PB") & (type.to %in% PBTpNames))
EPGD7ToPFX$nameOrder.from <- PBRename(EPGD7ToPFX$name.from,EPGD7ToPFX$from)
#EPGD7ToPFX$nameOrder.from <- EPGD7ToPFX$nameOrder.from %>% lapply(function(x) str_replace(x,'EPG_|Delta7_','')) %>% unlist() %>% lapply(function(x) str_replace(x,'_L-|_R-','-')) %>% unlist()
EPGD7ToPFX$nameOrder.to <- PBRename(EPGD7ToPFX$name.to,EPGD7ToPFX$to)
#EPGD7ToPFX$nameOrder.to <- EPGD7ToPFX$nameOrder.to %>% 
#  lapply(function(x) str_replace(x,'PEN1_|PEN2_|PFRa_|PFRb_|PFGs_|PFNma_|PFNmb_|PFNpa_|PFNpb_|PFNpc_|PFNpd_|PFNpe_|PFNd_|PFNv_|PFL1_|PFL2_|PFL3_|PEG_|PFNa_','')) %>% 
#  unlist() %>% lapply(function(x) str_replace(x,'_L-|_R-','-')) %>% unlist()

cmax = 200
PBEBTpNames <- c("PEN_a(PEN1)","PEN_b(PEN2)","PEG")
PBEBPlt <- ggplot(EPGD7ToPFX %>% filter(type.to %in% PBEBTpNames)) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
PBEBPlt <- structureMatrixPlotByType_lines(PBEBPlt)

cmax = 150
PFN1TpNames <- c("PFNa","PFNd","PFNm_a","PFNm_b","PFNv")
PFN1Plt <- ggplot(EPGD7ToPFX %>% filter(type.to %in% PFN1TpNames)) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
PFN1Plt <- structureMatrixPlotByType_lines(PFN1Plt)

cmax = 150
PFN2TpNames <- c("PFNp_a","PFNp_b","PFNp_c","PFNp_e")
PFN2Plt <- ggplot(EPGD7ToPFX %>% filter(type.to %in% PFN2TpNames)) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
PFN2Plt <- structureMatrixPlotByType_lines(PFN2Plt)

cmax = 200
PFXTpNames <- c("PFGs","PFL1","PFL2","PFL3","PFR_a","PFR_b")
PFXPlt <- ggplot(EPGD7ToPFX %>% filter(type.to %in% PFXTpNames)) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
PFXPlt <- structureMatrixPlotByType_lines(PFXPlt)

PFNPlts <-  PFN1Plt / PFN2Plt + plot_layout(guides = 'collect')

PEFXPlts <-  PBEBPlt / PFXPlt + plot_layout(guides = 'collect')
```


Group the EPGs that arborize in the same PB glomerulus - for the EPG to D7 connections
```{r}
EPGGpToindD7 <- EPGToD7 %>% 
  group_by(nameOrder.to, name.from) %>% summarize(totalWeight = sum(ROIweight))
EPGGpToindD7$nameOrder.from <- EPGGpToindD7$name.from %>% lapply(function(x) sub('\\(PB08\\)','',x)) %>% unlist()
EPGGpToindD7$nameOrder.from <- factor(EPGGpToindD7$nameOrder.from,
                                   levels = as.factor(c('EPG_L8','EPG_L7','EPG_L6','EPG_L5','EPG_L4','EPG_L3','EPG_L2','EPG_L1',
                                                        'EPG_R1','EPG_R2','EPG_R3','EPG_R4','EPG_R5','EPG_R6','EPG_R7','EPG_R8')))
EPGGpToindD7$nameOrder.to <- EPGGpToindD7$nameOrder.to %>% lapply(function(x) sub('elta','',sub('\\(PB15\\)','',x))) %>% unlist()
EPGGpToindD7$nameOrder.to <- factor(EPGGpToindD7$nameOrder.to, levels = as.factor(sort(unique(EPGGpToindD7$nameOrder.to),decreasing=TRUE)))
```
Plot the connectivity
```{r}
cmax=125
EPGtoD7_CM_IndGp <- ggplot(EPGGpToindD7) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=totalWeight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  coord_equal(ratio=1) + xlab("postsynaptic neuron") + ylab("presynaptic type") +
  guides(fill = guide_colourbar(title = '# of synapses', title.position = 'left', barwidth = 0.25, title.theme = element_text(angle=90)))
print(EPGtoD7_CM_IndGp)
```

Get the D7 to EPG connections
```{r}
D7ToEPG <- EPGD7ToSelf %>% filter(type.from == 'Delta7', type.to =='EPG')
D7ToEPG$nameOrder.to <- PBRename(D7ToEPG$name.to,D7ToEPG$to)
```

Group the EPGs that arborize in the same PB glomerulus - for the D7 to EPG connections
```{r}
indD7ToEPGGp <- D7ToEPG %>% 
  group_by(nameOrder.from, name.to) %>% summarize(totalWeight = sum(ROIweight))
indD7ToEPGGp$nameOrder.to <- indD7ToEPGGp$name.to %>% lapply(function(x) sub('\\(PB08\\)','',x)) %>% unlist()
indD7ToEPGGp$nameOrder.to <- factor(indD7ToEPGGp$nameOrder.to,
                                   levels = as.factor(c('EPG_L8','EPG_L7','EPG_L6','EPG_L5','EPG_L4','EPG_L3','EPG_L2','EPG_L1',
                                                        'EPG_R1','EPG_R2','EPG_R3','EPG_R4','EPG_R5','EPG_R6','EPG_R7','EPG_R8')))
indD7ToEPGGp$nameOrder.from <- indD7ToEPGGp$nameOrder.from %>% lapply(function(x) sub('elta','',sub('\\(PB15\\)','',x))) %>% unlist()
indD7ToEPGGp$nameOrder.from <- factor(indD7ToEPGGp$nameOrder.from, levels = as.factor(sort(unique(indD7ToEPGGp$nameOrder.from),decreasing=TRUE)))
```
Plot the connectivity
```{r}
cmax=125
D7toEPG_CM_IndGp <- ggplot(indD7ToEPGGp) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=totalWeight)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic neuron") +
  guides(fill = guide_colourbar(title = '# of synapses', title.position = 'left', barwidth = 0.25, title.theme = element_text(angle=90)))
print(D7toEPG_CM_IndGp)
```

For each D7, for each side, compare the peak input to peak output
-Create an angle map for the D7s (treating each side independently)
```{r}
EPGsToAngs <- data.frame(EPG = c("EPG_R1","EPG_L8","EPG_R2","EPG_L7","EPG_R3","EPG_L6","EPG_R4","EPG_L5",
                                 "EPG_R5","EPG_L4","EPG_R6","EPG_L3","EPG_R7","EPG_L2","EPG_R8","EPG_L1"),
                         ang = seq(from = pi, to = -pi, length.out = 17)[1:16] - pi/16)
```
-Plot the EPG angle map
```{r}
EPGsToAngs$EPG <- factor(EPGsToAngs$EPG, levels = PBGlomSort(EPGsToAngs$EPG))
EPGAngMap <- ggplot(EPGsToAngs) + geom_point(aes(y = EPG, x = ang)) + 
  scale_x_continuous(breaks = seq(from = -pi, to = pi, by = pi/2), limits = c(-pi,pi), expand = c(0,0)) +
  theme_paper() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0))
vints <- seq(from = -pi, to = pi, by = pi/16)
for (v in 1:length(vints)){
  EPGAngMap <- EPGAngMap + geom_vline(xintercept = vints[v], lty = 2)
}
EPGAngMap
```
-Compare the peaks
```{r}
# Get the individual D7 names
D7NmsInd <- levels(indD7ToEPGGp$nameOrder.from)

# Create an empty data frame to hold the angle differences
angOffsets_ind <- data.frame(offset = c(), RL = c())

inAngInd <- data.frame(inputAng = c(), outputGlom = c())
for (d in 1:length(D7NmsInd)){
  
  # Get the EPG to D7 connection data
  EPGToD7_ind <- EPGGpToindD7 %>% filter(nameOrder.to == D7NmsInd[d])
  EPGToD7_ind$ang <- EPGToD7_ind$nameOrder.from %>% lapply(function(x) EPGsToAngs[which(EPGsToAngs$EPG == x),]$ang) %>% unlist()
  
  # Get the mean input angle
  D7InAng_ind_circMean <- Arg(mean(EPGToD7_ind$totalWeight*exp(EPGToD7_ind$ang*1i)))
  
  # Get the right D7 to EPG connection data
  R_D7ToEPG_ind <- indD7ToEPGGp %>% filter(grepl("R",nameOrder.to), nameOrder.from == D7NmsInd[d])
  R_D7ToEPG_ind$ang <- R_D7ToEPG_ind$nameOrder.to %>% lapply(function(x) EPGsToAngs[which(EPGsToAngs$EPG == x),]$ang) %>% unlist()
  
  # Calculate the mean right angle
  R_D7OutAng_ind_circMean <- Arg(mean(R_D7ToEPG_ind$totalWeight*exp(R_D7ToEPG_ind$ang*1i)))
  
  # Get the left D7 to EPG connection data
  L_D7ToEPG_ind <- indD7ToEPGGp %>% filter(grepl("L",nameOrder.to), nameOrder.from == D7NmsInd[d])
  L_D7ToEPG_ind$ang <- L_D7ToEPG_ind$nameOrder.to %>% lapply(function(x) EPGsToAngs[which(EPGsToAngs$EPG == x),]$ang) %>% unlist()
  
  # Calculate the mean left angle
  L_D7OutAng_ind_circMean <- Arg(mean(L_D7ToEPG_ind$totalWeight*exp(L_D7ToEPG_ind$ang*1i)))
  
  # Calculate the input to output differences
  R_angDiff_ind_circMean <- (D7InAng_ind_circMean - R_D7OutAng_ind_circMean) %% (2*pi)
  angOffsets_ind <- rbind(angOffsets_ind, data.frame(offset = R_angDiff_ind_circMean, RL = "R"))
  L_angDiff_ind_circMean <- (D7InAng_ind_circMean - L_D7OutAng_ind_circMean) %% (2*pi)
  angOffsets_ind <- rbind(angOffsets_ind, data.frame(offset = L_angDiff_ind_circMean, RL = "L"))
  
  inAngInd <- rbind(inAngInd, data.frame(inputAng = D7InAng_ind_circMean, outputGlom = strsplit(D7NmsInd[d],'_')[[1]][2]))
}
```
-Plot the peak differences
```{r}
meanOffsets_ind <- angOffsets_ind %>% group_by(RL) %>% summarize(mean = mean(offset))

angOffsetPltInd <- ggplot(angOffsets_ind) + geom_jitter(aes(x = as.factor(RL), y = offset, color = 'pt'), width = 0.25, alpha = 0.5) +
  geom_point(data = meanOffsets_ind, aes(x = as.factor(RL), y = mean, color = 'mean'), size = 2, shape = 21) +
  geom_hline(yintercept = pi) +
  geom_hline(yintercept = pi - pi/16, lty = 2) + geom_hline(yintercept = pi + pi/16, lty = 2) +
  scale_y_continuous(breaks = seq(from = 0, to = 2*pi, by = pi/2), limits = c(0,2*pi), expand = c(0,0)) +
  scale_color_manual(values = c('pt' = 'black', 'mean' = 'red')) +
  xlab('PB output side') + ylab('input to output peak offset') +
  theme_paper()# + ggtitle('EPG inputs grouped, individual D7s')

angOffsetPltInd
```
Plot the input peaks
```{r}
InOutAngComp <- ggplot(inAngInd) + geom_point(aes(x = as.factor(outputGlom), y = inputAng), alpha = 0.5) +
  scale_y_continuous(breaks = seq(from = -pi, to = pi, by = pi/2), limits = c(-pi,pi)) +
  xlab('D7 output gloms') + ylab('input angle') +
  theme_paper() + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0))
vints <- seq(from = -pi, to = pi, by = pi/4) + pi/8
for (v in 1:length(vints)){
  InOutAngComp <- InOutAngComp + geom_hline(yintercept = vints[v], lty = 2)
}
InOutAngComp
```

Combine all plots into one figure
```{r, fig.width = 8, fig.height = 8}
design = "
 1112
 1112
 3332
 4455
 4455
 4455"
D7InOutComp <- EPGtoD7_CM_IndGp + D7toEPG_CM_IndGp +
  EPGAngMap + InOutAngComp + angOffsetPltInd + 
  plot_layout(design = design, guides = 'collect')
D7InOutComp
```


