---
title: "Layered CX layout"
output: html_notebook
---

Load the libraries
```{r}
library(neuprintr)
library(neuprintrExtra)
library(tidyverse)
library(cowplot)
library(reshape2)
library(igraph)
library(ggraph)
library(paletteer)
library(patchwork)
source("C:\\Users\\dantu\\Documents\\neuprintR-notebooks\\R\\paperTheme.R")
source("C:\\Users\\dantu\\Documents\\neuprintR-notebooks\\R\\visualizeConnectivityTables.R")
source("C:\\Users\\dantu\\Documents\\neuprintR-notebooks\\EBFigures\\EBUtils.R")
```

Specify the types of interest and get the neuronBag for them
```{r}
nrons <- c("TuBu01", "TuBu02", "TuBu08", "TuBu09", "LAL138", "WED016",
          "ER4m", "ER3a_a", "ER3a_d", "ER3m", "ER4d", "ER2_a", "ER2_b", "ER2_d", "ER1_b", "ER1_a",
          "EPG", 
          "PEN_a(PEN1)", "PEG", 
          "Delta7",
          "PFNd","PFNv","PFNp_d", "PFNa", 
          "FC1A", "FC1B", "FC1C", "FC1D", "FC1E", "FC1F", "hDeltaB", "hDeltaC",
          "hDeltaA", "PFR_a","hDeltaG", "hDeltaH", "hDeltaI","vDeltaK",#"vDeltaL","PFR_b",
          "PFL1", "PFL2","PFL3",
          "LAL018","LAL046",
          "DNb01","DNa02","DNa04")
CXBag <- neuronBag(getTypesTable(nrons),by.roi=FALSE)
```

Laterialize specific types from the neuronBag
```{r}
nrons2lat <- c("TuBu01", "TuBu02", "TuBu08", "TuBu09", "LAL138", "WED016",
          "ER4m", "ER3a_a", "ER3a_d", "ER3m", "ER4d", "ER2_a", "ER2_b", "ER2_d", "ER1_b", "ER1_a",
          "EPG", "PEN_a(PEN1)", "PEG")
CXBag_lat <- lateralize_types(CXBag,typeList=nrons2lat)
```

Get the connectivity tables
```{r}
types4plt <- c("TuBu01_R", "TuBu02_R", "TuBu08_R", "TuBu09_R", "LAL138_L", "WED016_R",
          "ER4m_R", "ER3a_a_R", "ER3a_d_R", "ER3m_R", "ER4d_R", "ER2_a_R", "ER2_b_R", "ER2_d_R", "ER1_b_R", "ER1_a_R",
          "EPG_L", "EPG_R", 
          "PEN_a(PEN1)_L", "PEN_a(PEN1)_R", "PEG_L", "PEG_R", 
          "Delta7",
          "PFNd","PFNv","PFNp_d", "PFNa",
          "FC1A", "FC1B", "FC1C", "FC1D", "FC1E", "FC1F", "hDeltaB", "hDeltaC",
          "hDeltaA", "PFR_a","hDeltaG", "hDeltaH", "hDeltaI","vDeltaK",#"vDeltaL","PFR_b",
          "PFL1", "PFL2","PFL3",
          "LAL018","LAL046",
          "DNb01","DNa02","DNa04")
layers <- c(1,1,1,1,1,1,
            2,2,2,2,2,2,2,2,2,2,
            3,3,
            4,4,4,4,
            5,
            6,6,6,6,
            7,7,7,7,7,7,7,7,
            8,8,8,8,8,8,#8,8,
            9,9,9,
            10,10,
            11,11,11)
layerMap <- data.frame(type = types4plt,
                       layer=layers)
CX_T2T <- CXBag_lat$outputs %>% 
  filter(type.from %in% types4plt,
         type.to %in% types4plt)
```

Now, convert it into an igraph function
```{r}
CXNodes <- c(as.character(CX_T2T$type.to),as.character(CX_T2T$type.from)) %>% unique() %>% as.data.frame()
colnames(CXNodes) <- "nodes"
CXNodes$supertype <- CXNodes$nodes %>% supertype()
CXNodes$layer <- CXNodes$nodes %>% sapply(function(n) layerMap[which(n==layerMap$type),]$layer)

CXEdges <- CX_T2T %>% mutate(from = type.from, to = type.to, weight = weightRelative) %>%
  select(from,to,weight)
CXEdges$supertype.from <- CXEdges$from %>% supertype()

g <- graph_from_data_frame(CXEdges, directed = TRUE, vertices = CXNodes)


# Assign colors to the supertypes
sTs <- supertype2Palette()
sTs$breaks <- c(sTs$breaks,c("TuBu","WED","LAL","DN"))
sTs$pal <- c(sTs$pal, c(paletteer_d("Polychrome::palette36")[1:4]))
names(sTs$pal) <- sTs$breaks
sTScale <- scale_colour_manual(values=sTs$pal,breaks = sTs$breaks)
sTScale_edge <- scale_edge_colour_manual(values=sTs$pal,breaks = sTs$breaks,guide = FALSE)


CXRNN <- ggraph(g,layout='sugiyama', layers=CXNodes$layer,vgap=2) +
  geom_edge_fan(aes(width=weight,color=supertype.from),alpha=0.75,
                      strength=1,
                      end_cap = circle(0.1, 'cm')) + 
  geom_edge_loop(aes(direction=45,span=90,width=weight,color=supertype.from,strength=1),alpha=0.75) +
  geom_node_point(aes(color=supertype),size=8) + 
  scale_edge_width(range = c(0, 6)) +
  sTScale_edge +
  sTScale +
  #geom_node_text(aes(label=CXNodes$nodes)) +
  theme_paper() +
  coord_fixed(ratio = 1,clip="off") + 
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank())

print(CXRNN)
ggsave('C:\\Users\\dantu\\Dropbox (Personal)\\Professional\\Figures\\FIBSEM\\CXRNN_V5_noLabel.pdf',CXRNN,
       width = 16, height = 9, units = "in")
```


Specify the types of interest and get the neuronBag for them
```{r}
#nrons <- c("ER3a_a", "ER3a_b", "ER3a_c", "ER3a_d",
#           "ER3d_a", "ER3d_b", "ER3d_c", "ER3d_d",
#           "ER3m","EPG")
nrons <- c("ER4m", "ER3a_a", "ER3a_d", "ER3m", "ER4d", "ER2_a", "ER2_b", "ER2_d", "ER1_b", "ER1_a",
           "EPG")
#layers <- c(1,1,1,1,
#            1,1,1,1,
#            1,2)
layers <- c(1,1,1,1,1,1,1,1,1,1,
            2)
layerMap <- data.frame(type = nrons,
                       layer=layers)
ERBag <- neuronBag(getTypesTable(nrons),by.roi=FALSE)
```

Get the connectivity tables
```{r}
ER_CT <- ERBag$outputs_raw %>% 
  filter(type.from %in% nrons,
         type.to %in% nrons)
ER_CT$nameOrder.from <- EBGlomOrder(ER_CT$name.from,ER_CT$from,"EB") 
ER_CT$nameOrder.to <- EBGlomOrder(ER_CT$name.to,ER_CT$to,"EB") 
```

Now, convert it into an igraph function
```{r}
ERNodes <- c(as.character(ER_CT$nameOrder.to),as.character(ER_CT$nameOrder.from)) %>% unique() %>% as.data.frame()
colnames(ERNodes) <- "nodes"
ERNodes$type <- ERNodes$nodes %>% sapply(function(n) substring(n,1,gregexpr("_L|_R",n)[[1]][1]-1))
ERNodes$supertype <- ERNodes$type %>% supertype()
ERNodes$layer <- ERNodes$type %>% sapply(function(t) layerMap[which(t==layerMap$type),]$layer)

EREdges <- ER_CT %>% mutate(from = nameOrder.from, to = nameOrder.to, weight = ROIweight) %>%
  select(from,to,weight)
EREdges$supertype.from <- EREdges$from %>% sapply(function(f) supertype(substring(as.character(f),1,gregexpr("_L|_R",f)[[1]][1]-1)))

g <- graph_from_data_frame(EREdges, directed = TRUE, vertices = ERNodes)

# Assign colors to the supertypes
sTs <- supertype2Palette()
sTScale <- scale_colour_manual(values=sTs$pal,breaks = sTs$breaks)
sTScale_edge <- scale_edge_colour_manual(values=sTs$pal,breaks = sTs$breaks,guide = FALSE)


ERRNN <- ggraph(g)+#,layout='sugiyama', layers=ER3Nodes$layer,vgap=10) +
  geom_edge_fan(aes(width=weight,color=supertype.from),alpha=0.5,
                      strength=1,
                      end_cap = circle(0.2, 'cm')) + 
  geom_edge_loop(aes(direction=45,span=90,width=weight,color=supertype.from,strength=1),alpha=0.5) +
  geom_node_point(aes(color=supertype),size=4) + 
  scale_edge_width(range = c(0, 2)) +
  sTScale_edge +
  sTScale +
  theme_paper() +
  coord_fixed(ratio = 1,clip="off") + 
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank())

print(ERRNN)
ggsave('C:\\Users\\dantu\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\ERRNN_force.pdf',ERRNN)
```
ERBag
Plot the ordered connection table
```{r}
ERCT_Ordered_Plt <- plotConnectivityMatrix(ER_CT, byGroup = "id_sort")
ERCT_Ordered_Plt <- ERCT_Ordered_Plt + theme_paper() + xlab("postsynaptic neuron") + ylab("presynaptic neuron")
ERCT_Ordered_Plt <- structureMatrixPlotByType_lines(ERCT_Ordered_Plt)

print(ERCT_Ordered_Plt)
```
Plot a randomly order connection table
```{r}
ERCT_Rand <- ER_CT
ERCT_Rand$nameOrder.to <- factor(ERCT_Rand$to, levels = sample(unique(ERCT_Rand$to)))
ERCT_Rand$nameOrder.from <- factor(ERCT_Rand$from, levels = sample(unique(ERCT_Rand$from)))

ERCT_Rand_Plt <- plotConnectivityMatrix(ERCT_Rand, byGroup = "id_sort")
ERCT_Rand_Plt <- ERCT_Rand_Plt + theme_paper() + xlab("postsynaptic neuron") + ylab("presynaptic neuron") + theme(axis.text = element_blank())

print(ERCT_Rand_Plt)
```
Save the plot
```{r}
RadnVsOrd_ER <- ERCT_Rand_Plt + ERCT_Ordered_Plt + plot_layout(guides='collect')
ggsave('C:\\Users\\dantu\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\OrderedVsShuffledCT_ER.pdf',RadnVsOrd_ER,
       width = 8, height = 4, units = "in")
```

Get the connection table for FB types of interest
```{r}
FBNrons <- c("PFNp_d", "PFNa",
             "FC1A", "FC1B", "FC1C", "FC1D", "FC1E", "FC1F",
             "hDeltaB", "hDeltaC","hDeltaA", "PFR_a","hDeltaG", "hDeltaH", "hDeltaI",
             "vDeltaK","vDeltaL","PFR_b",
             "PFL1", "PFL2","PFL3")

FBCT <- getConnectionTable(getTypesTable(FBNrons)$bodyid, "POST",slctROI="FB")
```
Plot the ordered connection table
```{r}
FBCT_Ordered_Plt <- plotConnectivityMatrix(FBCT %>% filter(type.to %in% FBNrons))
FBCT_Ordered_Plt <- FBCT_Ordered_Plt + theme_paper() + xlab("postsynaptic neuron") + ylab("presynaptic neuron")
FBCT_Ordered_Plt <- structureMatrixPlotByType_lines(FBCT_Ordered_Plt)

print(FBCT_Ordered_Plt)
```
Plot a randomly order connection table
```{r}
FBCT_Rand <- FBCT %>% filter(type.to %in% FBNrons)
FBCT_Rand$nameOrder.to <- factor(FBCT_Rand$to, levels = sample(unique(FBCT_Rand$to)))
FBCT_Rand$nameOrder.from <- factor(FBCT_Rand$from, levels = sample(unique(FBCT_Rand$from)))

FBCT_Rand_Plt <- plotConnectivityMatrix(FBCT_Rand, byGroup = "id_sort")
FBCT_Rand_Plt <- FBCT_Rand_Plt + theme_paper() + xlab("postsynaptic neuron") + ylab("presynaptic neuron") + theme(axis.text = element_blank())

print(FBCT_Rand_Plt)
```
Save the plot
```{r}
RadnVsOrd <- FBCT_Rand_Plt + FBCT_Ordered_Plt + plot_layout(guides='collect')
ggsave('C:\\Users\\dantu\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\OrderedVsShuffledCT.pdf',RadnVsOrd,
       width = 8, height = 4, units = "in")
```

