---
title: "Notebook analyzing the input and output pathways of the EB at the ROI level"
output:
  html_document:
    df_print: paged
---

### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(plotly)
library(dplyr)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="EB"  

# Directory to save data to.
SaveDir="Z:/Cx_Connectome/BradData/EB_Analysis/"

# Directory to save plots to.
PlotDir="Z:/Cx_Connectome/BradData/EB_Analysis/RingNeuronSynapseLocs/"

```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}
source("inputOutputRegionsVis.r")
source("GetNeuronsInRoi.R")
```

### Get neuprint ROIs 
```{r}
roisDf = get_rois_df()
```

### Get neurons in the ROI
```{r}

NamedBodies = Get_AllNeurons_InRoi(ROI, FALSE)
NamedBodies =  mutate(NamedBodies, cropped = neuprint_get_meta(bodyid)$cropped)

```

### Threshold neurons (need to agree on criteria and clean up code)
```{r}

PreMaxThresh=10
PostMaxThresh=10
Output <-  SynapseStats_And_Threshold(NamedBodies, SaveDir, PreMaxThresh, PostMaxThresh)
list2env(Output ,.GlobalEnv)
remove(Output)

```

### Get the number of synapses in each ROI for individual neurons and individual neuron types
```{r message=FALSE, warning=FALSE}

minSynapses = 10
Output=InputOutput_ROI_PerNeuron(NamedBodies, minSynapses)
list2env(Output ,.GlobalEnv)
remove(Output)

```

### Set synapse count threshold, below which to exclude ROIs 
```{r}

SynThresh=30

```

## Make plot of ALL neurons in ALL ROis
```{r}

# Make roi and cell names for all EB neurons
plotdata=roi_Connect_bytype_df
plotdata$roi_names = paste(roi_Connect_bytype_df$roi, '(', roi_Connect_bytype_df$roi_hemi, ')', sep="")
plotdata$type_name = paste(roi_Connect_bytype_df$type, '(', roi_Connect_bytype_df$neuron_hemi, ')', sep="")

# Plot all of the ROIs (and sub ROIs) that all EB neurons innervate
p0<-ggplot(plotdata, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL EB Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "ALL_EB_","inputOutputRegions_perType.pdf",sep=""), plot = p0, device='pdf', scale = 1, width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "ALL_EB_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


```


# Look at just the right ring neurons, since all ring neurons innervate only one hemisphere.
```{r}

# Get just the ring neuron data
Rneuron_Connect_bytype_df=filter(roi_Connect_bytype_df, startsWith(unlist(roi_Connect_bytype_df$type), "R"))
Rneuron_Connect_bytype_df$roi_names = paste(Rneuron_Connect_bytype_df$roi, '(', Rneuron_Connect_bytype_df$roi_hemi, ')', sep="")
Rneuron_Connect_bytype_df$type_name = paste(Rneuron_Connect_bytype_df$type, '(', Rneuron_Connect_bytype_df$neuron_hemi, ')', sep="")

# Get right ring neurons 
R_R_plotdata=filter(Rneuron_Connect_bytype_df, neuron_hemi=='R')

# Plot all of the ROIs (and sub ROIs) that the right ring neurons innervate
p1<-ggplot(R_R_plotdata, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Right Ring Neuron Input/Output ROIs")
print(p1)
ggsave(paste(PlotDir, "RingNeuronRight_","inputOutputRegions_perType.pdf",sep=""), plot = p1, device='pdf', scale = 1, width = 14, height = 8, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "RingNeuronRight_","inputOutputRegions_perType.png",sep=""), plot = p1, device='png', scale = 1, width = 14, height = 8, units ="in", dpi = 600, limitsize = TRUE)


# Threshold based on synapse counts and plot again with ROIs arranged
R_R_plotdataSubset=filter(R_R_plotdata, R_R_plotdata$count > SynThresh)
R_R_plotdataSubset=filter(R_R_plotdataSubset, !(R_R_plotdataSubset$roi %in% "LX") )
R_R_plotdataSubset$roi_names = as.factor(R_R_plotdataSubset$roi_names)
R_R_plotdataSubset$roi_names <- factor(R_R_plotdataSubset$roi_names, levels = c("BU(R)","LAL(R)","GA(R)","EB(C)", "EBr1(C)","EBr2r4(C)","EBr3am(C)","EBr3d(C)","EBr3pw(C)","EBr5(C)","EBr6(C)"))

p2<-ggplot(R_R_plotdataSubset, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) + 
  facet_grid(cols=vars(prepost)) + theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) + 
  ggtitle(paste("Right Ring Neuron Input/Output ROIs with #synapses > ",as.character(SynThresh),sep=""))
print(p2)
ggsave(paste(PlotDir, "F_RingNeuronRight_Thresh_","inputOutputRegions_perType.pdf",sep=""), plot = p2, device='pdf', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "F_RingNeuronRight_Thresh_","inputOutputRegions_perType.png",sep=""), plot = p2, device='png', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)

remove(list=c("p1","p2"))

```



# Look at just the ExRs
```{r}

# Get just the ExR neuron data
ExRneuron_Connect_bytype_df=filter(roi_Connect_bytype_df, startsWith(unlist(roi_Connect_bytype_df$type), "ExR"))

# add an ROI name field
ExRneuron_Connect_bytype_df$roi_names = paste(ExRneuron_Connect_bytype_df$roi, '(', ExRneuron_Connect_bytype_df$roi_hemi, ')', sep="")
ExRneuron_Connect_bytype_df$type_name = paste(ExRneuron_Connect_bytype_df$type, '(', ExRneuron_Connect_bytype_df$neuron_hemi, ')', sep="")

# Plot all of the ROIs (and sub ROIs) that the ALLs ExRs innervate
p3<-ggplot(ExRneuron_Connect_bytype_df, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL ExR Input/Output ROIs with #synapses")
print(p3)
ggsave(paste(PlotDir, "ExR_ALL_","InOutRegions_perType.pdf",sep=""), plot = p3, device='pdf', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "ExR_ALL_","InOutRegions_perType.png",sep=""), plot = p3, device='png', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)


# Filter by synapse counts
ExRneuron_Connect_bytype_dfThresh=filter(ExRneuron_Connect_bytype_df, count>SynThresh)

# Plot all ExRs again
p4<-ggplot(ExRneuron_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL ExR  Input/Output ROIs with #synapses count thresholding at ",as.character(SynThresh),sep=""))
print(p4)
ggsave(paste(PlotDir, "ExR_ALLThresh1_","InOutRegions_perType.pdf",sep=""), plot = p4, device='pdf', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "ExR_ALLThresh1_","InOutRegions_perType.png",sep=""), plot = p4, device='png', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)


# Filter out some ROIs
ExRneuron_Connect_bytype_dfThresh=filter(ExRneuron_Connect_bytype_dfThresh, !(ExRneuron_Connect_bytype_dfThresh$roi %in% c("LX","CX","None","FB-column3")))

# Plot all ExRs again
p5<-ggplot(ExRneuron_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL ExR  Input/Output ROIs with #synapses count thresholding at ",as.character(SynThresh),sep=""))
print(p5)
ggsave(paste(PlotDir, "ExR_ALLThresh2_","InOutRegions_perType.pdf",sep=""), plot = p5, device='pdf', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "ExR_ALLThresh2_","InOutRegions_perType.png",sep=""), plot = p5, device='png', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)


# Plot the ExRs again, but excluding Fb and Eb subregions
ExRneuron_Connect_bytype_dfThresh_NoLayers=filter(ExRneuron_Connect_bytype_dfThresh, !(startsWith(ExRneuron_Connect_bytype_dfThresh$roi,"EBr") | startsWith(ExRneuron_Connect_bytype_dfThresh$roi,"FBl")) )

p6<-ggplot(ExRneuron_Connect_bytype_dfThresh_NoLayers, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL ExR  Input/Output ROIs with #synapses count thresholding at ",as.character(SynThresh),sep=""))
print(p6)
ggsave(paste(PlotDir, "F_ExR_ALLThresh2_NoLayers_","InOutRegions_perType.pdf",sep=""), plot = p6, device='pdf', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "F_ExR_ALLThresh2_NoLayers_","InOutRegions_perType.png",sep=""), plot = p6, device='png', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)

# Plot the ExRs again, but only in EB
ExRneuron_Connect_bytype_dfThresh_EBLayers=filter(ExRneuron_Connect_bytype_dfThresh, (startsWith(ExRneuron_Connect_bytype_dfThresh$roi,"EB")))

p7<-ggplot(ExRneuron_Connect_bytype_dfThresh_EBLayers, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL ExR  Input/Output ROIs with #synapses count thresholding at ",as.character(SynThresh),sep=""))
print(p7)
ggsave(paste(PlotDir, "F_ExR_ALLThresh2_EBLayers_","InOutRegions_perType.pdf",sep=""), plot = p7, device='pdf', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "F_ExR_ALLThresh2_EBLayers_","InOutRegions_perType.png",sep=""), plot = p7, device='png', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)


# Plot the ExRs again, but only in FB
ExRneuron_Connect_bytype_dfThresh_FBLayers=filter(ExRneuron_Connect_bytype_dfThresh, (startsWith(ExRneuron_Connect_bytype_dfThresh$roi,"FB")))

p8<-ggplot(ExRneuron_Connect_bytype_dfThresh_FBLayers, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL ExR  Input/Output ROIs with #synapses after count thresholding at ",as.character(SynThresh),sep=""))
print(p8)
ggsave(paste(PlotDir, "F_ExR_ALLThresh2_FBLayers_","InOutRegions_perType.pdf",sep=""), plot = p8, device='pdf', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "F_ExR_ALLThresh2_FBLayers_","InOutRegions_perType.png",sep=""), plot = p8, device='png', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)

remove(list=c("p3","p4","p5","p6","p7","p8"))


```



### Make same facet plots for all EB neurons that are not ring neurons or ExRs
```{r}

# Get all neurons that are not ring or ExRs
NonR_Connect_bytype_df=filter(roi_Connect_bytype_df, !(startsWith(unlist(roi_Connect_bytype_df$type), "ExR") | startsWith(unlist(roi_Connect_bytype_df$type), "R")) )

# add an ROI name field
NonR_Connect_bytype_df$roi_names = paste(NonR_Connect_bytype_df$roi, '(', NonR_Connect_bytype_df$roi_hemi, ')', sep="")
NonR_Connect_bytype_df$type_name = paste(NonR_Connect_bytype_df$type, '(', NonR_Connect_bytype_df$neuron_hemi, ')', sep="")

# Plot all of the ROIs (and sub ROIs) that the ALLs Non Rs innervate
p9<-ggplot(NonR_Connect_bytype_df, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL Non R Input/Output ROIs with #synapses")
print(p9)
ggsave(paste(PlotDir, "NonR_ALL_","InOutRegions_perType.pdf",sep=""), plot = p9, device='pdf', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "NonR_ALL_","InOutRegions_perType.png",sep=""), plot = p9, device='png', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)


# Filter by synapse counts
NonR_Connect_bytype_dfThresh=filter(NonR_Connect_bytype_df, count>SynThresh)

# Plot all Non Rs again
p10<-ggplot(NonR_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL Non R  Input/Output ROIs with #synapses after count thresholding at ",as.character(SynThresh),sep=""))
print(p10)
ggsave(paste(PlotDir, "NonR_ALLThresh1_","InOutRegions_perType.pdf",sep=""), plot = p10, device='pdf', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "NonR_ALLThresh1_","InOutRegions_perType.png",sep=""), plot = p10, device='png', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)



# Filter out some ROIs
NonR_Connect_bytype_dfThresh=filter(NonR_Connect_bytype_dfThresh, !(NonR_Connect_bytype_dfThresh$roi %in% c("LX","CX","None","FB-column3")))

# Plot all Non Rs again
p11<-ggplot(NonR_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL Non R  Input/Output ROIs with #synapses after count thresholding at ",as.character(SynThresh),sep=""))
print(p11)
ggsave(paste(PlotDir, "NonR_ALLThresh2_","InOutRegions_perType.pdf",sep=""), plot = p11, device='pdf', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "NonR_ALLThresh2_","InOutRegions_perType.png",sep=""), plot = p11, device='png', scale = 1, width = 20, height = 8, units ="in", dpi = 600, limitsize = TRUE)


# Plot the Non Rs again, but excluding Fb and Eb subregions
NonR_Connect_bytype_dfThresh_NoLayers=filter(NonR_Connect_bytype_dfThresh, !(startsWith(NonR_Connect_bytype_dfThresh$roi,"EBr") | startsWith(NonR_Connect_bytype_dfThresh$roi,"FBl")) )

p12<-ggplot(NonR_Connect_bytype_dfThresh_NoLayers, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL Non R  Input/Output ROIs with #synapses after count thresholding at ",as.character(SynThresh),sep=""))
print(p12)
ggsave(paste(PlotDir, "F_NonR_ALLThresh2_NoLayers_","InOutRegions_perType.pdf",sep=""), plot = p12, device='pdf', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "F_NonR_ALLThresh2_NoLayers_","InOutRegions_perType.png",sep=""), plot = p12, device='png', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)

# Plot the Non Rs again, but only in EB
NonRneuron_Connect_bytype_dfThresh_EBLayers=filter(NonR_Connect_bytype_dfThresh, (startsWith(NonR_Connect_bytype_dfThresh$roi,"EB")))

p13<-ggplot(NonRneuron_Connect_bytype_dfThresh_EBLayers, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL Non R  Input/Output ROIs with #synapses after count thresholding at ",as.character(SynThresh),sep=""))
print(p13)
ggsave(paste(PlotDir, "F_NonR_ALLThresh2_EBLayers_","InOutRegions_perType.pdf",sep=""), plot = p13, device='pdf', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "F_NonR_ALLThresh2_EBLayers_","InOutRegions_perType.png",sep=""), plot = p13, device='png', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)

# Plot the Non Rs again, but only in FB
NonRneuron_Connect_bytype_dfThresh_FBLayers=filter(NonR_Connect_bytype_dfThresh, (startsWith(NonR_Connect_bytype_dfThresh$roi,"FB")))

p14<-ggplot(NonRneuron_Connect_bytype_dfThresh_FBLayers, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle(paste("ALL Non R  Input/Output ROIs with #synapses after count thresholding at ",as.character(SynThresh),sep=""))
print(p14)
ggsave(paste(PlotDir, "F_NonR_ALLThresh2_FBLayers_","InOutRegions_perType.pdf",sep=""), plot = p14, device='pdf', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)
ggsave(paste(PlotDir, "F_NonR_ALLThresh2_FBLayers_","InOutRegions_perType.png",sep=""), plot = p14, device='png', scale = 1, width = 14, height = 7, units ="in", dpi = 600, limitsize = TRUE)

remove(list=c("p9","p10","p11","p12","p13","p14"))


```




# Get synapse distribution for all ring neurons
```{r}


# Get type name for all ring neurons
UniqueNamedBodies=as.character(unique(NamedBodies$bodytype))
RingNeuronTypes=UniqueNamedBodies[startsWith(unlist(UniqueNamedBodies), "R")]
RingNeuronBodies=filter(NamedBodies, startsWith(as.character(unlist(NamedBodies$bodytype)), "R") )

# Get all synapses for the ring neurons
for (typeNow in 1:length(RingNeuronTypes)){
  # Get BU synapses
  RingNeuronSyns = NamedBodies[ which(unlist(NamedBodies$bodytype) == RingNeuronTypes[typeNow]),]$bodyid %>% neuprint_get_synapses()
  RingNeuronSyns <-  RingNeuronSyns %>% mutate(name=as.character(RingNeuronTypes[typeNow]))%>%     mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
  if (typeNow==1){
    RingNeuronSynsAll= RingNeuronSyns
  }else{
    RingNeuronSynsAll <- rbind(RingNeuronSynsAll,RingNeuronSyns)
  }
  
}



```

# Make plot of each ring neuron's distribution of synapses 
```{r}



# Get neuron morphologies
MorphFile=paste(SaveDir,"RingNeuronMorpho.rds",sep="")
if (file.exists(MorphFile)){
  RingNeuronMorpho=readRDS(MorphFile)
} else {
  RingNeuronMorpho = neuprint_read_neurons(RingNeuronBodies$bodyid)
  saveRDS(RingNeuronMorpho, file = RingNeuronMorpho)
}

# Get min/max of x,y,z from morphologies
RingNeuronCharacter=names(RingNeuronMorpho)
X_MaxOut=c()
X_MinOut=c()
Y_MaxOut=c()
Y_MinOut=c()
Z_MaxOut=c()
Z_MinOut=c()
for (NNN in 1:length(RingNeuronCharacter)){
  X_tempstring=paste("RingNeuronMorpho$'",as.symbol(as.name(RingNeuronCharacter[NNN])),"'$d$X",sep="")
  Y_tempstring=paste("RingNeuronMorpho$'",as.symbol(as.name(RingNeuronCharacter[NNN])),"'$d$Y",sep="")
  Z_tempstring=paste("RingNeuronMorpho$'",as.symbol(as.name(RingNeuronCharacter[NNN])),"'$d$Z",sep="")
  
  
  X_MaxOut=max( c(X_MaxOut, max(eval(parse(text=X_tempstring))) ) )
  X_MinOut=min( c(X_MinOut, min(eval(parse(text=X_tempstring))) ) )
  Y_MaxOut=max( c(Y_MaxOut, max(eval(parse(text=Y_tempstring))) ) )
  Y_MinOut=min( c(Y_MinOut, min(eval(parse(text=Y_tempstring))) ) )
  Z_MaxOut=max( c(Z_MaxOut, max(eval(parse(text=Z_tempstring))) ) )
  Z_MinOut=min( c(Z_MinOut, min(eval(parse(text=Z_tempstring))) ) )
  
}

# Get max and min synapse positions, since clipping doesnt work well.
XLIM=c( min(c(RingNeuronSynsAll$x,X_MinOut)) , max(c(RingNeuronSynsAll$x),X_MaxOut) )
YLIM=c( min(c(RingNeuronSynsAll$y,Y_MinOut)) , max(c(RingNeuronSynsAll$y),Y_MaxOut) )
ZLIM=c( min(c(RingNeuronSynsAll$z,Z_MinOut)) , max(c(RingNeuronSynsAll$z),Z_MaxOut) )


# Get meshes for ROIs
ebMesh = neuprint_ROI_mesh("EB")
RbuMesh = neuprint_ROI_mesh("BU(R)")
noMesh = neuprint_ROI_mesh("NO")
lalMesh = neuprint_ROI_mesh("LAL(R)")
galMesh = neuprint_ROI_mesh("GA(R)")


# Get view file
RingNeuronView= readRDS('Z:/Cx_Connectome/BradData/code/RingNeuronView.rds')

# For each ring neuron type, loop over and plot synapse distributions
for (typeNow in 1:length(RingNeuronTypes)){

  
  TempBodies=NamedBodies$bodyid[ as.character(NamedBodies$bodytype)==RingNeuronTypes[typeNow] ]
  
  TempMorphos=RingNeuronMorpho[as.character(TempBodies)]
  TempMorphos=TempMorphos[lengths(TempMorphos) != 0 ]

  
  RingNeuronSyns = subset(RingNeuronSynsAll,RingNeuronSynsAll$name==RingNeuronTypes[typeNow])
  
  # Assign synapses into pre and post groups
  RingNeuronSyns_Post = RingNeuronSyns %>% filter(prepost==0) 
  RingNeuronSyns_Pre = RingNeuronSyns %>% filter(prepost==1)
  
  # Get view paramters
  #zoom<-par3d()$zoom
  #userMatrix<-par3d()$userMatrix
  #windowRect<-par3d()$windowRect
  #bbox2<-par3d()$bbox
  #scale<-par3d()$scale
  #viewport<-par3d()$viewport
  #FOV<-par3d()$FOV
  #pp2 <- par3d(no.readonly=TRUE)
  
  nclear3d()
  
  
  bgplot3d({
    plot.new()
    title(main = as.character(RingNeuronTypes[typeNow]), line = 3)})
  
  plot3d(RingNeuronSyns_Pre[c('x','y','z')], col='seagreen3', xlim = c(XLIM), ylim = YLIM, zlim = ZLIM,	forceClipregion = TRUE)
  plot3d(RingNeuronSyns_Post[c('x','y','z')], col='violet', add=TRUE, xlim = XLIM, ylim = YLIM, zlim = ZLIM,	forceClipregion = TRUE)
  
  
  plot3d(TempMorphos,color="black")
  plot3d(ebMesh, color="blue", alpha=0.1,  WithNodes=FALSE, add=TRUE)
  plot3d(RbuMesh, color="blue", alpha=0.1,  WithNodes=FALSE, add=TRUE)
  plot3d(noMesh, type="shade", alpha=0.05,  WithNodes=FALSE, add=TRUE)
  plot3d(lalMesh, type="shade", alpha=0.05,  WithNodes=FALSE, add=TRUE)
  plot3d(galMesh, type="shade", alpha=0.05,  WithNodes=FALSE, add=TRUE)
  decorate3d(box=FALSE) 
  #aspect3d(1,1,1)
  listener=par3d()$listener
   

  #FrontView=rbind(c(1,0,0,0),c(0, -0.15,-1,0),c(0, 1, -0.14,0),c(0,0,0,1))
  #par3d(zoom=0.6)
  #par3d(windowRect=c(1271, 332, 2563, 1231))
  #par3d(scale=c(0.813438, 1.333599, 1.038952))
  #par3d(viewport=c(0, 0, 1292, 899))
  #par3d(FOV=30)
  #par3d(userMatrix=FrontView)
  
  par3d(RingNeuronView)
  par3d(listeners=listener)
  par3d(viewport=c(0, 0, 1292, 899))
  par3d(windowRect=c(1271, 332, 2563, 1231))
  
  
  
  
  FileName=paste('Z:/Cx_Connectome/BradData/EB_Analysis/RingNeuronSynapseLocs/',as.character(RingNeuronTypes[typeNow]),'.png', sep = "")
  rgl.snapshot(FileName,fmt='png')

  
  rgl.close()
  
}

```













