---
title: "Notebook analyzing the input and output pathways of the EB at the ROI level"
output:
  html_document:
    df_print: paged
---

### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Command to load Renviron file is usethis::edit_r_environ()
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(plotly)
library(dplyr)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="EB"  

# Directory to save data to.
SaveDir="Z:/Cx_Connectome/BradData/EB_Analysis/"

# Directory to save plots to.
PlotDir="Z:/Cx_Connectome/BradData/EB_Analysis/"

```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}
source("inputOutputRegionsVis.r")
source("GetNeuronsInRoi.r")
```

### Get neuprint ROIs 
```{r}
rois = neuprint_ROIs()
heir=neuprint_ROI_hierarchy()
```


### Get the number of synapses in each ROI for all neurons and neuron types (unthresholded)
```{r}

Output=Get_SynapseCount_In_Rois(ROI, FALSE)
list2env(Output ,.GlobalEnv)
remove(Output)

```


## Make plot of ALL neurons and histogram of synapse counts
```{r}

# Plot all of the ROIs (and sub ROIs) that all EB neurons innervate
p0<-ggplot(roi_Connect_bytype_df, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL EB Neuron Input/Output ROIs")
ggsave(paste(PlotDir, "ALL_EB_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 30, height = 20, units ="in", dpi = 300, limitsize = TRUE)


# Plot histogram of synapse counts
HistDat=data.frame(Type=roi_Connect_bytype_df$type, NumberOfSyns= roi_Connect_bytype_df$count)
p1<-ggplot(HistDat, aes(x=NumberOfSyns)) + geom_histogram(binwidth=10) + xlim(0, 500) +
  ylim(0, length(HistDat$NumberOfSyns[HistDat$NumberOfSyns>2 & HistDat$NumberOfSyns<=11]) )
print(p1)

```


### Threshold relative synapse numbers and remove neurons that don't actually belong
```{r}

# 0.01 is good
RelSynThresh=0.01

# Get types based on relative synapse counts (This should be be moved to SynapseStats_And_Threshold)
EB_Type=NamedBodies_TypeAverage$bodytype[NamedBodies_TypeAverage$PrePost_Relative>RelSynThresh]

# Add/Remove types as needed
EB_Type = EB_Type[ !(EB_Type %in% c("FB1C","FB3E","Delta6I","FB6P","FQ10_a","SA3","SIFamide" )) ]

# Threshold EB neurons
ExcludedTypes=unique(filter(roi_Connect_bytype_df, !(type %in% EB_Type) )$type)
roi_Connect_bytype_df=filter(roi_Connect_bytype_df, type %in% EB_Type)

# Save neuron type list for other's use
save(EB_Type, RelSynThresh, ExcludedTypes, file = paste(SaveDir,"EB_Types.RData",sep=""))

```


























## Subset on parent ROIs and some sub ROIs as a princpled way of showing ROIs
```{r}

# Divide parent ROIs into smaller subROIs that we want to show
ROI_LIST=c("hemibrain","CX","NO","LX","LX(R)","LX(L)","PB","LAL(R)","EB") # List of parent ROIs to include
HB_Children=subset(heir, parent %in%  ROI_LIST)
HB_Children=subset(HB_Children, !(roi %in% ROI_LIST) )
HB_Children=subset(HB_Children, !(roi %in% c("POC","mALT(L)","mALT(R)","GF(R)","GC","AOT(R)"))) # Remove fiber bundles


# Create new dataframe (ROISubset) and create a new field (roi_heir_names) with roi names that match those in HB_Children$roi
ROISubset=roi_Connect_bytype_dfThresh
ROISubset$roi_heir_names=ROISubset$roi_names # Make new field with names that match those in HB_Children$roi, the desired ROI list
ROISubset$roi_heir_names= strsplit(as.character(ROISubset$roi_names), "[(]C[)]") # Get rid of (C) in those ROIs that have it
ROISubset$roi_heir_names[ startsWith(as.character(ROISubset$roi_heir_names), "PB(R") ] = 
  strsplit(as.character(ROISubset$roi_heir_names[ startsWith(as.character(ROISubset$roi_heir_names), "PB(R") ]), "[(]R[)]")
ROISubset$roi_heir_names[ startsWith(as.character(ROISubset$roi_heir_names), "PB(L") ] = 
  strsplit(as.character(ROISubset$roi_heir_names[ startsWith(as.character(ROISubset$roi_heir_names), "PB(L") ]), "[(]L[)]")


# Check ExcludedRois to make sure we arent missing an ROI we want
ExcludedRois=unique( ROISubset$roi_heir_names[ !(ROISubset$roi_heir_names %in% HB_Children$roi) ])


# Remove ROIs in ROISubset that aren't in the list provided by HB_Children$roi. Also remove LAL(R) and MB(R), which have super ROIs.
ROISubset=subset(ROISubset, (roi_heir_names %in% HB_Children$roi) & !(roi_names %in% c("LAL(R)","MB(R)")) )


# Relabel roi and roi_names field so that PB(R#) and PB(L#) rois are just PB(R) and PB(L)
ROISubset$roi[startsWith(ROISubset$roi,'PB(L')] <- "PB"
ROISubset$roi[startsWith(ROISubset$roi,'PB(R')] <- "PB"
ROISubset$roi_names = paste(ROISubset$roi, '(', ROISubset$roi_hemi, ')', sep="")
ROISubset$roi_heir_names[startsWith(ROISubset$roi_names,"PB(L")] <- "PB(L)"
ROISubset$roi_heir_names[startsWith(ROISubset$roi_names,"PB(R")] <- "PB(R)"
ROISubset$roi_heir_names=as.character(ROISubset$roi_heir_names)


# Do the same for HB_Children
colnames(HB_Children)[2]='roi_heir_names'
HB_Children$roi_heir_names=as.character(HB_Children$roi_heir_names)
HB_Children$parent=as.character(HB_Children$parent)
HB_Children$roi_heir_names[startsWith(HB_Children$roi_heir_names,"PB(L")] <- "PB(L)"
HB_Children$roi_heir_names[startsWith(HB_Children$roi_heir_names,"PB(R")] <- "PB(R)"
HB_Children=distinct(HB_Children)
HB_Children$parent[ endsWith(as.character(HB_Children$parent), "(L)") ] = 
  strsplit(as.character(HB_Children$parent[ endsWith(as.character(HB_Children$parent), "(L)") ]), "[(]L[)]")
HB_Children$parent[ endsWith(as.character(HB_Children$parent), "(R)") ] = 
  strsplit(as.character(HB_Children$parent[ endsWith(as.character(HB_Children$parent), "(R)") ]), "[(]R[)]")
HB_Children$parent[HB_Children$parent=="LAL"]<-"LX"


# Average PB(L) and PB(R) rois by cell type
ROISubset=aggregate(ROISubset$count, by=list(ROISubset$type, ROISubset$type_name,
                                                             ROISubset$roi,  ROISubset$roi_names, ROISubset$roi_heir_names,
                                                             ROISubset$prepost), mean)
colnames(ROISubset)[c(1,2,3,4,5,6,7)]=c("type","type_name","roi","roi_names","roi_heir_names","prepost","count")


# check to make sure that all plotted ROIs are a subset of the HD_Children ROIs
if (sum(ROISubset$roi_heir_names %in% unique(HB_Children$roi_heir_names)) != length(ROISubset$roi_heir_names)){
  warning('Not all plotted ROIs are in HD_Children!!!!')}


# Join ROISubset with the ROI level information
ROISubset <- merge(ROISubset,HB_Children,by="roi_heir_names")



# Manually set levels for x Axis
ROI_LEVELS=c("BU(L)","BU(R)","LAL(L)","LAL(-GA)(R)","GA(R)",
             "EBr1(C)","EBr2r4(C)","EBr3am(C)","EBr3d(C)","EBr3pw(C)","EBr5(C)","EBr6(C)",
             "PB(L)","PB(R)","NO(L)","NO(R)","FB(C)","AB(R)",
             "VLNP(R)","INP(C)","VMNP(C)","SNP(L)","SNP(R)",
             "GNG(C)")
ROI_LEVELS[which(!ROI_LEVELS %in% unique(ROISubset$roi_names))]
ROISubset$roi_names[ which(!ROISubset$roi_names %in% ROI_LEVELS)]
ROISubset$roi_names <- factor(ROISubset$roi_names, levels = ROI_LEVELS)


# Make facet for y axis
ROISubset$FACET <- NA
ROISubset$FACET[ startsWith(ROISubset$type_name,"R") ] <- "Ring Neurons"
ROISubset$FACET[ startsWith(ROISubset$type_name,"ExR")] <- "Extrinsic Ring Neurons"
ROISubset$FACET[ startsWith(ROISubset$type_name,"EP") | startsWith(ROISubset$type_name,"PE")|
                   startsWith(ROISubset$type_name,"PE") | startsWith(ROISubset$type_name,"EQ")] <- "Columnar Neurons"
ROISubset$FACET[ startsWith(ROISubset$type_name,"FB") | startsWith(ROISubset$type_name,"Delta")] <- "FB-EB Neurons"
ROISubset$type_name[is.na(ROISubset$FACET)]
sum(is.na(ROISubset$FACET))
ROISubset$FACET = factor(ROISubset$FACET, levels=c('Ring Neurons','Extrinsic Ring Neurons',
                                                   'Columnar Neurons','FB-EB Neurons'))


# Factor the types for plotting so the color is good
ROISubset$type = factor(ROISubset$type, levels=c( sort(unique(ROISubset$type[ROISubset$FACET == "Ring Neurons"]),decreasing = TRUE),
                                                         sort(unique(ROISubset$type[ROISubset$FACET == "Extrinsic Ring Neurons"]),decreasing = TRUE),
                                                         sort(unique(ROISubset$type[ROISubset$FACET == "Columnar Neurons"]),decreasing = TRUE),
                                                         sort(unique(ROISubset$type[ROISubset$FACET == "FB-EB Neurons"]),decreasing = TRUE)) )



# Plot all of the ROIs (and sub ROIs) that all NO neurons innervate
p0<-ggplot(ROISubset, aes(x=roi_names, y=type_name, size=count)) + geom_point()  + 
  facet_grid(cols=vars(prepost), rows=vars(FACET), scales="free_y", space="free_y") +  scale_fill_manual(values = vars(type)) + aes(color = type) +
  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Thresh/Subset EB Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "Figure_EbAll_InputOutput_perType.pdf",sep=""), plot = p0, device='pdf', scale = 1, 
       width = 16, height = 16, units ="in", dpi = 600, limitsize = TRUE)



# Remove left ring neurons and make plot again
ROISubset_Remove_Lring=subset(ROISubset, !(startsWith(ROISubset$type_name,"R") &  endsWith(ROISubset$type_name,"(L)")) )

# Plot all of the ROIs (and sub ROIs) that all NO neurons innervate
p0<-ggplot(ROISubset_Remove_Lring, aes(x=roi_names, y=type_name, size=count)) + geom_point()  + 
  facet_grid(cols=vars(prepost), rows=vars(FACET), scales="free_y", space="free_y") +  scale_fill_manual(values = vars(type)) + aes(color = type) +
  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Thresh/Subset EB Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "Figuref_EbNoLringNeurons_InputOutput_perType.pdf",sep=""), plot = p0, device='pdf', scale = 1, 
       width = 14, height = 14, units ="in", dpi = 600, limitsize = TRUE)



```







































