---
title: "Analysis of ExR connectivity"
output:
  html_document:
    df_print: paged
---

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
options(nat.plotengine = 'rgl')
library(igraph)

neuprint_login()
```

```{r, messages=FALSE, warning=FALSE}
# Get some custom functions
source("R/visualizeConnectivityTables.R")

# To be able to use ? for accessing doc strings in custom functions, please install the "docstring" package. Alternatively use docstring(function)
#library(docstring)

getBodyIdsForList = function (neuronList,prefix="",postfix=".*",...){
  #' Get one dataframe of bodyIDs for all search strings in neuronList
  #' @param neuronList: A list of search strings to be passed.
  #' @param prefix: String to be added before each query (default "")
  #' @param postfix: String to be added after each query (default ".*")
  #' @param ...: Parameters to be passed to neuprint_search. Note that meta=FALSE won't work for now.
  #' @return A data frame of metadata for the results of all the queries
  #' @examples
  #' \dontrun{
  #' # Both will return the same
  #' getBodyIdsForList(c("PFL1","PFL2"))
  #' getBodyIdsForList(c("PFL1","PFL2"),postfix="",field="type")
  #' }
  
  neuronList <-  paste0(prefix,neuronList,postfix)
  bodiesList <- lapply(neuronList,neuprint_search,...)
  return(bind_rows(bodiesList))
}
```


### Make selection of neurons to be used in connecitivy analysis
This should be done based on some broadly used criteria. Alternatively, one could read in previously curated lists of neurons.
```{r}
ROI = "NOr"
slctROI ="NO(R)"

splitLR = TRUE

makeAsymmetric = FALSE

saveName = paste0("all_in_", ROI) #RN_TB_ExR #RN_ExR_col_in_
if(splitLR){saveName = paste0(saveName,"_LR")}

useCuratedListPost = FALSE#
useCuratedListPre = FALSE#
curatedList = paste0("/Users/haberkernh/Dropbox (HHMI)/FIBSEM CX Paper Jan 2020/Figures/",ROI,"/",ROI,"_Types.RData")

#only relevant if one of the above is false:
useCustomPostSelection = FALSE
useCustomPreSelection = FALSE
usenbag = FALSE
inCX = FALSE

if(!useCustomPostSelection | !useCustomPreSelection){
  if(splitLR){
    roiTable = getTypesInRoiTable(slctROI,lateralize = TRUE, minTypePercentage = 0.5)
  }else{
    roiTable = getTypesInRoiTable(slctROI,lateralize = FALSE,minTypePercentage = 0.5)
  }
}
# filter based on what is in Shin-ya's CX neuron list
CXneuronList = read.csv("CX-cell-types060920.csv")
```


***Selection of neurons***
```{r}
# POST

if (useCuratedListPost) {
  # load list
  load(curatedList)
  
  # select neurons from there
  postNeuron = get(paste0(ROI,"_Type"))
  postNeuron <- gsub("\\(.*\\)", "", postNeuron)
  postName = paste0(ROI, " neurons")
  
  postIDs = getBodyIdsForList(postNeuron, field="type")
  
} else{
  if(useCustomPostSelection){
    postNeuron = c("FB1","FB2","FB3","FB4")
      #c(paste0("ER",seq(6)))
    postName = "FBt"
    postNeuron = paste0(postNeuron,".*")
    #c(paste0("ER",seq(6)))
    #c("FB1C","FB1H","FB2A","FB3A","FB4B","FB4C","FB4M","FB4Y")
    #c("EL", "ExR", "PEG","AVM08n","EPG")
    #c("ExR.*","PDM21a.*","TuBu.*","R1.*","R2.*","R3.*","R4.*","R5.*","R6.*")
    #c("EL","EPG","EPGt","PEG","PEN_a","PEN_b")#
    #, "ExR","EPG","EL","EPGt","PEG","PEN","PEN") #c("PDM21a.*","TuBu.*", "TuTuB.*")# 
    postIDs = getBodyIdsForList(postNeuron)
    if(inCX){
      postIDs = postIDs %>% filter(type %in% CXneuronList$n.type)
    }
  }else{
    postName = paste0("all in ", ROI)
    postIDs = roiTable$names
    postIDs = postIDs %>% filter(databaseType %in% CXneuronList$n.type)
  }
}

# PRE
if (useCuratedListPre) {
  # load list
  load(curatedList)
  
  # select neurons from there
  preNeuron = get(paste0(ROI,"_Type"))
  preNeuron <- gsub("\\(.*\\)", "", preNeuron)
  preIDs = getBodyIdsForList(preNeuron, field="type")
  preName = paste0(ROI, "neurons")

} else{
  if(useCustomPreSelection){
    preNeuron = postNeuron
    #c("hDeltaL","hDeltaF","hDeltaC","hDeltaM","hDeltaH","FC2C","FC2B")
    #"vDeltaH","hDeltaM","hDeltaH","FC2C","FC2B","FC2A", "ExR5"
    #c("PFR_a", "PFR_b", unique(getBodyIdsForList(paste0( c("PFN"),".*"))$type), "vDelta", "PFL", "FC", "hDelta")#postNeuron
    preName = postName#paste0("ER4m in ",slctROI)#
    preIDs = getBodyIdsForList(preNeuron)
    preIDs = preIDs %>% filter(type %in% CXneuronList$n.type)
  }else{
    if(usenbag){
      nbag = create_neuronBag(postIDs)
      preIDs = nbag$inputs %>% filter(roi == slctROI) %>% select(type.from) %>% unique()
      preIDs = getBodyIdsForList(preIDs$type.from , field="type")
      preName = paste0("all ", ROI)
    }else{
      preName = paste0("all ", ROI)
      preIDs = roiTable$names
      if(inCX){
        preIDs = preIDs %>% filter(databaseType %in% CXneuronList$n.type)
      }
    }
  }
}
```


### Get connectivity table
```{r, warning=FALSE}
preTypes = c(preIDs$bodyid, postIDs$bodyid) # preIDs$bodyid
postTypes = preTypes#postIDs$bodyid
myConnections = getConnectionTable(preTypes, "POST", slctROI)
myConnections = myConnections %>% filter(to %in% postTypes) 
  
#write.csv(myConnections, paste0("../neuprintR_analysis_plots/connectivityTable_",saveName,'_byid.csv'), row.names = FALSE)
```


### Make asymmetric matrix
```{r}
if (makeAsymmetric){
  myConnections = myConnections %>% filter(to %in% postIDs$bodyid)  %>% filter(from %in% preIDs$bodyid)
}
```

### Make type-to-type connectivity table
```{r}
typesTable <- getTypesTable(unique(myConnections$databaseType.to))

if (splitLR){
  # Subdivide types and build a custom types table
  myConnections = lateralize_types(myConnections, postfix="to")
  myConnections = lateralize_types(myConnections, postfix="from")
  typesTable = lateralize_types(typesTable, postfix="raw")
}

myConnectionsT2T = getTypeToTypeTable(myConnections,typesTable = typesTable)
```

```{r}
myConnections_nameid = myConnections %>% mutate(typeid.to = paste(type.to, to,sep="_"),
                                                typeid.from = paste(type.from, from, sep="_"))
edge_list <- myConnections_nameid[c("from","to","weightRelative")]
#[c("typeid.from","typeid.to","weightRelative")]
#G <- graph.data.frame(edge_list,directed=TRUE);
#A <- as_adjacency_matrix(G,type="both",names=TRUE,sparse=FALSE,attr="weightRelative")
#write.csv(A, paste0("../neuprintR_analysis_plots/adjacencyMatrix_",saveName,'_byid.csv'), row.names = FALSE)
#write.csv(edge_list, paste0("../neuprintR_analysis_plots/edgeList_",saveName,'_byid.csv'), row.names = FALSE)

```

```{r}
#alternative orderings for columnars
PBorder = c(paste0("R",seq(9,1,-1)),paste0("L",seq(1,9)))
PBorder

EBorder = c("R1","L1","R2","L8","R3","L7","R4","L6","R5","L5","R6","L4","R7","L3","R8","L2") #cut at bottom
EBorder

#myConnections = myConnections %>% mutate(colname.to = as.character(
#  regmatches(as.character(myConnections$name.to), gregexpr("[R,L]{1}[1-9]{1}",as.character(myConnections$name.to)) ) ))
#myConnections$colname.to = factor(myConnections$colname.to,levels = PBorder)

myConnections = myConnections %>% mutate(rowname.from = as.character(
  regmatches(as.character(myConnections$name.from), gregexpr("[R,L]{1}[1-9]{1}",as.character(myConnections$name.from)) ) ))
myConnections$rowname.from = factor(myConnections$rowname.from,levels = EBorder)
```

### Connectivity matrix
```{r}
plotW = 10#10#25#25#10#25# 45 # 20
plotH = 55#10#15#22#21 #4 #40  #17
cmax = NULL
cmaxtype = NULL

source("R/visualizeConnectivityTables.R")

connectionMeasures = c("weightRelative")

for (connectionMeasure in connectionMeasures){
  
  conMatPlot = plotConnectivityMatrix(myConnectionsT2T, byGroup = "type", connectionMeasure, cmaxtype)
  conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  
  print(conMatPlot)
  ggsave( paste("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_byType.pdf', sep=''), plot = conMatPlot, device='pdf', path = "../neuprintR_analysis_plots/",
    scale = 1.5, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
  
  #conMatPlot = plotConnectivityMatrix(myConnections, byGroup = "rowname", connectionMeasure,cmax)
  #conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  #conMatPlot = structureMatrixPlotByType(conMatPlot)
  #print(conMatPlot)
  #ggsave( paste("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_byColNameEB.pdf', sep=''), 
  #  plot = conMatPlot, device='pdf', path = "../neuprintR_analysis_plots/",
  #    scale = 1.5, width = plotW*0.8, height = plotH*0.8, units ="cm", dpi = 600, limitsize = TRUE)
  
  conMatPlot = plotConnectivityMatrix(myConnections, byGroup = "id", connectionMeasure, cmax)
  conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  conMatPlot = structureMatrixPlotByType_lines(conMatPlot)
  print(conMatPlot)
  ggsave(paste("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_byID.pdf', sep=''), 
    plot = conMatPlot, device='pdf', path = "../neuprintR_analysis_plots/",
    scale = 2, width = plotW*1., height =plotH*1, units ="cm", dpi = 600, limitsize = TRUE)
  
  conMatPlot = plotConnectivityMatrix(myConnections, byGroup = "name", connectionMeasure, cmax)
  conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  #conMatPlot = structureMatrixPlotByType_lines(conMatPlot)
  print(conMatPlot)
  ggsave(paste("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_byName.pdf', sep=''), 
    plot = conMatPlot, device='pdf', path = "../neuprintR_analysis_plots/",
    scale = 2, width = plotW*1., height =plotH*1, units ="cm", dpi = 600, limitsize = TRUE)
}
```

###  Draw graph

```{r, warning=FALSE} 
require(igraph)

connectionMeasures = c("weightRelative","weightROIRelativeTotal")
connectionMeasure = connectionMeasures[1]
cutoff = 0.01 # for weight 0.05, 0.01, 0

largeGraph = TRUE
selfFeedbackScale = 10
edcurve = 0.1#0.15
edgeNorm = 0.07#0.07#0.05#0.07#0.03#

showself = FALSE 
removeIso = TRUE

# drop na in "to" column
myConnectionsT2T = myConnectionsT2T %>% drop_na(type.to)
graphData = data.frame(from = myConnectionsT2T$type.from, to = myConnectionsT2T$type.to, relWeight = myConnectionsT2T$weightRelative)

graphData_noSelf = getNoSelfGraphData(graphData)  
graphData_self = getSelfFBGraphData(graphData)

if (showself){
  graphData = graphData
  graphName = saveName
} else {
  graphData = left_join(graphData_noSelf, graphData_self)
  graphName = paste0(saveName, "_noSelf")
}

# Graph parameter
if(largeGraph){
  vertexSize = 3#7#+ 7 * graphData$relWeightSelf * selfFeedbackScale
  plotSize = 15
}else{
  vertexSize = 12 #+ 12 * graphData$relWeightSelf * selfFeedbackScale
  plotSize = 10
}

selfFBscale = vertexSize
arrowSize= 0

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale, arrowSize, edgeNorm)


# remove isolated nodes
if(removeIso){
  Isolated = which(degree(myGraph) == 0)
  myGraph = delete.vertices(myGraph, Isolated)
}

l = layout_with_fr(myGraph)#layout_with_dh(myGraph)#
#l = layout_as_bipartite(myGraph, types = grepl(postpattern,V(myGraph)$name))
myGraph$main = paste0("Connectivity within the ",slctROI)
plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph)) # use 0.5 curved if edges overlap

dev.print(pdf, paste0("../neuprintR_analysis_plots/connectivityGraph_",graphName,'_in_',slctROI,
                      "_",connectionMeasure, round(100*cutoff),"perc.pdf"), width=plotSize, height=plotSize)
```

Graph with defined colormap from file
```{r, warning=FALSE} 
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")

myColorMap <- read.csv(paste0("~/Documents/code/neuprintR-notebooks/colorMap_",cmapNames[1],".csv"))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(paste0("~/Documents/code/neuprintR-notebooks/colorMap_",cmapName,".csv"))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}

if(splitLR){
  myColorMap_R = myColorMap %>% mutate(Type = paste0(Type, "_R"))
  myColorMap_L = myColorMap %>% mutate(Type = paste0(Type, "_L"))
  myColorMap= bind_rows(myColorMap_L, myColorMap_R)
}

myColorMap = myColorMap %>% filter(Simpletype == "no")
# drop na in "to" column
myConnectionsT2T = myConnectionsT2T %>% drop_na(type.to)
graphData = data.frame(from = myConnectionsT2T$type.from, to = myConnectionsT2T$type.to, relWeight = myConnectionsT2T$weightRelative)

graphData_noSelf = getNoSelfGraphData(graphData)  
graphData_self = getSelfFBGraphData(graphData)

if (showself){
  graphData = graphData
  graphName = saveName
} else {
  graphData = left_join(graphData_noSelf, graphData_self)
  graphName = paste(saveName, "_noSelf")
}

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale, arrowSize, edgeNorm, 
                                     colormap = myColorMap, useRandCol = FALSE)


# remove isolated nodes
if(removeIso){
  Isolated = which(degree(myGraph) == 0)
  myGraph = delete.vertices(myGraph, Isolated)
}

myGraph$main = paste0("Connectivity within   the ",slctROI)
plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph), legend=TRUE)

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=0.8,y=1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)),  bty = "n", seg.len=0.5)
#legend("topleft", legend = levels(as.factor(vertex_attr(myGraph, "comp"))), pch = 16, col = pal, bty = "n")

dev.print(pdf, paste0("../neuprintR_analysis_plots/connectivityGraph_",graphName,'_in_',slctROI,
                      "_",connectionMeasure, round(100*cutoff),"perc_custCol.pdf"), width=plotSize, height=plotSize)
```
