---
title: "FAFB vs. FIBSEM"
output: html_notebook
---

Load the libraries
```{r}
library(nat)
library(neuprintr)
library(tidyverse)
library(tidygraph)
library(ggraph)
library(gridExtra)
library(paletteer)
library(reshape2)
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\R\\supertypeUtils.R")
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\visualizeConnectivityTables.R")
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\neuprintQueryUtils.R")
options(nat.plotengine = 'rgl')
```

Connect to neuprint
```{r}
neuprint_l'ogin()
```

Function to load the FAFB data in a datframe
```{r}
FAFBLoad <- function(region){
  #' Get data frame of FAFB data in a given region
  #' @return Returns a data frame of the FAFB data in the specified region
  #' @param region: The chosen ROI
  
  # Load the csv file
  FAFBDat = read.csv(paste0(
    '\\\\dm11\\jayaramanlab\\Kris\\Catmaid\\connectivity_matrices\\matrix_',region,'_despiked.txt')
    , header=TRUE, sep ="")
  
  # Get out the names of the neurons within the dataset
  nrons = rownames(FAFBDat)
  
  # Create nameids and partnerids based off of the constituent neurons
  nameids = c()
  partnerids = c()
  for (rpt in (1:length(nrons))){
    nameids = append(nameids,nrons)
    for (r in (1:length(nrons))){
      partnerids = append(partnerids,nrons[rpt])
    }
  }
  
  # Populate a dataframe from the weight matrix
  colNames = names(FAFBDat)
  FAFB_df = data.frame(nameid = nameids,partnerid = partnerids, weight = integer(length(nrons)))
  for (i in 1:length(colNames)){
    for (j in 1:length(nrons)){
      FAFB_df$weight[which(FAFB_df$nameid == str_replace(colNames[i],'[.]','-') & FAFB_df$partnerid == nrons[j])] <- FAFBDat[j,i]
    }
  }
  
  # Alter the glom names to match the FIBSEM data
  nronNames = character(length(nrons))
  for (n in 1:length(nrons)){
    nmPrts = strsplit(nrons[n],"-")
    if (grepl("EPG",nmPrts[[1]][1]))
      nronNames[n] <- paste0("EPG(PB08)",'_',substr(nmPrts[[1]][2],2,2),substr(nmPrts[[1]][2],1,1),'_',substr(nmPrts[[1]][2],3,3))
    if (grepl("PEG",nmPrts[[1]][1]))
      nronNames[n] <- paste0("PEG(PB07)",'_',substr(nmPrts[[1]][2],2,2),substr(nmPrts[[1]][2],1,1))
    if (grepl("PEN",nmPrts[[1]][1])){
      if (grepl("1",substring(nmPrts[[1]][1],4,4))){
        if (nchar(nmPrts[[1]][2]) > 2)
          nronNames[n] <- paste0("PEN(PB06)",'_a_',substr(nmPrts[[1]][2],2,2),substr(nmPrts[[1]][2],1,1),'_',substr(nmPrts[[1]][2],3,3))
        else
          nronNames[n] <- paste0("PEN(PB06)",'_a_',substr(nmPrts[[1]][2],2,2),substr(nmPrts[[1]][2],1,1))
      }
      else {
        if (nchar(nmPrts[[1]][2]) > 2)
          nronNames[n] <- paste0("PEN(PB06)",'_b_',substr(nmPrts[[1]][2],2,2),substr(nmPrts[[1]][2],1,1),'_',substr(nmPrts[[1]][2],3,3))
        else
          nronNames[n] <- paste0("PEN(PB06)",'_b_',substr(nmPrts[[1]][2],2,2),substr(nmPrts[[1]][2],1,1))
      }
    }
    if (grepl("D7",nmPrts[[1]][1])){
      if (nchar(nmPrts[[1]][2]) > 4){
        if (paste0(substr(nmPrts[[1]][2],2,2),
                   substr(nmPrts[[1]][2],1,1)) == "R1"){
          nronNames[n] <- paste0("Delta7(PB15)",'_L8_',
                                 substr(nmPrts[[1]][2],2,2),
                                 substr(nmPrts[[1]][2],1,1),'_',
                                 substr(nmPrts[[1]][2],4,4),
                                 substr(nmPrts[[1]][2],3,3),'_',
                                 substr(nmPrts[[1]][2],5,5))
        } else {
          nronNames[n] <- paste0("Delta7(PB15)",'_',
                                 substr(nmPrts[[1]][2],4,4),
                                 substr(nmPrts[[1]][2],3,3),'_',
                                 substr(nmPrts[[1]][2],2,2),
                                 substr(nmPrts[[1]][2],1,1),'_',
                                 substr(nmPrts[[1]][2],5,5))
        }
      } else {
        nronNames[n] <- paste0("Delta7(PB15)",'_',
                               substr(nmPrts[[1]][2],4,4),
                               substr(nmPrts[[1]][2],3,3),'_',
                               substr(nmPrts[[1]][2],2,2),
                               substr(nmPrts[[1]][2],1,1))
      }
        
    }
    if (grepl("R",substring(nmPrts[[1]][1],1,1)))
      nronNames[n] <- paste0('R4m','_',substr(nmPrts[[1]][1],2,2))
    if (grepl("NO",nmPrts[[1]][1]))
      nronNames[n] <- "GLN"
    if (grepl("GE",nmPrts[[1]][1]))
      nronNames[n] <- "EQ5"
  }
  
  # Replace the names in the dataframe
  # Create nameids and partnerids based off of the constituent neurons
  nameids_New = nameids
  partnerids_New = partnerids
  for (n in 1:length(nrons)){
    nameids_New[which(grepl(nrons[n],nameids_New))] <- nronNames[n]
    partnerids_New[which(grepl(nrons[n],partnerids_New))] <- nronNames[n]
  }
  FAFB_df$nameid <- factor(nameids_New,levels=sort(unique(nameids_New)))
  FAFB_df$partnerid <- factor(partnerids_New,levels=sort(unique(partnerids_New)))
  
  return(FAFB_df)
}
  
```

Compare the FAFB data to the FIBSEM data - PB
```{r}
FAFB_PB_df <-FAFBLoad("PB")
FAFB_PB_df <- FAFB_PB_df %>% filter(grepl("EPG",partnerid) | grepl("Delta7",partnerid))

FAFBNames <- FAFB_PB_df$nameid %>% as.character() %>% append(FAFB_PB_df$partnerid %>% as.character()) %>% unique()
newFAFBNames <- c("PEN1-5R", "PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb", "PEN1-7R", "PEN1-7L",
                  "PEN2-5R", "PEN2-5L","PEN2-6Ra","PEN2-6Rb","PEN2-6La","PEN2-6Lb", "PEN2-7R", "PEN2-7L",
                  "EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6La","EPG-6Lb",
                  "PEG-5R", "PEG-5L","PEG-6R","PEG-6L",
                  "Delta7-5R4La","Delta7-5R4Lb","Delta7-6R3La","Delta7-6R3Lb","Delta7-7R2L","Delta7-2R7L","Delta7-1R9R8L")
nameLU_FAFB <- data.frame(oldName = FAFBNames, newName = newFAFBNames)
FAFB_PB_df$nameid <- sapply(FAFB_PB_df$nameid, function(x) nameLU_FAFB$newName[match(as.character(x), nameLU_FAFB$oldName)])
FAFB_PB_df$partnerid <- sapply(FAFB_PB_df$partnerid, function(x) nameLU_FAFB$newName[match(as.character(x), nameLU_FAFB$oldName)])

gFAFB <- ggplot(FAFB_PB_df) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =75, limits=c(0,150)) +
  geom_tile(aes(nameid,partnerid,fill=weight))+coord_fixed(ratio=1) + ggtitle("FAFB data")

print(gFAFB)

#ggsave("FAFB_PB.pdf", plot = gFAFB, device='pdf', 
#       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp",
#       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)

neuronList = c("PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L7",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R6",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L6",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L2R7",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L3R6",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L4R5",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L7R2",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L8")

FIBSEM_PB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "PB")
FIBSEM_PB$nameid.from = paste(as.character(FIBSEM_PB$name.from), as.character(FIBSEM_PB$from), sep = "_")
FIBSEM_PB$nameid.to = paste(as.character(FIBSEM_PB$name.to), as.character(FIBSEM_PB$to), sep = "_")

L6EPGs <- paste(getBodyIdsForList("EPG\\\\\\\\(PB08\\\\\\\\)_L6")$name, getBodyIdsForList("EPG\\\\\\\\(PB08\\\\\\\\)_L6")$bodyid, sep="_")
FIBSEM_PB_Mat <- FIBSEM_PB %>% select(nameid.from,nameid.to,ROIweight)
FIBSEM_PB_Mat <-rbind(FIBSEM_PB_Mat,
                      data.frame(nameid.from = L6EPGs, nameid.to = L6EPGs, ROIweight = 0))
FIBSEM_PB_Mat <- FIBSEM_PB_Mat %>% dcast(nameid.to~nameid.from)
FIBSEM_PB_Mat[is.na(FIBSEM_PB_Mat)] <- 0
FIBSEM_PB_Mat <- FIBSEM_PB_Mat %>% melt()
colnames(FIBSEM_PB_Mat) <- c("nameid.to","nameid.from","ROIweight")

gFIBSEM <- ggplot(FIBSEM_PB_Mat) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =75, limits=c(0,150)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1)

print(gFIBSEM)

ggsave("FIBSEM_PB.pdf", plot = gFIBSEM, device='pdf', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\",
       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)
```

Downselect the FIBSEM neurons for a direct comparison
```{r}
DSneuronList <- c("EPG\\\\\\\\(PB08\\\\\\\\)_R6",
                  "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
                  "Delta7\\\\\\\\(PB15\\\\\\\\)_L2R7",
                  "Delta7\\\\\\\\(PB15\\\\\\\\)_L3R6",
                  "Delta7\\\\\\\\(PB15\\\\\\\\)_L4R5",
                  "Delta7\\\\\\\\(PB15\\\\\\\\)_L7R2",
                  "Delta7\\\\\\\\(PB15\\\\\\\\)_L8")
numNrons <-  c(2,2,1,2,2,1,1)

FIBSEM_PB_Cut <- FIBSEM_PB_Mat

for (ds in 1:length(DSneuronList)){
  bodyids2cut <- getBodyIdsForList(DSneuronList[ds])$bodyid
  bodyids2cut <- bodyids2cut %>% sample(length(bodyids2cut)-numNrons[ds])
  nameids2cut <- paste(neuprint_get_meta(bodyids2cut)$name,bodyids2cut,sep='_')
  FIBSEM_PB_Cut <- FIBSEM_PB_Cut %>% 
    filter(!(nameid.from %in% nameids2cut) & !(nameid.to %in% nameids2cut))
}

FIBSEMNames <- FIBSEM_PB_Cut$nameid.from %>% as.character() %>% append(FIBSEM_PB_Cut$nameid.to %>% as.character()) %>% unique()
newFIBSEMNames <- c("Delta7-7R2L","Delta7-6R3La","Delta7-6R3Lb","Delta7-5R4La","Delta7-5R4Lb","Delta7-2R7L","Delta7-1R9R8L",
                    "EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb",
                    "PEG-5L", "PEG-6L","PEG-5R","PEG-6R",
                    "PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-7L","PEN1-5R", "PEN1-6Ra","PEN1-6Rb","PEN1-7R",
                    "PEN2-5L", "PEN2-6La","PEN2-6Lb","PEN2-7L","PEN2-5R", "PEN2-6Ra","PEN2-6Rb","PEN2-7R")

nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_PB_Cut$nameid.from <- sapply(FIBSEM_PB_Cut$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_PB_Cut$nameid.to <- sapply(FIBSEM_PB_Cut$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])

gFIBSEM_DS <- ggplot(FIBSEM_PB_Cut) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =75, limits=c(0,150)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) + ggtitle("select FIBSEM data")

print(gFAFB)
print(gFIBSEM_DS)
```

Compare the two matrices
```{r}
FAFB_PB_df_Mat <- FAFB_PB_df %>% dcast(partnerid~nameid)
rownames(FAFB_PB_df_Mat) <- FAFB_PB_df_Mat$partnerid
FAFB_PB_df_Mat <- FAFB_PB_df_Mat[,2:ncol(FAFB_PB_df_Mat)] %>% data.matrix

FIBSEM_PB_Cut_Mat <- FIBSEM_PB_Cut %>% dcast(nameid.from~nameid.to)
rownames(FIBSEM_PB_Cut_Mat) <- FIBSEM_PB_Cut_Mat$partnerid
FIBSEM_PB_Cut_Mat <- FIBSEM_PB_Cut_Mat[,2:ncol(FIBSEM_PB_Cut_Mat)] %>% data.matrix

matDiff <- FAFB_PB_df_Mat - FIBSEM_PB_Cut_Mat
matSum <- FAFB_PB_df_Mat + FIBSEM_PB_Cut_Mat

perMat <- matrix(0L,nrow=nrow(matDiff),ncol=ncol(matDiff))
diffMat <- matrix(0L,nrow=nrow(matDiff),ncol=ncol(matDiff))
for (r in 1:nrow(perMat)){
  for (c in 1:ncol(perMat)){
    if (FAFB_PB_df_Mat[r,c] == 0){
      diffMat[r,c] <- -FIBSEM_PB_Cut_Mat[r,c]
      next
    }
    if (FIBSEM_PB_Cut_Mat[r,c] == 0){
      diffMat[r,c] <- FAFB_PB_df_Mat[r,c]
      next
    }
    if (matSum[r,c] > 0)
      perMat[r,c] <- matDiff[r,c]/matSum[r,c]
  }
}

rownames(perMat) <- FAFB_PB_df$partnerid %>% as.character() %>% unique() %>% sort()
rownames(diffMat) <- FAFB_PB_df$partnerid %>% as.character() %>% unique() %>% sort()
colnames(perMat) <- FAFB_PB_df$nameid %>% as.character() %>% unique() %>% sort()
colnames(diffMat) <- FAFB_PB_df$nameid %>% as.character() %>% unique() %>% sort()

gPer <- ggplot(melt(perMat)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint =0, limits=c(-1,1)) +
  geom_tile(aes(Var2,Var1,fill=value))+coord_fixed(ratio=1,expand=FALSE) + ggtitle("diff/sum when both have synapses")

gDiff <- ggplot(melt(diffMat)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint =0, limits=c(-45,45)) +
  geom_tile(aes(Var2,Var1,fill=value))+coord_fixed(ratio=1,expand=FALSE) + ggtitle("synapses for only one dataset")

print(gPer)
print(gDiff)
```

Plot a summary statistic for the per and diff metrics
```{r}
perPB <- melt(perMat)
diffPB <- melt(diffMat)

perPB <- perPB[which(perPB$value != 0),]
diffPB <- diffPB[which(diffPB$value != 0),]

perPB$supergroup.from <- "columnar"
perPB[which(grepl("Delta7",as.character(perPB$Var1))),]$supergroup.from <- "tangential"
perPB$supergroup.to <- "columnar"
perPB[which(grepl("Delta7",as.character(perPB$Var2))),]$supergroup.to <- "tangential"
perPB <- perPB %>% mutate(connType = paste(supergroup.from, supergroup.to, sep="->"))

diffPB$supergroup.from <- "columnar"
diffPB[which(grepl("Delta7",as.character(diffPB$Var1))),]$supergroup.from <- "tangential"
diffPB$supergroup.to <- "columnar"
diffPB[which(grepl("Delta7",as.character(diffPB$Var2))),]$supergroup.to <- "tangential"
diffPB <- diffPB %>% mutate(connType = paste(supergroup.from, supergroup.to, sep="->"))

ggplot(perPB) + geom_point(aes(x = as.factor(connType), y = value),size=4,alpha=0.25) + 
  theme_classic() + ylim(-1,1) + geom_hline(yintercept = 0) +
  xlab('partners') + ylab('(FAFB cts - FIBSEM cts)/(total cts)')

ggplot(diffPB) + geom_point(aes(x = as.factor(connType), y = value),size=4,alpha=0.25) + 
  theme_classic() + ylim(-30,30) + geom_hline(yintercept = 0) +
  xlab('partners') + ylab('FIBSEM cts  FAFB cts')
```

Put them all on one plot and compare
```{r}
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\PBComp.pdf", width = 20, height = 20)
print(grid.arrange(gFAFB,gFIBSEM_DS,gPer,gDiff,
                   layout_matrix = rbind(c(3,1),c(4,5))))
dev.off()
```

Just plot EPG and D7 connections in the PB
```{r}
neuronList = c("EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L2R7",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L3R6",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L4R5",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L7R2",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L8")

FIBSEM_PB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "PB")
FIBSEM_PB$nameid.from = paste(as.character(FIBSEM_PB$name.from), as.character(FIBSEM_PB$from), sep = "_")
FIBSEM_PB$nameid.to = paste(as.character(FIBSEM_PB$name.to), as.character(FIBSEM_PB$to), sep = "_")

FIBSEMNames <- FIBSEM_PB$nameid.from %>% as.character() %>% append(FIBSEM_PB$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("Delta7-7R2La","Delta7-7R2Lb","Delta7-7R2Lc","Delta7-7R2Ld","Delta7-7R2Le",
                    "Delta7-6R3La","Delta7-6R3Lb","Delta7-6R3Lc","Delta7-6R3Ld",
                    "Delta7-5R4La","Delta7-5R4Lb","Delta7-5R4Lc","Delta7-5R4Ld","Delta7-5R4Le",
                    "Delta7-2R7La","Delta7-2R7Lb","Delta7-2R7Lc",
                    "Delta7-1R9R8La","Delta7-1R9R8Lb","Delta7-1R9R8Lc","Delta7-1R9R8Ld","Delta7-1R9R8Le",
                    "EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-6Lc","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb","EPG-6Rc")
PBlevels <- c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6Rc","EPG-6La","EPG-6Lb","EPG-6Lc",
              "Delta7-5R4La","Delta7-5R4Lb","Delta7-5R4Lc","Delta7-5R4Ld","Delta7-5R4Le",
              "Delta7-6R3La","Delta7-6R3Lb","Delta7-6R3Lc","Delta7-6R3Ld",
              "Delta7-7R2La","Delta7-7R2Lb","Delta7-7R2Lc","Delta7-7R2Ld","Delta7-7R2Le",
              "Delta7-2R7La","Delta7-2R7Lb","Delta7-2R7Lc",
              "Delta7-1R9R8La","Delta7-1R9R8Lb","Delta7-1R9R8Lc","Delta7-1R9R8Ld","Delta7-1R9R8Le")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_PB$nameid.from <- sapply(FIBSEM_PB$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_PB$nameid.to <- sapply(FIBSEM_PB$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])

nronsToAdd <-  c("EPG-6La","EPG-6Lb","EPG-6Lc")
FIBSEM_PB <- FIBSEM_PB %>% select(nameid.from, nameid.to, ROIweight)
for (nPre in 1:length(nronsToAdd)){
  for (nPost in 1:length(nronsToAdd)){
    if (nrow(FIBSEM_PB %>%
             filter(as.character(nameid.from) == nronsToAdd[nPre] &
                    as.character(nameid.to) == nronsToAdd[nPost])) == 0)
      FIBSEM_PB <- FIBSEM_PB %>% rbind(data.frame(nameid.from = nronsToAdd[nPre], nameid.to = nronsToAdd[nPost], ROIweight = 0))
  }
}
FIBSEM_PB <- FIBSEM_PB %>% dcast(nameid.from~nameid.to)
FIBSEM_PB[is.na(FIBSEM_PB)] <- 0
FIBSEM_PB <- melt(FIBSEM_PB)
colnames(FIBSEM_PB) <- c("nameid.from","nameid.to","ROIweight")
FIBSEM_PB$nameid.from <- factor(FIBSEM_PB$nameid.from, levels = PBlevels)
FIBSEM_PB$nameid.to <- factor(FIBSEM_PB$nameid.to, levels = PBlevels)

gFIBSEM <- ggplot(FIBSEM_PB) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =30, limits=c(0,60)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 12.5) + geom_vline(xintercept = 12.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\PBEPGsD7s_FIBSEM.pdf", width = 10, height = 10)
print(gFIBSEM)
dev.off()
```

Just plot EPG and PEN1 connections in the PB
```{r}
neuronList = c("EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7")

FIBSEM_PB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "PB")
FIBSEM_PB$nameid.from = paste(as.character(FIBSEM_PB$name.from), as.character(FIBSEM_PB$from), sep = "_")
FIBSEM_PB$nameid.to = paste(as.character(FIBSEM_PB$name.to), as.character(FIBSEM_PB$to), sep = "_")

FIBSEMNames <- FIBSEM_PB$nameid.from %>% as.character() %>% append(FIBSEM_PB$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-6Lc","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb","EPG-6Rc",
                    "PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-5R", "PEN1-6Ra","PEN1-6Rb")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_PB$nameid.from <- sapply(FIBSEM_PB$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_PB$nameid.to <- sapply(FIBSEM_PB$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])

nronsToAdd <-  c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6Rc","EPG-6La","EPG-6Lb","EPG-6Lc",
              "PEN1-5R","PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb","PEN1-7R","PEN1-7L")
FIBSEM_PB <- FIBSEM_PB %>% select(nameid.from, nameid.to, ROIweight)
for (nPre in 1:length(nronsToAdd)){
  for (nPost in 1:length(nronsToAdd)){
    if (nrow(FIBSEM_PB %>%
             filter(as.character(nameid.from) == nronsToAdd[nPre] &
                    as.character(nameid.to) == nronsToAdd[nPost])) == 0)
      FIBSEM_PB <- FIBSEM_PB %>% rbind(data.frame(nameid.from = nronsToAdd[nPre], nameid.to = nronsToAdd[nPost], ROIweight = 0))
  }
}
FIBSEM_PB <- FIBSEM_PB %>% dcast(nameid.from~nameid.to)
FIBSEM_PB[is.na(FIBSEM_PB)] <- 0
FIBSEM_PB <- melt(FIBSEM_PB)
colnames(FIBSEM_PB) <- c("nameid.from","nameid.to","ROIweight")
FIBSEM_PB$nameid.from <- factor(FIBSEM_PB$nameid.from, levels = nronsToAdd)
FIBSEM_PB$nameid.to <- factor(FIBSEM_PB$nameid.to, levels = nronsToAdd)

gFIBSEM <- ggplot(FIBSEM_PB) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =20, limits=c(0,40)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 12.5) + geom_vline(xintercept = 12.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\PBEPGsPEN1s_FIBSEM.pdf", width = 5, height = 5)
print(gFIBSEM)
dev.off()
```

Just plot EPG, Delta7, PEN2, and PEG connections in the PB
```{r}
neuronList = c("EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L7",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R6",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L6",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L2R7",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L3R6",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L4R5",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L7R2",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L8")

FIBSEM_PB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "PB")
FIBSEM_PB$nameid.from = paste(as.character(FIBSEM_PB$name.from), as.character(FIBSEM_PB$from), sep = "_")
FIBSEM_PB$nameid.to = paste(as.character(FIBSEM_PB$name.to), as.character(FIBSEM_PB$to), sep = "_")

FIBSEMNames <- FIBSEM_PB$nameid.from %>% as.character() %>% append(FIBSEM_PB$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("Delta7-7R2La","Delta7-7R2Lb","Delta7-7R2Lc","Delta7-7R2Ld","Delta7-7R2Le",
                    "Delta7-6R3La","Delta7-6R3Lb","Delta7-6R3Lc","Delta7-6R3Ld",
                    "Delta7-5R4La","Delta7-5R4Lb","Delta7-5R4Lc","Delta7-5R4Ld","Delta7-5R4Le",
                    "Delta7-2R7La","Delta7-2R7Lb","Delta7-2R7Lc",
                    "Delta7-1R9R8La","Delta7-1R9R8Lb","Delta7-1R9R8Lc","Delta7-1R9R8Ld","Delta7-1R9R8Le",
                    "EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-6Lc","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb","EPG-6Rc",
                    "PEG-5L", "PEG-6L","PEG-5R", "PEG-6R",
                    "PEN2-5L", "PEN2-6La","PEN2-6Lb","PEN2-7L","PEN2-5R", "PEN2-6Ra","PEN2-6Rb","PEN2-7R")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_PB$nameid.from <- sapply(FIBSEM_PB$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_PB$nameid.to <- sapply(FIBSEM_PB$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
PBlevels <- c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6Rc","EPG-6La","EPG-6Lb","EPG-6Lc",
              "Delta7-5R4La","Delta7-5R4Lb","Delta7-5R4Lc","Delta7-5R4Ld","Delta7-5R4Le",
              "Delta7-6R3La","Delta7-6R3Lb","Delta7-6R3Lc","Delta7-6R3Ld",
              "Delta7-7R2La","Delta7-7R2Lb","Delta7-7R2Lc","Delta7-7R2Ld","Delta7-7R2Le",
              "Delta7-2R7La","Delta7-2R7Lb","Delta7-2R7Lc",
              "Delta7-1R9R8La","Delta7-1R9R8Lb","Delta7-1R9R8Lc","Delta7-1R9R8Ld","Delta7-1R9R8Le",
              "PEN2-5R","PEN2-5L","PEN2-6Ra","PEN2-6Rb","PEN2-6La","PEN2-6Lb","PEN2-7R","PEN2-7L", 
              "PEG-5R","PEG-5L","PEG-6R","PEG-6L")
                    
nronsToAdd <-  c("EPG-6La","EPG-6Lb","EPG-6Lc")
FIBSEM_PB <- FIBSEM_PB %>% select(nameid.from, nameid.to, ROIweight)
for (nPre in 1:length(nronsToAdd)){
  for (nPost in 1:length(nronsToAdd)){
    if (nrow(FIBSEM_PB %>%
             filter(as.character(nameid.from) == nronsToAdd[nPre] &
                    as.character(nameid.to) == nronsToAdd[nPost])) == 0)
      FIBSEM_PB <- FIBSEM_PB %>% rbind(data.frame(nameid.from = nronsToAdd[nPre], nameid.to = nronsToAdd[nPost], ROIweight = 0))
  }
}
FIBSEM_PB <- FIBSEM_PB %>% dcast(nameid.from~nameid.to)
FIBSEM_PB[is.na(FIBSEM_PB)] <- 0
FIBSEM_PB <- melt(FIBSEM_PB)
colnames(FIBSEM_PB) <- c("nameid.from","nameid.to","ROIweight")
FIBSEM_PB$nameid.from <- factor(FIBSEM_PB$nameid.from, levels = PBlevels)
FIBSEM_PB$nameid.to <- factor(FIBSEM_PB$nameid.to, levels = PBlevels)

FIBSEM_PB <- FIBSEM_PB %>% filter(!grepl("Delta7",nameid.to))

gFIBSEM <- ggplot(FIBSEM_PB) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =75, limits=c(0,150)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 12.5) + geom_vline(xintercept = 12.5) + geom_vline(xintercept = 20.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\PBEPGsD7sPEN2sPEGs_FIBSEM.pdf", width = 10, height = 10)
print(gFIBSEM)
dev.off()
```

Just plot EPG, Delta7, and PEN1 in the PB
```{r}
neuronList = c("EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L2R7",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L3R6",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L4R5",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L7R2",
              "Delta7\\\\\\\\(PB15\\\\\\\\)_L8")

FIBSEM_PB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "PB")
FIBSEM_PB$nameid.from = paste(as.character(FIBSEM_PB$name.from), as.character(FIBSEM_PB$from), sep = "_")
FIBSEM_PB$nameid.to = paste(as.character(FIBSEM_PB$name.to), as.character(FIBSEM_PB$to), sep = "_")

FIBSEMNames <- FIBSEM_PB$nameid.from %>% as.character() %>% append(FIBSEM_PB$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("Delta7-7R2La","Delta7-7R2Lb","Delta7-7R2Lc","Delta7-7R2Ld","Delta7-7R2Le",
                    "Delta7-6R3La","Delta7-6R3Lb","Delta7-6R3Lc","Delta7-6R3Ld",
                    "Delta7-5R4La","Delta7-5R4Lb","Delta7-5R4Lc","Delta7-5R4Ld","Delta7-5R4Le",
                    "Delta7-2R7La","Delta7-2R7Lb","Delta7-2R7Lc",
                    "Delta7-1R9R8La","Delta7-1R9R8Lb","Delta7-1R9R8Lc","Delta7-1R9R8Ld","Delta7-1R9R8Le",
                    "EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-6Lc","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb","EPG-6Rc",
                    "PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-7L","PEN1-5R", "PEN1-6Ra","PEN1-6Rb","PEN1-7R")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_PB$nameid.from <- sapply(FIBSEM_PB$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_PB$nameid.to <- sapply(FIBSEM_PB$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
PBlevels <- c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6Rc","EPG-6La","EPG-6Lb","EPG-6Lc",
              "Delta7-5R4La","Delta7-5R4Lb","Delta7-5R4Lc","Delta7-5R4Ld","Delta7-5R4Le",
              "Delta7-6R3La","Delta7-6R3Lb","Delta7-6R3Lc","Delta7-6R3Ld",
              "Delta7-7R2La","Delta7-7R2Lb","Delta7-7R2Lc","Delta7-7R2Ld","Delta7-7R2Le",
              "Delta7-2R7La","Delta7-2R7Lb","Delta7-2R7Lc",
              "Delta7-1R9R8La","Delta7-1R9R8Lb","Delta7-1R9R8Lc","Delta7-1R9R8Ld","Delta7-1R9R8Le",
              "PEN1-5R","PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb","PEN1-7R","PEN1-7L")
 
nronsToAddPre <-  c("Delta7-1R9R8La","Delta7-1R9R8Lb","Delta7-1R9R8Lc","Delta7-1R9R8Ld","Delta7-1R9R8Le")
nronsToAddPost <- c("PEN1-5R","PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb","PEN1-7R","PEN1-7L")
FIBSEM_PB <- FIBSEM_PB %>% select(nameid.from, nameid.to, ROIweight)
for (nPre in 1:length(nronsToAddPre)){
  for (nPost in 1:length(nronsToAddPost)){
    if (nrow(FIBSEM_PB %>%
             filter(as.character(nameid.from) == nronsToAddPre[nPre] &
                    as.character(nameid.to) == nronsToAddPost[nPost])) == 0)
      FIBSEM_PB <- FIBSEM_PB %>% rbind(data.frame(nameid.from = nronsToAddPre[nPre], nameid.to = nronsToAddPost[nPost], ROIweight = 0))
  }
}
FIBSEM_PB <- FIBSEM_PB %>% dcast(nameid.from~nameid.to)
FIBSEM_PB[is.na(FIBSEM_PB)] <- 0
FIBSEM_PB <- melt(FIBSEM_PB)
colnames(FIBSEM_PB) <- c("nameid.from","nameid.to","ROIweight")
FIBSEM_PB$nameid.from <- factor(FIBSEM_PB$nameid.from, levels = PBlevels)
FIBSEM_PB$nameid.to <- factor(FIBSEM_PB$nameid.to, levels = PBlevels)

FIBSEM_PB <- FIBSEM_PB %>% filter(!grepl("Delta7",nameid.to) & !grepl("EPG",nameid.to))

gFIBSEM <- ggplot(FIBSEM_PB) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =75, limits=c(0,150)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 12.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\PBEPGsD7sPEN1s_FIBSEM.pdf", width = 10, height = 10)
print(gFIBSEM)
dev.off()
```

Compare the FAFB data to the FIBSEM data - EB
```{r}

synapseCutOff = 0

FAFB_EB_df <-FAFBLoad("EB") %>% filter(nameid != "EQ5" & partnerid != "EQ5")

FAFBNames <- FAFB_EB_df$nameid %>% as.character() %>% append(FAFB_EB_df$partnerid %>% as.character()) %>% unique()
newFAFBNames <- c("PEN1-5R", "PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb", "PEN1-7R", "PEN1-7L",
                  "PEN2-5R", "PEN2-5L","PEN2-6Ra","PEN2-6Rb","PEN2-6La","PEN2-6Lb", "PEN2-7R", "PEN2-7L",
                  "EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6La","EPG-6Lb",
                  "PEG-5R", "PEG-5L","PEG-6R","PEG-6L",
                  "R4m-a","R4m-b","R4m-c","R4m-d","R4m-e","R4m-f","R4m-g")
EBlevels <- c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6La","EPG-6Lb",
              "PEN1-5R", "PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb", "PEN1-7R", "PEN1-7L",
              "PEN2-5R", "PEN2-5L","PEN2-6Ra","PEN2-6Rb","PEN2-6La","PEN2-6Lb", "PEN2-7R", "PEN2-7L",
              "PEG-5R", "PEG-5L","PEG-6R","PEG-6L",
              "R4m-a","R4m-b","R4m-c","R4m-d","R4m-e","R4m-f","R4m-g")
nameLU_FAFB <- data.frame(oldName = FAFBNames, newName = newFAFBNames)
FAFB_EB_df$nameid <- sapply(FAFB_EB_df$nameid, function(x) nameLU_FAFB$newName[match(as.character(x), nameLU_FAFB$oldName)])
FAFB_EB_df$nameid <- factor(FAFB_EB_df$nameid, levels = EBlevels)
FAFB_EB_df$partnerid <- sapply(FAFB_EB_df$partnerid, function(x) nameLU_FAFB$newName[match(as.character(x), nameLU_FAFB$oldName)])
FAFB_EB_df$partnerid <- factor(FAFB_EB_df$partnerid, levels = EBlevels)

gFAFB <- ggplot(FAFB_EB_df  %>% filter(weight > synapseCutOff)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =175/2, limits=c(0,175)) +
  geom_tile(aes(nameid,partnerid,fill=weight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 10.5) + geom_hline(yintercept = 18.5) + geom_hline(yintercept = 26.5) + geom_hline(yintercept = 30.5) + 
  geom_vline(xintercept = 10.5) + geom_vline(xintercept = 18.5) + geom_vline(xintercept = 26.5) + geom_vline(xintercept = 30.5)

ggsave("FAFB_EB.pdf", plot = gFAFB, device='pdf', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\",
       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)

neuronList = c("PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L7",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R6",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L6",
              "R4d")

FIBSEM_EB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "EB")
FIBSEM_EB$nameid.from = paste(as.character(FIBSEM_EB$name.from), as.character(FIBSEM_EB$from), sep = "_")
FIBSEM_EB$nameid.to = paste(as.character(FIBSEM_EB$name.to), as.character(FIBSEM_EB$to), sep = "_")

gFIBSEM <- ggplot(FIBSEM_EB  %>% filter(ROIweight > synapseCutOff)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =175/2, limits=c(0,175)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1)

ggsave("FIBSEM_EB.pdf", plot = gFIBSEM, device='pdf', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\",
       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)
```

Downselect the FIBSEM neurons for a direct comparison
```{r}
DSneuronList <- c("EPG\\\\\\\\(PB08\\\\\\\\)_R6",
                  "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
                  "R4d")
numNrons <-  c(2,2,7)

FIBSEM_EB_Cut <- FIBSEM_EB

for (ds in 1:length(DSneuronList)){
  bodyids2cut <- getBodyIdsForList(DSneuronList[ds])$bodyid
  bodyids2cut <- bodyids2cut %>% sample(length(bodyids2cut)-numNrons[ds])
  nameids2cut <- paste(neuprint_get_meta(bodyids2cut)$name,bodyids2cut,sep='_')
  FIBSEM_EB_Cut <- FIBSEM_EB_Cut %>% 
    filter(!(nameid.from %in% nameids2cut) & !(nameid.to %in% nameids2cut))
}

FIBSEMNames <- FIBSEM_EB_Cut$nameid.from %>% as.character() %>% append(FIBSEM_EB_Cut$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb",
                    "PEG-5L", "PEG-6L","PEG-5R","PEG-6R",
                    "PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-7L","PEN1-5R", "PEN1-6Ra","PEN1-6Rb","PEN1-7R",
                    "PEN2-5L", "PEN2-6La","PEN2-6Lb","PEN2-7L","PEN2-5R", "PEN2-6Ra","PEN2-6Rb","PEN2-7R",
                    "R4m-a","R4m-b","R4m-c","R4m-d","R4m-e","R4m-f","R4m-g")

nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_EB_Cut$nameid.from <- sapply(FIBSEM_EB_Cut$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB_Cut$nameid.from <- factor(FIBSEM_EB_Cut$nameid.from, levels = EBlevels)
FIBSEM_EB_Cut$nameid.to <- sapply(FIBSEM_EB_Cut$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB_Cut$nameid.to <- factor(FIBSEM_EB_Cut$nameid.to, levels = EBlevels)

gFIBSEM_DS <- ggplot(FIBSEM_EB_Cut) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =175/2, limits=c(0,175)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) + ggtitle("select FIBSEM data") +
  geom_hline(yintercept = 10.5) + geom_hline(yintercept = 18.5) + geom_hline(yintercept = 26.5) + geom_hline(yintercept = 30.5) + 
  geom_vline(xintercept = 10.5) + geom_vline(xintercept = 18.5) + geom_vline(xintercept = 26.5) + geom_vline(xintercept = 30.5)

print(gFAFB)
print(gFIBSEM_DS)
```

Compare the two matrices
```{r}
FAFB_EB_df_Mat <- FAFB_EB_df %>% dcast(partnerid~nameid)
FAFB_EB_df_Mat[is.na(FAFB_EB_df_Mat)] <- 0
rownames(FAFB_EB_df_Mat) <- FAFB_EB_df_Mat$partnerid
FAFB_EB_df_Mat <- FAFB_EB_df_Mat[,2:ncol(FAFB_EB_df_Mat)] %>% data.matrix

FIBSEM_EB_Cut_Mat <- FIBSEM_EB_Cut %>% select(nameid.from,nameid.to,ROIweight) %>% dcast(nameid.from~nameid.to)
FIBSEM_EB_Cut_Mat[is.na(FIBSEM_EB_Cut_Mat)] <- 0 
rownames(FIBSEM_EB_Cut_Mat) <- FIBSEM_EB_Cut_Mat$partnerid
FIBSEM_EB_Cut_Mat <- FIBSEM_EB_Cut_Mat[,2:ncol(FIBSEM_EB_Cut_Mat)] %>% data.matrix

matDiff <- FAFB_EB_df_Mat - FIBSEM_EB_Cut_Mat
matSum <- FAFB_EB_df_Mat + FIBSEM_EB_Cut_Mat

perMat <- matrix(0L,nrow=nrow(matDiff),ncol=ncol(matDiff))
diffMat <- matrix(0L,nrow=nrow(matDiff),ncol=ncol(matDiff))
for (r in 1:nrow(perMat)){
  for (c in 1:ncol(perMat)){
    if (FAFB_EB_df_Mat[r,c] == 0){
      diffMat[r,c] <- -FIBSEM_EB_Cut_Mat[r,c]
      next
    }
    if (FIBSEM_EB_Cut_Mat[r,c] == 0){
      diffMat[r,c] <- FAFB_EB_df_Mat[r,c]
      next
    }
    if (matSum[r,c] > 0)
      perMat[r,c] <- matDiff[r,c]/matSum[r,c]
  }
}

rownames(perMat) <- FAFB_EB_df$partnerid %>% as.character() %>% unique() %>% sort()
rownames(diffMat) <- FAFB_EB_df$partnerid %>% as.character() %>% unique() %>% sort()
colnames(perMat) <- FAFB_EB_df$nameid %>% as.character() %>% unique() %>% sort()
colnames(diffMat) <- FAFB_EB_df$nameid %>% as.character() %>% unique() %>% sort()

gPer <- ggplot(melt(perMat)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint =0, limits=c(-1,1)) +
  geom_tile(aes(Var2,Var1,fill=value))+coord_fixed(ratio=1,expand=FALSE) + ggtitle("diff/sum when both have synapses") +
  geom_hline(yintercept = 10.5) + geom_hline(yintercept = 18.5) + geom_hline(yintercept = 26.5) + geom_hline(yintercept = 30.5) + 
  geom_vline(xintercept = 10.5) + geom_vline(xintercept = 18.5) + geom_vline(xintercept = 26.5) + geom_vline(xintercept = 30.5)

gDiff <- ggplot(melt(diffMat)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint =0, limits=c(-45,45)) +
  geom_tile(aes(Var2,Var1,fill=value))+coord_fixed(ratio=1,expand=FALSE) + ggtitle("synapses for only one dataset") +
  geom_hline(yintercept = 10.5) + geom_hline(yintercept = 18.5) + geom_hline(yintercept = 26.5) + geom_hline(yintercept = 30.5) + 
  geom_vline(xintercept = 10.5) + geom_vline(xintercept = 18.5) + geom_vline(xintercept = 26.5) + geom_vline(xintercept = 30.5)

print(gPer)
print(gDiff)
```

Put them all on one plot and compare
```{r}
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\EBComp.pdf", width = 20, height = 20)
print(grid.arrange(gFAFB,gFIBSEM_DS,gPer,gDiff,
                   layout_matrix = rbind(c(3,1),c(4,5))))
dev.off()
```

Plot a summary statistic for the per and diff metrics
```{r}
perEB <- melt(perMat)
diffEB <- melt(diffMat)

perEB <- perEB[which(perEB$value != 0),]
diffEB <- diffEB[which(diffEB$value != 0),]

perEB$supergroup.from <- "columnar"
perEB[which(grepl("R4m",as.character(perEB$Var1))),]$supergroup.from <- "tangential"
perEB$supergroup.to <- "columnar"
perEB[which(grepl("R4m",as.character(perEB$Var2))),]$supergroup.to <- "tangential"
perEB <- perEB %>% mutate(connType = paste(supergroup.from, supergroup.to, sep="->"))

diffEB$supergroup.from <- "columnar"
diffEB[which(grepl("R4m",as.character(diffEB$Var1))),]$supergroup.from <- "tangential"
diffEB$supergroup.to <- "columnar"
diffEB[which(grepl("R4m",as.character(diffEB$Var2))),]$supergroup.to <- "tangential"
diffEB <- diffEB %>% mutate(connType = paste(supergroup.from, supergroup.to, sep="->"))

ggplot(perEB) + geom_point(aes(x = as.factor(connType), y = value),size=4,alpha=0.25) + 
  theme_classic() + ylim(-1,1) + geom_hline(yintercept = 0) +
  xlab('partners') + ylab('(FAFB cts - FIBSEM cts)/(total cts)')

ggplot(diffEB) + geom_point(aes(x = as.factor(connType), y = value),size=4,alpha=0.25) + 
  theme_classic() + ylim(-30,30) + geom_hline(yintercept = 0) +
  xlab('partners') + ylab('FIBSEM cts  FAFB cts')
```

Just plot EPG to EPG connections in the EB
```{r}
neuronList = c("EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6")

FIBSEM_EB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "EB")
FIBSEM_EB$nameid.from = paste(as.character(FIBSEM_EB$name.from), as.character(FIBSEM_EB$from), sep = "_")
FIBSEM_EB$nameid.to = paste(as.character(FIBSEM_EB$name.to), as.character(FIBSEM_EB$to), sep = "_")

FIBSEMNames <- FIBSEM_EB$nameid.from %>% as.character() %>% append(FIBSEM_EB$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-6Lc","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb","EPG-6Rc")
EBlevels <- c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6Rc","EPG-6La","EPG-6Lb","EPG-6Lc")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_EB$nameid.from <- sapply(FIBSEM_EB$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB$nameid.from <- factor(FIBSEM_EB$nameid.from, levels = EBlevels)
FIBSEM_EB$nameid.to <- sapply(FIBSEM_EB$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB$nameid.to <- factor(FIBSEM_EB$nameid.to, levels = EBlevels)

gFIBSEM <- ggplot(FIBSEM_EB  %>% filter(ROIweight > synapseCutOff)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =50, limits=c(0,100)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 6.5) + geom_hline(yintercept = 9.5) + 
  geom_vline(xintercept = 6.5) + geom_vline(xintercept = 9.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\EBEPGs_FIBSEM.pdf", width = 5, height = 5)
print(gFIBSEM)
dev.off()
```

Just plot EPG and PEN1 connections in the EB
```{r}
neuronList = c("EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7")

FIBSEM_EB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "EB")
FIBSEM_EB$nameid.from = paste(as.character(FIBSEM_EB$name.from), as.character(FIBSEM_EB$from), sep = "_")
FIBSEM_EB$nameid.to = paste(as.character(FIBSEM_EB$name.to), as.character(FIBSEM_EB$to), sep = "_")

FIBSEMNames <- FIBSEM_EB$nameid.from %>% as.character() %>% append(FIBSEM_EB$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-6Lc","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb","EPG-6Rc",
                    "PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-7L","PEN1-5R", "PEN1-6Ra","PEN1-6Rb","PEN1-7R")
EBlevels <- c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6Rc","EPG-6La","EPG-6Lb","EPG-6Lc",
              "PEN1-5R","PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb","PEN1-7R","PEN1-7L")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_EB$nameid.from <- sapply(FIBSEM_EB$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB$nameid.from <- factor(FIBSEM_EB$nameid.from, levels = EBlevels)
FIBSEM_EB$nameid.to <- sapply(FIBSEM_EB$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB$nameid.to <- factor(FIBSEM_EB$nameid.to, levels = EBlevels)

gFIBSEM <- ggplot(FIBSEM_EB) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =60, limits=c(0,120)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 12.5) + 
  geom_vline(xintercept = 12.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\EBEPGsPEN1s_FIBSEM.pdf", width = 5, height = 5)
print(gFIBSEM)
dev.off()
```

Just plot EPG, PEN2, and PEG connections in the EB
```{r}
neuronList = c("EPG\\\\\\\\(PB08\\\\\\\\)_R5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L5",
              "EPG\\\\\\\\(PB08\\\\\\\\)_R6",
              "EPG\\\\\\\\(PB08\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L7",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L5",
              "PEG\\\\\\\\(PB07\\\\\\\\)_R6",
              "PEG\\\\\\\\(PB07\\\\\\\\)_L6")

FIBSEM_EB = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "EB")
FIBSEM_EB$nameid.from = paste(as.character(FIBSEM_EB$name.from), as.character(FIBSEM_EB$from), sep = "_")
FIBSEM_EB$nameid.to = paste(as.character(FIBSEM_EB$name.to), as.character(FIBSEM_EB$to), sep = "_")

FIBSEMNames <- FIBSEM_EB$nameid.from %>% as.character() %>% append(FIBSEM_EB$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6La","EPG-6Lb","EPG-6Lc","EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-6Ra","EPG-6Rb","EPG-6Rc",
                    "PEG-5L", "PEG-6L","PEG-5R", "PEG-6R",
                    "PEN2-5L", "PEN2-6La","PEN2-6Lb","PEN2-7L","PEN2-5R", "PEN2-6Ra","PEN2-6Rb","PEN2-7R")
EBlevels <- c("EPG-5Ra","EPG-5Rb","EPG-5Rc","EPG-5La","EPG-5Lb","EPG-5Lc","EPG-6Ra","EPG-6Rb","EPG-6Rc","EPG-6La","EPG-6Lb","EPG-6Lc",
              "PEN2-5R","PEN2-5L","PEN2-6Ra","PEN2-6Rb","PEN2-6La","PEN2-6Lb","PEN2-7R","PEN2-7L",
              "PEG-5L","PEG-5R","PEG-6R","PEG-6L")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_EB$nameid.from <- sapply(FIBSEM_EB$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB$nameid.from <- factor(FIBSEM_EB$nameid.from, levels = EBlevels)
FIBSEM_EB$nameid.to <- sapply(FIBSEM_EB$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_EB$nameid.to <- factor(FIBSEM_EB$nameid.to, levels = EBlevels)

gFIBSEM <- ggplot(FIBSEM_EB) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =50, limits=c(0,100)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 12.5) + geom_hline(yintercept = 20.5) +
  geom_vline(xintercept = 12.5) + geom_vline(xintercept = 20.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\EBEPGsPEN2sPEGs_FIBSEM.pdf", width = 5, height = 5)
print(gFIBSEM)
dev.off()
```

Compare the FAFB data to the FIBSEM data - NO
```{r}

synapseCutOff = 0

FAFB_NO_df <-FAFBLoad("NO") %>% filter(nameid != "GLN" & partnerid != "GLN")

FAFBNames <- FAFB_NO_df$nameid %>% as.character() %>% append(FAFB_NO_df$partnerid %>% as.character()) %>% unique()
newFAFBNames <- c("PEN1-5R", "PEN1-5L","PEN1-6Ra","PEN1-6Rb","PEN1-6La","PEN1-6Lb", "PEN1-7R", "PEN1-7L",
                  "PEN2-5R", "PEN2-5L","PEN2-6Ra","PEN2-6Rb","PEN2-6La","PEN2-6Lb", "PEN2-7R", "PEN2-7L")
newLevels <- c("PEN1-5R","PEN1-6Ra","PEN1-6Rb","PEN1-7R","PEN1-5L","PEN1-6La","PEN1-6Lb","PEN1-7L",
               "PEN2-5R","PEN2-6Ra","PEN2-6Rb","PEN2-7R","PEN2-5L","PEN2-6La","PEN2-6Lb","PEN2-7L") %>% as.factor()
nameLU_FAFB <- data.frame(oldName = FAFBNames, newName = newFAFBNames)
FAFB_NO_df$nameid <- sapply(FAFB_NO_df$nameid, function(x) nameLU_FAFB$newName[match(as.character(x), nameLU_FAFB$oldName)])
FAFB_NO_df$nameid <- factor(FAFB_NO_df$nameid, levels = newLevels)
FAFB_NO_df$partnerid <- sapply(FAFB_NO_df$partnerid, function(x) nameLU_FAFB$newName[match(as.character(x), nameLU_FAFB$oldName)])
FAFB_NO_df$partnerid <- factor(FAFB_NO_df$partnerid, levels = newLevels)

gFAFB <- ggplot(FAFB_NO_df  %>% filter(weight > synapseCutOff)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =60, limits=c(0,200)) +
  geom_tile(aes(nameid,partnerid,fill=weight))+coord_fixed(ratio=1)

ggsave("FAFB_NO.pdf", plot = last_plot(), device='pdf', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\",
       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)

neuronListPost = c("PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L7")

neuronListPre = append(neuronListPost,"GLN\\\\\\\\(LAL-NO1\\\\\\\\)\\\\\\\\(AVM08\\\\\\\\)_L")

FIBSEM_NO = getConnectionTable_forSubset(getBodyIdsForList(neuronListPre)$bodyid, getBodyIdsForList(neuronListPost)$bodyid, "NO")
FIBSEM_NO$nameid.from = paste(as.character(FIBSEM_NO$name.from), as.character(FIBSEM_NO$from), sep = "_")
FIBSEM_NO$nameid.to = paste(as.character(FIBSEM_NO$name.to), as.character(FIBSEM_NO$to), sep = "_")

FIBSEMNames <- FIBSEM_NO$nameid.from %>% as.character() %>% append(FIBSEM_NO$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-7L","PEN1-5R", "PEN1-6Ra","PEN1-6Rb","PEN1-7R",
                    "PEN2-5L", "PEN2-6La","PEN2-6Lb","PEN2-7L","PEN2-5R", "PEN2-6Ra","PEN2-6Rb","PEN2-7R")

nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_NO$nameid.from <- sapply(FIBSEM_NO$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_NO$nameid.from <- factor(FIBSEM_NO$nameid.from, levels = newLevels)
FIBSEM_NO$nameid.to <- sapply(FIBSEM_NO$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_NO$nameid.to <- factor(FIBSEM_NO$nameid.to, levels = newLevels)

gFIBSEM <- ggplot(FIBSEM_NO  %>% filter(ROIweight > synapseCutOff)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =60, limits=c(0,200)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1)

ggsave("FIBSEM_NO.pdf", plot = last_plot(), device='pdf', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\",
       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)
```

Compare the two matrices
```{r}
FAFB_NO_df_Mat <- FAFB_NO_df %>% dcast(partnerid~nameid)
FAFB_NO_df_Mat[is.na(FAFB_NO_df_Mat)] <- 0
rownames(FAFB_NO_df_Mat) <- FAFB_NO_df_Mat$partnerid
FAFB_NO_df_Mat <- FAFB_NO_df_Mat[,2:ncol(FAFB_NO_df_Mat)] %>% data.matrix

FIBSEM_NO_Cut_Mat <- FIBSEM_NO %>% select(nameid.from,nameid.to,ROIweight) %>% dcast(nameid.from~nameid.to)
FIBSEM_NO_Cut_Mat[is.na(FIBSEM_NO_Cut_Mat)] <- 0 
rownames(FIBSEM_NO_Cut_Mat) <- FIBSEM_NO_Cut_Mat$partnerid
FIBSEM_NO_Cut_Mat <- FIBSEM_NO_Cut_Mat[,2:ncol(FIBSEM_NO_Cut_Mat)] %>% data.matrix

matDiff <- FAFB_NO_df_Mat - FIBSEM_NO_Cut_Mat
matSum <- FAFB_NO_df_Mat + FIBSEM_NO_Cut_Mat

perMat <- matrix(0L,nrow=nrow(matDiff),ncol=ncol(matDiff))
diffMat <- matrix(0L,nrow=nrow(matDiff),ncol=ncol(matDiff))
for (r in 1:nrow(perMat)){
  for (c in 1:ncol(perMat)){
    if (FAFB_NO_df_Mat[r,c] == 0){
      diffMat[r,c] <- -FIBSEM_NO_Cut_Mat[r,c]
      next
    }
    if (FIBSEM_NO_Cut_Mat[r,c] == 0){
      diffMat[r,c] <- FAFB_NO_df_Mat[r,c]
      next
    }
    if (matSum[r,c] > 0)
      perMat[r,c] <- matDiff[r,c]/matSum[r,c]
  }
}

rownames(perMat) <- FAFB_NO_df$partnerid %>% as.character() %>% unique() %>% sort()
rownames(diffMat) <- FAFB_NO_df$partnerid %>% as.character() %>% unique() %>% sort()
colnames(perMat) <- FAFB_NO_df$nameid %>% as.character() %>% unique() %>% sort()
colnames(diffMat) <- FAFB_NO_df$nameid %>% as.character() %>% unique() %>% sort()

gPer <- ggplot(melt(perMat)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint =0, limits=c(-1,1)) +
  geom_tile(aes(Var2,Var1,fill=value))+coord_fixed(ratio=1,expand=FALSE) + ggtitle("diff/sum when both have synapses")

gDiff <- ggplot(melt(diffMat)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint =0, limits=c(-45,45)) +
  geom_tile(aes(Var2,Var1,fill=value))+coord_fixed(ratio=1,expand=FALSE) + ggtitle("synapses for only one dataset")

print(gPer)
print(gDiff)
```

Put them all on one plot and compare
```{r}
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\NOComp.pdf", width = 20, height = 20)
print(grid.arrange(gFAFB,gFIBSEM,gPer,gDiff,
                   layout_matrix = rbind(c(3,1),c(4,5))))
dev.off()
```

Plot a summary statistic for the per and diff metrics
```{r}
perNO <- melt(perMat)
diffNO <- melt(diffMat)

perNO <- perEB[which(perNO$value != 0),]
diffNO <- diffEB[which(diffNO$value != 0),]

perNO$supergroup.from <- "columnar"
perNO$supergroup.to <- "columnar"
perNO <- perNO %>% mutate(connType = paste(supergroup.from, supergroup.to, sep="->"))

diffNO$supergroup.from <- "columnar"
diffNO$supergroup.to <- "columnar"
diffNO <- diffNO %>% mutate(connType = paste(supergroup.from, supergroup.to, sep="->"))

ggplot(perNO) + geom_point(aes(x = as.factor(connType), y = value),size=4,alpha=0.25) + 
  theme_classic() + ylim(-1,1) + geom_hline(yintercept = 0) +
  xlab('partners') + ylab('(FAFB cts - FIBSEM cts)/(total cts)')

ggplot(diffNO) + geom_point(aes(x = as.factor(connType), y = value),size=4,alpha=0.25) + 
  theme_classic() + ylim(-30,30) + geom_hline(yintercept = 0) +
  xlab('partners') + ylab('FIBSEM cts  FAFB cts')
```

Plot the FIBSEM vs. FAFB comparison statistics for the PB, EB, and NO data
```{r}
dodge = position_dodge(width=0.25)

perPB$ROI <- "PB"
perEB$ROI <- "EB"
perNO$ROI <- "NO"

perAll <- rbind(perPB,rbind(perEB,perNO))

gPer <- ggplot(perAll) + geom_point(aes(x = as.factor(connType), y = value, color=ROI),size=3,alpha=0.1,position=dodge) + 
  theme_classic() + ylim(-1,1) + geom_hline(yintercept = 0) +
  ylab('(FAFB cts - FIBSEM cts)/(total cts)') + theme(axis.title.x = element_blank())

diffPB$ROI <- "PB"
diffEB$ROI <- "EB"
diffNO$ROI <- "NO"

diffAll <- rbind(diffPB,rbind(diffEB,diffNO))

gDiff <- ggplot(diffAll) + geom_point(aes(x = as.factor(connType), y = value, color=ROI),size=3,alpha=0.1,position=dodge) + 
  theme_classic() + ylim(-30,30) + geom_hline(yintercept = 0) +
  ylab('FIBSEM cts          FAFB cts') + theme(axis.title.x = element_blank()) + ggtitle("synapses in one dataset but not the other")

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\SummaryStatistics.pdf", width = 8, height = 8)
print(grid.arrange(gPer, gDiff, nrow = 2))
dev.off()

```

Just plot PEN1 connections in the NO
```{r}
neuronList = c("PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7")

FIBSEM_NO = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "NO")
FIBSEM_NO$nameid.from = paste(as.character(FIBSEM_NO$name.from), as.character(FIBSEM_NO$from), sep = "_")
FIBSEM_NO$nameid.to = paste(as.character(FIBSEM_NO$name.to), as.character(FIBSEM_NO$to), sep = "_")

FIBSEMNames <- FIBSEM_NO$nameid.from %>% as.character() %>% append(FIBSEM_NO$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-7L","PEN1-5R", "PEN1-6Ra","PEN1-6Rb","PEN1-7R")
NOlevels <- c("PEN1-5R","PEN1-6Ra","PEN1-6Rb","PEN1-7R","PEN1-5L","PEN1-6La","PEN1-6Lb","PEN1-7L")
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_NO$nameid.from <- sapply(FIBSEM_NO$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_NO$nameid.from <- factor(FIBSEM_NO$nameid.from, levels = NOlevels)
FIBSEM_NO$nameid.to <- sapply(FIBSEM_NO$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_NO$nameid.to <- factor(FIBSEM_NO$nameid.to, levels = NOlevels)

gFIBSEM <- ggplot(FIBSEM_NO) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =25, limits=c(0,50)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 4.5) + 
  geom_vline(xintercept = 4.5)

print(gFIBSEM)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\NOPEN1s_FIBSEM.pdf", width = 5, height = 5)
print(gFIBSEM)
dev.off()
```

All PEN FIBSEM data - NO
```{r}
neuronList = c("PEN_a\\\\\\\\(PB06a\\\\\\\\)_R5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L5",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L6",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_R7",
              "PEN_a\\\\\\\\(PB06a\\\\\\\\)_L7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L5",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L6",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_R7",
              "PEN_b\\\\\\\\(PB06b\\\\\\\\)_L7")

FIBSEM_NO = getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "NO")
FIBSEM_NO$nameid.from = paste(as.character(FIBSEM_NO$name.from), as.character(FIBSEM_NO$from), sep = "_")
FIBSEM_NO$nameid.to = paste(as.character(FIBSEM_NO$name.to), as.character(FIBSEM_NO$to), sep = "_")

FIBSEMNames <- FIBSEM_NO$nameid.from %>% as.character() %>% append(FIBSEM_NO$nameid.to %>% as.character()) %>% unique() %>% sort()
newFIBSEMNames <- c("PEN1-5L", "PEN1-6La","PEN1-6Lb","PEN1-7L","PEN1-5R", "PEN1-6Ra","PEN1-6Rb","PEN1-7R",
                    "PEN2-5L", "PEN2-6La","PEN2-6Lb","PEN2-7L","PEN2-5R", "PEN2-6Ra","PEN2-6Rb","PEN2-7R")
newLevels <- c("PEN1-5R","PEN1-6Ra","PEN1-6Rb","PEN1-7R","PEN1-5L","PEN1-6La","PEN1-6Lb","PEN1-7L",
               "PEN2-5R","PEN2-6Ra","PEN2-6Rb","PEN2-7R","PEN2-5L","PEN2-6La","PEN2-6Lb","PEN2-7L") %>% as.factor()
nameLU_FIBSEM <- data.frame(oldName = FIBSEMNames, newName = newFIBSEMNames)
FIBSEM_NO$nameid.from <- sapply(FIBSEM_NO$nameid.from, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_NO$nameid.from <- factor(FIBSEM_NO$nameid.from, levels = newLevels)
FIBSEM_NO$nameid.to <- sapply(FIBSEM_NO$nameid.to, function(x) nameLU_FIBSEM$newName[match(as.character(x), nameLU_FIBSEM$oldName)])
FIBSEM_NO$nameid.to <- factor(FIBSEM_NO$nameid.to, levels = newLevels)

gFIBSEM <- ggplot(FIBSEM_NO) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="#ff694a", high="#6b000d", midpoint =30, limits=c(0,50)) +
  geom_tile(aes(nameid.to,nameid.from,fill=ROIweight))+coord_fixed(ratio=1) +
  geom_hline(yintercept = 8.5) + geom_vline(xintercept = 8.5)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\2019_EMPaper\\Manuscript\\RevisionForNeuron\\Figures\\FIBSEMComp\\NOPENs_FIBSEM.pdf", width = 5, height = 5)
print(gFIBSEM)
dev.off()
```


EPG and D7 connections in PB
```{r}
neuronList <- c("EPG","Delta7")
FIBSEM_EPGD7PB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "PB")
FIBSEM_EPGD7PB <- FIBSEM_EPGD7PB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt <- plotConnectivityMatrix(FIBSEM_EPGD7PB, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt <- structureMatrixPlotByType(conTabPlt)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\EPGD7PB_Connectivity.pdf", width = 5, height = 4)
print(conTabPlt)
dev.off()
```

hyper local recurrence in EB of EPGs
```{r}
neuronList <- c("EPG")
FIBSEM_EPGEB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "EB")
FIBSEM_EPGEB <- FIBSEM_EPGEB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt <- plotConnectivityMatrix(FIBSEM_EPGEB, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt <- structureMatrixPlotByType(conTabPlt)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\EPGEB_Connectivity.pdf", width = 5, height = 4)
print(conTabPlt)
dev.off()
```

EPG + D7 to PEN1/2 in PB
```{r}
neuronList_Pre <- c("EPG","Delta7")
neuronList_Post <- c("PEN_a","PEN_b")
FIBSEM_EPGD7ToPENsPB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList_Pre)$bodyid, getBodyIdsForList(neuronList_Post)$bodyid, "PB")
FIBSEM_EPGD7ToPENsPB <- FIBSEM_EPGD7ToPENsPB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt <- plotConnectivityMatrix(FIBSEM_EPGD7ToPENsPB, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt <- structureMatrixPlotByType(conTabPlt)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\EPGD7ToPENPB_Connectivity.pdf", width = 4, height = 5)
print(conTabPlt)
dev.off()
```
 
EPG <-> PEN1/2 in EB
```{r}
neuronList <- c("EPG","PEN")
FIBSEM_EPGPENsEB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "EB")
FIBSEM_EPGPENsEB <- FIBSEM_EPGPENsEB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt <- plotConnectivityMatrix(FIBSEM_EPGPENsEB, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt <- structureMatrixPlotByType(conTabPlt)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\EPGPENsEB_Connectivity.pdf", width = 5, height = 4)
print(conTabPlt)
dev.off()
```
 
Ring neuron connectivity in the ring
```{r}
neuronList <- c("EPG","R4m")
FIBSEM_EPGR4mEB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList)$bodyid, getBodyIdsForList(neuronList)$bodyid, "EB")
FIBSEM_EPGR4mEB <- FIBSEM_EPGR4mEB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt <- plotConnectivityMatrix(FIBSEM_EPGR4mEB, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt <- structureMatrixPlotByType(conTabPlt)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\EPGRingEB_Connectivity.pdf", width = 5, height = 4)
print(conTabPlt)
dev.off()
``` 

PEN1 -> EPG synapse counts in EB
```{r}
neuronList_Pre <- c("PEN_a")
neuronList_Post <- c("EPG")
FIBSEM_PEN1ToEPGEB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList_Pre)$bodyid, getBodyIdsForList(neuronList_Post)$bodyid, "EB")
FIBSEM_PEN1ToEPGEB <- FIBSEM_PEN1ToEPGEB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt_PEN1 <- plotConnectivityMatrix(FIBSEM_PEN1ToEPGEB, byGroup = "id", connectionMeasure="ROIweight")
print(conTabPlt_PEN1)

FIBSEM_PEN1ToEPGEB <- FIBSEM_PEN1ToEPGEB %>% mutate(nameid.from = paste(name.from,from,sep='_'),
                                                    nameid.to = paste(name.to,to,sep='_'))
g_totSynsPEN1_L <- ggplot(FIBSEM_PENaToEPGEB %>% filter(grepl("_L",nameid.from))) +
  geom_bar(aes(y=ROIweight, x=nameid.to, fill = nameid.from),stat="identity") +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(g_totSynsPEN1_L)
g_totSynsPEN1_R <- ggplot(FIBSEM_PENaToEPGEB %>% filter(grepl("_R",nameid.from))) +
  geom_bar(aes(y=ROIweight, x=nameid.to, fill = nameid.from),stat="identity") +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(g_totSynsPEN1_R)

neuronList_Pre <- c("PEN_b")
neuronList_Post <- c("EPG")
FIBSEM_PEN2ToEPGEB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList_Pre)$bodyid, getBodyIdsForList(neuronList_Post)$bodyid, "EB")
FIBSEM_PEN2ToEPGEB <- FIBSEM_PEN2ToEPGEB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt_PEN2 <- plotConnectivityMatrix(FIBSEM_PEN2ToEPGEB, byGroup = "id", connectionMeasure="ROIweight")
print(conTabPlt_PEN2)

FIBSEM_PEN2ToEPGEB <- FIBSEM_PEN2ToEPGEB %>% mutate(nameid.from = paste(name.from,from,sep='_'),
                                                    nameid.to = paste(name.to,to,sep='_'))
g_totSynsPEN2_L <- ggplot(FIBSEM_PEN2ToEPGEB %>% filter(grepl("_L",nameid.from))) +
  geom_bar(aes(y=ROIweight, x=nameid.to, fill = nameid.from),stat="identity") +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(g_totSynsPEN2_L)
g_totSynsPEN2_R <- ggplot(FIBSEM_PEN2ToEPGEB %>% filter(grepl("_R",nameid.from))) +
  geom_bar(aes(y=ROIweight, x=nameid.to, fill = nameid.from),stat="identity") +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(g_totSynsPEN2_R)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\PENsEB_SynNums.pdf", width = 25, height = 10)
print(grid.arrange(conTabPlt_PEN1,g_totSynsPEN1_L,g_totSynsPEN1_R,
                   conTabPlt_PEN2,g_totSynsPEN2_L,g_totSynsPEN2_R,
                   layout_matrix=rbind(c(1,2,3),c(4,5,6))))
dev.off()
```

Quantify ring synapses around the ring
```{r}
EPGOrder <- c("R5","L4","R6","L3","R7","L2","R8","L1","R1","L8","R2","L7","R3","L6","R4","L5")

neuronList_Pre <- c("R4m")
neuronList_Post <- c("EPG")
FIBSEM_R4mToEPGEB <- getConnectionTable_forSubset(getBodyIdsForList(neuronList_Pre)$bodyid, getBodyIdsForList(neuronList_Post)$bodyid, "EB")
FIBSEM_R4mToEPGEB <- FIBSEM_R4mToEPGEB %>% filter(type.to != "EPGt" & type.from != "EPGt")

FIBSEM_R4mToEPGEB <- FIBSEM_R4mToEPGEB %>% mutate(nameid.from = paste(name.from,from,sep='_'),
                                                    nameid.to = paste(name.to,to,sep='_'))
preNames <- FIBSEM_R4mToEPGEB$nameid.from %>% unique() %>% as.character()
preNames_R <- preNames[which(grepl("_R_",preNames))]
preNames_L <- preNames[which(grepl("_L_",preNames))]
postNames <- FIBSEM_R4mToEPGEB$nameid.to %>% unique() %>% as.character()
postNames_sorted <- c()
for (o in 1:length(EPGOrder)){
  postNames_sorted <- append(postNames_sorted,postNames[which(grepl(EPGOrder[o],postNames))])
}
FIBSEM_R4mToEPGEB$nameid.to <- factor(FIBSEM_R4mToEPGEB$nameid.to, levels = as.factor(postNames_sorted))
FIBSEM_R4mToEPGEB$RNLoc <- "R"
FIBSEM_R4mToEPGEB[which(FIBSEM_R4mToEPGEB$nameid.from %in% preNames_L),]$RNLoc <- "L"

conTabPlt <- plotConnectivityMatrix(FIBSEM_R4mToEPGEB, byGroup = "id", connectionMeasure="ROIweight")
print(conTabPlt)

g_R4Profile <- ggplot()
for (pn in 1:length(preNames_R)){
  g_R4Profile <- g_R4Profile + geom_line(data = FIBSEM_R4mToEPGEB %>% filter(nameid.from == preNames_R[pn]),aes(x=as.factor(nameid.to),y=ROIweight,group=1,color=RNLoc))
}
for (pn in 1:length(preNames_L)){
  g_R4Profile <- g_R4Profile + geom_line(data = FIBSEM_R4mToEPGEB %>% filter(nameid.from == preNames_L[pn]),aes(x=as.factor(nameid.to),y=ROIweight,group=1,color=RNLoc))
}
g_R4Profile <- g_R4Profile + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(g_R4Profile)

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\RNsToEPGsEB_SynNums.pdf", width = 10, height = 10)
print(grid.arrange(conTabPlt,g_R4Profile,ncol=1))
dev.off()
```
 
Number of EPGs, PEGs, PENs per glom
```{r}
gloms <- c("L9","L8","L7","L6","L5","L4","L3","L2","L1",
           "R1","R2","R3","R4","R5","R6","R7","R8","R9")

nrons <- c("EPG","PEN_a","PEN_b","PEG")
g_list <- list()
for (n in 1:length(nrons)){
  nronNames <- paste0(getBodyIdsForList(nrons[n])$name, getBodyIdsForList(nrons[n])$bodyid, sep='_') %>% unique
  glomCts <- vector(mode="numeric", length=length(gloms))
  for (g in 1:length(gloms)){
    glomCts[g] <- length(which(grepl(gloms[g],nronNames)))
  }
  glomDF <- data.frame(gloms = factor(gloms,levels=as.factor(gloms)), counts = glomCts)
  g_list[[n]] <- ggplot(glomDF) + geom_bar(aes(x=gloms, y=counts),stat="identity") + ggtitle(paste(nrons[n],"neurons per glomerulus",sep='-')) +
    theme_classic() + ylim(0,4)
}

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\GlomCounts.pdf", width = 10, height = 5)
print(grid.arrange(grobs=g_list,layout_matrix=rbind(c(1,2),c(4,3))))
dev.off()

```

 Entire weight matrix (of given types) from FIBSEM dataset in EB,PB,NO
```{r}
nrons <- c("EPG","PEN","PEG","Delta7","R4m")

FIBSEM_PB <- getConnectionTable_forSubset(getBodyIdsForList(nrons)$bodyid, getBodyIdsForList(nrons)$bodyid, "PB")
FIBSEM_PB <- FIBSEM_PB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt_PB <- plotConnectivityMatrix(FIBSEM_PB, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt_PB <- structureMatrixPlotByType(conTabPlt_PB) + ggtitle("PB connectivity")

FIBSEM_EB <- getConnectionTable_forSubset(getBodyIdsForList(nrons)$bodyid, getBodyIdsForList(nrons)$bodyid, "EB")
FIBSEM_EB <- FIBSEM_EB %>% filter(type.to != "EPGt" & type.from != "EPGt")
conTabPlt_EB <- plotConnectivityMatrix(FIBSEM_EB, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt_EB <- structureMatrixPlotByType(conTabPlt_EB) + ggtitle("EB connectivity")

FIBSEM_NO <- getConnectionTable_forSubset(getBodyIdsForList(nrons)$bodyid, getBodyIdsForList(nrons)$bodyid, "NO")
conTabPlt_NO <- plotConnectivityMatrix(FIBSEM_NO, byGroup = "id", connectionMeasure="ROIweight")
conTabPlt_NO <- structureMatrixPlotByType(conTabPlt_NO) + ggtitle("NO connectivity")

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\Overview\\FAFBComp\\EBPBNO_Connectivity.pdf", width = 30, height = 8)
print(grid.arrange(conTabPlt_PB,conTabPlt_EB,conTabPlt_NO,nrow=1))
dev.off()
```
 