---
title: "FB explorations"
output: html_notebook
---

Load the libraries
```{r}
library(nat)
library(neuprintr)
library(tidyverse)
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\pathways.R")
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\visualizeConnectivityTables.R")
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\neuprintQueryUtils.R")
options(nat.plotengine = 'rgl')
```

Connect to neuprint
```{r}
neuprint_login()
```


Define the FB neuron types
```{r}
# Find the name of all neurons that get input in the FB
FBNronTypes = neuprint_find_neurons("FB")$bodytype %>% unique()
FBNronTypes <- FBNronTypes[which(!is.na(FBNronTypes))]
```

For each neuron type, find the number of inputs and outputs in or outside of the FB
```{r}
FBpreNpostRatios <- preNpostRatios(FBNronTypes,"FB")

FBpreNpostRatios <- FBpreNpostRatios[which(FBpreNpostRatios$preRelative > 0.05 | FBpreNpostRatios$postRelative > 0.05),]
FBpreNpostRatios <- FBpreNpostRatios[which(FBpreNpostRatios$regPr > 3 | FBpreNpostRatios$regPost > 3),]
FBpreNpostRatios <- FBpreNpostRatios[order(FBpreNpostRatios$prePostDiff),]

FBpreNpostRatios['classification'] = 'inner'
FBpreNpostRatios[which(FBpreNpostRatios$prePostDiff > 0.15),]$classification = 'input'
FBpreNpostRatios[which(FBpreNpostRatios$prePostDiff < -0.1),]$classification = 'output'
FBpreNpostRatios$classification <- factor(FBpreNpostRatios$classification, levels = c('input','inner','output'))

p <- ggplot(data = FBpreNpostRatios[which(!grepl("Delta",FBpreNpostRatios$type)),], aes()) + 
  geom_hline(yintercept = 0) +
  geom_point(aes(x= reorder(as.factor(type), -prePostRatio),
                 y=prePostDiff,
                 color=classification),
                 size = 3,
                 alpha = 0.2) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_color_manual(values = c('green','blue','red')) +
  xlab('neuron type') + ylab('pre ratio - post ratio')
print(p)
```

Look at who FB-Q's output to
```{r}
FQTypes = neuprint_search('FQ.*')$type %>% unique() 
FQ_Post = getConnectionTable(getBodyIdsForList(c("FQ")),"POST","CRE(R)")
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","CRE(L)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SMP(R)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SMP(L)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SIP(R)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SIP(L)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SLP(R)"))

for (tp in 1:length(FQTypes)){
  
  FQ_Post_Sum <- aggregate(weight~type+partnerType,
                              FQ_Post[which(FQ_Post$type==FQTypes[tp]),],
                              sum)
  FQ_Post_Mean <- aggregate(weight~type+partnerType,
                               FQ_Post[which(FQ_Post$type==FQTypes[tp]),],
                               mean)

  conmatPlot = ggplot(FQ_Post_Sum %>% filter(weight > 5)) + 
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
    geom_tile(aes(type,partnerType,fill=weight))
  print(conmatPlot)
  
  conmatPlot = ggplot(FQ_Post_Mean) + 
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
    geom_tile(aes(type,partnerType,fill=weight))
  print(conmatPlot)
    
}
```

Look at who PFR_b's output to
```{r}
PFRbs_Post <- getConnectionTable(getBodyIdsForList(c("PFR_b")),"POST","CRE(R)")

plotConnectivityMatrix(PFRbs_Post, synapseCutOff = 3, 1)

```



Get all Delta neurons and plot presynapses
```{r}
Deltas = neuprint_search("Delta.*")
DeltaTypes = unique(Deltas$type)

for (typeNow in 1:length(DeltaTypes)){
  if (is.na(DeltaTypes[typeNow])) {
    next
  }
  DeltaSyns = Deltas[which(Deltas$type == DeltaTypes[typeNow]),]$bodyid %>% neuprint_get_synapses()
  DeltaSyns <-  DeltaSyns %>% mutate(name=as.character(DeltaTypes[typeNow]))%>%  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
  
  p1 <- ggplot(DeltaSyns[which(DeltaSyns$prepost == 1),]) + geom_point(aes(x,z,color= bodyid))+coord_fixed(ratio = 1) + theme_void()+ ggtitle(as.character(DeltaTypes[typeNow]))
  
  print(p1)
}

```

Get all Delta neurons and plot postsynapses - for the Delta 0s, info goes up but doesn't come down...
```{r}
Deltas = neuprint_search("Delta.*")
DeltaTypes = unique(Deltas$type)

for (typeNow in 1:length(DeltaTypes)){
  if (is.na(DeltaTypes[typeNow])) {
    next
  }
  DeltaSyns = Deltas[which(Deltas$type == DeltaTypes[typeNow]),]$bodyid %>% neuprint_get_synapses()
  DeltaSyns <-  DeltaSyns %>% mutate(name=as.character(DeltaTypes[typeNow]))%>%  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
  
  p1 <- ggplot(DeltaSyns[which(DeltaSyns$prepost == 0),]) + geom_point(aes(x,z,color= bodyid))+coord_fixed(ratio = 1) + theme_void()+ ggtitle(as.character(DeltaTypes[typeNow]))
  
  print(p1)
}

```

Cluster each Delta into groups of 3 and plot the centers.
```{r}
for (typeNow in 1:length(DeltaTypes)){
  if (is.na(DeltaTypes[typeNow])) {
    next
  }
  bodyIds = Deltas[which(Deltas$type == DeltaTypes[typeNow]),]$bodyid
  
  #allCentsPre = data.frame(cents.x = c(), cents.y = c(), cents.z = c(), bodyid = c())
  allDists = data.frame(dist1 = c(), dist2 = c(), dist3 = c(), bodyid = c())

  
  for (bId in 1:length(bodyIds)){
    DeltaSyns = neuprint_get_synapses(bodyIds[bId])
    DeltaSyns <-  DeltaSyns %>% mutate(name=as.character(DeltaTypes[typeNow]))%>%  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
    
    kmeanMat = DeltaSyns[which(DeltaSyns$prepost == 1),] %>% select(x,y,z)
    synClusts = kmeans(kmeanMat,3, iter.max = 50, nstart = 10)

    centDist = dist(synClusts$centers)
    distsNow = data.frame(dist1 = centDist[1], dist2 = centDist[2], dist3 = centDist[3], bodyid = as.factor(bodyIds[bId]))
    allDists <- rbind(allDists,distsNow)
    #centsNow = data.frame(cents = synClusts$centers, bodyid = as.factor(bodyIds[bId]))
    #allCentsPre <- rbind(allCentsPre,centsNow)
  }
  
  p1 <- ggplot(allDists)+geom_point(aes(x=bodyid, y=dist1))+geom_point(aes(x=bodyid, y=dist2))+geom_point(aes(x=bodyid, y=dist3))
  
  print(p1)
}
```

```{r}
ThreeClusts = c("Delta0S","Delta12a","Delta12c","Delta12g","Delta12h","Delta6D","Delta6F_a")

for (typeNow in 1:length(DeltaTypes)){
  if (is.na(DeltaTypes[typeNow])) {
    next
  }
  bodyIds = Deltas[which(Deltas$type == DeltaTypes[typeNow]),]$bodyid
  if (DeltaTypes[typeNow] %in% ThreeClusts)
    numClusts = 3
  else
    numClusts = 2
  
  allPostGps = data.frame(dist1 = c(), dist2 = c(), dist3 = c(), bodyid = c())
  
  for (bId in 1:length(bodyIds)){
    DeltaSyns = neuprint_get_synapses(bodyIds[bId])
    DeltaSyns <-  DeltaSyns %>% mutate(name=as.character(DeltaTypes[typeNow]))%>%  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
    
    kmeanMat = DeltaSyns[which(DeltaSyns$prepost == 1),] %>% select(x,y,z)
   
    synClusts = kmeans(kmeanMat,numClusts, iter.max = 50, nstart = 10)
    
    postSyns = DeltaSyns[which(DeltaSyns$prepost == 0),] %>% select(x,y,z) %>% 
      mutate(dist1 = sqrt((x-synClusts$centers[1,1])^2+(y-synClusts$centers[1,2])^2+(z-synClusts$centers[1,3])^2))  %>% 
      mutate(dist2 = sqrt((x-synClusts$centers[2,1])^2+(y-synClusts$centers[2,2])^2+(z-synClusts$centers[2,3])^2))
    if (numClusts == 2){
      postClustIDs = postSyns %>% select(dist1, dist2) %>% apply(1,which.max)
      clustGps = data.frame(numGp1 = length(which(postClustIDs == 1)), numGp2 = length(which(postClustIDs == 2)), bodyid = as.factor(bodyIds[bId]))
    } else if (numClusts == 3){
      postSyns <- postSyns %>% mutate(dist3 = sqrt((x-synClusts$centers[3,1])^2+(y-synClusts$centers[3,2])^2+(z-synClusts$centers[3,3])^2))
      postClustIDs = postSyns %>% select(dist1, dist2, dist3) %>% apply(1,which.max)
      clustGps = data.frame(numGp1 = length(which(postClustIDs == 1)), numGp2 = length(which(postClustIDs == 2)), numGp3 = length(which(postClustIDs == 3)), bodyid = as.factor(bodyIds[bId]))
    }

    allPostGps <- rbind(allPostGps,clustGps)
    
  }
  if (numClusts==2)
    p1 <- ggplot(allPostGps)+geom_point(aes(x=bodyid, y=numGp1))+geom_point(aes(x=bodyid, y=numGp2))
  else
    p1 <- ggplot(allPostGps)+geom_point(aes(x=bodyid, y=numGp1))+geom_point(aes(x=bodyid, y=numGp2))+geom_point(aes(x=bodyid, y=numGp3))
  
  print(p1)
}
```

Analyses to do:
Show connections between those inputs and outputs
```{r}
PFNs_Post <- getConnectionTable(getBodyIdsForList(c("PFN")),"POST","FB")
conmatPlot = ggplot(PFNs_Post   %>% filter(weight > 3)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)
```

Look at inputs to PFL1,2,3s, group by type, calculate correlation
```{r}
PFL_Pre = getConnectionTable(getBodyIdsForList(c("PFL")),"PRE","FB")
  
PFL_Pre_Sum <- aggregate(weight~type+partnerType,
                            PFL_Pre,
                            sum)
PFL_Pre_Mean <- aggregate(weight~type+partnerType,
                             PFL_Pre,
                             mean)

conmatPlot = ggplot(PFL_Pre_Sum %>% filter(weight > 5)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

conmatPlot = ggplot(PFL_Pre_Mean) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

# Look at the correlations across input types
corrDat = spread(PFL_Pre_Mean,type,weight)
corrDat[is.na(corrDat)] <- 0
rownames(corrDat)<-corrDat$partnerType
corrDat$partnerType<-NULL
library(corrplot)
corrplot(cor(corrDat))
    
```

As above but for FQs
```{r}
FQ_Pre = getConnectionTable(getBodyIdsForList(c("FQ","PFR")),"PRE","FB")
  
FQ_Pre_Sum <- aggregate(weight~type+partnerType,
                            FQ_Pre,
                            sum)
FQ_Pre_Mean <- aggregate(weight~type+partnerType,
                             FQ_Pre,
                             mean)

conmatPlot = ggplot(FQ_Pre_Sum %>% filter(weight > 5)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

conmatPlot = ggplot(FQ_Pre_Mean) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

# Look at the correlations across input types
corrDat = spread(FQ_Pre_Mean,type,weight)
corrDat[is.na(corrDat)] <- 0
rownames(corrDat)<-corrDat$partnerType
corrDat$partnerType<-NULL
library(corrplot)
corrplot(cor(corrDat))
```

As above, for PFN outputs
```{r}
PFN_Post = getConnectionTable(getBodyIdsForList(c("PFN")),"POST","FB")
  
PFN_Post_Sum <- aggregate(weight~type+partnerType,
                            PFN_Post,
                            sum)
PFN_Post_Mean <- aggregate(weight~type+partnerType,
                             PFN_Post,
                             mean)

conmatPlot = ggplot(PFN_Post_Sum %>% filter(weight > 5)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

conmatPlot = ggplot(PFN_Post_Mean) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

# Look at the correlations across input types
corrDat = spread(PFN_Post_Mean,type,weight)
corrDat[is.na(corrDat)] <- 0
rownames(corrDat)<-corrDat$partnerType
corrDat$partnerType<-NULL
library(corrplot)
corrplot(cor(corrDat))
```


Find the shortest path between a given input and output neuron
```{r}
inNrons1 = inputTypes[17] %>% paste(".*",sep="") %>% neuprint_search()
outNrons1 = outputTypes[19] %>% paste(".*",sep="") %>% neuprint_search()

# Don't forget the min weight!!!
queryNow = "MATCH (a:`hemibrain_Neuron`{bodyId:" %>% paste0(inNrons1$bodyid[1]) %>% paste0("}), (b:`hemibrain_Neuron`{bodyId:") %>% paste0(outNrons1$bodyid[1]) %>% paste0("}), p = allShortestPaths((a)-[:ConnectsTo*]->(b)) WHERE ALL (x in relationships(p) WHERE x.weight >= 5 AND EXISTS(apoc.convert.fromJsonMap(x.roiInfo).FB)) RETURN length(p) AS `length(path)`, [n in nodes(p) | [n.bodyId, n.type]] AS path, [x in relationships(p) | x.weight] AS weights")

shortestPathQuery = neuprint_fetch_custom(cypher = queryNow)
```

Create a Sankey plot of the shortest pathways
```{r}


allNames = c()
for (path in 1:length(shortestPathQuery$data)){
  for (link in 1:(shortestPathQuery$data[[path]][[1]]+1)){
    allNames <- append(allNames,shortestPathQuery$data[[path]][[2]][[link]][[2]])
  }
}

allNames <- unique(allNames) %>% sort()

SPGroups = c(length(allNames))
for (nm in 1:length(allNames)){
  SPGroups[nm] <- "other"
  if (grepl("FB",allNames[nm])){
    SPGroups[nm] <- "FB"
  }
  if (grepl("Q",allNames[nm])){
    SPGroups[nm] <- "FB-Q"
  }
  if (grepl("PB",allNames[nm])){
    SPGroups[nm] <- "PB"
  }
  if (grepl("Delta",allNames[nm])){
    SPGroups[nm] <- "Delta"
  }
}

allPre = c()
allPost = c()
allWeights = c()
for (path in 1:length(shortestPathQuery$data)){
  for (link in 1:shortestPathQuery$data[[path]][[1]]){
    preID = which(allNames %in% shortestPathQuery$data[[path]][[2]][[link]][[2]])
    allPre <- append(allPre,preID-1)
    postID = which(allNames %in% shortestPathQuery$data[[path]][[2]][[link+1]][[2]])
    allPost <- append(allPost,postID-1)
    allWeights <- append(allWeights,shortestPathQuery$data[[path]][[3]][[link]])  }
}

SPNodes = data.frame(name = allNames, group = SPGroups )
SPLinks = data.frame(source = allPre, target = allPost, value = allWeights)

library(networkD3)

sankeyNetwork(Links = SPLinks, Nodes = SPNodes, Source = "source", Target = "target", Value = "value", NodeID = "name", NodeGroup = "group", units = "synapses", fontSize = 12, nodeWidth = 30)

```

Find the paths between two given neurons that are at most x steps long
```{r}
cxnThresh = 3

inNrons1 = inputTypes[17] %>% paste(".*",sep="") %>% neuprint_search()
outNrons1 = outputTypes[19] %>% paste(".*",sep="") %>% neuprint_search()

queryNow = "MATCH p = (src :`hemibrain_Neuron` { bodyId: 974627674 })-[:ConnectsTo*0..3]->(dest:`hemibrain_Neuron`{ bodyId: 757694775 }) WHERE ALL (x in relationships(p) WHERE x.weight >= 10 AND EXISTS(apoc.convert.fromJsonMap(x.roiInfo).FB)) RETURN length(p) AS `length(path)`, [n in nodes(p) | [n.bodyId, n.type]] AS path, [x in relationships(p) | x.weight] AS weights"

# )

pathsQuery = neuprint_fetch_custom(cypher = queryNow)
```

Create a Sankey plot of these connections grouped by type
```{r}
allNames = c()
for (path in 1:length(pathsQuery$data)){
  for (link in 1:(pathsQuery$data[[path]][[1]]+1)){
    allNames <- append(allNames,pathsQuery$data[[path]][[2]][[link]][[2]])
  }
}

allNames <- unique(allNames) %>% sort()

SPGroups = c(length(allNames))
for (nm in 1:length(allNames)){
  SPGroups[nm] <- "other"
  if (grepl("FB",allNames[nm])){
    SPGroups[nm] <- "FB"
  }
  if (grepl("Q",allNames[nm])){
    SPGroups[nm] <- "FB-Q"
  }
  if (grepl("PB",allNames[nm])){
    SPGroups[nm] <- "PB"
  }
  if (grepl("Delta",allNames[nm])){
    SPGroups[nm] <- "Delta"
  }
}

allPre = c()
allPost = c()
allWeights = c()
for (path in 1:length(pathsQuery$data)){
  for (link in 1:pathsQuery$data[[path]][[1]]){
    preID = which(allNames %in% pathsQuery$data[[path]][[2]][[link]][[2]])
    allPre <- append(allPre,preID-1)
    postID = which(allNames %in% pathsQuery$data[[path]][[2]][[link+1]][[2]])
    allPost <- append(allPost,postID-1)
    allWeights <- append(allWeights,pathsQuery$data[[path]][[3]][[link]])  }
}

SPNodes = data.frame(name = allNames, group = SPGroups )
SPLinks = data.frame(source = allPre, target = allPost, value = allWeights)

library(networkD3)

sankeyNetwork(Links = SPLinks, Nodes = SPNodes, Source = "source", Target = "target", Value = "value", NodeID = "name", NodeGroup = "group", units = "synapses", fontSize = 12, nodeWidth = 30)
```

Create a Sankey plot of these connections for each individual neuron
```{r}
allNames = c()
allBodyIds = c()

for (path in 1:length(pathsQuery$data)){
  for (link in 1:(pathsQuery$data[[path]][[1]]+1)){
    if (!(pathsQuery$data[[path]][[2]][[link]][[1]] %in% allBodyIds)){
        allNames <- append(allNames,pathsQuery$data[[path]][[2]][[link]][[2]])
        allBodyIds <- append(allBodyIds,pathsQuery$data[[path]][[2]][[link]][[1]])
      }
  }
}

SPGroups = c(length(allNames))
for (nm in 1:length(allNames)){
  SPGroups[nm] <- "other"
  if (grepl("FB",allNames[nm])){
    SPGroups[nm] <- "FB"
  }
  if (grepl("Q",allNames[nm])){
    SPGroups[nm] <- "FB-Q"
  }
  if (grepl("PB",allNames[nm])){
    SPGroups[nm] <- "PB"
  }
  if (grepl("Delta",allNames[nm])){
    SPGroups[nm] <- "Delta"
  }
}

allPre = c()
allPost = c()
allWeights = c()
for (path in 1:length(pathsQuery$data)){
  for (link in 1:pathsQuery$data[[path]][[1]]){
    preID = which(allBodyIds %in% pathsQuery$data[[path]][[2]][[link]][[1]])
    allPre <- append(allPre,preID-1)
    postID = which(allBodyIds %in% pathsQuery$data[[path]][[2]][[link+1]][[1]])
    allPost <- append(allPost,postID-1)
    allWeights <- append(allWeights,pathsQuery$data[[path]][[3]][[link]])  }
}

SPNodes = data.frame(name = allNames, group = SPGroups )
SPLinks = data.frame(source = allPre, target = allPost, value = allWeights)

library(networkD3)

sankeyNetwork(Links = SPLinks, Nodes = SPNodes, Source = "source", Target = "target", Value = "value", NodeID = "name", NodeGroup = "group", units = "synapses", fontSize = 12, nodeWidth = 30)
```




Pull out an example Delta6
```{r}
D6s = neuprint_search("Delta6C.*")
D6syns = neuprint_get_synapses(D6s$bodyid[[1]])
D6syns <-  D6syns %>% mutate(name="D6")%>%
  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))

ggplot(D6syns[which(D6syns$prepost == 1),]) + geom_point(aes(x,z,color= interaction(name,prepost))) +scale_color_brewer(palette="Set2")+coord_fixed(ratio = 1) + theme_void() + geom_point(data = D6syns[which(D6syns$prepost == 0),],aes(x,z,color= interaction(name,prepost))) +scale_color_brewer(palette="Set2")+coord_fixed(ratio = 1) + theme_void()

kmeanMat = D6syns[which(D6syns$prepost == 1),] %>% select(x,y,z)

maxClusts = 6
clustStats = data.frame(clustIDs = 1:maxClusts, tot.withinss = integer(maxClusts))
for (clust in 1:maxClusts){
  synClusts = kmeans(kmeanMat,clust, iter.max = 50, nstart = 10)
  clustStats$tot.withinss[clust] = synClusts$tot.withinss
}

ggplot(clustStats, aes(clustIDs, tot.withinss)) + geom_point() + ylim(0,5E9)

synClusts = kmeans(kmeanMat,3, iter.max = 50, nstart = 10)

ggplot(D6syns[which(D6syns$prepost == 1),], aes(x,z, color = as.factor(synClusts$cluster))) + geom_point()
```

