---
title: "FB explorations"
output: html_notebook
---

Load the libraries
```{r}
library(nat)
library(neuprintr)
library(tidyverse)
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\pathways.R")
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\visualizeConnectivityTables.R")
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\neuprintQueryUtils.R")
options(nat.plotengine = 'rgl')
```

Connect to neuprint
```{r}
neuprint_login()
```


Define the FB neuron types
```{r}
# Find the name of all neurons that get input in the FB
FBNronTypes = neuprint_find_neurons("FB")$bodytype %>% unique()
FBNronTypes <- FBNronTypes[which(!is.na(FBNronTypes))]
```

For each neuron type, find the number of inputs and outputs in or outside of the FB
```{r}
FBpreNpostRatios <- preNpostRatios(FBNronTypes,"FB")

# Look at the pre and post ratios and then cut those neurons with minimal innervations
ggplot(FBpreNpostRatios, aes(x=preRelative, y=postRelative,color=type)) + geom_point() + theme(legend.position="none")
FBpreNpostRatios <- FBpreNpostRatios[which(FBpreNpostRatios$preRelative > 0.2 | FBpreNpostRatios$postRelative > 0.15),]
ggplot(FBpreNpostRatios, aes(x=preRelative, y=postRelative,color=type)) + geom_point() + theme(legend.position="none")

FBpreNpostRatios <- FBpreNpostRatios[which(FBpreNpostRatios$regPr > 3 | FBpreNpostRatios$regPost > 3),]
FBpreNpostRatios <- FBpreNpostRatios[order(FBpreNpostRatios$prePostDiff),]

FBpreNpostRatios['classification'] = 'inner'
FBpreNpostRatios[which(FBpreNpostRatios$prePostDiff > 0.15),]$classification = 'input'
FBpreNpostRatios[which(FBpreNpostRatios$prePostDiff < -0.1),]$classification = 'output'
FBpreNpostRatios$classification <- factor(FBpreNpostRatios$classification, levels = c('input','inner','output'))

p <- ggplot(data = FBpreNpostRatios[which(!grepl("Delta",FBpreNpostRatios$type)),], aes()) + 
  geom_hline(yintercept = 0) +
  geom_point(aes(x= reorder(as.factor(type), -prePostRatio),
                 y=prePostDiff,
                 color=classification),
                 size = 3,
                 alpha = 0.2) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_color_manual(values = c('green','blue','red')) +
  xlab('neuron type') + ylab('pre ratio - post ratio')
print(p)

#ggsave("FBInputsAndOutputs.pdf", plot = last_plot(), device='pdf', 
#       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
#       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)

# Average the pre and post values within a given class
FBpreNpostDiffMean <- aggregate(prePostDiff~type,
                     FBpreNpostRatios,
                          mean)
colnames(FBpreNpostDiffMean)[2] <- "prePostDiffMean"
FBpreNpostDiffSd <- aggregate(prePostDiff~type,
                     FBpreNpostRatios,
                          sd)
colnames(FBpreNpostDiffSd)[2] <- "prePostDiffSd"
FBpreRelativeMean <- aggregate(preRelative~type,
                     FBpreNpostRatios,
                          mean)
colnames(FBpreRelativeMean)[2] <- "preRelativeMean"
FBpreRelativeSd <- aggregate(preRelative~type,
                     FBpreNpostRatios,
                          sd)
colnames(FBpreRelativeSd)[2] <- "preRelativeSd"
FBpostRelativeMean <- aggregate(postRelative~type,
                     FBpreNpostRatios,
                          mean)
colnames(FBpostRelativeMean)[2] <- "postRelativeMean"
FBpostRelativeSd <- aggregate(postRelative~type,
                     FBpreNpostRatios,
                          sd)
colnames(FBpostRelativeSd)[2] <- "postRelativeSd"
FBpreNpost <- Reduce(function(x, y) merge(x, y, all=TRUE), list(FBpreNpostDiffMean, FBpreNpostDiffSd,FBpreRelativeMean,FBpreRelativeSd,FBpostRelativeMean,FBpostRelativeSd))
FBpreNpost['classification'] = 'inner'
FBpreNpost[which(FBpreNpost$prePostDiffMean > 0.05),]$classification = 'input'
FBpreNpost[which(FBpreNpost$prePostDiffMean < -0.25),]$classification = 'output'
FBpreNpost$classification <- factor(FBpreNpost$classification, levels = c('input','inner','output'))
FBpreNpost <- FBpreNpost[order(FBpreNpost$prePostDiffMean),]

FBpreNpost$group = FBpreNpost$type %>% as.character()
FBpreNpost$group[which(grepl("FB",FBpreNpost$group))] <- "tangential"
FBpreNpost$group[which(grepl("SA3",FBpreNpost$group))] <- "tangential"
FBpreNpost$group[which(grepl("PF",FBpreNpost$group))] <- "PB-FB columnar"
FBpreNpost$group[which(grepl("Delta6",FBpreNpost$group))] <- "cross columnar within a layer"
FBpreNpost$group[which(grepl("Delta0",FBpreNpost$group))] <- "cross layer within a column"
FBpreNpost$group[which(grepl("FQ",FBpreNpost$group))] <- "columnar output"
FBpreNpost$group[which(grepl("ExR",FBpreNpost$group))] <- "other"
FBpreNpost$group[which(grepl("OA",FBpreNpost$group))] <- "other"
FBpreNpost$group <- as.factor(FBpreNpost$group)

rbow = rainbow(7)
cols <- c("input" = "red", "inner" = "blue", "output" = "darkgreen",
          "tangential" = rbow[7],"PB-FB columnar" = rbow[6],"cross columnar within a layer" = rbow[5],
          "cross layer within a column" = rbow[4],"columnar output" = rbow[3],"other" = rbow[1])
#plotOrd = as.factor(c("input","inner","outer",
#            "tangential","PB-FB columnar","cross columnar within a layer",
#            "cross layer within a column","columnar output","other"))
#FBpreNpost$type <- factor(FBpreNpost$type,levels = plotOrd)
#FBpreNpost$group <- factor(FBpreNpost$group,levels = plotOrd)

ggplot(FBpreNpost, aes(x=preRelativeMean, y=postRelativeMean)) +
  geom_point(size=3,aes(color=classification)) +
  geom_errorbar(aes(ymin=postRelativeMean-postRelativeSd, ymax=postRelativeMean+postRelativeSd,
                    color=classification),
                width=.02, position=position_dodge(0.05),alpha=0.4) +
  geom_errorbarh(aes(xmin=preRelativeMean-preRelativeSd, xmax=preRelativeMean+preRelativeSd,
                     color=classification),
                height=.02, position=position_dodge(0.05),alpha=0.4) +
  geom_text(aes(label=type,color =group,alpha=0.5),hjust=-0.2, vjust=-0.2,size = 3,show.legend = FALSE) +
  theme_classic() + xlab('pre ratio') + ylab('post ratio') + 
  coord_fixed(ratio =1 ,xlim=c(0, 1.1),ylim=c(0, 1.1),expand=FALSE)  + 
  geom_abline(intercept = 0, slope = 1, color="black", linetype="dashed", size=1) +
  theme(panel.grid.major = element_line(colour = "gray",linetype="dashed"),text=element_text(size=18)) +
  scale_color_manual(values = cols,breaks=c("input","inner","output",
                                            "tangential","PB-FB columnar","cross columnar within a layer",
                                            "cross layer within a column","columnar output","other"))

ggsave("FBInputsAndOutputsMean2D.svg", plot = last_plot(), device='svg', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)


for (tp in 1:4){
  if (tp == 1){
    datNow = FBpreNpost[which(grepl("PF",FBpreNpost$type)),]
    saveName = "FBInputsAndOutputs_PF.pdf"
    w = 20
    h = 15
  }
  if (tp == 2){
    datNow = FBpreNpost[which(grepl("FQ",FBpreNpost$type)),]
    saveName = "FBInputsAndOutputs_FQ.pdf"
    w = 20
    h = 15
  }
  if (tp == 3){
    datNow = FBpreNpost[which(grepl("FB",FBpreNpost$type)),]
    saveName = "FBInputsAndOutputs_FB.pdf"
    w = 40
    h = 5
  }
  if (tp == 4) {
    datNow = FBpreNpost[which(grepl("ExR",FBpreNpost$type) | grepl("OA",FBpreNpost$type)),]
    datNow <- datNow[which(datNow$type != "ExR8"),]
    saveName = "FBInputsAndOutputs_other.pdf"
    w = 20
    h = 15
  }
  
  dodge <- position_dodge(width = 0.9)
  limits <- aes(ymax = datNow$prePostDiffMean + datNow$prePostDiffSd,
                ymin = datNow$prePostDiffMean - datNow$prePostDiffSd)

  p2 <- ggplot(data = datNow, aes(x = reorder(as.factor(type), -prePostDiffMean), y = prePostDiffMean, fill = classification))
  p2 <- p2 +
    geom_hline(yintercept = 0) +
    geom_bar(stat = "identity", position = dodge) +
    geom_errorbar(limits, position = dodge, width = 0.25) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1),text = element_text(size=18)) +
    xlab('neuron type') + ylab('pre ratio - post ratio')
  
  p2 <- p2 + scale_fill_manual(values = c('forestgreen','blue','red2'))
  print(p2)
  
  ggsave(saveName, plot = last_plot(), device='pdf', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
       scale = 1.5, width = w, height = h, units ="cm", dpi = 600, limitsize = TRUE)
}
```

Look at who FB-Q's output to
```{r}
FQTypes = neuprint_search('FQ.*')$type %>% unique() 
FQ_Post = getConnectionTable(getBodyIdsForList(c("FQ")),"POST","CRE(R)")
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","CRE(L)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SMP(R)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SMP(L)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SIP(R)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SIP(L)"))
FQ_Post <- rbind(FQ_Post,getConnectionTable(getBodyIdsForList(c("FQ")),"POST","SLP(R)"))

for (tp in 1:length(FQTypes)){
  
  FQ_Post_Sum <- aggregate(weight~type+partnerType,
                              FQ_Post[which(FQ_Post$type==FQTypes[tp]),],
                              sum)
  FQ_Post_Mean <- aggregate(weight~type+partnerType,
                               FQ_Post[which(FQ_Post$type==FQTypes[tp]),],
                               mean)

  conmatPlot = ggplot(FQ_Post_Sum %>% filter(weight > 5)) + 
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
    geom_tile(aes(type,partnerType,fill=weight))
  print(conmatPlot)
  
  conmatPlot = ggplot(FQ_Post_Mean) + 
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
    geom_tile(aes(type,partnerType,fill=weight))
  print(conmatPlot)
    
}
```

Look at who PFR_b's output to
```{r}
PFRbs_Post <- getConnectionTable(getBodyIdsForList(c("PFR_b")),"POST","CRE(R)")

plotConnectivityMatrix(PFRbs_Post, synapseCutOff = 3, 1)

```

Show connections between those inputs and outputs
```{r}
PFNs_Post <- getConnectionTable(getBodyIdsForList(c("PFN")),"POST","FB")
conmatPlot = ggplot(PFNs_Post   %>% filter(weight > 3)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)
```

Look at inputs to PFL1,2,3s, group by type, calculate correlation
```{r}
PFL_Pre = getConnectionTable(getBodyIdsForList(c("PFL")),"PRE","FB")
  
PFL_Pre_Sum <- aggregate(weight~type+partnerType,
                            PFL_Pre,
                            sum)
PFL_Pre_Mean <- aggregate(weight~type+partnerType,
                             PFL_Pre,
                             mean)

conmatPlot = ggplot(PFL_Pre_Sum %>% filter(weight > 5)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

conmatPlot = ggplot(PFL_Pre_Mean) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

# Look at the correlations across input types
corrDat = spread(PFL_Pre_Mean,type,weight)
corrDat[is.na(corrDat)] <- 0
rownames(corrDat)<-corrDat$partnerType
corrDat$partnerType<-NULL
library(corrplot)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\CorrelationBetweenPFLInputs.pdf", width = 20, height = 15)
corrplot(cor(corrDat))
dev.off()

   
```

As above but for FQs
```{r}
FQ_Pre = getConnectionTable(getBodyIdsForList(c("FQ","PFR")),"PRE","FB")
  
FQ_Pre_Sum <- aggregate(weight~type+partnerType,
                            FQ_Pre,
                            sum)
FQ_Pre_Mean <- aggregate(weight~type+partnerType,
                             FQ_Pre,
                             mean)

conmatPlot = ggplot(FQ_Pre_Sum %>% filter(weight > 5)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

conmatPlot = ggplot(FQ_Pre_Mean) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

# Look at the correlations across input types
corrDat = spread(FQ_Pre_Mean,type,weight)
corrDat[is.na(corrDat)] <- 0
rownames(corrDat)<-corrDat$partnerType
corrDat$partnerType<-NULL
library(corrplot)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\CorrelationBetweenFQInputs.pdf", width = 20, height = 15)
corrplot(cor(corrDat))
dev.off()
 
```

As above, for PFN outputs
```{r}
PFN_Post = getConnectionTable(getBodyIdsForList(c("PFN")),"POST","FB")
  
PFN_Post_Sum <- aggregate(weight~type+partnerType,
                            PFN_Post,
                            sum)
PFN_Post_Mean <- aggregate(weight~type+partnerType,
                             PFN_Post,
                             mean)

conmatPlot = ggplot(PFN_Post_Sum %>% filter(weight > 5)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

conmatPlot = ggplot(PFN_Post_Mean) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

# Look at the correlations across input types
corrDat = spread(PFN_Post_Mean,type,weight)
corrDat[is.na(corrDat)] <- 0
rownames(corrDat)<-corrDat$partnerType
corrDat$partnerType<-NULL
library(corrplot)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\CorrelationBetweenPFNOutputs.pdf", width = 20, height = 15)
corrplot(cor(corrDat))
dev.off()

```

Plot graph of Delta<->Delta connections
```{r}
preNeuron = c("Delta")
postNeuron = c("Delta")
slctROI = "FB"

# Get connectivity table
preIDs = getBodyIdsForList(preNeuron)
postIDs = getBodyIdsForList(postNeuron)
myConnections = getConnectionTable_forSubset(preIDs$bodyid,postIDs$bodyid, slctROI)

require(igraph)
# Reroganize to make graph with types instead of bodyids
graphData = data.frame(from = myConnections$partnerType, to = myConnections$type, weight = myConnections$weight)
graphData = graphData %>% group_by(from, to) %>% summarise(weight = mean(weight, na.rm = TRUE)) %>% ungroup()

# Cutoff low synapse counts (and compare connections before and after)
hist(graphData$weight, n=100)
cutoff = 2
graphData = graphData %>% filter(weight > cutoff)
hist(graphData$weight, n=100)

# Separate connections within a type and across types
graphData_noSelf = graphData %>% filter(as.character(from) != as.character(to))
graphData_toSelf = graphData %>% filter(as.character(from) == as.character(to))

# Pull out the nodes of the graph
nodes  = union(unique(graphData_noSelf$from), unique(graphData_noSelf$to))

# Process self connections (will serve as size of circles in plot)
graphData_selfFB = full_join(data.frame("from" = graphData_toSelf$from, "weight" = graphData_toSelf$weight), data.frame("from" = nodes))
graphData_selfFB$weight[is.na(graphData_selfFB$weight)] <- 0

# Create a graph object from the connections across types
connectGraph = graph_from_data_frame(graphData_noSelf)
connectGraph <- delete_edges(connectGraph, E(connectGraph)[weight<cutoff])
connectGraph

# Assign colors to the nodes from the lookup table
nodeCols = seq(1, length(nodes))
for (i in seq(1, length(simpleTypesNodes))) {
  nodeCols[i] = colors()[colorValueLookup$col[colorValueLookup$type == nodes[i]]]
}

# Make labels for the nodes in the graph
V(connectGraph)$label.color="black"
V(connectGraph)$label.cex=0.8
V(connectGraph)$label.dist=0

# Make the size of each node correspond to the number of self connections
V(connectGraph)$size = 7 + as.numeric(7*graphData_selfFB$weight/max(c(1, max(graphData_selfFB$weight) ) ) )
V(connectGraph)$vertex.frame.color="gray"
V(connectGraph)$color=nodeCols

# Set edge width based on weight:
E(connectGraph)$width <- E(connectGraph)$weight/5.
#change arrow size and edge color:
E(connectGraph)$arrow.size <- 1
#E(connectGraph)$edge.color <- "gray80"
edge.start <- ends(connectGraph, es=E(connectGraph), names=F)[,1]
edge.col = V(connectGraph)$color[edge.start]

l <- layout_with_fr(connectGraph) # layout_components

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\DeltaNetwork.pdf", width = 10, height = 10)#, units ="cm", dpi = 600)
plot(connectGraph,edge.color=edge.col, edge.curved=0.5, layout=l)  #vertex.shape="fcircle", 

```

Look at Delta6B inputs
```{r}
D6B_Pre <- getConnectionTable(getBodyIdsForList(c("Delta6B")),"PRE","FB")
D6B_Pre <- 
p <- connectivityBarPlot(D6B_Pre,"PRE") + ggtitle("Delta6B inputs")
print(p)
ggsave("Delta6BInputs.pdf", plot = last_plot(), device='pdf', 
       path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
       scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)
```

Look at primary outputs of PFNs
```{r}

for (pfn in 1:8){
  if (pfn == 1)
    typeNow = "PFNa"
  if (pfn == 2)
    typeNow = "PFNp_c"
  if (pfn == 3)
    typeNow = "PFNm_a"
  if (pfn == 4)
    typeNow = "PFNp_a"
  if (pfn == 5)
    typeNow = "PFNd"
  if (pfn == 6)
    typeNow = "PFNm_b"
  if (pfn == 7)
    typeNow = "PFNp_b"
  if (pfn == 8)
    typeNow = "PFNv"
  
  bodyIDs = neuprint_search(paste0(typeNow,'.*'),field='type')
  
  PF_Post <- getConnectionTable(bodyIDs,"POST","FB")
  PF_Post <- PF_Post[which(PF_Post$weight>4),]
  p <- connectivityBarPlot(PF_Post,"POST") + ggtitle(paste(typeNow,"outputs",sep=' ')) + ylim(0,80)
  print(p)
  ggsave(paste(typeNow,"Outputs.pdf",sep='_'), plot = last_plot(), device='pdf', 
         path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
         scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)
}

```

Look at primary inputs onto PFLs
```{r}

for (pfn in 1:3){
  if (pfn == 1)
    typeNow = "PFL1"
  if (pfn == 2)
    typeNow = "PFL2"
  if (pfn == 3)
    typeNow = "PFL3"
  
  bodyIDs = neuprint_search(paste0(typeNow,'.*'),field='type')
  
  PF_Post <- getConnectionTable(bodyIDs,"PRE","FB")
  PF_Post <- PF_Post[which(PF_Post$weight>4),]
  p <- connectivityBarPlot(PF_Post,"POST") + ggtitle(paste(typeNow,"inputs",sep=' ')) + ylim(0,100)
  print(p)
  ggsave(paste(typeNow,"Inputs.pdf",sep='_'), plot = last_plot(), device='pdf', 
         path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
         scale = 1.5, width = 20, height = 15, units ="cm", dpi = 600, limitsize = TRUE)
}

```

Look at the correlation between the different PF types outputs
```{r}
FQ_Post = getConnectionTable(getBodyIdsForList(c("PF")),"POST","FB")
FQ_Post <- FQ_Post[which(!grepl("PFL",FQ_Post$type) & !grepl("PFR_b",FQ_Post$type)),]

FQ_Post_Sum <- aggregate(weight~type+partnerType,
                            FQ_Post,
                            sum)
FQ_Post_Mean <- aggregate(weight~type+partnerType,
                             FQ_Post,
                             mean)

conmatPlot = ggplot(FQ_Post_Sum %>% filter(weight > 5)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,100)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

conmatPlot = ggplot(FQ_Post_Mean) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="ivory", mid="peachpuff", high="black", limits=c(0,20)) +
  geom_tile(aes(type,partnerType,fill=weight))
print(conmatPlot)

# Look at the correlations across input types
corrDat = spread(FQ_Post_Mean,type,weight)
corrDat[is.na(corrDat)] <- 0
rownames(corrDat)<-corrDat$partnerType
corrDat$partnerType<-NULL
library(corrplot)
pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\CorrelationBetweenPFOutputs.pdf", width = 20, height = 15)
corrplot(cor(corrDat))
dev.off()
 
```

Find the shortest path between a given input and output neuron
```{r}
inNrons1 = inputTypes[17] %>% paste(".*",sep="") %>% neuprint_search()
outNrons1 = outputTypes[19] %>% paste(".*",sep="") %>% neuprint_search()

# Don't forget the min weight!!!
queryNow = "MATCH (a:`hemibrain_Neuron`{bodyId:" %>% paste0(inNrons1$bodyid[1]) %>% paste0("}), (b:`hemibrain_Neuron`{bodyId:") %>% paste0(outNrons1$bodyid[1]) %>% paste0("}), p = allShortestPaths((a)-[:ConnectsTo*]->(b)) WHERE ALL (x in relationships(p) WHERE x.weight >= 5 AND EXISTS(apoc.convert.fromJsonMap(x.roiInfo).FB)) RETURN length(p) AS `length(path)`, [n in nodes(p) | [n.bodyId, n.type]] AS path, [x in relationships(p) | x.weight] AS weights")

shortestPathQuery = neuprint_fetch_custom(cypher = queryNow)
```

Create a Sankey plot of the shortest pathways
```{r}


allNames = c()
for (path in 1:length(shortestPathQuery$data)){
  for (link in 1:(shortestPathQuery$data[[path]][[1]]+1)){
    allNames <- append(allNames,shortestPathQuery$data[[path]][[2]][[link]][[2]])
  }
}

allNames <- unique(allNames) %>% sort()

SPGroups = c(length(allNames))
for (nm in 1:length(allNames)){
  SPGroups[nm] <- "other"
  if (grepl("FB",allNames[nm])){
    SPGroups[nm] <- "FB"
  }
  if (grepl("Q",allNames[nm])){
    SPGroups[nm] <- "FB-Q"
  }
  if (grepl("PB",allNames[nm])){
    SPGroups[nm] <- "PB"
  }
  if (grepl("Delta",allNames[nm])){
    SPGroups[nm] <- "Delta"
  }
}

allPre = c()
allPost = c()
allWeights = c()
for (path in 1:length(shortestPathQuery$data)){
  for (link in 1:shortestPathQuery$data[[path]][[1]]){
    preID = which(allNames %in% shortestPathQuery$data[[path]][[2]][[link]][[2]])
    allPre <- append(allPre,preID-1)
    postID = which(allNames %in% shortestPathQuery$data[[path]][[2]][[link+1]][[2]])
    allPost <- append(allPost,postID-1)
    allWeights <- append(allWeights,shortestPathQuery$data[[path]][[3]][[link]])  }
}

SPNodes = data.frame(name = allNames, group = SPGroups )
SPLinks = data.frame(source = allPre, target = allPost, value = allWeights)

library(networkD3)

sankeyNetwork(Links = SPLinks, Nodes = SPNodes, Source = "source", Target = "target", Value = "value", NodeID = "name", NodeGroup = "group", units = "synapses", fontSize = 12, nodeWidth = 30)

```

Find the paths between two given neurons that are at most x steps long
```{r}
cxnThresh = 3

inNrons1 = inputTypes[17] %>% paste(".*",sep="") %>% neuprint_search()
outNrons1 = outputTypes[19] %>% paste(".*",sep="") %>% neuprint_search()

queryNow = "MATCH p = (src :`hemibrain_Neuron` { bodyId: 974627674 })-[:ConnectsTo*0..3]->(dest:`hemibrain_Neuron`{ bodyId: 757694775 }) WHERE ALL (x in relationships(p) WHERE x.weight >= 10 AND EXISTS(apoc.convert.fromJsonMap(x.roiInfo).FB)) RETURN length(p) AS `length(path)`, [n in nodes(p) | [n.bodyId, n.type]] AS path, [x in relationships(p) | x.weight] AS weights"

# )

pathsQuery = neuprint_fetch_custom(cypher = queryNow)
```

Create a Sankey plot of these connections grouped by type
```{r}
allNames = c()
for (path in 1:length(pathsQuery$data)){
  for (link in 1:(pathsQuery$data[[path]][[1]]+1)){
    allNames <- append(allNames,pathsQuery$data[[path]][[2]][[link]][[2]])
  }
}

allNames <- unique(allNames) %>% sort()

SPGroups = c(length(allNames))
for (nm in 1:length(allNames)){
  SPGroups[nm] <- "other"
  if (grepl("FB",allNames[nm])){
    SPGroups[nm] <- "FB"
  }
  if (grepl("Q",allNames[nm])){
    SPGroups[nm] <- "FB-Q"
  }
  if (grepl("PB",allNames[nm])){
    SPGroups[nm] <- "PB"
  }
  if (grepl("Delta",allNames[nm])){
    SPGroups[nm] <- "Delta"
  }
}

allPre = c()
allPost = c()
allWeights = c()
for (path in 1:length(pathsQuery$data)){
  for (link in 1:pathsQuery$data[[path]][[1]]){
    preID = which(allNames %in% pathsQuery$data[[path]][[2]][[link]][[2]])
    allPre <- append(allPre,preID-1)
    postID = which(allNames %in% pathsQuery$data[[path]][[2]][[link+1]][[2]])
    allPost <- append(allPost,postID-1)
    allWeights <- append(allWeights,pathsQuery$data[[path]][[3]][[link]])  }
}

SPNodes = data.frame(name = allNames, group = SPGroups )
SPLinks = data.frame(source = allPre, target = allPost, value = allWeights)

library(networkD3)

sankeyNetwork(Links = SPLinks, Nodes = SPNodes, Source = "source", Target = "target", Value = "value", NodeID = "name", NodeGroup = "group", units = "synapses", fontSize = 12, nodeWidth = 30)
```

Create a Sankey plot of these connections for each individual neuron
```{r}
allNames = c()
allBodyIds = c()

for (path in 1:length(pathsQuery$data)){
  for (link in 1:(pathsQuery$data[[path]][[1]]+1)){
    if (!(pathsQuery$data[[path]][[2]][[link]][[1]] %in% allBodyIds)){
        allNames <- append(allNames,pathsQuery$data[[path]][[2]][[link]][[2]])
        allBodyIds <- append(allBodyIds,pathsQuery$data[[path]][[2]][[link]][[1]])
      }
  }
}

SPGroups = c(length(allNames))
for (nm in 1:length(allNames)){
  SPGroups[nm] <- "other"
  if (grepl("FB",allNames[nm])){
    SPGroups[nm] <- "FB"
  }
  if (grepl("Q",allNames[nm])){
    SPGroups[nm] <- "FB-Q"
  }
  if (grepl("PB",allNames[nm])){
    SPGroups[nm] <- "PB"
  }
  if (grepl("Delta",allNames[nm])){
    SPGroups[nm] <- "Delta"
  }
}

allPre = c()
allPost = c()
allWeights = c()
for (path in 1:length(pathsQuery$data)){
  for (link in 1:pathsQuery$data[[path]][[1]]){
    preID = which(allBodyIds %in% pathsQuery$data[[path]][[2]][[link]][[1]])
    allPre <- append(allPre,preID-1)
    postID = which(allBodyIds %in% pathsQuery$data[[path]][[2]][[link+1]][[1]])
    allPost <- append(allPost,postID-1)
    allWeights <- append(allWeights,pathsQuery$data[[path]][[3]][[link]])  }
}

SPNodes = data.frame(name = allNames, group = SPGroups )
SPLinks = data.frame(source = allPre, target = allPost, value = allWeights)

library(networkD3)

sankeyNetwork(Links = SPLinks, Nodes = SPNodes, Source = "source", Target = "target", Value = "value", NodeID = "name", NodeGroup = "group", units = "synapses", fontSize = 12, nodeWidth = 30)
```


Pull out an example Delta6
```{r}
D6s = neuprint_search("Delta6C.*")
D6syns = neuprint_get_synapses(D6s$bodyid[[1]])
D6syns <-  D6syns %>% mutate(name="D6")%>%
  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))

ggplot(D6syns[which(D6syns$prepost == 1),]) + geom_point(aes(x,z,color= interaction(name,prepost))) +scale_color_brewer(palette="Set2")+coord_fixed(ratio = 1) + theme_void() + geom_point(data = D6syns[which(D6syns$prepost == 0),],aes(x,z,color= interaction(name,prepost))) +scale_color_brewer(palette="Set2")+coord_fixed(ratio = 1) + theme_void()

kmeanMat = D6syns[which(D6syns$prepost == 1),] %>% select(x,y,z)

maxClusts = 6
clustStats = data.frame(clustIDs = 1:maxClusts, tot.withinss = integer(maxClusts))
for (clust in 1:maxClusts){
  synClusts = kmeans(kmeanMat,clust, iter.max = 50, nstart = 10)
  clustStats$tot.withinss[clust] = synClusts$tot.withinss
}

ggplot(clustStats, aes(clustIDs, tot.withinss)) + geom_point() + ylim(0,5E9)

synClusts = kmeans(kmeanMat,3, iter.max = 50, nstart = 10)

ggplot(D6syns[which(D6syns$prepost == 1),], aes(x,z, color = as.factor(synClusts$cluster))) + geom_point()
```


```{r}
preSynFBPlot <- function(type,prePost){
  # Load the reshape library 
  library(reshape2)
  
  # Specify the number of bins to use
  nbins <- 100
  
  # Pull the FB mesh
  FB_Mesh = neuprint_ROI_mesh("FB")
  FB_xyz = data.frame(x = FB_Mesh$vb[1,], y = FB_Mesh$vb[2,], z = FB_Mesh$vb[3,])
  
  # Get the x and z bins
  x.bin <- seq(floor(min(FB_xyz$x)), ceiling(max(FB_xyz$x)), length=nbins)
  z.bin <- seq(floor(min(FB_xyz$z)), ceiling(max(FB_xyz$z)), length=nbins)
  
  # Create a 2D histogram of the FB points
  FBfreq <-  melt(table(findInterval(FB_xyz$x, x.bin),findInterval(FB_xyz$z, z.bin)))
  FBfreq2D <- diag(nbins)*0
  FBfreq2D[cbind(FBfreq[,1], FBfreq[,2])] <- FBfreq[,3]
  dimnames(FBfreq2D) <- list(x.bin, z.bin)
  FBhist.melt <- melt(FBfreq2D)
  names(FBhist.melt) <- c("x", "z", "numPts")
  
  # Make a binary mask out of the FB points
  FBhist.melt[which(FBhist.melt$numPts>=0.1),]$numPts <- 0.1
  FBhist.melt[which(FBhist.melt$numPts<0.1),]$numPts <- 0
  FBhist.melt <- FBhist.melt[which(FBhist.melt$numPts>0),]
  
  # Get the body ids
  bodyIds = neuprint_search(paste0(type,".*"))$bodyid
  
  # Assign a color map given the number of synapsese
  cMap = c("#000000FF")
  cMap = append(cMap,rainbow(length(bodyIds)))
  
  # Create a plot with the FB outline
  p1 <- ggplot() + geom_tile(data = FBhist.melt, aes(x = x,y = z, fill = numPts))
  for (bid in 1:length(bodyIds)){
    
    # Pull the individual PFL synapses
    syns = neuprint_get_synapses(bodyIds[bid], roi="FB")
    if (grepl("PRE",prePost))
      syns <-  syns[which(syns$prepost == 0),]
    else
      syns <- syns[which(syns$prepost == 1),]
    if (nrow(syns)==0)
      next
    syns <- syns %>% mutate(name=as.character(type))%>%  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
     
    # Create a 2D histogram of the synapses
    freq <-  melt(table(findInterval(syns$x, x.bin),findInterval(syns$z, z.bin)))
    freq2D <- diag(nbins)*0
    freq2D[cbind(freq[,1], freq[,2])] <- freq[,3]
    dimnames(freq2D) <- list(x.bin, z.bin)
    hist.melt <- melt(freq2D)
    names(hist.melt) <- c("xPos", "zPos", "numSyns")
    
    # Make a binary mask out of the synapses
    hist.melt[which(hist.melt$numSyns>=0.1),]$numSyns <- bid+1
    hist.melt[which(hist.melt$numSyns<0.1),]$numSyns <- 0
    
    hist.melt$bodyid = bodyIds[bid]

    #p1 <- p1 + geom_contour(data=hist.melt, aes(x = xPos,y = zPos,z = numSyns,color=bodyid),bins=1)
    hist.melt <- hist.melt[which(hist.melt$numSyns>0),]
    p1 <- p1 + geom_tile(data=hist.melt,aes(x=xPos,y=zPos,fill=numSyns,alpha=0.25))
    
  }
  p1 <- p1 + coord_fixed(ratio = 1) + theme_void() +
    scale_x_reverse() + scale_y_reverse() +
    scale_fill_gradientn(colors=cMap) + theme(legend.position="none")
  if (grepl("PRE",prePost))
    p1 <-  p1 + ggtitle(paste0(as.character(type),": outputs (n=",length(bodyIds),")")) 
  else
    p1 <-  p1 + ggtitle(paste0(as.character(type),": inputs (n=",length(bodyIds),")")) 
  
  return(p1)
}
```


```{r}
plotAndSaveSynDistrosFB <- function(typeRoot,prePost){
  allNrons = neuprint_search(paste0(typeRoot,".*"))
  types = unique(allNrons$type)
  plot_list = list()
  for (t in 1:length(types)){
    if (is.na(types[t])) {
      next
    }
    p <- preSynFBPlot(types[t],prePost)
    plot_list[[t]] = p
  }
  return(plot_list)
}

```

```{r}
library(gridExtra)

# PFNs
pPFN_Pre <- plotAndSaveSynDistrosFB("PFN","PRE")
pPFN_Post <- plotAndSaveSynDistrosFB("PFN","POST")

# PFRs
pPFR_Pre <- plotAndSaveSynDistrosFB("PFR","PRE")
pPFR_Post <- plotAndSaveSynDistrosFB("PFR","POST")

# PFGs
pPFG_Pre <- plotAndSaveSynDistrosFB("PFG","PRE")
pPFG_Post <- plotAndSaveSynDistrosFB("PFG","POST")

# PFLs
pPFL_Pre <- plotAndSaveSynDistrosFB("PFL","PRE")
pPFL_Post <- plotAndSaveSynDistrosFB("PFL","POST")

gPF1 = do.call("grid.arrange", c(c(pPFN_Post[1:4]), ncol=4))
gPF2 = do.call("grid.arrange", c(c(pPFN_Pre[1:4]), ncol=4))
gPF3 = do.call("grid.arrange", c(c(pPFN_Post[5:8]), ncol=4))
gPF4 = do.call("grid.arrange", c(c(pPFN_Pre[5:8]), ncol=4))
gPF5 = do.call("grid.arrange", c(c(pPFG_Post,pPFR_Post), ncol=4))
gPF6 = do.call("grid.arrange", c(c(pPFG_Pre,pPFR_Pre), ncol=4))
gPF7 = do.call("grid.arrange", c(c(pPFL_Post), ncol=4))
gPF <-grid.arrange(gPF1,gPF2,gPF3,gPF4,gPF5,gPF6,gPF7,ncol=1) 
ggsave(paste0("PFSynapses.pdf"), gPF, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)


# PFQs
pFQ_Pre <- plotAndSaveSynDistrosFB("FQ","PRE")
pFQ_Post <- plotAndSaveSynDistrosFB("FQ","POST")

gFQ1 = do.call("grid.arrange", c(c(pFQ_Post[1:5]), ncol=5))
gFQ2 = do.call("grid.arrange", c(c(pFQ_Pre[1:5]), ncol=5))
gFQ3 = do.call("grid.arrange", c(c(pFQ_Post[6:10]), ncol=5))
gFQ4 = do.call("grid.arrange", c(c(pFQ_Pre[6:10]), ncol=5))
gFQ5 = do.call("grid.arrange", c(c(pFQ_Post[11:15]), ncol=5))
gFQ6 = do.call("grid.arrange", c(c(pFQ_Pre[11:15]), ncol=5))
gFQ7 = do.call("grid.arrange", c(c(pFQ_Post[16:20]), ncol=5))
gFQ8 = do.call("grid.arrange", c(c(pFQ_Pre[16:20]), ncol=5))
gFQ <-grid.arrange(gFQ1,gFQ2,gFQ3,gFQ4,gFQ5,gFQ6,gFQ7,gFQ8,ncol=1) 
ggsave(paste0("FQSynapses.pdf"), gFQ, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)


# Delta 0s
Delta0_Pre <- plotAndSaveSynDistrosFB("Delta0","PRE")
Delta0_Post <- plotAndSaveSynDistrosFB("Delta0","POST")

gD01 = do.call("grid.arrange", c(c(Delta0_Post[1:4]), ncol=4))
gD02 = do.call("grid.arrange", c(c(Delta0_Pre[1:4]), ncol=4))
gD03 = do.call("grid.arrange", c(c(Delta0_Post[5:8]), ncol=4))
gD04 = do.call("grid.arrange", c(c(Delta0_Pre[5:8]), ncol=4))
gD05 = do.call("grid.arrange", c(c(Delta0_Post[9:12]), ncol=4))
gD06 = do.call("grid.arrange", c(c(Delta0_Pre[9:12]), ncol=4))
gD07 = do.call("grid.arrange", c(c(Delta0_Post[13:16]), ncol=4))
gD08 = do.call("grid.arrange", c(c(Delta0_Pre[13:16]), ncol=4))
gD0 <-grid.arrange(gD01,gD02,gD03,gD04,gD05,gD06,gD07,gD08,ncol=1) 
ggsave(paste0("Delta0Synapses.pdf"), gD0, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)


# Delta 6s
Delta6_Pre <- plotAndSaveSynDistrosFB("Delta6","PRE")
Delta6_Post <- plotAndSaveSynDistrosFB("Delta6","POST")

gD61 = do.call("grid.arrange", c(c(Delta6_Post[1:4]), ncol=4))
gD62 = do.call("grid.arrange", c(c(Delta6_Pre[1:4]), ncol=4))
gD63 = do.call("grid.arrange", c(c(Delta6_Post[5:8]), ncol=4))
gD64 = do.call("grid.arrange", c(c(Delta6_Pre[5:8]), ncol=4))
gD65 = do.call("grid.arrange", c(c(Delta6_Post[9:12]), ncol=4))
gD66 = do.call("grid.arrange", c(c(Delta6_Pre[9:12]), ncol=4))
gD67 = do.call("grid.arrange", c(c(Delta6_Post[13]), ncol=4))
gD68 = do.call("grid.arrange", c(c(Delta6_Pre[13]), ncol=4))
gD6 <-grid.arrange(gD61,gD62,gD63,gD64,gD65,gD66,gD67,gD68,ncol=1) 
ggsave(paste0("Delta6Synapses.pdf"), gD6, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
```

Plot histograms of inputs and outputs of a set of types by layer
```{r}
FBLayerHist <- function(types,legOff,yl){
  
  library(gridExtra)
  
  ROIs = neuprint_ROIs()
  ROIs <- ROIs[which(grepl("FB",ROIs) & (ROIs!="FB"))]
  
  plot_list = list()
  for (pp in 1:2){
    if (pp == 1)
      prePost = "PRE"
    else
      prePost = "POST"
    
    FBSyns = neuprint_connection_table(
      getBodyIdsForList(types),
      prepost=prePost,by.roi=TRUE)
    
    FBSyns <- FBSyns[FBSyns$roi %in% ROIs,]
    FBSyns <- FBSyns %>% mutate(type = neuprint_get_meta(bodyid)$type, 
                                    partnerType = neuprint_get_meta(partner)$type)
    emptyROIs = ROIs[which(!(ROIs %in% unique(FBSyns$roi)))]
    if (length(emptyROIs)>0){
      for (eR in 1:length(emptyROIs)){
        dfTmp = data.frame(bodyid  = 0, partner = 0, prepost = pp-1,
                           roi = emptyROIs[eR],
                           ROIweight = 0, weight = 0, type = NA, partnerType = NA)
        FBSyns <- rbind(FBSyns,dfTmp)
      }
    }
  
    p <- ggplot(FBSyns,aes(x=roi,y=ROIweight,fill=factor(type))) + geom_bar(stat="identity") +
      ggtitle(paste(paste(types, collapse = ','),prePost,sep="-")) + coord_flip() + ylim(0, yl) +
      theme_classic() + theme(panel.grid.major = element_line(colour = "gray",linetype="dashed"))
    if ((legOff == 1) | (pp == 2))
      p <- p + theme(legend.position="none")
    
    plot_list[[pp]] = p
  }
  g = do.call("grid.arrange", c(c(plot_list), nrow=2))
  return(g)
}

```

Show the pre and post synaptic layer synapse counts for the columnar neurons
```{r}
yl = 100000
gPFN = FBLayerHist("PFN",0,yl)
ggsave(paste0("PFNSynsByLayer.pdf"), gPFN, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 10, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
gPFOther = FBLayerHist(c("PFR","PFG"),0,yl)
ggsave(paste0("PFOtherSynsByLayer.pdf"), gPFOther, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\Overview\\",
   scale = 1.5, width = 10, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
gPFL = FBLayerHist("PFL",0,yl)
ggsave(paste0("PFLSynsByLayer.pdf"), gPFL, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 10, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
gFQ = FBLayerHist("FQ",0,yl)
ggsave(paste0("FQSynsByLayer.pdf"), gFQ, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 10, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
gD0 = FBLayerHist("Delta0",0,yl)
ggsave(paste0("Delta0SynsByLayer.pdf"), gD0, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 10, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
gD6 = FBLayerHist("Delta6",0,yl)
ggsave(paste0("Delta6SynsByLayer.pdf"), gD6, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\SynapseDistributions\\",
   scale = 1.5, width = 10, height = 15, units ="cm", dpi = 72, limitsize = TRUE)


gAll <-grid.arrange(gPFN,gD6,gD0,gPFOther,gFQ,gPFL,nrow=1) 
ggsave(paste0("AllSynsByLayer.pdf"), gAll, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\Overview\\",
   scale = 1.5, width = 60, height = 10, units ="cm", dpi = 72, limitsize = TRUE)
```

Show the pre and post synaptic layer synapse counts for the tangential neurons
```{r}
# Get the FB tangential neuron names
tangFBtypes = neuprint_search("FB.*")$type %>% unique
tangFBtypes <- tangFBtypes[which(!is.na(tangFBtypes) & !(tangFBtypes=="SA3"))]

yl = 100000
gFBTang = FBLayerHist(c("FB","SA3"),1,2*yl)
ggsave(paste0("FBTangentialSynsByLayer.pdf"), gFBTang, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\Overview\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)

gExR = FBLayerHist(c("ExR1","ExR3","ExR5","OA-VPM3"),0,yl)
ggsave(paste0("ExRSynsByLayer.pdf"), gExR, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\Overview\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)

gAll2 <-grid.arrange(gPFN,gD6,gD0,gPFOther,gFBTang,gExR,gFQ,gPFL,nrow=2) 
ggsave(paste0("AllSynsByLayerWTang.pdf"), gAll2, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\Overview\\",
   scale = 1.5, width = 30, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
```

Plot the FB layers
```{r}
 # Load the reshape library 
library(reshape2)

# Specify the number of bins to use
nbins <- 100

# Assign a color map for each layer
cMap = rainbow(9)

# Pull the FB mesh
FB_Mesh = neuprint_ROI_mesh("FB")
FB_xyz = data.frame(x = FB_Mesh$vb[1,], y = FB_Mesh$vb[2,], z = FB_Mesh$vb[3,])

# Get the x and z bins
x.bin <- seq(floor(min(FB_xyz$x)), ceiling(max(FB_xyz$x)), length=nbins)
y.bin <- seq(floor(min(FB_xyz$y)), ceiling(max(FB_xyz$y)), length=nbins)
z.bin <- seq(floor(min(FB_xyz$z)), ceiling(max(FB_xyz$z)), length=nbins)

# Create a plot with the FB outline
p1 <- ggplot()

# Pull and plot the FB mesh for each layer
for (l in 1:9){
  FB_Mesh = neuprint_ROI_mesh(paste0("FBl",l))
  FB_xyz = data.frame(x = FB_Mesh$vb[1,], y = FB_Mesh$vb[2,], z = FB_Mesh$vb[3,])
  
  # Create a 2D histogram of the FB points
  FBfreq <-  melt(table(findInterval(FB_xyz$z, z.bin),findInterval(FB_xyz$x, x.bin)))
  FBfreq2D <- diag(nbins)*0
  FBfreq2D[cbind(FBfreq[,1], FBfreq[,2])] <- FBfreq[,3]
  dimnames(FBfreq2D) <- list(z.bin, x.bin)
  FBhist.melt <- melt(FBfreq2D)
  names(FBhist.melt) <- c("x", "z", "numPts")
  
  # Make a binary mask out of the FB points
  FBhist.melt[which(FBhist.melt$numPts>=0.1),]$numPts <- l
  FBhist.melt[which(FBhist.melt$numPts<0.1),]$numPts <- 0
  FBhist.melt <- FBhist.melt[which(FBhist.melt$numPts>0),]
  
  FBhist.melt$numPts <- as.factor(FBhist.melt$numPts)
  p1 <- p1 + geom_tile(data = FBhist.melt, aes(x = x,y = z, fill = numPts),alpha=0.5)
}

p1 <- p1 + coord_fixed(ratio = 1) + theme_void() +
  scale_x_reverse() + scale_y_reverse() +
  scale_fill_manual(values=cMap,name = "FB layer")

ggsave(paste0("FBLayerOverview_xz.pdf"), p1, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
```

Plot the FB columns - color by PB glom
```{r}
type = "PFN"
prePost = "PRE"

PBGloms = c("FB",
            "L9","L8","L7","L6","L5","L4","L3","L2","L1",
            "R1","R2","R3","R4","R5","R6","R7","R8","R9")

# Load the reshape library 
library(reshape2)

# Specify the number of bins to use
nbins <- 100

# Pull the FB mesh
FB_Mesh = neuprint_ROI_mesh("FB")
FB_xyz = data.frame(x = FB_Mesh$vb[1,], y = FB_Mesh$vb[2,], z = FB_Mesh$vb[3,])

# Get the x and z bins
x.bin <- seq(floor(min(FB_xyz$x)), ceiling(max(FB_xyz$x)), length=nbins)
z.bin <- seq(floor(min(FB_xyz$z)), ceiling(max(FB_xyz$z)), length=nbins)

# Create a 2D histogram of the FB points
FBfreq <-  melt(table(findInterval(FB_xyz$x, x.bin),findInterval(FB_xyz$z, z.bin)))
FBfreq2D <- diag(nbins)*0
FBfreq2D[cbind(FBfreq[,1], FBfreq[,2])] <- FBfreq[,3]
dimnames(FBfreq2D) <- list(x.bin, z.bin)
FBhist.melt <- melt(FBfreq2D)
names(FBhist.melt) <- c("x", "z", "numPts")

# Make a binary mask out of the FB points
FBhist.melt <- FBhist.melt[which(FBhist.melt$numPts>0),]
FBhist.melt$numPts <- "FB"
FBhist.melt$numPts <- factor(FBhist.melt$numPts, levels = PBGloms)

# Get the body ids
bodyIds = neuprint_search(paste0(type,".*"))$bodyid

# Assign a color map given the number of synapsese
cMap = c("#000000FF")
cMap = append(cMap,rainbow(length(PBGloms)))

# Create a plot with the FB outline
p1 <- ggplot() + geom_tile(data = FBhist.melt, aes(x = x,y = z, fill = numPts))

for (bid in 1:length(bodyIds)){
  
  # Pull the individual PFL synapses
  syns = neuprint_get_synapses(bodyIds[bid], roi="FB")
  if (grepl("PRE",prePost)){
    syns <-  syns[which(syns$prepost == 0),]
  } else{
    syns <- syns[which(syns$prepost == 1),]
  }
  if (nrow(syns)==0)
    next
  syns <- syns %>% mutate(name=as.character(type))%>%  mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
   
  # Create a 2D histogram of the synapses
  freq <-  melt(table(findInterval(syns$x, x.bin),findInterval(syns$z, z.bin)))
  freq2D <- diag(nbins)*0
  freq2D[cbind(freq[,1], freq[,2])] <- freq[,3]
  dimnames(freq2D) <- list(x.bin, z.bin)
  hist.melt <- melt(freq2D)
  names(hist.melt) <- c("xPos", "zPos", "numSyns")
  
  # Get the PB ROI
  ROIDat = neuprint_get_roiInfo(bodyIds[bid])
  PBROIs = colnames(ROIDat)
  PBROIs <- PBROIs[which(grepl("PB",PBROIs) & PBROIs != "PB.post")]
  if (length(PBROIs) > 1){
    PBROI = names(which.max(ROIDat[,which(colnames(ROIDat) %in% PBROIs)]))
  } else {
    PBROI = PBROIs
  }
  if (length(PBROI) == 0)
    next
    
  
  # Make a binary mask out of the synapses
  hist.melt <- hist.melt[which(hist.melt$numSyns>0),]
  glomIndex = PBGloms %>% lapply(function(x){grepl(x[[1]],PBROI)}) %>% unlist() %>% which() 
  hist.melt[which(hist.melt$numSyns>=0.1),]$numSyns <- PBGloms[glomIndex]
  hist.melt$numSyns <- factor(hist.melt$numSyns,levels=PBGloms)
  
  hist.melt$bodyid = bodyIds[bid]

  p1 <- p1 + geom_tile(data=hist.melt,aes(x=xPos,y=zPos,fill=numSyns,alpha=0.1))
  
}
p1 <- p1 + coord_fixed(ratio = 1) + theme_void() +
  scale_x_reverse() + scale_y_reverse()  +  scale_fill_manual(values=cMap,name = "PB Glom")
if (grepl("PRE",prePost)) {
  p1 <-  p1 + ggtitle(paste0(as.character(type),": outputs (n=",length(bodyIds),")")) 
} else {
  p1 <-  p1 + ggtitle(paste0(as.character(type),": inputs (n=",length(bodyIds),")")) 
}

ggsave(paste0("FBColumnsPFNs.pdf"), p1, device='pdf', 
   path = "C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FB\\",
   scale = 1.5, width = 20, height = 15, units ="cm", dpi = 72, limitsize = TRUE)
```

