---
title: "Notebook plotting synapse distributions for columnar neurons of the FB"
output:
  html_document:
    df_print: paged
---

### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(plotly)
library(dplyr)
library(matlib)
library(car)
library(imager)
library(reshape2)
library(zoo)
library(ggpubr)
library(ks)
library(RColorBrewer)
require(alphahull)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="FB"  

# Directory to save data to.
SaveDir="Z:/Cx_Connectome/BradData/FB_Analysis/"

# Directory to save plots to.
PlotDir="Z:/Cx_Connectome/BradData/FB_Analysis/ColumnarSynapseLocs/"


```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}
source("inputOutputRegionsVis.r")
source("GetNeuronsInRoi.r")
source("SynapsePCAUtils.r")
source("GetRoiMeshOutline.r")
```


### Get neurons in the ROI and
### Exclude neurons not in known FB types
```{r}

# get all FB bodies
NamedBodies = Get_AllNeurons_InRoi(ROI, FALSE)
NamedBodies=ComputeRelativeSynapseCounts(NamedBodies)


# Exclude bodies that are not columnar
FB_Columnar_Type=c("PF","Delta","FR","FS","FC")
ExcludedTypes=unique(NamedBodies$bodytype[!( startsWith(NamedBodies$bodytype, FB_Columnar_Type))])
IncludedTypes=unique(NamedBodies$bodytype[( startsWith(NamedBodies$bodytype, FB_Columnar_Type))])
ColumnarBodies=subset(NamedBodies, NamedBodies$bodytype %in% IncludedTypes)


```


### Get synapse distributions for all columnar neurons (or load previous data) and subset by layer
```{r}
# load(paste(SaveDir,"FBColumnarSynapses.RData",sep=""))


# Get all synapses for the ring neurons
SynLocs=GetSynapseLocs(ColumnarBodies$bodyid, "FB",TRUE)
FBC_SynsAll=SynLocs
remove(SynLocs)


# Get meshes
Mesh_FB= neuprint_ROI_mesh("FB")
Mesh_FB_L1= neuprint_ROI_mesh("FBl1")
Mesh_FB_L2= neuprint_ROI_mesh("FBl2")
Mesh_FB_L3= neuprint_ROI_mesh("FBl3")
Mesh_FB_L4= neuprint_ROI_mesh("FBl4")
Mesh_FB_L5= neuprint_ROI_mesh("FBl5")
Mesh_FB_L6= neuprint_ROI_mesh("FBl6")
Mesh_FB_L7= neuprint_ROI_mesh("FBl7")
Mesh_FB_L8= neuprint_ROI_mesh("FBl8")
Mesh_FB_L9= neuprint_ROI_mesh("FBl9")


# Assign synapses to layers (Note ~0.05% of synapses are not in a layer, where layer=NA )
FBC_SynsAll$Layer=NA
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L1)] <- "L1"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L2)] <- "L2"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L3)] <- "L3"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L4)] <- "L4"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L5)] <- "L5"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L6)] <- "L6"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L7)] <- "L7"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L8)] <- "L8"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L9)] <- "L9"
FBC_SynsAll$Layer=as.factor(FBC_SynsAll$Layer)

# Save synapse locations for later loading
save(FBC_SynsAll, Mesh_FB, Mesh_FB_L1, Mesh_FB_L2, Mesh_FB_L3, Mesh_FB_L4, Mesh_FB_L5,
     Mesh_FB_L6, Mesh_FB_L7, Mesh_FB_L8, Mesh_FB_L9, file = paste(SaveDir,"FBColumnarSynapses.RData",sep=""))



```


# Get mesh points
```{r}

Mesh_FB_Points=MeshPoints(Mesh_FB)
Mesh_FB_L1_Points=MeshPoints(Mesh_FB_L1)
Mesh_FB_L2_Points=MeshPoints(Mesh_FB_L2)
Mesh_FB_L3_Points=MeshPoints(Mesh_FB_L3)
Mesh_FB_L4_Points=MeshPoints(Mesh_FB_L4)
Mesh_FB_L5_Points=MeshPoints(Mesh_FB_L5)
Mesh_FB_L6_Points=MeshPoints(Mesh_FB_L6)
Mesh_FB_L7_Points=MeshPoints(Mesh_FB_L7)
Mesh_FB_L8_Points=MeshPoints(Mesh_FB_L8)
Mesh_FB_L9_Points=MeshPoints(Mesh_FB_L9)

```


# Center synapses and mesh points at new origin
```{r}


# define new origin from roi center of mass
origin = getCOM(Mesh_FB_Points)


#reset orgin of all layers
Mesh_FB_Points = resetOrigin(Mesh_FB_Points, origin)
Mesh_FB_L1_Points = resetOrigin(Mesh_FB_L1_Points, origin)
Mesh_FB_L2_Points = resetOrigin(Mesh_FB_L2_Points, origin)
Mesh_FB_L3_Points = resetOrigin(Mesh_FB_L3_Points, origin)
Mesh_FB_L4_Points = resetOrigin(Mesh_FB_L4_Points, origin)
Mesh_FB_L5_Points = resetOrigin(Mesh_FB_L5_Points, origin)
Mesh_FB_L6_Points = resetOrigin(Mesh_FB_L6_Points, origin)
Mesh_FB_L7_Points = resetOrigin(Mesh_FB_L7_Points, origin)
Mesh_FB_L8_Points = resetOrigin(Mesh_FB_L8_Points, origin)
Mesh_FB_L9_Points = resetOrigin(Mesh_FB_L9_Points, origin)


# Reset origin of all synapses 
FBC_SynsAll = resetOrigin(FBC_SynsAll, origin)


```


# Perform PCA and rotation to get axes
```{r}

#get eigenvectors
roiEigen = covPCA(Mesh_FB_Points)

# Rotate PCs some
RotMat=makeRotMatYZ(-33) # 33
roiEigen$vectors= roiEigen$vectors %*% RotMat
RotMat=makeRotMatXY(-3) # -3
roiEigen$vectors= roiEigen$vectors %*% RotMat

# Project meshes into PCA space
Mesh_FB_Points = changeBasis(Mesh_FB_Points, roiEigen)
Mesh_FB_L1_Points = changeBasis(Mesh_FB_L1_Points, roiEigen)
Mesh_FB_L2_Points = changeBasis(Mesh_FB_L2_Points, roiEigen)
Mesh_FB_L3_Points = changeBasis(Mesh_FB_L3_Points, roiEigen)
Mesh_FB_L4_Points = changeBasis(Mesh_FB_L4_Points, roiEigen)
Mesh_FB_L5_Points = changeBasis(Mesh_FB_L5_Points, roiEigen)
Mesh_FB_L6_Points = changeBasis(Mesh_FB_L6_Points, roiEigen)
Mesh_FB_L7_Points = changeBasis(Mesh_FB_L7_Points, roiEigen)
Mesh_FB_L8_Points = changeBasis(Mesh_FB_L8_Points, roiEigen)
Mesh_FB_L9_Points = changeBasis(Mesh_FB_L9_Points, roiEigen)


# Project synapses into PCA space
FBC_SynsAll=changeBasis_df(FBC_SynsAll, roiEigen)



```


# Plot data in new and old reference frame
```{r message=FALSE}


# Make scatter plot new projection
ggplot(Mesh_FB_Points, aes(x=X, y=-Y)) + geom_point(size=1, alpha = 0.05) +  xlab("x=PC1") + ylab("y=PC2") + coord_fixed(ratio = 1) 
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L1_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + coord_fixed(ratio = 1) 



# Make scatter plot of original space
ggplot(Mesh_FB_Points, aes(x=x, y=-z)) + geom_point(size=1, alpha = 0.05) +  xlab("x=PC1") + ylab("y=PC2") + coord_fixed(ratio = 1) 
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L1_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + coord_fixed(ratio = 1) 


# Scatter subset of synapses, colored by layer
data2=FBC_SynsAll[seq(from = 1, to = length(FBC_SynsAll$x), by = 500), ]
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=X, y=-Y), colour= "darkgray",  size=1, alpha = 0.01) +
           geom_point(data=data2, aes(x=X, y=-Y, colour= Layer),  size=1, alpha = 0.7) + coord_fixed(ratio = 1) 
remove(data2)


```



# Save data for later loading
```{r}
# load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
# Save synapse locations for later loading
save(FBC_SynsAll, Mesh_FB_Points, Mesh_FB_L1_Points, Mesh_FB_L2_Points, Mesh_FB_L3_Points, Mesh_FB_L4_Points,
     Mesh_FB_L5_Points, Mesh_FB_L6_Points, Mesh_FB_L7_Points, Mesh_FB_L8_Points, Mesh_FB_L9_Points,
     roiEigen, origin, file = paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))

```


# Get rid of original frame (the lowercase x,y,z data)
```{r}

# Meshes
Mesh_FB_Points=Mesh_FB_Points[ , !(names(Mesh_FB_Points) %in% c("x","y","z"))]
Mesh_FB_L1_Points=Mesh_FB_L1_Points[ , !(names(Mesh_FB_L1_Points) %in% c("x","y","z"))]
Mesh_FB_L2_Points=Mesh_FB_L2_Points[ , !(names(Mesh_FB_L2_Points) %in% c("x","y","z"))]
Mesh_FB_L3_Points=Mesh_FB_L3_Points[ , !(names(Mesh_FB_L3_Points) %in% c("x","y","z"))]
Mesh_FB_L4_Points=Mesh_FB_L4_Points[ , !(names(Mesh_FB_L4_Points) %in% c("x","y","z"))]
Mesh_FB_L5_Points=Mesh_FB_L5_Points[ , !(names(Mesh_FB_L5_Points) %in% c("x","y","z"))]
Mesh_FB_L6_Points=Mesh_FB_L6_Points[ , !(names(Mesh_FB_L6_Points) %in% c("x","y","z"))]
Mesh_FB_L7_Points=Mesh_FB_L7_Points[ , !(names(Mesh_FB_L7_Points) %in% c("x","y","z"))]
Mesh_FB_L8_Points=Mesh_FB_L8_Points[ , !(names(Mesh_FB_L8_Points) %in% c("x","y","z"))]
Mesh_FB_L9_Points=Mesh_FB_L9_Points[ , !(names(Mesh_FB_L9_Points) %in% c("x","y","z"))]


#Synapses
FBC_SynsAll=FBC_SynsAll[ , !(names(FBC_SynsAll) %in% c("x","y","z"))]


```



# Get outlines of each layer
```{r}

# Get XY outlines of each layer, with Y direction reverse so dorsal is up
Outline_L1_XY=MeshOutline(Mesh_FB_L1_Points, "XY")
Outline_L2_XY=MeshOutline(Mesh_FB_L2_Points, "XY")
Outline_L3_XY=MeshOutline(Mesh_FB_L3_Points, "XY")
Outline_L4_XY=MeshOutline(Mesh_FB_L4_Points, "XY")
Outline_L5_XY=MeshOutline(Mesh_FB_L5_Points, "XY")
Outline_L6_XY=MeshOutline(Mesh_FB_L6_Points, "XY")
Outline_L7_XY=MeshOutline(Mesh_FB_L7_Points, "XY")
Outline_L8_XY=MeshOutline(Mesh_FB_L8_Points, "XY")
Outline_L9_XY=MeshOutline(Mesh_FB_L9_Points, "XY")


# Get XZ outlines of each layer, with Y direction reverse so dorsal is up
Outline_L1_XZ=MeshOutline(Mesh_FB_L1_Points, "XZ")
Outline_L2_XZ=MeshOutline(Mesh_FB_L2_Points, "XZ")
Outline_L3_XZ=MeshOutline(Mesh_FB_L3_Points, "XZ")
Outline_L4_XZ=MeshOutline(Mesh_FB_L4_Points, "XZ")
Outline_L5_XZ=MeshOutline(Mesh_FB_L5_Points, "XZ")
Outline_L6_XZ=MeshOutline(Mesh_FB_L6_Points, "XZ")
Outline_L7_XZ=MeshOutline(Mesh_FB_L7_Points, "XZ")
Outline_L8_XZ=MeshOutline(Mesh_FB_L8_Points, "XZ")
Outline_L9_XZ=MeshOutline(Mesh_FB_L9_Points, "XZ")


# Check layer 6 for alignment
ggplot() + geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=-Y), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L6_XY, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L6_XZ, aes(x=c1, y=c2), size = 1) 


```
















