---
title: "Notebook plotting synapse distributions for columnar neurons of the FB"
output:
  html_document:
    df_print: paged
---

### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(plotly)
library(dplyr)
library(matlib)
library(car)
library(imager)
library(reshape2)
library(zoo)
library(ggpubr)
library(ks)
library(RColorBrewer)
require(alphahull)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="FB"  

# Directory to save data to.
SaveDir="Z:/Cx_Connectome/BradData/FB_Analysis/"

# Directory to save plots to.
PlotDir="Z:/Cx_Connectome/BradData/FB_Analysis/ColumnarSynapseLocs/"


```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}
source("inputOutputRegionsVis.r")
source("GetNeuronsInRoi.r")
source("SynapsePCAUtils.r")
source("GetRoiMeshOutline.r")
```


### Get neurons in the ROI and
### Exclude neurons not in known FB types
```{r}

# get all FB bodies
NamedBodies = Get_AllNeurons_InRoi(ROI, FALSE)
NamedBodies=ComputeRelativeSynapseCounts(NamedBodies)

# Load known FB types
load(paste(SaveDir,"FB_Types.RData",sep=""))

# Exclude bodies that are not columnar
FB_Columnar_Type=c("PF","Delta","FR","FS","FC")
ExcludedTypes=unique(NamedBodies$bodytype[!( startsWith(NamedBodies$bodytype, FB_Columnar_Type))])
IncludedTypes=unique(NamedBodies$bodytype[( startsWith(NamedBodies$bodytype, FB_Columnar_Type))])
ColumnarBodies=subset(NamedBodies, NamedBodies$bodytype %in% IncludedTypes)


```


### Get synapse distributions for all columnar neurons (or load previous data) and subset by layer
```{r}
# load(paste(SaveDir,"FBColumnarSynapses.RData",sep=""))


# Get all synapses for the ring neurons
SynLocs=GetSynapseLocs(ColumnarBodies$bodyid, "FB",TRUE)
FBC_SynsAll=SynLocs
remove(SynLocs)


# Get meshes
Mesh_FB= neuprint_ROI_mesh("FB")
Mesh_FB_L1= neuprint_ROI_mesh("FBl1")
Mesh_FB_L2= neuprint_ROI_mesh("FBl2")
Mesh_FB_L3= neuprint_ROI_mesh("FBl3")
Mesh_FB_L4= neuprint_ROI_mesh("FBl4")
Mesh_FB_L5= neuprint_ROI_mesh("FBl5")
Mesh_FB_L6= neuprint_ROI_mesh("FBl6")
Mesh_FB_L7= neuprint_ROI_mesh("FBl7")
Mesh_FB_L8= neuprint_ROI_mesh("FBl8")
Mesh_FB_L9= neuprint_ROI_mesh("FBl9")


# Assign synapses to layers (Note ~0.05% of synapses are not in a layer, where layer=NA )
FBC_SynsAll$Layer=NA
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L1)] <- "L1"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L2)] <- "L2"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L3)] <- "L3"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L4)] <- "L4"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L5)] <- "L5"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L6)] <- "L6"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L7)] <- "L7"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L8)] <- "L8"
FBC_SynsAll$Layer[pointsinside(FBC_SynsAll, Mesh_FB_L9)] <- "L9"
FBC_SynsAll$Layer=as.factor(FBC_SynsAll$Layer)

# Save synapse locations for later loading
save(FBC_SynsAll, Mesh_FB, Mesh_FB_L1, Mesh_FB_L2, Mesh_FB_L3, Mesh_FB_L4, Mesh_FB_L5,
     Mesh_FB_L6, Mesh_FB_L7, Mesh_FB_L8, Mesh_FB_L9, file = paste(SaveDir,"FBColumnarSynapses.RData",sep=""))



```


# Get mesh points
```{r}

Mesh_FB_Points=MeshPoints(Mesh_FB)
Mesh_FB_L1_Points=MeshPoints(Mesh_FB_L1)
Mesh_FB_L2_Points=MeshPoints(Mesh_FB_L2)
Mesh_FB_L3_Points=MeshPoints(Mesh_FB_L3)
Mesh_FB_L4_Points=MeshPoints(Mesh_FB_L4)
Mesh_FB_L5_Points=MeshPoints(Mesh_FB_L5)
Mesh_FB_L6_Points=MeshPoints(Mesh_FB_L6)
Mesh_FB_L7_Points=MeshPoints(Mesh_FB_L7)
Mesh_FB_L8_Points=MeshPoints(Mesh_FB_L8)
Mesh_FB_L9_Points=MeshPoints(Mesh_FB_L9)

```


# Center synapses and mesh points at new origin
```{r}


# define new origin from roi center of mass
origin = getCOM(Mesh_FB_Points)


#reset orgin of all layers
Mesh_FB_Points = resetOrigin(Mesh_FB_Points, origin)
Mesh_FB_L1_Points = resetOrigin(Mesh_FB_L1_Points, origin)
Mesh_FB_L2_Points = resetOrigin(Mesh_FB_L2_Points, origin)
Mesh_FB_L3_Points = resetOrigin(Mesh_FB_L3_Points, origin)
Mesh_FB_L4_Points = resetOrigin(Mesh_FB_L4_Points, origin)
Mesh_FB_L5_Points = resetOrigin(Mesh_FB_L5_Points, origin)
Mesh_FB_L6_Points = resetOrigin(Mesh_FB_L6_Points, origin)
Mesh_FB_L7_Points = resetOrigin(Mesh_FB_L7_Points, origin)
Mesh_FB_L8_Points = resetOrigin(Mesh_FB_L8_Points, origin)
Mesh_FB_L9_Points = resetOrigin(Mesh_FB_L9_Points, origin)


# Reset origin of all synapses 
FBC_SynsAll = resetOrigin(FBC_SynsAll, origin)


```


# Perform PCA and rotation to get axes
```{r}

#get eigenvectors
roiEigen = covPCA(Mesh_FB_Points)

# Rotate PCs some
RotMat=makeRotMatYZ(-33) # 33
roiEigen$vectors= roiEigen$vectors %*% RotMat
RotMat=makeRotMatXY(-3) # -3
roiEigen$vectors= roiEigen$vectors %*% RotMat

# Project meshes into PCA space
Mesh_FB_Points = changeBasis(Mesh_FB_Points, roiEigen)
Mesh_FB_L1_Points = changeBasis(Mesh_FB_L1_Points, roiEigen)
Mesh_FB_L2_Points = changeBasis(Mesh_FB_L2_Points, roiEigen)
Mesh_FB_L3_Points = changeBasis(Mesh_FB_L3_Points, roiEigen)
Mesh_FB_L4_Points = changeBasis(Mesh_FB_L4_Points, roiEigen)
Mesh_FB_L5_Points = changeBasis(Mesh_FB_L5_Points, roiEigen)
Mesh_FB_L6_Points = changeBasis(Mesh_FB_L6_Points, roiEigen)
Mesh_FB_L7_Points = changeBasis(Mesh_FB_L7_Points, roiEigen)
Mesh_FB_L8_Points = changeBasis(Mesh_FB_L8_Points, roiEigen)
Mesh_FB_L9_Points = changeBasis(Mesh_FB_L9_Points, roiEigen)


# Project synapses into PCA space
FBC_SynsAll=changeBasis_df(FBC_SynsAll, roiEigen)



```


# Get pre and post type names based on bodyids, and subset based on known types
```{r}

# Get pre and post body names (to get pb columns later)
BodyId_And_Names=NamedBodies[c("bodyid","bodyname")]
BodyId_And_PartnerNames=NamedBodies[c("bodyid","bodyname")]
colnames(BodyId_And_PartnerNames)<-c("partner","partnername")
FBC_SynsAll=merge(FBC_SynsAll, BodyId_And_Names, by="bodyid")
FBC_SynsAll=merge(FBC_SynsAll, BodyId_And_PartnerNames, by="partner")

# subset based on known types
FBC_SynsAll=subset(FBC_SynsAll, (type %in% FB_Type) & (partner_type %in% FB_Type) )


```



# Plot data in new and old reference frame
```{r message=FALSE}


# Make scatter plot new projection
ggplot(Mesh_FB_Points, aes(x=X, y=-Y)) + geom_point(size=1, alpha = 0.05) +  xlab("x=PC1") + ylab("y=PC2") + coord_fixed(ratio = 1) 
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L1_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=1, alpha = 0.01) + coord_fixed(ratio = 1) 



# Make scatter plot of original space
ggplot(Mesh_FB_Points, aes(x=x, y=-z)) + geom_point(size=1, alpha = 0.05) +  xlab("x=PC1") + ylab("y=PC2") + coord_fixed(ratio = 1) 
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L1_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=x, y=-z), colour= "cadetblue3",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=x, y=-z), colour= "blueviolet",  size=1, alpha = 0.01) + coord_fixed(ratio = 1) 


# Scatter subset of synapses, colored by layer
data2=FBC_SynsAll[seq(from = 1, to = length(FBC_SynsAll$x), by = 500), ]
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=X, y=-Y), colour= "darkgray",  size=1, alpha = 0.01) +
           geom_point(data=data2, aes(x=X, y=-Y, colour= Layer),  size=1, alpha = 0.7) + coord_fixed(ratio = 1) 
remove(data2)




```



# Save data for later loading
```{r}
# load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
# Save synapse locations for later loading
save(FBC_SynsAll, Mesh_FB_Points, Mesh_FB_L1_Points, Mesh_FB_L2_Points, Mesh_FB_L3_Points, Mesh_FB_L4_Points,
     Mesh_FB_L5_Points, Mesh_FB_L6_Points, Mesh_FB_L7_Points, Mesh_FB_L8_Points, Mesh_FB_L9_Points,
     roiEigen, origin, file = paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))

```


# Get rid of original frame (the lowercase x,y,z data)
```{r}

# Meshes
Mesh_FB_Points=Mesh_FB_Points[ , !(names(Mesh_FB_Points) %in% c("x","y","z"))]
Mesh_FB_L1_Points=Mesh_FB_L1_Points[ , !(names(Mesh_FB_L1_Points) %in% c("x","y","z"))]
Mesh_FB_L2_Points=Mesh_FB_L2_Points[ , !(names(Mesh_FB_L2_Points) %in% c("x","y","z"))]
Mesh_FB_L3_Points=Mesh_FB_L3_Points[ , !(names(Mesh_FB_L3_Points) %in% c("x","y","z"))]
Mesh_FB_L4_Points=Mesh_FB_L4_Points[ , !(names(Mesh_FB_L4_Points) %in% c("x","y","z"))]
Mesh_FB_L5_Points=Mesh_FB_L5_Points[ , !(names(Mesh_FB_L5_Points) %in% c("x","y","z"))]
Mesh_FB_L6_Points=Mesh_FB_L6_Points[ , !(names(Mesh_FB_L6_Points) %in% c("x","y","z"))]
Mesh_FB_L7_Points=Mesh_FB_L7_Points[ , !(names(Mesh_FB_L7_Points) %in% c("x","y","z"))]
Mesh_FB_L8_Points=Mesh_FB_L8_Points[ , !(names(Mesh_FB_L8_Points) %in% c("x","y","z"))]
Mesh_FB_L9_Points=Mesh_FB_L9_Points[ , !(names(Mesh_FB_L9_Points) %in% c("x","y","z"))]


#Synapses
FBC_SynsAll=FBC_SynsAll[ , !(names(FBC_SynsAll) %in% c("x","y","z"))]


```



# Get outlines of each layer
```{r}

# Get XY outlines of each layer, with Y direction reverse so dorsal is up
Outline_FB_XY=MeshOutline(Mesh_FB_Points, "XY")
Outline_L1_XY=MeshOutline(Mesh_FB_L1_Points, "XY")
Outline_L2_XY=MeshOutline(Mesh_FB_L2_Points, "XY")
Outline_L3_XY=MeshOutline(Mesh_FB_L3_Points, "XY")
Outline_L4_XY=MeshOutline(Mesh_FB_L4_Points, "XY")
Outline_L5_XY=MeshOutline(Mesh_FB_L5_Points, "XY")
Outline_L6_XY=MeshOutline(Mesh_FB_L6_Points, "XY")
Outline_L7_XY=MeshOutline(Mesh_FB_L7_Points, "XY")
Outline_L8_XY=MeshOutline(Mesh_FB_L8_Points, "XY")
Outline_L9_XY=MeshOutline(Mesh_FB_L9_Points, "XY")


# Get XZ outlines of each layer, with Y direction reverse so dorsal is up
Outline_FB_XZ=MeshOutline(Mesh_FB_Points, "XZ")
Outline_L1_XZ=MeshOutline(Mesh_FB_L1_Points, "XZ")
Outline_L2_XZ=MeshOutline(Mesh_FB_L2_Points, "XZ")
Outline_L3_XZ=MeshOutline(Mesh_FB_L3_Points, "XZ")
Outline_L4_XZ=MeshOutline(Mesh_FB_L4_Points, "XZ")
Outline_L5_XZ=MeshOutline(Mesh_FB_L5_Points, "XZ")
Outline_L6_XZ=MeshOutline(Mesh_FB_L6_Points, "XZ")
Outline_L7_XZ=MeshOutline(Mesh_FB_L7_Points, "XZ")
Outline_L8_XZ=MeshOutline(Mesh_FB_L8_Points, "XZ")
Outline_L9_XZ=MeshOutline(Mesh_FB_L9_Points, "XZ")


# Check layer 6 for alignment
ggplot() + geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=-Y), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L6_XY, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L6_XZ, aes(x=c1, y=c2), size = 1) 


```


# Make plots of FB layers as a schematic
```{r}


# Make scatter plot new projection
CCC=rainbow(9)
AAA=0.02
SSS=2
P1<-ggplot() + geom_point(data=Mesh_FB_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L1_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=X, y=-Y), colour= "cadetblue3",  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=X, y=-Y), colour= "blueviolet",  size=SSS, alpha = AAA) + 
          coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position="none")
ggsave(paste(PlotDir, "FB_1.png",sep=""),
       plot = P1, device='png', scale = 1, width = 6, height = 6, units ="in", dpi = 300, limitsize = TRUE)


P1<-ggplot() + geom_point(data=Mesh_FB_L1_Points, aes(x=X, y=-Y), colour= CCC[1],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=X, y=-Y), colour= CCC[2],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=X, y=-Y), colour= CCC[3],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=X, y=-Y), colour= CCC[4],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=X, y=-Y), colour= CCC[5],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=-Y), colour= CCC[6],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=X, y=-Y), colour= CCC[7],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=X, y=-Y), colour= CCC[8],  size=SSS, alpha = AAA) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=X, y=-Y), colour= CCC[9],  size=SSS, alpha = AAA) + 
           coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position="none")
ggsave(paste(PlotDir, "FB_2.png",sep=""),
       plot = P1, device='png', scale = 1, width = 6, height = 6, units ="in", dpi = 300, limitsize = TRUE)


```



# Get PB glomeruli or columns (Some columns are mixed and are named _L1/2 for example)
```{r}


# Assign side (pb or fb column half)
FBC_SynsAll$Side=NA
FBC_SynsAll$Side[grepl("_R",FBC_SynsAll$bodyname)]<-"R"
FBC_SynsAll$Side[grepl("_L",FBC_SynsAll$bodyname)]<-"L"

# Assign PB glom
FBC_SynsAll$PBglom=NA
RightColumns=str_extract(FBC_SynsAll$bodyname, "_R(\\d+)")
LeftColumns=str_extract(FBC_SynsAll$bodyname, "_L(\\d+)")
FBC_SynsAll$PBglom[which(!is.na(RightColumns))]=RightColumns[which(!is.na(RightColumns))]
FBC_SynsAll$PBglom[which(!is.na(LeftColumns))]=LeftColumns[which(!is.na(LeftColumns))]
FBC_SynsAll$PBglom=sapply(FBC_SynsAll$PBglom, substring, 2, 3)

# Assign FB glom
FBC_SynsAll$FBcol=NA
FBC_SynsAll$FBcol=str_extract(FBC_SynsAll$bodyname, "_C(\\d+)")
FBC_SynsAll$FBcol=sapply(FBC_SynsAll$FBcol, substring, 2, 3)

# print list of PF body names to make sure parsing worked. 
A=subset(FBC_SynsAll, startsWith(type, "PF"))
unique(A$bodyname)

```



# Various functions
```{r}


SetColumnOrder <- function(TypeX_Syns){
  TypeX_MeanPos= aggregate(TypeX_Syns[c("X","Y","Z")], by = list(bodyid=TypeX_Syns$bodyid), FUN=mean)
  colnames(TypeX_MeanPos)[c(2,3,4)]<-c("mean_X","mean_Y","mean_Z")
  TypeX_MeanPos$Order_X=order(TypeX_MeanPos$mean_X)
  TypeX_Syns = merge(TypeX_Syns, TypeX_MeanPos)
  return(TypeX_Syns)
}



PlotSyns_byColumn <- function(Plot_Syns, Title, PlotName){
  
  
  col_vector=brewer.pal(8, "Paired")
  col_vector[9]=col_vector[1]
  col_vector=col_vector[c(1,4,7,2,5,8,3,6,9)]
  
  P1<-ggplot() + geom_point(data=Plot_Syns, aes(x=X, y=-Y, color=FBcol) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XY, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=col_vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(Title)
  
  
  P2<-ggplot() + geom_point(data=Plot_Syns, aes(x=X, y=Z, color=FBcol) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XZ, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=col_vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(Title)
  
  
  P12<-ggarrange(plotlist=list(P1,P2), ncol =2, nrow = 1)
  ggsave(paste(PlotDir, PlotName,".png",sep=""),
         plot = P12, device='png', scale = 1, width = 8, height = 5, units ="in", dpi = 300, limitsize = TRUE)
  
}


PlotSyns_byGlom <- function(Plot_Syns, Title, PlotName){
  
  # Get neurons that innervate the left or right pb
  Plot_Syns_Lpb=subset(Plot_Syns, startsWith(PBglom,"L") )
  Plot_Syns_Lpb$PBglom=factor( Plot_Syns_Lpb$PBglom, levels= sort(unique(Plot_Syns_Lpb$PBglom)) )
  
  Plot_Syns_Rpb=subset(Plot_Syns, startsWith(PBglom,"R") )
  Plot_Syns_Rpb$PBglom=factor( Plot_Syns_Rpb$PBglom, levels= sort(unique(Plot_Syns_Rpb$PBglom)) )
  
  
  L_col_vector=brewer.pal(8, "Paired")
  L_col_vector[9]=L_col_vector[1]
  L_col_vector=L_col_vector[c(1,4,7,2,5,8,3,6,9)]
  R_col_vector=rev(L_col_vector)
  RL_col_Vector=c(L_col_vector, R_col_vector)
  
  
  # Make color map for each that maps PB glomeruli to their appropriate columns
  P1<-ggplot() + geom_point(data=Plot_Syns_Lpb, aes(x=X, y=-Y, color=PBglom) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XY, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=L_col_vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(paste("LEFT ", Title))
  
  
  P2<-ggplot() + geom_point(data=Plot_Syns_Lpb, aes(x=X, y=Z, color=PBglom) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XZ, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=L_col_vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(paste("LEFT ", Title))
  
  
  
  P3<-ggplot() + geom_point(data=Plot_Syns_Rpb, aes(x=X, y=-Y, color=PBglom) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XY, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=R_col_vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(paste("RIGHT ", Title))
  
  
  P4<-ggplot() + geom_point(data=Plot_Syns_Rpb, aes(x=X, y=Z, color=PBglom) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XZ, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=R_col_vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(paste("RIGHT ", Title))
  
  
  
  P5<-ggplot() + geom_point(data=Plot_Syns, aes(x=X, y=-Y, color=PBglom) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XY, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=RL_col_Vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(paste("RIGHT ", Title))
  
  
  P6<-ggplot() + geom_point(data=Plot_Syns, aes(x=X, y=Z, color=PBglom) ,  size=2, alpha = 0.05, stroke = 0, shape=16) + 
    coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position = "top") +
    geom_path(data=Outline_FB_XZ, aes(x=c1, y=c2), size = 1) +  scale_color_manual(values=RL_col_Vector) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
    ggtitle(paste("RIGHT ", Title))
  
  
  
  P12<-ggarrange(plotlist=list(P1,P2,P3,P4,P5,P6), ncol =2, nrow = 2)
  ggsave(paste(PlotDir, PlotName,".png",sep=""),
         plot = P12, device='png', scale = 1, width = 8, height = 12, units ="in", dpi = 300, limitsize = TRUE)
  
}

```


# Make plot of all Fx neurons, each FX neuron type individually, and similar plots per FB layer
```{r}

All_Fx=subset(FBC_SynsAll, !(is.na(FBcol)) & startsWith(type,"F"))
All_Fx$FBcol=factor(All_Fx$FBcol, levels=sort(unique(All_Fx$FBcol)) )

PlotSyns_byColumn(All_Fx, "FX All", "FX_All")

FX_Types=unique(All_Fx$type)
for (ttt in 1:length(FX_Types)){
  SubData=subset(All_Fx, type == FX_Types[ttt])
  PlotSyns_byColumn(SubData, FX_Types[ttt], paste("FX_",FX_Types[ttt],sep=""))
}


```


# Make a plot of all PFX neurons, each PFX neuron type individually, and similar plots per FB layer
```{r}


All_PFX=subset(FBC_SynsAll, !(is.na(PBglom)) & startsWith(type,"PF"))

PlotSyns_byGlom(All_PFX, "PB-FB-XX ALL", "PB_FB_XX_ALL")


PFX_Types=unique(All_PFX$type)
for (ttt in 1:length(PFX_Types)){
  SubData=subset(All_PFX, type == PFX_Types[ttt])
  PlotSyns_byGlom(SubData, PFX_Types[ttt], paste("PB_FB_XX_",PFX_Types[ttt],sep=""))
}



```

































# Make plot of all Delta0 neurons
```{r}

col_vector=brewer.pal(8, "Paired")
col_vector[9]=col_vector[1]
col_vector=col_vector[c(1,4,7,2,5,8,3,6,9)]


All_D0=subset(FBC_SynsAll, startsWith(type,"Delta0"))
All_D0$FBcol=factor(All_Fx$FBcol, levels=sort(unique(All_Fx$FBcol)) )

PlotSyns(All_Fx, All_Fx$FBcol, col_vector, "FX All", "FX_All")

```






# for each type plot the full front view of synapses, colored by cell type x position order
```{r}

ColumnarTypes=unique(FBC_SynsAll$type)


col_vector=brewer.pal(12, "Paired")
col_vector=col_vector[c(1,4,7,10,2,5,8,11,3,6,9,12)]


for (nnn in 1:length(ColumnarTypes) ){
  
  # Take subset of of this type
  TypeX_Syns=subset(FBC_SynsAll, FBC_SynsAll$type %in% ColumnarTypes[nnn])
  
  # Get ordering
  TypeX_Syns=SetColumnOrder(TypeX_Syns)
  
  
  P1<-ggplot() + geom_point(data=TypeX_Syns, aes(x=X, y=-Y, color = mean_X ) ,  size=2, alpha = 0.1, stroke = 0, shape=16) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position="none") +
  geom_path(data=Outline_FB_XY, aes(x=c1, y=c2), size = 1) + scale_colour_gradientn(colours = col_vector) + 
  ggtitle(as.character(TypeX_Syns$type[1]))
  
  
  P2<-ggplot() + geom_point(data=TypeX_Syns, aes(x=X, y=Z, color= mean_X ),  size=2, alpha = 0.1, stroke = 0, shape=16) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(fill=FALSE) + theme(legend.position="none") +
  geom_path(data=Outline_FB_XZ, aes(x=c1, y=c2), size = 1) + scale_colour_gradientn(colours = col_vector) 
    


  P12<-ggarrange(plotlist=list(P1,P2), ncol =2, nrow = 1)
  ggsave(paste(PlotDir, as.character(TypeX_Syns$type[1]) , "_ALL",".png",sep=""),
       plot = P12, device='png', scale = 1, width = 12, height = 7, units ="in", dpi = 300, limitsize = TRUE)
  
}




```















