---
title: "FC1 subtyping"
output: html_notebook
---

Load the libraries
```{r}
library(nat)
library(neuprintr)
library(tidyverse)
library(neuprintrExtra)
library(cowplot)
library(reshape2)
library(paletteer)
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\FBNetworkVisUtils.R")
options(nat.plotengine = 'rgl')
```

Specify plotting text sizes
```{r}
tickLabSz <- 6
axLabSz <- 8
legSz <- 6
legTitSz <- 8
pltTit <- 8

theme_set(theme(axis.title = element_text(size = axLabSz), 
      axis.text = element_text(size = tickLabSz),
      legend.text = element_text(size = legSz),
      legend.title = element_text(size = legTitSz),
      plot.title = element_text(size = pltTit)))

stCols <- supertype2Palette()
```

Function to rename FB neurons
```{r}
FBRename <- function(name,id){
  
  # From a unique nameif from the PB type, the PB gloms where it arborizes, and the bodyid
  name  <- gsub("\\s*\\([^\\)]+\\)","",as.character(name))
  nameid <- paste(name, as.character(id), sep='-')
  
  # Extract the unique names and types
  allNames = nameid %>% unique() %>% sort()
  nameLabels = name %>% unique() %>% sort()
  types = strsplit(allNames,'_') %>% lapply(function(x){x[[1]]}) %>% unique() %>% unlist()
  types = gsub("([\\(\\)])", "\\\\\\1",types)
  
  # Sort the names by the order of the glomeruli in the PB and exchange the bodyid for a number
  newNames = c()
  for (tp in 1:length(types)){
    allNames[which(grepl(paste0('^',types[tp],"_"),allNames))] <- 
      allNames[which(grepl(paste0('^',types[tp],"_"),allNames))] %>% sort()
    nmOrder <- allNames[which(grepl(paste0('^',types[tp],"_"),allNames))] %>% sort()
    nms <- nameLabels[which(grepl(paste0('^',types[tp],"_"),nameLabels))]
    for (n in 1:length(nms)){
      nmsNow <- nmOrder[which(grepl(nms[n],nmOrder))]
      nmsNow <- paste(nms[n],seq(1:length(nmsNow)),sep='-')
      nmOrder[which(grepl(nms[n],nmOrder))] <- nmsNow
    }
    newNames = append(newNames,nmOrder)
  }
  # Create a lookup table between the old and new names
  nmSwap <- data.frame(oldNm = allNames, newNm = newNames)
  
  # Swap in the new names
  nameid <- lapply(nameid, function(x) nmSwap$newNm[match(x, nmSwap$oldNm)]) %>%
    factor(levels = nmSwap$newNm)
  
  return(nameid)
}
```

```{r}
# Get the connection table
conTab_FCs_From <- getConnectionTable(getTypesTable(c("FC1","FC1A","FC1B","FC1C","FC1D","FC1E","FC1F"))$bodyid,
                                   "PRE",
                                   "FB")
conTab_FCs_From$id.from <- FBRename(conTab_FCs_From$name.from, conTab_FCs_From$from)
conTab_FCs_From$id.to <- FBRename(conTab_FCs_From$name.to, conTab_FCs_From$to)

plt_conTab_FCs_From <- ggplot(conTab_FCs_From) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(conTab_FCs_From$weightRelative),
                       limits=c(0,max(conTab_FCs_From$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_cowplot() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,size=1,hjust=1),
        axis.text.y = element_text(size=1)) +
  xlab("post-synaptic neuron") + ylab("pre-synaptic neuron")

offset <- 0.5
tpsFrom <- conTab_FCs_From$type.from %>% unique() %>% sort()
idsFrom <- conTab_FCs_From$id.from %>% unique() %>% sort()
for (t in 1:length(tpsFrom)){
  offset <- offset + length(which(grepl(tpsFrom[t],idsFrom)))
  plt_conTab_FCs_From <- plt_conTab_FCs_From + geom_hline(yintercept = offset)
}

offset <- 0.5
tpsTo <- conTab_FCs_From$type.to %>% unique() %>% sort()
idsTo <- conTab_FCs_From$id.to %>% unique() %>% sort()
for (t in 1:length(tpsTo)){
  offset <- offset + length(which(grepl(tpsTo[t],idsTo)))
  plt_conTab_FCs_From <- plt_conTab_FCs_From + geom_vline(xintercept = offset)
}

print(plt_conTab_FCs_From)
```

```{r}
# Get the connection table
conTab_FCs_To <- getConnectionTable(getTypesTable(c("FC1","FC1A","FC1B","FC1C","FC1D","FC1E","FC1F"))$bodyid,
                                   "POST",
                                   "FB")
conTab_FCs_To$id.from <- FBRename(conTab_FCs_To$name.from, conTab_FCs_To$from)
conTab_FCs_To$id.to <- FBRename(conTab_FCs_To$name.to, conTab_FCs_To$to)

plt_conTab_FCs_To <- ggplot(conTab_FCs_To) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(conTab_FCs_To$weightRelative),
                       limits=c(0,max(conTab_FCs_To$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_cowplot() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,size=1,hjust=1),
        axis.text.y = element_text(size=1)) +
  xlab("post-synaptic neuron") + ylab("pre-synaptic neuron")

offset <- 0.5
tpsFrom <- conTab_FCs_To$type.from %>% unique() %>% sort()
idsFrom <- conTab_FCs_To$id.from %>% unique() %>% sort()
for (t in 1:length(tpsFrom)){
  offset <- offset + length(which(grepl(tpsFrom[t],idsFrom)))
  plt_conTab_FCs_To <- plt_conTab_FCs_To + geom_hline(yintercept = offset)
}

offset <- 0.5
tpsTo <- conTab_FCs_To$type.to %>% unique() %>% sort()
idsTo <- conTab_FCs_To$id.to %>% unique() %>% sort()
for (t in 1:length(tpsTo)){
  offset <- offset + length(which(grepl(tpsTo[t],idsTo)))
  plt_conTab_FCs_To <- plt_conTab_FCs_To + geom_vline(xintercept = offset)
}

print(plt_conTab_FCs_To)
```

```{r}
print(plt_conTab_FCs_To)
print(plt_conTab_FCs_From)
```


Look at clustering the FC1 neurons - by outputs
```{r}
# Get the connection table
conTab_FCs_To <- getConnectionTable(getTypesTable(c("FC1","FC1A","FC1B","FC1C","FC1D","FC1E","FC1F"))$bodyid,
                                   "POST",
                                   "FB")
conTab_FCs_To$id.from <- FBRename(conTab_FCs_To$name.from, conTab_FCs_To$from)
conTab_FCs_To$id.to <- FBRename(conTab_FCs_To$name.to, conTab_FCs_To$to)
conTab_FCs_To$type.from <- "FC1"
conTab_FCs_To$type.to[which(grepl("FC1",conTab_FCs_To$type.to))] <- "FC1"

# Select only the relevant columns
Data4Clust <- conTab_FCs_To%>% select(id.from,type.to)

# Recast it into a matrix
Data4Clust <- dcast(Data4Clust,id.from~type.to)
Data4Clust[is.na(Data4Clust)] <- 0
rownames(Data4Clust) <- Data4Clust$id.from
Data4Clust <- Data4Clust %>% select(tail(colnames(Data4Clust),ncol(Data4Clust)-1))# Calculate the dissimilarity matrix
Data4Clust <- scale(Data4Clust)
d <- dist(Data4Clust, method = "euclidean")# Perform hierarchical clustering
hc_from <- hclust(d, method = "ward.D2" )# Order the FB tangential cells according to their clustering

fromOrder <- hc_from$labels[hc_from$order]
fromDend <- dendPlot(hc_from,TRUE)
print(fromDend)
```

Look at clustering the FC neurons - by inputs
```{r}
# Get the connection table
conTab_FCs_From <- getConnectionTable(getTypesTable(c("FC1","FC1A","FC1B","FC1C","FC1D","FC1E","FC1F"))$bodyid,
                                   "PRE",
                                   "FB")
conTab_FCs_From$id.from <- FBRename(conTab_FCs_From$name.from, conTab_FCs_From$from)
conTab_FCs_From$id.to <- FBRename(conTab_FCs_From$name.to, conTab_FCs_From$to)
conTab_FCs_From$type.to <- "FC1"
conTab_FCs_From$type.from[which(grepl("FC1",conTab_FCs_From$type.from))] <- "FC1"

# Select only the relevant columns
Data4Clust <- conTab_FCs_From%>% select(type.from,id.to)

# Recast it into a matrix
Data4Clust <- dcast(Data4Clust,id.to~type.from)
Data4Clust[is.na(Data4Clust)] <- 0
rownames(Data4Clust) <- Data4Clust$id.to
Data4Clust <- Data4Clust %>% select(tail(colnames(Data4Clust),ncol(Data4Clust)-1))# Calculate the dissimilarity matrix
Data4Clust <- scale(Data4Clust)
d <- dist(Data4Clust, method = "euclidean")# Perform hierarchical clustering
hc_to <- hclust(d, method = "ward.D2" )# Order the FB tangential cells according to their clustering

toOrder <- hc_to$labels[hc_to$order]
toDend <- dendPlot(hc_to,TRUE)
print(toDend)
```

Load Shinya's classification and plot them on the dendrogram
```{r}
FCInfo <- getTypesTable(c("FC1","FC1A","FC1B","FC1C","FC1D","FC1E","FC1F"))
FCInfo$name <- gsub("\\s*\\([^\\)]+\\)","",as.character(FCInfo$name))
FCInfo$id <- FBRename(FCInfo$name,FCInfo$bodyid)

dend_to <- as.dendrogram(hc_to)
dend_to_data <- dendro_data(dend_to, type = "rectangle")

# Add a group category
HClabels_to <- dend_to_data$labels
HClabels_to$group <- lapply(HClabels_to$label, function(l) FCInfo$type[which(FCInfo$id == l)]) %>% unlist() %>% as.factor()
  
p_to <- ggplot(dend_to_data$segments) +
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_text(data = HClabels_to, aes(x, y, label = label,color=group),
            hjust = 1, angle = 90, size = 3) + 
  theme_cowplot()
print(p_to)

dend_from <- as.dendrogram(hc_from)
dend_from_data <- dendro_data(dend_from, type = "rectangle")

# Add a group category
HClabels_from <- dend_from_data$labels
HClabels_from$group <- lapply(HClabels_from$label, function(l) FCInfo$type[which(FCInfo$id == l)]) %>% unlist() %>% as.factor()
  
p_from <- ggplot(dend_from_data$segments) +
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_text(data = HClabels_from, aes(x, y, label = label,color=group),
            hjust = 1, angle = 90, size = 3) + 
  theme_cowplot()
print(p_from)
```

Split the from dendrogram into 5 groups and the to dendrogram into 4 groups, compare
```{r}
fromSplit <- cutree(hc_from,5)
toSplit <- cutree(hc_to,4)

GpDat <- data.frame(name = names(fromSplit), from_group = as.numeric(fromSplit))
GpDat$to_group = as.numeric(toSplit)

ggplot(GpDat) + geom_point(aes(x=to_group,y=from_group),alpha=0.1)

# Manually reclassify some of the outliers
GpDat$from_group[which(GpDat$from_group == 5)] <- 4
GpDat$group <- 26
GpDat$group[which(GpDat$from_group == 1 & GpDat$to_group == 1)] <- 1
GpDat$group[which(GpDat$from_group == 2 & GpDat$to_group == 1)] <- 1
GpDat$group[which(GpDat$from_group == 3 & GpDat$to_group == 1)] <- 2
GpDat$group[which(GpDat$from_group == 3 & GpDat$to_group == 4)] <- 2
GpDat$group[which(GpDat$from_group == 2 & GpDat$to_group == 2)] <- 3
GpDat$group[which(GpDat$from_group == 1 & GpDat$to_group == 3)] <- 4
GpDat$group[which(GpDat$from_group == 2 & GpDat$to_group == 3)] <- 5
GpDat$group[which(GpDat$from_group == 4 & GpDat$to_group == 4)] <- 6
GpDat$group[which(GpDat$from_group == 4 & GpDat$to_group == 1)] <- 6

ggplot(GpDat) + geom_point(aes(x=to_group,y=from_group,color=as.factor(group)),alpha=0.1)

dend_to <- as.dendrogram(hc_to)
dend_to_data <- dendro_data(dend_to, type = "rectangle")

# Add a group category
HClabels_to <- dend_to_data$labels
HClabels_to$group <- lapply(HClabels_to$label, function(l) GpDat$group[which(GpDat$name == l)]) %>% unlist() %>% as.factor()
  
p_to <- ggplot(dend_to_data$segments) +
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_text(data = HClabels_to, aes(x, y, label = label,color=group),
            hjust = 1, angle = 90, size = 3) + 
  theme_cowplot()
print(p_to)

dend_from <- as.dendrogram(hc_from)
dend_from_data <- dendro_data(dend_from, type = "rectangle")

# Add a group category
HClabels_from <- dend_from_data$labels
HClabels_from$group <- lapply(HClabels_from$label, function(l) GpDat$group[which(GpDat$name == l)]) %>% unlist() %>% as.factor()
  
p_from <- ggplot(dend_from_data$segments) +
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_text(data = HClabels_from, aes(x, y, label = label,color=group),
            hjust = 1, angle = 90, size = 3) + 
  theme_cowplot()
print(p_from)
```

Rename the neurons according to their groups and plot their connectivity matrices
```{r}

conTab_FCs_To$type.from <- lapply(conTab_FCs_To$id.from, function(i)
  paste("FC1", letters[GpDat$group[which(GpDat$name == i)]], sep='_')) %>%
  unlist() %>% as.character()
conTab_FCs_To$name.from <- lapply(seq(1:nrow(conTab_FCs_To)), function(n)
  gsub("FC1",conTab_FCs_To$type.from[n],conTab_FCs_To$name.from[n])) %>%
  unlist() %>% as.character()
conTab_FCs_To$id.from <- FBRename(conTab_FCs_To$name.from,conTab_FCs_To$from)

conTab_FCs_To$type.to[which(conTab_FCs_To$type.to == "FC1")] <- lapply(conTab_FCs_To$id.to[which(conTab_FCs_To$type.to == "FC1")], function(i)
  paste("FC1",letters[GpDat$group[which(GpDat$name == i)]],sep='_')) %>% 
  unlist() %>% as.character()
conTab_FCs_To$name.to[which(grepl("FC1",conTab_FCs_To$type.to))] <- lapply(which(grepl("FC1",conTab_FCs_To$type.to)), function(n)
  gsub("FC1",conTab_FCs_To$type.to[n],conTab_FCs_To$name.to[n])) %>%
  unlist() %>% as.character()
conTab_FCs_To$id.to <- FBRename(conTab_FCs_To$name.to,conTab_FCs_To$to)

FCTypes <- conTab_FCs_To$type.from %>% unique() %>% sort()
FCCols <- paletteer_d("colorblindr::OkabeIto")

txtLabsFrom <- conTab_FCs_To$id.from %>% unique() %>% sort()
txtColsFrom <- lapply(txtLabsFrom, function(t) FCCols[which(grepl(substring(t,1,5),FCTypes))]) %>% unlist()

plt_conTab_FCs_To <- ggplot(conTab_FCs_To %>% filter(!grepl("FC1",type.to))) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(conTab_FCs_To$weightRelative),
                       limits=c(0,max(conTab_FCs_To$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_cowplot() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,size=1,hjust=1),
        axis.text.y = element_text(color=txtColsFrom,size=1)) +
  xlab("post-synaptic neuron") + ylab("pre-synaptic neuron")

offset <- 0.5
tpsFrom <- conTab_FCs_To$type.from %>% unique() %>% sort()
idsFrom <- conTab_FCs_To$id.from %>% unique() %>% sort()
for (t in 1:length(tpsFrom)){
  offset <- offset + length(which(grepl(tpsFrom[t],idsFrom)))
  plt_conTab_FCs_To <- plt_conTab_FCs_To + geom_hline(yintercept = offset)
}

offset <- 0.5
tpsTo <- conTab_FCs_To %>% filter(!grepl("FC1",type.to)) %>% select(type.to) %>% unlist() %>% unique() %>% sort()
idsTo <- conTab_FCs_To$id.to %>% unique() %>% sort()
for (t in 1:length(tpsTo)){
  offset <- offset + length(which(grepl(tpsTo[t],idsTo)))
  plt_conTab_FCs_To <- plt_conTab_FCs_To + geom_vline(xintercept = offset)
}

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_6_ColNronNetwork\\FCClustTo.pdf")
print(plt_conTab_FCs_To)
dev.off()
```

Rename the neurons according to their groups and plot their connectivity matrices
```{r}
conTab_FCs_From$type.to <- lapply(conTab_FCs_From$id.to, function(i)
  paste("FC1", letters[GpDat$group[which(GpDat$name == i)]], sep='_')) %>%
  unlist() %>% as.character()
conTab_FCs_From$name.to <- lapply(seq(1:nrow(conTab_FCs_From)), function(n)
  gsub("FC1",conTab_FCs_From$type.to[n],conTab_FCs_From$name.to[n])) %>%
  unlist() %>% as.character()
conTab_FCs_From$id.to <- FBRename(conTab_FCs_From$name.to,conTab_FCs_From$to)

conTab_FCs_From$type.from[which(conTab_FCs_From$type.from == "FC1")] <- lapply(conTab_FCs_From$id.from[which(conTab_FCs_From$type.from == "FC1")], function(i)
  paste("FC1",letters[GpDat$group[which(GpDat$name == i)]],sep='_')) %>% 
  unlist() %>% as.character()
conTab_FCs_From$name.from[which(grepl("FC1",conTab_FCs_From$type.from))] <- lapply(which(grepl("FC1",conTab_FCs_From$type.from)), function(n)
  gsub("FC1",conTab_FCs_From$type.from[n],conTab_FCs_From$name.from[n])) %>%
  unlist() %>% as.character()
conTab_FCs_From$id.from <- FBRename(conTab_FCs_From$name.from,conTab_FCs_From$from)

txtLabsTo <- conTab_FCs_From$id.to %>% unique() %>% sort()
txtColsTo <- lapply(txtLabsTo, function(t) FCCols[which(grepl(substring(t,1,5),FCTypes))]) %>% unlist()

plt_conTab_FCs_From <- ggplot(conTab_FCs_From %>% filter(!grepl("FC1",type.from))) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(conTab_FCs_From$weightRelative),
                       limits=c(0,max(conTab_FCs_From$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_cowplot() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,
                                   color = txtColsTo,
                                   size = 1,
                                   hjust = 1),
        axis.text.y = element_text(size=1)) +
  xlab("post-synaptic neuron") + ylab("pre-synaptic neuron")

offset <- 0.5
tpsFrom <- conTab_FCs_From %>% filter(!grepl("FC1",type.from)) %>% select(type.from) %>% unlist() %>% unique() %>% sort()
idsFrom <- conTab_FCs_From$id.from %>% unique() %>% sort()
for (t in 1:length(tpsFrom)){
  offset <- offset + length(which(grepl(tpsFrom[t],idsFrom)))
  plt_conTab_FCs_From <- plt_conTab_FCs_From + geom_hline(yintercept = offset)
}

offset <- 0.5
tpsTo <- conTab_FCs_From$type.to %>% unique() %>% sort()
idsTo <- conTab_FCs_From$id.to %>% unique() %>% sort()
for (t in 1:length(tpsTo)){
  offset <- offset + length(which(grepl(tpsTo[t],idsTo)))
  plt_conTab_FCs_From <- plt_conTab_FCs_From + geom_vline(xintercept = offset)
}

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_6_ColNronNetwork\\FCClustFrom.pdf")
print(plt_conTab_FCs_From)
dev.off()
```

Plot FC to FC connections
```{r}
conTab_FC_To_FC <- conTab_FCs_From %>% filter(grepl("FC1",type.from))

txtLabsTo <- conTab_FC_To_FC$id.to %>% unique() %>% sort()
txtColsTo <- lapply(txtLabsTo, function(t) FCCols[which(grepl(substring(t,1,5),FCTypes))]) %>% unlist()
txtLabsFrom <- conTab_FC_To_FC$id.from %>% unique() %>% sort()
txtColsFrom <- lapply(txtLabsFrom, function(t) FCCols[which(grepl(substring(t,1,5),FCTypes))]) %>% unlist()

plt_conTab_FC_To_FC <- ggplot(conTab_FC_To_FC) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(conTab_FC_To_FC$weightRelative),
                       limits=c(0,max(conTab_FC_To_FC$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_cowplot() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,
                                   color = txtColsTo,
                                   size = 1,
                                   hjust = 1),
        axis.text.y = element_text(color = txtColsFrom,
                                   size=1)) +
  xlab("post-synaptic neuron") + ylab("pre-synaptic neuron")

offset <- 0.5
tpsFrom <- conTab_FC_To_FC$type.from %>% unique() %>% sort()
idsFrom <- conTab_FC_To_FC$id.from %>% unique() %>% sort()
for (t in 1:length(tpsFrom)){
  offset <- offset + length(which(grepl(tpsFrom[t],idsFrom)))
  plt_conTab_FC_To_FC<- plt_conTab_FC_To_FC + geom_hline(yintercept = offset)
}

offset <- 0.5
tpsTo <- conTab_FC_To_FC$type.to %>% unique() %>% sort()
idsTo <- conTab_FC_To_FC$id.to %>% unique() %>% sort()
for (t in 1:length(tpsTo)){
  offset <- offset + length(which(grepl(tpsTo[t],idsTo)))
  plt_conTab_FC_To_FC <- plt_conTab_FC_To_FC + geom_vline(xintercept = offset)
}

pdf("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_6_ColNronNetwork\\FCClustSelf.pdf")
print(plt_conTab_FC_To_FC)
dev.off()
```

Come up with new type and name for each FC1 bodyid
```{r}
FCInfo <- getTypesTable(c("FC1","FC1A","FC1B","FC1C","FC1D","FC1E","FC1F"))
FCInfo$name <- gsub("\\s*\\([^\\)]+\\)","",as.character(FCInfo$name))
FCInfo$id <- FBRename(FCInfo$name,FCInfo$bodyid)
FCInfo$type <- lapply(FCInfo$id,
                      function(n) paste0("FC1",letters[GpDat$group[which(GpDat$name == n)]])) %>% unlist() %>% as.character()
FCInfo <- FCInfo %>% select(bodyid,type)

write.csv(FCInfo,"C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_6_ColNronNetwork\\FC1Types.csv")
```
