---
title: "MBON Redux"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(ggraph)
library(plotly)
library(dplyr)
library(pbapply)
library(tidygraph)
library(gridExtra)

# Go to the neurpintR-notebooks directory before loading these functions
source("visualizeConnectivityTables.R")
source("neuprintQueryUtils.R")
source("R/table2ggraphUtils.R")
source("InputOutputByTypeUtils.R")
source("R/rois.R")
source("R/supertypeUtils.R")
source("colorCodeLookup.R")
source("pathways.R")
source("inputOutputRegionsVis.R")
source("GetNeuronsInRoi.R")
source("FBNetworkVisUtils.R")

options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose save/plot directories
```{r}
# Directory to save data to.
SaveDir = "/Users/danc/Dropbox (HHMI)/WorkDrop/Data/FIBSEM_Analysis"

# Directory to save plots to.
PlotDir = "/Users/danc/Dropbox (HHMI)/WorkDrop/Data/FIBSEM_Analysis"
```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint
```{r}
# neuprint_login()
neuprint_login(config=httr::set_config(httr::config(ssl_verifypeer = 0L)))
```

### Pulling neurons postsynaptic to MBONs
```{r}
MBON_Names <- neuprint_search("MBON.*")
# Find the postsynaptic partners of all MBONs
MBON_PostConnections <- getConnectionTable(MBON_Names,synapseType = "POST") ## Keeping the default threshold (3)
```

### Selecting CX types as those present in Shin-ya's list.
```{r}
CXTypes <- supertype(read_csv("/Users/danc/Dropbox (HHMI)/WorkDrop/Manuscripts/FIBSEM CX Paper Jan 2020/CX-cell-types042020") %>% rename(databaseType=n.type))
MBONCXTargetsL <- unique(MBON_PostConnections$type.to)[unique(MBON_PostConnections$type.to) %in% CXTypes$databaseType]
MBONCXTargets <- getTypesTable(MBONCXTargetsL)
```

### Creating a relatively high level ROI set
```{r}
roisH <- getRoiTree()
roiSelection <- selectRoiSet(roisH,default_level=1,exceptions=list("CX"=2))
```

### Find secondary targets of MBONs
```{r}
# Find the postsynaptic partners of all MBON targets
MBON_2ndaryPostConnections <- getConnectionTable(MBON_PostConnections$to,synapseType = "POST") ## Keeping the default threshold (3)
# head(MBON_2ndaryPostConnections)
```

```{r}
# Find the MBON secondary targets in the CX
MBONCX2ndaryTargetsL <- unique(MBON_2ndaryPostConnections$type.to)[unique(MBON_2ndaryPostConnections$type.to) %in% CXTypes$databaseType]
MBONCX2ndaryTargets <- getTypesTable(MBONCX2ndaryTargetsL)
```

### Creating neuron bags of MBON primary and secondary CX targets
```{r}
MBONTargetBag <- buildInputsOutputsByType(MBONCXTargets,slctROI=unique(roiSelection$roi))
MBON2ndaryTargetBag <- buildInputsOutputsByType(MBONCX2ndaryTargets,slctROI=unique(roiSelection$roi))
```

### Separating left and right neurons in there as some tangential input regions might be cut on the left.
```{r}
MBONTargetBagLat <- lateralizeInputOutputList(MBONTargetBag)
MBON2ndaryTargetBagLat <- lateralizeInputOutputList(MBON2ndaryTargetBag)
```

### Isolating the MBON primary and secondary inputs to right side neurons in there
```{r}
MBONTargetInp <- MBONTargetBagLat$inputs %>% filter(startsWith(type.from,"MBON")& grepl("_R",type.to))
MBON2ndaryTargetInp <- MBON2ndaryTargetBagLat$inputs %>% filter(grepl("_R",type.to))
```


```{r}
MBON2ndaryCXTargetTypes <- unique(as.vector(MBON2ndaryTargetInp$databaseType.to))


```



### Combine all input regions into one (to get a "more fair" relative weight). Add a variable, totalMBContribution, that summarize how much of the total input the MBONs contribute to, and use it to sort the CX types.
```{r}
MBONTargetInputCombined <- combineRois(MBONTargetBagLat,unique(MBONTargetInp$roi),newRoi="MBON outputs")
MBONTargetInpC <- MBONTargetInputCombined$inputs %>% filter(startsWith(type.from,"MBON") & grepl("_R",type.to)) %>% 
  group_by(roi,type.to) %>% mutate(totalMBContribution = sum(weightRelative)) %>% 
                            ungroup() %>%
                                     arrange(desc(totalMBContribution))  %>%
                                     mutate(type.to = factor(type.to,levels=unique(type.to)))## Filter MBON to right CX neurons (some of the left ones can be cut)

plotConnMat_MBON_CX_Romain <- plotConnectivityMatrix(MBONTargetInpC,byGroup="type")
print(plotConnMat_MBON_CX_Romain)
ggsave("MBON_CX_ConnectionsByType_weightRelative_Romain.eps", plot=plotConnMat_MBON_CX_Romain, device="eps", path=PlotDir, scale=1, 
       width=11, height=8, units="in", dpi=300, limitsize=TRUE)

inputProportions <- ggplot(MBONTargetInpC,aes(x=type.to)) + geom_col(aes(y=weightRelative,fill=type.from)) + scale_fill_manual(values=typesPalette(unique(MBONTargetInpC$type.from)),name="MBON types",guide=guide_legend(ncol=2)) + theme_classic()  + theme(axis.text.x = element_text(angle = 90)) + labs(y="Relative weight in input regions",x="Type")
print(inputProportions)
ggsave("CXfromMBON_InputProportionsByType_weightRelative_Romain.eps", plot=inputProportions, device="eps", path=PlotDir, scale=1, 
       width=11, height=8, units="in", dpi=300, limitsize=TRUE)
```


```{r}
### Pull significant MBONTargetInpC connections based on "totalMBContribution"
# Find Strongly connected MBON targets in the CX
StrongMBONTargetInpC <- MBONTargetInpC  %>% filter(totalMBContribution > 0.05)
StrongMBON2CX_TargetsType <- unique(as.vector(StrongMBONTargetInpC$databaseType.to))
StrongMBON2CX_TargetNeurons <- getTypesTable(StrongMBON2CX_TargetsType)
# head(StrongMBON2CX_TargetNeurons)
```

```{r}
### Plot the pathways from MBONs to CX
# Set up the layout for the pathway plot
types <- unique(c(unique(as.vector(StrongMBONTargetInpC$type.from)),unique(as.vector(StrongMBONTargetInpC$type.to))))
numFrom <- length(unique(as.vector(StrongMBONTargetInpC$type.from)))
numTo <- length(unique(as.vector(StrongMBONTargetInpC$type.to)))
xyLookup = data.frame(type = types, x = c(rep(-1,times = numFrom),rep(0,times = numTo)), y = c(seq(-1,1,length.out = numFrom), seq(-1,1,length.out = numTo)))

# Graph the TypeToType ConnTable using the lookupTable
StrongMBONTargetInpCdf <- StrongMBONTargetInpC
StrongMBONTargetInpCdf$type.to <- as.vector(StrongMBONTargetInpCdf$type.to)
gg_MBON2TargetTab <- graphConTab(StrongMBONTargetInpCdf,xyLookup,FALSE,TRUE)
gg_MBON2TargetTab <- gg_MBON2TargetTab + scale_y_reverse()
print(gg_MBON2TargetTab)
ggsave("StrongMBON2CXtargetsTab.svg", plot=gg_MBON2TargetTab, device="svg", path=PlotDir, scale=1, 
       width=11, height=8, units="in", dpi=300, limitsize=TRUE)
```
Notes: 
1) MBON05 has no branches ipsilateral to the cell body, only contralateral. FB4R only has dendrites ipsilateral to cell body. Therefore, only MBON05_L (not MBON05_R) makes synapses onto FB4R_R.
2) MBON09 has bilateral branches, but only makes contact with ipsilateral FB4R, i.e., MBON09_R onto FB4R_R.
3) MBON21 has bilateral branches, and synapses onto FB4R bilaterally.
4) MBON04 has bilateral branches, but more contralaterally relative to the name (although the *_L cell body is just off to the midline on the right side).
5) MBON12R and MBON13R only have branches ipsilateral to the cell body.
6) MBON03 has bilateral branches, but more contralaterally relative to the name.
7) MBON22 has ipsilateral branches in the calyz and bilateral branches in SIP/SMP.
8) MBON30 has bilateral branches, but more ipsilateral to the cell body.

```{r}
# Find the postsynaptic partners of StrongMBON2CX_TargetNeurons
StrongMBON2CX_TargetsCnctTable <- getConnectionTable(StrongMBON2CX_TargetNeurons,synapseType="POST")
# head(StrongMBON2CX_TargetsCnctTable)
StrongMBON2CXTargetsToPostInFB <- getConnectionTable_forSubset(StrongMBON2CX_TargetNeurons$bodyid, StrongMBON2CX_TargetsCnctTable$to,"FB")
StrongMBON2CXTargetsToPostInFB_Type2TypeTab <- getTypeToTypeTable(StrongMBON2CXTargetsToPostInFB)
# StrongMBON2CXTargetsToPostInFB_Type2TypeTab <- StrongMBON2CXTargetsToPostInFB_Type2TypeTab %>% arrange(type.from %in% StrongMBON2CX_TargetsType)

# Filter the table by weightRelative
# StrongMBON2CXTargetsToPostInFB_Type2TypeTab <- StrongMBON2CXTargetsToPostInFB_Type2TypeTab  %>% filter(weightRelative > 0.05)

# Plot and save the StrongMBON2CXTargetsToPostInFB_Type2TypeTab based on the connectionMeasure of "weightRelative"
p4 <- plotConnectivityMatrix(StrongMBON2CXTargetsToPostInFB_Type2TypeTab,byGroup="type",connectionMeasure="weightRelative")
print(p4)
ggsave("StrongMBON2CXTargetsToPostInFB_Type2TypeTable_weightRelative.eps", plot=p4, device="eps", path=PlotDir, scale=1, 
       width=11, height=8, units="in", dpi=300, limitsize=TRUE)
```

########### ran well up to here ################

### put a break here

### Find connections among strong direct MBON targets in CX
```{r}
# StrongMBON2CXTargetsToSelfInFB_Type2TypeTab <- StrongMBON2CXTargetsToPostInFB_Type2TypeTab %>% filter(type.to %in% type.from)
# Plot the mutual connections among these
```

### Plot the pathways from strong direct MBON->CX targets to secondary CX targets
```{r}
# Set up the layout for the pathway plot
types <- unique(c(unique(as.vector(StrongMBON2CXTargetsToPostInFB_Type2TypeTab$type.from)),unique(as.vector(StrongMBON2CXTargetsToPostInFB_Type2TypeTab$type.to))))
numTypes <- length(types)
numFrom <- length(unique(as.vector(StrongMBON2CXTargetsToPostInFB_Type2TypeTab$type.from)))
numTo <- length(unique(as.vector(StrongMBON2CXTargetsToPostInFB_Type2TypeTab$type.to)))

# Arrange the primary MBON->CX targets in a circle
angs <- seq(-pi,pi,length.out = numFrom + 1)
angs <- angs[1:(length(angs)-1)]
xFrom <- sin(angs) - 1
yFrom <- cos(angs)

# xyLookup = data.frame(type = types, x = c(rep(-1,times = numFrom),rep(0,times = numTypes-numFrom)), 
#                      y = c(seq(-1,1,length.out = numFrom), seq(-1,1,length.out = numTypes-numFrom)))

xyLookup = data.frame(type = types, x = c(xFrom,rep(1,times = numTypes-numFrom)), 
                      y = c(yFrom, seq(-1,1,length.out = numTypes-numFrom)))

# Graph the TypeToType ConnTable using the xyLookup lookupTable
gg_MBON1stTo2ndaryTargetTab <- graphConTab(StrongMBON2CXTargetsToPostInFB_Type2TypeTab,xyLookup,FALSE,TRUE)
gg_MBON1stTo2ndaryTargetTab <- gg_MBON1stTo2ndaryTargetTab + scale_y_reverse()
print(gg_MBON1stTo2ndaryTargetTab)
ggsave("MBON1stTo2ndaryTargetTab.svg", plot=gg_MBON1stTo2ndaryTargetTab, device="svg", path=PlotDir, scale=1, 
       width=11, height=8, units="in", dpi=300, limitsize=TRUE)
```





```{r}



























Focus on the FB now (the only exception is LCNp which can probably be treated separately) and try to compute a "pathway weight" per CX target type. For every connection, `MBONInfluence` is the product of the relative weight with the total contribution of MBONs to the presynaptic neuron. `pathwaysWeight` is the sum of that over a target type (basically the sum of all its indirect MBON influences). 

***Should also find pathways through middle neurons outside of the CX. 
```{r}
MBONTargetFBOut <- MBONTargetBagLat$outputs %>% filter(roi=="FB" & type.from %in% MBONTargetInpC$type.to) %>% 
  mutate(MBONInfluence = MBONTargetInpC$totalMBContribution[match(type.from,MBONTargetInpC$type.to)]*weightRelative) %>% group_by(type.to) %>% mutate(pathwaysWeight = sum(MBONInfluence)) %>% ungroup()
  
```
Looking at this table and sorting it according to various ways, the things that first pops out is that it's mostly a FB tangential network (meaning most FB tangential neuron targets in the FB are other FB tangential neurons, I guess something reminiscent of the ring neurons). So we'd need a way to wean this recurrence in the way we consider which parts of the network are influenced by the MBONs.
```{r}
MBONTargetFBOutSummary <- MBONTargetFBOut %>% group_by(type.to) %>% summarise(pathwaysWeight = pathwaysWeight[1])
```

Considering FB4R separately
```{r}
MBONTargetFB4R <- MBONTargetFBOut %>% filter(type.from == "FB4R_R") %>% group_by(type.to) %>% summarise(pathwaysWeight = pathwaysWeight[1])
```

Suggestion: redo that, but study the pool of neurons influenced by a single MBON type at a time.

Other axis to explore: FB tangential inhomogeneous inputs onto columnar neurons.


