---
title: "MB-CX connections"
output: html_notebook
---

### Load the libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(plotly)
library(dplyr)
source("/Users/danc/Repos/neuprintR-notebooks/pathways.R")
source("/Users/danc/Repos/neuprintR-notebooks/visualizeConnectivityTables.R")
source("/Users/danc/Repos/neuprintR-notebooks/neuprintQueryUtils.R")
source("/Users/danc/Repos/neuprintR-notebooks/inputOutputRegionsVis.R")
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose save/plot directories
```{r}
# Directory to save data to.
SaveDir="/Users/danc/Dropbox (HHMI)/WorkDrop/Data/FIBSEM_Analysis"

# Directory to save plots to.
PlotDir="/Users/danc/Dropbox (HHMI)/WorkDrop/Data/FIBSEM_Analysis"
```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint
```{r}
neuprint_login()
```

### Get CX neurons with inputs from MB directly
```{r}
MBTypes <- getTypesInRoi("MB")
```


### Get CX neurons with outputs in MB directly


### Get the MBONs
```{r}
# Find all MBONs
MBON_Names <- neuprint_search("MBON.*")
head(MBON_Names)
```

### Find who the MBONs talk to
```{r}
# Find the postsynaptic partners of all MBONs
MBON_PostConnections <- getConnectionTable(MBON_Names,synapseType = "POST",synThresh=3)
head(MBON_PostConnections)
```

### Among these, find who innervate the CX
```{r}
# Find the MBON postsynaptic partners that innervate the FB
outputROIinfo <- neuprint_get_roiInfo(MBON_PostConnections$to)
FBOutputs <- outputROIinfo  %>% filter(FB.pre +FB.post > 30)
MBONFbConnections <- MBON_PostConnections %>% filter(to %in% FBOutputs$bodyid)
```

### Plot the connectivity matrix
```{r}
MBONFbConnections %>% plotConnectivityMatrix
```

### Make the TypeToType connection table from MBON to CX
```{r}
MBONFbTypeToTypeConnections <- getTypeToTypeTable(MBONFbConnections)
head(MBONFbTypeToTypeConnections)
```

### Plot the TypeToType connetivity matrix
```{r}
plotConnectivityMatrix(MBONFbTypeToTypeConnections,byGroup = "type")
```


### Make type-by-type synapse heat map in the CX


### Get the FB neuron types
```{r}

```

### Find all connections between all MBONs and FB neurons
