---
title: "Example for getting meshes and morphos in 2D"
output: html_notebook
---


# Command to clear environment is: rm(list = ls(all.names = TRUE))
# Load libraries
```{r message=FALSE, warning=FALSE}

library(nat)
library(neuprintr)
library(tidyverse)
library(reshape2)
library(plotly)
options(nat.plotengine = 'rgl')

```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="EB"  

# Directory to save data to.
SaveDir="Z:/Cx_Connectome/BradData/EB_Analysis/"

# Directory to save plots to.
PlotDir="Z:/Cx_Connectome/BradData/EB_Analysis/RingNeuronSynapseLocs/"

```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}
source("GetNeuronsInRoi.R")
```


### Get neurons in the ROI
```{r}

NamedBodies = Get_AllNeurons_InRoi(ROI, FALSE)
NamedBodies =  mutate(NamedBodies, cropped = neuprint_get_meta(bodyid)$cropped)

```


### Get synapses and morphologies for a few example ring neurons (R5)
```{r}

# Get body IDs for R5
UniqueNamedBodies=as.character(unique(NamedBodies$bodytype))
RingNeuronTypes=UniqueNamedBodies[startsWith(unlist(UniqueNamedBodies), "R5")]
RingNeuronBodies=filter(NamedBodies, startsWith(as.character(unlist(NamedBodies$bodytype)), "R5") )

# Get all synapses for the ring neurons
for (typeNow in 1:length(RingNeuronTypes)){
  # Get BU synapses
  RingNeuronSyns = NamedBodies[ which(unlist(NamedBodies$bodytype) == RingNeuronTypes[typeNow]),]$bodyid %>% neuprint_get_synapses()
  RingNeuronSyns <-  RingNeuronSyns %>% mutate(name=as.character(RingNeuronTypes[typeNow]))%>%     mutate(x=as.numeric(x),y=as.numeric(y),z=as.numeric(z),prepost=as.logical(prepost))
  if (typeNow==1){
    RingNeuronSynsAll= RingNeuronSyns
  }else{
    RingNeuronSynsAll <- rbind(RingNeuronSynsAll,RingNeuronSyns)
  }
  
}
remove(RingNeuronSyns)

# Get neuron morphologies
MorphFile=paste(SaveDir,"R5_RingNeuronMorpho.rds",sep="")
if (file.exists(MorphFile)){
  RingNeuronMorpho=readRDS(MorphFile)
} else {
  RingNeuronMorpho = neuprint_read_neurons(RingNeuronBodies$bodyid)
  saveRDS(RingNeuronMorpho, file = MorphFile)
}


```


# See if we can get ROI meshes and neuron morphologies in 2D
```{r}

# Load new library. Might have to install.packages("car")
library(car)

# Get meshes for ROIs
ebMesh = neuprint_ROI_mesh("EB")
RbuMesh = neuprint_ROI_mesh("BU(R)")

# Get X,Y,Z coordinates from meshes
EBData=data.frame(x=ebMesh$vb[1,], y=ebMesh$vb[2,],z=ebMesh$vb[3,],name="EB")
BUData=data.frame(x=RbuMesh$vb[1,], y=RbuMesh$vb[2,],z=RbuMesh$vb[3,],name="BU(R)")


# Put all data into a single data frame
AllData=data.frame
AllData=rbind(EBData, BUData)
AllData=rbind(AllData, RingNeuronSynsAll[,c(3,4,5,10)])


# Plot data in 3D to make sure it overlaps. Doesn't the EB look too tall?
nclear3d()
plot3d(EBData[c('x','y','z')], col='black', alpha=0.05 ,	forceClipregion = FALSE)
plot3d(BUData[c('x','y','z')], col='black', alpha=0.05 ,	add=TRUE,forceClipregion = FALSE)
plot3d(RingNeuronSynsAll[c('x','y','z')], col='violet', alpha=0.4, add=TRUE,	forceClipregion = FALSE)


# plot data in 2D to make sure it overlaps
ggplot(AllData, aes(x=x, y=-z, color=name)) + geom_point()
ggplot(AllData, aes(x=x, y=y, color=name)) + geom_point()






```