---
title: "Notebook analyzing the input and output pathways of the NO at the ROI level"
output:
  html_document:
    df_print: paged
---

### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Command to load Renviron file is usethis::edit_r_environ()
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(plotly)
library(dplyr)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="NO"  

# Directory to save data to.
SaveDir="Z:/Cx_Connectome/BradData/NO_Analysis/"

# Directory to save plots to.
PlotDir="Z:/Cx_Connectome/BradData/NO_Analysis/"

```

### Create save/plot directory if they dont exists yet
```{r}
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}
source("inputOutputRegionsVis.r")
source("GetNeuronsInRoi.r")
```

### Get neuprint ROIs 
```{r}
rois = neuprint_ROIs()
heir=neuprint_ROI_hierarchy()
```

### Get neurons in the ROI
```{r}
NO_NamedBodies = Get_AllNeurons_InRoi("NO", TRUE)
NO1_NamedBodies = Get_AllNeurons_InRoi("NO1", TRUE)
NO2_NamedBodies = Get_AllNeurons_InRoi("NO2", TRUE)
NO3_NamedBodies = Get_AllNeurons_InRoi("NO3", TRUE)
```



### Threshold neurons (need to agree on criteria and clean up code)
```{r}

PreMaxThresh=10
PostMaxThresh=10

# NO
Output <-  SynapseStats_And_Threshold(NO_NamedBodies, SaveDir, PreMaxThresh, PostMaxThresh)
list2env(Output ,.GlobalEnv)
NO_NamedBodies=NamedBodies
rm(Output, NamedBodies)

# NO1
Output <-  SynapseStats_And_Threshold(NO1_NamedBodies, SaveDir, PreMaxThresh, PostMaxThresh)
list2env(Output ,.GlobalEnv)
NO1_NamedBodies=NamedBodies
rm(Output, NamedBodies)

# NO2
Output <-  SynapseStats_And_Threshold(NO2_NamedBodies, SaveDir, PreMaxThresh, PostMaxThresh)
list2env(Output ,.GlobalEnv)
NO2_NamedBodies=NamedBodies
rm(Output, NamedBodies)

# NO3
Output <-  SynapseStats_And_Threshold(NO3_NamedBodies, SaveDir, PreMaxThresh, PostMaxThresh)
list2env(Output ,.GlobalEnv)
NO3_NamedBodies=NamedBodies
rm(Output, NamedBodies)


```

### Compute type averages of named bodies to get an idea of where threshold on relative synapse counts should be
```{r}

# NO
NO_NamedBodies_TypeAverage= aggregate(NO_NamedBodies[, 6:17], list(NO_NamedBodies$bodytype), mean)
colnames(NO_NamedBodies_TypeAverage)[1]="bodytype"

#NO1
NO1_NamedBodies_TypeAverage=aggregate(NO1_NamedBodies[, 6:17], list(NO1_NamedBodies$bodytype), mean)
colnames(NO1_NamedBodies_TypeAverage)[1]="bodytype"

#NO2
NO2_NamedBodies_TypeAverage=aggregate(NO2_NamedBodies[, 6:17], list(NO2_NamedBodies$bodytype), mean)
colnames(NO2_NamedBodies_TypeAverage)[1]="bodytype"

#NO3
NO3_NamedBodies_TypeAverage=aggregate(NO3_NamedBodies[, 6:17], list(NO3_NamedBodies$bodytype), mean)
colnames(NO3_NamedBodies_TypeAverage)[1]="bodytype"

```



### Get the number of synapses in each ROI for individual neurons and individual neuron types
```{r message=FALSE, warning=FALSE}

minSynapses = 30

# NO
Output=InputOutput_ROI_PerNeuron(NO_NamedBodies, minSynapses)
list2env(Output ,.GlobalEnv)
NO_roi_Connect_bytype_df=roi_Connect_bytype_df
NO_roi_Connect_df=roi_Connect_df
rm(Output, roi_Connect_bytype_df, roi_Connect_df)

# NO1
Output=InputOutput_ROI_PerNeuron(NO1_NamedBodies, minSynapses)
list2env(Output ,.GlobalEnv)
NO1_roi_Connect_bytype_df=roi_Connect_bytype_df
NO1_roi_Connect_df=roi_Connect_df
rm(Output, roi_Connect_bytype_df, roi_Connect_df)

# NO2
Output=InputOutput_ROI_PerNeuron(NO2_NamedBodies, minSynapses)
list2env(Output ,.GlobalEnv)
NO2_roi_Connect_bytype_df=roi_Connect_bytype_df
NO2_roi_Connect_df=roi_Connect_df
rm(Output, roi_Connect_bytype_df, roi_Connect_df)

# NO3
Output=InputOutput_ROI_PerNeuron(NO3_NamedBodies, minSynapses)
list2env(Output ,.GlobalEnv)
NO3_roi_Connect_bytype_df=roi_Connect_bytype_df
NO3_roi_Connect_df=roi_Connect_df
rm(Output, roi_Connect_bytype_df, roi_Connect_df)

```



### Add ROI and neuron type names that will be displayed on plots
```{r}

# NO
NO_roi_Connect_bytype_df$roi_names = paste(NO_roi_Connect_bytype_df$roi, '(', NO_roi_Connect_bytype_df$roi_hemi, ')', sep="")
NO_roi_Connect_bytype_df$type_name = paste(NO_roi_Connect_bytype_df$type, '(', NO_roi_Connect_bytype_df$neuron_hemi, ')', sep="")

# NO1
NO1_roi_Connect_bytype_df$roi_names = paste(NO1_roi_Connect_bytype_df$roi, '(', NO1_roi_Connect_bytype_df$roi_hemi, ')', sep="")
NO1_roi_Connect_bytype_df$type_name = paste(NO1_roi_Connect_bytype_df$type, '(', NO1_roi_Connect_bytype_df$neuron_hemi, ')', sep="")

# NO2
NO2_roi_Connect_bytype_df$roi_names = paste(NO2_roi_Connect_bytype_df$roi, '(', NO2_roi_Connect_bytype_df$roi_hemi, ')', sep="")
NO2_roi_Connect_bytype_df$type_name = paste(NO2_roi_Connect_bytype_df$type, '(', NO2_roi_Connect_bytype_df$neuron_hemi, ')', sep="")

# NO3
NO3_roi_Connect_bytype_df$roi_names = paste(NO3_roi_Connect_bytype_df$roi, '(', NO3_roi_Connect_bytype_df$roi_hemi, ')', sep="")
NO3_roi_Connect_bytype_df$type_name = paste(NO3_roi_Connect_bytype_df$type, '(', NO3_roi_Connect_bytype_df$neuron_hemi, ')', sep="")

  
```



## Make plot of ALL neurons in NO, NO1, NO2, and NO3, before thresholding
```{r}


# Plot all of the ROIs (and sub ROIs) that all NO neurons innervate
p0<-ggplot(NO_roi_Connect_bytype_df, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL NO Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "ALL_NO_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


# Plot all of the ROIs (and sub ROIs) that all NO1 neurons innervate
p0<-ggplot(NO1_roi_Connect_bytype_df, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL NO1 Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "ALL_NO1_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


# Plot all of the ROIs (and sub ROIs) that all NO2 neurons innervate
p0<-ggplot(NO2_roi_Connect_bytype_df, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL NO2 Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "ALL_NO2_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


# Plot all of the ROIs (and sub ROIs) that all NO3 neurons innervate
p0<-ggplot(NO3_roi_Connect_bytype_df, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("ALL NO3 Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "ALL_NO3_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


```



### Threshold relative synapse numbers and remove neurons that don't actually belong
```{r}

RelSynThresh=0.07

# Get types based on relative synapse counts (This should be be moved to SynapseStats_And_Threshold)
NO_Type=NO_NamedBodies_TypeAverage$bodytype[NO_NamedBodies_TypeAverage$PrePost_Relative>RelSynThresh]
NO1_Type=NO1_NamedBodies_TypeAverage$bodytype[NO1_NamedBodies_TypeAverage$PrePost_Relative>RelSynThresh]
NO2_Type=NO2_NamedBodies_TypeAverage$bodytype[NO2_NamedBodies_TypeAverage$PrePost_Relative>RelSynThresh]
NO3_Type=NO3_NamedBodies_TypeAverage$bodytype[NO3_NamedBodies_TypeAverage$PrePost_Relative>RelSynThresh]

# Threshold NO
NO_ExcludedTypes=unique(filter(NO_roi_Connect_bytype_df, !(type %in% NO_Type) )$type)
NO_roi_Connect_bytype_dfThresh=filter(NO_roi_Connect_bytype_df, type %in% NO_Type)

# Threshold NO1
NO1_ExcludedTypes=unique(filter(NO1_roi_Connect_bytype_df, !(type %in% NO1_Type) )$type)
NO1_roi_Connect_bytype_dfThresh=filter(NO1_roi_Connect_bytype_df, type %in% NO1_Type)

# Threshold NO2
NO2_ExcludedTypes=unique(filter(NO2_roi_Connect_bytype_df, !(type %in% NO2_Type) )$type)
NO2_roi_Connect_bytype_dfThresh=filter(NO2_roi_Connect_bytype_df, type %in% NO2_Type)

# Threshold NO3
NO3_ExcludedTypes=unique(filter(NO3_roi_Connect_bytype_df, !(type %in% NO3_Type) )$type)
NO3_roi_Connect_bytype_dfThresh=filter(NO3_roi_Connect_bytype_df, type %in% NO3_Type)



```



## Make plot of THRESHOLDED neurons in NO, NO1, NO2, and NO3
```{r}

# Plot all of the ROIs (and sub ROIs) that all NO neurons innervate
p0<-ggplot(NO_roi_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Thresh NO Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "Thresh_NO_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


# Plot all of the ROIs (and sub ROIs) that all NO1 neurons innervate
p0<-ggplot(NO1_roi_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Thresh NO1 Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "Thresh_NO1_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


# Plot all of the ROIs (and sub ROIs) that all NO2 neurons innervate
p0<-ggplot(NO2_roi_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Thresh NO2 Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "Thresh_NO2_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


# Plot all of the ROIs (and sub ROIs) that all NO3 neurons innervate
p0<-ggplot(NO3_roi_Connect_bytype_dfThresh, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Thresh NO3 Neuron Input/Output ROIs")
print(p0)
ggsave(paste(PlotDir, "Thresh_NO3_","inputOutputRegions_perType.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 20, height = 10, units ="in", dpi = 600, limitsize = TRUE)


```


### The sub ROIs do not seem to do a great job of segregating the NO neurons, since most neurons have synapses in multiple NOs
### So, plot the NO comparements each cell types innervates
```{r}

# get just the NO compartments
JustNoROIs=subset(NO_roi_Connect_bytype_dfThresh, startsWith(roi,c("NO1","NO2","NO3")) )

# Plot all of the ROIs (and sub ROIs) that all NO neurons innervate
p0<-ggplot(JustNoROIs, aes(x=roi_names, y=type_name, size=count)) + geom_point(aes(color=roi)) +
  facet_grid(cols=vars(prepost)) +  theme_bw() + theme(axis.text.x = element_text(angle = 90))  + guides(fill=FALSE) +
  ggtitle("Thresh NO Neuron Input/Output NO sub ROIs")
print(p0)
ggsave(paste(PlotDir, "Thresh_NO_","subROIs.png",sep=""), plot = p0, device='png', scale = 1, 
       width = 10, height = 5, units ="in", dpi = 600, limitsize = TRUE)


```

































