---
title: "Visualization of shared input or output"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(plotly)
library(paletteer)
library(igraph)
library(neuprintrExtra)
library(gridExtra)
options(nat.plotengine = 'rgl')

```

```{r}
source("R/connectivityMatricesTools.R")
source("R/visualizeConnectivityTables.R")

getBodyIdsForList = function (neuronList,prefix="",postfix=".*",...){
  #' Get one dataframe of bodyIDs for all search strings in neuronList
  #' @param neuronList: A list of search strings to be passed.
  #' @param prefix: String to be added before each query (default "")
  #' @param postfix: String to be added after each query (default ".*")
  #' @param ...: Parameters to be passed to neuprint_search. Note that meta=FALSE won't work for now.
  #' @return A data frame of metadata for the results of all the queries
  #' @examples
  #' \dontrun{
  #' # Both will return the same
  #' getBodyIdsForList(c("PFL1","PFL2"))
  #' getBodyIdsForList(c("PFL1","PFL2"),postfix="",field="type")
  #' }
  
  neuronList <-  paste0(prefix,neuronList,postfix)
  bodiesList <- lapply(neuronList,neuprint_search,...)
  return(bind_rows(bodiesList))
}

myplot_dist <- function(dd,order=TRUE){
  ddM <- as.matrix(dd)
  if (order){
    hcl <- hclust(dd)
    ddM <- ddM[hcl$order,hcl$order]
  }
  ggplot(reshape2::melt(ddM)) + geom_tile(aes(x=Var1,y=Var2,fill=1-value)) +
    theme_classic() +
    scale_fill_gradient2(low="white", mid="grey", high="black", 
                         midpoint =0.5, limits=c(0,1), name="Similarity") +
    theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5)) + 
    xlab("") + ylab("")+coord_fixed() 
  
}
```

```{r}
neuprint_login()
```

### Select types for comparison
```{r}
myTypeList = c("GLNO","LNO1","LNO2","LNO3","LNOa", "LCNOpm","LCNOp") #paste0(c("ExR"),seq(1,8))
#c(unique(getBodyIdsForList(paste0( c("PFN"),".*"))$type),  "PEN_a.*", "PEN_b.*")
side ="_R" # "_L"#
myTypeList_lat = paste0(myTypeList, side)
#c(paste0(myTypeList, side), paste0(c("PEN_a(PEN1)", "PEN_b(PEN2)"), side))

#c("GLNO","LNO1","LNO2","LNO3","LNOa", "LCNOpm","LCNOp", "ER1_a","ER1_b","ER3a_b","ER3a_c", "ER6")
#c("ExR.*")#,"GLNO","LCNOpm","LCNOp"
#unique(getBodyIdsForList(paste0( c("ER2"),".*"))$type)

saveName = "LNO_comparison"

minWeightRel = 0.01 #used to filter connectivity tables

saveDir = "../neuprintR_analysis_plots/"
```

```{r}
myTypes_bag_full = neuronBag(myTypeList)

# Filter out neurons from left side?
splitLR = TRUE
if(splitLR){
  myTypes_bag_full = lateralize_types(myTypes_bag_full)
  }
```

### Filter neuron bag to contain only subset of types (considering lateralization)
```{r}
myTypes_bag =  filter(myTypes_bag_full, filterPartners = FALSE, type %in% myTypeList_lat)
```

### Generate list of ROIs to consider
```{r}
roiTree = getRoiTree()
slctROIs = selectRoiSet(roiTree, default_level = 2, 
                        exceptions = list("OL(R)"=1,"AL(R)"=1,"PENP"=1,"AL(L)"=1,"MB(+ACA)(R)"=1,"MB(L)"=1,
                                          "VMNP"=1,"INP"=1, "LX(R)"=3, "LX(L)"=3), exceptionLevelMatch = 1)
slctROIs = unique(slctROIs$roi)
slctROIs_r = slctROIs[!grepl("\\(L\\)",slctROIs)]
slctROIs_r
```

# Use raw inputs as few connections in non-CX ROIs are significant according to general criteria??
```{r}
myTypes_in = myTypes_bag$inputs
myTypes_out = myTypes_bag$outputs
myTypes = myTypes_bag$names
```


### Generate dataframe of inputs to types of interest
# Filter based on rois to use
```{r}
minsyn = 10

myTypes_in_filt = myTypes_in %>% filter(roi %in% slctROIs) %>%
  #filter(type.to %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.to) %>% filter(sum(weight) >= minsyn) %>% filter(weightRelative >= minWeightRel)

myTypes_in_filt = bind_cols(myTypes_in_filt, data.frame(dir = rep("in", length(myTypes_in_filt$roi))))

myTypes_out_filt = myTypes_out %>% filter(roi %in% slctROIs) %>%
  #filter(type.from %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.from) %>% filter(sum(weight) >= minsyn) %>% filter(outputContribution >= minWeightRel)

myTypes_out_filt = bind_cols(myTypes_out_filt, data.frame(dir = rep("out", length(myTypes_out_filt$roi))))
```

```{r}
#myTypes_in_filt %>% group_by(roi,  type.from,  type.to) %>% summarise(sw = sum(weight))
plotData = myTypes_in_filt %>% ungroup() %>% group_by(roi,  type.from, type.to) %>% summarise(sw = sum(weight))
ggplot(data = plotData) + 
  geom_freqpoly( aes(x=sw, color=type.to), bins=100) + xlim(0, 100) +
  facet_grid(rows = vars(roi))

plotData = myTypes_out_filt %>% ungroup() %>% group_by(roi,  type.to, type.from) %>% summarise(sw = sum(weight))
ggplot(data = plotData) + 
  geom_freqpoly( aes(x=sw, color=type.from), bins=100) + xlim(0, 100) +
  facet_grid(rows = vars(roi))
```


# Visualize in bar graph different input types
```{r}
inOutContributionDataPrep <- function(myTypes_in_filt, myTypes_out_filt,  supertypeLevel){
  inData = myTypes_in_filt %>% select(c("roi","databaseType.from","type.from", "type.to", "weightRelative","outputContribution", "dir")) %>% 
    mutate(ref = type.to, measure=weightRelative) %>% rename(databaseType=databaseType.from)
  
  outData = myTypes_out_filt %>% select(c("roi","databaseType.to","type.from", "type.to","weightRelative", "outputContribution", "dir")) %>% 
    mutate(ref = type.from, measure=outputContribution) %>% rename(databaseType=databaseType.to)
  
  if(supertypeLevel == 0){
    inData <- supertype(inData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
    
    outData <- supertype(outData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
  }else if(supertypeLevel == -1){
    inData <- supertype(inData) %>% selectSupertypeSet(default_level = 3,exceptions = list("EB Columnar"=3,"FB Columnar"=3,"FB Tangential"=3,"FB Interneuron"=3,"FB Output"=3,"Antennal lobe"=3,"LH"=3),exceptionLevelMatch = 3) 
    %>% mutate(partner = supertype, partner2=supertype2)
    
    outData <- supertype(outData) %>% selectSupertypeSet(default_level = 3,exceptions = list("EB Columnar"=3,"FB Columnar"=3,"FB Tangential"=3,"FB Interneuron"=3,"FB Output"=3,"Antennal lobe"=3,"LH"=3),exceptionLevelMatch = 3)
    %>% mutate(partner = supertype, partner2=supertype2)
  }else{
    inData = supertype(inData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
    outData = supertype(outData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
  }
  data = bind_rows(inData,outData)
  return(data)
}

```

```{r}
inOutContributionDataPrep <- function(myTypes_in_filt, myTypes_out_filt,  supertypeLevel){

  inData = myTypes_in_filt %>% select(c("roi","databaseType.from","type.from", "type.to", "weightRelative","outputContribution", "dir")) %>% mutate(ref = type.to, measure=weightRelative)
  
  outData = myTypes_out_filt %>% select(c("roi","databaseType.to","type.from", "type.to","weightRelative", "outputContribution", "dir")) %>% mutate(ref = type.from, measure=outputContribution)
  
  if(supertypeLevel == 0){
    inData <- supertype(inData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% 
      mutate(partner = supertype, partner2=supertype2)
    
    outData <- supertype(outData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>%
      mutate(partner = supertype, partner2=supertype2)
    
  }else if(supertypeLevel == -1){
    inData <- supertype(inData) %>% selectSupertypeSet(default_level = 3,exceptions = list("EB Columnar"=3,"FB Columnar"=3,"FB Tangential"=3,"FB Interneuron"=3,"FB Output"=3,"Antennal lobe"=3,"LH"=3),exceptionLevelMatch = 3) %>% 
      mutate(partner = supertype, partner2=supertype2)
    
    outData <- supertype(outData) %>% selectSupertypeSet(default_level = 3,exceptions = list("EB Columnar"=3,"FB Columnar"=3,"FB Tangential"=3,"FB Interneuron"=3,"FB Output"=3,"Antennal lobe"=3,"LH"=3),exceptionLevelMatch = 3) %>%
      mutate(partner = supertype, partner2=supertype2)
  }else{
    inData = inData %>% mutate(partner=supertype(type.from,supertypeLevel))
    outData = outData %>% mutate(partner=supertype(type.to,supertypeLevel))
  }
  data = bind_rows(inData,outData)
  return(data)
}
```


```{r}
for(st in c(0,2,3)){
  myTypes_filt = inOutContributionDataPrep(myTypes_in_filt, myTypes_out_filt,  st) %>% filter(roi %in% slctROIs_r)
  
  if(sum(is.na(myTypes_filt$partner)) > 0){
    myTypes_filt = myTypes_filt  %>% mutate(partner = coalesce(partner, "Other"))
  }
  bar = inOutContributionPlot(myTypes_filt)+ facet_grid(cols=vars(roi), rows=vars(dir), scales="free_x", space = "free")
  show(bar)
  
  ggsave(paste("inputAndOutputComposition_",saveName,"_supertype",st,'.pdf', sep=''),plot = bar, device='pdf', path = "../neuprintR_analysis_plots/",
      scale = 1, width=25, height=10, units ="cm", dpi = 600, limitsize = TRUE)
  
  #bar2 = inOutContributionPlot(myTypes_filt) + facet_grid(rows=vars(roi), cols=vars(dir))
  #show(bar2)
  
  #ggsave(paste("inputAndOutputComposition_",saveName,"_supertype",st,'_v2.pdf', sep=''),plot = bar2, device='pdf', path = "../neuprintR_analysis_plots/",
  #    scale = 1, width=15, height=33, units ="cm", dpi = 600, limitsize = TRUE)
}

```

```{r}
myTypes_filt0 = inOutContributionDataPrep(myTypes_in_filt, myTypes_out_filt,  0) %>% filter(roi %in% slctROIs_r)
```

### Compare input and outputs to these types
# select inputs to focus types in main input regions
```{r}
myROIs = unique(myTypes_filt$roi)[unique(myTypes_filt$roi)!="EB"] 
#c("PB", "EB", "NO(R)") #c("LAL(R)","WED(R)", "GNG")#
myROIsName = "allROIbutEB"#paste(myROIs, collapse = '-') #"PB_EB_NOr" #
myROIs  

```

# construct new connection table for combined ROIs
```{r}
myTypes_bag_comboRoi = combineRois(myTypes_bag, myROIs, "comboRoi")
typesInput_combiRoi = myTypes_bag_comboRoi$inputs %>% filter(type.to %in% myTypeList_lat)
typesOutput_combiRoi = myTypes_bag_comboRoi$outputs %>% filter(type.from %in% myTypeList_lat)

myTypeList_lat_in = unique(typesInput_combiRoi$type.to)
myTypeList_lat_out = unique(typesOutput_combiRoi$type.from)
```

# Connectivity matrix from neuron bag
```{r}
weightMeasure ="weightRelative" 
groupBy = "type"
cmax = max(typesInput_combiRoi$weightRelative)

conMatPlot = plotConnectivityMatrix(typesInput_combiRoi, byGroup = groupBy, weightMeasure , cmax)
conMatPlot = addMatrixPlotLabs(conMatPlot, "Inputs",  "",paste(myROIs, collapse = '-'), weightMeasure)

print(conMatPlot)

plotW = 7
plotH = 15#20

ggsave(paste("connectivityMatrix_",saveName,'_in_',myROIsName,'_', weightMeasure,'_fromNBag.pdf', sep=''), plot = conMatPlot, device='pdf', path = "../neuprintR_analysis_plots/",
  scale = 2, width = plotW, height =plotH, units ="cm", dpi = 600, limitsize = TRUE)

```

```{r}
weightMeasure ="weightRelative" 
groupBy = "type"
cmax = max(typesOutput_combiRoi$weightRelative)

conMatPlot = plotConnectivityMatrix(typesOutput_combiRoi, byGroup = groupBy, weightMeasure , cmax)
conMatPlot = addMatrixPlotLabs(conMatPlot, "Outputs",  "",paste(myROIs, collapse = '-'), weightMeasure)

print(conMatPlot)

plotW = 25
plotH = 6

ggsave(paste("connectivityMatrix_out_",saveName,'_in_',myROIsName,'_', weightMeasure,'_fromNBag.pdf', sep=''), plot = conMatPlot, device='pdf', path = "../neuprintR_analysis_plots/",
  scale = 2, width = plotW, height =plotH, units ="cm", dpi = 600, limitsize = TRUE)

```

# Cluster input vectors to reference neurons
```{r}
conmat <- connectivityMatrix( typesInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = 0.7#0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8) + theme_paper()# + rect.hclust(hcl, h=cut, border = "red")

dev.print(pdf, paste0("../neuprintR_analysis_plots/inputCorrelation_",saveName,'_', myROIsName,'_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typeClusters <- stack(clu.h) %>% rename(type = ind, clust=values) %>% arrange(clust)

ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_nBag.pdf', sep=''), plot = plt, device='pdf', path = "../neuprintR_analysis_plots/", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)

```

```{r}
conmat <- connectivityMatrix( typesInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")
conmat_cd = cos_dist(t(conmat))
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")
dev.print(pdf, paste0("../neuprintR_analysis_plots/inputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typePreClusters <- stack(clu.h) %>% rename(type = ind, preclust=values) %>% arrange(preclust)

ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag.pdf', sep=''), plot = plt, device='pdf', path = "../neuprintR_analysis_plots/", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)

```
# Cluster output vectors to reference neurons

```{r}
conmat <- connectivityMatrix( typesOutput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = 0.7#0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")

dev.print(pdf, paste0("../neuprintR_analysis_plots/outputCorrelation_",saveName,'_', myROIsName,'_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typeClusters <- stack(clu.h) %>% rename(type = ind, clust=values) %>% arrange(clust)

ggsave( paste("outputCorrelation_",saveName,'_', myROIsName,'_nBag.pdf', sep=''), plot = plt, device='pdf', path = "../neuprintR_analysis_plots/", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)

```

```{r}
conmat <- connectivityMatrix( typesOutput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")
conmat_cd = cos_dist(t(conmat))
plt <- myplot_dist(conmat_cd, order=TRUE)
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")
dev.print(pdf, paste0("../neuprintR_analysis_plots/outputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typePreClusters <- stack(clu.h) %>% rename(type = ind, preclust=values) %>% arrange(preclust)

ggsave( paste("outputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag.pdf', sep=''), plot = plt, device='pdf', path = "../neuprintR_analysis_plots/", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)

```

# For LNO/PFN
## Investigate inptuts outside of NO
```{r}
inputDatabaseTypes = unique(typesInput_combiRoi$databaseType.from)
NAtypes = typesInput_combiRoi %>% filter(is.na(databaseType.from)) %>% select(type.from)
#inputDatabaseTypes = c(inputDatabaseTypes,NAtypes$type.from)
inputTypes = unique(typesInput_combiRoi$type.from)

myInputTypes_bag = create_neuronBag(inputDatabaseTypes)

# Filter out neurons from left side
splitLR = TRUE
if(splitLR){
  myInputTypes_bag = lateralize_types(myInputTypes_bag)
}
```

#TODO: Improve filtering to get one side (R) of the pathways
```{r}
# Find which rois inputs are innervating
myROIs_in = unique(myInputTypes_bag$inputs$roi) 
myROIs_in = intersect(myROIs_in,slctROIs)
myROIs_in
```

```{r}
myInputTypes_bag_comboRoi = combineRois(myInputTypes_bag, myROIs_in, "comboRoi")
#myInputTypes_bag_comboRoi = filter(myInputTypes_bag_comboRoi,filterPartners = FALSE, type %in% inputTypes)

inInput_combiRoi = myInputTypes_bag_comboRoi$inputs %>% filter(type.to %in% inputTypes)
```

```{r}
conmat <- connectivityMatrix(inInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE)
plt

hcl=hclust(conmat_cd)
cut2 = 0.8# 0.995 used for LNO inputs, 0.8 used otherwise
plot(hcl,hang= -1, cex = 0.6)#,labels = TRUE, )
rect.hclust(hcl, h=cut2, border = "red")
dev.print(pdf, paste0("../neuprintR_analysis_plots/inputCorrelation_",saveName,'_', myROIsName,'_inputs_nBag_tree.pdf'), width=8, height=4)

clu.h2=cutree(hcl,h=cut2) # cut tree/dendrogram from height 80

inTypeClusters <- stack(clu.h2) %>% rename(type = ind, inclust=values) %>% arrange(inclust)

ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_inputs_nBag.pdf', sep=''), plot = plt, device='pdf', path = "../neuprintR_analysis_plots/", scale = 1, width = 22, height = 22, units ="cm", dpi = 600, limitsize = TRUE)
```

```{r}
inTypesContribution <- myInputTypes_bag_comboRoi$outputs %>% filter(type.to %in% myTypeList_lat)

inTypesCon <- left_join(inTypesContribution, inTypeClusters, by=c("type.from"="type")) %>% 
  mutate(fromCluster = paste(inclust,type.from, sep="_"))
inTypesCon <- left_join(inTypesCon, typeClusters, by=c("type.to"="type")) %>% 
  mutate(toCluster = paste(clust,type.to, sep="_"))

cmax = max(inTypesCon$weightRelative)

plt <- ggplot(data = inTypesCon) + geom_tile(aes(x=type.to,y=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(inclust, desc(inclust)) ~ clust, space="free", scales="free",switch="both")
print(plt)

ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster.pdf', sep=''), plot = plt, device='pdf',
       path = "../neuprintR_analysis_plots/",width = 15, height= 40, units ="cm", dpi = 600, limitsize = TRUE)
#width = 11, 12 height =35, 15

plt <- ggplot(data = inTypesCon) + geom_tile(aes(y=type.to,x=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(clust, desc(clust)) ~ inclust, space="free", scales="free",switch="both")
print(plt)

ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_v2.pdf', sep=''), plot = plt, device='pdf',
       path = "../neuprintR_analysis_plots/",width = 45, height =10, units ="cm", dpi = 600, limitsize = TRUE)
#width = 40,  17, height =8, 10
```

```{r}
inTypesContribution <- typesInput_combiRoi

inTypesConPre <- left_join(inTypesContribution, typePreClusters, by=c("type.from"="type")) %>% 
  mutate(fromCluster = paste(preclust,type.from, sep="_"))
inTypesConPre <- left_join(inTypesConPre, typeClusters, by=c("type.to"="type")) %>% 
  mutate(toCluster = paste(clust,type.to, sep="_"))

cmax = max(inTypesConPre$weightRelative)

plt <- ggplot(data = inTypesConPre) + geom_tile(aes(x=type.to,y=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(preclust, desc(preclust)) ~ clust, space="free", scales="free",switch="both")
print(plt)

ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_pre_alltypes.pdf', sep=''), plot = plt, device='pdf',
       path = "../neuprintR_analysis_plots/",width = 15, height= 40,  units ="cm", dpi = 600, limitsize = TRUE)

```


```{r}
inTypesConPre <- left_join(inTypesContribution, typePreClusters, by=c("type.from"="type")) %>% 
  mutate(fromCluster = paste(preclust,type.from, sep="_"))
inTypesConPre <- left_join(inTypesConPre, typeClusters, by=c("type.to"="type")) %>% 
  mutate(toCluster = paste(clust,type.to, sep="_"))

cmax = max(inTypesConPre$weightRelative)

plt <- ggplot(data = inTypesConPre) + geom_tile(aes(x=type.to,y=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(preclust, desc(preclust)) ~ clust, space="free", scales="free",switch="both")
print(plt)

ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_pre.pdf', sep=''), plot = plt, device='pdf',
       path = "../neuprintR_analysis_plots/",width = 15, height= 40,  units ="cm", dpi = 600, limitsize = TRUE)

plt <- ggplot(data = inTypesConPre) + geom_tile(aes(y=type.to,x=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(clust, desc(clust)) ~ preclust, space="free", scales="free",switch="both")
print(plt)

ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_pre_v2.pdf', sep=''), plot = plt, device='pdf',
       path = "../neuprintR_analysis_plots/",width = 45, height =10, units ="cm", dpi = 600, limitsize = TRUE)
```


## Relate clustering from inputs based on their inputs to the clustering based on their output
```{r}
# output based clusters: typePreClusters
# input based clusters: inTypeClusters

clustCompare = full_join(inTypeClusters,typePreClusters, by="type") %>% na.omit()

preclustStats = clustCompare %>% group_by(preclust) %>% summarise(n_clust = length(unique(inclust)), members = length(inclust)) %>%
  mutate(av_n = members/n_clust)

inclustStats = clustCompare %>% group_by(inclust) %>% summarise(n_clust = length(unique(preclust)), members = length(preclust)) %>%
  mutate(av_n = members/n_clust)
```

```{r}
preclustStats_fit = preclustStats %>% 
    do({
      mod = lm(n_clust ~ members, data = .)
      data.frame(Intercept = coef(mod)[1], Slope = coef(mod)[2])
    })

inclustStats_fit = inclustStats %>% 
    do({
      mod = lm(n_clust ~ members, data = .)
      data.frame(Intercept = coef(mod)[1], Slope = coef(mod)[2])
    })

lim1 = 20
lim2 = 10
inClustStatPlot = ggplot(preclustStats,aes(members, n_clust)) + coord_fixed() + theme_classic() + xlim(0,lim1) + ylim(0,lim1) + 
  geom_jitter(height=0.15, width=0.15)+
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle(paste0("Fit: slope = ",round(preclustStats_fit$Slope,2),", intercept = ", round(preclustStats_fit$Intercept,2))) +
  xlab("# members per output-based cluster") + ylab("#different input-clusters")
#Each dot is a cluster of the LNO inputs, based on their connectivity to LNO (i.e. output-based cluster). 

preClustStatPlot = ggplot(inclustStats,aes(y=n_clust,x=members))  + coord_fixed() + theme_classic() + xlim(0,lim2) + ylim(0,lim2) +
  geom_jitter(height=0.15, width=0.15) +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle(paste0("Fit: slope = ",round(inclustStats_fit$Slope,2),", intercept = ", round(inclustStats_fit$Intercept,2))) +
  xlab("# members per input-based cluster") + ylab("# different output-clusters")

plt = grid.arrange(inClustStatPlot, preClustStatPlot, nrow = 1)
ggsave(paste("clusterStatistic_",saveName,'_', myROIsName,'_inputClustersPerOutputCluster.pdf', sep=''), plot = plt, device='pdf',path = "../neuprintR_analysis_plots/",width = 20, height =10, units ="cm", dpi = 600, limitsize = TRUE, useDingbats=FALSE)
```
## divergence/convergence between steps

```{r}
# type
types_inin = unique(inInput_combiRoi$type.from)
types_in = unique(inInput_combiRoi$type.to)
types_in2 = unique(typesInput_combiRoi$type.from)
types_in3 = unique(c(types_in,types_in2))
types_to = unique(typesInput_combiRoi$type.to)

print(length(types_inin))
print(length(types_in))
print(length(types_in2))
print(length(types_in3))
print(length(types_to))
print(types_to)
```

```{r}

clustGraph = clustCompare %>% mutate(from = paste0("f",inclust), to = paste0("t",preclust)) %>% select(c("from","to")) %>% mutate(relWeight = 1)
nodesSet1 = unique(clustGraph$from)
nodesSet2 = unique(clustGraph$to)
# first we give prefixes to the nodes to discern the two partition
g <- graph.empty()
g <- add.vertices(g,nv=length(nodesSet1),attr=list(name=nodesSet1,type=rep(TRUE,length(nodesSet1))))
g <- add.vertices(g,nv=length(nodesSet2),attr=list(name=nodesSet2,type=rep(FALSE,length(nodesSet2))))

# we need to turn edgeList into a vector
edgeListVec <- as.vector(t(as.matrix(clustGraph%>% select(c("from","to")))))
g <- add.edges(g,edgeListVec)

# check if is recognized as bipartite: is.bipartite(g)

#plot.igraph(g, layout=layout.bipartite, vertex.color=c("orange","grey")[V(g)$type+1])

arrowSize= .3
vertexSize= 5 #clustCompare %>% group_by(inclust) %>% count()
#vertexSize = 5 + vertexSize$n
selfFBscale = vertexSize
edgeNorm = .8
cutoff = 0
edcurve = 0

myGraph = constructConnectivityGraph(clustGraph, cutoff, vertexSize, selfFBscale, arrowSize, edgeNorm, useRandCol = TRUE)

l = layout_as_bipartite(myGraph, types = grepl("t",V(myGraph)$name))

myGraph$main = paste0("Cluster relationship\n layer 1: ",length(types_inin), " -> ",length(types_in2),"; layer 2:", length(types_in2), " -> ",length(types_to))
graphPlot = plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph))


dev.print(pdf, paste0("../neuprintR_analysis_plots/clusterGraph_",saveName,'_', myROIsName,".pdf"), width=20, height=15)

d = decompose(myGraph, mode ="weak", max.comps = NA, min.vertices = 0)
d

todeg <- degree(myGraph, v = V(myGraph)[grepl("t",V(myGraph)$name)], mode = "in",loops = TRUE, normalized = FALSE)
fromdeg <- degree(myGraph, v = V(myGraph)[grepl("f",V(myGraph)$name)], mode = "out",loops = TRUE, normalized = FALSE)

todeg = stack(todeg) %>% rename(to = ind, degree=values) %>% mutate(direction = "upstream")
fromdeg = stack(fromdeg) %>% rename(from = ind, degree=values) %>% mutate(direction = "downstream")

degreeDist = ggplot(data = bind_rows(todeg, fromdeg), aes(degree,fill=direction, color=direction,alpha=0.6)) + geom_bar(alpha=0.5) + theme_classic()
degreeDist

ggsave(paste("clusterGraph_degreeDistribution_",saveName,'_', myROIsName,'.pdf', sep=''), plot = degreeDist, device='pdf',path = "../neuprintR_analysis_plots/",width = 12, height =7, units ="cm", dpi = 600, limitsize = TRUE)
```



## Generate a data frame that lists all inputs by type and for each input type, provides a list of ROIs in they innervate

```{r}
roiTree = getRoiTree()

simpleROIs  = selectRoiSet(roiTree, default_level = 2, 
                        exceptions = list("OL(R)"=1,"AL(R)"=1,"PENP"=1,"AL(L)"=1,"MB(+ACA)(R)"=1,"MB(L)"=1,
                                          "VMNP"=1,"INP"=1,"SNP(R)"=1,"SNP(L)"=1, "LX(R)"=3, "LX(L)"=3), exceptionLevelMatch = 1)
simpleROIs = as.character(unique(simpleROIs$roi))
simpleROIs = c(simpleROIs[!simpleROIs=="NO"])
simpleROIs = c(c("NO(R)","NO(L)"),simpleROIs)
#simpleROIs = c(simpleROIs[!simpleROIs=="FB"])
#simpleROIs = c(paste0("FBl",seq(1,9)),simpleROIs)
simpleROIs
```


```{r}
myTypes_bag_filt = filter(myTypes_bag_full,filterPartners = FALSE, type %in% myTypeList_lat)#databaseType %in% paste0(myTypeList))
myInputTypes_bag_filt= filter(myInputTypes_bag,filterPartners = FALSE,  type %in% inputTypes)

# get roi info
typeROI = getROISummary(myTypes_bag_filt) %>% filter(roi %in% simpleROIs)
inTypeROI = getROISummary(myInputTypes_bag_filt) %>% filter(roi %in% simpleROIs)
```

```{r}
# lookup table of input types -> types
inputTypes_2_types = myInputTypes_bag_filt$outputs %>% filter(roi %in% simpleROIs) %>% filter(type.to %in% myTypeList_lat) %>% select(c("type.from", "type.to",  "roi", "weightRelative", "absoluteWeight"))

inputTypeROIs_by_types  = inputTypes_2_types %>% group_by(roi, type.to) %>% 
  summarise(sumWeightRel = sum(weightRelative),
            absWeight =  as.integer(sum(absoluteWeight))) %>% ungroup()

# Generate list of ROIs for each type
th = 30
inType_ROIs = inTypeROI %>% filter((upstream> th) | (downstream > th)) %>%
  mutate(roisimple = sub("\\(R\\)", "r", roi))  %>% 
  mutate(roisimple = sub("\\(L\\)", "l", roisimple)) %>%
  mutate(roisupsimple = sub("\\(R\\)", "", roi))  %>% 
  mutate(roisupsimple = sub("\\(L\\)", "", roisupsimple)) %>% select(c("roi","roisimple", "roisupsimple","type", "n")) %>% distinct()
```

```{r}
# add info on to-type
type_inputTypeMap <- data.frame() 
for(type in myTypeList_lat){
  print(type)
  onetype_inputTypeMap = right_join(inType_ROIs, inputTypes_2_types  %>% select(type.from, type.to, absoluteWeight, weightRelative) %>% filter(type.to == type), 
                                   by=c("type" = "type.from")) %>% 
    group_by(roisimple, type.to) %>% summarise(weightRel_all =  mean(weightRelative),
                                               weightAbs_all = as.integer(mean(absoluteWeight)),
                                               n = length(weightAbs_all)) %>% ungroup()
  type_inputTypeMap = bind_rows(type_inputTypeMap,onetype_inputTypeMap)
}
```

```{r}
cmax = max(type_inputTypeMap$weightRel_all)# - 0.05
wRel_plt <- ggplot(type_inputTypeMap, aes(x=type.to,y=roisimple,fill=weightRel_all)) + geom_tile() +
  scale_fill_gradient2(low="azure2", mid="azure4", high="black", 
                         midpoint =0.5*cmax, limits=c(0,cmax))  +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))

wAbs_plt <- ggplot(type_inputTypeMap, aes(x=type.to,y=roisimple,fill=weightAbs_all)) + geom_tile() +
  scale_fill_gradient2(low="azure2", mid="azure4", high="black", 
                         midpoint =0.5*max(type_inputTypeMap$weightAbs_all), limits=c(0,max(type_inputTypeMap$weightAbs_all)))  +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))

pltin <- grid.arrange(wRel_plt, wAbs_plt, nrow = 1)
ggsave(paste("InputMap_inputs_",saveName,'_', myROIsName,'.pdf', sep=''), plot = pltin, device='pdf',path = "../neuprintR_analysis_plots/",width = 20, height=12, units ="cm", dpi = 600, limitsize = TRUE)
```

Map of input places
```{r}
th = 30
type_inputMap = typeROI %>%  filter((upstream> th) | (downstream > th))  %>% group_by(type, roi) %>% summarise(upstream_all =  as.integer(mean(upstream)),
                                                                                          downstream_all = as.integer(mean(downstream))) %>% ungroup()

upstr_plt <- ggplot(type_inputMap, aes(x=type,y=roi,fill=upstream_all)) + 
  geom_tile() +
  scale_fill_gradient2(low="azure2", mid="azure4", high="black", 
                         midpoint =0.5*max(type_inputMap$upstream_all), limits=c(0,max(type_inputMap$upstream_all)))  +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))

dwstr_plt <- ggplot(type_inputMap, aes(x=type,y=roi,fill=downstream_all)) + 
  geom_tile() +
  scale_fill_gradient2(low="azure2", mid="azure4", high="black",
                         midpoint =0.5*max(type_inputMap$downstream_all), limits=c(0,max(type_inputMap$downstream_all)))  +
  theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))

plt <- grid.arrange(upstr_plt, dwstr_plt, nrow = 1)
ggsave(paste("InputOutputMap_",saveName,'_', myROIsName,'.pdf', sep=''), plot = plt, device='pdf',path = "../neuprintR_analysis_plots/",width=25, height=8, units ="cm", dpi = 600, limitsize = TRUE)

```

