---
title: "CX neurons fiber diameters"
output: html_notebook
---

## Preparing the environment
```{r,message=F}
library(neuprintrExtra)
library(hemibrainr)
library(dplyr)
library(ggplot2)
library(readr)
library(paletteer)
library(stringr)
```

```{r}
source(file.path("..","R","paperTheme.R"))
```

## Measuring the diameter of the main neurite of all CX neurons
We start by collating all CX neurons:
```{r}
CXtypes <- supertype(read_csv(file.path("CX-cell-types060920.csv")) %>% rename(databaseType=n.type))
CXNeurons <- getTypesTable(CXtypes$databaseType)
CXNeurons <- cxRetyping(CXNeurons,postfix="raw") %>% filter(cropped==FALSE) %>% 
  supertype() %>% 
  filter(grepl("_R",type) | supertype3 == "FB Interneuron") %>% 
    mutate(glomerulus=factor(gsub("_","",str_extract(name.from,"_[L|R][1-9]_")),
                             levels=c(paste0("L",9:1),paste0("R",1:9))),
           column=factor(gsub("_","",str_extract(name.from,"_C[1-9]")),
                         levels=paste0("C",9:1)))

# In case this notebook has already been run and one wants to skip the slow skeleton extraction
#CXNeurons <- readRDS("CXNeuronsWithDiameters.rds")%>% 
#  filter(grepl("_R",type) | supertype3 == "FB Interneuron") %>% 
#    mutate(glomerulus=factor(gsub("_","",str_extract(name,"_[L|R][1-9]_")),
#                             levels=c(paste0("L",9:1),paste0("R",1:9))),
#           column=as.integer(gsub("_C","",str_extract(name,"_C[0-9]"))))
```

We then gather the skeleton for all CX neurons, and correct their soma locations using the nice annotation from the `hemibrainr` package:
```{r}
allCXSkeletons <- neuprint_read_neurons(CXNeurons$bodyid,heal.threshold = Inf)
allCXSkeletons <- hemibrain_reroot(allCXSkeletons)
```

We then extract their main neurites (defined as the process between their somas and their primary branchpoint). `primary_neurite` is a function from the `hemibrainr` package:
```{r}
allCXMainNeurites <- primary_neurite(allCXSkeletons)
```



```{r}
CXNeurons <- rowwise(CXNeurons) %>%
  mutate(mainNeuriteW = median(allCXMainNeurites[[as.character(bodyid)]]$d$W*8/1000),
         allNeuronW = median(allCXSkeletons[[as.character(bodyid)]]$d$W*8/1000)
         )%>%
  ungroup()
```

```{r}
EBNeuronsWidthPlot <- 
ggplot(filter(CXNeurons,grepl("_R",type) | supertype3 == "FB Interneuron",
              supertype3 %in% c("EB Columnar","ER","ExR")),
       aes(x=type,y=mainNeuriteW,color=supertype2)) + 
  geom_point() + 
  facet_grid(.~supertype2,scales = "free",space="free",switch = "x") + 
  theme_paper(axis.text.x=element_text(angle=90),
              strip.placement="outside",
              legend.position="none") + 
  scale_color_manual(values=supertype2Palette()$pal) +
  ylab("main neurite diameter (μm)") + ylim(c(0,1.3))
EBNeuronsWidthPlot
```
```{r}
save_plot("EBDiams.svg",EBNeuronsWidthPlot,ncol=1.2,nrow=0.6)
```


```{r}
OthersNeuronsWidthPlot <- 
ggplot(filter(CXNeurons,grepl("_R",type) | supertype3 == "FB Interneuron",
              supertype3 %in% c("LNO","SA","PB Interneurons","PB Input")),
       aes(x=type,y=mainNeuriteW,color=supertype2)) + 
  geom_point() + 
  facet_grid(.~supertype2,scales = "free",space="free",switch = "x") + 
  theme_paper(axis.text.x=element_text(angle=90),
              strip.placement="outside",
              legend.position="none") + 
  scale_color_manual(values=supertype2Palette()$pal) +
  ylab("main neurite diameter (μm)") + ylim(c(0,1.3))
OthersNeuronsWidthPlot
```

```{r}
save_plot("OthersDiams.svg",OthersNeuronsWidthPlot,ncol=0.5,nrow=0.6)
```

```{r}
FBNeuronsWidthPlot <- 
ggplot(filter(CXNeurons,grepl("_R",type) | supertype3 == "FB Interneuron",
              supertype3 %in% c("FB Columnar","FB Output","FB Interneuron")),
       aes(x=type,y=mainNeuriteW,color=supertype2)) + 
  geom_point() + 
  facet_grid(.~supertype2,scales = "free",space="free",switch = "x") + 
  theme_paper(axis.text.x=element_text(angle=90),
              strip.placement="outside",
              legend.position="none") + 
  scale_color_manual(values=supertype2Palette()$pal) +
  ylab("main neurite diameter (μm)") + ylim(c(0,1.3))
FBNeuronsWidthPlot
```
```{r}
save_plot("FBDiams.svg",FBNeuronsWidthPlot,ncol=1.6,nrow=0.6)
```

```{r}
FBtPal <- c("#fce61fff","#98ca43ff","#40b875ff","#1fa387ff","#228a8dff","#2f708eff","#38578dff","#453882ff","#431853ff")

FBtNeuronsWidthPlot <- 
ggplot(filter(CXNeurons,grepl("_R",type) | supertype3 == "FB Interneuron",
              supertype2 == "FBt"),
       aes(x=type,y=mainNeuriteW,color=supertype1)) + 
  geom_point() + 
  facet_grid(.~supertype1,scales = "free",space="free",switch = "x") + 
  theme_paper(axis.text.x=element_text(angle=90),
              strip.placement="outside",
              legend.position="none") + 
  scale_color_manual(values=FBtPal) +
  ylab("main neurite diameter (μm)") + ylim(c(0,1.3))
FBtNeuronsWidthPlot
```
```{r}
save_plot("FBtDiams.svg",FBtNeuronsWidthPlot,ncol=1.6,nrow=0.6)
```

```{r}
neurons4Bundles <- filter(CXNeurons,
                          supertype3 %in% c("FB Interneuron","FB Output","FB Columnar"))
```

```{r}
pdm01Neurons <- filter(CXNeurons,
                       cellBodyFiber == "PDM01",
                       supertype3 %in% c("FB Interneuron","FB Output","FB Columnar"),
                       bodyid %in% filter(hemibrain_somas,X<25500)$bodyid)
                       

#pdm01Skeletons <- neuprint_read_neurons(pdm01Neurons$bodyid,heal.threshold = Inf)
#pdm01Skeletons[,"supertype2"] <- supertype(pdm01Skeletons[,"type"])
```

```{r}
pdm02Neurons <- filter(CXNeurons,
                       cellBodyFiber == "PDM02",
                       supertype3 %in% c("FB Interneuron","FB Output","FB Columnar"),
                       bodyid %in% filter(hemibrain_somas,X<25500)$bodyid)
                       

pdm02Skeletons <- neuprint_read_neurons(pdm02Neurons$bodyid,heal.threshold = Inf)
pdm02Skeletons[,"supertype2"] <- supertype(pdm02Skeletons[,"type"])
```
```{r}
pdm03Neurons <- filter(CXNeurons,
                       cellBodyFiber == "PDM03",
                       supertype3 %in% c("FB Interneuron","FB Output","FB Columnar"),
                       bodyid %in% filter(hemibrain_somas,X<25500)$bodyid)
                       

pdm03Skeletons <- neuprint_read_neurons(pdm03Neurons$bodyid,heal.threshold = Inf)
pdm03Skeletons[,"supertype2"] <- supertype(pdm03Skeletons[,"type"])
```

```{r}
pdm04Neurons <- filter(CXNeurons,
                       cellBodyFiber == "PDM04",
                       supertype3 %in% c("FB Interneuron","FB Output","FB Columnar"),
                       bodyid %in% filter(hemibrain_somas,X<25500)$bodyid)
                       

#pdm04Skeletons <- neuprint_read_neurons(pdm04Neurons$bodyid,heal.threshold = Inf)
#pdm04Skeletons[,"supertype2"] <- supertype(pdm04Skeletons[,"type"])
```

```{r}
write_csv(pdm01Neurons,"FB-PDM1.csv")
write_csv(pdm02Neurons,"FB-PDM2.csv")
write_csv(pdm03Neurons,"FB-PDM3.csv")
write_csv(pdm04Neurons,"FB-PDM4.csv")
write_csv(data.frame(supertype2=supertype2Palette()$breaks,color=as.character(supertype2Palette()$pal)),"paletteFibers.csv")
```

