---
title: "CX to CX connections (figure 57)"
output: html_notebook
---

## Preparing the environment
```{r}
library(dplyr)
#library(stringr)
library(ggplot2)
library(neuprintrExtra)
#library(nat)
library(paletteer)
```

Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source("outputFunctions-core.R")
source(file.path("..","R","paperTheme.R"))
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure57-CX2CX"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
# Basic metadata:
load(file.path(dataFolder,"outputsBasics.RData"))
# Pathway weights tables
CXInfluence <- readRDS(file.path(dataFolder,"cx-influence.rds"))
CXoutFull <- readRDS(file.path(dataFolder,"pathwayWeightsTable.rds"))
#CXoutAllSteps <- readRDS(file.path(dataFolder,"pathways-allsteps.rds"))

CX_outGraph <- readRDS(file.path(dataFolder,"output_graph.rds"))

load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
```


## Composition and importance of the CX to CX connections in "non local" neuropils (panel A)
Those are the types described in figure 56, to be excluded in that figure
```{r}
localNeuropileNeurons <- c("EL","EPG","PEG","ER6",
                           "ExR1","ExR2","ExR3","ExR5","ExR6",
                           "PFR_a","PFR_b","FR1","FR2")
```

We summarize the influence of those types exert by supertype:
```{r}
CXInfluenceOther <- filter(CXInfluence,
                           !(databaseType.from %in% localNeuropileNeurons) & type.from %in% CXOutputTypes) %>%
  group_by(supertype3.to,type.from,supertype3.from) %>% 
  summarize(Path_weight=sum(Path_weight)) %>% 
  ungroup()
head(CXInfluenceOther)
```
Generate panel A from this table. `supertype3Palette` is a custom palette defined in "outputFunctions-display.R" to be used throughout the section: 
```{r}
backCXCompositionOther <- ggplot(CXInfluenceOther,aes(x=type.from,y=Path_weight)) +
  geom_col(aes(fill=supertype3.to)) + 
  scale_fill_manual(name="target supertype",values=supertype3Palette) + 
  theme_paper(strip.text.x=element_blank(),axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5))+
  facet_grid(.~supertype3.from,scales = "free",space="free") + 
  ylab("normalized pathway weight") + 
  xlab("CX output type")
backCXCompositionOther
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"outputs-CXInfluenceCompositionOther.svg"),
          backCXCompositionOther,ncol=1,nrow=6,base_width = 8.5,base_height = 11/35)
```

## Connectivity matrix (panel B and figure supplement 1 panel B)
We generate the connectivity matrix of all (direct and indirect) CX to CX connections outside of the CX by filtering the pathway weights table `CXoutFull` to CX types (and to pathway weights over 0.5%):
```{r}
CX2CXFullMat <- filter(CXoutFull,databaseType.to %in% CXOutsideTypes$databaseType) %>%
  mutate(roi="outside") %>% 
  supertype() %>% 
  filter(Path_weight>0.005)
```

### Main panel
For the main figure, we exclude the FBt from the matrix:
```{r}
CX2CXFullPLotRedux <- plotConnectivity(filter(CX2CXFullMat,
                                              supertype2.from != "FBt" & 
                                                supertype2.to != "FBt" & 
                                                !(databaseType.from %in% localNeuropileNeurons)),
                                       grouping = "type",
                                       facetInputs="supertype3.from",facetOutputs = "supertype3.to",
                                       xaxis = "outputs",
                                       connectionMeasure = "Path_weight",
                                       orderIn = typesCXOrder,
                                       orderOut=typesCXOrder,
                                       theme=theme_paper_rects(strip.placement="outside"),
                                       switch="both") + 
  xlab("target type") + ylab("CX output type")+
  guides(fill=guide_colorbar(title="pathway weight"))+ 
  scale_fill_paletteer_c("ggthemes::Blue")  
  
CX2CXFullPLotRedux
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"outputs-CX2CXReduxMat.svg"),
          CX2CXFullPLotRedux,base_width = 6.5,base_height = 4)
```

### Figure supplement panel B
This is the same plot, but not excluding the FBt:
```{r}
CX2CXFullPlot <- plotConnectivity(CX2CXFullMat,
                                  grouping = "type",
                                  facetInputs="supertype3.from",facetOutputs = "supertype3.to",
                                  xaxis = "outputs",
                                  connectionMeasure = "Path_weight",
                                  switch="both",
                                  orderIn = typesCXOrder,orderOut=typesCXOrder,
                                  theme=theme_paper_grid_rects(strip.placement="outside")) + 
  xlab("target type") + ylab("CX output type")+
  guides(fill=guide_colorbar(title="pathway weight"))+ 
  scale_fill_paletteer_c("ggthemes::Blue") + 
  theme(legend.position = c(0.1,0.35))

CX2CXFullPlot
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"outputs-CX2CXFullMat.svg"),
          CX2CXFullPlot,ncol=1.3,nrow=19,base_width = 8.5,base_height = 11/35)
```


## Figure supplement 1 panel A: distinguishing different type of CX to CX connections
Generating a summary per type and "kind" of connection (one also has to restrict it to outputs of CX output neurons):
```{r}
CXInfluenceSummary <- group_by(filter(CXInfluence,type.from %in% CXOutputTypes),type.from,kind) %>%
  summarize(totalOC=sum(Path_weight)) %>% 
  ungroup() %>% 
  mutate(databaseType.from=type.from) %>% 
  supertype()
```
Generating the plot, coloring per "kind":
```{r}
CXInfluenceSummaryPlot <- ggplot(CXInfluenceSummary,aes(x=type.from,y=totalOC)) +
  geom_col(aes(fill=kind)) + 
  theme_paper(strip.text.x=element_blank(),axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5))+
  facet_grid(.~supertype3.from,scales = "free",space="free") +
  scale_fill_paletteer_d("ggthemes::Tableau_20",name="target kind") + 
  ylab("normalized pathway weight") + xlab("")
CXInfluenceSummaryPlot
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"outputs-CXInfluenceSummary.svg"),CXInfluenceSummaryPlot,ncol=1.3,nrow=6,base_width = 8.5,base_height = 11/25)
```

## Graphs of PFL to LNO connections
We first generate a palette:
```{r}
customGraphPalette <- supertype3Palette[names(supertype3Palette) %in% filter(mainFFConns,
                                                                             Path_weight>0.005)$supertype3.to]
extraPal <- p36[!p36 %in% customSupertypePalette & !p36 %in% customGraphPalette]
extraLevs <- unique(mainFFConns$supertype2.to[mainFFConns$supertype3.to=="Terra incognita"])
extraPal <- extraPal[1:length(extraLevs)]
names(extraPal) <- extraLevs
customGraphPalette <- c(customGraphPalette,extraPal)
names(customGraphPalette)[1] <- "Source"
```

### PFL2 to LNO3 (panel Ci)
We then use the `getLocalSubgraph`, defined in "outputFunctions-display.R", which takes input types, output types, and the number of connections to "search" away from both inputs and outputs types (here only one step):
```{r}
PFL2toLNO <- getLocalSubgraph(c("PFL2_L","PFL2_R"),c("LNO3_R"),CX_outGraph,order=1)
```
We can then plot it with `ggraph`:
```{r}
PFL2toLNOGraph <- ggraph(PFL2toLNO,layout="sugiyama") +
  geom_edge_fan(aes(color=supertype2.from,width=weightRelative),
                end_cap = circle(3, "mm"),
                linejoin = "mitre",linemitre=3,
                arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
  geom_node_point(aes(color=supertype2),size=4)+
  geom_node_text(aes(label=type),nudge_y = 0.05)+
  theme_paper_map(legend.position=c(0.8,0.8))+
  scale_color_manual(values=c(customGraphPalette,"PFL"=supertype3Palette[["FB Columnar"]],
                              supertype3Palette),name="Type")+
  scale_edge_color_manual(values=c(customGraphPalette,"PFL"=supertype3Palette[["FB Columnar"]],
                                   "LC"=supertype3Palette[["Visual PNs"]])) +
  scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="Relative weight") +
  guides(edge_color="none",color="none") + 
  coord_cartesian(clip="off")

PFL2toLNOGraph
```
Then save the graph:
```{r}
save_plot(file.path(outputsFolder,"PFL2toLNO3Graph.svg"),
          PFL2toLNOGraph,nrow=1,ncol=1,base_height = 11/5,base_width = 8.5/3)
```

### PFL3 to LCNO and EB neurons
We generated graphs in ways similar as the one used above for PFL2. However, for readability, we use a manual layout of the nodes. The tidygraph object is therefore defined manually and with x and y properties defined for every node (`induced_subgraph` is an igraph function):
```{r}
PFL3_toEB <- as_tbl_graph(induced_subgraph(CX_outGraph,c(
  "PFL3_L*",
  "LAL121_R",
  "LAL076_R",
  "CRE041_R",
  "LCNOp_R",
  "ER6_L",
  "ExR6_L",
  "ExR4_L"))) %N>% 
  mutate(x=case_when(
    type %in% c("PFL3_L*","LCNOp_R") ~ 1,
    type %in% c("LAL121_R","LAL076_R") ~ 1.25,
    type %in% c("CRE041_R") ~ 0.8,
    type == "ER6_L" ~ 1.3,
    type == "ExR6_L" ~ 1.4,
    type == "ExR4_L" ~ 1.5
  ),
  y=case_when(
    type %in% c("PFL3_L*") ~ 3,
    type %in% c("CRE041_R") ~ 2.3,
    type %in% c("LAL076_R") ~ 2.5,
    type %in% c("LAL121_R") ~ 2.0,
    type %in% c("LCNOp_R","ER6_L","ExR4_L") ~ 1.5,
    type == "ExR6_L" ~ 1.6)
  ) %>% selectSupertypeSet(default_level = 1) %>%
  customOutputSupertype()  %E>% 
  mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)])
PFL3_toEB
```
We can then similarly plot the object using ggraph:
```{r}
PFL3toEBPlot <- ggraph(PFL3_toEB,layout="manual",x=x,y=y) +
  geom_vline(xintercept = 1.25,lty=2,color="grey50")+
  geom_edge_fan(aes(color=customSupertype.from,width=weightRelative),
                end_cap = circle(3, "mm"),
                linejoin = "mitre",linemitre=3,
                arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
  geom_node_point(aes(color=customSupertype),size=4)+
  geom_node_text(aes(label=type))+
  theme_paper_map()+
  scale_color_manual(values=c(customGraphPalette,customSupertypePalette))+
  scale_edge_color_manual(values=c(customGraphPalette,customSupertypePalette)) +
  scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="Relative weight") +
  guides(color="none",edge_color="none") + coord_cartesian(clip="off")

PFL3toEBPlot 
```
Then save the graph:
```{r}
save_plot(file.path(outputsFolder,"PFL3toEBNO.svg"),PFL3toEBPlot,base_height = 2,base_width = 5)
```

### PFL1 to ER1 neurons (panel Ciii)
As for PFL3, we use a manual layout:
```{r}
PFL1_toEB <- as_tbl_graph(induced_subgraph(CX_outGraph,c(
  "PFL1_L*",
  "LAL047_R",
  "LAL188_R",
  "WED034_R",
  "WED035_R",
  "LAL138_R",
  "ER1_b_L",
  "ER1_a_R")))%N>% mutate(x=case_when(
    type %in% c("PFL1_L*","LAL047_R","WED034_R") ~ 1,
    type %in% c("WED035_R","ER1_a_R") ~ 0.75,
    type %in% c("LAL188_R") ~ 1.2,
    type == "LAL138_R" ~ 1.25,
    type == "ER1_b_L" ~ 1.4
  ),
  y=case_when(
    type %in% c("PFL1_L*") ~ 3,
    type %in% c("LAL047_R") ~ 2.8,
    type %in% c("LAL188_R","WED035_R","WED034_R","LAL188_R") ~ 2.5,
    type %in% c("LAL138_R") ~ 2.2,
    type %in% c("ER1_a_R","ER1_b_L") ~ 1.8)
  ) %>% selectSupertypeSet(default_level = 1) %>%
  customOutputSupertype()  %E>% 
  mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)])
```
Then the plot:
```{r}
PFL1toEBPlot <- ggraph(PFL1_toEB,layout="manual",x=x,y=y) +
  geom_vline(xintercept = 1.25,lty=2,color="grey50")+
  geom_edge_fan(aes(color=customSupertype.from,width=weightRelative),
                end_cap = circle(3, "mm"),
                linejoin = "mitre",linemitre=3,
                arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
  geom_node_point(aes(color=customSupertype),size=4)+
  geom_node_text(aes(label=type))+theme_paper_map()+
  scale_color_manual(values=c(customGraphPalette,customSupertypePalette))+
  scale_edge_color_manual(values=c(customGraphPalette,customSupertypePalette)) +
  scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="Relative weight") +
  guides(color="none",edge_color="none") + coord_cartesian(clip="off")

PFL1toEBPlot 
```
Saving:
```{r}
save_plot(file.path(outputsFolder,"PFL1toEB.svg"),PFL1toEBPlot,base_height = 2,base_width = 5)
```

