---
title: "CX to CX motifs, figure 58"
output: html_notebook
---

## Preparing the environment
```{r}
library(dplyr)
library(tidyr)
library(neuprintrExtra)
library(paletteer)
```

```{r message=FALSE}
source("outputFunctions-display.R")
source(file.path("..","R","paperTheme.R"))
source(file.path("..","R","table2ggraphUtils.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure58-CX2CX-Motifs"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
# The pathway weights for all targets
CXoutFull <- readRDS(file.path(dataFolder,"pathwayWeightsTable.rds"))
# Base metadata
load(file.path(dataFolder,"outputsBasics.RData"))
```

## Create the data frame of connections in the CX of neurons connected outside the CX
We first select all CX to CX connections to look for motifs in. 
We exclude projections to CX neurons that are mostly axonal, and consider only connections with pathway weights over 0.5%.
```{r}
CXOutAxonals <- filter(CXOutsideTypes,downstreamRatio>0.75)

CX2CXaxDendMat <- filter(CXoutFull,
                         databaseType.to %in% CXOutsideTypes$databaseType &
                            !databaseType.to %in% CXOutAxonals$databaseType &
                            databaseType.from != databaseType.to) %>%
   mutate(roi="outside") %>% supertype() %>% filter(Path_weight>0.005)
head(CX2CXaxDendMat)
```
We then build the connection tables for the recipient types in the CX neuropils (we also make a graph object of it):
```{r}
recurrentInCXBag <- neuronBag(filter(CXNeurons,type %in% unique(c(CX2CXaxDendMat$type.from,CX2CXaxDendMat$type.to))),
                              renaming = cxRetyping,
                              omitInputs = T,
                              slctROI=c("EB","FB","NO(R)","NO(L)","PB"))

allRecurrentCX <- recurrentInCXBag$outputs
allRecurrentGraph <- makeGraph(allRecurrentCX)
allRecurrentGraph
```

## Example motifs (panels B,C,D)

### Canonical feedback (panel B)
#### Bodyids for renderings:
PFL1 to FB2B_b. Bodyids to be used in renderings:
```{r}
PFL1bodies <- getTypesTable("PFL1") %>% cxRetyping() %>% filter(type=="PFL1_L*")
PFL1bodies$bodyid
```

```{r}
FB2BBodies <- getTypesTable("FB2B_b") %>% cxRetyping() %>% filter(type=="FB2B_b_R")
FB2BBodies$bodyid
```

#### PFL1 network motifs
We use the `plotMotifs` function, defined in "outputFunctions-display", that takes as input the connections tables in the two neuropils (or sets of neuropils) we're considering, the neuron of interest (at the center of the motif graph) and the stat considered:
```{r}
canMot <- plotMotifs(getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),
                                      allRecurrentCX,
                                      "PFL1_L*","Path_weight"))
canMot
```
And save the graph:
```{r}
save_plot(file.path(outputsFolder,"outputs-canMot.svg"),canMot,ncol=6,nrow=6,base_width = 8.5/10,base_height=11/28)
```

### Parallel connections (panel C)
#### Bodyids for renderings:
FB6T to FB6E. 
```{r}
FB6Tbodies <- getTypesTable("FB6T") %>% cxRetyping() %>% filter(type=="FB6T_R")
FB6Tbodies$bodyid
```

```{r}
FB6Ebodies <- getTypesTable("FB6E") %>% cxRetyping() %>% filter(type=="FB6E_R")
FB6Ebodies$bodyid
```

#### FB6T network motifs:
```{r}
parMot <- plotMotifs(getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),
                                      allRecurrentCX,"FB6T_R","Path_weight"))
parMot
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"outputs-parMot.svg"),
          parMot,ncol=6,nrow=6,base_width = 8.5/10,base_height=11/28)
```

### Linked targets (panel D)
#### Bodyids for renderings
FB8F_a to FB6C_a/FB6C_b/FB6G/FB6I. 
```{r}
FB8Fabodies <- getTypesTable("FB8F_a") %>% cxRetyping() %>% filter(type=="FB8F_a_R")
FB8Fabodies$bodyid
```

```{r}
FB8FTargetsbodies <- getTypesTable(c("FB6C_a","FB6C_b","FB6G","FB6I")) %>% cxRetyping() %>% filter(grepl("_R",type))
FB8FTargetsbodies$bodyid
```

#### FB8F_a network motifs:
```{r}
linkMot <- plotMotifs(getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),allRecurrentCX,"FB8F_a_R","Path_weight"))
linkMot
```
And save the graph:
```{r}
save_plot(file.path(outputsFolder,"outputs-linkMot.svg"),linkMot,ncol=6,nrow=6,base_width = 8.5/10,base_height=11/28)
```


## Motifs prevalence summary (panel E):
We then count the prevalence of every motif for every CX output type present in the CX to CX connections table:
- the prevalence canonical feedbacks is the number of reciprocal connections in the CX (divided by the number of connections outside the CX)
- the prevalence of parallel connections is the number of matching connections in the CX (divided by the number of connections outside the CX)
- the prevalence of linked targets is the number of connections between any 2 of the targets in the CX, divided by the number of possible connections (n choose 2, where n is the number of targets)
```{r}
recurrentMotifsSummary <- group_by(CX2CXaxDendMat,
                                   type.from,supertype1.from,supertype3.from) %>%
   summarize("CX parallel connection"=sum(paste0(type.from,type.to) %in%
                                       paste0(allRecurrentCX$type.from,allRecurrentCX$type.to))/n(),
             "CX canonical feedback"=sum(paste0(type.to,type.from) %in%
                                       paste0(allRecurrentCX$type.from,allRecurrentCX$type.to))/n(),
             "linked targets in CX"=if (n()==1) 0 else
                sum(as.vector(combn(type.to,2,paste0,collapse="")) %in%
                                          c(paste0(allRecurrentCX$type.from,allRecurrentCX$type.to),
                           paste0(allRecurrentCX$type.to,allRecurrentCX$type.from)))/(choose(n(),2))
                                                ) %>%
   ungroup()
head(recurrentMotifsSummary)
```
We then pivot the table to a longer format for easier plotting:
```{r}
recurrentMotifsSummary <-  pivot_longer(recurrentMotifsSummary,c("CX parallel connection",
                                                                 "CX canonical feedback",
                                                                 "linked targets in CX"),
                                        names_to="stat",values_to="Proportion") %>% 
   mutate(type.fromF = factor(type.from,levels=typesCXOrder),
          stat=factor(stat,levels=c("CX parallel connection",
                                    "CX canonical feedback","linked targets in CX")))
head(recurrentMotifsSummary)
```

We then plot the prevalence of each motif per type:
```{r}
recurrentMotifsPrevalence <- ggplot(recurrentMotifsSummary ,aes(x=type.fromF,y=stat)) +
   geom_point(size=3,color="grey90")+ 
   geom_point(aes(size=Proportion,color=stat))  +
   facet_grid(.~supertype3.from,scale="free",space="free")+ 
   theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),
               strip.text.x = element_text(angle=90)) + 
   xlab("CX output type") + 
   scale_size_area(name="prevalence",max_size = 3) + ylab("motif") + scale_color_paletteer_d(name="motif","ggthemes::Traffic")

#motifPal <- c("Plum",paletteer_d("ggthemes::Traffic")[1:3])
#names(motifPal) <- c("Out of CX pathways","CX Parallel connection","CX Canonical feedback","Linked #targets in CX")

recurrentMotifsPrevalence
```

And save the panel:
```{r}
save_plot(file.path(outputsFolder,"outputs-prevalences.svg"),
          recurrentMotifsPrevalence,ncol=1.3,nrow=6,base_width = 8.5,base_height=11/28)
```
