---
title: "Output pathways: quantification of divergence/convergence/recurrence figure"
output: html_notebook

---

This notebook generates the panels for the figure 55, summarizing the output pathways, mostly in terms of their divergence and recurrence.

## Preparing the environment
```{r}
library(neuprintr)
library(ggplot2)
#library(cowplot)
#library(patchwork)
library(dplyr)
library(neuprintrExtra)
#library(nat)
library(paletteer)
library(tidygraph)
library(ggraph)
```

Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source(file.path("..","R","paperTheme.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure55-OutputsDivergence"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
# Basic metadata
load("outputsBasics.RData")
# The pathway weights connectivity
CXoutAllSteps <- readRDS("pathways-allsteps.rds")
# The full graph in different formats (and the metadata about all the neurons in there)
CX_outGraph <- readRDS("output_graph.rds")
CX_outPaths <- readRDS("output_paths.rds")
allNodes <- readRDS("all-nodes.rds")
```

## Divergence summary (panel A)

We use the table of all pathway weights to find for each neuron the shortest path to that neuron from the CX. This corresponds to a type's "layer" and is stored as `hop.to` in that table. We need to set the CX output neurons to the "0" layer as they are the origin neurons by definition. We also store it in the `allNodes` table.
```{r}
pathways <- CXoutAllSteps %>% filter(n_steps %in% 1:5) %>% 
   mutate(n_steps=as.numeric(n_steps),
          n_type=(CX_outGraph %E>% as_tibble())$n_type[match(type.to,(CX_outGraph %E>% as_tibble())$type.to)]) %>%
   group_by(type.to) %>% mutate(hop.to=min(n_steps)) %>% ungroup()

pathways$hop.to[pathways$type.to %in% CXOutputNeurons$type] <- 0

allNodes$layer <- pathways$hop.to[match(allNodes$type,pathways$type.to)]
allNodes$layer[is.na(allNodes$layer)] <- 0
```

We then assign nodes in the graph of the all networks to their corresponding layers. We call "layer" the source layer, and "hop" the target layer:
```{r}
CX_outGraph <- CX_outGraph %N>% mutate(layer=allNodes$layer[match(type,allNodes$type)]) %E>%
   mutate(layer=allNodes$layer[match(type.from,allNodes$type)],
          hop=allNodes$layer[match(type.to,allNodes$type)])
CX_outGraph
```

We then count how many connections for each source layer/target layer exist in the full graph, by number of types reached (`nTypes`), or by number of neurons reached (`nNeurons`, this simplifies by assuming all instances of a type are reached. Not unreasonable given that those are significant type to type connections in a very large graph.) in `overallFlowRef`. We also keep the information about the total number of types/neurons in `overallGraphNode`. We're going to use those two objects to build a graph object for the panel.
```{r}
overallFlowRef <- CX_outGraph %E>% as_tibble() %>% 
   group_by(layer,hop) %>% 
   summarize(nTypes=length(unique(type.to)),
             nNeurons=sum(n_type[match(unique(type.to),type.to)])) %>% ungroup()

overallGraphNodes <- CX_outGraph %N>% as_tibble() %>% 
   group_by(layer) %>% 
   summarize(nTypes=length(unique(type)),
             nNeurons=sum((CX_outGraph %E>% as_tibble())$n_type[match(unique(type),(CX_outGraph %E>% as_tibble())$type.to)]))%>% ungroup()

## Layer 0 number of neurons need to be manually inputed
overallGraphNodes$nNeurons[1] <- nrow(CXOutputNeurons)
head(overallFlowRef)
```

We then reformat the table and create a tidy graph objects from them:
```{r}
overallGraphNodes <- mutate(overallGraphNodes,name=layer,
                            label=case_when(layer==0 ~ "CX output",
                                            layer>=1 ~ paste0("Layer ",layer)))
overallFlowRef <- mutate(overallFlowRef,from=layer+1,to=hop+1) %>% filter(from>=0)
overallGraph <- tbl_graph(nodes=overallGraphNodes,edges=overallFlowRef,node_key = "name")
```

Finally, we generate the graph using `ggraph`:
```{r}
overallGraphPlot <- ggraph(overallGraph,layout="linear") +
   geom_edge_arc(aes(color=as.factor(.N()$layer[from]),width=nNeurons)) +
   geom_edge_loop(aes(color=as.factor(.N()$layer[from]),width=nNeurons)) +
   geom_node_point(aes(size=nNeurons,fill=as.factor(layer)),shape=21) + theme_paper_map() +
   geom_node_text(aes(label=paste0(label,"\n",nNeurons," neurons"),fontface="bold",fontsize=6),nudge_y=0.5)+ 
   scale_fill_paletteer_d("ggthemes::Color_Blind") +
   scale_edge_color_manual(values=paletteer_d("ggthemes::Color_Blind")[1:6]) + 
   guides(fill="none",edge_color="none",size="none") + scale_edge_width(name="# neurons contacted") + theme(plot.margin = margin(t=30))
overallGraphPlot
```
And we save it:
```{r}
save_plot(file.path(outputsFolder,"generalFlow.svg"),overallGraphPlot,ncol=2,nrow=1)
```

## Measuring convergence and recurrence (panel B)

First, we're getting a raw number of divergence and convergence (expressed as number of target types or target neurons) for every type in the graph: 
```{r}
allNeurons_divergence <- group_by(CX_outGraph %E>% as_tibble(),type.from) %>% summarize(divergenceType=n(),
                                                                       divergenceNeuron=sum(n_type)) %>% ungroup()
allNeurons_convergence <- group_by(CX_outGraph %E>% as_tibble(),type.to) %>% summarize(convergenceType=n()) %>% ungroup()
head(allNeurons_divergence)
```

We then recursively build a table that keeps track, for each layer, of:
- the number of types (`n_types`) and neurons (`n_neurons`) in the layer 
- the number of types targeted by the previous layer (`total_types`), which is necessarily larger than `n_types` because of convergence
- the predicted number of types from the mean divergence in each layer (`divergence_types`). It is necessarily larger than `total_types` because of convergence (and exponentially so)
`mean_divergence_type` is the mean divergence for the types present in the layer (only used in intermediate calculations).
```{r}
divergenceTableTot <- data.frame(n_hops=0,
                                 n_types=length(CXOutputTypes),
                                 n_neurons=nrow(CXOutputNeurons),
                                 mean_divergence_type=mean(allNeurons_divergence[allNeurons_divergence$type.from %in% CXOutputTypes,]$divergenceType),
                                 divergence_types=length(CXOutputTypes),
                                 total_types=length(CXOutputTypes)
                                 )

for (n in 1:5){
   divergenceTableTot <- rbind(divergenceTableTot,
   data.frame(n_hops=n,
              n_types=nrow(distinct(pathways[pathways$hop.to==n & pathways$n_steps==n ,],type.to)),
              n_neurons=sum(distinct(pathways[pathways$hop.to==n & pathways$n_steps==n,],type.to,n_type)$n_type),
              mean_divergence_type = mean(allNeurons_divergence[allNeurons_divergence$type.from %in% CX_outPaths[[n]]$type.from,]$divergenceType),
              total_types=nrow(distinct(CX_outPaths[[n]],type.to))) %>% mutate(divergence_types=divergenceTableTot[divergenceTableTot$n_hops==n-1,]$divergence_types * mean_divergence_type))
}

head(divergenceTableTot)
```

We then pivot the table to a long format (using `tidyr`) for convenient plotting:
```{r}
divergenceTableTotLongTypes <- pivot_longer(divergenceTableTot,cols=contains("types"),names_to = "Measure") %>%
   mutate(Measure=case_when(Measure == "divergence_types" ~ "divergence projection",
                            Measure == "n_types" ~ "types in layer",
                            Measure == "total_types" ~ "# targets from previous layer")) %>%
   mutate(Measure=factor(Measure,levels=c("divergence projection","# targets from previous layer","types in layer")))
```

Then generate the plot:
```{r}
totalDivergencePlot <- ggplot(divergenceTableTotLongTypes,aes(x=n_hops,y=value)) +
   geom_line(aes(col=Measure)) + theme_paper() + 
   scale_y_log10(limits=c(NA,16000)) +xlab("layer") + ylab("# types") +
   scale_color_grey(start = 0.8, end = 0.2)+
   geom_hline(yintercept =nrow(allNodes),lty=4,col="grey") + 
   annotate(geom="segment",x=5,xend=5,y=divergenceTableTot$n_types[6],yend=divergenceTableTot$total_types[6],arrow=arrow(ends="both",type="closed",length=unit(2,"mm"))) +
   annotate(geom="text",x=2,y=15500,label=paste0(sum(divergenceTableTot$n_types)," types/",sum(divergenceTableTot$n_neurons)," neurons total")) + 
   annotate(geom="text",x=3,y=1000,label=paste0("mean divergence: ",format(mean(allNeurons_divergence$divergenceType),digits=3),"\n",
                                                   "mean convergence: ",format(mean(allNeurons_convergence$convergenceType),digits=3)),hjust=0) +
   annotate(geom="text",x=4.85,y=5000,angle=90,label="recurrence") +
   theme(legend.position=c(0.2,0.2))

totalDivergencePlot
```
Then save it:
```{r}
save_plot(file.path(outputsFolder,"total_divergence.svg"),totalDivergencePlot,ncol = 0.7)
```

## Total number of neurons reached per CX output type (panel E)
We build a table (again recursively) that keep track of the number of neurons reached in every layer by pathways originitating from given CX output types (using the `pathways` object we built earlier):
```{r}
divergenceTablePerType <- data.frame(n_hops=rep(0,length(CXOutputTypes)),
                                     type.from=CXOutputTypes,
                                     n_types=rep(1,length(CXOutputTypes)))
 
for (n in 1:5){
   divergenceTablePerType <- rbind(divergenceTablePerType,
   data.frame(type.from=CXOutputTypes) %>% mutate(
               n_hops=n,
               n_types=sapply(type.from,function(ty) nrow(pathways[pathways$n_steps==n & pathways$type.from==ty,]))))  
}

# pathways$hop.to==n & 

divergenceTablePerType <- supertype(mutate(divergenceTablePerType,databaseType=type.from,type=type.from)) %>% selectSupertypeSet(exceptions=list("PFL"=1,"EL"=3,"EPG"=3,"PEG"=3))
```


```{r}
nReachedPlot <- ggplot(divergenceTablePerType,aes(x=type.from,y=n_types)) + geom_col(aes(fill=as.factor(n_hops))) + scale_fill_manual(name="# steps",values=paletteer_d("ggthemes::Color_Blind")[1:6])+ theme_paper()+ theme(strip.text.x=element_blank(),axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5))+facet_grid(.~supertype3,scales = "free",space="free") +ylab("# types reached") + xlab("CX output types")
nReachedPlot
```
Then save the plot:
```{r}
save_plot(file.path(outputsFolder,"reachability.svg"),nReachedPlot,ncol=2,nrow=1)
```

## Composition of different layers of the graph (panels C and D)
We're going to use the `pathways` object created earlier. First, we add a column with a convenient supertyping (and we make it a factor):
```{r}
pathways <- mutate(pathways,supertype3.to=allNodes$supertype3[match(type.to,allNodes$type)])

pathways$supertype3.to <- factor(pathways$supertype3.to,levels=c("Unassigned","Terra incognita","EB Columnar","ER","ExR","FB Columnar","FB Output","FB Tangential","PB Input","LNO","SA","DN","Visual PNs","Fru","Antennal lobe","KC","MBON","DAN","LH","OA","5HT","Peptidergic","Clock","Other Sensory"))
```

We then summarize it at two level of groupings. `pathwaysSummary` is used for the bar plot, `pathwaysSuperSummary` to get the value of the total pathway weights received in each layer:
```{r}
pathwaysSummary <- group_by(pathways,supertype3.to,hop.to) %>%
   summarize(pathWeight=sum(Path_weight),nTypes=length(unique(type.to))) %>% ungroup() %>%
   group_by(hop.to) %>% 
   mutate(normalizedPathWeight=pathWeight/sum(pathWeight),normalizedNTypes=nTypes/sum(nTypes)) %>% #normalize
   ungroup() %>% filter(hop.to>0)

pathwaysSuperSummary <- group_by(pathwaysSummary,hop.to) %>% summarize(totalWeight=sum(pathWeight))
```
We then generate the two plots (the second one focuses on the known types that are not CX types):
```{r}
outputComposition <- ggplot(pathwaysSummary,aes(x=hop.to,y=normalizedPathWeight,fill=supertype3.to)) +
   geom_col() + theme_paper() + 
   scale_fill_manual(values=supertype3Palette,name="supertype")+ 
   xlab("layer")+ylab("normalized weight received") + 
   theme(strip.background=element_rect(fill = "grey80",color=NA)) +
   scale_y_continuous(breaks=c(0,0.2,0.4,0.6,0.8,1))+
   geom_text(data=pathwaysSuperSummary,aes(x=hop.to,y=1.03,label=format(totalWeight,digits=1,scientific=FALSE)),inherit.aes = F,size=5*mm2pt*1.327492) +
   geom_point(data=pathwaysSuperSummary,aes(x=hop.to,y=1.1,size=totalWeight),inherit.aes = F) + scale_size(limits=c(0,28)) + guides(size="none")

outputCompositionZoom <-  ggplot(filter(pathwaysSummary,hop.to>0 & supertype3.to %in% c("5HT","Antennal lobe","Clock","DAN","DN","Fru","KC","LH","MBON","OA","Peptidergic","Visual PNs")),aes(x=hop.to,y=normalizedPathWeight,fill=supertype3.to)) + geom_col() + theme_paper() + scale_fill_manual(values=supertype3Palette,name="Supertype")+ xlab("layer")+ylab("normalized weight received")+ 
   theme(strip.background=element_rect(fill = "grey80",color=NA)) +
   geom_point(data=pathwaysSuperSummary,aes(x=hop.to,y=0.08,size=totalWeight),inherit.aes = F)+
   scale_size(limits=c(0,28)) +guides(fill="none",size="none")


outputComposition
outputCompositionZoom
```
Finally we save those two plots:
```{r}
save_plot(file.path(outputsFolder,"outputsComposition.svg"),outputComposition,ncol=0.7)
save_plot(file.path(outputsFolder,"outputsCompositionZoom.svg"),outputCompositionZoom,ncol=0.4)
```


