---
title: "CX to CX motifs, figure 58"
output: html_notebook
---

## Preparing the environment
```{r}
#library(neuprintr)
#library(tidyverse)
#library(cowplot)
#library(patchwork)
library(dplyr)
library(neuprintrExtra)
#library(nat)
#library(Cairo)
library(paletteer)
#library(ggraph)
#library(tidygraph)
```

```{r message=FALSE}
source("outputFunctions-display.R")
source(file.path("..","R","paperTheme.R"))
#source("../R/neuronMeshes.R")
source(file.path("..","R","table2ggraphUtils.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure58-CX2CX-Motifs"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
# The pathway weights for all targets
CXoutFull <- readRDS(file.path(dataFolder,"pathwayWeightsTable.rds"))
# Base metadata
load(file.path(dataFolder,"outputsBasics.RData"))
```

## Create the data frame of motifs
We first select all CX to CX connections to look for motifs in. 
We exclude projections to CX neurons that are mostly axonal, and consider only connections with pathway weights over 0.5%.
```{r}
CXOutAxonals <- filter(CXOutsideTypes,downstreamRatio>0.75)

CX2CXaxDendMat <- filter(CXoutFull,
                         databaseType.to %in% CXOutsideTypes$databaseType &
                            !databaseType.to %in% CXOutAxonals$databaseType &
                            databaseType.from != databaseType.to) %>%
   mutate(roi="outside") %>% supertype() %>% filter(Path_weight>0.005)
head(CX2CXaxDendMat)
```
We then build the connection tables for the recipient types in the CX neuropils (we also make a graph object of it):
```{r}
recurrentInCXBag <- neuronBag(filter(CXNeurons,type %in% unique(c(CX2CXaxDendMat$type.from,CX2CXaxDendMat$type.to))),
                              renaming = cxRetyping,
                              omitInputs = T,
                              slctROI=c("EB","FB","NO(R)","NO(L)","PB"))

allRecurrentCX <- recurrentInCXBag$outputs
allRecurrentGraph <- makeGraph(allRecurrentCX)
allRecurrentGraph
```

## Example motifs (panels B,C,D)

### Canonical feedback (panel B)
#### Bodyids for renderings:
PFL1 to FB2B_b. Bodyids to be used in renderings:
```{r}
PFL1bodies <- getTypesTable("PFL1") %>% cxRetyping() %>% filter(type=="PFL1_L*")
PFL1bodies$bodyid
```

```{r}
FB2BBodies <- getTypesTable("FB2B_b") %>% cxRetyping() %>% filter(type=="FB2B_b_R")
FB2BBodies$bodyid
```

#### PFL1 network motifs
We use the `plotMotifs` function, defined in "outputFunctions-display", that takes as input the connections tables in the two neuropils (or sets of neuropils) we're considering, the neuron of interest (at the center of the motif graph) and the stat considered:
```{r}
canMot <- plotMotifs(getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),
                                      allRecurrentCX,
                                      "PFL1_L*","Path_weight"))
canMot
```

### Parallel connections (panel C)
#### Bodyids for renderings:
FB6T to FB6E. 
```{r}
FB6Tbodies <- getTypesTable("FB6T") %>% cxRetyping() %>% filter(type=="FB6T_R")
FB6Tbodies$bodyid
```

```{r}
FB6Ebodies <- getTypesTable("FB6E") %>% cxRetyping() %>% filter(type=="FB6E_R")
FB6Ebodies$bodyid
```

#### FB6T network motifs:
```{r}
parMot <- plotMotifs(getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),
                                      allRecurrentCX,"FB6T_R","Path_weight"))
parMot
```

### Linked targets (panel D)
#### Bodyids for renderings
FB8F_a to FB6C_a/FB6C_b/FB6G/FB6I. 
```{r}
FB8Fabodies <- getTypesTable("FB8F_a") %>% cxRetyping() %>% filter(type=="FB8F_a_R")
FB8Fabodies$bodyid
```

```{r}
FB8FTargetsbodies <- getTypesTable(c("FB6C_a","FB6C_b","FB6G","FB6I")) %>% cxRetyping() %>% filter(grepl("_R",type))
FB8FTargetsbodies$bodyid
```

#### FB8F_a network motifs:
```{r}
linkMot <- plotMotifs(getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),allRecurrentCX,"FB8F_a_R","Path_weight"))
linkMot
```


## Motifs prevalence summary (panel E):


```{r}
recurrentMotifsSummary <- group_by(CX2CXaxDendMat,type.from,supertype1.from,supertype3.from) %>% summarize("CX Parallel connection"=sum(paste0(type.from,type.to) %in% paste0(allRecurrentCX$type.from,allRecurrentCX$type.to))/n(),
                                                "CX Canonical feedback"=sum(paste0(type.to,type.from) %in% paste0(allRecurrentCX$type.from,allRecurrentCX$type.to))/n(),
                                                "Linked targets in CX"=if (n()==1) 0 else sum(as.vector(combn(type.to,2,paste0,collapse="")) %in%
                                                                          c(paste0(allRecurrentCX$type.from,allRecurrentCX$type.to),paste0(allRecurrentCX$type.to,allRecurrentCX$type.from)))/(choose(n(),2))
                                                ) %>% pivot_longer(c("CX Parallel connection","CX Canonical feedback","Linked targets in CX"),names_to="stat",values_to="Proportion") %>% mutate(type.fromF = factor(type.from,levels=typesCXOrder),
                                                                                                                                                             stat=factor(stat,levels=c("CX Parallel connection","CX Canonical feedback","Linked targets in CX")))

recurrentMotifSuperSummary <- recurrentMotifsSummary %>% group_by(supertype1.from,supertype3.from,stat) %>% 
   summarize(Proportion=mean(Proportion))
```
```{r}
recurrentMotifsPrevalence <- ggplot(recurrentMotifsSummary ,aes(x=type.fromF,y=stat)) + geom_point(size=3,color="grey90")+ geom_point(aes(size=Proportion,color=stat))  + facet_grid(.~supertype3.from,scale="free",space="free")+ theme_paper() + theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.text.x = element_text(angle=90)) + xlab("CX output type") + scale_size_area(name="Prevalence",max_size = 3) + ylab("motif") + scale_color_paletteer_d(name="Motif","ggthemes::Traffic")

motifPal <- c("Plum",paletteer_d("ggthemes::Traffic")[1:3])
names(motifPal) <- c("Out of CX pathways","CX Parallel connection","CX Canonical feedback","Linked targets in CX")


recurrentMotifsPrevalence
```

## Example motifs

#### Canonical feedback
PFL1 to FB2B_b. Bodyids to be used in renderings:
```{r}
PFL1bodies <- getTypesTable("PFL1") %>% cxRetyping() %>% filter(type=="PFL1_L*")
PFL1bodies$bodyid
```

```{r}
FB2BBodies <- getTypesTable("FB2B_b") %>% cxRetyping() %>% filter(type=="FB2B_b_R")
FB2BBodies$bodyid
```

```{r}
PFL1Synapses <- neuprint_get_synapses(PFL1bodies$bodyid,roi=c("LAL(R)","CRE(R)")) %>% filter(prepost==0, partner %in% FB2BBodies$bodyid) %>% mutate(synapseType="Out of CX pathways")
FB2BSynapses <- neuprint_get_synapses(FB2BBodies$bodyid,roi="FB") %>% filter(prepost==0, partner %in% PFL1bodies$bodyid) %>% mutate(synapseType="CX Canonical feedback")
```

```{r}
displayAnatomies(neurons=list("Terra incognita"=PFL1bodies$bodyid,"FB Tangential"=FB2BBodies$bodyid),
                 synapses=rbind(PFL1Synapses,FB2BSynapses),
                 ROIs = c("FB","PB","LAL(R)"),saveName ="PFL1-FB2B",neuronPalette = supertype3Palette,synapseCluster = "synapseType",synapsePalette = motifPal,size=8)
```
```{r}
canFBViews <- ggdraw(xlim = c(0,2)) + 
   draw_image(paste0(outputsFolder,"PFL1-FB2B-front.png"),scale=1.6,clip="on") + 
   draw_image(paste0(outputsFolder,"PFL1-FB2B-side.png"),scale=1.6,hjust=-0.9,clip="on") + 
   theme_paper_map()
#canFBViews
```

```{r}
canMot <- plotMotifs(getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),allRecurrentCX,"PFL1_L*","Path_weight"))
canMot
```

#### Parallel
FB6T to FB6E

```{r}
FB6Tbodies <- getTypesTable("FB6T") %>% cxRetyping() %>% filter(type=="FB6T_R")
FB6Ebodies <- getTypesTable("FB6E") %>% cxRetyping() %>% filter(type=="FB6E_R")

FB6ESynapses <- neuprint_get_synapses(FB6Ebodies$bodyid,roi=c("SIP(R)","SMP(R)")) %>% filter(prepost==1, partner %in% FB6Tbodies$bodyid)%>% mutate(synapseType="Out of CX pathways")
FB6TSynapses <- neuprint_get_synapses(FB6Tbodies$bodyid,roi="FB") %>% filter(prepost==0, partner %in% FB6Ebodies$bodyid)%>% mutate(synapseType="CX Parallel connection")
```

```{r}
displayAnatomies(neurons=list("Terra incognita"=FB6Tbodies$bodyid,"FB Tangential"=FB6Ebodies$bodyid),
                 synapses=rbind(FB6ESynapses,FB6TSynapses),
                 ROIs = c("FB","SIP(R)"),saveName ="FB6T-FB6E",neuronPalette = supertype3Palette,synapseCluster = "synapseType",synapsePalette = motifPal,size=8)

```

```{r}
parFBViews <- ggdraw(xlim = c(0,2)) + 
   draw_image(paste0(outputsFolder,"FB6T-FB6E-front.png"),scale=1.6,clip="on") + 
   draw_image(paste0(outputsFolder,"FB6T-FB6E-side.png"),scale=1.6,hjust=-1,clip="on") + 
   theme_paper_map() 
#parFBViews
```




#### Linked targets
FB8F_a to FB6C_a/FB6C_b/FB6G/FB6I

```{r}
FB8Fabodies <- getTypesTable("FB8F_a") %>% cxRetyping() %>% filter(type=="FB8F_a_R")
FB8FTargetsbodies <- getTypesTable(c("FB6C_a","FB6C_b","FB6G","FB6I")) %>% cxRetyping() %>% filter(grepl("_R",type))

FB8FSynapses <- neuprint_get_synapses(FB8Fabodies$bodyid,roi=c("SIP(R)","SLP(R)","SMP(R)")) %>% filter(prepost==0, partner %in% FB8FTargetsbodies$bodyid)%>% mutate(synapseType="Out of CX pathways")
FB6NetSynapses <- neuprint_get_synapses(FB8FTargetsbodies$bodyid,roi="FB") %>% filter(partner %in% FB8FTargetsbodies$bodyid)%>% mutate(synapseType="Linked targets in CX")
```

```{r}
displayAnatomies(neurons=list("Terra incognita"=FB8Fabodies$bodyid,"FB Tangential"=FB8FTargetsbodies$bodyid),
                 synapses=rbind(FB8FSynapses,FB6NetSynapses),
                 ROIs = c("FB","SIP(R)"),saveName ="FB8F-FB6",neuronPalette = supertype3Palette,synapseCluster = "synapseType",synapsePalette = motifPal,size=8)
```

```{r}
linkFBViews <- ggdraw(xlim = c(0,2)) + 
   draw_image(paste0(outputsFolder,"FB8F-FB6-front.png"),scale=1.6,clip="on") + 
   draw_image(paste0(outputsFolder,"FB8F-FB6-side.png"),scale=1.6,hjust=-1,clip="on") + 
   theme_paper_map() 
#linkFBViews
```


#### Figure 4
```{r}
layout <- c(
   area(t=2,b=4,l=1,r=10),
   area(t=5,b=11,l=1,r=7),
   area(t=6,b=10,l=8,r=10),
   area(t=12,b=18,l=1,r=7),
   area(t=13,b=17,l=8,r=10),
   area(t=19,b=25,l=1,r=7),
   area(t=20,b=24,l=8,r=10),
   area(t=26,b=28,l=1,r=10)
)

save_plot(paste0(outputsFolder,"outputs-canMot.svg"),canMot,ncol=6,nrow=6,base_width = 8.5/10,base_height=11/28)
save_plot(paste0(outputsFolder,"outputs-parMot.svg"),parMot,ncol=6,nrow=6,base_width = 8.5/10,base_height=11/28)
save_plot(paste0(outputsFolder,"outputs-linkMot.svg"),linkMot,ncol=6,nrow=6,base_width = 8.5/10,base_height=11/28)
save_plot(paste0(outputsFolder,"outputs-prevalences.svg"),recurrentMotifsPrevalence,ncol=1.3,nrow=6,base_width = 8.5,base_height=11/28)

figure4 <- guide_area() + canFBViews + canMot + parFBViews + parMot + linkFBViews + linkMot + (recurrentMotifsPrevalence + plot_layout(guides="keep")) + plot_layout(design=layout,guides="collect") + plot_annotation(tag_levels="A",title="Outputs figure 4: CX to CX motifs",theme=theme(title=element_text(size=12,face="bold")))& theme(plot.tag.position = c(-0.05, 1.05))

#figure4 <- canFBViews / parFBViews / linkFBViews/ (canMot+parMot+linkMot+plot_layout(guides = "collect",widths=1)) / recurrentMotifsPrevalence + plot_layout(heights=c(3,3,3,2,1)) + plot_annotation(tag_levels="A",title="Outputs figure 4: CX to CX motifs")
#figure3_2
```

```{r}
save_plot(paste0(outputsFolder,"outputs-Figure4.pdf"),figure4,ncol=1,nrow=4,base_width = 8.5,base_height = 11/4,device=cairo_pdf)
```

#### SI Motifs
Plot Motifs for individual original neurons, at different depths
```{r}
#for (sty in unique(CX2CXaxDendMat$supertype3.from)){
#   localDf <- filter(CX2CXaxDendMat,supertype3.from==sty)
#   allMotifPlots <- lapply(unique(localDf$type.from),function(ty){
#      motifDf <- getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),allRecurrentCX,ty,"Path_weight")
#      if(!is.null(motifDf)){
#      motifPlot <- plotMotifs(motifDf) + ggtitle(ty)}else{NULL}
#   })
#   allMotifPlots <- allMotifPlots[!is.null(allMotifPlots)]
#   motPlot <- patchwork::wrap_plots(allMotifPlots,ncol=3,widths=1,guides = "collect")
#   save_plot(paste0(outputsFolder,"outputs-Figure4-SI2-",sty,".pdf"),motPlot,ncol=3,nrow=ceiling(length(allMotifPlots)/3),base_width = 8.5/3,base_height = 11/6,device=cairo_pdf)
#}


allMotifPlots <- lapply(sort(factor(unique(CX2CXaxDendMat$type.from),levels= typesCXOrder)),
                        function(ty){
      motifDf <- getMotifsGraphDf(mutate(CX2CXaxDendMat,roi="Outside"),allRecurrentCX,ty,"Path_weight")
      if(!is.null(motifDf)){
      motifPlot <- plotMotifs(motifDf) + ggtitle(ty)}else{NULL}
   })
   allMotifPlots <- allMotifPlots[!is.null(allMotifPlots)]
   motPlot <- patchwork::wrap_plots(append(list(legend=guide_area()),allMotifPlots),ncol=4,widths=1,guides = "collect") + plot_annotation(title="Outputs figure 4 - SI1: All CX to CX Motifs",theme=theme(plot.title=element_text(size=12,face="bold")))
   save_plot(paste0(outputsFolder,"outputs-Figure4-SI1.svg"),motPlot,ncol=3,nrow=ceiling(length(allMotifPlots)/4),base_width = 8.5/3,base_height = 11/6)


```