---
title: "Outputs figure : CX neurons innervation outside the CX (figure 54)"
output: html_notebook
---

This notebook generates the panels for the first outputs figure (figure 54).
## Preparing the environment
```{r}
library(ggplot2)
library(dplyr)
library(paletteer)
```
Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source(file.path("..","R","paperTheme.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure54-CXOutputs"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Loading some objects necessary to generate the figures (created in "Outputs-Core.Rmd")"
```{r}
load("outputsBasics.RData")
```

## What do their respective innervation patterns look like ?
### As a neuropil innervation plot (panel A)
Generate a ROI set and palette restricted to the output neuropils:
```{r}
roiH <- getRoiTree()
roisOut <- selectRoiSet(roiH,exceptions=list("LAL(R)"=4,"CRE(R)"=4))
roisOut <- roisOut %>% filter((!(level2 %in% c("ATL(L)","ICL(L)"))) & (!level1 %in% "CX")) 
roiOutLabels <- selectRoiSet(roiH,default_level = 0)
rPal <- roisPalette(rois = roiOutLabels)
```

Generate the summary per ROI, limiting to neuropils with at least 20 downstream synapses:
```{r}
CXOutputSummary <- getROISummary(CXOutputNeurons,threshold=20) %>% filter(downstream>20)
head(CXOutputSummary)
```

Generate the plot and save it:
```{r}
outputsInnervation_R <- haneschPlot(CXOutputSummary,roiSelect = roisOut,grouping = "supertype3",roiLabel = roiOutLabels,flip=T,theme = theme_paper_grid(),showCount = T)
outputsInnervation_R
save_plot(file.path(outputsFolder,"outputs-Hanesch.svg"),outputsInnervation_R,ncol=1.3,nrow=7,base_width = 8.5,base_height = 11/15)
```

### As synapses in an anatomical frame (panel B)
First load the synapses (the data frame was generated in "Outputs-Core.Rmd"):
```{r}
CXOutSyn <- readRDS("CX-outsideSynapses.rds")
```

Then generate and save the 2 views of the rendering as pngs. The `displayAnatomies` function is defined in "outputFunctions-display.R":
```{r}
displayAnatomies(synapses=CXOutSyn,
                 ROIs=c("EB","FB","PB","NO","LAL(R)","BU(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "allOuts-pale4",
                 saveFolder=outputsFolder,
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customSupertype",
                 size = c(3000,3000))
```

## Total relative weight contributed by individual types to output network (panel C)

Get the connections for just the first step of the output networks from the object generated in the "Ouptuts-Core.Rmd" notebook:
```{r}
firstStep <- readRDS("output_paths.rds")[[1]]
```

We then summarize this table per CX type of origin:
```{r}
firstStageSummary <- firstStep %>% supertype() %>% 
   group_by(type.from,supertype3.from) %>% 
   summarize(totalWeight=sum(weightRelative),totalWeightRaw=sum(absoluteWeight),totalDown=sum(totalPreROIweight*n_from),meanDown=sum(totalPreROIweight)) %>% 
   filter(totalWeightRaw>20)

firstStageSummary$supertype.from <- CXOutputNeurons$customSupertype[match(firstStageSummary$type.from,CXOutputNeurons$type)]
```
Then generate the plot of synapse counts:
```{r}

countsSummary <- ggplot(firstStageSummary,aes(x=type.from,y=totalWeightRaw,color=supertype.from)) + geom_point() + 
   scale_color_manual(name="synapses from",values=customSupertypePalette) + theme_paper() + 
   facet_grid(.~supertype3.from,scales = "free",space="free") + ylab("# downstream synapses") + xlab("CX type") + theme(strip.text.x=element_blank(),axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5)) + scale_y_log10()
countsSummary
```
And save it:
```{r}
save_plot(file.path(outputsFolder,"outputs-Counts.svg"),countsSummary,ncol=1.3,nrow=3,base_width = 8.5,base_height = 11/15)
```


