---
title: "Pathways to known endpoints figure"
output: html_notebook
---
## Prepare the environment:

Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source(file.path("..","R","paperTheme.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure60-KnownTargets"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
## Known types in the output graph
knownTypesTable <- readRDS(file.path(dataFolder,"known-table.rds"))
## The normalized pathway weights to known neurons table
endpointsInfluence <- readRDS(file.path(dataFolder,"endpoints-influence.rds"))
mainEndpointInfluencers <- readRDS(file.path(dataFolder,"main-endpoints.rds"))

## Information about the main targets in the graph
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))

## The pathway weights table
CXoutFull <- readRDS(file.path(dataFolder,"pathwayWeightsTable.rds"))
```

## Contributions to known pathways (panels A and B)
We generate a palette, consistent with the palettes used in the rest of the section (but with the CX simplified to one category, as well as all uninformative types):
```{r}
endpointsPalette <- c("Unknown"="grey80",
                      "CX"=p36[2],
                      "5HT"=p36[14],
                      "OA"=p36[16],
                      "Peptidergic"=p36[28],
                      "DAN"=p36[29],
                      "MBON"=p36[4],
                      "LH"=p36[31],
                      "DN"=p36[24],
                      "Fru"=p36[30],
                      "KC"=p36[13],
                      "Antennal lobe"=p36[20],
                      "Clock"=p36[6],
                      "Visual PNs"=p36[32],
                      "Other Sensory"=p36[3])

endpointsLevels <- c(  "Unknown",
                       "CX",
                       "5HT",
                       "OA",
                       "Peptidergic",
                       "DAN",
                       "MBON",
                       "LH",
                       "DN",
                       "Fru",
                       "KC",
                       "Antennal lobe",
                       "Clock",
                       "Visual PNs",
                       "Other Sensory")
```

We then generate a summary of the normalized pathway weights for all the strong CX output types contributors:
```{r}
endpointsInfluenceSummary <- group_by(filter(endpointsInfluence,
                                             type.from %in% mainFFConns$mainContributor),
                                      type.from,supertype3.from,supertype.to) %>%
  summarize(Path_weight=sum(Path_weight)) %>%
  mutate(supertype.to=factor(supertype.to,levels=endpointsLevels)) %>%
  ungroup()
```
One infers the contribution made to pathway not ending on any known type by substracting the full weights from 1, and add it to the summary data frame:
```{r}
unknownInfluence <- group_by(endpointsInfluenceSummary,type.from,supertype3.from) %>%
  summarize(supertype.to="Unknown",Path_weight=1-sum(Path_weight)) %>% 
  ungroup()

endpointsInfluenceSummary <- rbind(endpointsInfluenceSummary,unknownInfluence)
```
We then remove the pathways ending on the CX from this summary (we only want to cover feed forward targets):
```{r}
endpointsInfluenceSummary <- filter(endpointsInfluenceSummary,
                                          supertype.to != "CX" & 
                                            type.from %in% mainFFConns$mainContributor)
```

Finally, one generates the two versions of the plot used in the figure (one includes the unknowns, the other one doesn't):
```{r}
endpointsComposition <- ggplot(endpointsInfluenceSummary,aes(x=type.from,y=Path_weight)) +
  geom_col(aes(fill=supertype.to)) + 
  scale_fill_manual(name="target supertype",values=endpointsPalette)+ 
  theme_paper(axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5),
              strip.background.x=element_rect(color="black"))+ 
  facet_grid(.~supertype3.from,scales = "free",space="free") +
  ylab("normalized pathway weight") + xlab("CX output type")

endpointsCompositionKnown <- ggplot(filter(endpointsInfluenceSummary,
                                           supertype.to != "Unknown"),
                                    aes(x=type.from,y=Path_weight)) +
  geom_col(aes(fill=supertype.to)) + 
  scale_fill_manual(name="target supertype",values=endpointsPalette)+ 
  theme_paper(axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5),
              strip.text.x=element_blank())+ 
  facet_grid(.~supertype3.from,scales = "free",space="free") + 
  ylab("normalized pathway weight") + xlab("CX output type")

endpointsComposition 
endpointsCompositionKnown
```
Save the plots:
```{r}
save_plot(file.path(outputsFolder,"endpointsComposition.svg"),
          endpointsComposition,ncol=1.5,nrow=0.6)

save_plot(file.path(outputsFolder,"endpointsCompositionKnown.svg"),
          endpointsCompositionKnown,ncol=1.5,nrow=0.6)
```

## CX influence received by the main known targets
We then work directly with pathway weights, selecting for types that both receive at least 0.5% of pathway weight from the central complex and are part of the "known" neurons. We relabel the supertypes to end up with a manageable number of levels (we pool together the types that contribute close to nothing to output pathways):
```{r}
CXoutFFEndpoints <- filter(CXoutFull,
                           type.to %in% endpointsInfluence$type.to & 
                             type.to %in% mainFFConns$type.to & 
                             fullCXwr>0.005) %>%
  mutate(supertype.to=knownTypesTable$supertype[match(type.to,knownTypesTable$type)],
         customType.from=CXOutputNeurons$customSupertype[match(databaseType.from,
                                                               CXOutputNeurons$databaseType)],
         customTypeFig = case_when(customType.from %in% c("EB Columnar",
                                                          "ExR2-6",
                                                          "FB4",
                                                          "FB5",
                                                          "FB6-7",
                                                          "FS3",
                                                          "FS4","PFR_a") ~ "Other",
                                   TRUE ~ customType.from)) 
## Relabel so that the antennal lobe label fits the plot
CXoutFFEndpoints$supertype.to[CXoutFFEndpoints$supertype.to=="Antennal lobe"] <- "AL"
```

Then generate the plot:
```{r}
CXFFInfl <- ggplot(CXoutFFEndpoints,aes(x=type.to,y=Path_weight)) +
  geom_col(aes(fill=customTypeFig))+ 
  scale_fill_manual(name="source supertype",
                    values=c(customSupertypePalette,"Other"="grey90"))+
  facet_grid(.~supertype.to,scale="free",space="free")+
  theme_paper(axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5),
              strip.background.x=element_rect(colour="black")) +   
  ylab("total pathway weight") + xlab("target type")

CXFFInfl 
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"mainCXTargets.svg"),
          CXFFInfl,ncol=0.8,nrow=0.8)
```





