---
title: "FB bump tracking"
output: html_notebook
---


```{r}
library(neuprintr)
library(tidyverse)
library(neuprintrExtra)
library(reshape2)
library(patchwork)
library(gridExtra)
source(file.path("..","PBFigures","PBAnalysisUtils.R"))
source(file.path("..","FBFigures","FBNetworkVisUtils.R"))
```

Function to convert a connection table into a weight matrix
```{r}
conTabToWM <- function(conTab, allPreIds, allPostIds){
  # Create a matrix of just the weights
  justWeights = matrix(0L,nrow=length(allPreIds),ncol=length(allPostIds))
  for (i in 1:length(allPreIds)){
    for (j in 1:length(allPostIds)){
      w = conTab[which(as.character(conTab$id.from) == as.character(allPreIds[i]) &
                         as.character(conTab$id.to) == as.character(allPostIds[j])),]$weight
      if (length(w) > 0)
        justWeights[i,j] = w
    }
  }
  
  rownames(justWeights) <- allPreIds
  colnames(justWeights) <- allPostIds 
  return(justWeights)
}
```


Create a bump in the EB
```{r}
gloms = c("R1","L8","R2","L7","R3","L6","R4","L5",
         "R5","L4","R6","L3","R7","L2","R8","L1")
actProfvM <- data.frame(act = vonMisesProf(),glom = gloms)
actProfvM$glom <- factor(actProfvM$glom,levels=gloms)

g_EB <- ggplot(actProfvM) + geom_line(aes(x=glom,y=act,group=1)) + theme_cowplot() + scale_x_discrete(expand = c(0,0)) + ggtitle('EB \"activity\"')
```

Move it to the PB (via EPG mapping)
```{r}
actProfvM <- rbind(actProfvM, data.frame(act = c(0,0), glom = c("L9","R9")))
glomOrder <- c("R9","R8","R7","R6","R5","R4","R3","R2","R1",
               "L1","L2","L3","L4","L5","L6","L7","L8","L9")
actProfvM$glom <- factor(actProfvM$glom,levels=as.factor(glomOrder))
actProfvM$LR <- lapply(actProfvM$glom, function(g) substring(g,1,1)) %>% unlist() %>% as.factor()

g_PB <- ggplot(actProfvM) + geom_line(aes(x=glom,y=act,group=1,color=LR)) + theme_cowplot() + scale_x_discrete(expand = c(0,0))  + ggtitle('PB \"activity\"') + guides(color=FALSE)
```

Look at how it moves to the D7s
```{r}

# Get the EPG to D7 connections and convert to a weight matrix
conTab <- getConnectionTable(getTypesTable("EPG")$bodyid,"POST","PB") %>% 
  filter(type.to == "Delta7")
conTab$id.from <- PBRename(conTab$name.from,conTab$from)
conTab$id.to <- PBRename(conTab$name.to,conTab$to)

WM <- conTabToWM(conTab,unique(conTab$id.from),unique(conTab$id.to))

# Get the EPG glomeruli
EPGDat <- data.frame(name = rownames(WM))
EPGDat$glom <- lapply(EPGDat$name, function(n) strsplit(strsplit(n,'_')[[1]][2],'-')[[1]][1]) %>% unlist() %>% as.character()
EPGDat$act <- lapply(EPGDat$glom, function(g) actProfvM$act[which(actProfvM$glom == g)]) %>% unlist() %>% as.numeric()

# Get the D7 activity per glomerulus
D7Dat <- data.frame(name = colnames(WM), act =  as.vector(EPGDat$act %*% WM))
D7Dat$glom1 <- lapply(D7Dat$name, function(n) substring(strsplit(n,'_')[[1]][2],1,2)) %>% unlist() %>% as.character()
D7Dat$glom2 <- lapply(D7Dat$name, function(n) substring(strsplit(n,'_')[[1]][2],3,4)) %>% unlist() %>% as.character()
D7Dat$glom3 <- lapply(D7Dat$name, function(n) substring(strsplit(n,'_')[[1]][2],5,6)) %>% unlist() %>% as.character()

D7Dat <- melt(D7Dat, id = c("name","act"), value.name = c("glom"))
D7Dat <- D7Dat[which(D7Dat$glom != ""),]

D7aveAct <- D7Dat %>% group_by(glom) %>% summarize(meanAct = mean(act))
D7aveAct$LR <- lapply(D7aveAct$glom, function(g) substring(g,1,1)) %>% unlist() %>% as.factor()
D7aveAct$glom <- factor(D7aveAct$glom, levels = as.factor(c("R9","R8","R7","R6","R5","R4","R3","R2","R1",
                                                          "L1","L2","L3","L4","L5","L6","L7","L8","L9")))
# Normalize
D7aveAct$meanAct <- D7aveAct$meanAct / max(D7aveAct$meanAct)

g_PB_D7 <- ggplot(D7aveAct) + geom_line(aes(x=glom,y=meanAct,group=1,color=LR)) + theme_cowplot() + scale_x_discrete(expand = c(0,0))  + ggtitle('D7 \"activity\"') + guides(color=FALSE)
```

Move it to the FB (via PFGs mapping)
```{r}
PFType <- "PFGs"

# Get the info for the PFX type
PFtypeDat <- getTypesTable(PFType)
PFtypeDat$gloms <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][2]) %>% unlist() %>% as.character()
PFtypeDat$LR <- lapply(PFtypeDat$gloms, function(g) substring(g,1,1)) %>% unlist() %>% as.factor()
PFtypeDat$cols <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][3]) %>% unlist() %>% as.character()
PFtypeDat$cols <- factor(PFtypeDat$cols, levels = unique(PFtypeDat$cols) %>% sort())
PFtypeDat$id <- FBRename(PFtypeDat$name,PFtypeDat$bodyid)

# Place the activity into the given type
PFtypeDat$act <- lapply(PFtypeDat$gloms, function(g) actProfvM$act[which(actProfvM$glom == g)]) %>% unlist() %>% as.numeric()

# Average over each column
colAve_PFGs <- PFtypeDat %>% group_by(cols,LR) %>% summarize(meanAct = mean(act))

# Plot the presynaptic "activity"
g_FB_PFGs <- ggplot(colAve_PFGs) + geom_line(aes(x=cols,y=meanAct,group=LR,color=LR)) +
    theme_cowplot() + scale_x_discrete(expand = c(0,0)) +
    ggtitle("PFGs") + guides(color=FALSE)
```

Move it to the FB (via PFL3 mapping)
```{r}
PFType <- "PFL3"

# Get the info for the PFX type
PFtypeDat <- getTypesTable(PFType)
PFtypeDat$gloms <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][2]) %>% unlist() %>% as.character()
PFtypeDat$LR <- lapply(PFtypeDat$gloms, function(g) substring(g,1,1)) %>% unlist() %>% as.factor()
PFtypeDat$cols <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][3]) %>% unlist() %>% as.character()
PFtypeDat$cols <- factor(PFtypeDat$cols, levels = unique(PFtypeDat$cols) %>% sort())
PFtypeDat$id <- FBRename(PFtypeDat$name,PFtypeDat$bodyid)

# Place the activity into the given type
PFtypeDat$act <- lapply(PFtypeDat$gloms, function(g) actProfvM$act[which(actProfvM$glom == g)]) %>% unlist() %>% as.numeric()

# Average over each column
colAve_PFL <- PFtypeDat %>% group_by(cols,LR) %>% summarize(meanAct = mean(act))

# Plot the presynaptic "activity"
g_FB_PFL <- ggplot(colAve_PFL) + geom_line(aes(x=cols,y=meanAct,group=LR,color=LR)) +
    theme_cowplot() + scale_x_discrete(expand = c(0,0)) +
    ggtitle("PFL3") + guides(color=FALSE)
```

Move it to the FB (via PFNd mapping)
```{r}
PFType <- "PFNd"

# Get the info for the PFX type
PFtypeDat <- getTypesTable(PFType)
PFtypeDat$gloms <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][2]) %>% unlist() %>% as.character()
PFtypeDat$LR <- lapply(PFtypeDat$gloms, function(g) substring(g,1,1)) %>% unlist() %>% as.factor()
PFtypeDat$cols <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][3]) %>% unlist() %>% as.character()
PFtypeDat$cols <- factor(PFtypeDat$cols, levels = unique(PFtypeDat$cols) %>% sort())
PFtypeDat$id <- FBRename(PFtypeDat$name,PFtypeDat$bodyid)

# Place the activity into the given type
PFtypeDat$act <- lapply(PFtypeDat$gloms, function(g) actProfvM$act[which(actProfvM$glom == g)]) %>% unlist() %>% as.numeric()

# Average over each column
colAve_PFN <- PFtypeDat %>% group_by(cols,LR) %>% summarize(meanAct = mean(act))

# Plot the presynaptic "activity"
g_FB_PFNd <- ggplot(colAve_PFN) + geom_line(aes(x=cols,y=meanAct,group=LR,color=LR)) +
    theme_cowplot() + scale_x_discrete(expand = c(0,0)) +
    ggtitle("PFNd") + guides(color=FALSE)
```

Copy the bump from a the R or L PFNd neurons to a second neuron and plot
```{r}
FPost <- "hDeltaA"

# Get the info for the postsynaptic FB type
FPostDat <- getTypesTable(FPost)
FPostDat$cols <- lapply(FPostDat$name, function(n) strsplit(n,'_')[[1]][3]) %>% unlist() %>% as.character()
FPostDat$cols <- factor(FPostDat$cols, levels = as.factor(c("C1","C2","C3","C4","C5","C6","C7","C8","C9","C10","C11","C12")))
FPostDat$id <- FBRename(FPostDat$name,FPostDat$bodyid)

# Get the connection table between the two types
conTab <- getConnectionTable(getTypesTable(PFType)$bodyid,"POST","FB") %>% filter(type.to == FPost)
conTab$id.from <- FBRename(conTab$name.from,conTab$from)
conTab$id.to <- FBRename(conTab$name.to,conTab$to)

# Get info about the pre and post neurons
allPreIds = PFtypeDat$id
allPostIds = FPostDat$id

# Create a matrix of just the weights
justWeights = matrix(0L,nrow=length(allPreIds),ncol=length(allPostIds))
for (i in 1:length(allPreIds)){
  for (j in 1:length(allPostIds)){
    w = conTab[which(conTab$id.from == allPreIds[i] & conTab$id.to == allPostIds[j]),]$weight
    if (length(w) > 0)
      justWeights[i,j] = w
  }
}

# Use the weights to get the downstream "activity"
act_L <- PFtypeDat$act
act_L[which(PFtypeDat$LR == "R")] <- 0 
FPostDat$act_L <- act_L %*% justWeights %>% as.vector()
FPostDat$act_L <- FPostDat$act_L / max(FPostDat$act_L)
act_R <- PFtypeDat$act
act_R[which(PFtypeDat$LR == "L")] <- 0 
FPostDat$act_R <- act_R %*% justWeights %>% as.vector()
FPostDat$act_R <- FPostDat$act_R / max(FPostDat$act_R)

# Average the activy across columns
colAve_hDA <- FPostDat %>% group_by(cols) %>% summarize(meanAct_L = mean(act_L),
                                                   meanAct_R = mean(act_R))

# Plot it
g_FB_hDA <- ggplot(colAve_hDA) + geom_line(aes(x=cols,y=meanAct_L,group="L"),color='red',linetype='dashed') +
  geom_line(aes(x=cols,y=meanAct_R,group="R"),color='cyan',linetype='dashed') +
  theme_cowplot() + scale_x_discrete(expand = c(0,0)) +
  ggtitle(paste0(PFType," -> ",FPost))
```

Move it to the FB (via PFNp_a mapping)
```{r}
PFType <- "PFNp_c"

# Get the info for the PFX type
PFtypeDat <- getTypesTable(PFType)
PFtypeDat$gloms <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][3]) %>% unlist() %>% as.character()
PFtypeDat$LR <- lapply(PFtypeDat$gloms, function(g) substring(g,1,1)) %>% unlist() %>% as.factor()
PFtypeDat$cols <- lapply(PFtypeDat$name, function(n) strsplit(n,'_')[[1]][4]) %>% unlist() %>% as.character()
PFtypeDat$cols <- factor(PFtypeDat$cols, levels = unique(PFtypeDat$cols) %>% sort())
PFtypeDat$id <- FBRename(PFtypeDat$name,PFtypeDat$bodyid)

# Place the activity into the given type
PFtypeDat$act <- lapply(PFtypeDat$gloms, function(g) actProfvM$act[which(actProfvM$glom == g)]) %>% unlist() %>% as.numeric()

# Average over each column
colAve_PFN <- PFtypeDat %>% group_by(cols,LR) %>% summarize(meanAct = mean(act))

# Plot the presynaptic "activity"
g_FB_PFNp_c <- ggplot(colAve_PFN) + geom_line(aes(x=cols,y=meanAct,group=LR,color=LR)) +
    theme_cowplot() + scale_x_discrete(expand = c(0,0)) +
    ggtitle("PFNp_c") + guides(color=FALSE)
```

Copy the bump from a the R or L PFNd neurons to a second neuron and plot
```{r}
FPost <- "vDeltaK"

# Get the info for the postsynaptic FB type
FPostDat <- getTypesTable(FPost)
FPostDat$cols <- lapply(FPostDat$name, function(n) strsplit(n,'_')[[1]][2]) %>% unlist() %>% as.character()
FPostDat$cols <- factor(FPostDat$cols, levels = as.factor(c("C0","C1","C2","C3","C4","C5","C6","C7","C8","C9")))
FPostDat$id <- FBRename(FPostDat$name,FPostDat$bodyid)

# Get the connection table between the two types
conTab <- getConnectionTable(getTypesTable(PFType)$bodyid,"POST","FB") %>% filter(type.to == FPost)
conTab$id.from <- FBRename(conTab$name.from,conTab$from)
conTab$id.to <- FBRename(conTab$name.to,conTab$to)

# Get info about the pre and post neurons
allPreIds = PFtypeDat$id
allPostIds = FPostDat$id

# Create a matrix of just the weights
justWeights = matrix(0L,nrow=length(allPreIds),ncol=length(allPostIds))
for (i in 1:length(allPreIds)){
  for (j in 1:length(allPostIds)){
    w = conTab[which(as.character(conTab$id.from) == as.character(allPreIds[i]) &
                       as.character(conTab$id.to) == as.character(allPostIds[j])),]$weight
    if (length(w) > 0)
      justWeights[i,j] = w
  }
}

# Use the weights to get the downstream "activity"
act_L <- PFtypeDat$act
act_L[which(PFtypeDat$LR == "R")] <- 0 
FPostDat$act_L <- act_L %*% justWeights %>% as.vector()
act_R <- PFtypeDat$act
act_R[which(PFtypeDat$LR == "L")] <- 0 
FPostDat$act_R <- act_R %*% justWeights %>% as.vector()
FPostDat$act_R <- FPostDat$act_R / max(FPostDat$act_R)

# Average the activy across columns
colAve_vDK <- FPostDat %>% group_by(cols) %>% summarize(meanAct_L = mean(act_L),
                                                   meanAct_R = mean(act_R))
colAve_vDK$meanAct_L <- colAve_vDK$meanAct_L / max(colAve_vDK$meanAct_L)
colAve_vDK$meanAct_R <- colAve_vDK$meanAct_R / max(colAve_vDK$meanAct_R)

# Plot it
g_FB_vDK <- ggplot(colAve_vDK) + geom_line(aes(x=cols,y=meanAct_L,group="L"),color='red',linetype='dashed') +
  geom_line(aes(x=cols,y=meanAct_R,group="R"),color='cyan',linetype='dashed') +
  theme_cowplot() + scale_x_discrete(expand = c(0,0)) +
  ggtitle(paste0(PFType," -> ",FPost))
```

Combine the plots and save
```{r}
actEBPBFB <- (g_EB | plot_spacer() | plot_spacer() | plot_spacer()) /
  (g_PB | g_PB_D7 | plot_spacer() | plot_spacer()) /
  (g_FB_PFGs | g_FB_PFNd | g_FB_PFNp_c | g_FB_PFL) /
  (plot_spacer() | g_FB_hDA | g_FB_vDK | plot_spacer())

print(actEBPBFB)
```