---
title: "FB Figure PFL inputs from the bump"
output: html_notebook
---

Load the libraries
```{r}
library(nat)
library(neuprintr)
library(neuprintrExtra)
library(reshape2)
library(patchwork)
source("..\\FBFigures\\FBNetworkVisUtils.R")
source("..\\R\\paperTheme.R")
source("..\\PBFigures\\PBAnalysisUtils.R")
source("..\\R\\visualizeConnectivityTables.R")
options(nat.plotengine = 'rgl')
```

Function to convert a connection table into a weight matrix
```{r}
conTabToWM <- function(conTab, allPreIds, allPostIds){
  # Create a matrix of just the weights
  justWeights = matrix(0L,nrow=length(allPreIds),ncol=length(allPostIds))
  for (i in 1:length(allPreIds)){
    for (j in 1:length(allPostIds)){
      w = conTab[which(as.character(conTab$nameOrder.from) == as.character(allPreIds[i]) &
                         as.character(conTab$nameOrder.to) == as.character(allPostIds[j])),]$weight
      if (length(w) > 0)
        justWeights[i,j] = w
    }
  }
  
  rownames(justWeights) <- allPreIds
  colnames(justWeights) <- allPostIds 
  return(justWeights)
}
```

Get the EPG neuron bag
```{r}
EPGBag <- neuronBag(getTypesTable("EPG"))
```

Get the EPG to PFL2,3 connectivity
```{r}
EPGToPFL23 <- EPGBag$outputs_raw %>% filter((type.to %in% c("PFL2","PFL3")) & (roi=="PB"))
EPGToPFL23$nameOrder.to <- PBRename(EPGToPFL23$name.to,EPGToPFL23$to)
EPGToPFL23$nameOrder.from <- PBRename(EPGToPFL23$name.from,EPGToPFL23$from)
```

Plot the EPG to PFL2,3 connectivity
```{r}
cmax=100

EPGToPFL23Plt <- ggplot(EPGToPFL23) + 
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                         midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")  +
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  facet_grid(cols = vars(type.to),space="free", scales="free")
print(EPGToPFL23Plt)
```

Get all of the EPG ids
```{r}
EPGids <- levels(EPGToPFL23$nameOrder.from)
```

Get all of the PFL ids
```{r}
PFL2ids <- levels(PBRename(filter(EPGToPFL23,type.to == "PFL2")$name.to,filter(EPGToPFL23,type.to == "PFL2")$to))
PFL3ids <- levels(PBRename(filter(EPGToPFL23,type.to == "PFL3")$name.to,filter(EPGToPFL23,type.to == "PFL3")$to))
```

Convert the connection tables to weight matrices
```{r}
EPG_To_PFL2 <- conTabToWM(EPGToPFL23, EPGids, PFL2ids)
EPG_To_PFL3 <- conTabToWM(EPGToPFL23, EPGids, PFL3ids)
```

Find the activity in the PFLs that results from a bump at various locations in the EB
```{r}
gloms = c("R1","L8","R2","L7","R3","L6","R4","L5",
         "R5","L4","R6","L3","R7","L2","R8","L1")
PBglomOrder <- c("R9","R8","R7","R6","R5","R4","R3","R2","R1",
                 "L1","L2","L3","L4","L5","L6","L7","L8","L9")
vMprof <- vonMisesProf()

# Create arrays to hold the PFL activity
PFL2_PB_act <- data.frame(id = as.character(PFL2ids))
PFL3_PB_act <- data.frame(id = as.character(PFL3ids))


# Move the bump around the EB
for (mov in 1:length(vonMisesProf())) {
  
  # Get the bump profile in the PB
  actProfvM <- data.frame(act = c(tail(vMprof,-mov),head(vMprof,mov)),glom = gloms)
  actProfvM$glom <- factor(actProfvM$glom,levels=as.factor(PBglomOrder))
  
  # Place the bump into the EPGs
  EPG_PB_act <- data.frame(id = as.character(EPGids))
  EPG_PB_act$glom <- lapply(EPG_PB_act$id, function(id) strsplit(strsplit(id,'-')[[1]][1],'_')[[1]][2]) %>% unlist()
  EPG_PB_act$act <- lapply(EPG_PB_act$glom, function(g) actProfvM[which(actProfvM$glom == g),]$act) %>% unlist()
  
  # Find the projected PFL activity
  EPG_PB_act$id <- factor(EPG_PB_act$id, levels = rownames(EPG_To_PFL2))
  PFL2_PB_act[EPG_PB_act[which.max(EPG_PB_act$act),]$glom] <- EPG_PB_act$act %*% EPG_To_PFL2 %>% as.numeric()
  
  EPG_PB_act$id <- factor(EPG_PB_act$id, levels = rownames(EPG_To_PFL3))
  PFL3_PB_act[EPG_PB_act[which.max(EPG_PB_act$act),]$glom] <- EPG_PB_act$act %*% EPG_To_PFL3 %>% as.numeric()
}

```

Plot the activity vs. position
```{r}
pltGloms = c("R5","L4","R6","L3","R7","L2","R8","L1",
             "R1","L8","R2","L7","R3","L6","R4","L5")

PFL2_plt_dat <- melt(PFL2_PB_act, id.vars = 'id',variable.name='peakGlom',value.name='act')
PFL2_plt_dat$id <- factor(PFL2_plt_dat$id,levels=PFL2ids)
PFL2_plt_dat$peakGlom <- factor(PFL2_plt_dat$peakGlom,levels=pltGloms)
PFL2_act_plt <- ggplot(PFL2_plt_dat) + 
  geom_tile(aes(x=id,y=peakGlom,fill=act)) + 
  scale_fill_gradient(low="white",high="black",limits=c(0,200)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90)) + 
  xlab("neuron name") + ylab('glom. of peak EPG act.')

PFL3_plt_dat <- melt(PFL3_PB_act, id.vars = 'id',variable.name='peakGlom',value.name='act')
PFL3_plt_dat$id <- factor(PFL3_plt_dat$id,levels=PFL3ids)
PFL3_plt_dat$peakGlom <- factor(PFL3_plt_dat$peakGlom,levels=pltGloms)
PFL3_act_plt <- ggplot(PFL3_plt_dat) + 
  geom_tile(aes(x=id,y=peakGlom,fill=act)) + 
  scale_fill_gradient(low="white",high="black",limits=c(0,200)) + 
  theme_paper() + theme(axis.text.x = element_text(angle=90),
                        axis.title.y = element_blank()) + 
  xlab("neuron name")

PFL_plts <- PFL2_act_plt + PFL3_act_plt
print(PFL_plts)
```

Sum the activity across PFLs
```{r}
summedPFL2act <- PFL2_plt_dat %>% group_by(peakGlom) %>% summarize(netAct = sum(act))
summedPFL2act$type.from <- "PFL2"
summedPFL3act <- PFL3_plt_dat %>% group_by(peakGlom) %>% summarize(netAct = sum(act))
summedPFL3act$type.from <- "PFL3"
#summedPFLact <- rbind(summedPFL2act,summedPFL3act)
#summedPFLact$peakGlom <- factor(summedPFLact$peakGlom, levels = gloms)

#sum_PFL_plts <- ggplot(summedPFLact) + geom_line(aes(x=peakGlom,y=netAct,group=1)) +
#  facet_grid(cols = vars(type.from)) +
#  theme_paper()

sumPFL2_plt <- ggplot(summedPFL2act) + geom_line(aes(x=peakGlom,y=netAct,group=1)) + coord_flip() + 
  theme_paper() + ylim(c(300,550)) +
  theme(axis.title.y = element_blank()) + ylab("summed act.")
sumPFL3_plt <- ggplot(summedPFL3act) + geom_line(aes(x=peakGlom,y=netAct,group=1)) + coord_flip() + 
  theme_paper() + ylim(c(300,550)) +
  theme(axis.title.y = element_blank()) + ylab("summed act.")
  
PFLactAll <- PFL2_act_plt + sumPFL2_plt + PFL3_act_plt + sumPFL3_plt + plot_layout(widths = c(3,1,3,1),guides='collect')
print(PFLactAll)
```

Get the PFL to DN connection table
```{r}
PFLs_to_DNs <- getConnectionTable(getTypesTable(c("PFL2","PFL3")),"POST") %>% filter(grepl("DN",type.to))
PFLs_to_DNs$nameOrder.from <- PBRename(PFLs_to_DNs$name.from,PFLs_to_DNs$from)
PFLs_to_DNs$nameOrder.to <- PBRename(PFLs_to_DNs$name.to,PFLs_to_DNs$to)
```

Plot the connection table
```{r}
cmax=100
PFL2ToDNPlt <- ggplot(PFLs_to_DNs %>% filter((type.to != "MDN") & (type.from == "PFL2"))) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")  +
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  coord_fixed(ratio=1)
print(PFL2ToDNPlt)

PFL3ToDNPlt <- ggplot(PFLs_to_DNs %>% filter((type.to != "MDN") & (type.from == "PFL3"))) + 
  scale_fill_gradient2(low="mistyrose", mid="firebrick3", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  geom_tile(aes(nameOrder.to,nameOrder.from,fill=ROIweight)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")  +
  theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  coord_fixed(ratio=1)
print(PFL3ToDNPlt)
```

Multiply the PFL2 and PFL3 "activity" by the DN weights
```{r}
typesTo <- PFLs_to_DNs$type.to %>% unique() %>% sort()
DNact_PFL2 <- data.frame(peakGlom <- c(),
                         act <- c(),
                         name <- c())
DNact_PFL3 <- data.frame(peakGlom <- c(),
                         act <- c(),
                         name <- c())
for (t in 1:length(typesTo)){
  PFL2_To_DN <- conTabToWM(PFLs_to_DNs, PFL2ids, 
                           PFLs_to_DNs %>% filter(type.to == typesTo[t]) %>% select(nameOrder.to) %>% unlist() %>% as.character() %>% unique() %>% sort())
  PFL3_To_DN <- conTabToWM(PFLs_to_DNs, PFL3ids, 
                           PFLs_to_DNs %>% filter(type.to == typesTo[t]) %>% select(nameOrder.to) %>% unlist() %>% as.character() %>% unique() %>% sort())
  for (r in 2:ncol(PFL2_PB_act)){
    DNact_PFL2 <- rbind(DNact_PFL2,
                        data.frame(peakGlom = colnames(PFL2_PB_act)[r],
                                   input = max(as.numeric(unlist(PFL2_PB_act[,r])) %*% PFL2_To_DN),
                                   name = typesTo[t]))
  }
  for (r in 2:ncol(PFL3_PB_act)){
    DNact_PFL3 <- rbind(DNact_PFL3,
                        data.frame(peakGlom = colnames(PFL3_PB_act)[r],
                                   input = max(as.numeric(unlist(PFL3_PB_act[,r])) %*% PFL3_To_DN),
                                   name = typesTo[t]))
  }
  
}
```

Plot it
```{r}
DNact_PFL2$peakGlom <- factor(DNact_PFL2$peakGlom, levels = rev(pltGloms))
DNact_PFL3$peakGlom <- factor(DNact_PFL3$peakGlom, levels = rev(pltGloms))

DN_From_PFL2_plt <- ggplot(DNact_PFL2 %>% filter(name %in% c("DNa03","DNb01"))) + geom_line(aes(x=peakGlom,y=input,group=name)) +
  facet_grid(cols = vars(name),scales="free") +
  theme_paper() +
  theme(axis.text.x = element_text(angle=90)) +
  xlab('glom. of peak EPG act.') + ylab('summed act') +
  theme(axis.text.x = element_text(angle=90)) + coord_flip()

DN_From_PFL3_plt <- ggplot(DNact_PFL3 %>% filter(name %in% c("DNa02","DNa03","DNa04","DNb01"))) + geom_line(aes(x=peakGlom,y=input,group=name)) +
  facet_grid(cols = vars(name),scales="free") +
  theme_paper() +
  xlab('glom. of peak EPG act.') + ylab('summed act') +
  theme(axis.text.x = element_text(angle=90)) + coord_flip()

DN_plt <- PFL2ToDNPlt + DN_From_PFL2_plt + PFL3ToDNPlt + DN_From_PFL3_plt + plot_layout(widths = c(1,2,1,4))
print(DN_plt)
```

Now, do the same for an impulse input
Find the activity in the PFLs that results from an impulse input at various locations in the EB
```{r}
impProf <- vector(mode="numeric",length = 16)
impProf[8] <- 1

# Create arrays to hold the PFL activity
PFL2_PB_act_imp <- data.frame(id = as.character(PFL2ids))
PFL3_PB_act_imp <- data.frame(id = as.character(PFL3ids))


# Move the bump around the EB
for (mov in 1:length(impProf)) {
  
  # Get the bump profile in the PB
  actProfImp <- data.frame(act = c(tail(impProf,-mov),head(impProf,mov)),glom = gloms)
  actProfImp$glom <- factor(actProfImp$glom,levels=as.factor(PBglomOrder))
  
  # Place the bump into the EPGs
  EPG_PB_act <- data.frame(id = as.character(EPGids))
  EPG_PB_act$glom <- lapply(EPG_PB_act$id, function(id) strsplit(strsplit(id,'-')[[1]][1],'_')[[1]][2]) %>% unlist()
  EPG_PB_act$act <- lapply(EPG_PB_act$glom, function(g) actProfImp[which(actProfImp$glom == g),]$act) %>% unlist()
  
  # Find the projected PFL activity
  EPG_PB_act$id <- factor(EPG_PB_act$id, levels = rownames(EPG_To_PFL2))
  PFL2_PB_act_imp[EPG_PB_act[which.max(EPG_PB_act$act),]$glom] <- EPG_PB_act$act %*% EPG_To_PFL2 %>% as.numeric()
  
  EPG_PB_act$id <- factor(EPG_PB_act$id, levels = rownames(EPG_To_PFL3))
  PFL3_PB_act_imp[EPG_PB_act[which.max(EPG_PB_act$act),]$glom] <- EPG_PB_act$act %*% EPG_To_PFL3 %>% as.numeric()
}

```

Plot the activity vs. position
```{r}
PFL2_plt_dat_imp <- melt(PFL2_PB_act_imp, id.vars = 'id',variable.name='peakGlom',value.name='act')
PFL2_plt_dat_imp$id <- factor(PFL2_plt_dat_imp$id,levels=PFL2ids)
PFL2_plt_dat_imp$peakGlom <- factor(PFL2_plt_dat_imp$peakGlom,levels=pltGloms)
PFL2_act_plt_imp <- ggplot(PFL2_plt_dat_imp) + 
  geom_tile(aes(x=id,y=peakGlom,fill=act)) + 
  scale_fill_gradient(low="white",high="black") + 
  theme_paper() + theme(axis.text.x = element_text(angle=90))

PFL3_plt_dat_imp <- melt(PFL3_PB_act_imp, id.vars = 'id',variable.name='peakGlom',value.name='act')
PFL3_plt_dat_imp$id <- factor(PFL3_plt_dat_imp$id,levels=PFL3ids)
PFL3_plt_dat_imp$peakGlom <- factor(PFL3_plt_dat_imp$peakGlom,levels=pltGloms)
PFL3_act_plt_imp <- ggplot(PFL3_plt_dat_imp) + 
  geom_tile(aes(x=id,y=peakGlom,fill=act)) + 
  scale_fill_gradient(low="white",high="black") + 
  theme_paper() + theme(axis.text.x = element_text(angle=90))

PFL_plts_imp <- PFL2_act_plt_imp + PFL3_act_plt_imp
print(PFL_plts_imp)
```
Multiply the PFL2 and PFL3 "activity" by the DN weights
```{r}
DNact_PFL2_imp <- data.frame(peakGlom <- c(),
                         act <- c(),
                         name <- c())
DNact_PFL3_imp <- data.frame(peakGlom <- c(),
                         act <- c(),
                         name <- c())
for (t in 1:length(typesTo)){
  PFL2_To_DN <- conTabToWM(PFLs_to_DNs, PFL2ids, 
                           PFLs_to_DNs %>% filter(type.to == typesTo[t]) %>% select(nameOrder.to) %>% unlist() %>% as.character() %>% unique() %>% sort())
  PFL3_To_DN <- conTabToWM(PFLs_to_DNs, PFL3ids, 
                           PFLs_to_DNs %>% filter(type.to == typesTo[t]) %>% select(nameOrder.to) %>% unlist() %>% as.character() %>% unique() %>% sort())
  for (r in 2:ncol(PFL2_PB_act_imp)){
    DNact_PFL2_imp <- rbind(DNact_PFL2_imp,
                        data.frame(peakGlom = colnames(PFL2_PB_act_imp)[r],
                                   input = max(as.numeric(unlist(PFL2_PB_act_imp[,r])) %*% PFL2_To_DN),
                                   name = typesTo[t]))
  }
  for (r in 2:ncol(PFL3_PB_act_imp)){
    DNact_PFL3_imp <- rbind(DNact_PFL3_imp,
                        data.frame(peakGlom = colnames(PFL3_PB_act_imp)[r],
                                   input = max(as.numeric(unlist(PFL3_PB_act_imp[,r])) %*% PFL3_To_DN),
                                   name = typesTo[t]))
  }
  
}
```

Sum the activity across PFLs
```{r}
summedPFL2act_imp <- PFL2_plt_dat_imp %>% group_by(peakGlom) %>% summarize(netAct = sum(act))
summedPFL2act_imp$type.from <- "PFL2"
summedPFL2act_imp$peakGlom <- factor(summedPFL2act_imp$peakGlom, levels = rev(pltGloms))
summedPFL3act_imp <- PFL3_plt_dat_imp %>% group_by(peakGlom) %>% summarize(netAct = sum(act))
summedPFL3act_imp$type.from <- "PFL3"
summedPFL3act_imp$peakGlom <- factor(summedPFL3act_imp$peakGlom, levels = rev(pltGloms))
#summedPFLact_imp <- rbind(summedPFL2act_imp,summedPFL3act_imp)
#summedPFLact_imp$peakGlom <- factor(summedPFLact_imp$peakGlom, levels = pltGloms)

#sum_PFL_plts_imp <- ggplot(summedPFLact_imp) + geom_line(aes(x=peakGlom,y=netAct,group=1)) +
#  facet_grid(cols = vars(type.from)) +
#  theme_paper()

sumPFL2_plt_imp <- ggplot(summedPFL2act_imp) + geom_line(aes(x=peakGlom,y=netAct,group=1)) + #coord_flip() + 
  theme_paper() + ylim(c(0,300)) +
  xlab('glom. of peak EPG act.') + ylab("summed act.") + theme(axis.text.x = element_text(angle=90))
sumPFL3_plt_imp <- ggplot(summedPFL3act_imp) + geom_line(aes(x=peakGlom,y=netAct,group=1)) + #coord_flip() + 
  theme_paper() + ylim(c(0,300)) +
  theme(axis.title.y = element_blank()) + xlab('glom. of peak EPG act.') + theme(axis.text.x = element_text(angle=90))

print(sumPFL2_plt_imp)
print(sumPFL3_plt_imp)
```

Plot it
```{r}
DNact_PFL2_imp$peakGlom <- factor(DNact_PFL2_imp$peakGlom, levels = rev(pltGloms))
DNact_PFL3_imp$peakGlom <- factor(DNact_PFL3_imp$peakGlom, levels = rev(pltGloms))

DN_From_PFL2_plt_imp <- ggplot(DNact_PFL2_imp %>% filter(name != "MDN")) + geom_line(aes(x=peakGlom,y=input,group=name)) +
  facet_grid(rows = vars(name),scales="free") +
  ggtitle("inputs from PFL2") + theme_paper() +
  xlab('glom. of peak EPG act.') + ylab('summed act') +
  theme(axis.text.x = element_text(angle=90))

DN_From_PFL3_plt_imp <- ggplot(DNact_PFL3_imp  %>% filter(name != "MDN")) + geom_line(aes(x=peakGlom,y=input,group=name)) +
  facet_grid(rows = vars(name),scales="free") +
  ggtitle("inputs from PFL3") + theme_paper() +
  xlab('glom. of peak EPG act.') + ylab('summed act') +
  theme(axis.text.x = element_text(angle=90))

DN_plt_imp <- DN_From_PFL2_plt_imp + DN_From_PFL3_plt_imp
print(DN_plt_imp)
```
Save the plots
```{r}
ggsave("EPGToPFLCM.pdf",EPGToPFL23Plt,
       width=4, height=4, units = "in")
```
```{r}
PFL23ToDNPlt <- PFL2ToDNPlt + PFL3ToDNPlt + plot_layout(widths = c(1,2), guides = 'collect')
ggsave("PFLToDNCM.pdf",PFL23ToDNPlt,
       width=3.5, height=2.5, units = "in")
```
```{r}
ggsave("PFLBumpAct.pdf",PFLactAll,
       width=6, height=2.5, units = "in")
```
```{r}
sumPFL_plts_imp <- sumPFL2_plt_imp + sumPFL3_plt_imp
ggsave("EPGToPFLActImp.pdf",sumPFL_plts_imp,
       width=3.5, height=1.5, units = "in")
```
```{r}
DN_plts <- DN_From_PFL2_plt + DN_From_PFL3_plt + plot_layout(widths = c(1,2))
ggsave("EPGToPFLToDNAct.pdf",DN_plts,
       width=4, height=2.5, units = "in")
```