---
title: "Convergence/Divergence plots in Figure 6 - Supplemental information 1 A,B, Figure 7 - Supplemental information 1 A,B"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Quantification of convergence/divergence for a type-2-type connection

(a) From how many type A cells does a single type B cell get input?
(b) To how many type A cells does a single type B cell give input?


#### Load packages and custom functions
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(paletteer)
library(gridExtra)

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","SynapsePCAUtils.R"))

neuprint_login()
```

#### Load colormaps
```{r}
# Generate color map
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")
myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

### Convergence/Divergence between MC and TuBu neurons
Choose ROI and list of neurons to consider
```{r}
myROI = "AOTU(R)"
my_posttypes = paste0("TuBu", ".*")
postPartnerList = c(paste0("TuBu0",seq(1,9)),"TuBu10")
postGroup = "TuBu"
prePartnerList = c("MC61","MC64")
preGroup = "MC"
```

...use this list to get synapse info
```{r}
my_synapses = neuprint_get_synapses(as.numeric(getBodyIdsForList(my_posttypes)$bodyid),myROI)
# From the doc: A data frame, where each entry is a connection between the specified bodyid and its partner, either presynaptic to the bodyid (prepost=0) or postsynaptic (prepost=1). Each connection is associated with a synapse that has its own unique connector_id, XYZ coordinates and a confidence in its existence.

my_synapses = my_synapses %>% mutate(
  name=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["name"]],
  type=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["type"]],
  partnerName=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["name"]],
  partnertype=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["type"]])

my_synapses = data.frame(type = as.factor(my_synapses$type), 
                    partnerType = as.factor(my_synapses$partnertype),
                    name = as.factor(my_synapses$name), 
                    partnerName = as.factor(my_synapses$partnerName),
                    id = as.factor(my_synapses$bodyid),
                    partnerid = as.factor(my_synapses$partner),
                    prepost = as.factor(my_synapses$prepost))

#Add simple type name
my_synapses = my_synapses %>% filter(partnerType %in% prePartnerList) %>% mutate(simpleType = gsub("_.*", "",type))
```

Count synapses made from individual neurons of one type to individual neurons of an other type ("focus type")
```{r, warning=FALSE}
conPattern = data.frame("focustype"=character(0), "partnertype"=character(0), "focustypeid"=character(0), "n_partners"=integer(0))
for (post in seq(0,1)){
  partnertypelist = prePartnerList

  for (partnertype in partnertypelist){ #
    dataTypefilt = my_synapses %>% filter(partnerType == partnertype)
    focustypelist = c(postPartnerList, prePartnerList)
   
    for (focustype in focustypelist){
      if(post == 1){ direction = paste0(preGroup,"2",postGroup) }else{ direction = paste0(postGroup,"2",preGroup)}
      
      data = dataTypefilt %>% filter((type %in% c(focustype)) & (prepost == post)) %>%
          mutate(groupingvar = id)
      neuron2neuron = data %>% select(type, partnerType, id, partnerid, prepost) %>% group_by(id, partnerid) %>% mutate(nsyn =  length(prepost))
    
      neuron2neuron = unique(neuron2neuron)
      
      if(is_empty(unique(data$groupingvar))){next}
      postFocus = neuron2neuron  %>% group_by(id) %>% summarize(n = length(prepost), s = sum(nsyn))
      tmpDF = data.frame("focustypeSyn"="post", "focustypeid"=postFocus$id, "n_partners"= postFocus$n,
                         "focustype" = focustype, "partnertype" = partnertype, syndir = direction, "syn"=postFocus$s)
      conPattern =  bind_rows(conPattern, tmpDF)
      
      preFocus = neuron2neuron  %>% group_by(partnerid) %>% summarize(n = length(prepost), s = sum(nsyn))
      tmpDF = data.frame("focustypeSyn"="pre", "focustypeid"=preFocus$partnerid, "n_partners"= preFocus$n,
                         "focustype" = partnertype, "partnertype" = focustype, syndir = direction, "syn"=preFocus$s)
      conPattern =  bind_rows(conPattern, tmpDF)
    }
  }
}

```

For MC -> TB (Figure 6 figure supplement 1 A,B)
```{r}
selectDir = "MC2TuBu"

filtdat = conPattern %>% filter(focustypeSyn == "post" & syndir == selectDir) %>% unique()
postPlot <- ggplot(data=filtdat,aes(x=partnertype, y=n_partners,size = syn)) + 
  geom_boxplot(outlier.shape = NA,lwd=.3) + geom_jitter(width = 0.2, height = 0, aes(color=partnertype)) +
  facet_grid(cols = vars(focustype), scales = "free_x",space='free_x') + theme_classic() + 
  scale_size(range=c(0,2)) +
  theme(axis.text.x = element_text(angle = 90),text = element_text(size=8), axis.line = element_line(colour = 'black', size = .3)) +
  guides(color=FALSE) + labs(title = paste(postGroup, "gets input from..."))

filtdat = conPattern %>% filter(focustypeSyn == "pre" & syndir == selectDir) %>% unique()
myCM = myColorMap %>% filter(Type %in% unique(filtdat$partnertype))
myCM = myCM[match(as.character(unique(filtdat$partnertype)), myCM$Type),] %>% arrange(unique(filtdat$partnertype))

prePlot <- ggplot(data=filtdat,aes(x=partnertype, y=n_partners,size = syn)) + 
  geom_boxplot(outlier.shape = NA,lwd=.3) + geom_jitter(width = 0.2,height = 0, aes(color=partnertype)) + 
  facet_grid(cols = vars(focustype), scales = "free_x",space='free_x') + theme_classic()   +
  scale_color_manual(values = as.character(myCM$hex)) + scale_size(range=c(0,2)) +
  theme(axis.text.x = element_text(angle = 90), text = element_text(size=8), axis.line = element_line(colour = 'black', size = .3)) +
  guides(color=FALSE) + labs(title=paste(preGroup, "gives output to..."))

conPatternPlot <- grid.arrange(postPlot,prePlot, nrow=2) #nrow-1

if(savePlot){
  ggsave(paste("connectionPattern",preGroup,"_and_",postGroup,'_', selectDir,'.pdf', sep=''),
                plot = conPatternPlot, device='pdf', path = file.path("plots"), 
                scale = 1, width = 20, height = 16, units ="cm", dpi = 600, useDingbats=FALSE) 
}
```


### Convergence/Divergence between TuBu and Ring neurons
Choose ROI and list of neurons to consider
```{r}
myROI = "BU(R)"
my_posttypes = paste0("ER",seq(1,6))
prePartnerList = c(paste0("TuBu0",seq(1,9)),"TuBu10")#
preGroup = "TuBu"
postPartnerList = getBodyIdsForList(my_posttypes)$type
postGroup = "ER"
```

...use this list to get synapse info
```{r}
my_synapses = neuprint_get_synapses(as.numeric(getBodyIdsForList(my_posttypes)$bodyid),myROI)
# From the doc: A data frame, where each entry is a connection between the specified bodyid and its partner, either presynaptic to the bodyid (prepost=0) or postsynaptic (prepost=1). Each connection is associated with a synapse that has its own unique connector_id, XYZ coordinates and a confidence in its existence.

my_synapses = my_synapses %>% mutate(
  name=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["name"]],
  type=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["type"]],
  partnerName=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["name"]],
  partnertype=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["type"]])

my_synapses = data.frame(type = as.factor(my_synapses$type), 
                    partnerType = as.factor(my_synapses$partnertype),
                    name = as.factor(my_synapses$name), 
                    partnerName = as.factor(my_synapses$partnerName),
                    id = as.factor(my_synapses$bodyid),
                    partnerid = as.factor(my_synapses$partner),
                    prepost = as.factor(my_synapses$prepost),
                    synID = as.factor(my_synapses$connector_id))

#Add simple type name
my_synapses = my_synapses %>% filter(partnerType %in% prePartnerList) %>% mutate(simpleType = gsub("_.*", "",type))
```

```{r, warning=FALSE}
conPattern = data.frame("focustype"=character(0), "partnertype"=character(0), "focustypeid"=character(0), "n_partners"=integer(0))
for (post in seq(0,1)){
  partnertypelist = prePartnerList

  for (partnertype in partnertypelist){ #
    dataTypefilt = my_synapses %>% filter(partnerType == partnertype)
    focustypelist = c(postPartnerList, prePartnerList)
   
    for (focustype in focustypelist){
      if(post == 1){ direction = paste0(preGroup,"2",postGroup) }else{ direction = paste0(postGroup,"2",preGroup)}
      
      data = dataTypefilt %>% filter((type %in% c(focustype)) & (prepost == post)) %>%
          mutate(groupingvar = id)
      neuron2neuron = data %>% select(type, partnerType, id, partnerid, prepost) %>% group_by(id, partnerid) %>% mutate(nsyn =  length(prepost))
    
      neuron2neuron = unique(neuron2neuron)
      
      if(is_empty(unique(data$groupingvar))){next}
      postFocus = neuron2neuron  %>% group_by(id) %>% summarize(n = length(prepost), s = sum(nsyn))
      tmpDF = data.frame("focustypeSyn"="post", "focustypeid"=postFocus$id, "n_partners"= postFocus$n,
                         "focustype" = focustype, "partnertype" = partnertype, syndir = direction, "syn"=postFocus$s)
      conPattern =  bind_rows(conPattern, tmpDF)
      
      preFocus = neuron2neuron  %>% group_by(partnerid) %>% summarize(n = length(prepost), s = sum(nsyn))
      tmpDF = data.frame("focustypeSyn"="pre", "focustypeid"=preFocus$partnerid, "n_partners"= preFocus$n,
                         "focustype" = partnertype, "partnertype" = focustype, syndir = direction, "syn"=preFocus$s)
      conPattern =  bind_rows(conPattern, tmpDF)
    }
  }
}

```

For TB -> TRing (Figure 7 figure supplement 1 A,B)
```{r}
selectDir = "TuBu2ER"
filtdat = conPattern %>% filter(focustypeSyn == "post" & syndir == selectDir) %>% unique()
myCM = myColorMap %>% filter(Type %in% unique(filtdat$partnertype))
myCM = myCM[match(as.character(unique(filtdat$partnertype)), myCM$Type),] %>% arrange(unique(filtdat$partnertype))

postPlot <- ggplot(data=filtdat,aes(x=partnertype, y=n_partners,size = syn)) + 
  geom_jitter(width = 0.2, height = 0.15, aes(color=partnertype)) +
  scale_color_manual(values = as.character(myCM$hex)) + scale_size(range=c(0,2.5)) +
  facet_grid(cols = vars(focustype), scales = "free_x",space='free_x') + theme_classic() + 
  theme(axis.text.x = element_text(angle = 90),text = element_text(size=8), axis.line = element_line(colour = 'black', size = .3)) +
  guides(color=FALSE) + labs(title = paste(postGroup, "gets input from..."))

filtdat = conPattern %>% filter(focustypeSyn == "pre" & syndir == selectDir) %>% unique()
myCM = myColorMap %>% filter(Type %in% unique(filtdat$partnertype))
myCM = myCM[match(as.character(unique(filtdat$partnertype)), myCM$Type),] %>% arrange(unique(filtdat$partnertype))

prePlot <- ggplot(data=filtdat,aes(x=partnertype, y=n_partners,size = syn)) + 
  geom_jitter( width = 0.2,height = 0.15, aes(color=partnertype)) + 
  scale_color_manual(values = as.character(myCM$hex)) + scale_size(range=c(0,2.5)) +
  facet_grid(cols = vars(focustype), scales = "free_x", space='free_x') + theme_classic()   +
  theme(axis.text.x = element_text(angle = 90), text = element_text(size=8), axis.line = element_line(colour = 'black', size = .3)) +
  guides(color=FALSE) + labs(title=paste(preGroup, "gives output to..."))

conPatternPlot <- grid.arrange(postPlot,prePlot, nrow=2)

if(savePlot){
  ggsave(paste("connectionPattern",preGroup,"_and_",postGroup,'_', selectDir,'.pdf', sep=''),
                plot = conPatternPlot, device='pdf', path =file.path("plots"),
                scale = 1, width = 35, height = 18, units ="cm", dpi = 600, useDingbats=FALSE) 
}
```