---
title: "Create vizualization of synapse locations in glomeruli"
output:
  html_document:
    df_print: paged
---

# Create vizualization of synapse locations in glomeruli
Generates plots for Figure 7 - Supplemental information 1 panel C

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(neuprintrExtra)
library(paletteer)
require(RColorBrewer)
library(gridExtra)

options(nat.plotengine = 'rgl')
source(file.path("..","R","SynapsePCAUtils.R"))
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```


### (0) Get some synapse locations
Choose ROI and get curated list of neurons.
For Ci choose perspective = "TuBu", for Cii choose "ER"
```{r}
myROI = "BU(R)"

perspective = "TuBu" # {"ER", "TuBu"}
if (perspective == "TuBu"){
  my_types = c("TuBu")
  partnerSubset = getBodyIdsForList(paste0(c("ER"),".*"))
  focustype = "TuBu06"
}else if (perspective == "ER"){
  my_types = c("ER1","ER2","ER3","ER4","ER5","ER6")
  partnerSubset = getBodyIdsForList(paste0(c("TuBu"),".*"))
  focustype = "ER5"
}else{print("Please choose a valid perspective value.")}

my_types = paste0(my_types, ".*")
my_neurons = getBodyIdsForList(my_types)

# Generate color map
cmapNames = c("RingNeurons", "TuBus","ExR_and_AOTU46")
myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}
```
### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

...use this list to get synapse locations
```{r}
my_synapses = neuprint_get_synapses(as.numeric(getBodyIdsForList(my_types)$bodyid),myROI)

my_synapses = my_synapses %>% mutate(
name=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["name"]],
type=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["type"]],
partnerName=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["name"]],
partnertype=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["type"]])
```

### (1) Import of ROI meshes and get vertices in x,y,z
```{r}
roiMesh = neuprint_ROI_mesh(myROI)
roiMeshPts = data.frame(dotprops(roiMesh)$points)
names(roiMeshPts) <- c("x","y","z")
```


### (2) Find convenient coordinate system based on PCA of vertices and center of mass of the ROI
***Transform mesh  and synapse locations***
```{r}
# define new origin from roi center of mass
origin = getCOM(roiMeshPts)

#reset orgin
roiMeshPts = resetOrigin(roiMeshPts, origin)

#get eigenvectors
roiEigen = covPCA(roiMeshPts)

roiMeshPtsRot = changeBasis(roiMeshPts, roiEigen)

#Synapse locations
synPts = data.frame(x=as.numeric(my_synapses$x),
                    y=as.numeric(my_synapses$y),
                    z=as.numeric(my_synapses$z))
synPts = resetOrigin(synPts, origin)
synPtsRot = changeBasis(synPts, roiEigen)

```

***Select either original or EV coordinates and rotate***
```{r}
if (myROI == "AOTU(R)"){
  rot = c(0,0,0)
}else if (myROI == "BU(R)"){
  rot = c(45,0,0)
}else if (myROI == "EB"){
  rot =  c(0,0,180)
}else{
  rot = c(0,0,0)
}

flipx = 1
flipy = -1
flipz = 1

roiMeshPtsPlane = data.frame(x=roiMeshPtsRot$X,
                             y=roiMeshPtsRot$Y,
                             z=roiMeshPtsRot$Z)
synPtsPlane = data.frame(x=synPtsRot$X,
                             y=synPtsRot$Y,
                             z=synPtsRot$Z)
# rotate points
roiMeshPtsPlane = data.matrix(roiMeshPtsPlane)
synPtsPlane = data.matrix(synPtsPlane)

roiMeshPtsPlane = roiMeshPtsPlane %*% makeRotMatXY(rot[1])
synPtsPlane = synPtsPlane %*% makeRotMatXY(rot[1])
roiMeshPtsPlane = roiMeshPtsPlane %*% makeRotMatYZ(rot[2])
synPtsPlane = synPtsPlane %*% makeRotMatYZ(rot[2])
roiMeshPtsPlane = roiMeshPtsPlane %*% makeRotMatXZ(rot[3])
synPtsPlane = synPtsPlane %*% makeRotMatXZ(rot[3])

roiMeshPtsPlane = data.frame(x=flipx*roiMeshPtsPlane[,1],y=flipy*roiMeshPtsPlane[,2],z=flipz*roiMeshPtsPlane[,3])
synPtsPlane = data.frame(x=flipx*synPtsPlane[,1],y=flipy*synPtsPlane[,2],z=flipz*synPtsPlane[,3],
                         type = as.factor(my_synapses$type), 
                         partnerType = as.factor(my_synapses$partnertype),
                         name = as.factor(my_synapses$name), 
                         partnerName = as.factor(my_synapses$partnerName),
                         id = as.factor(my_synapses$bodyid),
                         partnerid = as.factor(my_synapses$partner),
                         prepost = as.factor(my_synapses$prepost))

#Add simple type name
synPtsPlane = synPtsPlane %>% mutate(simpleType = gsub("_.*", "",type))

synCount = synPtsPlane %>% count(type)
typeFilter = synCount$type[synCount$n > 10]

# generate color map
dataFilt = synPtsPlane %>% filter(type %in% typeFilter)

myTypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$simpleType)) %>% filter(Simpletype == "yes")
myTypeCols = myTypeCols[match(as.character(unique(dataFilt$simpleType)), myTypeCols$Type),] %>%
  arrange(unique(dataFilt$simpleType))

mySubtypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$type)) %>% filter(Simpletype == "no")
mySubtypeCols = mySubtypeCols[match(as.character(unique(dataFilt$type)), mySubtypeCols$Type),] %>%
  arrange(unique(dataFilt$type))


```

### Look at synapse distributions of individual neurons
Plot a slice for a focus type neuron.
The default distance is in pixels with 8x8x8 nm/pixel resolution, so we convert to um as follows: pixels*8(nm/pixel)/1000(nm/um).

```{r}
xrange = c(-1500, 1000)
yrange = c(-500, 1500)
zrange = c(-800, 400)
nsyn =40
xrange_slice = c(-300, 300)

convfactor = 8/1000
```

```{r}
data = dataFilt %>% filter(partnerType %in% partnerSubset$type) %>% filter(type %in% c(focustype))

toplot_2D = data %>% filter(x >= xrange[1] & x < xrange[2] ) %>%  filter(y >= yrange[1] & y < yrange[2] ) %>% 
  filter(z >= zrange[1] & z < zrange[2] ) %>% mutate(id = as.character(id)) %>% select(c('x','y','z', 'id'))

if (focustype  == "TuBu06"){
  colPal = paletteer_d("colRoz::salt_lake")
}else{
  colPal = paletteer_c("grDevices::Heat 2", n=length(unique(toplot_2D$id)))
}

xyproj <- ggplot(toplot_2D) + geom_point(aes(x=x*convfactor, y=y*convfactor, color=id, size=0.25, alpha=0.8,stroke = 0)) + 
  geom_point(data=toplot_2D %>% group_by(id) %>% summarize_each(mean), aes(x=x*convfactor, y=y*convfactor, color=id, size=0.5)) +
  scale_color_manual(values = colPal, breaks = unique(toplot_2D$id)) + xlab("x [µm]") + ylab("y [µm]") + 
  geom_vline(xintercept = xrange_slice[1]*convfactor) + geom_vline(xintercept = xrange_slice[2]*convfactor) +
  coord_fixed() + guides(size=FALSE,alpha=FALSE)+ theme_paper()

# take a slice in z and only plot points from neurons with > nsyn synapses in slice

toplot_slice = toplot_2D %>% filter(x >= xrange_slice[1] & x < xrange_slice[2] )
idfilt = toplot_slice %>%  count(id) %>% filter(n>=nsyn)

zyproj <- ggplot(toplot_slice %>% filter(id %in% idfilt$id) ) + geom_point(aes(x=z*convfactor, y=y*convfactor, color=id, size=0.25, alpha=0.8,stroke = 0)) + 
  geom_point(data=toplot_slice %>% filter(id %in% idfilt$id) %>% group_by(id) %>% summarize_each(mean), aes(x=z*convfactor,y=y*convfactor, color=id, size=0.5)) +
  scale_color_manual(values = colPal, breaks = unique(toplot_2D$id)) + xlab("z [µm]") + ylab("y [µm]") +
  coord_fixed() + guides(size=FALSE, alpha=FALSE) + theme_paper()

projPlot <- grid.arrange(xyproj,zyproj, nrow=1)

if (savePlot){
  ggsave(paste("glomeruliPlot_",focustype,'.pdf', sep=''), plot = projPlot, device='pdf',
          path = "plots", scale = 1, width = 15, height = 5, units ="cm", dpi = 600, useDingbats=FALSE)
}
```


Glomeruli size

```{r}
synRelDist = dataFilt %>% group_by(id) %>% filter(partnerType %in% partnerSubset$type) %>%
  mutate(x_h = x - mean(x), y_h = y - mean(y),z_h = z - mean(z)) %>%
  mutate(syndist = sqrt( x_h^2 + y_h^2 + z_h^2)) %>%
  mutate(npartner = length(unique(partnerid)))

synDistDistr = ggplot(data=synRelDist) + 
  geom_density(aes(x=syndist,color=type, hue=id)) +
  scale_color_manual(values = as.character(mySubtypeCols$hex)) +
  guides() + theme_classic() + coord_cartesian(xlim = c(0, 1500))

print(synDistDistr)

```

