---
title: "Analysis of anterior visual pathway: Connectivity graphs in the AOTU (Figure 6C) and BU (Figure 8B)"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

#Analysis of anterior visual pathway: Normalized synapse densities and related visualizations
This notebook shows how to generate normalized synapse densitites and related plots for various types in a given region (AOTU and BU)
* Figure 6D
* Figure 6E (TBD what the final visualization will be)
* Figure 7C
* Figure 8C,D

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(igraph)
#library(paletteer)

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

getBodyIdsForList = function (neuronList,prefix="",postfix=".*",...){
  #' Get one dataframe of bodyIDs for all search strings in neuronList
  #' @param neuronList: A list of search strings to be passed.
  #' @param prefix: String to be added before each query (default "")
  #' @param postfix: String to be added after each query (default ".*")
  #' @param ...: Parameters to be passed to neuprint_search. Note that meta=FALSE won't work for now.
  #' @return A data frame of metadata for the results of all the queries
  #' @examples
  #' \dontrun{
  #' # Both will return the same
  #' getBodyIdsForList(c("PFL1","PFL2"))
  #' getBodyIdsForList(c("PFL1","PFL2"),postfix="",field="type")
  #' }
  
  neuronList <-  paste0(prefix,neuronList,postfix)
  bodiesList <- lapply(neuronList,neuprint_search,...)
  return(bind_rows(bodiesList))
}
```

```{r}
neuprint_login()
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```


