---
title: "Analysis of anterior visual pathway: Connectivity graphs in the AOTU (Figure 6C) and BU (Figure 8B)"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

#Analysis of anterior visual pathway: Normalized synapse densities and related visualizations
This notebook shows how to generate normalized synapse densitites and related plots for various types in a given region (AOTU and BU)
* Figure 6D
* Figure 6E (TBD what the final visualization will be)
* Figure 7C
* Figure 8C,D

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(gridExtra)
library(alphahull)
library(hexbin)
library(paletteer)
require(RColorBrewer)

options(nat.plotengine = 'rgl')
source(file.path("..","R","SynapsePCAUtils.R"))
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))


```

### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

## Get some synapse locations
Choose ROI and get curated list of neurons.

Settings for...
- Figure 6 Di:myROI = "AOTU(R)", my_types = c("MC61","MC64"), saveName: "MC_in_"
- Figure 6 Dii: myROI = "AOTU(R)", my_types = c("TuBu"), saveName: "TuBu_in_"

- Figure8 Ci: myROI = "BU(R)", my_types = c("TuBu"), saveName: "TuBu_in_", choose typeSelection for contralaterally projecting types 
- Figure8 Cii: myROI = "BU(R)", my_types = paste0("ER",seq(1,6)), saveName: "ER_in_", choose typeSelection for contralaterally projecting types 

- Figure 8 Ci: myROI = "AOTU(R)", my_types = c("AOTU046"), saveName: "AOTU46_in_"
- Figure 8 Cii: myROI = "AOTU(R)", my_types = c("TuTuB"), saveName: "TuTuB_in_"
- Figure 8 Di,ii: myROI = "BU(R)", my_types = c("AOTU046", "ExR"), saveName: "ContraTypes_in_", choose typeSelection for contralaterally projecting types (see below)

```{r message=FALSE, warning=FALSE}
myROI = "BU(R)" #"AOTU(R)" #

saveName = paste0("TuBu_in_", myROI)
my_types = c("TuBu")

# For plots with many types, define grouping to split into multiple subplots.........
## For TuBu (Figure 6 Dii)
#typeSelection = list(c("TuBu01","TuBu06"),paste0("TuBu",c("02","03","04","05")),paste0("TuBu",c("07","08","09","10")))
## For TuBu (Figure 7 Cii)
typeSelection = list(paste0("TuBu",c("06","07","08","09","10")),paste0("TuBu",c("01","02","03","04","05")))

## For ER (Figure 7 Cii)
#typeSelection = list(paste0("ER",c("2_a","2_b","2_c","2_d","3w","4d","5","6")),
#                     paste0("ER",c("3a_a","3a_d","3d_a","3d_b","3d_c","3d_d","3m","3p_a","3p_b","4m")))

## For contralaterally projecting types (Figure 8 Di,ii)
#typeSelection = list(c("AOTU046","ExR1"),paste0("ExR",c("02","03","05")))
```

```{r}
my_types = paste0(my_types, ".*")
my_neurons = getBodyIdsForList(my_types)

# Generate color map
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")
myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}
```

...use this list to get synapse locations
```{r}
my_synapses = neuprint_get_synapses(as.numeric(getBodyIdsForList(my_types)$bodyid),myROI)

my_synapses = my_synapses %>% mutate(
name=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["name"]],
type=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["type"]],
partnerName=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["name"]],
partnertype=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["type"]])
```


## (1) Import of ROI meshes and get vertices in x,y,z
```{r}
roiMesh = neuprint_ROI_mesh(myROI)
roiMeshPts = data.frame(dotprops(roiMesh)$points)
names(roiMeshPts) <- c("x","y","z")
```


## (2) Find convenient coordinate system based on PCA of vertices and center of mass of the ROI
***Transform mesh and synapse locations***
```{r}
# define new origin from roi center of mass
origin = getCOM(roiMeshPts)

#reset orgin
roiMeshPts = resetOrigin(roiMeshPts, origin)

#get eigenvectors
roiEigen = covPCA(roiMeshPts)

roiMeshPtsRot = changeBasis(roiMeshPts, roiEigen)

#Synapse locations
synPts = data.frame(x=as.numeric(my_synapses$x),
                    y=as.numeric(my_synapses$y),
                    z=as.numeric(my_synapses$z))
synPts = resetOrigin(synPts, origin)
synPtsRot = changeBasis(synPts, roiEigen)

```

***Select either original or EV coordinates and rotate***
The default distance is in pixels with 8x8x8 nm/pixel resolution, so we convert to um as follows: pixels*8(nm/pixel)/1000(nm/um).
```{r}
if (myROI == "AOTU(R)"){ rot = c(0,0,0)
}else if (myROI == "BU(R)"){ rot = c(45,0,0)
}else if (myROI == "EB"){ rot =  c(0,0,180)
}else{ rot = c(0,0,0) }

convfactor = 8/1000

# rotate points and scale to obtain positions in um.
roiMeshPtsPlane <- rotatePoints(roiMeshPtsRot$X*convfactor,roiMeshPtsRot$Y*convfactor,roiMeshPtsRot$Z*convfactor, rot)
synPtsPlane <- rotatePoints(synPtsRot$X*convfactor,synPtsRot$Y*convfactor,synPtsRot$Z*convfactor, rot)

synPtsPlane <- synPtsPlane %>% mutate( type = as.factor(my_synapses$type), 
                                       partnerType = as.factor(my_synapses$partnertype),
                                       name = as.factor(my_synapses$name), 
                                       partnerName = as.factor(my_synapses$partnerName),
                                       id = as.factor(my_synapses$bodyid),
                                       partnerid = as.factor(my_synapses$partner),
                                       prepost = as.factor(my_synapses$prepost))
#Add simple type name
synPtsPlane = synPtsPlane %>% mutate(simpleType = gsub("_.*", "",type))

synCount = synPtsPlane %>% count(type)
typeFilter = synCount$type[synCount$n > 10]

# generate color map
dataFilt = synPtsPlane %>% filter(type %in% typeFilter)

myTypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$simpleType)) %>% filter(Simpletype == "yes")
myTypeCols = myTypeCols[match(as.character(unique(dataFilt$simpleType)), myTypeCols$Type),] %>%
  arrange(unique(dataFilt$simpleType))

mySubtypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$type)) %>% filter(Simpletype == "no")
mySubtypeCols = mySubtypeCols[match(as.character(unique(dataFilt$type)), mySubtypeCols$Type),] %>%
  arrange(unique(dataFilt$type))

```

## (3) Plot distributions

```{r}
#Helper plotting function
coloredDensityPlot <- function(mydata, dims, grouping, levelBins, colorcode){
  densPlot = ggplot() + stat_density_2d_filled(data = mydata, 
                          aes(x=.data[[dims[1]]], y=.data[[dims[2]]], fill=.data[[grouping]], alpha = stat(nlevel)),
                          bins=levelBins,contour_var = "ndensity", geom = "polygon") +
  scale_alpha(range=c(0,1)) + 
  coord_fixed(ratio = 1) + theme_void() + guides(fill=guide_legend(ncol=1)) +
  scale_fill_manual(values = as.character(cols$hex), name="type")
  return(densPlot)
}
```

### Generate mesh outlines for different orientations
```{r}
if(myROI=="AOTU(R)"){
  alphaval = 160*convfactor
}else{alphaval = 120*convfactor}

# get outline
meshOutline <- ahull(x=roiMeshPtsPlane$x,y=roiMeshPtsPlane$y,alpha=alphaval)
outline_xy = data.frame(meshOutline$arcs)

meshOutline <- ahull(x=roiMeshPtsPlane$z,y=roiMeshPtsPlane$y,alpha=alphaval)
outline_zy = data.frame(meshOutline$arcs)

meshOutline <- ahull(x=roiMeshPtsPlane$x,y=roiMeshPtsPlane$z,alpha=alphaval)
outline_xz = data.frame(meshOutline$arcs)

```

### 2D histograms
```{r}
nbins = 40
ncolumns = 5

# the size indicator shows 10 um distance

# front view (xy)
synprojFront = ggplot() + 
  geom_hex(data=dataFilt, aes(x=x, y=y), bins=nbins) +
  scale_fill_gradientn(colours = brewer.pal(5,"BuPu"), oob = scales::squish) +
  geom_segment(data=outline_xy,aes(x = -40, y = -20, xend = -30, yend = -20)) +
  facet_wrap(~type, ncol=ncolumns) + coord_fixed(ratio = 1) + theme_void() + guides(color=FALSE) +
  geom_path(data=outline_xy, aes(x=c1, y=c2), size = 0.5)
print(synprojFront)

# side view (zy)
synprojSide = ggplot() + 
  geom_hex(data=dataFilt, aes(x=z, y=y), bins=nbins) +
  scale_fill_gradientn(colours = brewer.pal(5,"BuPu"), oob = scales::squish) +
  facet_wrap(~type, ncol=ncolumns) + coord_fixed(ratio = 1) + theme_void() + guides(color=FALSE) +
  geom_segment(data=outline_zy,aes(x = -30, y = -20, xend = -20, yend = -20 )) +
  geom_path(data=outline_zy, aes(x=c1, y=c2), size = 0.5)
print(synprojSide)

# top view (xz)
synprojTop = ggplot() + 
  geom_hex(data=dataFilt, aes(x=x, y=z), bins=nbins) +
  scale_fill_gradientn(colours = brewer.pal(5,"BuPu"), oob = scales::squish) +
  facet_wrap(~type, ncol=ncolumns) + coord_fixed(ratio = 1) + theme_void() + guides(color=FALSE) +
  geom_segment(data=outline_xz,aes(x = -40, y = -20, xend = -30, yend = -20)) +
  geom_path(data=outline_xz, aes(x=c1, y=c2), size = 0.5)
print(synprojTop)

```

### 2D densitiy distributions
```{r}
plotW = 10
plotH =  15
levelBins = 4

dataPlot <- dataFilt %>% mutate(group = 0)
for (i in seq(1,length(typeSelection))){
  dataPlot <- dataPlot %>% mutate(group = replace(group, type %in% typeSelection[[i]], i))
}

# front view (xy)
synprojFront = ggplot() + 
  stat_density_2d_filled(data = dataPlot, aes(x=x, y=y, fill=type,alpha = ..nlevel..),
                         bins=levelBins,contour_var = "ndensity", geom = "polygon") +
  scale_alpha(range=c(0,1)) + coord_fixed(ratio = 1) + theme_void() +
  scale_fill_manual(values = as.character(mySubtypeCols$hex), name="type") +
  geom_segment(data=outline_xy,aes(x = -40, y = -20, xend = -30, yend = -20)) +
  facet_grid(vars(group)) + guides(fill=guide_legend(ncol=1))

synprojFront = synprojFront + geom_path(data=outline_xy, aes(x=c1, y=c2), size = 0.5)
synprojFront
if (savePlot){
  ggsave( paste("synapseDistributions_",saveName,'_front.pdf', sep=''), plot = synprojFront, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}

# side view (zy)
synprojSide = ggplot() + 
  stat_density_2d_filled(data = dataPlot, aes(x=z, y=y, fill=type,alpha = ..nlevel..),
                         bins=levelBins,contour_var = "ndensity", geom = "polygon") +
  scale_alpha(range=c(0,1)) + coord_fixed(ratio = 1) + theme_void() +
  scale_fill_manual(values = as.character(mySubtypeCols$hex), name="type") +
  geom_segment(data=outline_zy,aes(x = -30, y = -20, xend = -20, yend = -20)) +
  facet_grid(vars(group)) + guides(fill=guide_legend(ncol=1))

synprojSide = synprojSide + geom_path(data=outline_zy, aes(x=c1, y=c2), size = 0.5)
synprojSide
if (savePlot){
  ggsave( paste("synapseDistributions_",saveName,'_side.pdf', sep=''), plot = synprojSide, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}

# top view (xz)
synprojTop = ggplot() + 
  stat_density_2d_filled(data = dataPlot, aes(x=x, y=z, fill=type,alpha = ..nlevel..),
                         bins=levelBins,contour_var = "ndensity", geom = "polygon") +
  scale_alpha(range=c(0,1)) + coord_fixed(ratio = 1) + theme_void() +
  scale_fill_manual(values = as.character(mySubtypeCols$hex), name="type") +
  geom_segment(data=outline_xz,aes(x = -40, y = -20, xend = -30, yend = -20)) +
  facet_grid(vars(group)) + guides(fill=guide_legend(ncol=1)) 

synprojTop = synprojTop + geom_path(data=outline_xz, aes(x=c1, y=c2), size = 0.5)
synprojTop
if (savePlot){
  ggsave( paste("synapseDistributions_",saveName,'_top.pdf', sep=''), plot = synprojTop, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}

```


### Look at synapse distributions of individual neurons
3D plot (just to aid visual intuition, not used in paper)
```{r}
post = 1
minConnections = synPtsPlane %>% group_by(id) %>% count() %>% filter(n >= 10)
data = synPtsPlane %>% filter(id %in% minConnections$id)

partnerType = as.character(data$partnerType[[1]])#"MC61"
print(partnerType)
partnerSubset = getBodyIdsForList(paste0(c(as.character(partnerType)),".*"))
data = data %>% filter(partnerType %in% partnerSubset$type) 

focustype = as.character(data$type[[1]])
print(focustype)
data = data %>% filter(type %in% c(focustype) & prepost == post)

myids = unique(data$id)
mycols = paletteer_c("pals::ocean.phase", n=1+length(myids))[-1]

nclear3d()
for (i in seq(1,length(myids),1)){
  toplot = synPtsPlane%>%filter(id == myids[i]) %>% select(c('x','y','z'))
  plot3d(toplot, col=mycols[i], add=TRUE,  size=5, alpha=0.3)
  plot3d(toplot %>% summarise(across(c(x,y,z), mean)), col=mycols[i], size=10, add=TRUE)
}

plot3d(roiMeshPtsPlane, size=2, alpha=0.1, add=TRUE)
decorate3d(box=FALSE)
```

The following plot is for *Figure 6E*. Run this with the settings for Figure 6 Dii (my_types = c("TuBu")) as described at at the beginning of this notebook.

```{r, warning=FALSE}
prePartnerList =c("MC61","MC64") # c(paste0("TuBu0",seq(1,9)),"TuBu10")#
preGroup = "MC"
postPartnerList = c("TuBu01","TuBu03")#unique(getBodyIdsForList(my_types)$type)

xrange = c(-5000, 2000)*convfactor
yrange = c(-3000, 4000)*convfactor
zrange = c(-4000, 3000)*convfactor
```

```{r, warning=FALSE}
saveName = paste0("MC_to_TB_in_", myROI)
perspective = "post"
for (post in seq(0,1)){
  partnertypelist = postPartnerList
  
  for (partnertype in partnertypelist){ #
    
    dataTypefilt = synPtsPlane %>% filter(type == partnertype)
    focustypelist = prePartnerList
    
    for (focustype in focustypelist){
      savestring = paste0(partnertype,'_and_',focustype,"_per_",focustype)
      
      data = dataTypefilt %>% filter((partnerType %in% c(focustype)) & (prepost == post)) %>% mutate(groupingvar = partnerid)
      
      minConnections = data %>% group_by(groupingvar) %>% count() %>% filter(n >= 10)
      data = data %>% filter(groupingvar %in% minConnections$groupingvar)
      
      toplot_2D = data %>% mutate(groupingvar = as.character(groupingvar)) %>% select(c('x','y','z', 'groupingvar'))
      
      if(is_empty(unique(toplot_2D$groupingvar))){next}
      if(length((toplot_2D$groupingvar))<=10){ next}
      print(savestring)

      colPal = paletteer_c("pals::ocean.phase",n=1+length(unique(toplot_2D$groupingvar)))[-1]

      xyproj <- ggplot(toplot_2D) + geom_point(aes(x=x, y=y, color=groupingvar, size=1, alpha=0.8)) + 
        geom_point(data=toplot_2D %>% group_by(groupingvar) %>% 
                     summarize_each(mean), aes(x=x, y=y, color=groupingvar, size=3)) +
        scale_color_manual(values = colPal, breaks = unique(toplot_2D$groupingvar)) + 
        geom_path(data=outline_xy, aes(x=c1, y=c2), size = 0.5)  +
        coord_fixed() + theme_void() + guides(size=FALSE, color=FALSE, alpha=FALSE) + lims(x=xrange,  y=yrange)
      
      zyproj <- ggplot(toplot_2D) + geom_point(aes(x=z, y=y, color=groupingvar, size=1, alpha=0.8)) + 
        geom_point(data=toplot_2D %>% group_by(groupingvar) %>% 
                     summarize_each(mean), aes(x=z,y=y, color=groupingvar, size=3)) +
        scale_color_manual(values = colPal, breaks = unique(toplot_2D$groupingvar)) + 
        geom_path(data=outline_zy, aes(x=c1, y=c2), size = 0.5) +
        coord_fixed() +theme_void() + guides(size=FALSE, color=FALSE, alpha=FALSE) + lims(x=zrange,  y=yrange)
      
      xzproj <- ggplot(toplot_2D) + geom_point(aes(x=x, y=z, color=groupingvar, size=1, alpha=0.8)) + 
        geom_point(data=toplot_2D %>% group_by(groupingvar) %>% 
                     summarize_each(mean), aes(x=x,y=z, color=groupingvar, size=3)) +
        scale_color_manual(values = colPal, breaks = unique(toplot_2D$groupingvar)) + 
        geom_path(data=outline_xz, aes(x=c1, y=c2), size = 0.5) +
        coord_fixed() +theme_void() + guides(size=FALSE, color=FALSE, alpha=FALSE) + lims(x=xrange,  y=zrange)
      
      projPlot <- grid.arrange(xyproj,zyproj,xzproj, nrow=1)
      
      if (savePlot){
        ggsave(paste("synapseDistributions_",savestring,'_post_projection.pdf', sep=''),
                plot = projPlot, device='pdf', path = "plots", 
                scale = 1, width = 60, height = 20, units ="cm", dpi = 600, useDingbats=FALSE)
      }
     
    }
  }
}

```


```{r, warning=FALSE}
saveName = paste0("TB_to_MC_in_", myROI)
perspective = "pre"

for (post in seq(0,1)){
  partnertypelist = prePartnerList
  for (partnertype in partnertypelist){
    
    dataTypefilt = synPtsPlane %>% filter(partnerType == partnertype)
    focustypelist = postPartnerList
    
    for (focustype in focustypelist){
      savestring = paste0(partnertype,'_and_',focustype,"_per_",focustype)
      
      data = dataTypefilt %>% filter((type %in% c(focustype)) & (prepost == post)) %>% mutate(groupingvar = id)
      
      minConnections = data %>% group_by(groupingvar) %>% count() %>% filter(n >= 10)
      data = data %>% filter(groupingvar %in% minConnections$groupingvar)
      
      toplot_2D = data %>% mutate(groupingvar = as.character(groupingvar)) %>% select(c('x','y','z', 'groupingvar'))
      
      if(is_empty(unique(toplot_2D$groupingvar))){next}
      if(length((toplot_2D$groupingvar))<=10){ next}
      print(savestring)

      colPal = paletteer_c("pals::ocean.phase",n=1+length(unique(toplot_2D$groupingvar)))[-1]

      xyproj <- ggplot(toplot_2D) + geom_point(aes(x=x, y=y, color=groupingvar, size=1, alpha=0.8)) + 
        geom_point(data=toplot_2D %>% group_by(groupingvar) %>% 
                     summarize_each(mean), aes(x=x, y=y, color=groupingvar, size=3)) +
        scale_color_manual(values = colPal, breaks = unique(toplot_2D$groupingvar)) + 
        geom_path(data=outline_xy, aes(x=c1, y=c2), size = 0.5)  +
        coord_fixed() + theme_void() + guides(size=FALSE, color=FALSE, alpha=FALSE) + lims(x=xrange,  y=yrange)
      
      zyproj <- ggplot(toplot_2D) + geom_point(aes(x=z, y=y, color=groupingvar, size=1, alpha=0.8)) + 
        geom_point(data=toplot_2D %>% group_by(groupingvar) %>% 
                     summarize_each(mean), aes(x=z,y=y, color=groupingvar, size=3)) +
        scale_color_manual(values = colPal, breaks = unique(toplot_2D$groupingvar)) + 
        geom_path(data=outline_zy, aes(x=c1, y=c2), size = 0.5) +
        coord_fixed() +theme_void() + guides(size=FALSE, color=FALSE, alpha=FALSE) + lims(x=zrange,  y=yrange)
      
      xzproj <- ggplot(toplot_2D) + geom_point(aes(x=x, y=z, color=groupingvar, size=1, alpha=0.8)) + 
        geom_point(data=toplot_2D %>% group_by(groupingvar) %>% 
                     summarize_each(mean), aes(x=x,y=z, color=groupingvar, size=3)) +
        scale_color_manual(values = colPal, breaks = unique(toplot_2D$groupingvar)) + 
        geom_path(data=outline_xz, aes(x=c1, y=c2), size = 0.5) +
        coord_fixed() +theme_void() + guides(size=FALSE, color=FALSE, alpha=FALSE) + lims(x=xrange,  y=zrange)
      
      projPlot <- grid.arrange(xyproj,zyproj,xzproj, nrow=1)
      
      if (savePlot){
        ggsave(paste("synapseDistributions_",savestring,'_pre_projection.pdf', sep=''),
                plot = projPlot, device='pdf', path = "plots", 
                scale = 1, width = 60, height = 20, units ="cm", dpi = 600, useDingbats=FALSE)
      }
     
    }
  }
}

```




