---
title: "Analysis of anterior visual pathway: Connectivity graphs in the AOTU (Figure 6C) and BU (Figure 8B)"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of mechanosensory information pathway coming into CX via R1 neurons

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(igraph)
#library(paletteer)

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

getBodyIdsForList = function (neuronList,prefix="",postfix=".*",...){
  #' Get one dataframe of bodyIDs for all search strings in neuronList
  #' @param neuronList: A list of search strings to be passed.
  #' @param prefix: String to be added before each query (default "")
  #' @param postfix: String to be added after each query (default ".*")
  #' @param ...: Parameters to be passed to neuprint_search. Note that meta=FALSE won't work for now.
  #' @return A data frame of metadata for the results of all the queries
  #' @examples
  #' \dontrun{
  #' # Both will return the same
  #' getBodyIdsForList(c("PFL1","PFL2"))
  #' getBodyIdsForList(c("PFL1","PFL2"),postfix="",field="type")
  #' }
  
  neuronList <-  paste0(prefix,neuronList,postfix)
  bodiesList <- lapply(neuronList,neuprint_search,...)
  return(bind_rows(bodiesList))
}
```

```{r}
neuprint_login()
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```


### Make selection of neurons to be used in connecitivy analysis
```{r}
ROI = "AOTU" #name for reference
slctROI ="AOTU(R)" #name as in neuprint

splitLR = TRUE # Whether or not to split neurons within a type into a left and right group.
makeAsymmetric = TRUE # Whether to enforce showing only pregroup -> postgroup connections as opposed to all connections within {pregroup,postgroup}

saveName = paste0("Inputs_in_", ROI)
if(splitLR){saveName = paste0(saveName,"_LR")}

#only relevant if one of the above is false:
useCustomPreSelection = FALSE
useCustomPostSelection = TRUE
usenbag = FALSE
inCX = FALSE

if(!useCustomPostSelection | !useCustomPreSelection){
  if(splitLR){
    roiTable = getTypesInRoiTable(slctROI)
  }else{
    roiTable = getTypesInRoiTable(slctROI,renaming = cxRetyping,minTypePercentage = 0.5)
  }
}
# filter based on what is in Shin-ya's CX neuron list
CXneuronList = read.csv(file.path("..","CX-cell-types060920.csv"))
```


***Selection of neurons***
```{r}
# POST
if(useCustomPostSelection){
  postNeuron = c("TuBu","TuTuB","AOTU046")
  postNeuron = paste0(postNeuron,".*")
  postName = "TuBu, TuTu and  AOTU46"
  postIDs = getBodyIdsForList(postNeuron)
  if(inCX){
    postIDs = postIDs %>% filter(type %in% CXneuronList$n.type)
  }
}else{
  postName = paste0("all in ", ROI)
  postIDs = roiTable$names
  postIDs = postIDs %>% filter(databaseType %in% CXneuronList$n.type)
}

# PRE
if(useCustomPreSelection){
  preNeuron = c('FB.*')
  preName = "FBt"
  preIDs = getBodyIdsForList(preNeuron)
  preIDs = preIDs %>% filter(type %in% CXneuronList$n.type)
}else{
  if(usenbag){
    nbag = create_neuronBag(postIDs)
    preIDs = nbag$inputs %>% filter(roi == slctROI) %>% select(type.from) %>% unique()
    preIDs = getBodyIdsForList(preIDs$type.from , field="type")
    preName = paste0("all ", ROI)
  }else{
    preName = paste0("all ", ROI)
    preIDs = roiTable$names
    if(inCX){
      preIDs = preIDs %>% filter(databaseType %in% CXneuronList$n.type)
    }
  }
}

```


### Get connectivity table
```{r, warning=FALSE}
preTypes = c(preIDs$bodyid, postIDs$bodyid) # preIDs$bodyid
postTypes = preTypes#postIDs$bodyid
myConnections = getConnectionTable(preTypes, "POST", slctROI)
myConnections = myConnections %>% filter(to %in% postTypes) 
```


### Format the connectivity matrix, convert to type-to-type
```{r}
# Make asymmetric matrix
if (makeAsymmetric){
  myConnections = myConnections %>% filter(to %in% postIDs$bodyid)  %>% filter(from %in% preIDs$bodyid)
}

# Make type-to-type connectivity table
typesTable <- getTypesTable(unique(myConnections$databaseType.to))

if (splitLR){
  # Subdivide types and build a custom types table
  myConnections = lateralize_types(myConnections, postfix="to")
  myConnections = lateralize_types(myConnections, postfix="from")
  typesTable = lateralize_types(typesTable, postfix="raw")
}

myConnectionsT2T = getTypeToTypeTable(myConnections,typesTable = typesTable)
```

### Connectivity matrix
```{r}
plotW = 15
plotH =  10
plotType = "type" #id, name
cmax = NULL
cmaxtype = NULL
 
connectionMeasure = "weightRelative"
conMatPlot = plotConnectivityMatrix(myConnectionsT2T, byGroup = plotType, connectionMeasure, cmaxtype)
conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
print(conMatPlot)
if (savePlot){
  ggsave( paste0("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_by',plotType,'.pdf'), plot = conMatPlot, device='pdf',
          path = "plots", scale = 1.5, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}
```

###  Draw graph

```{r, warning=FALSE} 
require(igraph)

connectionMeasure = "weightRelative"
cutoff = 0.01 # for weight 0.05, 0.01, 0

largeGraph = FALSE
selfFeedbackScale = 10
edcurve = 0.1#0.15
edgeNorm = 0.07#0.07#0.05#0.07#0.03#

showself = FALSE 
removeIso = TRUE

# drop na in "to" column
myConnectionsT2T = myConnectionsT2T %>% drop_na(type.to)
graphData = data.frame(from = myConnectionsT2T$type.from, to = myConnectionsT2T$type.to, relWeight = myConnectionsT2T$weightRelative)

graphData_noSelf = getNoSelfGraphData(graphData)  
graphData_self = getSelfFBGraphData(graphData)

if (showself){
  graphData = graphData
  graphName = saveName
} else {
  graphData = left_join(graphData_noSelf, graphData_self)
  graphName = paste0(saveName, "_noSelf")
}

# Graph parameter
if(largeGraph){
  vertexSize = 3
  plotSize = 15
}else{
  vertexSize = 12
  plotSize = 10
}

selfFBscale = vertexSize
arrowSize = 0.5 # set to 0 if you prefer styling arrows in e.g. adobe illustrator

```

Plot graph with defined colormap from file
```{r, warning=FALSE} 
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")

myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}

if(splitLR){
  myColorMap_R = myColorMap %>% mutate(Type = paste0(Type, "_R"))
  myColorMap_L = myColorMap %>% mutate(Type = paste0(Type, "_L"))
  myColorMap= bind_rows(myColorMap_L, myColorMap_R)
}

myColorMap = myColorMap %>% filter(Simpletype == "no")

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale, arrowSize, edgeNorm, colormap = myColorMap)

# remove isolated nodes
if(removeIso){
  Isolated = which(degree(myGraph) == 0)
  myGraph = delete.vertices(myGraph, Isolated)
}

myGraph$main = paste0("Connectivity within   the ",slctROI)
l = layout_with_fr(myGraph)

plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph), legend=TRUE,
     family="Arial", vertex.label.family  = "sans",edge.arrow.size=arrowSize)

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-1,y=-0,legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5),  bty = "n", seg.len=0.5)

if (savePlot){
  dev.print(pdf, file.path("plots",paste0("connectivityGraph_",graphName,'_in_',slctROI,
                        "_",connectionMeasure, round(100*cutoff),"perc.pdf")), width=plotSize, height=plotSize)
}
```

Layered layout
```{r}
patternLayers = c("MC","TuTu","AOTU","TuBu")
layerPos = c(0,3,4,5)
defaultX = 1
edcurve = 0 #0.15

vertexProps = data.frame(name = V(myGraph)$name, col = V(myGraph)$color) %>% mutate(name = gsub("_[R,L]", "", name))
vertexProps = vertexProps %>% mutate(loc = "default", yloc = seq(length(vertexProps$col)), xloc = defaultY)

for(layer in seq(length(patternLayers))){
  vertexProps[grepl(patternLayers[layer],vertexProps$name),] = vertexProps[grepl(patternLayers[layer],vertexProps$name),] %>% 
    mutate(loc = paste0("layer",layerPos[layer]+1), xloc = layerPos[layer], yloc = 1*seq(length(loc))/length(loc) )
}
vertexProps$yloc[vertexProps$loc == "default"] = (1/length(vertexProps$loc))*seq(length(vertexProps$loc[vertexProps$loc == "default"]))

plot(myGraph,edge.curved=edcurve, layout=layout.norm(as.matrix(vertexProps[,c("xloc","yloc")])),
     edge.color = customizeGraphEdges(myGraph), family="Arial", vertex.label.family = "sans",edge.arrow.size=arrowSize)

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-1,y=-0.1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5),  bty = "n", seg.len=0.5)

if (savePlot){
  dev.print(pdf, file.path("plots",paste0("connectivityGraph_",graphName,'_in_',slctROI,
                "_",connectionMeasure, round(100*cutoff),"perc_layered.pdf")), width=plotSize, height=plotSize)
}
```

