---
title: "Inputs summary figures preparation (generates data for figure 5 and 15)"
output: html_notebook
---

This notebook does the computing legwork and save objects to be used by the figure notebooks (figures 5 and 15). This is in large parts (polarity notwithstanding) to the "Outputs-Core.Rmd" notebook in the outputs section.
# Preparing the environment
Loading necessary packages
```{r message=FALSE, warning=FALSE}
library(readr)
```
Loading some local functions (this uses code associated with the outputs analysis)
```{r message=FALSE}
source(file.path("..","outputsFig","outputFunctions-core.R"))
source(file.path("..","R","table2ggraphUtils.R"))
```

A folder where we'll save the data locally to be used by other notebooks:
```{r}
dataFolder <- "data"
if (!dir.exists(dataFolder)) dir.create(dataFolder)
```

# Building the inputs neuron pathways

## Find neurons innervating outside the CX
We first load the central complex types from our hand curated table, extending it with some neuprint metadata, and retyped with `cxRetyping`, a function from `neuprintrExtra`, that splits types by side in the brain while taking care of the few exceptions for FB columnar neurons. 
```{r}
roiH <- getRoiTree()
CXtypes <- supertype(read_csv(file.path("..","CX-cell-types060920.csv")) %>% 
                        rename(databaseType=n.type))
CXNeurons <- getTypesTable(CXtypes$databaseType)
CXNeurons <- cxRetyping(CXNeurons,postfix="raw")
CXNeurons <- supertype(CXNeurons)%>% mutate(supertype="CX")
head(CXNeurons)
```

We define the "outside" regions as any neuropile that is not in the CX and not on the left side of the brain (we want to work with the right side, which is more complete).
```{r}
outsideRegions <- unique(selectRoiSet(exceptions=sapply(as.character(unique(roiH$level1[grepl(roiH$level1,pattern="(R)")])),
                                                        function(i) return(1),
                                                        USE.NAMES = TRUE,simplify=FALSE),
                                      exceptionLevelMatch = 1)$roi[roiH$level1!="CX" & roiH$side4!="Left"])
```
We then select all CX types with at least 20 synapses either upstream or downstream in the outside regions, and compute different metrics of their relative polarity in those regions. 
```{r}
CXOutsideTypes <- getROISummary(CXNeurons,threshold=0)

CXOutsideTypes <- filter(CXOutsideTypes,roi %in% outsideRegions) %>% group_by(type,databaseType,n,supertype1,supertype2,supertype3) %>%
   summarize(upstream=sum(upstream),
             downstream=sum(downstream),
             fullWeight=sum(fullWeight),
             downstreamRatio=downstream/fullWeight,
             polarityRatio=(downstream/totalDownstream[1])/(upstream/totalUpstream[1])) %>%
   ungroup() %>% distinct()
CXOutsideTypes <- filter(CXOutsideTypes,upstream>20 | downstream>20)
CXOutsideNeurons <- filter(CXNeurons,type %in% CXOutsideTypes$type)
head(CXOutsideTypes)
```

List all the neurons we know something about in a table -- following the classification defined in Scheffer et al. The `customRetyping` function, defined in "outputFunctions-core.R" is the same as `cxRetyping` (from the `neuprintrExtra` package) with the added retyping of what appears as DNb01 in the database but is likely two different types.
```{r}
knownTypesTable <- list("CX"=CXNeurons,
                        "DA"= neuprint_search("^PPL.*|^PAM.*|^PPM.*") %>% 
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="DAN"),
                        "MBON"=neuprint_search("^MBON.*") %>% 
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype() %>% supertype()%>% mutate(supertype="MBON"),
                        "5-HT"=neuprint_search(".*5-HT.*|.*5HT.*") %>% 
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="5HT"),
                        "OA"=neuprint_search("^OA-.*") %>% 
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="OA"),
                        "KC"=neuprint_search("^KC.*") %>% 
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="KC"),
                        "Peptidergic"=neuprint_search("^AstA.*|^CRZ.*|^DSKMP.*|^NPFL.*|^PI1.*|^SIF.*") %>%
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="Peptidergic"),
                        "Clock"=neuprint_search("^DN1.*|l-LNv.*|LNd.*|^LPN.*|s-LNv.*") %>%
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="Clock"),
                        "Fru"=neuprint_search("^ovi.*|^aSP.*|^aDT.*|^aIP.*|^pC1.*|^vpo.*") %>%
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="Fru"),
                        "DN"=neuprint_search("^Giant.*|^MDN.*|^DN[a-z].*|^DN\\\\\\\\?.*") %>%
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="DN"),
                        "Sensory"=neuprint_search("^HRN.*|^JO.*|^OGC.*|^ORN.*|^TRN.*") %>%
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="Other Sensory"),
                                  "LH"=neuprint_search("^LH.*") %>%
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="LH"),
                                  "Visual"=neuprint_search("^aMe.*|^CTX.*|^DCH.*|^H[1-3].*|^HBeyelet.*|^HS.*|^LC[1-9].*|^Li[1-9].*|^LLPC.*|^LPC.*|^LT[1-9].*|^MC[1-9].*|^VCH.*|^VS.*") %>% 
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="Visual PNs"),
                                  "AL"=neuprint_search("^AL-.*|^AL[B|I]N.*|^D_ad.*|^D[A|C|L|M|P][1-9].*|^il3.*|^l2LN.*|^lLN[1-9].*|^M_.*|^mAL.*|^MZ_.*|^v2LN[1-9].*|^V[A|C|L][1-9].*|^vLN.*|^V[M|P][1-9].*|^Z_v.*|^Z_lv.*") %>%
                           mutate(databaseType=type) %>% customRetyping() %>% 
                           supertype()%>% mutate(supertype="Antennal lobe")
                                  )

knownTypesTable <- do.call(rbind,lapply(1:length(knownTypesTable), function(i) mutate(knownTypesTable[[i]],group.to=names(knownTypesTable)[i])))
knownTypesTable <- retype.na_meta(knownTypesTable)
knownTypesTable <- distinct(rbind(select(knownTypesTable,type,supertype),
                                   data.frame(type=lrInvert(knownTypesTable$type),supertype=knownTypesTable$supertype)))
allKnownTypes <- unique(knownTypesTable$type) 
head(knownTypesTable)
```

Save it so that it can be reused in the figure making notebooks:
```{r}
saveRDS(knownTypesTable,file.path(dataFolder,"known-table.rds"))
```

## Get type to type connection tables up to 5 hops out
Calculate a massive pathway table of everything presynaptic to those neurons outside of the CX, in 5(!!) steps or less (doing it "raw" for more flexibility afterwards). 
The `overruleThreshold` set here to 50, means that any neuron that a connection with more than 50 synapses will be kept even if other criterions are not met. This is to deal with very large neurons innervating with large swaths of the outside regions (since we collate all the neuropiles in there together as a super ROI).
This generates a list of 5 type to type connection tables (one for each step).
CAUTION: Running this cell will take more than 30 minutes.
```{r}
CX_inGraphBi <- get_type2typePath_raw(type.to=CXOutsideNeurons,
                                      ROI=list("Outside_regions(R)"=outsideRegions),
                                      n_steps=1:5,addContraPaths = T,thresholdPerROI = 20,verbose=TRUE,renaming=customRetyping,overruleThreshold=50,largeOnly=TRUE)
head(CX_inGraphBi[[1]])
```

We then filter out types receiving close to nothing (types that in total receive less than 20 synapses from neurons outside of the central complex), and propagates through the 5 layers.
```{r}
CX_inGraphBi[[5]] <- CX_inGraphBi[[5]] %>% 
   group_by(type.to,supertype3.to) %>% 
   mutate(totalWeightRaw=sum(absoluteWeight)) %>% 
   filter(totalWeightRaw>20) %>% 
   select(-totalWeightRaw)

for (n in 4:1){
   CX_inGraphBi[[n]] <- filter(CX_inGraphBi[[n]],type.to %in% CX_inGraphBi[[n+1]]$type.from)
}
```

Reduced version of the pathways: we have simulated the left side of the brain, but since we want to analyze only pathways that end on the right side of the brain, we need to remove connections from CX neurons that have been simulated in the last step (those will have ROI "Outside_regions(R)_contra" instead of "Outside_regions(R)")
```{r}
CX_inPaths <- CX_inGraphBi
CX_inPaths[[5]] <- filter(CX_inPaths[[5]],roi == "Outside_regions(R)") 

##List the types
CXInputTypes <- unique(CX_inPaths[[5]]$type.to)
CXInputNeurons <- filter(CXOutsideNeurons,type %in% CXInputTypes)

for (n in 4:1){
   CX_inPaths[[n]] <- filter(CX_inPaths[[n]],type.to %in% CX_inPaths[[n+1]]$type.from)
   CX_inPaths[[n]] <- filter(CX_inPaths[[n]],!(type.to %in% CXInputTypes & roi=="Outside_regions(R)_contra"))
}
```

Supertype at a very broad level for some of the figure coloring to come. `customOutputSupertype` is defined in "outputFunctions-core.R" and divides the types as they are throughout the output section (for example, see figure 54B)
```{r}
CXInputNeurons <- selectSupertypeSet(CXInputNeurons,default_level = 1) %>%
   customOutputSupertype(postfix = "raw")
```

Save simple variables
```{r}
save(CXInputNeurons,CXOutsideTypes,CXInputTypes,outsideRegions,CXOutsideNeurons,CXNeurons,
     file=file.path(dataFolder,"inputsBasics.RData"))
```

Then make tables of all post-synapses to CX neurons in the outside regions (omitting the FB tangentials as those will be plotted in the FB section). This uses the `collectSynapses` function defined in "Outputs/outputFunctions-core.R". This is will be used in the synapse location plots.
CAUTION: Executing this cell will take around 30 minutes
```{r,warning=FALSE}
CXInSyn <- collectSynapses(filter(CXInputNeurons,
                                  supertype2 != "FBt"),
                           outsideRegions,polarity="post")

CXInSyn <- supertype(CXInSyn)
```
```{r}
saveRDS(CXInSyn,file.path(dataFolder,"CX-outsideSynapses_Inputs.rds"))
```

## The CX input graph
We now want to treat this "5 steps" pathways collection as a large graph.
### Create the graph
We first collate all connections present:
```{r}
CX_inGraph <- distinct(do.call(rbind,CX_inPaths))
```
For cases where a neuron pair has connections on both sides of the brain, we use the average relative weight, weighted on the importance of the innervation on each side: 
```{r}
## For contra ROI + ipsi ROI case, we need an approximation of the relative weight and output contribution
CX_inGraph <- group_by(CX_inGraph,type.to) %>% 
   mutate(combineROIweight=sum(totalROIweight[match(unique(roi),roi)])) %>% ungroup() 

CX_inGraph <- group_by(CX_inGraph,type.from,type.to,
                       supertype1.from,supertype2.from,supertype3.from,
                       supertype1.to,supertype2.to,supertype3.to,
                       databaseType.from,databaseType.to,n_type) %>%
   summarize(weightRelative=mean(weightRelative*totalROIweight/combineROIweight),
             outputContribution=sum(weight)/sum(totalPreROIweight*n_from)) %>% 
   ungroup()
```

We are also using a normalized relative weight (so that it sums to 1 for all significant connections to a given neuron, this will be used to make figure 5 panel B interpretable)
```{r}
CX_inGraph <- group_by(CX_inGraph,type.to) %>% 
   mutate(wr_norm=weightRelative/sum(weightRelative)) %>% 
   ungroup() 

```

We then create a graph from the connection table as a `tidygraph` object, using `makeGraph` which is defined in **R/table2ggraphUtils.R**.
`allNodes` is a data frame of all the neurons (nodes) in the graph, stored for convenience.
```{r}
CX_inGraph <- makeGraph(CX_inGraph)

allNodes <- CX_inGraph %>% activate(nodes) %>% as_tibble()
```

### Calculate pathway weights
We then calculate pathway weights from all the possible sources from the CX output types, multiplying the adjacency matrix of the whole graph to convergence, as described in the Methods figure.

- First we gather the graph as an adjacency matrix using an `igraph` function. We build the adjacency matrix here, with the normalized relative weights.
```{r}
CXin_AdjWRNorm <- igraph::as_adjacency_matrix(CX_inGraph,attr="wr_norm")
```

We then use functions `endpointConnections_raw` and `endpointConnections` defined in **../Outputs/outputFunctions-core.R**. Those do the legwork of recursively multiplying/adding the connectivity matrices and checking for convergence. We run this from all the "known" types present in the graph.
```{r}
knownNeuronsReached <- allNodes$type[allNodes$type %in% allKnownTypes]

endpointsInfluencerM <- endpointConnections(CXin_AdjWRNorm,
                                            endpoint=knownNeuronsReached,
                                            polarity = "from_sources",
                                            maxIt=100,eps=10^-8)

endpointsInfluence <- reshape2::melt(as.matrix(endpointsInfluencerM[,CXInputTypes]),
                                     na.rm=TRUE,value.name="Path_weight") %>% 
   filter(Path_weight>0) %>%
   rename(type.from=Var1,type.to=Var2)

endpointsInfluence <- mutate(endpointsInfluence,
                             type.from=as.character(type.from),
                             type.to=as.character(type.to),
                      databaseType.to=allNodes$databaseType[match(type.to,allNodes$type)],
                      databaseType.from=allNodes$databaseType[match(type.from,allNodes$type)],
                      supertype.from=knownTypesTable$supertype[match(type.from,knownTypesTable$type)]
                      ) %>% supertype()

head(endpointsInfluence)
```

```{r}
saveRDS(endpointsInfluence,file.path(dataFolder,"endpoints-influence_Inputs.rds"))
```
