---
title: "Analysis of wind (mechanosensoy) info comming into CX"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of mechanosensory information pathway coming into CX via R1 neurons

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(igraph)
source(file.path("..","R","visualizeConnectivityTables.R"))
options(nat.plotengine = 'rgl')


```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

## Bodyid's of neurons that are potentially involved
The propose pathway presented in Suver et al is Johnstons organs -> APN3/APN2 -> WPN

Here we will try to identify which neurons in the EM volume correspond to APN2, APN3 and WPN and illustrate a potential route toward the fly's heading circuit.
```{r}
#APN3s (presynaptic of APN2s):
APN3ids = c(975289165, 1099073905, 1130458829)
#APN2s (postsynaptic of APN3s): 
APN2ids = c(1539649574, 2096909915, 2096913987)

# get names
for (i in APN3ids) {
  print(neuprint_get_neuron_names(i))
}
for (i in APN2ids) {
  print(neuprint_get_neuron_names(i))
}
```
We will also consider the putative WL-L neuron, which is wind sensitive and connects to R1
```{r}
#WL-L
WLLids = c(1386849677, 1539632818)

for (i in WLLids) {
  print(neuprint_get_neuron_names(i))
}
```

Get all neurons of the type described by the bodyids  above
```{r}
APN2type =  c("SAD004", "SAD003")
APN3type = "SAD077"
APN3 = neuprint_search("SAD077_.*")
APN2 = bind_rows(neuprint_search("SAD004.*"),neuprint_search("SAD003.*"))
APN2and3 = bind_rows(APN2, APN3) 

APNBodies = c(APN3$bodyid,APN2$bodyid)

WLLtype = "LAL138"
WLL = neuprint_search(paste0(WLLtype,".*"))

```


Also get body ID's of putative downstream partners
```{r}
# Putative WPN, based on morphology and connectivity:
#(these were identified in a shortest path analysis as shown later)
WPNtype = "LHPV6q1"
WPN = neuprint_search(paste0(WPNtype,".*"))

# Ring neurons
ER1 = neuprint_search("ER1_.*")
ER1a = neuprint_search("ER1_a.*")
ER1b = neuprint_search("ER1_b.*")

ER3a= neuprint_search("ER3a.*")

ER1and3a =  bind_rows(ER1, ER3a) 

ER1and3_andWLLWPN =  bind_rows(ER1, ER3a, WLL,WPN) 

splitLR = TRUE
```

## Find paths to the CX
```{r}
maxL = 5

APN_to_ER1_t2tpath = get_type2typePath(APN2and3, ER1b, by.roi = FALSE, n_steps = seq(maxL),renaming=lateralize_types)
```

```{r}
APN_to_ER1or3_t2tpath = get_type2typePath(APN2and3, ER1and3a, by.roi = FALSE, n_steps = seq(maxL),renaming=lateralize_types)
```


```{r}
cutoff = 0#0.02#0.01#
edcurve = 0.15
vertexSize = 7
edgeNorm = 0.04
minPathWeight = 0.1 ** maxL#
plotSize = 10

cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")

myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}

if(splitLR){
  myColorMap_R = myColorMap %>% mutate(Type = paste0(Type, "_R"))
  myColorMap_L = myColorMap %>% mutate(Type = paste0(Type, "_L"))
  myColorMap= bind_rows(myColorMap_L, myColorMap_R)
  
}
graphName = "pathGraph_APN_2_ER1or3_0-1-exp5"

pathDf = APN_to_ER1or3_t2tpath %>% filter(weightRelative_path  >= minPathWeight )

graphDataFrame = pathDf2graphDf(pathDf) %>% mutate(relWeight =  weightRelative)
myColorMap = myColorMap %>% filter(Simpletype == "no")

myGraph = constructConnectivityGraph(graphDataFrame, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm,colormap = myColorMap)

l = layout_with_dh(myGraph)
myGraph$main = paste("Min path weight = ", minPathWeight)

plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph), 
     family="Arial", vertex.label.family  = "sans")
maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-0.8,y=1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)),  bty = "n", seg.len=0.5)

#dev.print(pdf, paste0("plots",graphName,".pdf"), width=plotSize, height=plotSize,useDingbats=FALSE)
```

Layered layout
```{r}
patternLayers =c("SAD","WEDPN","WED","PV","LAL","ER")
layerPos = c(0,2,3,4,5,6)
defaultX = 1
edcurve = 0.1
arrowSize = 0.4 # set to 0 if you prefer styling arrows in e.g. adobe illustrator

myGraph = constructConnectivityGraph(graphDataFrame, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm,colormap = myColorMap)

vertexProps = data.frame(name = V(myGraph)$name, col = V(myGraph)$color) %>% mutate(name = gsub("_[R,L]", "", name))
vertexProps = vertexProps %>% mutate(loc = "default", yloc = seq(length(vertexProps$col)), xloc = defaultX)

for(layer in seq(length(patternLayers))){
  vertexProps[grepl(patternLayers[layer],vertexProps$name),] = vertexProps[grepl(patternLayers[layer],vertexProps$name),] %>% 
    mutate(loc = paste0("layer",layerPos[layer]+1), xloc = layerPos[layer], yloc = 1*seq(length(loc))/length(loc) )
}
vertexProps$yloc[vertexProps$loc == "default"] = (1/length(vertexProps$loc))*seq(length(vertexProps$loc[vertexProps$loc == "default"]))

plot(myGraph,edge.curved=edcurve, layout=layout.norm(as.matrix(vertexProps[,c("xloc","yloc")])),
     edge.color = customizeGraphEdges(myGraph), family="Arial", vertex.label.family = "sans",edge.arrow.size=arrowSize)

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=0.1,y=-0.1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5),  bty = "n", seg.len=0.5)

if (savePlot){
  dev.print(pdf, file.path("plots",paste0("connectivityGraph_",graphName,'_',round(100*cutoff),"perc_layered.pdf")), width=plotSize, height=plotSize)
}
```
