---
title: "Analysis of windsensory ring neurons in LAL"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of mechanosensory information coming into CX via ER1 neurons

Code to generate visualizations of synapse distributions (Figure 9E, Figure 9 figure supplement 1 B) and a specilized connectivity matrix (Figure 9 figure supplement 1 A).

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
#library(dplyr)
library(neuprintrExtra)
library(alphahull)
#library(igraph)
library(paletteer)
library(gridExtra)

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","SynapsePCAUtils.R"))
source(file.path("..","R","paperTheme.R"))

getBodyIdsForList = function (neuronList,prefix="",postfix=".*",...){
  #' Get one dataframe of bodyIDs for all search strings in neuronList
  #' @param neuronList: A list of search strings to be passed.
  #' @param prefix: String to be added before each query (default "")
  #' @param postfix: String to be added after each query (default ".*")
  #' @param ...: Parameters to be passed to neuprint_search. Note that meta=FALSE won't work for now.
  #' @return A data frame of metadata for the results of all the queries
  #' @examples
  #' \dontrun{
  #' # Both will return the same
  #' getBodyIdsForList(c("PFL1","PFL2"))
  #' getBodyIdsForList(c("PFL1","PFL2"),postfix="",field="type")
  #' }
  
  neuronList <-  paste0(prefix,neuronList,postfix)
  bodiesList <- lapply(neuronList,neuprint_search,...)
  return(bind_rows(bodiesList))
}

neuprint_login()
```


### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

## Get some synapse locations
Choose ROI and get curated list of neurons. 
For *Figure 9Ei* choose my_types = c("ER1_a"), preName = "ER1aInput", postName = "ER1_a".
For *Figure 9Eii* and *Figure 9 -- figure supplement 1* choose my_types = c("ER1_b"), preName = "ER1bInput", postName = "ER1_b".
```{r message=FALSE, warning=FALSE}
myROI = "LAL(R)"

my_types = c("ER1_b") #This should be the post-synaptic partners

preName = "ER1bInput"
postName = "ER1_b"
saveName = paste0(preName, "_", myROI)

my_types = paste0(my_types, ".*")

my_neurons = getBodyIdsForList(my_types)
```

```{r}
my_types = paste0(my_types, ".*")
my_neurons = getBodyIdsForList(my_types)

# Generate color map
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")
myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}
```

...use this list to get synapse locations
```{r}
my_synapses = neuprint_get_synapses(as.numeric(getBodyIdsForList(my_types)$bodyid),myROI)

my_synapses = my_synapses %>% mutate(
name=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["name"]],
type=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["type"]],
partnerName=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["name"]],
partnertype=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["type"]])
```


## (1) Import of ROI meshes and get vertices in x,y,z
```{r}
roiMesh = neuprint_ROI_mesh(myROI)
roiMeshPts = data.frame(dotprops(roiMesh)$points)
names(roiMeshPts) <- c("x","y","z")
```


## (2) Find convenient coordinate system based on PCA of vertices and center of mass of the ROI
***Transform mesh  and synapse locations***
```{r}
# define new origin from roi center of mass
origin = getCOM(roiMeshPts)

#reset orgin
roiMeshPts = resetOrigin(roiMeshPts, origin)

#get eigenvectors
roiEigen = covPCA(roiMeshPts)

roiMeshPtsRot = changeBasis(roiMeshPts, roiEigen)

#Synapse locations
synPts = data.frame(x=as.numeric(my_synapses$x),
                    y=as.numeric(my_synapses$y),
                    z=as.numeric(my_synapses$z))
synPts = resetOrigin(synPts, origin)
synPtsRot = changeBasis(synPts, roiEigen)
```

***Select either original or EV coordinates and rotate***
```{r}
flipx = 1; flipy = -1; flipz = 1

rot = c(180,0,0)

roiMeshPtsPlane = data.frame(x=roiMeshPtsRot$X, y=roiMeshPtsRot$Y, z=roiMeshPtsRot$Z)
synPtsPlane = data.frame(x=synPtsRot$X, y=synPtsRot$Y, z=synPtsRot$Z)

# rotate points
roiMeshPtsPlane = data.matrix(roiMeshPtsPlane)
synPtsPlane = data.matrix(synPtsPlane)

roiMeshPtsPlane = roiMeshPtsPlane %*% makeRotMatXY(rot[1])
synPtsPlane = synPtsPlane %*% makeRotMatXY(rot[1])
roiMeshPtsPlane = roiMeshPtsPlane %*% makeRotMatYZ(rot[2])
synPtsPlane = synPtsPlane %*% makeRotMatYZ(rot[2])
roiMeshPtsPlane = roiMeshPtsPlane %*% makeRotMatXZ(rot[3])
synPtsPlane = synPtsPlane %*% makeRotMatXZ(rot[3])

roiMeshPtsPlane = data.frame(x=flipx*roiMeshPtsPlane[,1],y=flipy*roiMeshPtsPlane[,2],z=flipz*roiMeshPtsPlane[,3])
synPtsPlane = data.frame(x=flipx*synPtsPlane[,1],y=flipy*synPtsPlane[,2],z=flipz*synPtsPlane[,3],
                         type = as.factor(my_synapses$type), 
                         partnerType = as.factor(my_synapses$partnertype),
                         name = as.factor(my_synapses$name), 
                         partnerName = as.factor(my_synapses$partnerName),
                         id = as.factor(my_synapses$bodyid),
                         partnerid = as.factor(my_synapses$partner),
                         prepost = as.factor(my_synapses$prepost))

#Add simple type name
synPtsPlane = synPtsPlane %>% mutate(simpleType = gsub("_.*", "",type))

synCount = synPtsPlane %>% count(type)
typeFilter = synCount$type[synCount$n > 10]

# generate color map
dataFilt = synPtsPlane %>% filter(type %in% typeFilter)

myTypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$simpleType)) %>% filter(Simpletype == "yes")
myTypeCols = myTypeCols[match(as.character(unique(dataFilt$simpleType)), myTypeCols$Type),] %>%
  arrange(unique(dataFilt$simpleType))
```

### Look at synapse distributions of individual neurons
```{r}
# get outline
meshOutline <- ahull(x=roiMeshPtsPlane$y,y=roiMeshPtsPlane$x,alpha=150)
outline_xy = data.frame(meshOutline$arcs)

meshOutline <- ahull(x=roiMeshPtsPlane$z,y=roiMeshPtsPlane$y,alpha=150)
outline_zy = data.frame(meshOutline$arcs)

meshOutline <- ahull(x=roiMeshPtsPlane$x,y=roiMeshPtsPlane$z,alpha=150)
outline_xz = data.frame(meshOutline$arcs)
```

Find major partners of ER1_b in the LAL
```{r}
minSyn = 5
inputTypes = my_synapses %>% filter(prepost == 1 ) %>% group_by(partnertype) %>% count() %>% filter(n>=minSyn)
mainInput = inputTypes %>% filter(n>=minSyn)
mainInput = mainInput$partnertype
mainInput

mainInputIDs = getBodyIdsForList(mainInput)
mainOutputIDs = getBodyIdsForList(my_types)

splitLR  = FALSE
```


# Get connectivity table
```{r, warning=FALSE}
myConnections = getConnectionTable(mainInputIDs$bodyid, "POST", myROI)
myConnections = myConnections %>% filter(to %in% mainOutputIDs$bodyid) 
  
typesTable <- getTypesTable(unique(myConnections$databaseType.to))

myConnectionsT2T = getTypeToTypeTable(myConnections,typesTable = typesTable)
```

Connectivity matrix
```{r}
plotW = 12
plotH = 20
cmax = NULL

connectionMeasure = c("weightRelative")

position = synPtsPlane %>% select(c('x','id')) %>% group_by(id)  %>% summarize_each(mean) %>% arrange(x) %>% mutate(oder = seq(length(x)))
position$id =as.numeric(as.character(position$id))
myConnections_plot = left_join(myConnections,position, by=c("to" = "id"))

conMatPlot = plotConnectivityMatrix(myConnections_plot, byGroup = "id", connectionMeasure, cmax, postfixto=as.character(myConnections_plot$oder))
conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, myROI, connectionMeasure)
  
print(conMatPlot)
ggsave(paste0("connectivityMatrix_",saveName,'_',connectionMeasure,'_byID_minSyn',minSyn,'.pdf'), 
    plot = conMatPlot, device='pdf', path = "plots",
    scale = 1, width = plotW+3, height =plotH, units ="cm", dpi = 600, limitsize = TRUE)
  
conMatPlot = structureMatrixPlotByType_lines(conMatPlot, TRUE)
print(conMatPlot)
ggsave(paste0("connectivityMatrix_",saveName,'_',connectionMeasure,'_byID_grouped_minSyn',minSyn,'.pdf'), 
    plot = conMatPlot, device='pdf', path = "plots",
    scale = 1, width = plotW, height =plotH, units ="cm", dpi = 600, limitsize = TRUE)
```


3D plot (not part of paper)
```{r}
post = 1
partnerType = arrange(inputTypes, desc(n))$partnertype[2]
partnerSubset = getBodyIdsForList(paste0(c(partnerType),".*")) #  "TuBu", "ER"
focustype = postName
data = synPtsPlane %>% filter(partnerType %in% partnerSubset$type) %>% 
  filter(type %in% c(focustype) & prepost == post)

myids = unique(data$id)
mycols = paletteer_c("pals::ocean.phase", n=1+length(myids))[-1]

nclear3d()
for (i in seq(1,length(myids),1)){
  toplot = synPtsPlane%>%filter(id == myids[i]) %>% select(c('x','y','z'))
  if (! i %% 1){
    plot3d(toplot, col=mycols[i], add=TRUE,  size=5, alpha=0.4)
    plot3d(toplot %>% summarize_each(mean), col=mycols[i], size=10, add=TRUE)
  }
  plot3d(toplot %>% summarize_each(mean), col=mycols[i], size=8, add=TRUE)
}

plot3d(roiMeshPtsPlane, size=2, alpha=0.1, add=TRUE)
decorate3d(box=FALSE)
```

### Illustrate synapse distributions of focus type
This plot is shown for in Figure 9 Ei (for ER1_a) and Eii (for ER1_b). 
```{r, warning=FALSE}
xrange = c(-6000, 7000)
yrange = c(-7000, 8000)
zrange = c(-5000, 4000)

data = synPtsPlane %>% filter(type %in% c(focustype) & prepost == 1)

focusTypeLoc = ggplot(data) + geom_point(aes(x=y, y=x, color=id, shape=name),size = 1, alpha=1.0, stroke = 0, shape = 16) + 
     geom_point(data = data %>% group_by(id) %>% summarize_each(mean), aes(x=y, y=x, fill=id), shape = 21, color='black',size=3,stroke=1) +
     scale_color_manual(values = paletteer_d("Polychrome::palette36", n=9+length(unique(data$id)))[-seq(9)]) + 
     scale_fill_manual(values = paletteer_d("Polychrome::palette36", n=9+length(unique(data$id)))[-seq(9)]) + 
     geom_path(data=outline_xy, aes(x=c1, y=c2), size = 0.5) + xlim(xrange)  + ylim(yrange) +
     coord_fixed() + theme_void() + guides(size=FALSE, alpha=FALSE) 

print(focusTypeLoc)

ggsave(paste("synapseLocations_",focustype,'_byID_projection.pdf', sep=''),
                plot = focusTypeLoc, device='pdf', path = "plots", 
                scale = 1, width = 18, height = 8, units ="cm", dpi = 600, useDingbats=FALSE)

```

```{r, warning=FALSE}
minConN = 20

for (partner in c(arrange(inputTypes, desc(n))$partnertype[-1])){
  print(partner)
  
  toplot_2D = data%>%filter(partnerType==partner) %>% select(c('x','y','z', 'partnerid','id', 'type', 'partnerType', 'name', 'partnerName')) %>%
    mutate("nameid" = paste(name, id,sep="_"),"partnerNameid" = paste(partnerName, partnerid,sep="_"))
  minConnections = toplot_2D %>% group_by(id) %>% count() %>% filter(n >= minConN)
  toplot_2D = toplot_2D %>% filter(id %in% minConnections$id)
  
  if(length(toplot_2D$partnerid) == 0  ){
    print("not enough connections")
    next
  }
  xyproj <- ggplot(toplot_2D) + 
    #stat_density_2d(aes(x=y, y=x, fill=partnerName, alpha = stat(nlevel)), bins=3, geom = "polygon") +
    geom_point(aes(x=y, y=x, color=partnerid, shape=partnerName),size=1, alpha=1) + 
    scale_color_manual(values = paletteer_d("Polychrome::palette36", n=9+length(unique(toplot_2D$partnerid)))[-seq(9)]) + 
    geom_point(data = toplot_2D %>% group_by(partnerid) %>% summarize_each(mean), aes(x=y, y=x, fill=partnerid), shape = 21, color='black',size=3,stroke=1) +
    scale_fill_manual(values = paletteer_d("Polychrome::palette36", n=9+length(unique(toplot_2D$partnerid)))[-seq(9)]) + 
    geom_path(data=outline_xy, aes(x=c1, y=c2), size = 0.5) + xlim(xrange)  + ylim(yrange) +
    coord_fixed() + theme_void() + guides(size=FALSE, alpha=FALSE) 
  
  print(xyproj)
  
  ggsave(paste("synapseDistributions_",focustype,'_',partner,'_post_projection.pdf', sep=''),
                plot = xyproj, device='pdf', path = "plots", 
                scale = 1, width = 18, height = 8, units ="cm", dpi = 600, useDingbats=FALSE)
}

```
