---
title: "Analysis of inputs to the noduli (NO): Type comparison plots (partners by region bar graph and similarity analysis)"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of inputs to the NO: Type comparison plots (partners by region bar graph and similarity analysis)
This notebook shows how neuron groups were selected for generating the connectivity graphs. It also will generate a type-to-type connectivity  matrix that shows all connections (i.e. no cutoff weight as used on the graphs).

Generate type comparison plots (partners by region bar graph and similarity analysis, as well as ordered connectivity matrices)
* Figure 26 B (bar graph)
* Figure 26 C (similarity matrix)
* Figure 26 figure supplement 1A (non-normalized bar graph)
* Figure 26 figure supplement 1B,C (Connectivity matrices ordered by similarity)
* Figure 27 A (bar graph)
* Figure 27 figure supplement A (similarity matrices)
* Figure 27 figure supplement B (Connectivity matrices ordered by similarity)

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(plotly)
library(paletteer)
library(igraph)
library(neuprintrExtra)
library(gridExtra)
options(nat.plotengine = 'rgl')

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

```{r}
#util function
myplot_dist <- function(dd,order=TRUE){
  ddM <- as.matrix(dd)
  if (order){
    hcl <- hclust(dd)
    ddM <- ddM[hcl$order,hcl$order]
  }
  ggplot(reshape2::melt(ddM)) + geom_tile(aes(x=Var1,y=Var2,fill=1-value)) +
    theme_classic() +
    scale_fill_gradient2(low="white", mid="grey", high="black", 
                         midpoint =0.5, limits=c(0,1), name="Similarity") +
    theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5)) + 
    xlab("") + ylab("")+coord_fixed() 
}
```

### Select types for comparison
```{r}
myTypeList = c(unique(getBodyIdsForList(paste0( c("PEN"),".*"))$type),unique(getBodyIdsForList(paste0( c("PFN"),".*"))$type))
  #c("ER3a_a","ER3a_b","ER3a_c","ER3a_d","ER1_a","ER1_b")
  #paste0(c("ExR"),seq(1,8))
  #c("PFR_a", "PFR_b", unique(getBodyIdsForList(paste0( c("PFN"),".*"))$type), "vDeltaJ", "vDeltaK", "vDeltaL", "vDeltaM")
  #c("FB6A","FB6C_a","FB6C_b","FB6D","FB6E","FB6F","FB6G","FB6H","FB6I","FB6Z","FB7A","FB7B","FB7K","FB7L","FB5J","FB5H","FB5I","FB5AA", "FB5AB","FB1D","FB1E")
  #c("GLNO","LNO1","LNO2","LNO3","LNOa", "LCNOpm","LCNOp") #
side ="_L" # "_R"#
myTypeList_lat = paste0(myTypeList, side)

saveName = "PFN-PEN_comparison"
saveDir = "plots"
```


```{r}
myTypes_bag_full = neuronBag(myTypeList)

# Filter out neurons from left side?
splitLR = TRUE
if(splitLR){
  myTypes_bag_full = lateralize_types(myTypes_bag_full)
  }
```

### Filter neuron bag to contain only subset of types (considering lateralization)
```{r}
myTypes_bag =  filter(myTypes_bag_full, filterPartners = FALSE, type %in% myTypeList_lat)
```

### Generate list of ROIs to consider
```{r}
roiTree = getRoiTree()
slctROIs = selectRoiSet(roiTree, default_level = 2, 
                        exceptions = list("OL(R)"=1,"AL(R)"=1,"PENP"=1,"AL(L)"=1,"MB(+ACA)(R)"=1,"MB(L)"=1,
                                          "VMNP"=1,"INP"=1, "LX(R)"=3, "LX(L)"=3), exceptionLevelMatch = 1)
slctROIs = unique(slctROIs$roi)
slctROIs_r = slctROIs[!grepl("\\(L\\)",slctROIs)]
slctROIs_r
```

# Use raw inputs as few connections in non-CX ROIs are significant according to general criteria??
```{r}
myTypes_in = myTypes_bag$inputs
myTypes_out = myTypes_bag$outputs
myTypes = myTypes_bag$names
```


### Generate dataframe of inputs to types of interest
# Filter based on rois to use
```{r}
minsyn = 3
minWeightRel = 0.001 #used to filter connectivity tables


myTypes_in_filt = myTypes_in %>% filter(roi %in% slctROIs) %>%
  #filter(type.to %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.to) %>% filter(sum(weight) >= minsyn) %>% filter(weightRelative >= minWeightRel)

myTypes_in_filt = bind_cols(myTypes_in_filt, data.frame(dir = rep("in", length(myTypes_in_filt$roi))))

myTypes_out_filt = myTypes_out %>% filter(roi %in% slctROIs) %>%
  #filter(type.from %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.from) %>% filter(sum(weight) >= minsyn) %>% filter(outputContribution >= minWeightRel)

myTypes_out_filt = bind_cols(myTypes_out_filt, data.frame(dir = rep("out", length(myTypes_out_filt$roi))))
```

```{r}
#myTypes_in_filt %>% group_by(roi,  type.from,  type.to) %>% summarise(sw = sum(weight))
plotData = myTypes_in_filt %>% ungroup() %>% group_by(roi,  type.from, type.to) %>% summarise(sw = sum(weight))
ggplot(data = plotData) + geom_freqpoly( aes(x=sw, color=type.to), bins=100) + xlim(0, 100) + facet_grid(rows = vars(roi))

plotData = myTypes_out_filt %>% ungroup() %>% group_by(roi,  type.to, type.from) %>% summarise(sw = sum(weight))
ggplot(data = plotData) + 
  geom_freqpoly( aes(x=sw, color=type.from), bins=100) + xlim(0, 100) +
  facet_grid(rows = vars(roi))
```

# Visualize in bar graph different input types
```{r}
inOutContributionDataPrep <- function(myTypes_in_filt, myTypes_out_filt,  supertypeLevel){
  inData = myTypes_in_filt %>% select(c("roi","databaseType.from","type.from", "type.to", "weightRelative","weight","absoluteWeight","outputContribution", "dir")) %>% 
    mutate(ref = type.to, measure=weightRelative) %>% rename(databaseType=databaseType.from)
  
  outData = myTypes_out_filt %>% select(c("roi","databaseType.to","type.from", "type.to","weightRelative", "weight","absoluteWeight","outputContribution", "dir")) %>% 
    mutate(ref = type.from, measure=outputContribution) %>% rename(databaseType=databaseType.to)
  
  if(supertypeLevel == 0){
    inData <- supertype(inData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
    
    outData <- supertype(outData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
  }else{
    inData = supertype(inData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
    outData = supertype(outData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
  }
  data = bind_rows(inData,outData)
  return(data)
}


for(st in c(0,2,3)){
  myTypes_filt = inOutContributionDataPrep(myTypes_in_filt, myTypes_out_filt,  st) %>% filter(roi %in% slctROIs_r)
  
  if(sum(is.na(myTypes_filt$partner)) > 0){
    myTypes_filt = myTypes_filt  %>% mutate(partner = coalesce(partner, "Other"))
  }
  bar = inOutContributionPlot(myTypes_filt)+ facet_grid(cols=vars(roi), rows=vars(dir), scales="free_x", space = "free") 
  show(bar)
  if (savePlot & st == 2){
    ggsave(paste("inputAndOutputComposition_",saveName,"_supertype",st,'.pdf', sep=''),plot = bar, device='pdf', path = "plots",
        scale = 1.5, width=23, height=10, units ="cm", dpi = 600, limitsize = TRUE)
  }
}

```

```{r, warning=FALSE}

inOutContributionPlotNotNorm <- function(data){
  ncol = length(unique(data$partner))
  data = data %>% ungroup() %>% group_by(partner, roi, dir, ref) %>% summarise(measure = sum(absoluteWeight))
  bar = ggplot(data, aes(x=ref, y=measure, fill=partner)) + 
    geom_bar(position = "stack",stat="identity") + 
    theme_classic() + theme_paper() + theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))
  
  if(ncol <= 31){
    bar = bar + scale_fill_manual(values=paletteer_d("Polychrome::palette36", n=5+length(unique(data$partner)))[c(-seq(5))])
  }else if(ncol <= 36){
    bar = bar + scale_fill_manual(values=paletteer_d("Polychrome::palette36", n=length(unique(data$partner))))
  }
  return(bar)
}

for(st in c(0,2,3)){
  myTypes_filt = inOutContributionDataPrep(myTypes_in_filt, myTypes_out_filt,  st) %>% filter(roi %in% slctROIs_r)
  
  if(sum(is.na(myTypes_filt$partner)) > 0){
    myTypes_filt = myTypes_filt  %>% mutate(partner = coalesce(partner, "Other"))
  }
  bar = inOutContributionPlotNotNorm(myTypes_filt)+ facet_grid(cols=vars(roi), rows=vars(dir), scales="free_x", space = "free")
  show(bar)
  
  if (savePlot & st == 2){
    ggsave(paste("inputAndOutputComposition_",saveName,"_supertype",st,'_nonNorm.pdf', sep=''),plot = bar, device='pdf', path = "plots",
        scale = 1.5, width=23, height=10, units ="cm", dpi = 600, limitsize = TRUE)
  }
}

```

### Compare input and outputs to these types
# select inputs to focus types in main input regions

***Figure 26 C***
For Figure 26 C top, select myROIs ="NO" and myROIsName = "NO", for Figure 26 C bottom, select myROIs ="PB" and myROIsName = "PB".

```{r}
myROIs = "NO" # unique(myTypes_filt$roi)[unique(myTypes_filt$roi)!="EB"]
myROIsName = "NO" #paste(myROIs, collapse = '-')#"allButEB" #"allROIbutNO" # #"PB_EB_NOr" #
myROIs  

```

# construct new connection table for combined ROIs
```{r}
myTypes_bag_comboRoi = combineRois(myTypes_bag, myROIs, "comboRoi")
typesInput_combiRoi = myTypes_bag_comboRoi$inputs %>% filter(type.to %in% myTypeList_lat)
typesOutput_combiRoi = myTypes_bag_comboRoi$outputs %>% filter(type.from %in% myTypeList_lat)

myTypeList_lat_in = unique(typesInput_combiRoi$type.to)
myTypeList_lat_out = unique(typesOutput_combiRoi$type.from)
```

# Connectivity matrix from neuron bag
```{r}
weightMeasure ="weightRelative" 
groupBy = "type"
cmax = max(typesInput_combiRoi$weightRelative)

conMatPlot = plotConnectivityMatrix(typesInput_combiRoi, byGroup = groupBy, weightMeasure , cmax)
conMatPlot = addMatrixPlotLabs(conMatPlot, "Inputs",  "",paste(myROIs, collapse = '-'), weightMeasure)

print(conMatPlot)

cmax = max(typesOutput_combiRoi$weightRelative)

conMatPlot = plotConnectivityMatrix(typesOutput_combiRoi, byGroup = groupBy, weightMeasure , cmax)
conMatPlot = addMatrixPlotLabs(conMatPlot, "Outputs",  "",paste(myROIs, collapse = '-'), weightMeasure)

print(conMatPlot)
```


```{r}
inTypesContribution <- myInputTypes_bag_comboRoi$outputs %>% filter(type.to %in% myTypeList_lat)

inTypesCon <- left_join(inTypesContribution, inTypeClusters, by=c("type.from"="type")) %>% 
  mutate(fromCluster = paste(inclust,type.from, sep="_"))
inTypesCon <- left_join(inTypesCon, typeClusters, by=c("type.to"="type")) %>% 
  mutate(toCluster = paste(clust,type.to, sep="_"))

cmax = max(inTypesCon$weightRelative)

plt <- ggplot(data = inTypesCon) + geom_tile(aes(x=type.to,y=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(inclust, desc(inclust)) ~ clust, space="free", scales="free",switch="both")
print(plt)

if (savePlot){
  ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster.pdf', sep=''), plot = plt, device='pdf',
         path = "plots",width = 15, height= 30, units ="cm", dpi = 600, limitsize = TRUE)
}

plt <- ggplot(data = inTypesCon) + geom_tile(aes(y=type.to,x=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(clust, desc(clust)) ~ inclust, space="free", scales="free",switch="both")
print(plt)

if (savePlot){
  #ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_v2.pdf', sep=''), plot = plt, device='pdf', path = "plots",width = 30, height =10, units ="cm", dpi = 600, limitsize = TRUE)
}
```


# Cluster input vectors to reference neurons
Generate the similarity matrices shown in ***Figure 26 C*** (PFN, PEN in NO and PB).

```{r}
conmat <- connectivityMatrix( typesInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8) + theme_paper()# + rect.hclust(hcl, h=cut, border = "red")

dev.print(pdf, paste0("plots/inputCorrelation_",saveName,'_', myROIsName,'_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typeClusters <- stack(clu.h) %>% rename(type = ind, clust=values) %>% arrange(clust)

if (savePlot){
  ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)
}
```

```{r}
conmat <- connectivityMatrix( typesInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")
conmat_cd = cos_dist(t(conmat))
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")
#dev.print(pdf, paste0("plots/inputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag_tree.pdf'), width=12, height=6)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typePreClusters <- stack(clu.h) %>% rename(type = ind, preclust=values) %>% arrange(preclust)

if (savePlot){
  #ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots", scale = 1, width = 16, height = 16, units ="cm", dpi = 600, limitsize = TRUE)
}
```
# Cluster output vectors to reference neurons
```{r}
conmat <- connectivityMatrix( typesOutput_combiRoi %>% filter(is.finite(weightRelative) ), "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")

#dev.print(pdf, paste0("plots/outputCorrelation_",saveName,'_', myROIsName,'_nBag_tree.pdf'), width=12, height=6)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typeClusters <- stack(clu.h) %>% rename(type = ind, clust=values) %>% arrange(clust)

if (savePlot){
  #ggsave( paste("outputCorrelation_",saveName,'_', myROIsName,'_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots", scale = 1, width = 16, height = 16, units ="cm", dpi = 600, limitsize = TRUE)
}
```

```{r}
conmat <- connectivityMatrix( typesOutput_combiRoi %>% filter(is.finite(weightRelative) ), "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")
conmat_cd = cos_dist(t(conmat))
plt <- myplot_dist(conmat_cd, order=TRUE)
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")
#dev.print(pdf, paste0("plots/outputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typePreClusters <- stack(clu.h) %>% rename(type = ind, preclust=values) %>% arrange(preclust)

if (savePlot){
  #ggsave( paste("outputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)
}
```


# For LNO/PFN
## Investigate inptuts outside of NO
```{r}
inputDatabaseTypes = unique(typesInput_combiRoi$databaseType.from)
NAtypes = typesInput_combiRoi %>% filter(is.na(databaseType.from)) %>% select(type.from)
inputTypes = unique(typesInput_combiRoi$type.from)

myInputTypes_bag = neuronBag(inputDatabaseTypes)

# Filter out neurons from left side
splitLR = TRUE
if(splitLR){
  myInputTypes_bag = lateralize_types(myInputTypes_bag)
}
```

```{r}
# Find which rois inputs are innervating
myROIs_in = unique(myInputTypes_bag$inputs$roi) 
myROIs_in = intersect(myROIs_in,slctROIs)
myROIs_in
```

```{r}
myInputTypes_bag_comboRoi = combineRois(myInputTypes_bag, myROIs_in, "comboRoi")
inInput_combiRoi = myInputTypes_bag_comboRoi$inputs %>% filter(type.to %in% inputTypes)
```

```{r}
conmat <- connectivityMatrix(inInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE)
plt

hcl=hclust(conmat_cd)
cut2 = 0.9# 0.995 used for LNO inputs, 0.8 used otherwise
plot(hcl,hang= -1, cex = 0.6)#,labels = TRUE, )
rect.hclust(hcl, h=cut2, border = "red")
dev.print(pdf, paste0("plots/inputCorrelation_",saveName,'_', myROIsName,'_inputs_nBag_tree.pdf'), width=8, height=4)

clu.h2=cutree(hcl,h=cut2) # cut tree/dendrogram from height 80

inTypeClusters <- stack(clu.h2) %>% rename(type = ind, inclust=values) %>% arrange(inclust)

if (savePlot){
  ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_inputs_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots", scale = 1, width = 22, height = 22, units ="cm", dpi = 600, limitsize = TRUE)
}
```

```{r}
inTypesContribution <- myInputTypes_bag_comboRoi$outputs %>% filter(type.to %in% myTypeList_lat)

inTypesCon <- left_join(inTypesContribution, inTypeClusters, by=c("type.from"="type")) %>% 
  mutate(fromCluster = paste(inclust,type.from, sep="_"))
inTypesCon <- left_join(inTypesCon, typeClusters, by=c("type.to"="type")) %>% 
  mutate(toCluster = paste(clust,type.to, sep="_"))

cmax = max(inTypesCon$weightRelative)

plt <- ggplot(data = inTypesCon) + geom_tile(aes(x=type.to,y=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(inclust, desc(inclust)) ~ clust, space="free", scales="free",switch="both")
print(plt)

if (savePlot){
  ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster.pdf', sep=''), plot = plt, device='pdf',
         path = "plots",width = 15, height= 30, units ="cm", dpi = 600, limitsize = TRUE)
}

plt <- ggplot(data = inTypesCon) + geom_tile(aes(y=type.to,x=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(clust, desc(clust)) ~ inclust, space="free", scales="free",switch="both")
print(plt)

if (savePlot){
  ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_v2.pdf', sep=''), plot = plt, device='pdf',
         path = "plots",width = 30, height =10, units ="cm", dpi = 600, limitsize = TRUE)
}
```

```{r}
inTypesContribution <- typesInput_combiRoi

inTypesConPre <- left_join(inTypesContribution, typePreClusters, by=c("type.from"="type")) %>% 
  mutate(fromCluster = paste(preclust,type.from, sep="_"))
inTypesConPre <- left_join(inTypesConPre, typeClusters, by=c("type.to"="type")) %>% 
  mutate(toCluster = paste(clust,type.to, sep="_"))

cmax = max(inTypesConPre$weightRelative)

plt <- ggplot(data = inTypesConPre) + geom_tile(aes(x=type.to,y=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")#+coord_fixed()
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(preclust, desc(preclust)) ~ clust, space="free", scales="free",switch="both")
print(plt)

if (savePlot){
  ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_pre_alltypes.pdf', sep=''), plot = plt, device='pdf',
         path = "plots",width = 15, height= 30,  units ="cm", dpi = 600, limitsize = TRUE)
}
```
