---
title: "Analysis of inputs to the noduli (NO): Type comparison plots (partners by region bar graph and similarity analysis)"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of inputs to the NO: Type comparison plots (partners by region bar graph and similarity analysis)
This notebook shows how neuron groups were selected for generating the connectivity graphs. It also will generate a type-to-type connectivity  matrix that shows all connections (i.e. no cutoff weight as used on the graphs).

* Figure 26 B (bar graph)
* Figure 26 C (similarity matrix)
* Figure 26 figure supplement 1A (non-normalized bar graph)
* Figure 26 figure supplement 1B,C (Connectivity matrices ordered by similarity)
* Figure 27 A (bar graph)
* Figure 27 C (clustering of LNO neurons)
* Figure 27 figure supplement 1A (similarity matrices)
* Figure 27 figure supplement 1B (Connectivity matrices ordered by similarity)

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(plotly)
library(paletteer)
library(igraph)
library(neuprintrExtra)
library(gridExtra)
options(nat.plotengine = 'rgl')

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

```{r}
#util function
myplot_dist <- function(dd,order=TRUE){
  ddM <- as.matrix(dd)
  if (order){
    hcl <- hclust(dd)
    ddM <- ddM[hcl$order,hcl$order]
  }
  ggplot(reshape2::melt(ddM)) + geom_tile(aes(x=Var1,y=Var2,fill=1-value)) +
    theme_classic() +
    scale_fill_gradient2(low="white", mid="grey", high="black", 
                         midpoint =0.5, limits=c(0,1), name="Similarity") +
    theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5)) + 
    xlab("") + ylab("")+coord_fixed() 
}
```

### Select types for comparison
For **Figure 26 B**, **Figure 26 C**, **Figure 26 figure supplement 1A** and **Figure 26 figure supplement 1B,C** choose: 
selection = "PFN-PEN"

For **Figure 27A**, **Figure 27 figure supplement 1A** and **Figure 26 figure supplement 1B,C** choose: 
selection = "LNO"
* Figure 27 figure supplement 1A (similarity matrices)
* Figure 27 figure supplement 1B (Connectivity matrices ordered by similarity)

```{r}
selection = "PFN-PEN" #"LNO" #

if (selection == "PFN-PEN"){
  myTypeList = c(unique(getBodyIdsForList(paste0( c("PEN"),".*"))$type),unique(getBodyIdsForList(paste0( c("PFN"),".*"))$type))
  side ="_L"
}else if(selection == "LNO"){
  myTypeList = c(unique(getBodyIdsForList(paste0( c("LNO","LCNO", "GLNO"),".*"))$type))
  side ="_R"
}

myTypeList_lat = paste0(myTypeList, side)
saveName = paste0(selection,"_comparison")
saveDir = "plots"
```

### Construct and filter neuron bag to contain only subset of types (considering lateralization)
```{r}
myTypes_bag_full = neuronBag(myTypeList)
myTypes_bag_full = lateralize_types(myTypes_bag_full)

myTypes_bag =  filter(myTypes_bag_full, filterPartners = FALSE, type %in% myTypeList_lat)
```

### Generate list of ROIs to consider
```{r}
roiTree = getRoiTree()
slctROIs = selectRoiSet(roiTree, default_level = 2, 
                        exceptions = list("OL(R)"=1,"AL(R)"=1,"PENP"=1,"AL(L)"=1,"MB(+ACA)(R)"=1,"MB(L)"=1,
                                          "VMNP"=1,"INP"=1, "LX(R)"=3, "LX(L)"=3), exceptionLevelMatch = 1)
slctROIs = unique(slctROIs$roi)
slctROIs_r = slctROIs[!grepl("\\(L\\)",slctROIs)]
slctROIs_r
```

# Use raw inputs as few connections in non-CX ROIs are significant according to general criteria??
```{r}
myTypes_in = myTypes_bag$inputs
myTypes_out = myTypes_bag$outputs
myTypes = myTypes_bag$names
```


### Generate dataframe of inputs to types of interest
# Filter based on rois to use
```{r}
minsyn = 3
minWeightRel = 0.001 #used to filter connectivity tables


myTypes_in_filt = myTypes_in %>% filter(roi %in% slctROIs) %>%
  #filter(type.to %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.to) %>% filter(sum(weight) >= minsyn) %>% filter(weightRelative >= minWeightRel)

myTypes_in_filt = bind_cols(myTypes_in_filt, data.frame(dir = rep("in", length(myTypes_in_filt$roi))))

myTypes_out_filt = myTypes_out %>% filter(roi %in% slctROIs) %>%
  #filter(type.from %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.from) %>% filter(sum(weight) >= minsyn) %>% filter(outputContribution >= minWeightRel)

myTypes_out_filt = bind_cols(myTypes_out_filt, data.frame(dir = rep("out", length(myTypes_out_filt$roi))))
```

# Visualize in bar graph different input types
```{r}
inOutContributionDataPrep <- function(myTypes_in_filt, myTypes_out_filt,  supertypeLevel){
  inData = myTypes_in_filt %>% select(c("roi","databaseType.from","type.from", "type.to", "weightRelative","weight","absoluteWeight","outputContribution", "dir")) %>% 
    mutate(ref = type.to, measure=weightRelative) %>% rename(databaseType=databaseType.from)
  
  outData = myTypes_out_filt %>% select(c("roi","databaseType.to","type.from", "type.to","weightRelative", "weight","absoluteWeight","outputContribution", "dir")) %>% 
    mutate(ref = type.from, measure=outputContribution) %>% rename(databaseType=databaseType.to)
  
  if(supertypeLevel == 0){
    inData <- supertype(inData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
    
    outData <- supertype(outData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
  }else{
    inData = supertype(inData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
    outData = supertype(outData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
  }
  data = bind_rows(inData,outData)
  return(data)
}

for(st in c(0,2,3)){
  myTypes_filt = inOutContributionDataPrep(myTypes_in_filt, myTypes_out_filt,  st) %>% filter(roi %in% slctROIs_r)
  
  if(sum(is.na(myTypes_filt$partner)) > 0){
    myTypes_filt = myTypes_filt  %>% mutate(partner = coalesce(partner, "Other"))
  }
  bar = inOutContributionPlot(myTypes_filt)+ facet_grid(cols=vars(roi), rows=vars(dir), scales="free_x", space = "free") 
  show(bar)
  if (savePlot & st == 2){
    ggsave(paste("inputAndOutputComposition_",saveName,"_supertype",st,'.pdf', sep=''),plot = bar, device='pdf', path = "plots",
        scale = 1.5, width=23, height=10, units ="cm", dpi = 600, limitsize = TRUE)
  }
}

```

```{r, warning=FALSE}
inOutContributionPlotNotNorm <- function(data){
  ncol = length(unique(data$partner))
  data = data %>% ungroup() %>% group_by(partner, roi, dir, ref) %>% summarise(measure = sum(absoluteWeight))
  bar = ggplot(data, aes(x=ref, y=measure, fill=partner)) + 
    geom_bar(position = "stack",stat="identity") + 
    theme_classic() + theme_paper() + theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))
  
  if(ncol <= 31){
    bar = bar + scale_fill_manual(values=paletteer_d("Polychrome::palette36", n=5+length(unique(data$partner)))[c(-seq(5))])
  }else if(ncol <= 36){
    bar = bar + scale_fill_manual(values=paletteer_d("Polychrome::palette36", n=length(unique(data$partner))))
  }
  return(bar)
}

for(st in c(0,2,3)){
  myTypes_filt = inOutContributionDataPrep(myTypes_in_filt, myTypes_out_filt,  st) %>% filter(roi %in% slctROIs_r)
  
  if(sum(is.na(myTypes_filt$partner)) > 0){
    myTypes_filt = myTypes_filt  %>% mutate(partner = coalesce(partner, "Other"))
  }
  bar = inOutContributionPlotNotNorm(myTypes_filt)+ facet_grid(cols=vars(roi), rows=vars(dir), scales="free_x", space = "free")
  show(bar)
  
  if (savePlot & st == 2 & selection == "PFN-PEN"){
    ggsave(paste("inputAndOutputComposition_",saveName,"_supertype",st,'_nonNorm.pdf', sep=''),plot = bar, device='pdf', path = "plots",
        scale = 1.5, width=23, height=10, units ="cm", dpi = 600, limitsize = TRUE)
  }
}

```

### Compare input and outputs to these types
# select inputs to focus types in main input regions
**Figure 26 C** (adjust for top vs bottom panel) and **Figure 27C**. 
```{r}
if (selection == "PFN-PEN"){
  myROIs ="NO(R)"  # select "PB" for bottom panel
  myROIsName = "NOr" # select "PB" for bottom panel
}else if(selection == "LNO"){
  myROIs = unique(myTypes_filt$roi)[unique(myTypes_filt$roi)!="NO"]
  myROIsName = "allButNO"
}
cutTH = 0.8
myROIs
```

# construct new connection table for combined ROIs
```{r}
myTypes_bag_comboRoi = combineRois(myTypes_bag, myROIs, "comboRoi")
typesInput_combiRoi = myTypes_bag_comboRoi$inputs %>% filter(type.to %in% myTypeList_lat)
myTypeList_lat_in = unique(typesInput_combiRoi$type.to)
```

# Connectivity matrix from neuron bag (inputs)
```{r}
weightMeasure ="weightRelative" 
groupBy = "type"
cmax = max(typesInput_combiRoi$weightRelative)

conMatPlot = plotConnectivityMatrix(typesInput_combiRoi, byGroup = groupBy, weightMeasure , cmax)
conMatPlot = addMatrixPlotLabs(conMatPlot, "Inputs",  "",paste(myROIs, collapse = '-'), weightMeasure)

print(conMatPlot)
```

# Cluster input vectors to reference neurons
Generate the similarity matrices shown in **Figure 26 C** (PFN, PEN in NO and PB) and **Figure 27 figure supplement 1 Ai** (LNO in outside of NO), as well as the dendrogram in **Figure 27 C**.
```{r}
conmat <- connectivityMatrix( typesInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8) + theme_paper() #+ rect.hclust(hcl, h=cut, border = "red")

dev.print(pdf, paste0("plots/inputCorrelation_",saveName,'_', myROIsName,'_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cutTH) # cut tree/dendrogram from height 80

typeClusters <- stack(clu.h) %>% rename(type = ind, clust=values) %>% arrange(clust)

if (savePlot){
  ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)
}
```


```{r}
conmat <- connectivityMatrix( typesInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")
conmat_cd = cos_dist(t(conmat))
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)

cut = cutTH
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")
#dev.print(pdf, paste0("plots/inputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag_tree.pdf'), width=12, height=6)
clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80
typePreClusters <- stack(clu.h) %>% rename(type = ind, preclust=values) %>% arrange(preclust)

#if (savePlot){ ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots", scale = 1, width = 16, height = 16, units ="cm", dpi = 600, limitsize = TRUE) }
```

Reordered connectivity matrices as shown in **Figure 26 figure supplement 1B,C** and **Figure 27 figure supplement 1B**
```{r}
inTypesContribution <- typesInput_combiRoi

if (selection == "PFN-PEN"){
  pw = 15
  ph = 22
}else if(selection == "LNO"){
  pw = 11
  ph = 35
}

inTypesConPre <- left_join(inTypesContribution, typePreClusters, by=c("type.from"="type")) %>% 
  mutate(fromCluster = paste(preclust,type.from, sep="_"))
inTypesConPre <- left_join(inTypesConPre, typeClusters, by=c("type.to"="type")) %>% 
  mutate(toCluster = paste(clust,type.to, sep="_"))

cmax = max(inTypesConPre$weightRelative)

plt <- ggplot(data = inTypesConPre) + geom_tile(aes(x=type.to,y=type.from,fill=weightRelative)) +
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*cmax, limits=c(0,cmax))   +
    xlab("") + ylab("")
plt <- plt + theme(strip.placement = "outside", 
                   strip.background = element_rect(fill=NA, colour="grey50")) +
    facet_grid(reorder(preclust, desc(preclust)) ~ clust, space="free", scales="free",switch="both")
print(plt)

ggsave(paste("connectivityMatrix_",saveName,'_', myROIsName,'_byCluster_pre.pdf', sep=''), plot = plt, device='pdf',
       path = "plots",width=pw+2, height=ph,  units ="cm", dpi = 600, limitsize = TRUE)

```

# Cluster output vectors to reference neurons
This will generate **Figure 27 figure supplement 1 Aii**. (Choose selection = "LNO" at the beginning of the notebook.)
```{r}
myROIs = "NO"
myROIsName = "onlyNO"
cutTH = 0.8
```

# construct new connection table for combined ROIs
```{r}
myTypes_bag_comboRoi = combineRois(myTypes_bag, myROIs, "comboRoi")
typesOutput_combiRoi = myTypes_bag_comboRoi$outputs %>% filter(type.from %in% myTypeList_lat)
myTypeList_lat_out = unique(typesOutput_combiRoi$type.from)
```

```{r}
conmat <- connectivityMatrix( typesOutput_combiRoi %>% filter(is.finite(weightRelative) ), "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt

hcl=hclust(conmat_cd)
cut = cutTH
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")
clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80
typeClusters <- stack(clu.h) %>% rename(type = ind, clust=values) %>% arrange(clust)

```

```{r}
conmat <- connectivityMatrix( typesOutput_combiRoi %>% filter(is.finite(weightRelative) ), "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")
conmat_cd = cos_dist(t(conmat))
plt <- myplot_dist(conmat_cd, order=TRUE)
plt

hcl=hclust(conmat_cd)

cut = cutTH
tplt <- plot(hcl,hang= -.5,cex = 0.8)
dev.print(pdf, paste0("plots/outputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag_tree.pdf'), width=6, height=4)

clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typePreClusters <- stack(clu.h) %>% rename(type = ind, preclust=values) %>% arrange(preclust)

ggsave( paste("outputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag.pdf', sep=''), plot = plt, device='pdf', path = "plots/", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)

```