---
title: "EPGs vs EPGts"
output: html_notebook
---

Load the functions
```{r}
library(neuprintr)
library(tidyverse)
library(cowplot)
library(neuprintrExtra)
library(reshape2)
library(patchwork)
library(ggnewscale)
library(gridExtra)
source(file.path("..","PBFigures","PBAnalysisUtils.R"))
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))
```


Compare the EPG and EPGt connections in the PB - inputs
```{r}
EPGt_CT_PB_PRE <- getConnectionTable(getTypesTable(c("EPG","EPGt"))$bodyid,"PRE","PB")
EPGt_CT_PB_PRE <- EPGt_CT_PB_PRE %>% filter(!is.na(type.to) & !is.na(type.from)) %>%
  filter(type.to !="SIFa" & type.from !="SIFa")

EPGt_T2T_PB_PRE <- getTypeToTypeTable(EPGt_CT_PB_PRE)

T2TPlot_EPGt_PB_PRE <- plotConnectivityMatrix(EPGt_T2T_PB_PRE, byGroup = "type") + 
  coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  guides(fill = guide_colourbar(title = 'relative weight', title.position = 'left', title.theme = element_text(angle = 90), barwidth = 0.5, title.hjust = 0.5))

print(T2TPlot_EPGt_PB_PRE)
```
Compare the EPG and EPGt connections in the PB - outputs
```{r}
EPGt_CT_PB_POST <- getConnectionTable(getTypesTable(c("EPG","EPGt"))$bodyid,"POST","PB")
EPGt_CT_PB_POST <- EPGt_CT_PB_POST %>% filter(!is.na(type.to) & !is.na(type.from)) %>%
  filter(type.to !="SIFa" & type.from !="SIFa")

EPGt_T2T_PB_POST <- getTypeToTypeTable(EPGt_CT_PB_POST,
                                  pThresh=0.1)

T2TPlot_EPGt_PB_POST <- plotConnectivityMatrix(EPGt_T2T_PB_POST, byGroup = "type", connectionMeasure="outputContribution") + 
    coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
    guides(fill = guide_colourbar(title = 'output contribution', direction = 'horizontal', title.position = 'top', barheight = 0.5))

print(T2TPlot_EPGt_PB_POST)
```


Get the total number of input and output synapses by roi
```{r}
EPG_ROIs <- neuprint_get_roiInfo(getTypesTable(c("EPG","EPGt"))$bodyid)
```

Plot the relative number of output synapses
```{r}
EPG_outputROIs <- EPG_ROIs %>% select(bodyid,PB.downstream,EB.downstream,`LAL(R).downstream`)
EPG_outputROIs[is.na(EPG_outputROIs)] <- 0
colnames(EPG_outputROIs) <- c("bodyid","PB","EB","LAL")
EPG_outputROIs <- melt(EPG_outputROIs,id.vars='bodyid',value.name='syns',variable.name = 'ROI')
EPG_outputROIs <- EPG_outputROIs %>% mutate(type = neuprint_get_meta(bodyid)$type,
                                          name = neuprint_get_meta(bodyid)$name)
EPG_outputROIs$nameid <- PBRename(EPG_outputROIs$name,EPG_outputROIs$bodyid)
EPG_outputROIs$ROI <- factor(EPG_outputROIs$ROI,levels = c("EB","PB","LAL"))

relEPGOutputs <- ggplot(EPG_outputROIs,aes(color=as.factor(type),y=syns,x=ROI)) +
  geom_point(position=position_jitterdodge(dodge.width=0.4),alpha=0.5,size=3) +
  theme_cowplot() + scale_y_continuous(expand = c(0, 0)) + 
  ylab("presynapses") +
  scale_color_manual(values = supertype2Palette()$pal,
                     breaks = supertype2Palette()$breaks) +
  coord_cartesian(clip = 'off')

relEPGOutputs
```


Compare the EPG and EPGt connections in the EB - inputs
```{r}
EPGt_CT_EB_PRE <- getConnectionTable(getTypesTable(c("EPG","EPGt"))$bodyid,"PRE","EB")
EPGt_CT_EB_PRE <- EPGt_CT_EB_PRE %>% filter(!is.na(type.to) & !is.na(type.from))

EPGt_T2T_EB_PRE <- getTypeToTypeTable(EPGt_CT_EB_PRE)

T2TPlot_EPGt_EB_PRE <- plotConnectivityMatrix(EPGt_T2T_EB_PRE, byGroup = "type") + 
    coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
    guides(fill = guide_colourbar(title = 'relative weight', title.position = 'left', title.theme = element_text(angle = 90), barwidth = 0.5, title.hjust = 0.5))

print(T2TPlot_EPGt_EB_PRE)
```


Create weight matrices that compare the PEN1 and PEN2 connectivity in the EB
```{r}
EPGt_CT_EB_PRE <- getConnectionTable(getTypesTable(c("EPG","EPGt"))$bodyid,"PRE","EB",synThresh= 0)
EPGt_CT_EB_PRE <- EPGt_CT_EB_PRE %>% filter(type.from %in% c('PEN_a(PEN1)','PEN_b(PEN2)'))
EPGt_CT_EB_PRE$nameOrder.from <- PBRename(EPGt_CT_EB_PRE$name.from, EPGt_CT_EB_PRE$from)
EPGt_CT_EB_PRE$nameOrder.to <- PBRename(EPGt_CT_EB_PRE$name.to, EPGt_CT_EB_PRE$to)

pltLevels <- levels(EPGt_CT_EB_PRE$nameOrder.to)
pltLevels <- c(pltLevels[47:48],pltLevels[1:46],pltLevels[49:50])
EPGt_CT_EB_PRE$nameOrder.to <- factor(EPGt_CT_EB_PRE$nameOrder.to,levels=pltLevels)

conmatPlot_EPGt_EB_PRE <- plotConnectivityMatrix(EPGt_CT_EB_PRE, byGroup = "id_sort") + 
  coord_equal(ratio=1) + xlab("postsynaptic neuron") + ylab("presynaptic neuron") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  guides(fill = guide_colourbar(title = 'relative weight', direction = 'horizontal', title.position = 'top', barheight = 0.5)) +
  geom_vline(xintercept = 2.5) + geom_vline(xintercept = 48.5) + geom_vline(xintercept = 50.5) +
  geom_hline(yintercept = 20.5) + geom_hline(yintercept = 42.5) +
  ggtitle("EB")

print(conmatPlot_EPGt_EB_PRE)
```

Create weight matrices that compare the PEN1 and PEN2 connectivity in the PB
```{r}
EPGt_CT_PB_POST <- getConnectionTable(getTypesTable(c("EPG","EPGt"))$bodyid,"POST","PB",synThresh= 0)
EPGt_CT_PB_POST <- EPGt_CT_PB_POST %>% filter(!is.na(type.to) & !is.na(type.from))
EPGt_CT_PB_POST <- EPGt_CT_PB_POST %>% filter(type.to %in% c('PEN_a(PEN1)','PEN_b(PEN2)'))
EPGt_CT_PB_POST$nameOrder.from <- PBRename(EPGt_CT_PB_POST$name.from, EPGt_CT_PB_POST$from)
EPGt_CT_PB_POST$nameOrder.to <- PBRename(EPGt_CT_PB_POST$name.to, EPGt_CT_PB_POST$to)


pltLevels <- levels(EPGt_CT_PB_POST$nameOrder.from)
pltLevels <- c(pltLevels[47:48],pltLevels[1:46],pltLevels[49:50])
EPGt_CT_PB_POST$nameOrder.from <- factor(EPGt_CT_PB_POST$nameOsrder.from,levels=pltLevels)

conmatPlot_EPGt_PB_POST <- plotConnectivityMatrix(EPGt_CT_PB_POST, byGroup = "id_sort") + 
  coord_equal(ratio=1) + xlab("postsynaptic neuron") + ylab("presynaptic neuron") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
  guides(fill = guide_colourbar(title = 'relative weight', direction = 'horizontal', title.position = 'top', barheight = 0.5)) +
  geom_hline(yintercept = 2.5) + geom_hline(yintercept = 48.5) + geom_hline(yintercept = 50.5) +
  geom_vline(xintercept = 20.5) + geom_vline(xintercept = 42.5) +
  ggtitle("PB")

print(conmatPlot_EPGt_PB_POST)
```   