---
title: "Analysis of connectivity inside the ellipsoid body (EB): connectivity graphs and matrices"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of connectivity inside the ellipsoid body (EB): Connectivity graphs and corresponding connectivity matrices
This notebook shows how to generate the connectivity graph in **Figure 10 F** as well as the connectivity matrix in **Figure 26 D**. It also will generate a type-to-type connectivity  matrix that shows all connections (i.e. no cutoff weight as used on the graph).

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(igraph)

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```


### Make selection of neurons to be used in connecitivy analysis
***Selection of ROI and criteria for neuron selection***

For the connectivity graph in **Figure 25B** select:
PFN_PEN_matrix = FALSE

For the connectivity matrix in **Figure 26D** select:
PFN_PEN_matrix = TRUE

```{r}
ROI = "NOr"
slctROI ="NO(R)"

splitLR = TRUE # Whether or not to split neurons within a type into a left and right group.
makeAsymmetric = TRUE # Whether to enforce showing only pregroup -> postgroup connections as opposed to all connections within {pregroup,postgroup}

saveName = paste0("Inputs_in_", ROI)
if(splitLR){saveName = paste0(saveName,"_LR")}

PFN_PEN_matrix = TRUE

if(!PFN_PEN_matrix){
  if(splitLR){
    roiTable = getTypesInRoiTable(slctROI,lateralize = TRUE, minTypePercentage = 0.5)
  }else{
    roiTable = getTypesInRoiTable(slctROI,lateralize = FALSE, minTypePercentage = 0.5)
  }
}
```


***Selection of neurons***
```{r}
# POST
if(PFN_PEN_matrix){
  postNeuron = c("PEN","PFN")
  postNeuron = paste0(postNeuron,".*")
  postName = "PEN, PFN"  #gets used in the connectivity matrix plot
  postIDs = getBodyIdsForList(postNeuron)
}else{
  postName = paste0("all in ", ROI)
  postIDs = roiTable$names
}

# PRE
if(PFN_PEN_matrix){
  preNeuron = postNeuron
  preName = postName
  preIDs = getBodyIdsForList(preNeuron)
}else{
    preName = paste0("all ", ROI)
    preIDs = roiTable$names
}

```


### Get connectivity table
```{r, warning=FALSE}
preTypes = c(preIDs$bodyid, postIDs$bodyid) # preIDs$bodyid
postTypes = preTypes#postIDs$bodyid
myConnections = getConnectionTable(preTypes, "POST", slctROI)
myConnections = myConnections %>% filter(to %in% postTypes) 
```


### Format the connectivity matrix, convert to type-to-type
```{r}
# Make asymmetric matrix
if (makeAsymmetric){
  myConnections = myConnections %>% filter(to %in% postIDs$bodyid)  %>% filter(from %in% preIDs$bodyid)
}

# Make type-to-type connectivity table
typesTable <- getTypesTable(unique(myConnections$databaseType.to))

if (splitLR){
  # Subdivide types and build a custom types table
  myConnections = lateralize_types(myConnections, postfix="to")
  myConnections = lateralize_types(myConnections, postfix="from")
  typesTable = lateralize_types(typesTable, postfix="raw")
}

myConnectionsT2T = getTypeToTypeTable(myConnections,typesTable = typesTable)
```

### Connectivity matrix
```{r}
cmax = NULL
cmaxtype = NULL
 
connectionMeasure = "weightRelative"
if(!PFN_PEN_matrix){ 
  conMatPlot = plotConnectivityMatrix(myConnectionsT2T, byGroup = "type", connectionMeasure, cmaxtype)
  conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
}else{
  conMatPlot = plotConnectivityMatrix(myConnections, byGroup = "id", connectionMeasure, cmax)
  conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  conMatPlot = structureMatrixPlotByType_lines(conMatPlot)
}
print(conMatPlot)

if (savePlot){
  ggsave(paste("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_byID.pdf', sep=''), 
      plot = conMatPlot, device='pdf', path = "plots", scale=1, width=21, height=18, units ="cm", dpi = 600, limitsize = TRUE)
}
```

###  Draw graph
```{r, warning=FALSE} 
require(igraph)

connectionMeasure = "weightRelative"
cutoff = 0.05 # for weight 0.05, 0.01, 0

largeGraph = TRUE
edcurve = 0.1
edgeNorm = 0.5
arrowSize = 0.4 # set to 0 if you prefer styling arrows in e.g. adobe illustrator

showself = TRUE 
selfFeedbackScale = 10
removeIso = TRUE

# drop na in "to" column
myConnectionsT2T = myConnectionsT2T %>% drop_na(type.to)
graphData = data.frame(from = myConnectionsT2T$type.from, to = myConnectionsT2T$type.to, relWeight = myConnectionsT2T$weightRelative)

graphData_noSelf = getNoSelfGraphData(graphData)  
graphData_self = getSelfFBGraphData(graphData)

if (showself){
  graphData = graphData
  graphName = saveName
} else {
  graphData = left_join(graphData_noSelf, graphData_self)
  graphName = paste0(saveName, "_noSelf")
}

# Graph parameter
if(largeGraph){
  vertexSize = 7
  plotSize = 15
  selfFBscale = vertexSize
}else{
  vertexSize = 12
  plotSize = 10
  selfFBscale = vertexSize
}
```

Plot graph with defined colormap from file
```{r, warning=FALSE} 
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")

myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}

if(splitLR){
  myColorMap_R = myColorMap %>% mutate(Type = paste0(Type, "_R"))
  myColorMap_L = myColorMap %>% mutate(Type = paste0(Type, "_L"))
  myColorMap= bind_rows(myColorMap_L, myColorMap_R)
}

myColorMap = myColorMap %>% filter(Simpletype == "no")

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale, arrowSize, edgeNorm, colormap = myColorMap)

# remove isolated nodes
if(removeIso){
  Isolated = which(degree(myGraph) == 0)
  myGraph = delete.vertices(myGraph, Isolated)
}

myGraph$main = paste0("Connectivity within   the ",slctROI)
l = layout_with_fr(myGraph)

plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph), legend=TRUE,
     family="Arial", vertex.label.family  = "sans",edge.arrow.size=arrowSize)

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-1.3,y=-0.3,legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5),  bty = "n", seg.len=0.5)

if (savePlot){
  dev.print(pdf, file.path("plots",paste0("connectivityGraph_",graphName,'_in_',slctROI,
                        "_",connectionMeasure, round(100*cutoff),"perc.pdf")), width=plotSize, height=plotSize)
}
```
