---
title: "Analysis of connectivity inside the ellipsoid body (EB): connectivity graphs and matrices"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of connectivity inside the ellipsoid body (EB): Connectivity graphs and corresponding connectivity matrices
This notebook shows how to generate the connectivity graph in **Figure 10 F** as well as the connectivity matrix in **Figure 26 D**. It also will generate a type-to-type connectivity  matrix that shows all connections (i.e. no cutoff weight as used on the graph).

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(igraph)

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

### Make selection of neurons to be used in connecitivy analysis
***Selection of ROI and criteria for neuron selection***

For the connectivity graph in **Figure 10F** select:
mySelection = "allEB

For the connectivity matrix in **Figure 11A** select:
mySelection = "ER2EPGEL"

For the connectivity matrix in **Figure 11D** select:
mySelection = "ER4m2EPG"

For the connectivity matrix in **Figure 13A** and the connectivity graph in **Figure 13C** select:
mySelection = "ER2ER"

For the connectivity matrix in **Figure 13 figure supplement 1A,B** select:
mySelection = "ER2PEN-PEG" for A
mySelection = "columnar2ER"for B

```{r}
mySelection = "ER2ER"

ROI = "EB"
slctROI ="EB"
splitLR = TRUE  # Whether or not to split neurons within a type into a left and right group.
makeAsymmetric = TRUE # Whether to enforce showing only pregroup -> postgroup connections as opposed to all connections within {pregroup,postgroup}
  
if (mySelection == "allEB"){
  splitLR = FALSE 
  makeAsymmetric = FALSE 
  saveName = paste0("Inputs_in_", ROI)
  
}else if (mySelection == "ER2EPGEL" | mySelection == "ER2PEN-PEG"){
  if (mySelection == "ER2EPGEL"){
    saveName = paste0("ER2EL-EPG_in_", ROI)
    postNeuron = paste0(c("EPG","EL"),".*")
  }else { # mySelection == "ER2PEN-PEG"
    saveName = paste0("ER2PEN-PEG_in_", ROI)
    postNeuron = paste0(c("PEN","PEG"),".*")
  }
  postName = "EPG, EL"  #gets used in the connectivity matrix plot
  preNeuron = paste0(paste0("ER",seq(1,6)),".*")
  preName = "ER neurons"
  
}else if (mySelection == "ER4m2EPG"){
  saveName = paste0("ER4m2EPG_in_", ROI)
  postNeuron = "EPG.*"
  postName = "EPG"  #gets used in the connectivity matrix plot
  preNeuron = "ER4m.*"
  preName = "ER4m"
  
}else if (mySelection == "ER2ER"){
  splitLR = FALSE 
  saveName = paste0("ER2ER_in_", ROI)
  postNeuron = paste0(paste0("ER",seq(1,6)),".*")
  postName = "ER"  #gets used in the connectivity matrix plot
  preNeuron = paste0(paste0("ER",seq(1,6)),".*")
  preName = "ER neurons"
  
}else if (mySelection == "columnar2ER"){
  saveName = paste0("columnar2ER_in_", ROI)
  postNeuron = paste0(paste0("ER",seq(1,6)),".*")
  postName = "ER neurons"  #gets used in the connectivity matrix plot
  preNeuron = paste0(c("PEN","PEG","EPG","EL"),".*")
  preName = "columnar neurons"
  
}else{
  saveName = paste0("neurons_in_", ROI)
  postNeuron = paste0(c("PEN","PFN"),".*")
  postName = "PEN, PFN"  #gets used in the connectivity matrix plot
  preNeuron = postNeuron
  preName = postName
}

if(splitLR){saveName = paste0(saveName,"_LR")}

if(mySelection == "allEB"){
  if(splitLR){
    roiTable = getTypesInRoiTable(slctROI,lateralize = TRUE, minTypePercentage = 0.5)
  }else{
    roiTable = getTypesInRoiTable(slctROI,lateralize = FALSE, minTypePercentage = 0.5)
  }
}
```


***Selection of neurons***
```{r}
# POST
if(mySelection != "allEB"){
  postIDs = getBodyIdsForList(postNeuron)
  if (mySelection == "ER2EPGEL"){ postIDs <- postIDs %>% filter(type %in% c("EPG","EL"))}
  if (mySelection == "ER4m2EPG"){ postIDs <- postIDs %>% filter(type %in% c("EPG"))}
}else{
  postIDs = roiTable$names
  postName = paste0("all ", ROI)
  print(postName)
}

# PRE
if(mySelection != "allEB"){
  preIDs = getBodyIdsForList(preNeuron)
}else{
  preName = paste0("all ", ROI)
  preIDs = roiTable$names
}

```

### Get connectivity table
```{r, warning=FALSE}
preTypes = c(preIDs$bodyid, postIDs$bodyid)
postTypes = postIDs$bodyid
myConnections = getConnectionTable(preTypes, "POST", slctROI)
myConnections = myConnections %>% filter(to %in% postTypes) 
```

### Format the connectivity matrix, convert to type-to-type
```{r}
# Make asymmetric matrix
if (makeAsymmetric){ myConnections = myConnections %>% filter(to %in% postIDs$bodyid)  %>% filter(from %in% preIDs$bodyid) }

# Make type-to-type connectivity table
typesTable <- getTypesTable(unique(myConnections$databaseType.to))

if (splitLR){ # Subdivide types and build a custom types table
  myConnections = lateralize_types(myConnections, postfix="to")
  myConnections = lateralize_types(myConnections, postfix="from")
  typesTable = lateralize_types(typesTable, postfix="raw")
}

myConnectionsT2T = getTypeToTypeTable(myConnections,typesTable = typesTable)
```

### Connectivity matrix
```{r}
cmax = NULL
cmaxtype = NULL
 
connectionMeasure = "weightRelative"
if(mySelection == "allEB"){ 
  conMatPlot = plotConnectivityMatrix(myConnectionsT2T, byGroup = "type", connectionMeasure, cmaxtype)
  conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  pw=26; ph=22
}else{
  conMatPlot = plotConnectivityMatrix(myConnections, byGroup = "id", connectionMeasure, cmax)
  conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  conMatPlot = structureMatrixPlotByType_lines(conMatPlot)
  if (mySelection == "ER2EPGEL"){pw=15; ph=35}
  else if (mySelection == "ER2ER"){pw=28; ph=25}
  else if (mySelection == "ER2PEN-PEG"){pw=20; ph=18}
  else if (mySelection == "columnar2ER"){pw=40; ph=18}
  else {pw=20; ph=15}
}
print(conMatPlot)

if (savePlot){
  ggsave(paste("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_byID.pdf', sep=''), 
      plot = conMatPlot, device='pdf', path = "plots", scale=1, width=pw, height=ph, units ="cm", dpi = 600, limitsize = TRUE)
}
```

Plot connectivity with columnar neurons ordered by columns (Figure 11 D)
```{r}
if (mySelection == "ER4m2EPG"){
    EBorder = c("R1","L8","R2","L7","R3","L6","R4","L5","R5","L4","R6","L3","R7","L2","R8","L1") #cut at bottom
    EBorder
    
    myConnections = myConnections %>% mutate(colname.to = as.character(
      regmatches(as.character(myConnections$name.to),
                 gregexpr("[R,L]{1}[1-9]{1}",as.character(myConnections$name.to)) ) ))
    myConnections$colname.to = factor(myConnections$colname.to,levels = EBorder)
    
    connectionMeasure = "weightRelative"
    conMatPlot = plotConnectivityMatrix(myConnections, byGroup = "colname", connectionMeasure,cmax)
    conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
    print(conMatPlot)
    if (savePlot){
      ggsave( paste("connectivityMatrix_",saveName,'_in_',slctROI,'_',connectionMeasure,'_byColNameEB.pdf', sep=''), 
              plot = conMatPlot, device='pdf', path = "plots",
              scale = 1, width = 21, height = 10, units ="cm", dpi = 600, limitsize = TRUE)
    }
 }
```

###  Draw regular connectivity graph
This is for Figure 10F and 13C.
```{r, warning=FALSE} 
require(igraph)

connectionMeasure = "weightRelative"
cutoff = 0.05 # for weight 0.05, 0.01, 0

edcurve = 0.1
edgeNorm = 0.1
arrowSize = 0.2 # set to 0 if you prefer styling arrows in e.g. adobe illustrator
removeIso = FALSE
showself = FALSE 
selfFeedbackScale = 10


# drop na in "to" column
myConnectionsT2T = myConnectionsT2T %>% drop_na(type.to)
graphData = data.frame(from = myConnectionsT2T$type.from, to = myConnectionsT2T$type.to, relWeight = myConnectionsT2T$weightRelative)

graphData_noSelf = getNoSelfGraphData(graphData)  
graphData_self = getSelfFBGraphData(graphData)

if (showself){
  graphData = graphData
  graphName = saveName
} else {
  graphData = left_join(graphData_noSelf, graphData_self)
  graphName = paste0(saveName, "_noSelf")
}

# Graph parameter
vertexSize = 7
plotSize = 15
selfFBscale = vertexSize
```

Plot graph with defined colormap from file
```{r, warning=FALSE} 
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")

myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}

if(splitLR){
  myColorMap_R = myColorMap %>% mutate(Type = paste0(Type, "_R"))
  myColorMap_L = myColorMap %>% mutate(Type = paste0(Type, "_L"))
  myColorMap= bind_rows(myColorMap_L, myColorMap_R)
}

myColorMap = myColorMap %>% filter(Simpletype == "no")

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale, arrowSize, edgeNorm, colormap = myColorMap)

# remove isolated nodes
if(removeIso){
  Isolated = which(degree(myGraph) == 0)
  myGraph = delete.vertices(myGraph, Isolated)
}

myGraph$main = paste0("Connectivity within   the ",slctROI)
l = layout_with_fr(myGraph)

plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph), legend=TRUE,
     family="Arial", vertex.label.family  = "sans",edge.arrow.size=arrowSize)

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-1.3,y=-0.3,legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5),  bty = "n", seg.len=0.5)

if (savePlot){
  dev.print(pdf, file.path("plots",paste0("connectivityGraph_",graphName,'_in_',slctROI,
                        "_",connectionMeasure, round(100*cutoff),"perc.pdf")), width=plotSize, height=plotSize)
}
```

***Hierarchy graph with node size indicating input/output ratio and sorted by EPG weight***
This is for Figure 13C.
```{r}
edgeNorm = 0.05
vertexSize = 10

EPGs = neuprint_search("EPG", field = "type")
myConnections_toEPG = getConnectionTable(preIDs$bodyid, "POST", slctROI)
myConnections_toEPG = myConnections_toEPG %>% filter(to %in% EPGs$bodyid) 

typesTable_toEPG <- getTypesTable(unique(myConnections_toEPG$databaseType.to))

if (splitLR){
  # Subdevide types and build a custom types table
  myConnections_toEPG = lateralize_types(myConnections_toEPG, postfix="to")
  myConnections_toEPG = lateralize_types(myConnections_toEPG, postfix="from")
  typesTable_toEPG = lateralize_types(typesTable_toEPG, postfix="raw")
}
myConnectionsT2T_toEPG = getTypeToTypeTable(myConnections_toEPG,typesTable = typesTable_toEPG)

```

Use community info, hierarchy measure and EPG input to generate a layout
```{r}
# find communities
wc = cluster_walktrap(myGraph)
print(modularity(wc))
communitymembership = stack(membership(wc))

# compute hierarchy measure for each node: # of nodes that can be reached
downstreamNodes = data.frame(vertex = V(myGraph)$name, 
                             closeness = closeness(myGraph, vids = V(myGraph), mode = "out", weights = NULL, normalized = TRUE),
                             ndownstream = 1)

for (v in V(myGraph)$name){
  subgraph = delete_vertices(myGraph,v)
  pathfromSouce = all_simple_paths(myGraph, V(myGraph)[v], to = V(myGraph)[c(V(subgraph)$name)], mode = "out")
  nv = length(V(myGraph)[unique(c(unlist(pathfromSouce)))])
  downstreamNodes <- within(downstreamNodes, ndownstream[vertex == v] <- nv)
}

for (v in V(myGraph)$name){
  
  subgraph = delete_vertices(myGraph,v)
}

# align community and EPG input data
layoutInfo = full_join(data.frame("type.from" = V(myGraph)$name), 
                  myConnectionsT2T_toEPG[c("type.from", "weightRelative")])
layoutInfo[is.na(layoutInfo)] <- 0
layoutInfo = layoutInfo %>% mutate(order = rank(weightRelative))
layoutInfo = full_join(layoutInfo, communitymembership, by=c("type.from" = "ind"))
```



```{r, warning=FALSE} 

inWeight = myConnectionsT2T %>% group_by(type.to) %>% summarise(inWeight = sum(weightRelative))
outWeight = myConnectionsT2T %>% group_by(type.from) %>% summarise(outWeight = sum(weightRelative))
weightRatio  = full_join(inWeight,outWeight,by = c("type.to" = "type.from")) %>% mutate(ratio = outWeight/inWeight) %>% rename("type" = "type.to")
weightRatio$ypos <- cut(weightRatio$ratio, breaks = c(seq(0,2.5,0.1), Inf), labels = seq(length(c(seq(0,2.5,0.1), Inf))-1))

vertexBaseSize = 4
myGraph = constructConnectivityGraph(graphData, cutoff, vertexBaseSize, selfFBscale, arrowSize, edgeNorm, colormap = myColorMap)

vertexSize = integer(length(V(myGraph)$name)) + vertexBaseSize
```


Plot
```{r}  
for (i in seq(1, length(V(myGraph)$name))) {
  ratio = weightRatio %>% filter(type == V(myGraph)$name[i]) %>% select(ratio)
  vertexSize[i] = ratio$ratio * vertexBaseSize + vertexBaseSize
}

V(myGraph)$size = vertexSize 
myLayout = matrix(c(jitter(layoutInfo$values*1), layoutInfo$order), ncol = 2, nrow = length(V(myGraph)$name))

myGraph$main = "Hierarchy between RNs \n(x ~ community + jitter, y ~ input to EPGs (low to high),  vertex size ~ hierarchy measure)"
plot(myGraph,edge.curved=0.15, layout=norm_coords(myLayout, xmin=-1.75, xmax=1.75, ymin=-1, ymax=1), 
     edge.color = customizeGraphEdges(myGraph), rescale=FALSE,  cex.lab=1.5, cex.axis=1, family="Arial", 
     vertex.label.family  = "sans",)

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-1.5,y=1,legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0),length.out=5),  bty = "n", seg.len=0.5)


dev.print(pdf, paste0("plots/connectivityGraph_",graphName,'_in_',slctROI,
                      "_",connectionMeasure, round(100*cutoff),"perc_byEPG.pdf"), width=20, height=10)
```

