---
title: 'Electrotonic distance of synapses to putative spike initiation zone for neurons in the EB'
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of electrotonic distance of synapses categorized by modality type to putative spike initiation zone.

Electrotonic distance calculuated should be approximately proportional to the actual electrotonic distance as we do not know the values of the specific intracellular and membrane resistivity.

Example of EPG and rootpoint (section 2)
* Figure 12A

CDFs of electrotonic and raw distances (section 3)
* Figure 12 C (normalized electrotonic distances)
* Figure 12 supplement 1E (raw distances along arbors)

Medians of distance distributions (section 4)
* Figure 12E - distributions of the medians of the electrotonic distance distributions for each modality (EPG)
* Figure 12 supplement 3B - distributions of the medians of the electrotonic distance distributions for each modality (EL)
* Figure 12 supplement 1F - distributions of the medians of the raw distances along arbor distributions for each modality
* Figure 12 supplement 2 - distributions of the medians of the electrotonic distance distributions for each neuron type within modalities

Rank ordering by medians (section 4a)
* Figure 12 supplement 1B - median rank ordering of modalities (EPG)
* Figure 12 supplement 3C - median rank ordering of modalities (EL)

Median distance between distributions (section 4b)
* Figure 12 supplement 1C - median distance between distributions of consecutive rank order

Distribution of synapses by modality in EB with mean distance contours (section 5)
* Figure 12C (left) - density of synapses with mean electotonic distance (EPG)
* Figure 12 supplement 3A (top) - density of synapses with mean electotonic distance (EL)
* Figure 12 supplement 1D - density of synapses with mean raw distance along arbor
* Figure 12C (right) - synapse densities grouped by modality (EPG)
* Figure 12 supplement 3A (bottom) - synapse densities grouped by modality (EL)
* Figure 12 supplement 1A - synapse densities grouped by modality, plotted separately



```{r, message=FALSE, warning=FALSE}
library(natverse)
library(neuprintr)
library(hemibrainr)
library(igraph)
library(ggplot2)
library(tidyr)
library(dplyr)
require(matlib)
library(neuprintrExtra)
source("../R/SynapsePCAUtils.R")
```

```{r, message=FALSE, warning=FALSE}
require(alphahull)
```

```{r, message=FALSE, warning=FALSE}
require(RColorBrewer)
library("paletteer")
source('../R/paperTheme.R')

conn = neuprint_login()
```

### Saving plots
Indicate if you would like to save the plots here (default is false). Plots will be saved inside this folder in a subdirectory "plots".
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

## (1) Load in neurons and prepare them for analysis
Choose which neuron type to analyze electrotonic distances on.
* Figure 12, Figure 12 supplement 1, Figure 12 supplement 2: set nronType = 'EPG'
* Figure 12 supplement 3: set nronType = 'EL'

```{r neuron info}
# neurons for which you care about the synaptic locations
nronType = 'EL'
nron_info = neuprint_search(paste(".*", nronType, ".*", sep = ""))
```

```{r}
# synaptic partners you're interested in
partner_info = neuprint_search(".*ring.*")
head(partner_info)
unique(partner_info$type)

partner_info = rbind(partner_info,neuprint_search(".*PEG.*"))
partner_info = rbind(partner_info, neuprint_search((".*PEN.*")))
partner_info = rbind(partner_info, neuprint_search(".*EPG.*"))
head(partner_info)
unique(partner_info$type)

# set this to NULL if you want to consider all synapses
#partner_info = NULL
```

Read in the neurons we care about. This might take a while depending on how many neurons you're trying to load in, so if there are ones you know you don't want to consider, include their index in the exclude list. 
```{r read in neurons}

if(nronType == 'EPG'){
  epgt = grep('EPGt',nron_info$name)
  epgR1 = grep('R1',nron_info$name)
  exclude = unique(c(epgt, epgR1))
} else {
  exclude = c()
}

if(is.null(exclude)){
  nronList = neuprint_read_neurons(nron_info$bodyid)
} else {
  nronList = neuprint_read_neurons(nron_info$bodyid[-exclude])
}
```

Find neurons with disoriented graphs (needed for EPGs, not ELs).
  - intersect each neuron with each significant ROI
  - find shortest path between points in each ROI to rootpoint
  - shortest path of these tells you which ROI the rootpoint is closest too
```{r}
if(nronType == 'EPG'){

# Significant ROIs for EPGs
sigROI = c('EB','PB')
sigROI_mesh = lapply(sigROI, FUN = neuprint_ROI_mesh)

distancesDF = data.frame()

for(roiMesh in sigROI_mesh){
  nronROI = lapply(nronList, function(n) subset(n, pointsinside(n, surf = roiMesh)))
  rpPN = sapply(nronList, function(n) n$d[rootpoints(n),'PointNo'])
  roiNodes = lapply(nronROI, function(n) n$d$PointNo)
  distRPtoROI = mapply(function(n,rp,nodes) min(distances(as.ngraph(n, weights = T), v = as.character(rp), to = as.character(nodes), mode = 'out')), n = nronList, rp = rpPN, nodes = roiNodes)
  
  if(ncol(distancesDF) == 0){
    distancesDF = as.data.frame(distRPtoROI)
  } else {
    distancesDF = cbind(distancesDF, distRPtoROI)
  }
  
}

colnames(distancesDF) = sigROI
distancesDF$closestROI = colnames(distancesDF)[apply(distancesDF,1,which.min)]

closestROInum = table(distancesDF$closestROI)
closestROInum

closestROIname = names(which.max(closestROInum))
disoriented = nronList[distancesDF$closestROI != closestROIname]

} else {
  disoriented = c()
}
```

Fix the disoriented graphs using hemibrain_reroot().
```{r}

if(length(disoriented) > 0){
  nronList = setdiff(nronList, disoriented)
  adjustRP = hemibrain_reroot(disoriented)
  nronList = c(nronList, adjustRP)
}

```

Find the synapses that are from the types of neurons we're interested in and add the partner type info to the data frame.
```{r synapses}
# this grabs all the synapses for you
nron_synapses = lapply(nronList, function(nron) nron$connectors)

# keep only the synapses from the partner types you're interested in
# if you're interested in all synapses, partner_info should be set to NULL
if(!is.null(partner_info)){
nron_synapses = lapply(nron_synapses, function(syn) subset(syn, partner %in% partner_info$bodyid))
}

# include partner type to dataframe
nron_synapses = lapply(nron_synapses, function(syn){
  partnerType = neuprint_get_meta(syn$partner)$type
  cbind(syn,partnerType)
})
```


## (2) Subset the neurons to just the parts that innervate the ROI of interest (here, the ellipsoid body (EB))

Intersect neuron and synapses with EB.
```{r subsetting neuron}
mainROI = 'EB'
mainROI_mesh = neuprint_ROI_mesh(roi = mainROI)

nronMainROI = nlapply(nronList, function(nron,mesh) subset(nron, pointsinside(nron, surf = mesh)), mesh = mainROI_mesh)

nronMainROI_synapses = lapply(nron_synapses, function(n,mesh) subset(n, pointsinside(n, surf = mesh)), mesh = mainROI_mesh)
```


Intersecting the neuron with the EB ROI often "fractures" the neuron (i.e., the associated graph is no longer connected). To fix this, we will first build up the neuron's graph until the fractures are healed, We will then prune the graph back down so that we retain only those vertices that are needed to keep the graph connected.

Once the graph is fixed, we can identify an appropriate rootpoint for each neuron to indicate the putative spike initiation zone.

This function builds up the neuron's graph to "heal" the fractures:
```{r}

buildGraph <- function(fullNron, subNron, synDF){

  # turn the subsetted neuron into a graph
  fullG = as.ngraph(subNron)
  
  # make sure all synapses that occur in EB are in this graph
  if(!all(synDF$treenode_id %in% V(fullG)$name)){
    inds = which(!(synDF$treenode_id %in% V(fullG)$name))
    pn = unique(synDF$treenode_id[inds])
    fullG = add_vertices(fullG, nv = length(pn), name = pn)
  }

  while(!is_connected(fullG)){
    # decompose the graph into it's connected parts
    graphCompList = decompose(fullG, mode = "weak")
    for(g in graphCompList){
      # if the subgraph doesn't have any synapses, 
      #   remove it from the full graph
      if(!any(V(g)$name %in% synDF$treenode_id)){
        fullG = fullG - as.character(V(g)$name)
      } else {
      # otherwise, identify the current root of the subgraph
      #   and find it's parent in the neuron.
        tempRoot = V(g)$name[!degree(g, mode = "in")]
        tempParent = fullNron$d[fullNron$d$PointNo == tempRoot,]$Parent
        # Add the parent if it is not already in the full graph
        if (!(tempParent %in% V(fullG)$name)){
          fullG = add_vertices(fullG, nv = 1, name = tempParent)
        }
        # Add the appropriate edge connecting the subgraphs root 
        #   to it's parent to the full graph
        fullG = add_edges(fullG, edges = as.character(c(tempParent, tempRoot)))
      }
    }
  }
  
  return(fullG)
}

```


This function prunes down the graph generated by the buildGraph function so that only the necessary nodes are kept on the root side:
```{r}

pruneGraph <- function(fullG, fullNron, synDF){
  
  # find the current root of the graph fullG 
  #   (by finding the only node with 0 edges pointing to it)
  root = V(fullG)$name[!degree(fullG, mode = "in")]
  # find the neighbors of this node (outward)
  rootNhb = neighbors(fullG, as.character(root), mode = "out")
  # indicator whether or not to keep going through while loop
  keepGoing = 1

  while(keepGoing){
    if(!(length(rootNhb) == 1)){ # if there is more than one neighbor,
      # check whether or not the path from each neighbor contains synapses
      # if it doesn't, remove that whole path from the graph
      for(nhb in rootNhb$name){
        nhbPath = dfs(fullG, as.character(nhb), neimode = 'out', unreachable = F)
        nhbPath = nhbPath$order[!is.na(nhbPath$order)]
        if(!any(nhbPath$name %in% synDF$treenode_id)){
          fullG = fullG - as.character(nhbPath$name)
        }
      }
    # have to rerun finding rootNhb here, otherwise igraph gets confused if you pull from the original rootNhb after deleting some of those vertices from the full graph.
    rootNhb = neighbors(fullG, as.character(root), mode = "out")
    if(length(rootNhb) > 1){ # if you still have more than one neighbor, stop pruning
      keepGoing = 0
      break
    } else if(length(rootNhb) == 0){ # if there are no neighbors left, something went wrong
      print('something went wrong, no neighbors left')
      break
    }
    }
    
  # if you made it here, there is only one neighbor left
  # find the path out from this neighbor to each synapse
    synapsePaths = shortest_paths(as.ngraph(fullNron), from = as.character(rootNhb$name), to = as.character(synDF$treenode_id), mode = 'out')
    synapsePathsLength = sapply(synapsePaths$vpath, length)
    if(any(synapsePathsLength == 0)){ # if any synapses can't be reached by the neighbor, stop pruning
      keepGoing = 0
    } else { # if all synapses are reachable from the neighbor, then remove the root node and repeat everything with the neighbor now as the root
      fullG = fullG - as.character(root)
      root = rootNhb$name
      rootNhb = neighbors(fullG, as.character(root), mode = "out")
    }
  }
  
  return(fullG)
}


```


Now that we have these functions, we can use them to fix the graphs (this will take a minute to run).
```{r}
# build graphs up (i.e., heal any fractures)
nronGraphs = mapply(buildGraph, nronList, nronMainROI, nronMainROI_synapses, SIMPLIFY = F)
```

```{r warning = F}
# prune graphs down on the root side
nronGraphs = mapply(pruneGraph, nronGraphs, nronList, nronMainROI_synapses, SIMPLIFY = F)
```

Update the subsetted neurons now that we have the correct graphs for them. 
```{r}
nronMainROI = nmapply(function(nron,g) subset(nron, PointNo %in% V(g)$name), nronList, g = nronGraphs) 
```

With the correct graphs we can automatically pull the rootpoint using the rootpoints function.

Figure 12A - example neuron and rootpoint.
```{r}
if(savePlot){
  pdf(paste('plots/example', nronType, '_RP.pdf', sep=""))
}

exInd = 2
nron = nronList[[exInd]]
rp = nronMainROI[[exInd]]$d[rootpoints(nronMainROI[[exInd]]),]
egNronPlot = plot(nron, WithNodes = F)
points(rp$X, rp$Y, col = '#1CFFCEFF', cex = 1, pch = 19)

if(savePlot){
  dev.off()
}
```

## (3) Compute electrotonic distances between synapses and rootpoint.

Compute the raw distance along the arbor between the synapses of interest and the rootpoint. 
```{r}

nronMainROI_synapses = mapply(function(nron,syn){
  distToRoot = distances(as.ngraph(nron, weights = T), v = as.character(nron$d$PointNo[rootpoints(nron)]), to = as.character(unique(syn$treenode_id)), mode = 'out')
  distToRoot = distToRoot[match(syn$treenode_id, unique(syn$treenode_id))]
  distToRoot = distToRoot/125 # converts distance to microns
  syn = cbind(syn, distToRoot)
}, nron = nronMainROI, syn = nronMainROI_synapses, SIMPLIFY = F)

```

With the raw distance we can compute the electrotonic distance (technically something proportional to the electrotonic distance) between the synapses of interest and the rootpoint. The following function does that.
```{r}

electrotonicDist <- function(nron,syn){
g = as.ngraph(nron,weights = T)
edgePath = shortest_paths(g, from = as.character(nron$d$PointNo[rootpoints(nron)]), to = as.character(unique(syn$treenode_id)), mode = 'out', output = 'epath')

electroDist = sapply(edgePath$epath, function(edges){
  edgeLength = edge_attr(g,'weight',index = edges)/125
  ver = ends(g,edges,names=T)[,2]
  verDiam = vertex_attr(g,'diam',index = as.character(ver))/125

  lengthConst = sqrt(verDiam/4)
  electroLength = edgeLength/lengthConst
  electroDist = sum(electroLength)
})

electroDist = electroDist[match(syn$treenode_id, unique(syn$treenode_id))]

syn = cbind(syn, electroDist)

}

```

Calculate the electrotonic distances for every neuron.
```{r}
nronMainROI_synapses = mapply(electrotonicDist, nron = nronMainROI, syn = nronMainROI_synapses, SIMPLIFY = F)

```

Turn this into one big dataframe:
```{r}
synapses = suppressWarnings(bind_rows(nronMainROI_synapses))
```

Normalize the electrotonic distances for better comparison across neurons.
```{r}

synapses = synapses %>% group_by(bodyid) %>%
              mutate(rangeEDist = electroDist - min(electroDist)) %>%
              mutate(normEDist = rangeEDist/(max(rangeEDist))) %>%
              ungroup()

```
  
Group synaptic partners of interest into groups of different input modalities. The modality types and the neurons that fall under each type are:
    Mechanosensory: ER1.
    Contralateral visual + motor: ER3a, ER3p, ER3m.
    Ipsilateral visual + pol: ER2, ER3w, ER4d, ER4m.
    Sleep: ER3d, ER5.
    Motor: PEN.

```{r}

ms = c('ER1_a','ER1_b')
cv = c('ER3a_a','ER3a_c','ER3m','ER3p_a','ER3p_b')
iv = c('ER2_a','ER2_b','ER2_c','ER2_d','ER3w', 'ER4d','ER4m')
sleep = c('ER3d_a','ER3d_b','ER3d_c','ER3d_d','ER5')
other = c('ER6')
ex = c('ExR1','ExR2','ExR3','ExR4','ExR5','ExR6','ExR7','ExR8')
motor = c('PEN_a(PEN1)','PEN_b(PEN2)')
rec = c('EPG','EPGt','PEG')
remove = c('ER3a_b','ER3a_d')

synapses = synapses %>% 
  mutate(modality = case_when(
    partnerType %in% ms ~ 'ms',
    partnerType %in% cv ~ 'cv',
    partnerType %in% iv ~ 'iv',
    partnerType %in% sleep ~ 'sleep',
    partnerType %in% other ~ 'other',
    partnerType %in% ex ~ 'ex',
    partnerType %in% motor ~ 'motor',
    partnerType %in% rec ~ 'rec',
    partnerType %in% remove ~ 'exclude'
  ))


```

Separate pre from post synapses.
```{r}
synapsesPre = synapses %>% filter(prepost == 1)
synapsesPost = synapses %>% filter(prepost == 0)
```

Modality colormap for plots
```{r}
Vivid_Red = '#F6222E'

Vivid_Violet = "#AA0DFE"
green = "#A8E2A8"
Vivid_Blue = "#2ED9FF"
darker_Blue = '#5343EF'
pink = '#EF8F9F'

modalityCMap =c(green,Vivid_Blue,Vivid_Violet,pink,darker_Blue)
```

Figure 12C - CDF of distributions of electrotonic distances between synapses and rootpoint (grouped by modality) for an example neuron.
```{r}
if(nronType == 'EPG'){
  egNum = 24
  nron_info_kept = nron_info[-exclude,]
} else {
  egNum = 1
  nron_info_kept = nron_info
}

modalityCDFPlot = ggplot(filter(synapsesPre, bodyid == nron_info_kept$bodyid[egNum], modality %in% c('cv','iv','motor','ms','sleep')), aes(x = normEDist, color = modality)) +
    stat_ecdf(geom = "step") +
    scale_colour_manual(values = modalityCMap) +
    theme_paper() +
    labs(x = 'normalized electrotonic distance to rootpoint', y = 'CDF') + 
  facet_wrap(~bodyid)

if(savePlot){
ggsave(paste('modalityCDF_', nronType, '_ED.pdf', sep = ""), plot = modalityCDFPlot, device='pdf', path = "plots")
}
```

Figure 12 supplement 1E - CDF of distributions of raw distance along arbor between synapses and rootpoint (grouped by modality) for same example neuron.
```{r}

modalityCDFPlot = ggplot(filter(synapsesPre, bodyid == nron_info_kept$bodyid[egNum], modality %in% c('cv','iv','motor','ms','sleep')), aes(x = distToRoot, color = modality)) +
    stat_ecdf(geom = "step") +
    scale_colour_manual(values = modalityCMap) +
    theme_paper() +
    labs(x = 'distance to rootpoint', y = 'CDF') + 
  facet_wrap(~bodyid)

if(savePlot){
ggsave(paste('modalityCDF_', nronType, '_RD.pdf', sep = ""), plot = modalityCDFPlot, device='pdf', path = "plots")
}

```

## (4) Compare medians of electrotonic distance distributions of different modalities

Calculate the medians.
```{r}
medOfEDist_nronType = filter(synapses, prepost == 1, modality %in% c('cv','iv','motor','ms','sleep')) %>% 
  group_by(bodyid, partnerType) %>%
  summarize(med = median(normEDist)) %>% 
  mutate(eg = case_when(
    bodyid == nron_info_kept$bodyid[egNum] ~ 1,
    TRUE ~ 0
  ))

medOfEDist = filter(synapses, prepost == 1) %>% group_by(bodyid, modality) %>%
            summarize(med = median(normEDist)) %>%
            filter(modality %in% c('cv','iv','motor','ms','sleep')) %>%
            group_by(bodyid) %>%
            mutate(rankOrder = rank(med)) %>%
            ungroup() %>% 
            mutate(eg = case_when(
              bodyid == nron_info_kept$bodyid[egNum] ~ 1,
              TRUE ~ 0
            )) %>% 
            mutate(modNum = case_when(
              modality == 'motor' ~ 1,
              modality == 'ms' ~ 2,
              modality == 'iv' ~ 3,
              modality == 'cv' ~ 4,
              modality == 'sleep' ~ 5
            )) 

```

Figure 12E (nronType = 'EPG') or Figure 12 supplement 3B (nronType = 'EL') - distributions of the medians of the electrotonic distance distributions for each modality
```{r}
  medHivePlot = ggplot(medOfEDist) +
  geom_line(aes(x = factor(modality, levels = c('motor','ms','iv','cv','sleep')), y = med,  group = factor(bodyid), color = factor(eg)), position = position_dodge(0.5), size = 0.5) +
  geom_point(aes(x = factor(modality, levels = c('motor','ms','iv','cv','sleep')), y = med, fill = modality, group = factor(bodyid)), color = 'black', pch = 21, position = position_dodge(0.5), size = 3, alpha = 0.75) +
  theme_paper() +
  guides(fill = 'legend') +
  scale_fill_manual(values = modalityCMap) +
  scale_color_manual(values = c('lightgray','black',modalityCMap)) +
  labs(x = 'modality', y = 'median') 
  
if(savePlot){
ggsave(paste('medianDists_hive_jitter_', nronType, '_ED.pdf', sep = ""), plot = medHivePlot, device='pdf', path = "plots")
}

```

Figure 12 supplement 1F - distributions of the medians of the raw distances along arbor distributions for each modality
```{r}
medOfDist = filter(synapses, prepost == 1) %>% group_by(bodyid, modality) %>%
            summarize(med = median(distToRoot)) %>%
            filter(modality %in% c('cv','iv','motor','ms','sleep')) %>%
            group_by(bodyid) %>%
            mutate(rankOrder = rank(med)) %>%
            ungroup() %>% 
            mutate(eg = case_when(
              bodyid == nron_info_kept$bodyid[egNum] ~ 1,
              TRUE ~ 0
            )) %>% 
            mutate(modNum = case_when(
              modality == 'motor' ~ 1,
              modality == 'ms' ~ 2,
              modality == 'iv' ~ 3,
              modality == 'cv' ~ 4,
              modality == 'sleep' ~ 5
            )) 

  medHivePlot = ggplot(medOfDist) +
  geom_line(aes(x = factor(modality, levels = c('motor','ms','iv','cv','sleep')), y = med,  group = factor(bodyid), color = factor(eg)), position = position_dodge(0.5), size = 0.5) +
  geom_point(aes(x = factor(modality, levels = c('motor','ms','iv','cv','sleep')), y = med, fill = modality, group = factor(bodyid)), color = 'black', pch = 21, position = position_dodge(0.5), size = 3, alpha = 0.75) +
  theme_paper() +
  guides(fill = 'legend') +
  scale_fill_manual(values = modalityCMap) +
  scale_color_manual(values = c('lightgray','black',modalityCMap)) +
  labs(x = 'modality', y = 'median')
  
if(savePlot){
  ggsave(paste('medianDists_hive_jitter_', nronType, '_RD.pdf', sep = ""), plot = medHivePlot, device='pdf', path='plots')
}

```

Figure 12 supplement 2 - distributions of the medians of the electrotonic distance distributions for each neuron type within modalities
```{r}
# Figure 12 supplement 2A
medHivePlot = ggplot(filter(medOfEDist_nronType, partnerType %in% motor)) +
  geom_line(aes(x = factor(partnerType), y = med,  group = factor(bodyid), color = factor(eg)), position = position_dodge(0.5), size = 0.5) +
  geom_point(aes(x = factor(partnerType), y = med, fill = partnerType, group = factor(bodyid)), color = 'black', pch = 21, position = position_dodge(0.5), size = 3, alpha = 0.75) +
  theme_paper() +
  guides(fill = 'legend') +
  scale_color_manual(values = c('lightgray','black')) +
  labs(x = 'partner type', y = 'median') +
  ylim(0.05,0.85)

if(savePlot){
ggsave(paste('medianDists_hive_jitter_', nronType, '_motorED.pdf', sep = ""), plot = medHivePlot, device='pdf', path = "plots")
}

# Figure 12 supplement 2B
medHivePlot = ggplot(filter(medOfEDist_nronType, partnerType %in% ms)) +
  geom_line(aes(x = factor(partnerType), y = med,  group = factor(bodyid), color = factor(eg)), position = position_dodge(0.5), size = 0.5) +
  geom_point(aes(x = factor(partnerType), y = med, fill = partnerType, group = factor(bodyid)), color = 'black', pch = 21, position = position_dodge(0.5), size = 3, alpha = 0.75) +
  theme_paper() +
  guides(fill = 'legend') +
  scale_color_manual(values = c('lightgray','black')) +
  labs(x = 'partner type', y = 'median') +
  ylim(0.05,0.85)

if(savePlot){
ggsave(paste('medianDists_hive_jitter_', nronType, '_msED.pdf', sep = ""), plot = medHivePlot, device='pdf', path = "plots")
}

# Figure 12 supplement 2C
medHivePlot = ggplot(filter(medOfEDist_nronType, partnerType %in% iv)) +
  geom_line(aes(x = factor(partnerType, levels = c('ER3w','ER2_a','ER2_b','ER2_c','ER2_d','ER4m','ER4d')), y = med,  group = factor(bodyid), color = factor(eg)), position = position_dodge(0.5), size = 0.5) +
  geom_point(aes(x = factor(partnerType, levels = c('ER3w','ER2_a','ER2_b','ER2_c','ER2_d','ER4m','ER4d')), y = med, fill = partnerType, group = factor(bodyid)), color = 'black', pch = 21, position = position_dodge(0.5), size = 3, alpha = 0.75) +
  theme_paper() +
  guides(fill = 'legend') +
  scale_color_manual(values = c('lightgray','black')) +
  labs(x = 'partner type', y = 'median') +
  ylim(0.05,0.85)
  
if(savePlot){
ggsave(paste('medianDists_hive_jitter_', nronType, '_ivED.pdf', sep = ""), plot = medHivePlot, device='pdf', path = "plots")
}

# Figure 12 supplement 2D
medHivePlot = ggplot(filter(medOfEDist_nronType, partnerType %in% cv)) +
  geom_line(aes(x = factor(partnerType, levels = c('ER3p_a','ER3p_b','ER3m','ER3a_a','ER3a_c')), y = med,  group = factor(bodyid), color = factor(eg)), position = position_dodge(0.5), size = 0.5) +
  geom_point(aes(x = factor(partnerType, levels = c('ER3p_a','ER3p_b','ER3m','ER3a_a','ER3a_c')), y = med, fill = partnerType, group = factor(bodyid)), color = 'black', pch = 21, position = position_dodge(0.5), size = 3, alpha = 0.75) +
  theme_paper() +
  guides(fill = 'legend') +
  scale_color_manual(values = c('lightgray','black')) +
  labs(x = 'partner type', y = 'median') +
  ylim(0.05,0.85)

if(savePlot){
ggsave(paste('medianDists_hive_jitter_', nronType, '_cvED.pdf', sep = ""), plot = medHivePlot, device='pdf', path = "plots")
}

# Figure 12 supplement 2E
medHivePlot = ggplot(filter(medOfEDist_nronType, partnerType %in% sleep)) +
  geom_line(aes(x = factor(partnerType, levels = c('ER3d_a','ER3d_b','ER3d_c','ER3d_d','ER5')), y = med,  group = factor(bodyid), color = factor(eg)), position = position_dodge(0.5), size = 0.5) +
  geom_point(aes(x = factor(partnerType, levels = c('ER3d_a','ER3d_b','ER3d_c','ER3d_d','ER5')), y = med, fill = partnerType, group = factor(bodyid)), color = 'black', pch = 21, position = position_dodge(0.5), size = 3, alpha = 0.75) +
  theme_paper() +
  guides(fill = 'legend') +
  scale_color_manual(values = c('lightgray','black')) +
  labs(x = 'partner type', y = 'median') +
  ylim(0.05,0.85)

if(savePlot){
ggsave(paste('medianDists_hive_jitter_', nronType, '_sleepED.pdf', sep = ""), plot = medHivePlot, device='pdf', path = "plots")
}

```


### (4a) Rank order modalities by median.
For EPGs, there are 5 orderings in all
- First ordering (motor, ms, iv, cv, sleep) is the most common and will be called the standard ordering 
- Second (motor, iv, ms, cs, sleep), one perturbation from standard ordering
- Third (motor, ms, cv, iv, sleep), one perturbation from standard ordering
- Fourth (ms, motor, iv, cv, sleep), one perturbation from standard ordering
- Fifth (iv, motor, ms, cv, sleep), two perturbations from standard ordering

Figure 12 supplement 1B (nronType = 'EPG') and supplement 3C (nronType = 'EL') - median rank ordering of modalities
```{r}
if(nronType == 'EPG'){
currentOrdering = sort(unique(synapses$bodyid), decreasing = T)
sortingLevel2 = currentOrdering[c(3,9,12,13,29,34,43)]
sortingLevel3 = currentOrdering[c(8,16,18,28,35)]
sortingLevel4 = currentOrdering[c(6,30,44)]
sortingLevel5 = currentOrdering[c(15,41)]
sortingLevel6 = currentOrdering[c(32)]
sortingLevel = c(sortingLevel2, sortingLevel3, sortingLevel4, sortingLevel5, sortingLevel6)
sortingLevel1 = setdiff(currentOrdering, sortingLevel)
sortingLevel = c(sortingLevel1, sortingLevel)

rankOrderingPlot = ggplot(medOfEDist) +
  geom_tile(aes(x = rankOrder, y = factor(bodyid, levels = rev(sortingLevel)), fill = modality), color = '#5A5156') +
  geom_tile(aes(x = rankOrder, y = as.factor(bodyid), fill = modality), color = '#5A5156') +
  theme_paper() +
  theme(axis.text.y = element_blank(), legend.position="top") +
  labs(y = "neurons", x = "rank order") +
  scale_fill_manual(values = modalityCMap)
} else {
  currentOrdering = sort(unique(synapses$bodyid), decreasing = T)
  sortingLevel2 = currentOrdering[c(4,5,10,14)]
  sortingLevel3 = currentOrdering[c(18)]
  sortingLevel = c(sortingLevel2, sortingLevel3)
  sortingLevel1 = setdiff(currentOrdering, sortingLevel)
  sortingLevel = c(sortingLevel1, sortingLevel)
  rankOrderingPlot = ggplot(medOfEDist) +
  geom_tile(aes(x = rankOrder, y = factor(bodyid, levels = rev(sortingLevel)), fill = modality), color = '#5A5156') +
  theme_paper() +
  theme(axis.text.y = element_blank(), legend.position="top") +
  labs(y = "neurons", x = "rank order") +
  scale_fill_manual(values = modalityCMap)
}

if(savePlot){
ggsave(paste('rankOrdering_', nronType, '_ED.pdf', sep = ""), plot = rankOrderingPlot, device='pdf', path = "plots")
}
```

### (4b) Median distance between distributions

Modify the data structure.
```{r}
if(nronType == 'EPG'){
medOfEDist = medOfEDist %>% group_by(bodyid) %>%
              mutate(orderingType = case_when(
                bodyid %in% sortingLevel1 ~ 1,
                bodyid %in% sortingLevel2 ~ 2,
                bodyid %in% sortingLevel3 ~ 3,
                bodyid %in% sortingLevel4 ~ 4,
                bodyid %in% sortingLevel5 ~ 5,
                bodyid %in% sortingLevel6 ~ 6
              )) %>%
              ungroup()
} else {
  medOfEDist = medOfEDist %>% group_by(bodyid) %>%
              mutate(orderingType = case_when(
                bodyid %in% sortingLevel1 ~ 1,
                bodyid %in% sortingLevel2 ~ 2,
                bodyid %in% sortingLevel3 ~ 3
              )) %>%
              ungroup()
}

dfRank1 = filter(medOfEDist, rankOrder == 1) %>% select(-c(rankOrder,modNum)) %>% rename(modality1 = modality, med1 = med)
dfRank2 = filter(medOfEDist, rankOrder == 2) %>% select(-c(rankOrder,modNum)) %>% rename(modality2 = modality, med2 = med)
dfRank3 = filter(medOfEDist, rankOrder == 3) %>% select(-c(rankOrder,modNum)) %>% rename(modality3 = modality, med3 = med)
dfRank4 = filter(medOfEDist, rankOrder == 4) %>% select(-c(rankOrder,modNum)) %>% rename(modality4 = modality, med4 = med)
dfRank5 = filter(medOfEDist, rankOrder == 5) %>% select(-c(rankOrder,modNum)) %>% rename(modality5 = modality, med5 = med)

medOfEDistWide = merge(dfRank1, dfRank2)
medOfEDistWide = merge(medOfEDistWide, dfRank3)
medOfEDistWide = merge(medOfEDistWide, dfRank4)
medOfEDistWide = merge(medOfEDistWide, dfRank5)

```

Calculate the difference of medians between distributions with consecutive rank orderings.
```{r}

medOfEDistWide = medOfEDistWide %>% 
                  mutate(dist12 = med2 - med1) %>%
                  mutate(dist23 = med3 - med2) %>%
                  mutate(dist34 = med4 - med3) %>%
                  mutate(dist45 = med5 - med4)

```

```{r}
l = length(nronList)

if(nronType == 'EPG'){
EdistBetween = data.frame(bodyid = medOfEDistWide$bodyid, orderingType = medOfEDistWide$orderingType, dist = c(medOfEDistWide$dist12, medOfEDistWide$dist23, medOfEDistWide$dist34, medOfEDistWide$dist45), betweenWho = c(rep('1-2',times = l), rep('2-3',times = l),rep('3-4',times = l),rep('4-5',times = l)))

EdistBetween = EdistBetween %>% mutate(flag = case_when(
  betweenWho == '1-2' & orderingType %in% c(5,6) ~ 1,
  betweenWho == '2-3' & orderingType %in% c(2,6) ~ 1,
  betweenWho == '3-4' & orderingType == 4 ~ 1,
  betweenWho == '4-5' & orderingType %in% c(3,6) ~ 1,
  TRUE ~ 0
))
} else {
  EdistBetween = data.frame(bodyid = medOfEDistWide$bodyid, orderingType = medOfEDistWide$orderingType, dist = c(medOfEDistWide$dist12, medOfEDistWide$dist23, medOfEDistWide$dist34, medOfEDistWide$dist45), betweenWho = c(rep('1-2',times = l), rep('2-3',times = l),rep('3-4',times = l),rep('4-5',times = l)))
  
  EdistBetween = EdistBetween %>% mutate(flag = case_when(
  betweenWho == '1-2' & orderingType == 3 ~ 1,
  betweenWho == '3-4' & orderingType == 2 ~ 1,
  TRUE ~ 0
))
}

```

Figure 12 supplement 1C - median distance between distributions of consecutive rank order
```{r}
distDistancePlot = ggplot(EdistBetween) +
  geom_boxplot(aes(y = dist, x = factor(flag), color = as.factor(flag))) +
  facet_grid(.~betweenWho) +
  scale_color_manual(values = c('#5A5156',Vivid_Red)) +
  theme_paper() +
  theme(legend.position = 'none') +
  labs(y = "median distance", x = "ordering", title = 'Median distance between distributions of rank orders:') +
  scale_x_discrete(labels = c('standard', 'permuted'))

if(savePlot){
ggsave(paste('distDistance_', nronType, '_ED.pdf', sep = ""), plot = distDistancePlot, device='pdf', path = "plots")
}
```


## (5) Distribution of synapses in EB by modality and how electrotonic distance depends on location (radial, depth) in EB.

Import of ROI meshes and get vertices in x,y,z
```{r}
roiMeshPts = data.frame(dotprops(mainROI_mesh)$points)
names(roiMeshPts) <- c("x","y","z")
```  

Find convenient coordinate system based on PCA of vertices and center of mass of the ROI
***Transform mesh  and synapse locations***
```{r}
# define new origin from roi center of mass
origin = getCOM(roiMeshPts)

#reset orgin
roiMeshPts = resetOrigin(roiMeshPts, origin)

#get eigenvectors
roiEigen = covPCA(roiMeshPts)

roiMeshPtsRot = changeBasis(roiMeshPts, roiEigen)

#Synapse locations
synPts = data.frame(x=as.numeric(synapses$x),
                    y=as.numeric(synapses$y),
                    z=as.numeric(synapses$z))
synPtsShift = resetOrigin(synPts, origin)
synPtsRot = changeBasis(synPtsShift, roiEigen)
synPtsRot = synPtsRot %>% select(X, Y, Z)
synPtsRot = cbind(synPts, synPtsRot)



rootPtsCoord = lapply(nronMainROI, function(nron) nron$d[rootpoints(nron), c('X','Y','Z')])
rootPtsCoord = bind_rows(rootPtsCoord)
rootPtsCoord = data.frame(x = as.numeric(rootPtsCoord$X),
                          y = as.numeric(rootPtsCoord$Y),
                          z = as.numeric(rootPtsCoord$Z))

rootPtsShift = resetOrigin(rootPtsCoord, origin)
rootPtsRot = changeBasis(rootPtsShift, roiEigen)
rootPtsRot = rootPtsRot %>% select(X, Y, Z)

```

Convert spatial units into microns
```{r}
# division by 125 converts units to microns

synapses = merge(synapses, synPtsRot)
synapses = synapses %>% mutate(radial = sqrt(X^2 + Y^2)/125, depth = -Z/125)

rootPtsNewCoord = rootPtsRot %>% mutate(radial = sqrt(X^2 + Y^2)/125, depth = -Z/125) %>% mutate(depth = depth - min(synapses$depth))

roiMeshPtsNewCoord = roiMeshPtsRot %>% mutate(radial = sqrt(X^2 + Y^2)/125, depth = -Z/125) %>% mutate(depth = depth - min(synapses$depth))

synapses = synapses %>% mutate(depth = depth - min(depth))

```

Generate outline of EB slice.
```{r}
# get outline
meshOutline <- ahull(x=roiMeshPtsNewCoord$depth,y=roiMeshPtsNewCoord$radial,alpha=100/125)
outline = data.frame(meshOutline$arcs)

```

Discretize space and calculate mean electrotonic and raw distances in each bin.
```{r, warning = FALSE}

xmax = ceiling(max(synapses$depth))
ymax = ceiling(max(synapses$radial))
dx = 0.75
dy = 0.75
sampsx = seq(dx,xmax-dx,2*dx)
sampsy = seq(dy,ymax-dy,2*dy)
meanNormEDist = data.frame(x = rep(sampsx, times = length(sampsy)), y = rep(sampsy, each = length(sampsx)))
zE = rep(NA, length(meanNormEDist$x))
zR = rep(NA, length(meanNormEDist$x))
for(i in seq(1,length(meanNormEDist$x))){
  d = meanNormEDist$x[i]
  r = meanNormEDist$y[i]
  zE[i] = mean(synapses$normEDist[(synapses$radial < r + dx) & (synapses$radial >= r - dx) & (synapses$depth < d + dx) & (synapses$depth >= d - dx)])
  zR[i] = mean(synapses$distToRoot[(synapses$radial < r + dx) & (synapses$radial >= r - dx) & (synapses$depth < d + dx) & (synapses$depth >= d - dx)])
}

meanNormEDist = cbind(meanNormEDist, zE)
meanNormEDist = cbind(meanNormEDist, zR)

```

Figure 12C (left) or Figure 12 supplement 3A (top) - density of synapses with mean electotonic distance
```{r}

depthVRadDensPlot = ggplot() +
  stat_density_2d(data = filter(synapses, prepost == 1), aes(x = depth, y = radial, alpha = stat(nlevel)), fill = 'grey', bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  geom_contour(data = meanNormEDist, aes(x = x, y = y, z = zE, color = stat(level))) +
  scale_colour_gradientn(colours = rev(brewer.pal(9,"Blues")), breaks=c(0,1), limits=c(0, 1)) +
  theme_paper() +
  coord_fixed(ratio = 1) +
  geom_point(data = rootPtsNewCoord, aes(y = radial, x = depth), color = '#5A5156', alpha = 0.75)

if(savePlot){
ggsave(paste('depthVsRadial_', nronType, '_ED.pdf', sep = ""), plot = depthVRadDensPlot, device='pdf', path = "plots", scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}

```

Figure 12 supplement 1D - density of synapses with mean raw distance along arbor
```{r}

depthVRadDensPlot = ggplot() +
  stat_density_2d(data = filter(synapses, prepost == 1), aes(x = depth, y = radial, alpha = stat(nlevel)), fill = 'grey', bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  geom_contour(data = meanNormEDist, aes(x = x, y = y, z = zR, color = stat(level))) +
  scale_colour_gradientn(colours = rev(brewer.pal(9,"Blues"))) +
  theme_paper() +
  coord_fixed(ratio = 1) +
  geom_point(data = rootPtsNewCoord, aes(y = radial, x = depth), color = '#5A5156', alpha = 0.75)

if (savePlot){
ggsave(paste('depthVsRadial_', nronType, '_RD.pdf', sep = ""), plot = depthVRadDensPlot, path = "plots", device='pdf', scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}

```

Figure 12C (right) and Figure 12 supplement 3A (bottom) - synapse densities grouped by modality
```{r}
depthVRadMod = ggplot(filter(synapses, prepost == 1, modality %in% c('motor','ms','cv','iv','sleep'))) +
  stat_density_2d(aes(x = depth, y = radial, fill = modality, alpha = stat(nlevel)), bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  scale_fill_manual(values = modalityCMap) +
  theme_paper() +
  coord_fixed(ratio = 1)

if(savePlot){
ggsave(paste('depthVsRadial_modalities_',nronType,'.pdf', sep = ""), plot = depthVRadMod, device='pdf', path = "plots", scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}


```

Figure 12 supplement 1A - synapse densities grouped by modality, plotted separately
```{r}
depthVRadMod = ggplot(filter(synapses, prepost == 1, modality %in% c('motor'))) +
  stat_density_2d(aes(y = radial, x = depth, fill = modality, alpha = stat(nlevel)), bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  scale_fill_manual(values = modalityCMap[3]) +
  theme_paper() +
  coord_fixed(ratio = 1)

if(savePlot){
ggsave(paste('depthVsRadial_modalities_',nronType,'_motor.pdf'), plot = depthVRadMod, device='pdf', path = "plots", scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}

depthVRadMod = ggplot(filter(synapses, prepost == 1, modality %in% c('ms'))) +
  stat_density_2d(aes(y = radial, x = depth, fill = modality, alpha = stat(nlevel)), bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  scale_fill_manual(values = modalityCMap[4]) +
  theme_paper() +
  coord_fixed(ratio = 1)

if(savePlot){
ggsave(paste('depthVsRadial_modalities',nronType,'_ms.pdf'), plot = depthVRadMod, device='pdf', path = "plots", scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}

depthVRadMod = ggplot(filter(synapses, prepost == 1, modality %in% c('iv'))) +
  stat_density_2d(aes(y = radial, x = depth, fill = modality, alpha = stat(nlevel)), bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  scale_fill_manual(values = modalityCMap[2]) +
  theme_paper() +
  coord_fixed(ratio = 1)

if(savePlot){
ggsave(paste('depthVsRadial_modalities',nronType,'_iv.pdf'), plot = depthVRadMod, device='pdf', path = "plots", scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}

depthVRadMod = ggplot(filter(synapses, prepost == 1, modality %in% c('cv'))) +
  stat_density_2d(aes(y = radial, x = depth, fill = modality, alpha = stat(nlevel)), bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  scale_fill_manual(values = modalityCMap[1]) +
  theme_paper() +
  coord_fixed(ratio = 1)

if(savePlot){
ggsave(paste('depthVsRadial_modalities',nronType,'_cv.pdf'), plot = depthVRadMod, device='pdf', path = "plots", scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}

depthVRadMod = ggplot(filter(synapses, prepost == 1, modality %in% c('sleep'))) +
  stat_density_2d(aes(y = radial, x = depth, fill = modality, alpha = stat(nlevel)), bins = 40, contour_var = 'ndensity', geom = 'polygon')+
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) +
  scale_fill_manual(values = modalityCMap[5]) +
  theme_paper() +
  coord_fixed(ratio = 1)

if(savePlot){
ggsave(paste('depthVsRadial_modalities',nronType,'_sleep.pdf'), plot = depthVRadMod, device='pdf', path = "plots", scale = 1.5, width = 7, height = 7, units ="cm", dpi = 600, limitsize = TRUE)
}


```

