---
title: "Analysis of anterior visual pathway: Connectivity graphs in the AOTU (Figure 6C) and BU (Figure 8B)"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

#Analysis of anterior visual pathway: Normalized synapse densities and related visualizations
This notebook shows how to generate normalized synapse densitites and related plots for various types in the EB using three types of projections.The specific plots and corresponding figures are listed below.Note that the ROI outlines will have additional lines that indicate the inner boundaries of the meshes from which the outlines are constructed. We removed those inner outlines in Adobe illustrator.

2D histograms (see section 3a below)
* Figure 10 B (ER4m)
* Figure 10 figure supplement 1 (ring neurons)
* Figure 10 figure supplement 2 (columnar neurons)
* Figure 10 figure supplement 3 (ExR neurons)

Normalized synapse density plots in slices through the EB (see section 3b)
* Figure 10 C-E
* Figure 10 figure supplement 4


```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(neuprintrExtra)
library(gridExtra)
library(alphahull)
library(hexbin)
library(matlib)
library(dplyr)
library(paletteer)
require(RColorBrewer)
library(cowplot)

options(nat.plotengine = 'rgl')
source(file.path("..","R","SynapsePCAUtils.R"))
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```

### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots".
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

## Get some synapse locations
Choose ROI and get curated list of neurons.
See below for how to 
* Figure 10 B, C, Figure 10 -- figure supplement 1: set neuronSelection = "ring"
* Figure 10 D, Figure 10 figure supplement 2: set neuronSelection = "columnar"
* Figure 10 E, Figure 10 figure supplement 3: set neuronSelection = "ExR"

```{r message=FALSE, warning=FALSE}
myROI = "EB"
neuronSelection = "ring" # {"ring","columnar","ExR"}

if (neuronSelection == "ring"){
  saveName = paste0("ER_in_", myROI)
  my_types = paste0("ER",seq(1,6))
}else if (neuronSelection == "columnar"){
  saveName = paste0("Columnar_in_", myROI)
  my_types = c("EL","EPG","EPGt","PEG","PEN_a","PEN_b")
} else if (neuronSelection == "ExR"){
  saveName = paste0("ExR_in_", myROI)
  my_types = c("ExR")
}
```

```{r}
my_types = paste0(my_types, ".*")
my_neurons = getBodyIdsForList(my_types)

# Generate color map
cmapNames = c("RingNeurons", "TuBus", "columnar",  "ExR_and_AOTU46")
myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))
if(length(cmapNames) > 1){
  for(cmapName in cmapNames[2:length(cmapNames)]){ 
    tmp = read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
    myColorMap <- full_join(myColorMap[c("Type", "Simpletype", "hex")], tmp[c("Type", "Simpletype","hex")])
    }
}
```

...use this list to get synapse locations
```{r}
my_synapses = neuprint_get_synapses(as.numeric(getBodyIdsForList(my_types)$bodyid),myROI)

my_synapses = my_synapses %>% mutate(
name=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["name"]],
type=neuprint_get_meta(as.numeric(bodyid), all_segments = TRUE)[["type"]],
partnerName=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["name"]],
partnertype=neuprint_get_meta(as.numeric(partner), all_segments = TRUE)[["type"]])
```


## (1) Import of ROI meshes and get vertices in x,y,z
```{r}
roiMesh = neuprint_ROI_mesh(myROI)
roiMeshPts = data.frame(dotprops(roiMesh)$points)
names(roiMeshPts) <- c("x","y","z")
```


## (2) Find convenient coordinate system based on PCA of vertices and center of mass of the ROI
***Transform mesh  and synapse locations***
```{r}
#Synapse locations
synPts = data.frame(x=as.numeric(my_synapses$x),
                    y=as.numeric(my_synapses$y),
                    z=as.numeric(my_synapses$z))

#define new origin from roi center of mass
origin = getCOM(roiMeshPts)

#reset orgin
roiMeshPts = resetOrigin(roiMeshPts, origin)
synPts = resetOrigin(synPts, origin)

#get eigenvectors and change basis of roi mesh and synapse locations
roiEigen = covPCA(roiMeshPts)
roiMeshPtsRot = changeBasis(roiMeshPts, roiEigen)
synPtsRot = changeBasis(synPts, roiEigen)

```

***Use EV coordinates and rotate for get "intuitive" view***
```{r}
rot =  c(0,0,180)
flip = c(1,-1, 1)

roiMeshPtsPlane <- rotatePoints(roiMeshPtsRot$X,roiMeshPtsRot$Y,roiMeshPtsRot$Z, rot, flip)
synPtsPlane <- rotatePoints(synPtsRot$X,synPtsRot$Y,synPtsRot$Z, rot, flip)

synPtsPlane <- synPtsPlane %>% mutate( type = as.factor(my_synapses$type), 
                                       partnerType = as.factor(my_synapses$partnertype),
                                       name = as.factor(my_synapses$name), 
                                       partnerName = as.factor(my_synapses$partnerName),
                                       id = as.factor(my_synapses$bodyid),
                                       partnerid = as.factor(my_synapses$partner),
                                       prepost = as.factor(my_synapses$prepost))
#Add simple type name
synPtsPlane = synPtsPlane %>% mutate(simpleType = gsub("_.*", "",type))
```

```{r}
# generate color map
synCount = synPtsPlane %>% count(type)
typeFilter = synCount$type[synCount$n > 10]
dataFilt = synPtsPlane %>% filter(type %in% typeFilter)

myTypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$simpleType)) %>% filter(Simpletype == "yes")
myTypeCols = myTypeCols[match(as.character(unique(dataFilt$simpleType)), myTypeCols$Type),] %>%
  arrange(unique(dataFilt$simpleType))

mySubtypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$type)) %>% filter(Simpletype == "no")
mySubtypeCols = mySubtypeCols[match(as.character(unique(dataFilt$type)), mySubtypeCols$Type),] %>%
  arrange(unique(dataFilt$type))
```

***Collapse along EB ring***
Compute angle of vectors to each point relative to x-axis
```{r}
syn_ang = numeric(length(synPtsPlane$x))
syn_dist = numeric(length(synPtsPlane$x))
for (i in seq(1,length(synPtsPlane$x))) {
  syn_ang[i] = angle(as.numeric(synPtsPlane[i,1:2]), c(0,-1))
  syn_dist[i] = sqrt(sum(synPtsPlane[i,1:2] * synPtsPlane[i,1:2]))
  if (synPtsPlane[i,1] < 0){
    syn_ang[i] = 360-syn_ang[i]
  }
}

synPtsPlane$angle = syn_ang
synPtsPlane$dist = syn_dist
```

```{r}
roi_dist = numeric(length(roiMeshPtsPlane$x))
roi_ang = numeric(length(roiMeshPtsPlane$x))
for (i in seq(1,length(roiMeshPtsPlane$x))) {
  roi_dist[i] = sqrt(sum(roiMeshPtsPlane[i,1:2] * roiMeshPtsPlane[i,1:2]))
  roi_ang[i] = angle(as.numeric(roiMeshPtsPlane[i,1:2]), c(0,-1))
  if (roiMeshPtsPlane[i,1] < 0){
    roi_ang[i] = 360-roi_ang[i]
  }
}
roiMeshPtsPlane$dist = roi_dist
roiMeshPtsPlane$angle = roi_ang
roiMeshPtsPlane = roiMeshPtsPlane %>%  mutate(angleGroup = cut(angle, breaks=c(-0, 1/8*360 ,2/8*360, 3/8*360, 1/2*360 ,5/8*360, 6/8*360, 7/8*360, 360), labels=c("1","2","3","4","5","6","7","8")))

```

## (3) Plot distributions
```{r}
#Helper plotting function
styleDensity2Dhist <- function(synDens, Cmax, roioutline){
  synDens <- synDens +
    scale_fill_gradientn(colours = brewer.pal(5,"BuPu"), breaks=c(0,Cmax), limits=c(0, Cmax), oob = scales::squish) +
    coord_fixed(ratio = 1) + theme_void() + guides(color=FALSE) +
    geom_path(data=roioutline, aes(x=c1, y=c2), size = 0.5)
    return(synDens)
}
```

### Generate mesh outlines for different orientations
```{r}
alphaval = 150

meshOutline <- ahull(x=roiMeshPtsPlane$x,y=roiMeshPtsPlane$y,alpha=alphaval)
outline_xy = data.frame(meshOutline$arcs)

meshOutline <- ahull(x=roiMeshPtsPlane$z,y=roiMeshPtsPlane$y,alpha=alphaval)
outline_zy = data.frame(meshOutline$arcs)

meshOutline <- ahull(x=roiMeshPtsPlane$z,y=roiMeshPtsPlane$dist,alpha=alphaval)
outline_slice = data.frame(meshOutline$arcs)

```

### (3a) 2D histograms
```{r}
nbins = 60
ncolumns_xy = 6
ncolumns_zy = 8
ncolumns_slice = 8

plotW = 22
plotH = 12

# front view (xy)
Cmax = 100
synprojFront <- ggplot() + geom_hex(data=dataFilt, aes(x=x, y=y), bins=nbins)
synprojFront <- styleDensity2Dhist(synprojFront, Cmax,outline_xy) + facet_wrap(~type, ncol=ncolumns_xy)
print(synprojFront)

# side view (zy)
Cmax = 160
synprojSide <- ggplot() + geom_hex(data=dataFilt, aes(x=z, y=y), bins=nbins) 
synprojSide <-  styleDensity2Dhist(synprojSide, Cmax,outline_zy) + facet_wrap(~type, ncol=ncolumns_zy)
print(synprojSide)

# slice view (radial-axial)
Cmax = 300
synprojSlice <- ggplot() + geom_hex(data=dataFilt, aes(x=z, y=syn_dist), bins=nbins/2)
synprojSlice <- styleDensity2Dhist(synprojSlice, Cmax,outline_slice) + facet_wrap(~type, ncol=ncolumns_slice)
print(synprojSlice)

if (savePlot){
  ggsave( paste("synapse2DHist_",saveName,'_front.pdf', sep=''), plot = synprojFront, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
  ggsave( paste("synapse2DHist_",saveName,'_side.pdf', sep=''), plot = synprojSide, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
  ggsave( paste("synapse2DHist_",saveName,'_slice.pdf', sep=''), plot = synprojSlice, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}
```

### 2D densitiy distributions
```{r}
plotW = 12
plotH =  12
levelBins = 4

# types
synprojSlice = ggplot() + 
  stat_density_2d_filled(data = dataFilt, aes(x=z, y=syn_dist, fill=type,alpha = ..nlevel..),
                         bins=levelBins,contour_var = "ndensity", geom = "polygon") +
  scale_alpha(range=c(0,1)) + coord_fixed(ratio = 1) + theme_void() +
  scale_fill_manual(values = as.character(mySubtypeCols$hex), name="type") +
  guides(fill=guide_legend(ncol=2)) 
synprojSlice = synprojSlice + geom_path(data=outline_slice, aes(x=c1, y=c2), size = 0.5)
synprojSlice
if (savePlot){
  ggsave( paste("synapseDistributions_",saveName,'_slice_byType.pdf', sep=''), plot = synprojSlice, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}

# simple types (grouping similar neuron types)
synprojSlice = ggplot() + 
  stat_density_2d_filled(data = dataFilt, aes(x=z, y=syn_dist, fill=simpleType,alpha = ..nlevel..),
                         bins=levelBins,contour_var = "ndensity", geom = "polygon") +
  scale_alpha(range=c(0,1)) + coord_fixed(ratio = 1) + theme_void() +
  scale_fill_manual(values = as.character(myTypeCols$hex), name="type") +
  guides(fill=guide_legend(ncol=1)) 

synprojSlice = synprojSlice + geom_path(data=outline_slice, aes(x=c1, y=c2), size = 0.5)
synprojSlice
if (savePlot){
  ggsave( paste("synapseDistributions_",saveName,'_slice_bySimpletype.pdf', sep=''), plot = synprojSlice, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}
```

Split into quadrants
```{r}
dataFilt = dataFilt %>% mutate(angleGroup = cut(angle, breaks=c(-0, 1/8*360 ,2/8*360, 3/8*360, 1/2*360 ,5/8*360, 6/8*360, 7/8*360, 360), labels=c("1","2","3","4","5","6","7","8")))

# get outline 
outline = data.frame()
for (i in unique(roiMeshPtsPlane$angleGroup)) {
  roiMeshPtsPlaneSub = roiMeshPtsPlane %>% filter(angleGroup == i)
  meshOutline <- ahull(x=roiMeshPtsPlaneSub$z,y=roiMeshPtsPlaneSub$dist,alpha=300)
  outlineGroup = data.frame(meshOutline$arcs) %>% mutate(angleGroup = i)
  outline = bind_rows(outline,outlineGroup)
}
```

```{r}
# simple types (grouping similar neuron types)
synprojSlice = ggplot() + 
  stat_density_2d_filled(data = dataFilt, aes(x=z, y=syn_dist, fill=simpleType,alpha = ..nlevel..),
                         bins=levelBins,contour_var = "ndensity", geom = "polygon") + 
  scale_alpha(range=c(0,1)) + coord_fixed(ratio = 1) + theme_void() +
  scale_fill_manual(values = as.character(myTypeCols$hex), name="type") +
  facet_wrap( ~ angleGroup,  ncol=4) +
  theme_cowplot(font_size=7,font_family="sans",rel_small=6/7,rel_tiny = 5/7,rel_large = 12/7, line_size = 0.5*mm2pt) +
  geom_path(data=outline, aes(x=c1, y=c2), size = 0.5) + guides(fill=guide_legend(ncol=1))
print(synprojSlice)

ggsave( paste("synapseDistributions_",saveName,'_slice_splitRad.pdf', sep=''), plot = synprojSlice, device='pdf', path = "plots",
    scale = 1.5, width = 13, height = 6, units ="cm", dpi = 600, limitsize = TRUE)
```

###Color code by region (Ring neurons only)
This plot corresponds to figure 10 Cii
```{r}
myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapNames[1],".csv")))

myTypeCols = myColorMap %>% filter(Type %in% unique(dataFilt$simpleType)) %>% filter(Simpletype == "yes")
myTypeCols = myTypeCols[match(as.character(unique(dataFilt$simpleType)), myTypeCols$Type),] %>%
  arrange(unique(dataFilt$simpleType))

regiondata = left_join(dataFilt, myTypeCols[c("Type","regions","hex")], by = c("simpleType" = "Type"))

synprojSlice = ggplot() + 
  stat_density_2d_filled(data = regiondata, aes(x=z, y=syn_dist, fill=regions,alpha = ..nlevel..),
                         bins=levelBins,contour_var = "ndensity", geom = "polygon") +
  scale_alpha(range=c(0,1)) + coord_fixed(ratio = 1) + theme_void() +
  scale_fill_manual(values = paletteer_d("basetheme::brutal", length(unique(myTypeCols$regions)))) + 
  guides(fill=guide_legend(ncol=2)) 
synprojSlice = synprojSlice + geom_path(data=outline_slice, aes(x=c1, y=c2), size = 0.5)
synprojSlice
if (savePlot){
  ggsave( paste("synapseDistributions_",saveName,'_slice_byRegion.pdf', sep=''), plot = synprojSlice, device='pdf',
          path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}
```
