---
title: "Analysis of connectivity in the ellipsoid body (EB): Connectivity of ER and collumnar neurons"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

#Analysis of connectivity in the ellipsoid body (EB): Connectivity of ER and collumnar neurons (Figure 13B)

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```

### Make selection of neurons to be used in connecitivy analysis
This should be done based on some broadly used criteria. Alternatively, one could read in previously curated lists of neurons.
```{r}
ROI = "EB"
slctROI ="EB"# "EB"#LAL(-GA)

saveName = paste0("EPG_with_RN",slctROI) #RN_TB_ExR #RN_ExR_col_in_ EPG-EL_with_RN

neuron1 = c("EPG", "EL")
neuron1 = paste0(neuron1,".*")
neuronName1 = "EPG-EL"#"columnar"
IDs1 = getBodyIdsForList(neuron1)

# group 2
neuron2 = c(paste0("ER",seq(6)))
neuron2 = paste0(neuron2,".*")
neuronName2 = "ER"
IDs2 = getBodyIdsForList(neuron2)

cmapName = "RingNeurons"
myColorMap <- read.csv(file.path("..","colormaps",paste0("colorMap_",cmapName,".csv")))
```

#### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

### Get connectivity table
```{r}
getT2Ttable <- function(preIDs, postIDs){
  myConnections = getConnectionTable(preIDs$bodyid, "POST", slctROI)
  myConnections = myConnections %>% filter(to %in% postIDs$bodyid) 
  typesTable <- getTypesTable(unique(myConnections$databaseType.to))
  
  myConnectionsT2T = getTypeToTypeTable(myConnections,typesTable = typesTable)
}
```

```{r, warning=FALSE}
myConnections_1to2_full = getT2Ttable(IDs1,IDs2)
myConnections_2to1_full = getT2Ttable(IDs2,IDs1)
```

```{r}
myConnections_1to2 = myConnections_1to2_full %>% select(c(type.from, type.to, weightRelative, weight)) %>% 
  rename(c(type1 = type.from, type2 = type.to)) %>% mutate(dir = paste("to",neuronName2)) %>%
  group_by(dir, type1) %>% mutate(normRelWeight = weightRelative/sum(weightRelative))
myConnections_2to1 = myConnections_2to1_full %>% select(c(type.from, type.to, weightRelative, weight)) %>% 
  rename(c(type2 = type.from, type1 = type.to)) %>% mutate(dir = paste("from",neuronName2)) %>%
  group_by(dir, type1) %>% mutate(normRelWeight = weightRelative/sum(weightRelative))
```

### Connectivity matrix
```{r}
myConnections = bind_rows(myConnections_2to1,myConnections_1to2)
plotW = 19 #24#25# 45 # 20
plotH = 5 #4 #40  #17
cmax = max(myConnections[["weightRelative"]]) #0.48

myConTab = myConnections  %>% 
  ungroup() %>% mutate(plotWeight = myConnections[["weightRelative"]]) %>% 
  filter(type1 %in% c("EPG", "EL"))

conmatPlot = ggplot(myConTab) + 
  geom_tile(aes(type2,dir,fill=plotWeight)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.5*cmax, limits=c(0,cmax)) +
  facet_grid(rows=vars(type1))

conmatPlot = conmatPlot +
    xlab("Post-synaptic neuron")+ylab("Pre-synaptic neuron") + labs(fill="weightRelative") +
    labs(title=paste(neuronName1,'to', neuronName2, 'Connectivity within', slctROI, sep=' ')) +
    theme(text = element_text(size=9), axis.line = element_line(colour = 'black', size = .3))

print(conmatPlot)

if (savePlot){
  ggsave( paste("typeConmarison_matrix_",saveName,'_in_',slctROI,'_weightRelative.pdf', sep=''), plot = conmatPlot,
          device='pdf', path = "plots", scale = 1, width = plotW, height = plotH, units ="cm", dpi = 600, limitsize = TRUE)
}

```


```{r}
library("paletteer")
myTypeCMap = myColorMap %>% filter(Simpletype == "no")
myConnections_regionInfo = left_join(myConTab, myTypeCMap, by=c("type2" = "Type")) %>% mutate()

plotW = 7#10
plotH = 8

bargraph_wr <- ggplot(data = myConnections_regionInfo) + 
  geom_bar(aes(y = weightRelative, x = type1, fill = type2), stat="identity") + 
  facet_grid(cols=vars(dir)) + scale_fill_manual(values = c(as.character(myTypeCMap$hex))) +
  theme_classic() + theme(text = element_text(size=9), axis.line = element_line(colour = 'black', size = .3)) +
  xlab("")+ylab("Relative weight") + labs(fill="Partner type") + guides(fill=guide_legend(ncol=2))

print(bargraph_wr)
  
bargraph_nwr <- ggplot(data = myConnections_regionInfo) + 
  geom_bar(aes(y = normRelWeight, x = type1, fill = type2), stat="identity") + 
  facet_grid(cols=vars(dir)) + scale_fill_manual(values = c(as.character(myTypeCMap$hex))) +
  theme_classic() + theme(text = element_text(size=9), axis.line = element_line(colour = 'black', size = .3)) +
  xlab("")+ylab("Normalized relative weight") + labs(fill="Partner type") + guides(fill=guide_legend(ncol=2))

print(bargraph_nwr)

if (savePlot){
  ggsave( paste("typeConmarison_bar_",saveName,'_in_',slctROI,'_norm_weightRelative.pdf', sep=''), plot = bargraph_nwr, device='pdf',
          path = "plots", scale = 1.5, width = plotW*0.8, height = plotH*0.8, units ="cm", dpi = 600, limitsize = TRUE)
}
```

```{r}
bargraph_wr <- ggplot(data = myConnections_regionInfo) + 
  geom_bar(aes(y = weightRelative, x = type1, fill = regions), stat="identity") + 
  facet_grid(cols=vars(dir)) + 
  scale_fill_manual(values = paletteer_d("Polychrome::kelly",n=length(unique(myColorMap$regions)))) +
  theme_classic() + theme(text = element_text(size=9), axis.line = element_line(colour = 'black', size = .3)) +
  xlab("")+ylab("Relative weight") + labs(fill="Partner type")

print(bargraph_wr)
  
bargraph_nwr <- ggplot(data = myConnections_regionInfo) + 
  geom_bar(aes(y = normRelWeight, x = type1, fill = regions), stat="identity") + 
  facet_grid(cols=vars(dir)) + 
  scale_fill_manual(values = paletteer_d("Polychrome::kelly",n=length(unique(myColorMap$regions)))) +
  theme_classic() + theme(text = element_text(size=9), axis.line = element_line(colour = 'black', size = .3)) +
  xlab("")+ylab("Normalized relative weight") + labs(fill="Partner type")

print(bargraph_nwr)
```