---
title: "EB Columnar Figure"
output: html_notebook
---

Load the functions
```{r}
library(neuprintr)
library(tidyverse)
library(cowplot)
library(neuprintrExtra)
library(reshape2)
library(patchwork)
library(ggnewscale)
library(gridExtra)
source("EBUtils.R")
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))
```


Get the connection matrix between the EPGs, PEN_as, PEN_bs, and PEGs in the EB
```{r}
neurons <- c("EPG","PEG","PEN_a(PEN1)","PEN_b(PEN2)")

EBColConTab <- getConnectionTable(getTypesTable(neurons)$bodyid,
                                  "POST","EB")
EBColConTab <- EBColConTab %>% filter(type.to %in% neurons)
```

Plot the connectivity table, sorting the neurons by either their EB position or by their PB glomeruli
```{r}
neuropil <- c("EB","PB")

# Create a list to hold the plots
plts <- list()

# Sort by the EB or PB and plot
for (n in 1:length(neuropil)){
  EBColConTab$nameOrder.from <- EBGlomOrder(EBColConTab$name.from,EBColConTab$from, neuropil[n])
  EBColConTab$nameOrder.to <- EBGlomOrder(EBColConTab$name.to,EBColConTab$to, neuropil[n])
  
  # Specify the order of the neuron types on the axes
  plotOrder <- c("EPG","PEN1","PEN2","PEG")
  fromLevelsOld <- levels(EBColConTab$nameOrder.from)
  fromLevelsNew <-  c()
  toLevelsOld <- levels(EBColConTab$nameOrder.to)
  toLevelsNew <-  c()
  for (p in 1:length(plotOrder)){
    fromLevelsNew <- fromLevelsNew %>%
      append(fromLevelsOld[which(grepl(paste0(plotOrder[p],'_'),fromLevelsOld))])
    toLevelsNew <- toLevelsNew %>%
      append(toLevelsOld[which(grepl(paste0(plotOrder[p],'_'),toLevelsOld))])
  }
  EBColConTab$nameOrder.from <- factor(EBColConTab$nameOrder.from,fromLevelsNew)
  EBColConTab$nameOrder.to <- factor(EBColConTab$nameOrder.to,toLevelsNew)
  
  # Plot the connectivity matrix
  conmatPlot <- plotConnectivityMatrix(EBColConTab, byGroup = "id_sort") + 
    coord_equal(ratio=1) + xlab("postsynaptic neuron") + ylab("presynaptic neuron") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
    guides(fill = guide_colourbar(title = 'relative weight', direction = 'horizontal', title.position = 'top', barheight = 0.5)) +
    ggtitle(neuropil[n])
  
  # Add lines to divide the cell types
  offset <- 0.5
  types <- c("EPG","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
  for (t in 1:length(types)){
    numNrons <- nrow(EBColConTab %>% filter(type.from == types[t]) %>% select(nameOrder.from) %>% unique())
    offset <- offset + numNrons
    conmatPlot <- conmatPlot + geom_hline(yintercept = offset)
  }
  
  offset <- 0.5
  types <- c("EPG","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
  for (t in 1:length(types)){
    offset <- offset + nrow(EBColConTab %>% filter(type.to == types[t]) %>% select(nameOrder.to) %>% unique())
    conmatPlot <- conmatPlot + geom_vline(xintercept = offset)
  }
  
  plts[[n]] <- conmatPlot
}
```
```{r}
print(plts[[1]] / plts[[2]] + plot_layout(guides = 'collect'))
```


Get the connection matrix between the EPGs, PEN_as, PEN_bs, and PEGs in the PB
```{r}
neurons = c("EPG","PEG","PEN_a(PEN1)","PEN_b(PEN2)")

PBColConTab <- getConnectionTable(getTypesTable(neurons)$bodyid,
                                  "POST","PB")
PBColConTab <- PBColConTab %>% filter(type.to %in% neurons)
PBColConTab$nameOrder.from <- EBGlomOrder(PBColConTab$name.from,PBColConTab$from,"PB")
PBColConTab$nameOrder.to <- EBGlomOrder(PBColConTab$name.to,PBColConTab$to,"PB")
```

Plot the connectivity matrix
```{r}
# Specify the order of the neuron types on the axes
plotOrder <- c("EPG","PEN1","PEN2","PEG")
fromLevelsOld <- levels(PBColConTab$nameOrder.from)
fromLevelsNew <-  c()
toLevelsOld <- levels(PBColConTab$nameOrder.to)
toLevelsNew <-  c()
for (p in 1:length(plotOrder)){
  fromLevelsNew <- fromLevelsNew %>%
    append(fromLevelsOld[which(grepl(paste0(plotOrder[p],'_'),fromLevelsOld))])
  toLevelsNew <- toLevelsNew %>%
    append(toLevelsOld[which(grepl(paste0(plotOrder[p],'_'),toLevelsOld))])
}
PBColConTab$nameOrder.from <- factor(PBColConTab$nameOrder.from,fromLevelsNew)
PBColConTab$nameOrder.to <- factor(PBColConTab$nameOrder.to,toLevelsNew)

#Remove singular EPG to EPG connections
PBColConTab <- PBColConTab %>% filter(type.to != 'EPG' & type.from == 'EPG')

#Plot
conmatPlot <- plotConnectivityMatrix(PBColConTab, byGroup = "id_sort") + 
    coord_equal(ratio=1) + xlab("postsynaptic neuron") + ylab("presynaptic neuron") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
    guides(fill = guide_colourbar(title = 'relative weight', direction = 'horizontal', title.position = 'top', barheight = 0.5)) +
    ggtitle("PB")

offset <- 0.5
types <- c("EPG","EPGt","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
for (t in 1:length(types)){
  numNrons <- nrow(PBColConTab %>% filter(type.from == types[t]) %>% select(nameOrder.from) %>% unique())
  offset <- offset + numNrons
  conmatPlot <- conmatPlot + geom_hline(yintercept = offset)
}

offset <- 0.5
types <- c("EPG","EPGt","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
for (t in 1:length(types)){
  offset <- offset + nrow(PBColConTab %>% filter(type.to == types[t]) %>% select(nameOrder.to) %>% unique())
  conmatPlot <- conmatPlot + geom_vline(xintercept = offset)
}

print(conmatPlot)
```


Plot a force network of the EPG and PEN1 connections
First, get the connectivity tables
```{r}
nrons <- c("EPG","PEN_a(PEN1)")
EBColBag <- neuronBag(getTypesTable(nrons))
EBCol_CT <- EBColBag$outputs_raw %>% 
  filter(type.to %in% nrons,
         roi %in% c("PB","EB"))
EBCol_CT$nameOrder.from <- EBGlomOrder(EBCol_CT$name.from,EBCol_CT$from,"EB")
EBCol_CT$nameOrder.to <- EBGlomOrder(EBCol_CT$name.to,EBCol_CT$to,"EB")
```

Now, convert it into an igraph function
```{r}
library(igraph)
library(ggraph)

# Set up the graph nodes
EBColNodes <- c(as.character(EBCol_CT$nameOrder.to),as.character(EBCol_CT$nameOrder.from)) %>% unique() %>% as.data.frame()
colnames(EBColNodes) <- "nodes"
EBColNodes$supertype <- EBColNodes$nodes %>% sapply(function(n) substring(n,1,gregexpr("_L|_R",n)[[1]][1]+1))
EBColNodes$label <- EBColNodes$nodes %>% sapply(function(n) substring(n,gregexpr("_L|_R",n)[[1]][1]+1,gregexpr("_L|_R",n)[[1]][1]+2))

# Set up the graph edges
EBColEdges <- EBCol_CT %>% mutate(from = nameOrder.from, to = nameOrder.to, weight = ROIweight) %>%
  select(from,to,weight)
EBColEdges$supertype.from <- EBColEdges$from %>% as.character() %>% sapply(function(n) substring(n,1,gregexpr("_L|_R",n)[[1]][1]+1))

# Make the graph
g <- graph_from_data_frame(EBColEdges, directed = TRUE, vertices = EBColNodes)

# Assign colors to the supertypes
colBreaks = c("EPG_L","EPG_R","PEN1_L","PEN1_R","EPGt_L","EPGt_R")
colPal = c("purple","purple4","red","skyblue","mediumpurple","mediumpurple4")
sTScale <- scale_colour_manual(values=colPal,breaks = colBreaks)
sTScale_edge <- scale_edge_colour_manual(values=colPal,breaks = colBreaks, guide = FALSE)

# Plot it
EBColForceGraph <- ggraph(g) +
  geom_edge_fan(aes(width=weight,color=supertype.from),alpha=0.5,
                      strength=1,
                      end_cap = circle(0.2, 'cm')) + 
  geom_edge_loop(aes(direction=45,span=90,width=weight,color=supertype.from,strength=1),alpha=0.5) +
  geom_node_point(aes(color=supertype),size=4) + 
  scale_edge_width(range = c(0, 2)) +
  sTScale_edge +
  sTScale +
  geom_node_text(aes(label=EBColNodes$label)) +
  theme_paper() +
  coord_fixed(ratio = 1,clip="off") + 
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank())

print(EBColForceGraph)
```


Look at the differing connectivity between PEN1s and PEN2s - PB
```{r}
neurons = c("PEN_a(PEN1)","PEN_b(PEN2)")

PBColConTab <- getConnectionTable(getTypesTable(neurons)$bodyid,
                                  "PRE","PB")
PBColConTab <- PBColConTab %>% filter(!is.na(type.from))

T2T_PENs_PB <- getTypeToTypeTable(PBColConTab)

T2T_conmatPlot_PB <- plotConnectivityMatrix(T2T_PENs_PB, byGroup = "type") + 
    coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
    guides(fill = guide_colourbar(title = 'relative weight', direction = 'horizontal', title.position = 'top', barheight = 0.5)) +
    ggtitle("PB")
```
Look at the differing connectivity between PEN1s and PEN2s - EB, PRE
```{r}
neurons = c("PEN_a(PEN1)","PEN_b(PEN2)")

EBColConTab_PRE <- getConnectionTable(getTypesTable(neurons)$bodyid,
                                      "PRE","EB")
EBColConTab_PRE <- EBColConTab_PRE %>% filter(!is.na(type.from))

T2T_PENs_EB_PRE <- getTypeToTypeTable(EBColConTab_PRE)

T2T_conmatPlot_EB_PRE <- plotConnectivityMatrix(T2T_PENs_EB_PRE, byGroup = "type") + 
    coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
    guides(fill = guide_colourbar(title = 'relative weight', title.position = 'left', title.theme = element_text(angle = 90), barwidth = 0.5, title.hjust = 0.5)) +
    ggtitle("EB")
```
Look at the differing connectivity between PEN1s and PEN2s - EB, POST
```{r}
neurons = c("PEN_a(PEN1)","PEN_b(PEN2)")

EBColConTab_POST <- getConnectionTable(getTypesTable(neurons)$bodyid,
                                       "POST","EB")
EBColConTab_POST <- EBColConTab_POST %>% filter(!is.na(type.to))

T2T_PENs_EB_POST <- getTypeToTypeTable(EBColConTab_POST)

T2T_conmatPlot_EB_POST <- plotConnectivityMatrix(T2T_PENs_EB_POST, byGroup = "type") + 
    coord_equal(ratio=1) + xlab("postsynaptic type") + ylab("presynaptic type") + theme_paper() + theme(axis.text.x = element_text(angle=90)) +
    guides(fill = guide_colourbar(title = 'relative weight', direction = 'horizontal', title.position = 'top', barheight = 0.5)) +
    ggtitle("EB")
```

```{r}
PEN1VsPEN2 <- (T2T_conmatPlot_PB + T2T_conmatPlot_EB_PRE) / T2T_conmatPlot_EB_POST
print(PEN1VsPEN2)
```