---
title: "EB Columnar Figure"
output: html_notebook
---


```{r}
library(neuprintr)
library(tidyverse)
library(cowplot)
library(neuprintrExtra)
library(reshape2)
library(patchwork)
library(ggnewscale)
library(gridExtra)
source("C:\\Users\\dantu\\Documents\\neuprintR-notebooks\\EBFigures\\EBUtils.R")
source("C:\\Users\\dantu\\Documents\\neuprintR-notebooks\\R\\paperTheme.R")
```

Specify plotting text sizes
```{r}
update_geom_defaults("text", list(size = 6*0.35))
theme_paper <- function(...){
  theme_cowplot(font_size=7,rel_small=6/7,rel_tiny = 5/7,rel_large = 8/7) + theme(strip.background = element_blank(),...)
  }
```


Get the connection matrix between the EPGs, EPGts, PEN1s, PEN2s, and PEGs in the EB
```{r}
neurons = c("EPG","PEG","PEN_a(PEN1)","PEN_b(PEN2)")

EBColConTab <- getConnectionTable(getTypesTable(neurons)$bodyid,
  "POST",
  "EB")
EBColConTab <- EBColConTab %>% filter(type.to %in% neurons)
EBColConTab$id.from <- EBGlomOrder(EBColConTab$name.from,EBColConTab$from,"EB")
EBColConTab$id.to <- EBGlomOrder(EBColConTab$name.to,EBColConTab$to,"EB")

plotOrder <- c("EPG","PEN1","PEN2","PEG")
fromLevelsOld <- levels(EBColConTab$id.from)
fromLevelsNew <-  c()
toLevelsOld <- levels(EBColConTab$id.to)
toLevelsNew <-  c()
for (p in 1:length(plotOrder)){
  fromLevelsNew <- fromLevelsNew %>%
    append(fromLevelsOld[which(grepl(paste0(plotOrder[p],'_'),fromLevelsOld))])
  toLevelsNew <- toLevelsNew %>%
    append(toLevelsOld[which(grepl(paste0(plotOrder[p],'_'),toLevelsOld))])
}
EBColConTab$id.from <- factor(EBColConTab$id.from,fromLevelsNew)
EBColConTab$id.to <- factor(EBColConTab$id.to,toLevelsNew)

conmatPlot <- ggplot(EBColConTab) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(EBColConTab$weightRelative),
                       limits=c(0,max(EBColConTab$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_cowplot() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,size=4,hjust=1),
        axis.text.y = element_text(size=4)) +
  xlab("post-synaptic neuron") + ylab("pre-synaptic neuron")

offset <- 0.5
types <- c("EPG","EPGt","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
for (t in 1:length(types)){
  numNrons <- nrow(EBColConTab %>% filter(type.from == types[t]) %>% select(id.from) %>% unique())
  offset <- offset + numNrons
  conmatPlot <- conmatPlot + geom_hline(yintercept = offset)
}

offset <- 0.5
types <- c("EPG","EPGt","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
for (t in 1:length(types)){
  offset <- offset + nrow(EBColConTab %>% filter(type.to == types[t]) %>% select(id.to) %>% unique())
  conmatPlot <- conmatPlot + geom_vline(xintercept = offset)
}

print(conmatPlot)
```

```{r}
save_plot('C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\EB\\columnarToColumnar\\EBColConmat-PBOriented.pdf',conmatPlot)
```

Look at the total number of input synapses by PB glom
```{r}
EBColConTab$glomname.from <- sapply(EBColConTab$id.from %>% as.character(),
                                    function(i) strsplit(i,'-')[[1]][1]) %>%
  unlist() %>% as.character()
EBColConTab$num.from <- sapply(EBColConTab$id.from %>% as.character(),
                                    function(i) strsplit(i,'-')[[1]][2]) %>%
  unlist() %>% as.character()
typesFrom <- c("EPG","PEG","PEN_a(PEN1)","PEN_b(PEN2)")
typesTo <- list()
typesTo[[1]] <- c("PEN_a(PEN1)","PEN_b(PEN2)","PEG")
typesTo[[2]] <- c("PEN_b(PEN2)")
typesTo[[3]] <- c("EPG")
typesTo[[4]] <- c("EPG")

g_synsIn <- list()
for (t in 1:length(typesToConsider)){
  g_synsIn[[t]] <- ggplot(EBColConTab %>% filter(type.from == typesFrom[t] & type.to %in% typesTo[[t]])) +
    geom_bar(stat='identity',aes(x = id.to, y = ROIweight, fill=id.from)) +
    theme_cowplot() + theme(axis.text.x = element_text(angle = 90)) + ggtitle(paste0('from ',typesFrom[t]))
  print(g_synsIn[[t]])
}

```

Look at the PB connections
```{r}
neurons = c("EPG","PEG","PEN_a(PEN1)","PEN_b(PEN2)")

PBColConTab <- getConnectionTable(getTypesTable(neurons)$bodyid,
  "POST",
  "PB")
PBColConTab <- PBColConTab %>% filter(type.to %in% neurons)
PBColConTab$id.from <- EBGlomOrder(PBColConTab$name.from,PBColConTab$from,"PB")
PBColConTab$id.to <- EBGlomOrder(PBColConTab$name.to,PBColConTab$to,"PB")

plotOrder <- c("EPG","PEN1","PEN2","PEG")
fromLevelsOld <- levels(PBColConTab$id.from)
fromLevelsNew <-  c()
toLevelsOld <- levels(PBColConTab$id.to)
toLevelsNew <-  c()
for (p in 1:length(plotOrder)){
  fromLevelsNew <- fromLevelsNew %>%
    append(fromLevelsOld[which(grepl(paste0(plotOrder[p],'_'),fromLevelsOld))])
  toLevelsNew <- toLevelsNew %>%
    append(toLevelsOld[which(grepl(paste0(plotOrder[p],'_'),toLevelsOld))])
}
PBColConTab$id.from <- factor(PBColConTab$id.from,fromLevelsNew)
PBColConTab$id.to <- factor(PBColConTab$id.to,toLevelsNew)

PBColConTab <- PBColConTab %>% filter(type.to != 'EPG' & type.from == 'EPG')

conmatPlot <- ggplot(PBColConTab) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(PBColConTab$weightRelative),
                       limits=c(0,max(PBColConTab$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_paper() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,hjust=1)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")

offset <- 0.5
types <- c("EPG","EPGt","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
for (t in 1:length(types)){
  numNrons <- nrow(PBColConTab %>% filter(type.from == types[t]) %>% select(id.from) %>% unique())
  offset <- offset + numNrons
  conmatPlot <- conmatPlot + geom_hline(yintercept = offset)
}

offset <- 0.5
types <- c("EPG","EPGt","PEN_a(PEN1)","PEN_b(PEN2)","PEG")
for (t in 1:length(types)){
  offset <- offset + nrow(PBColConTab %>% filter(type.to == types[t]) %>% select(id.to) %>% unique())
  conmatPlot <- conmatPlot + geom_vline(xintercept = offset)
}

print(conmatPlot)
```

```{r}
ggsave('C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\EB\\columnarToColumnar\\PBColConmat.pdf',
       conmatPlot, width = 4, height = 4)
```

Look at the differing connectivity between PEN1s and PEN2s - PB
```{r}
neurons = c("PEN_a(PEN1)","PEN_b(PEN2)")

PBColConTab <- getConnectionTable(getTypesTable(neurons)$bodyid,
  "PRE",
  "PB")
PBColConTab <- PBColConTab %>% filter(!is.na(type.from))

T2T_PENs_PB <- getTypeToTypeTable(PBColConTab)

T2T_conmatPlot_PB <- ggplot(T2T_PENs_PB) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(T2T_PENs_PB$weightRelative),
                       limits=c(0,max(T2T_PENs_PB$weightRelative))) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) +
  theme_paper() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,hjust=1)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
```
Look at the differing connectivity between PEN1s and PEN2s - EB, PRE
```{r}
neurons = c("PEN_a(PEN1)","PEN_b(PEN2)")

EBColConTab_PRE <- getConnectionTable(getTypesTable(neurons)$bodyid,
  "PRE",
  "EB")
EBColConTab_PRE <- EBColConTab_PRE %>% filter(!is.na(type.from))

T2T_PENs_EB_PRE <- getTypeToTypeTable(EBColConTab_PRE)

T2T_conmatPlot_EB_PRE <- ggplot(T2T_PENs_EB_PRE) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(T2T_PENs_EB_PRE$weightRelative),
                       limits=c(0,max(T2T_PENs_EB_PRE
                                      $weightRelative))) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) +
  theme_paper() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,hjust=1)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
```
Look at the differing connectivity between PEN1s and PEN2s - EB, POST
```{r}
neurons = c("PEN_a(PEN1)","PEN_b(PEN2)")

EBColConTab_POST <- getConnectionTable(getTypesTable(neurons)$bodyid,
  "POST",
  "EB")
EBColConTab_POST <- EBColConTab_POST %>% filter(!is.na(type.to))

T2T_PENs_EB_POST <- getTypeToTypeTable(EBColConTab_POST)

T2T_conmatPlot_EB_POST <- ggplot(T2T_PENs_EB_POST) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(T2T_PENs_EB_POST$weightRelative),
                       limits=c(0,max(T2T_PENs_EB_POST
                                      $weightRelative))) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) +
  theme_paper() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,hjust=1)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
```

```{r}
PEN1VsPEN2 <- (T2T_conmatPlot_PB + T2T_conmatPlot_EB_PRE) / T2T_conmatPlot_EB_POST
ggsave('C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\EB\\columnarToColumnar\\PEN1VsPEN2.pdf',
       PEN1VsPEN2, width = 8, height = 4)
```

Plot a force network of the EPG and PEN1 connections
First, get the connectivity tables
```{r}
nrons = c("EPG","PEN_a(PEN1)","EPGt")
EBColBag = neuronBag(getTypesTable(nrons))
EBCol_CT <- EBColBag$outputs_raw %>% 
  filter(type.to %in% nrons,
         roi %in% c("PB","EB"))
EBCol_CT$id.from <- EBGlomOrder(EBCol_CT$name.from,EBCol_CT$from,"EB")
EBCol_CT$id.to <- EBGlomOrder(EBCol_CT$name.to,EBCol_CT$to,"EB")
```

Now, convert it into an igraph function
```{r}
library(igraph)
library(ggraph)

EBColNodes <- c(as.character(EBCol_CT$id.to),as.character(EBCol_CT$id.from)) %>% unique() %>% as.data.frame()
colnames(EBColNodes) <- "nodes"
EBColNodes$supertype <- EBColNodes$nodes %>% sapply(function(n) substring(n,1,gregexpr("_L|_R",n)[[1]][1]+1))
EBColNodes$label <- EBColNodes$nodes %>% sapply(function(n) substring(n,gregexpr("_L|_R",n)[[1]][1]+1,gregexpr("_L|_R",n)[[1]][1]+2))

EBColEdges <- EBCol_CT %>% mutate(from = id.from, to = id.to, weight = ROIweight) %>%
  select(from,to,weight)
EBColEdges$supertype.from <- EBColEdges$from %>% as.character() %>% sapply(function(n) substring(n,1,gregexpr("_L|_R",n)[[1]][1]+1))

g <- graph_from_data_frame(EBColEdges, directed = TRUE, vertices = EBColNodes)

# Assign colors to the supertypes
colBreaks = c("EPG_L","EPG_R","PEN1_L","PEN1_R","EPGt_L","EPGt_R")
colPal = c("purple","purple4","red","skyblue","mediumpurple","mediumpurple4")
sTScale <- scale_colour_manual(values=colPal,breaks = colBreaks)
sTScale_edge <- scale_edge_colour_manual(values=colPal,breaks = colBreaks, guide = FALSE)

#sTs <- supertype2Palette()
#sTScale <- scale_colour_manual(values=sTs$pal,breaks = sTs$breaks)
#sTScale_edge <- scale_edge_colour_manual(values=sTs$pal,breaks = sTs$breaks,guide = FALSE)


EBColForceGraph <- ggraph(g) +
  geom_edge_fan(aes(width=weight,color=supertype.from),alpha=0.5,
                      strength=1,
                      end_cap = circle(0.2, 'cm')) + 
  geom_edge_loop(aes(direction=45,span=90,width=weight,color=supertype.from,strength=1),alpha=0.5) +
  geom_node_point(aes(color=supertype),size=4) + 
  scale_edge_width(range = c(0, 2)) +
  sTScale_edge +
  sTScale +
  geom_node_text(aes(label=EBColNodes$label)) +
  theme_paper() +
  coord_fixed(ratio = 1,clip="off") + 
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank())

print(EBColForceGraph)
ggsave('C:\\Users\\dantu\\Dropbox (Personal)\\Professional\\Figures\\FIBSEM\\EBColForceNetwork_wLabels_wEPGt.pdf',EBColForceGraph)
```

