---
title: "ExR motifs figure: EB to non-EB"
output: html_notebook
---

## Preparing the environment
```{r}
library(neuprintrExtra)
library(dplyr)
library(tidyr)
#library(ggplot2)
```


Loading local functions:
```{r}
source(file.path("..","Outputs","outputFunctions-display.R"))
source(file.path("..","R","paperTheme.R"))
source(file.path("..","R","table2ggraphUtils.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure15-ExR-Motifs"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "ExR-EB2XMotifs-Preparation.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "ExR-EB2XMotifs-Preparation.Rmd":
```{r}
ExRoutFull <- readRDS(file.path(dataFolder,"ExRpathwayWeightsTable.rds"))
load(file.path(dataFolder,"ExRoutputsBasics.RData"))
```


### Load pre-generated data


Generate a list of all EB neurons
```{r}
roiTable <- getTypesInRoiTable("EB", minTypePercentage = 0.8)#0.5
allEBTypes <-  unique(roiTable$names$databaseType)

allEBNeurons <- getTypesTable(allEBTypes)
allEBNeurons <- cxRetyping(allEBNeurons,postfix="raw")
allEBNeurons <- supertype(allEBNeurons) #%>% mutate(supertype="CX")
```

```{r}
allEBTypes <- getROISummary(allEBNeurons)

allEBTypes <- filter(allEBTypes,roi %in% outsideRegions) %>% group_by(type,databaseType,n,supertype1,supertype2,supertype3) %>%
   summarize(upstream=sum(upstream),
             downstream=sum(downstream),
             fullWeight=sum(fullWeight),
             downstreamRatio=downstream/fullWeight,
             polarityRatio=(downstream/totalDownstream[1])/(upstream/totalUpstream[1])) %>%
   ungroup() %>% distinct()
allEBTypes <- filter(allEBTypes,upstream>20 | downstream>20)

#Optional filtering:
allEBTypes <- allEBTypes %>% filter(supertype3 != "MBON")  %>% filter(supertype3 != "Terra incognita") %>% 
   filter(supertype3 != "DAN")  %>% filter(supertype3 != "DAN") 

```

Generate a list of all ExR partners
```{r}
partnerExRTypes <-unique(c(getConnectionTable(ExRNeurons$bodyid, "PRE")$databaseType.from,
                           getConnectionTable(ExRNeurons$bodyid, "POST")$databaseType.to))
partnerExRNeurons <- getTypesTable(partnerExRTypes$databaseType)
partnerExRNeurons <- cxRetyping(partnerExRNeurons,postfix="raw")
partnerExRNeurons <- supertype(partnerExRNeurons) #%>% mutate(supertype="CX")
```

```{r}
#partnerExRTypes <- getROISummary(partnerExRNeurons,threshold=0)

#partnerExRTypes <- filter(partnerExRTypes,roi %in% outsideRegions) %>% group_by(type,databaseType,n,supertype1,supertype2,supertype3) %>%
#   summarize(upstream=sum(upstream),
#             downstream=sum(downstream),
#             fullWeight=sum(fullWeight),
#             downstreamRatio=downstream/fullWeight,
#             polarityRatio=(downstream/totalDownstream[1])/(upstream/totalUpstream[1])) %>%
#   ungroup() %>% distinct()
#partnerExRTypes <- filter(partnerExRTypes,upstream>20 | downstream>20)
```


Looking at the strong axo dendritic connections only:
```{r}
partnerTypes <-  allEBTypes#EBOutsideTypes
EBOutAxonals <- filter(partnerTypes,downstreamRatio>0.75)

#direction = "outputs"
#if (direction == "outputs"){
EB2EBaxDendMat <- filter(ExRoutFull,databaseType.to %in% partnerTypes$databaseType & 
                           !databaseType.to %in% EBOutAxonals$databaseType & 
                           databaseType.from != databaseType.to) %>% 
  mutate(roi="outside") %>% supertype() %>% filter(Path_weight>0.005)

recurrentInEBBag <- neuronBag(filter(ExRNeurons,type %in% unique(c(EB2EBaxDendMat$type.from,EB2EBaxDendMat$type.to))),
                              renaming = cxRetyping,omitInputs = T,slctROI=c("EB")) #,"FB","NO(R)","NO(L)","PB"
allRecurrentEB <- recurrentInEBBag$outputs
#}else{
#   EB2EBaxDendMat <- filter(EBoutFull,databaseType.from %in% partnerTypes$databaseType &
#                               !databaseType.from %in% EBOutAxonals$databaseType & databaseType.from != databaseType.to) %>%
#      mutate(roi="outside") %>% supertype() %>% filter(Path_weight>0.005)

#   recurrentInEBBag <- neuronBag(filter(ExRNeurons,type %in% unique(c(EB2EBaxDendMat$type.from,EB2EBaxDendMat$type.to))),
#                                 renaming = cxRetyping,omitInputs = T,slctROI=outsideRegions)
#   allRecurrentEB <- recurrentInEBBag$outputs
#}

allRecurrentGraph <- makeGraph(allRecurrentEB)
```

```{r}
# A rough ordering of types for subsequent figures
typesEB <- unique(ExRNeurons$type)
typesEBOrder <- c(typesEB[startsWith(typesEB,"Ex")])
```

```{r}
recurrentMotifsSummary <- group_by(EB2EBaxDendMat,type.from,supertype1.from,supertype3.from) %>% 
  summarize("EB parallel connection"=sum(paste0(type.from,type.to) %in% paste0(allRecurrentEB$type.from,allRecurrentEB$type.to))/n(),
            "EB canonical feedback"=sum(paste0(type.to,type.from) %in% paste0(allRecurrentEB$type.from,allRecurrentEB$type.to))/n(),
            "linked targets in EB"=if (n()==1) 0 else sum(as.vector(combn(type.to,2,paste0,collapse="")) %in%
                                                            c(paste0(allRecurrentEB$type.from,allRecurrentEB$type.to),
                                                              paste0(allRecurrentEB$type.to,allRecurrentEB$type.from)))/(choose(n(),2))
  ) %>% 
  pivot_longer(c("EB parallel connection","EB canonical feedback","linked targets in EB"),names_to="stat",values_to="proportion") %>% 
  mutate(type.fromF = factor(type.from,levels=typesEBOrder),
         stat=factor(stat,levels=c("EB parallel connection","EB canonical feedback","linked targets in EB")))

recurrentMotifSuperSummary <- recurrentMotifsSummary %>% group_by(supertype1.from,supertype3.from,stat) %>% 
   summarize(proportion=mean(proportion))
```

```{r}
recurrentMotifsPrevalence <- ggplot(recurrentMotifsSummary %>% filter(supertype3.from == "ExR") ,aes(x=type.fromF,y=stat)) + 
   geom_point(size=3,color="grey90")+ 
   geom_point(aes(size=proportion,color=stat))  + 
   facet_grid(.~supertype1.from,scale="free",space="free")+ 
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.text.x = element_text(angle=90)) +
  xlab("CX output type") + scale_size_area(name="prevalence",max_size = 3) + ylab("motif") + 
  scale_color_paletteer_d(name="Motif","ggthemes::Traffic")

#motifPal <- c("Plum",paletteer_d("ggthemes::Traffic")[1:3])
#names(motifPal) <- c("Out of CX pathways","CX parallel connection","CX canonical feedback","linked targets in CX")

recurrentMotifsPrevalence

#ggsave(paste0('motifSummary_',direction,'.pdf'), plot = recurrentMotifsPrevalence, device='pdf', path = outputsFolder,
#    scale = 1,height=2.5, width=5, useDingbats=FALSE)
```

```{r}
supertypeMotifSummary <-  getMotifsGraphDf(mutate(EB2EBaxDendMat,roi="Outside"),allRecurrentEB,
                                           "ExR2_R","Path_weight") %>% 
  mutate(source = "ExR2_R")

for(mytype in c("ExR3_R","ExR4_R","ExR5_R","ExR6_R","ExR7_R")){
   #c("ExR1_L","ExR2_R","ExR2_L","ExR3_R","ExR3_L","ExR4_R","ExR5_R","ExR5_L","ExR6_R","ExR7_R","ExR7_L")
   myMotifGraph = getMotifsGraphDf(mutate(EB2EBaxDendMat,roi="Outside"),
                                   allRecurrentEB,mytype,"Path_weight")  %>% 
     mutate(source = mytype)
   supertypeMotifSummary = bind_rows(supertypeMotifSummary, myMotifGraph)
}

supertypeMotifSummary = supertypeMotifSummary %>% select(c(roi, source, motif, type.to, type.from, supertype1.to, supertype1.from,supertype2.to, supertype2.from, supertype3.to, supertype3.from, weightRelative))

```

```{r}

typesInMotif = ggplot(data = supertypeMotifSummary %>% filter(motif != "NA" & roi == "EB") , aes(x=source, y=weightRelative, fill=supertype3.to)) +
   geom_bar(position = "stack", stat="identity") + 
   facet_grid(rows=vars(motif)) +
   #scale_fill_manual(values=p36) + 
   scale_fill_manual(values=supertype3Palette) + 
   theme_classic() + theme_paper() + theme(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2))

typesInMotif

#ggsave(paste0('motifTypesSummary_',direction,'.pdf'), plot = typesInMotif, device='pdf', path = outputsFolder,
#    scale = 1,height=3.5,width=3, useDingbats=FALSE)
```

```{r}

plotMotifsCustom <- function(graphDf){
  focusContrib <- filter(graphDf,roi=="Outside") %>% group_by(type.to) %>% summarize(weightRelative=sum(weightRelative)) %>% ungroup()
  motifGG <- makeGraph(graphDf) 
  edgePal <- c("Plum",paletteer_d("ggthemes::Traffic")[1:3])
  names(edgePal) <- c("Out of CX pathways","CX Parallel connection","CX Canonical feedback","Linked targets in CX")
  
  motifGG <- motifGG %N>% 
    mutate(
      customSuper = ifelse(layer,"Source",supertype2))
  
  #customPal <- c("Source"="grey50",supertype2Palette()$pal)
  
  return(ggraph(motifGG,layout="focus",focus=(motifGG %N>% as_tibble())$layer)+
           graphlayouts::draw_circle(max.circle = 1,col="grey90") +
           geom_edge_fan2(aes(color=motif,
                              width=weightRelative),
                          end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                          arrow =arrow(length = unit(1, 'mm'),type = "closed"))+
           geom_node_point(aes(color=customSuper),size=4)+
           #scale_color_manual(values=customPal) +
           guides(color="none") +
           theme_paper_map() + scale_edge_color_manual(name="Motif",values=edgePal,breaks=c("Out of CX pathways","CX Parallel connection","CX Canonical feedback","Linked targets in CX"),drop=FALSE)+
           scale_edge_width(name="Relative weight/pathway weight",range=c(0.2,3),limits=c(0,1),)+
           geom_node_text(aes(label=name),size=1.5,nudge_y = 0.15) + 
           coord_fixed(clip="off"))
}

```

```{r}

mytype  =  "ExR6_R"
myMotifGraph = getMotifsGraphDf(mutate(EB2EBaxDendMat,roi="Outside"),allRecurrentEB,mytype,"Path_weight")
canMot <- plotMotifsCustom(myMotifGraph)
canMot
dev.print(pdf, paste0(outputsFolder,'motifGraph',mytype,'_',direction,".pdf"), width=5, height=3,useDingbats=FALSE)
#save_plot(paste0(c(outputsFolder,'motifGraph',mytype,'.pdf')), plot = canMot, base_width = 8.5,base_height = 11/4,device="pdf")
```




```{r}


getBodyIdsForList = function (neuronList,prefix="",postfix=".*",...){
  #' Get one dataframe of bodyIDs for all search strings in neuronList
  #' @param neuronList: A list of search strings to be passed.
  #' @param prefix: String to be added before each query (default "")
  #' @param postfix: String to be added after each query (default ".*")
  #' @param ...: Parameters to be passed to neuprint_search. Note that meta=FALSE won't work for now.
  #' @return A data frame of metadata for the results of all the queries
  #' @examples
  #' \dontrun{
  #' # Both will return the same
  #' getBodyIdsForList(c("PFL1","PFL2"))
  #' getBodyIdsForList(c("PFL1","PFL2"),postfix="",field="type")
  #' }
  
  neuronList <-  paste0(prefix,neuronList,postfix)
  bodiesList <- lapply(neuronList,neuprint_search,...)
  return(bind_rows(bodiesList))
}
```
