---
title: "ExR motifs figure: EB to non-EB"
output: html_notebook
---

## Preparing the environment

Loading local functions
```{r message=FALSE}
source(file.path("..","Outputs","outputFunctions-core.R"))
source(file.path("..","R","table2ggraphUtils.R"))
```

Where the data will be saved (so that the figure making notebook can be run without having to run the time consuming steps):
```{r}
dataFolder="data"
if (!dir.exists(dataFolder)) dir.create(dataFolder)
```

## Building ExR neurons output pathways
First define the outside neuropils (anything outside of the EB and not on the left side of the brain):
```{r}
roiH <- getRoiTree()
outsideRegions <- unique(selectRoiSet(exceptions=sapply(as.character(unique(roiH$level2[grepl(roiH$level2,pattern="(R)")])),
                                                        function(i) return(1),USE.NAMES = TRUE,simplify=FALSE),
                                     exceptionLevelMatch = 1)$roi[roiH$level2!="EB" & roiH$side4!="Left"])
outsideRegions
```
List the ExR neurons:
```{r}
ExRtypes <- supertype(neuprint_search("ExR.*",field = "type") %>% 
                         rename(databaseType=type)) %>% select(c("databaseType", "supertype1", "supertype2", "supertype3"))
ExRNeurons <- getTypesTable(ExRtypes$databaseType)
ExRNeurons <- cxRetyping(ExRNeurons,postfix="raw")
ExRNeurons <- supertype(ExRNeurons)%>% mutate(supertype="ExR")
head(ExRNeurons)
```

We summarize the ExR innervation in the "outside neuropils" and remove any type not contributing anything to those:
```{r}
ExROutsideTypes <- getROISummary(ExRNeurons,threshold=0)

ExROutsideTypes <- filter(ExROutsideTypes,roi %in% outsideRegions) %>% 
   group_by(type,databaseType,n,supertype1,supertype2,supertype3) %>%
   summarize(upstream=sum(upstream),
             downstream=sum(downstream),
             fullWeight=sum(fullWeight),
             downstreamRatio=downstream/fullWeight,
             polarityRatio=(downstream/totalDownstream[1])/(upstream/totalUpstream[1])) %>%
   ungroup() %>% distinct()

ExROutsideTypes <- filter(ExROutsideTypes,upstream>20 | downstream>20)
ExROutsideNeurons <- filter(ExRNeurons,type %in% ExROutsideTypes$type)
```
```{r}
# A rough ordering of types for subsequent figures
typesEB <- unique(ExRNeurons$type)
typesEBOrder <- c(typesEB[startsWith(typesEB,"Ex")])
```
## Get type to type connection tables up to 5 hops out
Calculate a massive pathway table of everything postsynaptic to the ExR neurons outside of the EB, in 5 steps or less (doing it "raw" for more flexibility afterwards):
```{r}
ExR_outGraphBi <- get_type2typePath_raw(type.from=ExROutsideNeurons,
                                       ROI=list("Outside_regions(R)"=outsideRegions),
                                       n_steps=1:5,
                                       addContraPaths = T,
                                       thresholdPerROI = 20,verbose=TRUE,
                                       renaming=customRetyping,overruleThreshold=50,largeOnly=TRUE)
head(ExR_outGraphBi[[1]])
```

Filtering out types contributing close to nothing to downstream partners
```{r}
ExR_outGraphBi[[1]] <- ExR_outGraphBi[[1]] %>% group_by(type.from,supertype3.from) %>% 
   mutate(totalWeightRaw=sum(absoluteWeight)) %>% 
   filter(totalWeightRaw>20) %>% select(-totalWeightRaw)

for (n in 2:5){
   ExR_outGraphBi[[n]] <- filter(ExR_outGraphBi[[n]],type.from %in% ExR_outGraphBi[[n-1]]$type.to)
}
```


Reduced version of the pathways: starting in the right side of the brain exclusively (and remove any connection from the origin neurons on the left side of the brain).
```{r}
ExR_outPaths <- ExR_outGraphBi
ExR_outPaths[[1]] <- filter(ExR_outPaths[[1]],roi == "Outside_regions(R)") 

##List the types
ExROutputTypes <- unique(ExR_outPaths[[1]]$type.from)
ExROutputNeurons <- filter(ExROutsideNeurons,type %in% ExROutputTypes)


for (n in 2:5){
   ExR_outPaths[[n]] <- filter(ExR_outPaths[[n]],type.from %in% ExR_outPaths[[n-1]]$type.to)
   ExR_outPaths[[n]] <- filter(ExR_outPaths[[n]],!(type.from %in% ExROutputTypes & roi=="Outside_regions(R)_contra"))
}
```

```{r}
#saveRDS(ExR_outPaths,file.path(dataFolder,"EBoutput_paths.rds"))
```

Get a good supertyping for coloring to come
```{r}
ExROutputNeurons <- selectSupertypeSet(ExROutputNeurons,default_level = 1) %>%
   customOutputSupertype(postfix = "raw")
   #mutate(customSupertype = case_when(supertype=="PFL" ~ databaseType,
   #                         grepl("ExR[2-7]",supertype) ~ "ExR2-7",
   #                         supertype3=="EB Columnar" ~ "EB Columnar",
   #                         TRUE ~ as.character(supertype)))
```

Then make tables of synapses
```{r,warning=FALSE}
#EBOutSyn <- collectSynapses(EBOutputNeurons,outsideRegions,polarity="post")
#EBOutSyn <-  mutate(EBOutSyn,customSupertype=EBOutputNeurons$customSupertype[match(type,EBOutputNeurons$type)])
#saveRDS(EBOutSyn,"EB-outsideSynapses.rds")
```

## The CX output graph
We first collate all connections present:
```{r}
ExR_outGraph <- distinct(do.call(rbind,ExR_outPaths))
```

For cases where a neuron pair has connections on both sides of the brain, we use the average relative weight, weighted on the importance of the innervation on each side: 

```{r}
## For contra ROI + ipsi ROI case, we need an approximation of the relative weight and output contribution
ExR_outGraph <- group_by(ExR_outGraph,type.to) %>%
   mutate(combineROIweight=sum(totalROIweight[match(unique(roi),roi)])) %>% 
   ungroup() 

ExR_outGraph <- group_by(ExR_outGraph,type.from,type.to,supertype1.from,supertype2.from,supertype3.from,
                        supertype1.to,supertype2.to,supertype3.to,databaseType.from,databaseType.to,n_type) %>%
   summarize(weightRelative=mean(weightRelative*totalROIweight/combineROIweight),
             outputContribution=sum(weight)/sum(totalPreROIweight*n_from)) %>% ungroup()

#ExR_outGraph <- group_by(ExR_outGraph,type.from) %>% 
#   mutate(wr_contribution=weightRelative/sum(weightRelative)) %>% ungroup() 
```

This next bit is a sanity check to make sure this averaging didn't create any "impossible" weights (weight relative summing to more than 1):
```{r}
ExR_outGraphTo <- group_by(ExR_outGraph,type.to) %>% 
   summarize(wr=sum(weightRelative)) %>% ungroup()

#ExR_outGraphFrom <- group_by(ExR_outGraph,type.from) %>%
#   summarize(oc=sum(outputContribution),wroc=sum(wr_contribution)) %>% ungroup()

all(ExR_outGraphTo$wr<=1) #& all(ExR_outGraphFrom$oc<=1) 
```

### Pathway weights

Create a graph, then calculate weightRelative contribution to all the possible targets from the CX output types, multiplying the adjacency matrix of the whole graph to convergence.
```{r}
ExR_outGraph <- makeGraph(ExR_outGraph)
allNodes <- ExR_outGraph %>% activate(nodes) %>% as_tibble()
head(allNodes)
```
```{r}
ExRout_AdjWR <- igraph::as_adjacency_matrix(ExR_outGraph,attr="weightRelative")
#EBout_AdjOCWR <- igraph::as_adjacency_matrix(EB_outGraph,attr="wr_contribution") ## Here we use the relative contribution - use this for "downstream" computations of influence

## For display, just first 8 steps
#EBoutAllSteps <- endpointConnections_raw(EBout_AdjWR,endpoint=EBOutputTypes,polarity="upstream",maxIt=8,eps=10^-8)
#EBoutAllSteps <- lapply(1:length(EBoutAllSteps),function(i){reshape2::melt(as.matrix(EBoutAllSteps[[i]]),na.rm=TRUE,value.name="Path_weight") %>% 
#      filter(Path_weight>0) %>%
#      rename(type.from=Var1,type.to=Var2) %>%
#      mutate(n_steps=i)})
#EBoutAllSteps <- do.call(rbind,EBoutAllSteps)

## The result at convergence
ExRoutFull <- endpointConnections(ExRout_AdjWR,endpoint=ExROutputTypes,polarity="from_sources",maxIt=100,eps=10^-8)

ExRoutFull <- reshape2::melt(as.matrix(ExRoutFull),na.rm=TRUE,value.name="Path_weight") %>% 
   filter(Path_weight>0) %>% rename(type.from=Var1,type.to=Var2) %>% mutate(n_steps="All")
#EBoutAllSteps <- rbind(EBoutAllSteps,EBoutFull) %>% mutate(type.from=as.character(type.from),type.to=as.character(type.to),
#                     databaseType.to=allNodes$databaseType[match(type.to,allNodes$type)],
#                      databaseType.from=allNodes$databaseType[match(type.from,allNodes$type)]
#                    )
ExRoutFull <- mutate(ExRoutFull,
                     type.from=as.character(type.from),type.to=as.character(type.to),
                     databaseType.to=allNodes$databaseType[match(type.to,allNodes$type)],
                     databaseType.from=allNodes$databaseType[match(type.from,allNodes$type)]
)

#ExRoutFull <- supertype(ExRoutFull) %>% group_by(type.to) %>% mutate(fullCXwr=sum(Path_weight)) %>% ungroup()
```

Save simple variables
```{r}
save(ExROutputNeurons,ExROutsideTypes,ExROutputTypes,outsideRegions,ExROutsideNeurons,typesEBOrder,ExRNeurons,file=file.path(dataFolder,"ExRoutputsBasics.RData"))
```

```{r}
saveRDS(ExRoutFull,file.path(dataFolder,"ExRpathwayWeightsTable.rds"))
#saveRDS(EBoutAllSteps,"EBpathways-allsteps.rds")
#saveRDS(allNodes,"EBall-nodes.rds")
```


