---
title: "ExR motifs figure: EB to non-EB"
output: html_notebook
---

## Preparing the environment
```{r}
library(tidyr)
library(readr)
```

Loading local functions:
```{r,warning=FALSE,message=FALSE}
source(file.path("..","Outputs","outputFunctions-display.R"))
source(file.path("..","R","paperTheme.R"))
source(file.path("..","R","table2ggraphUtils.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure15-ExR-Motifs"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "ExR-EB2XMotifs-Preparation.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "ExR-EB2XMotifs-Preparation.Rmd":
```{r}
## General metadata
load(file.path(dataFolder,"ExRoutputsBasics.RData"))
## The pathway weights table
ExRoutFull <- readRDS(file.path(dataFolder,"ExRpathwayWeightsTable.rds"))
```

And load the list of CX neurons:
```{r}
CXtypes <- supertype(read_csv(file.path("..","CX-cell-types060920.csv")) %>% rename(databaseType=n.type))
```


## Prepare the data
### List the EB neurons interacting with ExR neurons outside the EB
Generate a list of all EB neurons (we want all CX neurons with at least 80% of instances with synapses in the EB):
```{r}
## Neurons with at least 80% of instances touching the EB
roiTable <- getTypesInRoiTable("EB", minTypePercentage = 0.8)

## Intersect with the CX types
allEBTypes <-  CXtypes$databaseType[CXtypes$databaseType %in% roiTable$names$databaseType]

## Get a table of individual neurons
allEBNeurons <- getTypesTable(allEBTypes)
allEBNeurons <- cxRetyping(allEBNeurons,postfix="raw")
allEBNeurons <- supertype(allEBNeurons)

head(allEBNeurons)
```

We then further restrict this list of types to those that innervate regions outside the EB (at least 20 synapses), and filter out:
```{r}
allEBTypes <- getROISummary(allEBNeurons)

allEBTypes <- filter(allEBTypes,roi %in% outsideRegions) %>% group_by(type,databaseType,n,supertype1,supertype2,supertype3) %>%
   summarize(upstream=sum(upstream),
             downstream=sum(downstream),
             fullWeight=sum(fullWeight),
             downstreamRatio=downstream/fullWeight,
             polarityRatio=(downstream/totalDownstream[1])/(upstream/totalUpstream[1])) %>%
   ungroup() %>% distinct()
allEBTypes <- filter(allEBTypes,upstream>20 | downstream>20)

allEBNeurons <- filter(allEBNeurons,type %in% allEBTypes$type)
```

We then select all ExR to EB neurons connections outside the EB to look for motifs in. 
We exclude projections to EB neurons that are mostly axonal, and consider only connections with pathway weights over 0.5%.
```{r}
partnerTypes <-  allEBTypes
EBOutAxonals <- filter(partnerTypes,downstreamRatio>0.75)

EB2EBaxDendMat <- filter(ExRoutFull,
                         databaseType.to %in% partnerTypes$databaseType & 
                           !databaseType.to %in% EBOutAxonals$databaseType & 
                           databaseType.from != databaseType.to) %>% 
  mutate(roi="Outside") %>% supertype() %>% filter(Path_weight>0.005)
head(EB2EBaxDendMat)
```

### Build the connection table in the EB
We then build the EB connection tables for those ExR partners (we also make a graph object of it):
```{r}
recurrentInEBBag <- neuronBag(filter(allEBNeurons,type %in% unique(c(EB2EBaxDendMat$type.from,EB2EBaxDendMat$type.to))),
                              renaming = cxRetyping,omitInputs = T,slctROI=c("EB")) #,"FB","NO(R)","NO(L)","PB"
allRecurrentEB <- recurrentInEBBag$outputs

allRecurrentGraph <- makeGraph(allRecurrentEB)
allRecurrentGraph
```

```{r}
# A rough ordering of types for subsequent figures
#typesEB <- unique(ExRNeurons$type)
#typesEBOrder <- c(typesEB[startsWith(typesEB,"Ex")])
```

## Motifs prevalence (panel B)
We then count the prevalence of every motif for every ExR type present in the ExR to EB connections table:
- the prevalence canonical feedbacks is the number of reciprocal connections in the EB (divided by the number of connections outside the EB)
- the prevalence of parallel connections is the number of matching connections in the EB (divided by the number of connections outside the EB)
- the prevalence of linked targets is the number of connections between any 2 of the targets in the EB, divided by the number of possible connections (n choose 2, where n is the number of targets)
```{r}
recurrentMotifsSummary <- group_by(EB2EBaxDendMat,
                                   type.from,supertype1.from,supertype3.from) %>% 
  summarize("EB parallel connection"=sum(paste0(type.from,type.to) %in% 
                                           paste0(allRecurrentEB$type.from,allRecurrentEB$type.to))/n(),
            "EB canonical feedback"=sum(paste0(type.to,type.from) %in% 
                                          paste0(allRecurrentEB$type.from,allRecurrentEB$type.to))/n(),
            "linked targets in EB"=if (n()==1) 0 else 
              sum(as.vector(combn(type.to,2,paste0,collapse="")) %in%
                    c(paste0(allRecurrentEB$type.from,allRecurrentEB$type.to),
                      paste0(allRecurrentEB$type.to,allRecurrentEB$type.from)))/(choose(n(),2))
  ) %>% ungroup()
head(recurrentMotifsSummary)
```
We then pivot the table to a longer format for easier plotting:
```{r}
recurrentMotifsSummary <- pivot_longer(recurrentMotifsSummary,
                                       c("EB parallel connection","EB canonical feedback","linked targets in EB"),
                                       names_to="stat",values_to="proportion") %>% 
  mutate(type.fromF = factor(type.from,levels=unique(ExRNeurons$type)),
         stat=factor(stat,levels=c("EB parallel connection","EB canonical feedback","linked targets in EB")))

```

We then plot the prevalence of each motif per type:
```{r}
recurrentMotifsPrevalence <- ggplot(recurrentMotifsSummary %>% filter(supertype3.from == "ExR") ,aes(x=type.fromF,y=stat)) + 
   geom_point(size=3,color="grey90")+ 
   geom_point(aes(size=proportion,color=stat))  + 
   facet_grid(.~supertype1.from,scale="free",space="free")+ 
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.text.x = element_text(angle=90)) +
  xlab("CX output type") + scale_size_area(name="prevalence",max_size = 3) + ylab("motif") + 
  scale_color_paletteer_d(name="motif","ggthemes::Traffic")

recurrentMotifsPrevalence
```
And save it:
```{r}
ggsave("ExR-motifPrevalence.pdf", plot = recurrentMotifsPrevalence, device='pdf', path = outputsFolder,
    scale = 1,height=2.5, width=5, useDingbats=FALSE)
```

## Motifs weight breakdown (panel C)
We summarize each motif for each source type and supertype target by the total pathway weight contributed to neurons belonging to each of the motifs.
```{r}
supertypeMotifSummary <- group_by(EB2EBaxDendMat,
                                   type.from) %>% 
  mutate("parallel"=paste0(type.from,type.to) %in%                ## Collecting motif appartenance
                                           paste0(allRecurrentEB$type.from,allRecurrentEB$type.to),
            "canonical"=paste0(type.to,type.from) %in% 
                                          paste0(allRecurrentEB$type.from,allRecurrentEB$type.to),
            "linked"=if (n()==1) FALSE else 
              sapply(type.to,function(p) any(grepl(p,
                                as.vector(combn(type.to,2,paste,collapse=" "))[as.vector(combn(type.to,2,paste,collapse=" ")) %in%
                                                  c(paste(allRecurrentEB$type.from,allRecurrentEB$type.to),
                                                  paste(allRecurrentEB$type.to,allRecurrentEB$type.from))])))
  ) %>% 
  group_by(type.from,supertype1.from,supertype3.from,supertype3.to) %>%
  summarize("EB parallel connection"=sum(Path_weight[parallel]),        ## Summing over
            "EB canonical feedback"=sum(Path_weight[canonical]),
            "linked targets in EB"=sum(Path_weight[linked])
            )
head(supertypeMotifSummary)
```
We then pivot the table to a longer format for easier plotting:
```{r}
supertypeMotifSummary <- pivot_longer(supertypeMotifSummary,
                                       c("EB parallel connection","EB canonical feedback","linked targets in EB"),
                                       names_to="motif",values_to="contribution") %>% 
  mutate(type.fromF = factor(type.from,levels=unique(ExRNeurons$type)),
         motif=factor(motif,levels=c("EB parallel connection","EB canonical feedback","linked targets in EB"))) %>%
  filter(!is.na(contribution) & contribution >0)
head(supertypeMotifSummary)
```

And plot the result:
```{r}
typesInMotif = ggplot(data = supertypeMotifSummary, aes(x=type.from, y=contribution, fill=supertype3.to)) +
   geom_bar(position = "stack", stat="identity") + 
   facet_grid(rows=vars(motif)) +
   scale_fill_manual(name="partner supertype",values=supertype3Palette) + 
  theme_paper(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2)) +
  xlab("") + ylab("relative weight")

typesInMotif

```

```{r}
ggsave('ExR-motifContributions.pdf', plot = typesInMotif, device='pdf', path = outputsFolder,
    scale = 1,height=3.5,width=5, useDingbats=FALSE)
```

## Motifs plots (panels D through G)
We then use the `plotMotifs` function (defined in **outputFunctions-display.R**), which takes a graph object outputed by `getMotifsGraphDf` as an input and returns the radial motif plot used in the figures on each ExR of interest.

For example (change `mytype` to look at different source neurons):
```{r}
mytype <- "ExR2_R"
myMotifGraph <- getMotifsGraphDf(EB2EBaxDendMat,allRecurrentEB,mytype,"Path_weight")
exRMot <- plotMotifs(myMotifGraph)
exRMot
```
We run it in a loop for all ExR of interest to save the panels:
```{r}
for (mytype in c("ExR2_R","ExR3_R","ExR5_R","ExR6_R")){
  myMotifGraph <-  getMotifsGraphDf(EB2EBaxDendMat,allRecurrentEB,mytype,"Path_weight")
  exRMot <- plotMotifs(myMotifGraph)
  ggsave(paste0('motifGraph',mytype,".pdf"),path=outputsFolder, device="pdf", plot=exRMot,scale=1,width=5, height=3,useDingbats=FALSE)
}
```




## Old code

```{r}

plotMotifsCustom <- function(graphDf){
  focusContrib <- filter(graphDf,roi=="Outside") %>% group_by(type.to) %>% summarize(weightRelative=sum(weightRelative)) %>% ungroup()
  motifGG <- makeGraph(graphDf) 
  edgePal <- c("Plum",paletteer_d("ggthemes::Traffic")[1:3])
  names(edgePal) <- c("Out of CX pathways","CX Parallel connection","CX Canonical feedback","Linked targets in CX")
  
  motifGG <- motifGG %N>% 
    mutate(
      customSuper = ifelse(layer,"Source",supertype2))
  
  #customPal <- c("Source"="grey50",supertype2Palette()$pal)
  
  return(ggraph(motifGG,layout="focus",focus=(motifGG %N>% as_tibble())$layer)+
           graphlayouts::draw_circle(max.circle = 1,col="grey90") +
           geom_edge_fan2(aes(color=motif,
                              width=weightRelative),
                          end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                          arrow =arrow(length = unit(1, 'mm'),type = "closed"))+
           geom_node_point(aes(color=customSuper),size=4)+
           #scale_color_manual(values=customPal) +
           guides(color="none") +
           theme_paper_map() + scale_edge_color_manual(name="Motif",values=edgePal,breaks=c("out of CX pathways","CX parallel connection","CX canonical feedback","linked targets in CX"),drop=FALSE)+
           scale_edge_width(name="relative weight/pathway weight",range=c(0.2,3),limits=c(0,1),)+
           geom_node_text(aes(label=name),size=1.5,nudge_y = 0.15) + 
           coord_fixed(clip="off"))
}

```

For each ExR type participating in motifs, we collate the motifs using the `getMotifsGraphDf` function (defined in **Outputs/outputFunctions-display.R**): `getMotifsGraphDf` takes as input two connection tables (here one for the outside connections and one for the EB connections), a neuron of interest and a statistic and returns all the connections belonging to a motif in a graph object.
```{r}
supertypeMotifSummary <-  getMotifsGraphDf(mutate(EB2EBaxDendMat,roi="Outside"),allRecurrentEB,
                                           "ExR2_R","Path_weight") %>% 
  mutate(source = "ExR2_R")

for(mytype in c("ExR3_R","ExR5_R","ExR6_R","ExR7_R")){
   #c("ExR1_L","ExR2_R","ExR2_L","ExR3_R","ExR3_L","ExR4_R","ExR5_R","ExR5_L","ExR6_R","ExR7_R","ExR7_L")
   myMotifGraph = getMotifsGraphDf(mutate(EB2EBaxDendMat,roi="Outside"),
                                   allRecurrentEB,mytype,"Path_weight")  %>% 
     mutate(source = mytype)
   supertypeMotifSummary = bind_rows(supertypeMotifSummary, myMotifGraph)
}
head(supertypeMotifSummary)
```

We then sum all the weights of the connections involved in a given motif for a given ExR neuron, grouping:
- by recipient type for the parallel connection motif
- by source type for the canonical feedback motif
- by source type for the linked targets motif
```{r}
supertypeMotifSummary <- group_by(supertypeMotifSummary,supertype3.to,source,motif,roi) %>%
  summarize(weight=sum(weightRelative)) %>% ungroup()

head(supertypeMotifSummary)
```
