---
title: "ExR motifs figure: EB to non-EB"
output: html_notebook
---

## Preparing the environment
```{r}
#library(neuprintrExtra)
#library(dplyr)
library(tidyr)
library(readr)
#library(ggplot2)
```


Loading local functions:
```{r}
source(file.path("..","Outputs","outputFunctions-display.R"))
source(file.path("..","R","paperTheme.R"))
source(file.path("..","R","table2ggraphUtils.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure15-ExR-Motifs"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "ExR-EB2XMotifs-Preparation.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "ExR-EB2XMotifs-Preparation.Rmd":
```{r}
ExRoutFull <- readRDS(file.path(dataFolder,"ExRpathwayWeightsTable.rds"))
load(file.path(dataFolder,"ExRoutputsBasics.RData"))
```

And load the list of CX neurons:
```{r}
CXtypes <- supertype(read_csv(file.path("..","CX-cell-types060920.csv")) %>% rename(databaseType=n.type))
```


## Prepare the data


Generate a list of all EB neurons (we want all CX neurons with at least 80% of instances with synapses in the EB):
```{r}
roiTable <- getTypesInRoiTable("EB", minTypePercentage = 0.8)#0.5
allEBTypes <-  CXtypes$databaseType[CXtypes$databaseType %in% roiTable$names$databaseType]

allEBNeurons <- getTypesTable(allEBTypes)
allEBNeurons <- cxRetyping(allEBNeurons,postfix="raw")
allEBNeurons <- supertype(allEBNeurons)
```

We then further restrict this list of types to those that innervate the outside regions, and filter out :
```{r}
allEBTypes <- getROISummary(allEBNeurons)

allEBTypes <- filter(allEBTypes,roi %in% outsideRegions) %>% group_by(type,databaseType,n,supertype1,supertype2,supertype3) %>%
   summarize(upstream=sum(upstream),
             downstream=sum(downstream),
             fullWeight=sum(fullWeight),
             downstreamRatio=downstream/fullWeight,
             polarityRatio=(downstream/totalDownstream[1])/(upstream/totalUpstream[1])) %>%
   ungroup() %>% distinct()
allEBTypes <- filter(allEBTypes,upstream>20 | downstream>20)

#Optional filtering:
#allEBTypes <- allEBTypes %>% filter(supertype3 != "MBON")  %>% filter(supertype3 != "Terra incognita") %>% 
#   filter(supertype3 != "DAN")  %>% filter(supertype3 != "DAN") 

allEBNeurons <- filter(allEBNeurons,type %in% allEBTypes$type)
```

Generate a list of all ExR partners
```{r}
#partnerExRTypes <-unique(c(getConnectionTable(ExRNeurons$bodyid, "PRE")$databaseType.from,
#                           getConnectionTable(ExRNeurons$bodyid, "POST")$databaseType.to))
#partnerExRNeurons <- getTypesTable(partnerExRTypes$databaseType)
#partnerExRNeurons <- cxRetyping(partnerExRNeurons,postfix="raw")
#partnerExRNeurons <- supertype(partnerExRNeurons) #%>% mutate(supertype="CX")
```

```{r}
#partnerExRTypes <- getROISummary(partnerExRNeurons,threshold=0)

#partnerExRTypes <- filter(partnerExRTypes,roi %in% outsideRegions) %>% group_by(type,databaseType,n,supertype1,supertype2,supertype3) %>%
#   summarize(upstream=sum(upstream),
#             downstream=sum(downstream),
#             fullWeight=sum(fullWeight),
#             downstreamRatio=downstream/fullWeight,
#             polarityRatio=(downstream/totalDownstream[1])/(upstream/totalUpstream[1])) %>%
#   ungroup() %>% distinct()
#partnerExRTypes <- filter(partnerExRTypes,upstream>20 | downstream>20)
```

We first select all ExR to EB neurons connections outside the EB to look for motifs in. 
We exclude projections to EB neurons that are mostly axonal, and consider only connections with pathway weights over 0.5%.
```{r}
partnerTypes <-  allEBTypes
EBOutAxonals <- filter(partnerTypes,downstreamRatio>0.75)

#direction = "outputs"
#if (direction == "outputs"){
EB2EBaxDendMat <- filter(ExRoutFull,
                         databaseType.to %in% partnerTypes$databaseType & 
                           !databaseType.to %in% EBOutAxonals$databaseType & 
                           databaseType.from != databaseType.to) %>% 
  mutate(roi="Outside") %>% supertype() %>% filter(Path_weight>0.005)
```

We then build the connection tables for the recipient types in the CX neuropils (we also make a graph object of it):
```{r}
recurrentInEBBag <- neuronBag(filter(allEBNeurons,type %in% unique(c(EB2EBaxDendMat$type.from,EB2EBaxDendMat$type.to))),
                              renaming = cxRetyping,omitInputs = T,slctROI=c("EB")) #,"FB","NO(R)","NO(L)","PB"
allRecurrentEB <- recurrentInEBBag$outputs
#}else{
#   EB2EBaxDendMat <- filter(EBoutFull,databaseType.from %in% partnerTypes$databaseType &
#                               !databaseType.from %in% EBOutAxonals$databaseType & databaseType.from != databaseType.to) %>%
#      mutate(roi="outside") %>% supertype() %>% filter(Path_weight>0.005)

#   recurrentInEBBag <- neuronBag(filter(ExRNeurons,type %in% unique(c(EB2EBaxDendMat$type.from,EB2EBaxDendMat$type.to))),
#                                 renaming = cxRetyping,omitInputs = T,slctROI=outsideRegions)
#   allRecurrentEB <- recurrentInEBBag$outputs
#}

allRecurrentGraph <- makeGraph(allRecurrentEB)
```

```{r}
# A rough ordering of types for subsequent figures
typesEB <- unique(ExRNeurons$type)
typesEBOrder <- c(typesEB[startsWith(typesEB,"Ex")])
```

## Motifs prevalence (panel B)
We then count the prevalence of every motif for every ExR type present in the ExR to EB connections table:
- the prevalence canonical feedbacks is the number of reciprocal connections in the EB (divided by the number of connections outside the EB)
- the prevalence of parallel connections is the number of matching connections in the EB (divided by the number of connections outside the EB)
- the prevalence of linked targets is the number of connections between any 2 of the targets in the EB, divided by the number of possible connections (n choose 2, where n is the number of targets)
```{r}
recurrentMotifsSummary <- group_by(EB2EBaxDendMat,
                                   type.from,supertype1.from,supertype3.from) %>% 
  summarize("EB parallel connection"=sum(paste0(type.from,type.to) %in% 
                                           paste0(allRecurrentEB$type.from,allRecurrentEB$type.to))/n(),
            "EB canonical feedback"=sum(paste0(type.to,type.from) %in% 
                                          paste0(allRecurrentEB$type.from,allRecurrentEB$type.to))/n(),
            "linked targets in EB"=if (n()==1) 0 else 
              sum(as.vector(combn(type.to,2,paste0,collapse="")) %in%
                    c(paste0(allRecurrentEB$type.from,allRecurrentEB$type.to),
                      paste0(allRecurrentEB$type.to,allRecurrentEB$type.from)))/(choose(n(),2))
  ) %>% ungroup()
head(recurrentMotifsSummary)
```

```{r}
recurrentMotifsSummary <- pivot_longer(recurrentMotifsSummary,
                                       c("EB parallel connection","EB canonical feedback","linked targets in EB"),
                                       names_to="stat",values_to="proportion") %>% 
  mutate(type.fromF = factor(type.from,levels=typesEBOrder),
         stat=factor(stat,levels=c("EB parallel connection","EB canonical feedback","linked targets in EB")))

#recurrentMotifSuperSummary <- recurrentMotifsSummary %>% group_by(supertype1.from,supertype3.from,stat) %>% 
#   summarize(proportion=mean(proportion))
```


```{r}
recurrentMotifsPrevalence <- ggplot(recurrentMotifsSummary %>% filter(supertype3.from == "ExR") ,aes(x=type.fromF,y=stat)) + 
   geom_point(size=3,color="grey90")+ 
   geom_point(aes(size=proportion,color=stat))  + 
   facet_grid(.~supertype1.from,scale="free",space="free")+ 
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.text.x = element_text(angle=90)) +
  xlab("CX output type") + scale_size_area(name="prevalence",max_size = 3) + ylab("motif") + 
  scale_color_paletteer_d(name="motif","ggthemes::Traffic")

#motifPal <- c("Plum",paletteer_d("ggthemes::Traffic")[1:3])
#names(motifPal) <- c("Out of CX pathways","CX parallel connection","CX canonical feedback","linked targets in CX")

recurrentMotifsPrevalence


```

```{r}
ggsave("ExR-motifPrevalence.pdf", plot = recurrentMotifsPrevalence, device='pdf', path = outputsFolder,
    scale = 1,height=2.5, width=5, useDingbats=FALSE)
#ggsave(paste0('motifSummary_',direction,'.pdf'), plot = recurrentMotifsPrevalence, device='pdf', path = outputsFolder,
#    scale = 1,height=2.5, width=5, useDingbats=FALSE)
```

## Motifs weight breakdown (panel C)
For each ExR type participating in motifs, we collate the motifs using the `getMotifsGraphDf` function (defined in **Outputs/outputFunctions-display.R**):
```{r}
supertypeMotifSummary <-  getMotifsGraphDf(mutate(EB2EBaxDendMat,roi="Outside"),allRecurrentEB,
                                           "ExR2_R","Path_weight") %>% 
  mutate(source = "ExR2_R")

for(mytype in c("ExR3_R","ExR5_R","ExR6_R","ExR7_R")){
   #c("ExR1_L","ExR2_R","ExR2_L","ExR3_R","ExR3_L","ExR4_R","ExR5_R","ExR5_L","ExR6_R","ExR7_R","ExR7_L")
   myMotifGraph = getMotifsGraphDf(mutate(EB2EBaxDendMat,roi="Outside"),
                                   allRecurrentEB,mytype,"Path_weight")  %>% 
     mutate(source = mytype)
   supertypeMotifSummary = bind_rows(supertypeMotifSummary, myMotifGraph)
}
```

We then sum all the weights of the connections involved in a given motif for a given ExR neuron:
```{r}
supertypeMotifSummary <- group_by(supertypeMotifSummary,supertype3.to,source,motif,roi) %>%
  summarize(weight=sum(weightRelative)) %>% ungroup()
#supertypeMotifSummary = supertypeMotifSummary %>% 
#  select(c(roi, source, motif, type.to, type.from, supertype1.to, supertype1.from,supertype2.to, supertype2.from, supertype3.to, supertype3.from, weightRelative))

```
And plot the result:
```{r}

typesInMotif = ggplot(data = supertypeMotifSummary %>% filter(motif != "NA" & roi == "EB") , aes(x=source, y=weight, fill=supertype3.to)) +
   geom_bar(position = "stack", stat="identity") + 
   facet_grid(rows=vars(motif),scale="free") +
   #scale_fill_manual(values=p36) + 
   scale_fill_manual(name="partner supertype",values=supertype3Palette) + 
  theme_paper(axis.text.x = element_text(angle = 90, hjust=0.95,vjust=0.2)) +
  xlab("") + ylab("relative weight")

typesInMotif

```

```{r}
ggsave('ExR-motifContributions.pdf', plot = typesInMotif, device='pdf', path = outputsFolder,
    scale = 1,height=3.5,width=3, useDingbats=FALSE)

#ggsave(paste0('motifTypesSummary_',direction,'.pdf'), plot = typesInMotif, device='pdf', path = outputsFolder,
#    scale = 1,height=3.5,width=3, useDingbats=FALSE)
```

## Motifs plots (panels D through G)



```{r}
for (mytype in c("ExR2_R","ExR3_R","ExR5_R","ExR6_R")){
  myMotifGraph <-  getMotifsGraphDf(EB2EBaxDendMat,allRecurrentEB,mytype,"Path_weight")
  canMot <- plotMotifs(myMotifGraph)
  #canMot
  ggsave(paste0('motifGraph',mytype,".pdf"),path=outputsFolder, device="pdf", plot=canMot,scale=1,width=5, height=3,useDingbats=FALSE)
}
#save_plot(paste0(c(outputsFolder,'motifGraph',mytype,'.pdf')), plot = canMot, base_width = 8.5,base_height = 11/4,device="pdf")
```

```{r}
mytype <- "ExR2_R"
myMotifGraph = getMotifsGraphDf(EB2EBaxDendMat,allRecurrentEB,mytype,"Path_weight")
  canMot <- plotMotifs(myMotifGraph)
  canMot
```


## Old code

```{r}

plotMotifsCustom <- function(graphDf){
  focusContrib <- filter(graphDf,roi=="Outside") %>% group_by(type.to) %>% summarize(weightRelative=sum(weightRelative)) %>% ungroup()
  motifGG <- makeGraph(graphDf) 
  edgePal <- c("Plum",paletteer_d("ggthemes::Traffic")[1:3])
  names(edgePal) <- c("Out of CX pathways","CX Parallel connection","CX Canonical feedback","Linked targets in CX")
  
  motifGG <- motifGG %N>% 
    mutate(
      customSuper = ifelse(layer,"Source",supertype2))
  
  #customPal <- c("Source"="grey50",supertype2Palette()$pal)
  
  return(ggraph(motifGG,layout="focus",focus=(motifGG %N>% as_tibble())$layer)+
           graphlayouts::draw_circle(max.circle = 1,col="grey90") +
           geom_edge_fan2(aes(color=motif,
                              width=weightRelative),
                          end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                          arrow =arrow(length = unit(1, 'mm'),type = "closed"))+
           geom_node_point(aes(color=customSuper),size=4)+
           #scale_color_manual(values=customPal) +
           guides(color="none") +
           theme_paper_map() + scale_edge_color_manual(name="Motif",values=edgePal,breaks=c("out of CX pathways","CX parallel connection","CX canonical feedback","linked targets in CX"),drop=FALSE)+
           scale_edge_width(name="relative weight/pathway weight",range=c(0.2,3),limits=c(0,1),)+
           geom_node_text(aes(label=name),size=1.5,nudge_y = 0.15) + 
           coord_fixed(clip="off"))
}

```

