---
title: "Analysis of ExR connectivity"
output:
  html_document:
    df_print: paged
---
#Analysis of ExR connectivity: Connectivity and similarity matrices, bar graph of partners
* Figure 14 B (similarity matrices)
* Figure 14 C (connectivity matrices) TODO
* Figure 14 figure supplement 2A (similarity matrices)
* Figure 14 figure supplement 2B (bar graph) TODO
* Figure 14 figure supplement 3A,B (connectivity matrices) TODO

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(plotly)
library(paletteer)
library(neuprintrExtra)
library(gridExtra)
options(nat.plotengine = 'rgl')

options(nat.plotengine = 'rgl')
source(file.path("..","R","visualizeConnectivityTables.R"))
source(file.path("..","R","paperTheme.R"))

neuprint_login()
```

### Saving plots
Indicate if you would like to save the plots here (defualt is false). Plots will be saved inside this folder in a subdirectory "plots"
```{r}
savePlot = TRUE
if (savePlot){
  dir.create("plots")
}
```

```{r}
myplot_dist <- function(dd,order=TRUE){
  ddM <- as.matrix(dd)
  if (order){
    hcl <- hclust(dd)
    ddM <- ddM[hcl$order,hcl$order]
  }
  ggplot(reshape2::melt(ddM)) + geom_tile(aes(x=Var1,y=Var2,fill=1-value)) +
    theme_classic() +
    scale_fill_gradient2(low="white", mid="grey", high="black", 
                         midpoint =0.5, limits=c(0,1), name="Similarity") +
    theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5)) + 
    xlab("") + ylab("")+coord_fixed() 
  
}
```

### Select types for comparison
```{r}
myTypeList = paste0(c("ExR"),seq(1,8))
side ="_R"
myTypeList_lat = paste0(myTypeList, side)
saveName = "ExR_comparison"

saveDir = "plots"
```

### Filter neuron bag to contain only subset of types (considering lateralization)
```{r}
myTypes_bag_full = neuronBag(myTypeList)
myTypes_bag_full = lateralize_types(myTypes_bag_full)
saveName = paste0(saveName,"_LR")

myTypes_bag =  filter(myTypes_bag_full, filterPartners = FALSE, type %in% myTypeList_lat)
```

### Generate list of ROIs to consider
```{r}
roiTree = getRoiTree()
slctROIs = selectRoiSet(roiTree, default_level = 2, 
                        exceptions = list("OL(R)"=1,"AL(R)"=1,"PENP"=1,"AL(L)"=1,"MB(+ACA)(R)"=1,"MB(L)"=1,
                                          "VMNP"=1,"INP"=1, "LX(R)"=3, "LX(L)"=3), exceptionLevelMatch = 1)
slctROIs = unique(slctROIs$roi)
slctROIs_r = slctROIs[!grepl("\\(L\\)",slctROIs)]
slctROIs_r
```

### Use raw inputs as few connections in non-CX ROIs are significant according to general criteria??
```{r}
myTypes_in = myTypes_bag$inputs
myTypes_out = myTypes_bag$outputs
myTypes = myTypes_bag$names
```


### Generate dataframe of inputs to types of interest
#### Filter based on rois to use
```{r}
minsyn = 3
minWeightRel = 0.001 #used to filter connectivity tables


myTypes_in_filt = myTypes_in %>% filter(roi %in% slctROIs) %>%
  #filter(type.to %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.to) %>% filter(sum(weight) >= minsyn) %>% filter(weightRelative >= minWeightRel)

myTypes_in_filt = bind_cols(myTypes_in_filt, data.frame(dir = rep("in", length(myTypes_in_filt$roi))))

myTypes_out_filt = myTypes_out %>% filter(roi %in% slctROIs) %>%
  #filter(type.from %in% c(paste0(myTypeList,side))) %>%
  group_by(roi,  type.from) %>% filter(sum(weight) >= minsyn) %>% filter(outputContribution >= minWeightRel)

myTypes_out_filt = bind_cols(myTypes_out_filt, data.frame(dir = rep("out", length(myTypes_out_filt$roi))))
```

#### select inputs to focus types in main input regions
```{r}
myROIs = unique(bind_rows(myTypes_in_filt, myTypes_out_filt)$roi)#[unique(myTypes_filt$roi)!="EB"] #
myROIs  

```


### Compare input and outputs to these types
#### select inputs to focus types in main input regions
For **Figure 14B** choose:
myROIs = myROIs 
myROIsName ="all"

For **Figure 14 figure supplement 2A** choose:
myROIs = myROIs[myROIs!="EB"] 
myROIsName ="allButEB" 
```{r}
myROIs = myROIs #myROIs[myROIs!="EB"] #
myROIsName ="all" #"allButEB" #
myROIs  

```

#### construct new connection table for combined ROIs
```{r}
myTypes_bag_comboRoi = combineRois(myTypes_bag, myROIs, "comboRoi")
typesInput_combiRoi = myTypes_bag_comboRoi$inputs %>% filter(type.to %in% myTypeList_lat)
typesOutput_combiRoi = myTypes_bag_comboRoi$outputs %>% filter(type.from %in% myTypeList_lat)

myTypeList_lat_in = unique(typesInput_combiRoi$type.to)
myTypeList_lat_out = unique(typesOutput_combiRoi$type.from)
```

#### Cluster input vectors to reference neurons 
Inputs (Figure 14 Bi, Figure 14 figure supplement Ai)
```{r}
conmat <- connectivityMatrix( typesInput_combiRoi, "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")

conmat_cd = cos_dist(conmat)
plt <- myplot_dist(conmat_cd, order=TRUE) + theme_paper(axis.text.x = element_text(angle = 90)) 
plt
hcl=hclust(conmat_cd)

cut = 0.7#0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8) + theme_paper()# + rect.hclust(hcl, h=cut, border = "red")
clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80

typeClusters <- stack(clu.h) %>% rename(type = ind, clust=values) %>% arrange(clust)
if (savePlot){
  ggsave( paste("inputCorrelation_",saveName,'_', myROIsName,'_nBag.pdf', sep=''), plot = plt, device='pdf', 
          path ="plots", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)
}
```
#### Cluster output vectors to reference neurons
Outputs (Figure 14 Bii, Figure 14 figure supplement Aii)
```{r}
conmat <- connectivityMatrix( typesOutput_combiRoi %>% filter(is.finite(weightRelative) ), "comboRoi", allToAll = FALSE, from = "type.from", to = "type.to", value = "weightRelative", ref = "outputs")
conmat_cd = cos_dist(t(conmat))
plt <- myplot_dist(conmat_cd, order=TRUE)
plt

hcl=hclust(conmat_cd)

cut = 0.8
tplt <- plot(hcl,hang= -.5,cex = 0.8)# + rect.hclust(hcl, h=cut, border = "red")
clu.h=cutree(hcl,h=cut) # cut tree/dendrogram from height 80
typePreClusters <- stack(clu.h) %>% rename(type = ind, preclust=values) %>% arrange(preclust)

if (savePlot){
  ggsave( paste("outputCorrelation_",saveName,'_', myROIsName,'_onPre_nBag.pdf', sep=''), plot = plt, device='pdf',
          path = "plots", scale = 1, width = 8, height = 8, units ="cm", dpi = 600, limitsize = TRUE)
}
```


## Visualize pre- and postsynaptic partners in bar graph
This will create **Figure 14 figure supplement 2B**
```{r}
inOutContributionDataPrep <- function(myTypes_in_filt, myTypes_out_filt,  supertypeLevel){
  inData = myTypes_in_filt %>% select(c("roi","databaseType.from","type.from", "type.to", "weightRelative","weight","absoluteWeight","outputContribution", "dir")) %>% 
    mutate(ref = type.to, measure=weightRelative) %>% rename(databaseType=databaseType.from)
  
  outData = myTypes_out_filt %>% select(c("roi","databaseType.to","type.from", "type.to","weightRelative", "weight","absoluteWeight","outputContribution", "dir")) %>% 
    mutate(ref = type.from, measure=outputContribution) %>% rename(databaseType=databaseType.to)
  
  if(supertypeLevel == 0){
    inData <- supertype(inData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
    
    outData <- supertype(outData) %>% selectSupertypeSet(default_level = 3,
                        exceptions = list("AOTU"=2,"TuBu"=2,"LAL"=2,"SMP"=2,"MBON"=2, "LNO"=2,"ER"=2, "ExR"=2),exceptionLevelMatch = 2) %>% mutate(partner = supertype, partner2=supertype2)
  }else{
    inData = supertype(inData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
    outData = supertype(outData) %>% mutate(partner=!!sym(paste0("supertype",supertypeLevel)))#(databaseType,supertypeLevel))
  }
  data = bind_rows(inData,outData)
  return(data)
}

for(st in c(0,2,3)){
  myTypes_filt = inOutContributionDataPrep(myTypes_in_filt, myTypes_out_filt,  st) %>% filter(roi %in% slctROIs_r)
  
  if(sum(is.na(myTypes_filt$partner)) > 0){
    myTypes_filt = myTypes_filt  %>% mutate(partner = coalesce(partner, "Other"))
  }
  bar = inOutContributionPlot(myTypes_filt)+ facet_grid(cols=vars(roi), rows=vars(dir), scales="free_x", space = "free") 
  show(bar)
  if (savePlot & st == 0){
    ggsave(paste("inputAndOutputComposition_",saveName,"_supertype",st,'.pdf', sep=''),plot = bar, device='pdf', path = "plots", scale = 1.5, width=23, height=10, units ="cm", dpi = 600, limitsize = TRUE)
  }
}

```

## Connectivity matrices between ExR and columnar neurons

```{r}
ROI = "EB"
slctROI ="EB"
makeAsymmetric = TRUE
postNeuron = paste0(paste0("ExR",seq(1,8)),".*")
postName = "ExR neurons"  #gets used in the connectivity matrix plot
preNeuron = paste0(c("PEN","PEG","EPG","EL"),".*")
preName = "columnar neurons"

postIDs = getBodyIdsForList(postNeuron)
preIDs = getBodyIdsForList(preNeuron)
```

### Get connectivity table
```{r, warning=FALSE}
preTypes = c(preIDs$bodyid, postIDs$bodyid)
postTypes = postIDs$bodyid
myConnections_Col2ExR = getConnectionTable(preTypes, "POST", slctROI)
myConnections_ExR2Col = getConnectionTable(postTypes, "POST", slctROI)

myConnections_Col2ExR = myConnections_Col2ExR %>% filter(to %in% postTypes) 
myConnections_ExR2Col = myConnections_ExR2Col %>% filter(to %in% preTypes) 
```

### Format the connectivity matrix, convert to type-to-type
```{r}
# Make asymmetric matrix
myConnections_Col2ExR = myConnections_Col2ExR %>% filter(to %in% postIDs$bodyid)  %>% filter(from %in% preIDs$bodyid) 
myConnections_ExR2Col = myConnections_ExR2Col %>% filter(to %in% preIDs$bodyid)  %>% filter(from %in% postIDs$bodyid) 

# Make type-to-type connectivity table
typesTable_Col2ExR <- getTypesTable(unique(myConnections_Col2ExR$databaseType.to))
typesTable_ExR2Col <- getTypesTable(unique(myConnections_ExR2Col$databaseType.to))

myConnectionsT2T_Col2ExR = getTypeToTypeTable(myConnections_Col2ExR,typesTable = typesTable_Col2ExR)
myConnectionsT2T_ExR2Col = getTypeToTypeTable(myConnections_ExR2Col,typesTable = typesTable_ExR2Col)
```

### Connectivity matrices
```{r}
cmax = NULL
cmaxtype = NULL
 
connectionMeasure = "weightRelative"
conMatPlot = plotConnectivityMatrix(myConnectionsT2T_Col2ExR, byGroup = "type", connectionMeasure, cmaxtype)
conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure) + theme_paper()
print(conMatPlot)

conMatPlot_id = plotConnectivityMatrix(myConnections_Col2ExR, byGroup = "id", connectionMeasure, cmax)
conMatPlot_id = addMatrixPlotLabs(conMatPlot_id, preName,  postName, slctROI, connectionMeasure)
conMatPlot_id = structureMatrixPlotByType_lines(conMatPlot_id)
print(conMatPlot_id)

if (savePlot){
  pw=10; ph=6
  ggsave(paste("connectivityMatrix_col2ExR_in_",slctROI,'_',connectionMeasure,'_bytype.pdf', sep=''), 
      plot = conMatPlot, device='pdf', path = "plots", scale=1, width=pw, height=ph, units ="cm", dpi = 600, limitsize = TRUE)
  
  pw=11; ph=22
  ggsave(paste("connectivityMatrix_col2ExR_in_",slctROI,'_',connectionMeasure,'_byID.pdf', sep=''), 
      plot = conMatPlot_id, device='pdf', path = "plots", scale=1, width=pw, height=ph, units ="cm", dpi = 600, limitsize = TRUE)
}
```

```{r}
conMatPlot = plotConnectivityMatrix(myConnectionsT2T_ExR2Col, byGroup = "type", connectionMeasure, cmaxtype)
conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure) + theme_paper()
print(conMatPlot)

conMatPlot_id = plotConnectivityMatrix(myConnections_ExR2Col, byGroup = "id", connectionMeasure, cmax)
conMatPlot_id = addMatrixPlotLabs(conMatPlot_id, preName,  postName, slctROI, connectionMeasure)
conMatPlot_id = structureMatrixPlotByType_lines(conMatPlot_id)
print(conMatPlot_id)

if (savePlot){
  pw=8; ph=7
  ggsave(paste("connectivityMatrix_ExR2col_in_",slctROI,'_',connectionMeasure,'_bytype.pdf', sep=''), 
      plot = conMatPlot, device='pdf', path = "plots", scale=1, width=pw, height=ph, units ="cm", dpi = 600, limitsize = TRUE)
  
  pw=24; ph=9
  ggsave(paste("connectivityMatrix_ExR2col_in_",slctROI,'_',connectionMeasure,'_byID.pdf', sep=''), 
      plot = conMatPlot_id, device='pdf', path = "plots", scale=1, width=pw, height=ph, units ="cm", dpi = 600, limitsize = TRUE)
}
```