---
title: "Analysis of wind (mechanosensoy) info comming into CX"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of mechanosensory information pathway coming into CX via R1 neurons

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(igraph)

options(nat.plotengine = 'rgl')
```

```{r}
neuprint_login()
```

```{r messages=FALSE, warning=FALSE}
# Get some custom functions
source("../R/visualizeConnectivityTables.R")
```

## Bodyid's of neurons that are potentially involved
The propose pathway presented in Suver et al is Johnstons organs -> APN3/APN2 -> WPN

Here we will try to identify which neurons in the EM volume correspond to APN2, APN3 and WPN and illustrate a potential route toward the fly's heading circuit.
```{r}
#APN3s (presynaptic of APN2s):
APN3ids = c(975289165, 1099073905, 1130458829)
#APN2s (postsynaptic of APN3s): 
APN2ids = c(1539649574, 2096909915, 2096913987)

# get names
for (i in APN3ids) {
  print(neuprint_get_neuron_names(i))
}
for (i in APN2ids) {
  print(neuprint_get_neuron_names(i))
}
```
We will also consider the putative WL-L neuron, which is wind sensitive and connects to R1
```{r}
#WL-L
WLLids = c(1386849677, 1539632818)

for (i in WLLids) {
  print(neuprint_get_neuron_names(i))
}
```

Get all neurons of the type described by the bodyids  above
```{r}
APN2type =  c("SAD004", "SAD003")
APN3type = "SAD077"
APN3 = neuprint_search("SAD077_.*")
APN2 = bind_rows(neuprint_search("SAD004.*"),neuprint_search("SAD003.*"))
APN2and3 = bind_rows(APN2, APN3) 

APNBodies = c(APN3$bodyid,APN2$bodyid)

WLLtype =  "LAL138"
WLL = neuprint_search(paste0(WLLtype,".*"))

```


Also get body ID's of putative downstream partners
```{r}
# Putative WPN, based on morphology and connectivity:
#(these were identified in a shortest path analysis as shown later)
WPNtype = "LHPV6q1"
WPN = neuprint_search(paste0(WPNtype,".*"))

# Ring neurons
ER1 = neuprint_search("ER1_.*")
ER1a = neuprint_search("ER1_a.*")
ER1b = neuprint_search("ER1_b.*")

ER3a_b = neuprint_search("ER3a_b.*")
ER3a= neuprint_search("ER3a.*")

ER1and3a =  bind_rows(ER1, ER3a_b) 
ER1and3 =  bind_rows(ER1, ER3a) 

ER1and3_andWLLWPN =  bind_rows(ER1, ER3a, WLL,WPN) 

splitLR = TRUE
```

## Connectivity between WLL and ER neurons
```{r, warning=FALSE}
splitLR = TRUE
preTypes = c(ER1and3_andWLLWPN$bodyid, ER1and3_andWLLWPN$bodyid) # preIDs$bodyid
postTypes = preTypes#postIDs$bodyid
myConnections = getConnectionTable(preTypes, "POST", NULL)
myConnections = myConnections %>% filter(to %in% postTypes) 
  
typesTable <- getTypesTable(unique(myConnections$databaseType.to))

if (splitLR){
  # Subdivide types and build a custom types table
  myConnections = lateralize_types(myConnections, postfix="to")
  myConnections = lateralize_types(myConnections, postfix="from")
  typesTable = lateralize_types(typesTable, postfix="raw")
}

myConnectionsT2T = getTypeToTypeTable(myConnections,typesTable = typesTable)
```

```{r}
plotW = 12
plotH = 10
cmax = NULL
cmaxtype = NULL

source("../R/visualizeConnectivityTables.R")

connectionMeasures = c("weightRelative")
saveName = "windPathway"
if(splitLR){saveName = paste0(saveName,"_LR")}

for (connectionMeasure in connectionMeasures){
  
  conMatPlot = plotConnectivityMatrix(myConnectionsT2T, byGroup = "type", connectionMeasure, cmaxtype)
  #conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  print(conMatPlot)
  ggsave( paste("connectivityMatrix_",saveName,'_',connectionMeasure,'_byType.pdf', sep=''), plot = conMatPlot, device='pdf', path = "../../neuprintR_analysis_plots/",scale = 1.5, width = plotW*0.8, height = plotH*0.8, units ="cm", dpi = 600, limitsize = TRUE)

  conMatPlot = plotConnectivityMatrix(myConnections, byGroup = "id", connectionMeasure, cmax)
  #conMatPlot = addMatrixPlotLabs(conMatPlot, preName,  postName, slctROI, connectionMeasure)
  conMatPlot = structureMatrixPlotByType_lines(conMatPlot)
  print(conMatPlot)
  ggsave(paste("connectivityMatrix_",saveName,"_",connectionMeasure,'_byID.pdf', sep=''), 
    plot = conMatPlot, device='pdf', path = "../../neuprintR_analysis_plots/",
    scale = 2, width = plotW, height =plotH, units ="cm", dpi = 600, limitsize = TRUE)
}
```


## Find paths to the CX
```{r}
maxL = 5

APN_to_ER1_t2tpath = get_type2typePath(APN2and3, ER1b, by.roi = FALSE, n_steps = seq(maxL),renaming=lateralize_types)
```

```{r}
APN_to_ER1or3_t2tpath = get_type2typePath(APN2and3, ER1and3, by.roi = FALSE, n_steps = seq(maxL),renaming=lateralize_types)
```

```{r}
cutoff = 0#0.02#0.01#
edcurve = 0.15
vertexSize = 7
edgeNorm = 0.04
minPathWeight = 0.1 ** maxL#
plotSize = 10

graphName = "pathGraph_APN_2_ER1or3_0-1-exp5"

pathDf = APN_to_ER1or3_t2tpath %>% filter(weightRelative_path  >= minPathWeight )

graphDataFrame = pathDf2graphDf(pathDf) %>% mutate(relWeight =  weightRelative)

myGraph = constructConnectivityGraph(graphDataFrame, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm)

l = layout_with_dh(myGraph)
myGraph$main = paste("Min path weight = ", minPathWeight)

plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph), 
     family="Arial", vertex.label.family  = "sans")
maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-0.8,y=1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)),  bty = "n", seg.len=0.5)

dev.print(pdf, paste0("../../neuprintR_analysis_plots/",graphName,".pdf"), width=plotSize, height=plotSize,useDingbats=FALSE)
```

```{r}
patternLayers =c("SAD","WED","WEDPN","PV","LAL","ER")
layerPos = c(0,2,3,4,5,6)
defaultY = 1
edcurve = 0.1

myGraph = constructConnectivityGraph(graphDataFrame, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm)

vertexProps = data.frame(name = V(myGraph)$name, col = V(myGraph)$color) %>% mutate(name = gsub("_[R,L]", "", name))
vertexProps = vertexProps %>% mutate(loc = "default", yloc = seq(length(vertexProps$col)), xloc = defaultY)

for(layer in seq(length(patternLayers))){
  vertexProps[grepl(patternLayers[layer],vertexProps$name),] = vertexProps[grepl(patternLayers[layer],vertexProps$name),] %>% 
    mutate(loc = paste0("layer",layerPos[layer]+1), xloc = layerPos[layer], yloc = 1*seq(length(loc)))
}
vertexProps$yloc[vertexProps$loc == "default"] = 1*seq(length(vertexProps$loc[vertexProps$loc == "default"]))


plot(myGraph,edge.curved=edcurve, layout=layout.norm(as.matrix(vertexProps[,c("xloc","yloc")])), edge.color = customizeGraphEdges(myGraph), 
     family="Arial",family="Arial", vertex.label.family  = "sans")

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=0.8,y=1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)),  bty = "n", seg.len=0.5)

dev.print(pdf, paste0("../../neuprintR_analysis_plots/",graphName,"_structured.pdf"), width=plotSize, height=plotSize,useDingbats=FALSE)

```
