---
title: "Analysis of wind (mechanosensoy) info comming into CX"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#Analysis of mechanosensory information pathway coming into CX via R1 neurons

```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(neuprintrExtra)
library(igraph)

options(nat.plotengine = 'rgl')
```

```{r}
neuprint_login()
```

```{r messages=FALSE, warning=FALSE}
# Get some custom functions
source("../visualizeConnectivityTables.R")
```

## Bodyid's of neurons that are potentially involved
The propose pathway presented in Suver et al is Johnstons organs -> APN3/APN2 -> WPN

Here we will try to identify which neurons in the EM volume correspond to APN2, APN3 and WPN and illustrate a potential route toward the fly's heading circuit.
```{r}
#APN3s (presynaptic of APN2s):
APN3ids = c(975289165, 1099073905, 1130458829)
#APN2s (postsynaptic of APN3s): 
APN2ids = c(1539649574, 2096909915, 2096913987)

# get names
for (i in APN3ids) {
  print(neuprint_get_neuron_names(i))
}
for (i in APN2ids) {
  print(neuprint_get_neuron_names(i))
}
```
We will also consider the putative WL-L neuron, which is wind sensitive and connects to R1
```{r}
#WL-L
WLLids = c(1386849677, 1539632818)

for (i in WLLids) {
  print(neuprint_get_neuron_names(i))
}
```

Get all neurons of the type described by the bodyids  above
```{r}
APN2type =  c("SAD004", "SAD003")
APN3type = "SAD077"
APN3 = neuprint_search("SAD077_.*")
APN2 = bind_rows(neuprint_search("SAD004.*"),neuprint_search("SAD003.*"))
APN2and3 = bind_rows(APN2, APN3) 

APNBodies = c(APN3$bodyid,APN2$bodyid)

WLLtype =  "LAL138"
WLL = neuprint_search(paste0(WLLtype,".*"))

```


Also get body ID's of putative downstream partners
```{r}
# Putative WPN, based on morphology and connectivity:
#(these were identified in a shortest path analysis as shown later)
WPNtype = "LHPV6q1"
WPN = neuprint_search(paste0(WPNtype,".*"))

# Ring neurons
ER1 = neuprint_search("ER1_.*")
ER1a = neuprint_search("ER1_a.*")
ER1b = neuprint_search("ER1_b.*")

ER3a_b = neuprint_search("ER3a_b.*")

ER1and3 =  bind_rows(ER1, ER3a_b) 

splitLR = TRUE
```


## Find paths to the CX
```{r}
maxL = 5

APN_to_ER1_t2tpath = get_type2typePath(APN2and3, ER1b, by.roi = FALSE, n_steps = seq(maxL),renaming=lateralize_types)
```

```{r}
APN_to_ER1or3_t2tpath = get_type2typePath(APN2and3, ER1and3, by.roi = FALSE, n_steps = seq(maxL),renaming=lateralize_types)
```

```{r}
cutoff = 0#0.02#0.01#
edcurve = 0.15
vertexSize = 7
edgeNorm = 0.04
minPathWeight = 0.1 ** maxL#
plotSize = 10

graphName = "pathGraph_APN_2_ER1or3_0-1-exp5"

pathDf = APN_to_ER1or3_t2tpath %>% filter(weightRelative_path  >= minPathWeight )

graphDataFrame = pathDf2graphDf(pathDf) %>% mutate(relWeight =  weightRelative)

myGraph = constructConnectivityGraph(graphDataFrame, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm)

l = layout_with_dh(myGraph)
myGraph$main = paste("Min path weight = ", minPathWeight)

plot(myGraph,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph), 
     family="Arial", vertex.label.family  = "sans")
maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=-0.8,y=1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)),  bty = "n", seg.len=0.5)

dev.print(pdf, paste0("../../neuprintR_analysis_plots/",graphName,".pdf"), width=plotSize, height=plotSize,useDingbats=FALSE)
```

```{r}
patternLayers =c("SAD","WED","WEDPN","PV","LAL","ER")
layerPos = c(0,2,3,4,5,6)
defaultY = 1
edcurve = 0.1

myGraph = constructConnectivityGraph(graphDataFrame, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm)

vertexProps = data.frame(name = V(myGraph)$name, col = V(myGraph)$color) %>% mutate(name = gsub("_[R,L]", "", name))
vertexProps = vertexProps %>% mutate(loc = "default", yloc = seq(length(vertexProps$col)), xloc = defaultY)

for(layer in seq(length(patternLayers))){
  vertexProps[grepl(patternLayers[layer],vertexProps$name),] = vertexProps[grepl(patternLayers[layer],vertexProps$name),] %>% 
    mutate(loc = paste0("layer",layerPos[layer]+1), xloc = layerPos[layer], yloc = 1*seq(length(loc)))
}
vertexProps$yloc[vertexProps$loc == "default"] = 1*seq(length(vertexProps$loc[vertexProps$loc == "default"]))


plot(myGraph,edge.curved=edcurve, layout=layout.norm(as.matrix(vertexProps[,c("xloc","yloc")])), edge.color = customizeGraphEdges(myGraph), 
     family="Arial",family="Arial", vertex.label.family  = "sans")

maxEdge = max(E(myGraph)$width)
minEdge = min(E(myGraph)$width)
legend(x=0.8,y=1, legend = edgeNorm*seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)), 
       lwd	 = seq(round(minEdge, digits = 0),round(maxEdge, digits = 0)),  bty = "n", seg.len=0.5)

dev.print(pdf, paste0("../../neuprintR_analysis_plots/",graphName,"_structured.pdf"), width=plotSize, height=plotSize,useDingbats=FALSE)

```


## Find paths to the CX -- OLD METHOD
```{r}
allPathFromAPN_to_R1 = neuprint_get_paths(APNBodies,ER1$bodyid, n=4, weightT = 10, chunk = 1)

allPathFromWLL_to_R1 = neuprint_get_paths(WLL$bodyid,ER1$bodyid, n=2, weightT = 10, chunk = 2)

allPathFromAPN_to_WLL = neuprint_get_paths(APNBodies,WLL$bodyid, n=4, weightT = 10, chunk = 1)

allPathFromAPN_to_R3 = neuprint_get_paths(APNBodies,ER3a_b$bodyid, n=4, weightT = 10, chunk = 1)

allPathFromWLL_to_R3 = neuprint_get_paths(WLL$bodyid,ER3a_b$bodyid, n=2, weightT = 10, chunk = 1)
```

```{r}
allPathFromWPN_to_R1 = neuprint_get_paths(WPN$bodyid,ER1$bodyid, n=2, weightT = 10, chunk = 1)

allPathFromWPN_to_R3 = neuprint_get_paths(WPN$bodyid,ER3a_b$bodyid, n=2, weightT = 10, chunk = 1)
```


## Viusualize paths to the CX

```{r}

cutoff = 0.02#0.01#
edcurve = 0
vertexSize = 7
edgeNorm = 0.05

# helper functions
getPathConnections <- function(fromIDs, toIDs){
  
  pathConnections = getConnectionTable(unique(fromIDs), "POST")
  pathConnections = pathConnections %>% filter(to %in% unique(toIDs) )
  
  pathConnections = lateralize_types(pathConnections, postfix="to")
  pathConnections = lateralize_types(pathConnections, postfix="from")
  typesTable = getTypesTable(unique(pathConnections$databaseType.to))
  typesTable = lateralize_types(typesTable, postfix="raw")
  
  return(pathConnections)
}

```

### APN or WLL to R1
```{r}
#APN -> R1
APNpathConnections = getPathConnections(allPathFromAPN_to_R1$from,allPathFromAPN_to_R1$to)
typesTable <- getTypesTable(unique(APNpathConnections$databaseType.to))
myAPNPathT2T = getTypeToTypeTable(APNpathConnections,typesTable = typesTable)

# WLL -> R1
WLLpathConnections = getPathConnections(allPathFromWLL_to_R1$from,allPathFromWLL_to_R1$to)
typesTable <- getTypesTable(unique(WLLpathConnections$databaseType.to))
myWLLPathT2T = getTypeToTypeTable(WLLpathConnections,typesTable = typesTable)

# WPN -> R1
WPNpathConnections = getPathConnections(allPathFromWPN_to_R1$from,allPathFromWPN_to_R1$to)
typesTable <- getTypesTable(unique(WPNpathConnections$databaseType.to))
myWPNPathT2T = getTypeToTypeTable(WPNpathConnections,typesTable = typesTable)
```

```{r}
myPathT2T = full_join(full_join(myAPNPathT2T, myWLLPathT2T),myWPNPathT2T)

graphData = data.frame(from = myPathT2T$type.from,
                       to = myPathT2T$type.to,
                       relWeight = myPathT2T$weightRelative)

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale=1, arrowSize=0.4, edgeNorm)

# remove nodes that are not on path
APN2list = paste0(APN2type,'_R')
APN3list = paste0(APN3type,'_R')

WLLlist = c(paste0(WLLtype,'_L'))#,paste0(WLLtype,'_R'))
WPNlist =  c(paste0(WPNtype,'_L'))#,paste0(WLLtype,'_R'))

ERlist = c("ER1_a_R","ER1_b_L","ER1_b_R")

path2R1_1 = all_simple_paths(myGraph, V(myGraph)[APN2list], to = V(myGraph)[ERlist], mode = "out")
path2R1_2 = all_simple_paths(myGraph, V(myGraph)[APN3list], to = V(myGraph)[ERlist], mode = "out")
path2R1_3 = all_simple_paths(myGraph, V(myGraph)[WPNlist], to = V(myGraph)[ERlist], mode = "out")
path2R1_4 = all_simple_paths(myGraph, V(myGraph)[WLLlist], to = V(myGraph)[ERlist], mode = "out")

onpath = V(myGraph)[unique(c(unlist(path2R1_1),unlist(path2R1_2),unlist(path2R1_3),unlist(path2R1_4)))]

if(length(onpath) > 0){
  myR1Graph_filt = subgraph(myGraph, onpath)
}else{
  myR1Graph_filt = myGraph
}

l = layout_with_dh(myR1Graph_filt)

plot(myR1Graph_filt,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myR1Graph_filt))


dev.print(pdf, paste0("../neuprintR_analysis_plots/mechanoPW/connectivityGraph_APN_or_WPN_or_WLL_to_R1b_LR_",100*cutoff,"prcCutoff.pdf"), width=10, height=10)
```

# APN -> WLL
```{r}
pathConnections = getPathConnections(allPathFromAPN_to_WLL$from,allPathFromAPN_to_WLL$to)
typesTable <- getTypesTable(unique(pathConnections$databaseType.to))
typesTable = lateralize_types(typesTable, postfix="raw")

myPathT2T = getTypeToTypeTable(pathConnections,typesTable = typesTable)
```

```{r}
graphData = data.frame(from = myPathT2T$type.from,
                       to = myPathT2T$type.to,
                       relWeight = myPathT2T$weightRelative)

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm)

#set_vertex_attr(myGraph, n_neurons, index = V(myGraph), value)
myGraph$names = myPathT2T %>% select(c(type.to, n_targets)) %>% unique()

# remove nodes that are not on path
APN2list = paste0(APN2type,'_R')
APN3list = paste0(APN3type,'_R')

WLLlist = c(paste0(WLLtype,'_L'),paste0(WLLtype,'_R'))
WPNlist =  c(paste0(WPNtype,'_R'))#,paste0(WLLtype,'_R'))

path2WLL_1 = all_simple_paths(myGraph, V(myGraph)[WPNlist], to = V(myGraph)[WLLlist], mode = "out")
path2WLL_2 = all_simple_paths(myGraph, V(myGraph)[APN2list], to = V(myGraph)[WLLlist], mode = "out")
path2WLL_3 = all_simple_paths(myGraph, V(myGraph)[APN3list], to = V(myGraph)[WLLlist], mode = "out")

onpath = V(myGraph)[unique(c(unlist(path2WLL_1),unlist(path2WLL_2),unlist(path2WLL_3)))]

if(length(onpath) > 0){
  myWLLGraph_filt = subgraph(myGraph, onpath)
}else{
  myWLLGraph_filt = myGraph
}

l = layout_with_dh(myWLLGraph_filt)

myPathT2T_filt  = as_data_frame(myWLLGraph_filt)
myPathT2T_filt

plot(myWLLGraph_filt,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myWLLGraph_filt))
dev.print(pdf, paste0("../neuprintR_analysis_plots/mechanoPW/connectivityGraph_APN_to_WLL_LR_",100*cutoff,".pdf"), width=10, height=10)
```

### APN -> R3
```{r}
#APN -> R3
APNpathConnections = getPathConnections(allPathFromAPN_to_R3$from,allPathFromAPN_to_R3$to)
typesTable <- getTypesTable(unique(APNpathConnections$databaseType.to))
typesTable = lateralize_types(typesTable, postfix="raw")

myAPNPathT2T = getTypeToTypeTable(APNpathConnections,typesTable = typesTable)

# WLL -> R3
WLLpathConnections = getPathConnections(allPathFromWLL_to_R3$from,allPathFromWLL_to_R3$to)
typesTable <- getTypesTable(unique(WLLpathConnections$databaseType.to))
typesTable = lateralize_types(typesTable, postfix="raw")

myWLLPathT2T = getTypeToTypeTable(WLLpathConnections,typesTable = typesTable)

# WPN -> R3
WPNpathConnections = getPathConnections(allPathFromWPN_to_R3$from,allPathFromWPN_to_R3$to)
typesTable <- getTypesTable(unique(WPNpathConnections$databaseType.to))
typesTable = lateralize_types(typesTable, postfix="raw")

myWPNPathT2T = getTypeToTypeTable(WPNpathConnections,typesTable = typesTable)
```

```{r}
myPathT2T = full_join(full_join(myAPNPathT2T,myWPNPathT2T),myWLLPathT2T)

graphData = data.frame(from = myPathT2T$type.from,
                       to = myPathT2T$type.to,
                       relWeight = myPathT2T$weightRelative)

myGraph = constructConnectivityGraph(graphData, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm)

# remove nodes that are not on path

APN2list = paste0(APN2type[1],'_R')
APN3list = paste0(APN3type,'_R')

WLLlist = c(paste0(WLLtype,'_L'))#,paste0(WLLtype,'_R'))
WPNlist =  c(paste0(WPNtype,'_R'))#,paste0(WLLtype,'_L'))
ERlist = c("ER3a_b_R","ER3a_b_L")

path2R3_1 = all_simple_paths(myGraph, V(myGraph)[APN2list], to = V(myGraph)[ERlist], mode = "out")
path2R3_2 = all_simple_paths(myGraph, V(myGraph)[APN3list], to = V(myGraph)[ERlist], mode = "out")
path2R3_4 = all_simple_paths(myGraph, V(myGraph)[WLLlist], to = V(myGraph)[ERlist], mode = "out")
path2R3_5 = all_simple_paths(myGraph, V(myGraph)[WPNlist], to = V(myGraph)[ERlist], mode = "out")

onpath = V(myGraph)[unique(c(unlist(path2R3_1),unlist(path2R3_2),unlist(path2R3_4),unlist(path2R3_5)))] #,unlist(path2R3_3)

if(length(onpath) > 0){
  myR3Graph_filt = subgraph(myGraph, onpath)
}else{
  myR3Graph_filt = myGraph
}

l = layout_with_dh(myR3Graph_filt)

plot(myR3Graph_filt,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myR3Graph_filt))

dev.print(pdf, paste0("../neuprintR_analysis_plots/mechanoPW/connectivityGraph_APN_or_WPN_or_WLL_to_R3a_b_LR_",100*cutoff,".pdf"), width=10, height=10)

```
### Merge graphs of APN -> R1 and APN -> WLL and APN -> R3a_b
```{r}
myGraph_union_data = bind_rows(as_long_data_frame(myR1Graph_filt),as_long_data_frame(myWLLGraph_filt),
                               as_long_data_frame(myR3Graph_filt))

myGraph_union_data = myGraph_union_data %>% select(c(from_name, to_name, relWeight)) %>% 
  rename(from = from_name, to = to_name)

myGraph_union = constructConnectivityGraph(myGraph_union_data, cutoff, vertexSize, selfFBscale=1, arrowSize=0, edgeNorm)

l = layout_with_dh(myGraph_union)

plot(myGraph_union,edge.curved=edcurve, layout=l, edge.color = customizeGraphEdges(myGraph_union))

dev.print(pdf, paste0("../neuprintR_analysis_plots/mechanoPW/connectivityGraph_APN_to_WLL_to_R1_or_R3_LR_",100*cutoff,".pdf"), width=10, height=10)
```

