---
title: "Notebook for plotting average FB columnar neuron locations"
output:
  html_document:
    df_print: paged
---

# Load libraries
```{r message=FALSE, warning=FALSE}
library(neuprintrExtra)
library(neuprintr)
library(ggraph)
library(stringr)
library(dplyr)
library(prismatic)
```

# Make directories where figures will be saved to
```{r}

# Directory where synapse location data is stored (output of FB_GetAndSave_Synapses.Rmd)
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directories to save plots to.
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/Figure_ColumnLocations/"
PlotDirKmean=paste(PlotDir,"Kmeans_Examples/",sep='')
FigureDir=paste(PlotDir,"/Column_Locations/",sep='')

# Create plot directories if they dont exists yet
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
if (!dir.exists(PlotDirKmean)){dir.create(PlotDirKmean)}
if (!dir.exists(FigureDir)){dir.create(FigureDir)}

```

# Connect to neuprint server.
```{r}
neuprint_login()
```

# Get general functions
```{r}

source("FB_Analysis_Utils.R")

```

# Load pre-processed synapse location data and remove variables that won't be used
```{r}

load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
rm(list=c("roiEigen","Mesh_FB_Points","Mesh_FB_L1_Points", "Mesh_FB_L2_Points","Mesh_FB_L3_Points", "Mesh_FB_L4_Points",
          "Mesh_FB_L5_Points", "Mesh_FB_L6_Points","Mesh_FB_L7_Points", "Mesh_FB_L8_Points", "Mesh_FB_L9_Points","origin"))

# Assign Side, PB glom, and FB col info
FBC_SynsAll=Assign_FBcol_PBglom(FBC_SynsAll, "name", "Side", "PBglom", "FBcol")

```


# For neurons with arbors in two non-contiguous columns (the hDelta and C0 vDeltas), loop over each neuron
# and find the median location of its two arbors using K-mean clustering.
```{r message=FALSE, warning=FALSE}

# Get all hDelta neurons and the C0 vDelta neurons (those that innervate C1/C9)
Delta_SynsAll=subset(FBC_SynsAll, startsWith(type,"hDelta") | ((startsWith(type,"vDelta") & FBcol=="C0")) )
Delta_Types=unique(Delta_SynsAll$type)

# Make pre/post = 1/0
Delta_SynsAll$prepost[Delta_SynsAll$prepost == "Output"] = 1
Delta_SynsAll$prepost[Delta_SynsAll$prepost == "Input"] = 0
Delta_SynsAll$prepost=as.numeric(Delta_SynsAll$prepost)

# Loop over all individual neurons and find median location of pre/post arbors
SynThresh=10 # Minimum number of synapses per layer to run kmeans on (10 is good here)
PLOT=TRUE    # Whether to plot every neuron's synaptic point cloud and kmean groups
Delta_ColumnPositions=data.frame(LR=character(),X=numeric(),Y=numeric(), Z=numeric(), 
                                 bodyid=character(), type=character(), name=character(),
                                 prepost=numeric(), Layer=character(), numsyns=numeric())
for (ttt in 1:length(Delta_Types)){
  
  # Get synapses for just this neuron type
  TempTypeSynsAll=subset(Delta_SynsAll, type == Delta_Types[ttt])
  
  # Loop over neurons and plot data
  TempBodyIds=unique(TempTypeSynsAll$bodyid)
  for (nnn in 1:length(TempBodyIds)){
    
    # Get data just for this neuron
    TempNeuronData=subset(TempTypeSynsAll, bodyid == TempBodyIds[nnn])
    TempNeuronData$LR=NA
    
    # Perform K-means on synapses from all layers, add data to dataframe, and plot
    CurrentLayer="FB"
    TempNeuronData=Kmeans_Synapses(TempNeuronData)
    CurrentColumnPositions=ComputeMeanArbor(TempNeuronData, CurrentLayer)
    Delta_ColumnPositions=rbind(Delta_ColumnPositions,CurrentColumnPositions)
    eval(parse(text= paste("OUTLINE=Outline_", CurrentLayer,"_XZ",sep="")))
    if (PLOT==TRUE){Plot_Kmeans(TempNeuronData, CurrentColumnPositions, OUTLINE, CurrentLayer, PlotDirKmean)}
    
    # Now perform K-means on synapses in each layer, add data to dataframe
    TempLayers=sort(unique(TempNeuronData$Layer))
    for (lll in 1:length(TempLayers)){
  
      # Get data just for this layer
      TempLayerData=subset(TempNeuronData, Layer == TempLayers[lll])
      TempLayerData$LR=NA
      
      if (length(TempLayerData$bodyid)>=SynThresh){
        # Note that not all layers will have two clear clusters, especially those with very few synapses,
        # but these will get filtered out in the plotting steps in the next section.
        CurrentLayer=TempLayers[lll]
        TempLayerData=Kmeans_Synapses(TempLayerData)
        CurrentColumnPositions=ComputeMeanArbor(TempLayerData, CurrentLayer)
        
        # check to make sure the two clusters are actually well separated in space before adding to dataframe.
        if (abs(diff(CurrentColumnPositions$X))>3000){ 
          Delta_ColumnPositions=rbind(Delta_ColumnPositions, CurrentColumnPositions)
          eval(parse(text= paste("OUTLINE=Outline_", CurrentLayer,"_XZ",sep="")))
          if (PLOT==TRUE){Plot_Kmeans(TempLayerData, CurrentColumnPositions, OUTLINE, CurrentLayer, PlotDirKmean)}
        }
      }
    }
  }
}

```


# Plot the median location of each neuron's synapse distribution as a way to show where column locations are
# and how evenly spaced they are.
```{r message=FALSE, warning=FALSE}

# Get names of all FB columnar neuron types
Columnar_Types=sort(unique(FBC_SynsAll$type))

# Get median column locations, by layer, for all FB columnar neurons 
ColumnPositions_All= FBC_SynsAll %>% group_by(bodyid, name, Layer, type) %>% summarise(X=median(X),Y=median(Y), Z=median(Z), numsyns=n())
ColumnPositions_All$LR="Neither"
ColumnPositions_All$prepost="Neither"

# Get median column locations, across all layers , for all FB columnar neurons 
ColumnPositions_All_FB= FBC_SynsAll %>% group_by(bodyid, name, type) %>% summarise(X=median(X),Y=median(Y), Z=median(Z), numsyns=n())
ColumnPositions_All_FB$LR="Neither"
ColumnPositions_All_FB$prepost="Neither"
ColumnPositions_All_FB$Layer="FB"

# Combine layer-specific and all-FB column locations
ColumnPositions_All_FB=ColumnPositions_All_FB[colnames(ColumnPositions_All)]
ColumnPositions_All=rbind(as.data.frame(ColumnPositions_All),as.data.frame(ColumnPositions_All_FB))
remove(ColumnPositions_All_FB)

# Assign PB-FB-XX shapes based on L/R PB innervation
Delta_ColumnPositions=Assign_FBcol_PBglom(Delta_ColumnPositions, "name", "Side", "PBglom", "FBcol")
ColumnPositions_All=Assign_FBcol_PBglom(ColumnPositions_All, "name", "Side", "PBglom", "FBcol")
ColumnPositions_All$prepost[startsWith(ColumnPositions_All$type,"PF")]=ColumnPositions_All$Side[startsWith(ColumnPositions_All$type,"PF")]
ColumnPositions_All=ColumnPositions_All[colnames(Delta_ColumnPositions)]

# Get rid of neurons with two arbors, whose locations were computed above
ColumnPositions_All=subset(ColumnPositions_All,!bodyid %in% unique(Delta_ColumnPositions$bodyid))

# Add the neurons with two arbors back in
ColumnPositions_All=rbind(as.data.frame(ColumnPositions_All),as.data.frame(Delta_ColumnPositions))

# Make bodyid a factor
ColumnPositions_All$bodyid=as.factor(ColumnPositions_All$bodyid)

# Loop over columnar cell types and make plots
for (ttt in 1:length(Columnar_Types)){
  
  # Get synapses for just this neuron type
  TempTypeSynsAll=subset(ColumnPositions_All, type == Columnar_Types[ttt])
  
  # Find max columns for this type
  TempColNum=length(unique(TempTypeSynsAll$FBcol))
    
  # Plot median neuron location for all FB layers
  CurrentLayer="FB"
  PlotData=subset(TempTypeSynsAll, Layer==CurrentLayer)
  eval(parse(text= paste("OUTLINE=Outline_", CurrentLayer,"_XZ",sep="")))
  PlotData=GetColorFactor(PlotData, TempColNum)
  Colors=GetColorPalette(PlotData, TempColNum)
  PlotColLocs(PlotData, TempTypeSynsAll, Colors, OUTLINE, CurrentLayer, FigureDir)
  
  # Plot median neuron location for layer with most synapses (and layer 1 for vDelta types)
  LayersToPlot=TempTypeSynsAll %>% group_by(Layer) %>% summarise(Total_numsyns=sum(numsyns)) %>%
    subset(!startsWith(as.character(Layer),"FB")) %>% subset(Total_numsyns==max(Total_numsyns))
  LayersToPlot=as.character(LayersToPlot$Layer)
  if (startsWith(Columnar_Types[ttt],"vDelta")){LayersToPlot=c(LayersToPlot,"L1")}
  for (lll in 1:length(LayersToPlot)){
    CurrentLayer=LayersToPlot[lll]
    PlotData=subset(TempTypeSynsAll, Layer == CurrentLayer)
    eval(parse(text= paste("OUTLINE=Outline_", CurrentLayer,"_XZ",sep="")))
    PlotData=GetColorFactor(PlotData, TempColNum)
    Colors=GetColorPalette(PlotData, TempColNum)
    PlotColLocs(PlotData, TempTypeSynsAll, Colors, OUTLINE, CurrentLayer, FigureDir)
  }
}

```


# Save column position information for later use
```{r}

save(ColumnPositions_All, file = paste(SaveDir,"FB_ColumnPositions.RData",sep=""))

```

