---
title: "Notebook analyzing MBON to CX connections"
output:
  html_document:
    df_print: paged
---

# Load libraries
```{r message=FALSE, warning=FALSE}
library(neuprintrExtra)
library(neuprintr)
library(ggraph)
library(tidyverse)
library(tidygraph)
library(paletteer)
library(scales)
library(prismatic)
```

# Make directory to save plots to
```{r}

PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/MBONs2Cx/"
if (!dir.exists(PlotDir)){dir.create(PlotDir)}

```

# Connect to neuprint server
```{r}

```

# Get general functions
```{r}

source("FB_Mbon_to_Cx_Utils.R")

```

# Get all MBONs and table of CX neuron types
```{r message=FALSE, warning=FALSE}

# Get all MBONs
MB_NamedBodies=neuprint_search("^MBON.*")

# Load table of known CX types
CXTypes <- supertype(read_csv( paste(dirname(getwd()),"\\CX-cell-types060920.csv",sep="") ))$n.type

```


# ####################################################################################################################
# ######### Figure 1: MBON to CX direct connections ##################################################################
# ####################################################################################################################


# Get MBON to CX direct connections
```{r message=FALSE, warning=FALSE}

# Get MBON downstream connections, segregated by hemisphere (i.e. lateralized)
# Lateralization is important because it keeps the postsynaptic L and R groups separate.
# That way, when computing type-to-type weights, we aren't biased by postsyanptic neurons whose
# inputs may be cut, which could contribute a 0 weight just because of cut fibers. 
DownBag_L1=neuronBag(MB_NamedBodies, by.roi=TRUE, omitInputs=TRUE, omitOutputs=FALSE) %>% lateralize_types()

# Compute relative weight by summing ROIs not in the CX and not on the left side of the brain, which deals with polarity and lateralization issues.
# Polarity, since most FBt types receive a lot of input in the CX, the roi-independent relative weight can be very low.
# Lateralization, since some CX targets could have  dendrites on the left or dendrites on the right or both. 
# So it's best to use all MBONs (L and R) and just look at their targets in right ROIs (which should be more complete).
roiH <- getRoiTree()
outsideRegions <- unique(selectRoiSet(exceptions=sapply(as.character(unique(roiH$level1[grepl(roiH$level1,pattern="(R)")])),
                  function(i) return(1),USE.NAMES = TRUE,simplify=FALSE), exceptionLevelMatch = 1)$roi[roiH$level1!="CX" & roiH$side4!="Left"])
DownBag_L1 <- combineRois(DownBag_L1, outsideRegions, newRoi="NonCX") # Sum synapses across all non-CX ROIs on the right side 
                                  
# Recompute the lateralized type-to-type table but without using the t-test significance criteria. Because many FB tangential types 
# are composed of two neurons, the t-test can occasionally filter out strong connetions involving two neurons with variable weights. 
DownTypes_L1=getTypesTable(unique(c(DownBag_L1$outputs_raw$databaseType.from, DownBag_L1$outputs_raw$databaseType.to))) %>% lateralize_types()
Downstream_T2T_L1=getTypeToTypeTable(DownBag_L1$outputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0,
                                     singleNeuronThresholdN = 3, pThresh = 1, typesTable = DownTypes_L1, oldTable = NULL) 

# Restrict to just strong connetions to CX types (i.e. relative weight > 0.01 and at least 10 synapses).
MB2CX_Direct=subset(Downstream_T2T_L1, databaseType.to %in% CXTypes  & weightRelative>0.01 & weight>10)
MB2CX_Direct_Exclude=subset(Downstream_T2T_L1, databaseType.to %in% CXTypes & !(weightRelative>0.01 & weight>10) )

```


# Make network graph showing MBON to CX direct connections
```{r message=FALSE, warning=FALSE}

# Get just the MBON-->CX pairs with max weight, regardless of hemisphere. We can't jut average L/R pairs because relative
# weights needs to first be summed over all postsynaptic neurons, but this is hard to do, since we don't
# know for certain which fibers have been cut (would have to look at all CX and MBON neurons in detail). 
Graph_Data=MB2CX_Direct %>% group_by(databaseType.from, databaseType.to) %>% filter(weight == max(weight))
Graph_Data$type.from=Graph_Data$databaseType.from
Graph_Data$type.to=Graph_Data$databaseType.to

# Cluster the FB neurons by their input vectors
Graph_Data_Clust=connectivityCluster(inputsTable = Graph_Data, outputsTable = NULL) %>% setClusters(h = 0.8, k = NULL)
Graph_Data_Clust=Graph_Data_Clust$inputsTable %>% arrange(cluster.to)

# Now sort MBONs by which cluster they project most strongly to
PreOrder=Graph_Data_Clust %>% group_by(type.from) %>% filter(weightRelative == max(weightRelative))
PreOrder=PreOrder[c("type.from","cluster.to")]
colnames(PreOrder)=c("type.from","cluster.from")
Graph_Data_Clust=merge(Graph_Data_Clust,PreOrder, by="type.from")

# Plot network graph of direct connections 
P0=GraphData=Get_Direct_Graph(Graph_Data_Clust, PlotDir)
P0

```


# Make plots showing how the MBON-to-CX direct connections depend on connection strength thresholds
```{r message=FALSE, warning=FALSE}

# Get all direct MBON-to-CX type-to-type connections, regardless of strength (i.e. no thresholds)
All_MB2CX_Direct=Downstream_T2T_L1 %>%  subset(databaseType.to %in% CXTypes & !databaseType.from=="MBON15-like") %>%
                                        group_by(databaseType.from, databaseType.to) %>% filter(weight == max(weight))
All_MB2CX_Direct$type.from=All_MB2CX_Direct$databaseType.from
All_MB2CX_Direct$type.to=All_MB2CX_Direct$databaseType.to

# Loop over different relative weight thresholds and compute the number of direct CX targets
Threshes=seq(from=0.001, to=0.2, by=0.001)
Num_of_Cx_Types=data.frame(thresh=numeric(), NumofCxTypes=numeric())
for (ttt in 1:length(Threshes)){
  Temp_All_MB2CX_Direct=All_MB2CX_Direct %>% subset(weightRelative>Threshes[ttt] & weight > 0)
  if (length(Temp_All_MB2CX_Direct$databaseType.from)>0){
    Num_of_Cx_Types[ttt,1]=Threshes[ttt]
    Num_of_Cx_Types[ttt,2]=length(unique(Temp_All_MB2CX_Direct$databaseType.to))}
}

# For each MBON with direct connections to the CX, plot the max relative weight
MBON_Direct_byThresh_Plot=All_MB2CX_Direct %>% group_by(databaseType.from) %>% summarize(weightRelative=max(weightRelative))
P1=ggplot(data=MBON_Direct_byThresh_Plot, aes(x=databaseType.from, y=weightRelative)) + 
  geom_bar(stat="identity", color="black", fill='black', width=0.850) + theme_classic()  + 
  theme(axis.text.x = element_text(angle = 90)) + scale_y_continuous(breaks = seq(from=0, to=0.14, by=0.01), lim=c(0,0.14) )
P1
ggsave(paste(PlotDir, "MBON_by_Thrsh.png",sep=""),
         plot = P1, device='png', scale = 1, width =6, height = 3.5, units ="in", dpi = 500, limitsize = TRUE)

# Plot the number of CX types targeted as a function of the relative weight threshold
P2=ggplot(data=Num_of_Cx_Types, aes(x=thresh, y=NumofCxTypes)) + geom_line() + theme_classic() + 
  theme(axis.text.x = element_text(angle = 90)) + scale_x_continuous(breaks = seq(from=0, to=0.12, by=0.01), lim=c(0,0.12) )
P2
ggsave(paste(PlotDir, "NumOfCxTypes_by_Thrsh.png",sep=""),
         plot = P2, device='png', scale = 1, width =4, height = 3.5, units ="in", dpi = 500, limitsize = TRUE)
  
# Make a scatter plot of weight vs relative weight for each connection
P3=ggplot(data=All_MB2CX_Direct, aes(x=weight, y=weightRelative)) + geom_point(size=1, shape=1) +
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(breaks = seq(from=0, to=0.12, by=0.01), lim=c(0,0.12) ) + 
  scale_x_continuous(breaks = seq(from=0, to=150, by=10), lim=c(0,150) )
P3
ggsave(paste(PlotDir, "Thresh_Scatter.png",sep=""),
         plot = P3, device='png', scale = 1, width =4, height = 3.5, units ="in", dpi = 500, limitsize = TRUE)

```


# ####################################################################################################################
# ######### Figure 2: MBON to CX indirect connections ################################################################
# ####################################################################################################################


# Get indirect connections (from MBONs to CX types through one intermediate neuron type)
```{r message=FALSE, warning=FALSE}

# Get strong connections from MBONs to non-CX neurons
MB2NonCX=subset(Downstream_T2T_L1, !(databaseType.to %in% CXTypes)  & weightRelative>0.01 & weight>10)

# Get type table with intermediate neurons (excluding fragments with only bodyIDs and no type names)
L2_Types=sort(unique(MB2NonCX$databaseType.to))
L2_Types=L2_Types[is.na(as.numeric(L2_Types))]
L2_Types=L2_Types[!(startsWith(L2_Types,"(") | startsWith(L2_Types,"Ascending") | startsWith(L2_Types, "MBON"))]
L2_Types_Table=getTypesTable(L2_Types)

# Get second layer lateralized outputs (for the same reasons as explained above)
DownBag_L2=neuronBag(L2_Types_Table, by.roi=TRUE, omitInputs=TRUE, omitOutputs=FALSE) %>% lateralize_types()

# Compute relative by summing ROIs not in the CX and not on the left side of the brain,
# which deals with polarity and lateralization issues (as explained above)
DownBag_L2 <- combineRois(DownBag_L2, outsideRegions, newRoi="NonCX") 
                       
# Recompute type-to-type table without t-test significance criteria (explained above)
DownTypes_L2=getTypesTable(unique(c(DownBag_L2$outputs_raw$databaseType.from,  DownBag_L2$outputs_raw$databaseType.to))) %>% lateralize_types()
Downstream_T2T_L2=getTypeToTypeTable(DownBag_L2$outputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0,
                                     singleNeuronThresholdN = 3, pThresh = 1, typesTable = DownTypes_L2, oldTable = NULL) 

```


# Plot type-to-type connection matrices for MBON-to-intermediate and intermediate-to-CX pathways
# Restrict plots to only strong connections, otherwise there are too many pathways to visualize.
```{r message=FALSE, warning=FALSE}

# Get MBON-to-intermediate and intermediate-to-CX connection tables (relative weights > 0.02 and # of synapses > 20) 
OUT=Get_Max_T2T(MB2NonCX, Downstream_T2T_L2, 0.02, 20)
L1_to_L2_Max=OUT[[1]]
L2_to_Cx_Max=OUT[[2]]

# Plot MBON-to-intermediate type-to-type connection table
TempOrder= L1_to_L2_Max %>% arrange(type.from) %>% group_by(type.to) %>% filter(weight == max(weight))
OrderIn=(sort(unique(L1_to_L2_Max$type.from)))
OrderOut=TempOrder$type.to
P4=Plot_Indirect_Matrices(L1_to_L2_Max, OrderIn, OrderOut)
print(P4)
ggsave(paste(PlotDir, "L1_to_L2_Plot.png",sep=""),
        plot = P4, device='png', scale = 1, width =8, height = 6, units ="in", dpi = 500, limitsize = TRUE)

# Plot strong intermediate-to-CX type-to-type connection table
TempOrder2= L2_to_Cx_Max %>% arrange(match(type.from, TempOrder$type.to)) %>% 
            group_by(type.to) %>% filter(weight == max(weight))
OrderIn=TempOrder$type.to
OrderOut=unique(TempOrder2$type.to)
P5=Plot_Indirect_Matrices(L2_to_Cx_Max, OrderIn, OrderOut)
print(P5)
ggsave(paste(PlotDir, "L2_to_Cx_Plot.png",sep=""),
        plot = P5, device='png', scale = 1, width =8, height = 6, units ="in", dpi = 500, limitsize = TRUE)

# Remove pathway variables, which will be recomputed at a lower threshold below
rm(L1_to_L2_Max, L2_to_Cx_Max, OUT, OrderIn, OrderOut, TempOrder, TempOrder2)

```


# Plot the number of pathways from MBONs to the various FB layers
```{r message=FALSE, warning=FALSE}

# Get MBON-to-intermediate and intermediate-to-CX connection tables (relative weights > 0.01 and # of synapses > 10) 
OUT=Get_Max_T2T(MB2NonCX, Downstream_T2T_L2, 0.01, 10) # 0.01 and 10
L1_to_L2_Max=OUT[[1]]
L2_to_Cx_Max=OUT[[2]]

# Construct pathway object
MBON2CX_Indirect_Max=tableChain2path(L1_to_L2_Max, L2_to_Cx_Max) %>% subset(!is.na(type_N1))

# Compute the number of pathways from each MBON to each FB layer for relative weights greater than 0.01 and plot
MBON2CX_Indirect_Max_FBlayer=Compute_MBON_to_FBlayer(MBON2CX_Indirect_Max, 0.01)
P6=Plot_FbLayers_Targeted(MBON2CX_Indirect_Max_FBlayer)
P6
ggsave(paste(PlotDir, "byLayer_NumOfFBt.png",sep=""),
        plot = P6, device='png', scale = 1, width =8, height = 4, units ="in", dpi = 500, limitsize = TRUE)

# Do the same as above, but for relative weights greater than 0.02
MBON2CX_Indirect_Max_FBlayer_High=Compute_MBON_to_FBlayer(MBON2CX_Indirect_Max, 0.02)
MBON2CX_Indirect_Max_FBlayer_High$databaseType.from=factor(MBON2CX_Indirect_Max_FBlayer_High$databaseType.from,
                                              levels=sort(unique(MBON2CX_Indirect_Max_FBlayer$databaseType.from)))
P7=Plot_FbLayers_Targeted(MBON2CX_Indirect_Max_FBlayer_High)
P7
ggsave(paste(PlotDir, "byLayer_NumOfFBt_High.png",sep=""),
        plot = P7, device='png', scale = 1, width =8, height = 4, units ="in", dpi = 500, limitsize = TRUE)

```


# Get visual and thermo/hygro MBON types
```{r}

# Based on Figure 15 from the MB paper (Li et al, 2021, eLife) we can focus on MBONs that receive at least
# 20% of their input from KCs carrying either visual or thermo/hygro information
Visual_MBONs=c("MBON19","MBON27","MBON32","MBON33","MBON35")
ThermoHygro_MBONs=c("MBON10","MBON26","MBON28")

# Get intermediate supertypes (to assign edged colors in network graphs below)
Int_all=subset(MBON2CX_Indirect_Max, type.from %in% c(Visual_MBONs,ThermoHygro_MBONs) & weightRelative_N1>0.02 &
                 weightRelative_N2>0.02)$supertype1_N1 %>% sort() %>% unique()

```


# Make network graph showing indirect pathways from visual MBONs to the CX
```{r}

# Plot visual pathways
VisualPathway=subset(MBON2CX_Indirect_Max, type.from %in% Visual_MBONs & weightRelative_N1>0.02 & weightRelative_N2>0.02)
G1=Get_VisHygThermo_Graph(VisualPathway, Int_all)
G1
G1=ggsave(paste(PlotDir, "Visual_Graph.png",sep=""),
          plot = G1, device='png', scale = 1, width =8, height = 10, units ="in", dpi = 500, limitsize = TRUE)

# Plot thermo/hydro pathway
TherHygPahtway=subset(MBON2CX_Indirect_Max, type.from %in% ThermoHygro_MBONs & weightRelative_N1>0.02 & weightRelative_N2>0.02)
G2=Get_VisHygThermo_Graph(TherHygPahtway, Int_all)
G2
G2=ggsave(paste(PlotDir, "ThermoHygro_Graph.png",sep=""),
        plot = G2, device='png', scale = 1, width =8, height = 5, units ="in", dpi = 500, limitsize = TRUE)

# Plot pathways from MBONs to types other than FB tangentials
NonFBtPathways=subset(MBON2CX_Indirect_Max, !startsWith(type.to,"FB")  & weightRelative_N1>0.02 & weightRelative_N2>0.02) %>% arrange(type.from)
G3=Get_VisHygThermo_Graph(NonFBtPathways, Int_all)
G3
G3=ggsave(paste(PlotDir, "NonFBt_Graph.png",sep=""),
        plot = G3, device='png', scale = 1, width =8, height = 5, units ="in", dpi = 500, limitsize = TRUE)

```


