---
title: "Notebook for plotting PB-FB phase shifts (discrete + continuous mappings & FB connectivity)"
output:
  html_document:
    df_print: paged
---

### Load libraries
```{r message=FALSE, warning=FALSE}
library(neuprintrExtra)
library(neuprintr)
library(ggraph)
library(stringr)
library(tidygraph)
library(dplyr)
library(prismatic)
```

# Make directory where figures will be saved to
```{r}

# Directory where synapse data (output of FB_GetAndSave_Synapses.Rmd) and column location data (output of FB_ColumnLocations.Rmd) are stored
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save plots to
PlotDir=paste(SaveDir, "/Figure_PhaseShift/",sep="")
if (!dir.exists(PlotDir)){dir.create(PlotDir)}

```

# Connect to neuprint server.
```{r}
neuprint_login()
```

# Get general functions
```{r}

source("FB_Analysis_Utils.r")

```

# Load pre-processed synapse and column location data and remove variables that won't be used
```{r}

load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
rm(list=c("roiEigen","Mesh_FB_Points","Mesh_FB_L1_Points", "Mesh_FB_L2_Points","Mesh_FB_L3_Points", "Mesh_FB_L4_Points",
          "Mesh_FB_L5_Points", "Mesh_FB_L6_Points","Mesh_FB_L7_Points", "Mesh_FB_L8_Points", "Mesh_FB_L9_Points","origin"))
load(paste(SaveDir,"FB_ColumnPositions.RData",sep=""))

# Assign Side, PB glom, and FB col info
FBC_SynsAll=Assign_FBcol_PBglom(FBC_SynsAll, "name", "Side", "PBglom", "FBcol")

```


# Plot discrete PB glomeruli to FB column mappings for all PB-FB-XX types
```{r message=FALSE, warning=FALSE}

# Get all PB-FB-XX neurons and parse name to get PB glomeruli and FB column info
FB_Bodies=getNeuronsInRoiTable("FB",0)
FB_Bodies_Meta=neuprint_get_meta(FB_Bodies$bodyid)
PB_FB_Bodies=subset(FB_Bodies_Meta, startsWith(type,"PF"))
PB_FB_Bodies=Assign_FBcol_PBglom(PB_FB_Bodies, "name", "Side", "PBglom", "FBcol")

# Make graphs showing number of neurons connecting each PB glomerulus to each FB column
Plot_PBglom_FBcol_Mapping(PB_FB_Bodies, PlotDir)

```



# Plot connectivity matrices to show that PB-FB phase shifts are realized in connectivity
```{r message=FALSE, warning=FALSE}

# Pick a pre (PB-FB-XX type) and post (and downstream FB columnar type) 
Pre="PFNa"    # (PFNa or PFNp_a)
Post="FC1B"   # (for PFNa: FC1B or hDeltaC; for PFNp_a: PFL2 or vDeltaL)

# Get connectivity matrix
ConnectMeta=subset(FB_Bodies_Meta, type %in% c(Pre,Post))
PbFb_Bag=neuronBag(ConnectMeta, slctROI="FB")
Connect_Mat=PbFb_Bag$outputs_raw
Connect_Mat=subset(Connect_Mat, databaseType.from==Pre & databaseType.to==Post)

# Get PB glomerulus and FB column info from neuron names and compute average relative weights
Connect_Mat=Assign_FBcol_PBglom(Connect_Mat, "name.from", "Side.from", "PBglom.from", "FBcol.from")
Connect_Mat=Assign_FBcol_PBglom(Connect_Mat, "name.to", "Side.to", "PBglom.to", "FBcol.to")
Connect_Mat_Phase=Connect_Mat %>% group_by(PBglom.from, FBcol.to) %>% summarise(weightRelative=mean(weightRelative))

# Set factor levels so PB glomruli and FB columns are arrange properly along each axis
Connect_Mat_Phase$PBglom.from=factor(Connect_Mat_Phase$PBglom.from,
    levels=c("L9","R1","L8","R2","L7","R3","L6","R4","L5","R5","L4","R6","L3","R7","L2","R8","L1","R9"))
Connect_Mat_Phase$FBcol.to=factor(Connect_Mat_Phase$FBcol.to,
    levels=c("C0","C1","C2","C3","C4","C5","C6","C7","C8","C9","C10","C11","C12"))

# Plot connectivity matrix
P1 <- ggplot(Connect_Mat_Phase) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.03, limits=c(0,0.06)) +
  geom_tile(aes(FBcol.to,PBglom.from,fill=weightRelative)) + scale_y_discrete(drop=FALSE) + theme_classic() +
  ggtitle(paste(Pre, " to ", Post, sep="")) + theme(axis.text.x = element_text(angle = 90))
P1
ggsave(paste(PlotDir, Pre, "_to_", Post,"_PhaseShift", ".png", sep=""),
       plot = P1, device='png', scale = 1, width = 4, height = 5, units ="in", dpi = 500, limitsize = TRUE)


```

