---
title: "FB Figure - PFNs to outputs"
output: html_notebook
---

Load the libraries
```{r}
library(nat)
library(neuprintr)
library(tidyverse)
library(tidygraph)
library(ggraph)
library(gridExtra)
library(paletteer)
library(neuprintrExtra)
library(cowplot)
library(reshape2)
library(patchwork)
library(visNetwork)
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\FBNetworkVisUtils.R")
source("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\R\\connectivityMatricesTools.R")
options(nat.plotengine = 'rgl')
```

Specify plotting parameters
```{r}
update_geom_defaults("text", list(size = 6*0.35))
theme_paper <- function(...){
  theme_cowplot(font_size=7,rel_small=6/7,rel_tiny = 5/7,rel_large = 8/7) + theme(strip.background = element_blank(),...)
}

stCols <- supertype2Palette()
stCols$breaks <- append(stCols$breaks,'OA-VPM3')
stCols$pal <- append(stCols$pal,'#000000FF')
```

Look at the PFN to output connections
```{r}
typesFrom <- neuprint_search('PFN.*',field='type')$type %>% unique() %>% rev()
typesTo <- c(neuprint_search('FS.*',field='type')$type %>% unique(),
             'PFR_b',
             neuprint_search('FR.*',field='type')$type %>% unique(),
             neuprint_search('PFL.*',field='type')$type %>% unique())

exConTab <- getConnectionTable(getTypesTable(typesFrom),'POST','FB') %>% filter(type.to %in% typesTo)

exConTab$id.from <- FBRename(exConTab$name.from,exConTab$from)
exConTab$id.to <- FBRename(exConTab$name.to,exConTab$to)

exConTab$id.from <- factor(exConTab$id.from,
                           levels = lapply(typesFrom, function(t) exConTab$id.from[which(grepl(t,as.character(exConTab$id.from)))] %>% 
                                        unique() %>% as.character() %>% sort() %>% rev()) %>% unlist())
exConTab$id.to <- factor(exConTab$id.to,
                           levels = lapply(typesTo, function(t) exConTab$id.to[which(grepl(t,as.character(exConTab$id.to)))] %>% 
                                        unique() %>% as.character() %>% sort()) %>% unlist())

txtLabsTo <- exConTab$id.to %>% levels() %>% unlist() %>% as.character() 
typLabsTo <- lapply(txtLabsTo,function(t) exConTab[which(exConTab$id.to == t),]$type.to %>% unique()) %>% unlist()
txtColsTo <- lapply(typLabsTo,
                  function(t)
                    stCols$pal[
                      which(stCols$breaks == 
                              supertype(t))]) %>% unlist()

txtLabsFrom <- exConTab$id.from %>% levels() %>% unlist() %>% as.character()
typLabsFrom <- lapply(txtLabsFrom,function(t) exConTab[which(exConTab$id.from == t),]$type.from %>% unique()) %>% unlist()
txtColsFrom <- lapply(typLabsFrom,
                  function(t)
                    stCols$pal[
                      which(stCols$breaks == 
                              supertype(t))]) %>% unlist()


FBCol_Ex <- ggplot(exConTab) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(exConTab$weightRelative),
                       limits=c(0,max(exConTab$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_paper() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,color=txtColsTo),
        axis.text.y = element_text(color=txtColsFrom)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")

offset <- 0.5
for (g in 1:length(typesTo)){
  offset <- offset + length(which(grepl(typesTo[g],typLabsTo)))
  FBCol_Ex <- FBCol_Ex + geom_vline(xintercept = offset)
}

offset <- 0.5
for (g in 1:length(typesFrom)){
  offset <- offset + length(which(grepl(typesFrom[g],typLabsFrom)))
  FBCol_Ex <- FBCol_Ex + geom_hline(yintercept = offset)
}

print(FBCol_Ex)

ggsave("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_FB_ColNronNetwork\\PFNsToOutputs.pdf",FBCol_Ex)
```

Look at the PFNd to hDeltaA,B,H,J connections
```{r}
typesFrom <- c('PFNd')
typesTo <- c('hDeltaA','hDeltaB','hDeltaH','hDeltaJ')

exConTab <- getConnectionTable(getTypesTable(typesFrom),'POST','FB') %>% filter(type.to %in% typesTo)

exConTab$id.from <- FBRename(exConTab$name.from,exConTab$from)
exConTab$id.to <- FBRename(exConTab$name.to,exConTab$to)

exConTab$id.from <- factor(exConTab$id.from,
                           levels = lapply(typesFrom, function(t) exConTab$id.from[which(grepl(t,as.character(exConTab$id.from)))] %>% 
                                        unique() %>% as.character() %>% sort()) %>% unlist())
exConTab$id.to <- factor(exConTab$id.to,
                           levels = lapply(typesTo, function(t) exConTab$id.to[which(grepl(t,as.character(exConTab$id.to)))] %>% 
                                        unique() %>% as.character() %>% sort()) %>% unlist())

txtLabsTo <- exConTab$id.to %>% levels() %>% unlist() %>% as.character() 
typLabsTo <- lapply(txtLabsTo,function(t) exConTab[which(exConTab$id.to == t),]$type.to %>% unique()) %>% unlist()
txtColsTo <- lapply(typLabsTo,
                  function(t)
                    stCols$pal[
                      which(stCols$breaks == 
                              supertype(t))]) %>% unlist()

txtLabsFrom <- exConTab$id.from %>% levels() %>% unlist() %>% as.character()
typLabsFrom <- lapply(txtLabsFrom,function(t) exConTab[which(exConTab$id.from == t),]$type.from %>% unique()) %>% unlist()
txtColsFrom <- lapply(typLabsFrom,
                  function(t)
                    stCols$pal[
                      which(stCols$breaks == 
                              supertype(t))]) %>% unlist()


FBCol_Ex <- ggplot(exConTab) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(exConTab$weightRelative),
                       limits=c(0,max(exConTab$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_paper() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,color=txtColsTo),
        axis.text.y = element_text(color=txtColsFrom)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")

offset <- 0.5
for (g in 1:length(typesTo)){
  offset <- offset + length(which(grepl(typesTo[g],typLabsTo)))
  FBCol_Ex <- FBCol_Ex + geom_vline(xintercept = offset)
}

offset <- 0.5
for (g in 1:length(typesFrom)){
  offset <- offset + length(which(grepl(typesFrom[g],typLabsFrom)))
  FBCol_Ex <- FBCol_Ex + geom_hline(yintercept = offset)
}

print(FBCol_Ex)

ggsave("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_FB_ColNronNetwork\\PFNdshDeltas.pdf",FBCol_Ex)
```

Look at the hDeltaA,B,H,J to output connections
```{r}
typesFrom <- c('hDeltaJ','hDeltaH','hDeltaB','hDeltaA')
typesTo <- c(neuprint_search('FS.*',field='type')$type %>% unique(),
             'PFR_b',
             neuprint_search('FR.*',field='type')$type %>% unique(),
             neuprint_search('PFL.*',field='type')$type %>% unique())

exConTab <- getConnectionTable(getTypesTable(typesFrom),'POST','FB') %>% filter(type.to %in% typesTo)

exConTab$id.from <- FBRename(exConTab$name.from,exConTab$from)
exConTab$id.to <- FBRename(exConTab$name.to,exConTab$to)

exConTab$id.from <- factor(exConTab$id.from,
                           levels = lapply(typesFrom, function(t) exConTab$id.from[which(grepl(t,as.character(exConTab$id.from)))] %>% 
                                        unique() %>% as.character() %>% sort() %>% rev()) %>% unlist())
exConTab$id.to <- factor(exConTab$id.to,
                           levels = lapply(typesTo, function(t) exConTab$id.to[which(grepl(t,as.character(exConTab$id.to)))] %>% 
                                        unique() %>% as.character() %>% sort()) %>% unlist())

txtLabsTo <- exConTab$id.to %>% levels() %>% unlist() %>% as.character() 
typLabsTo <- lapply(txtLabsTo,function(t) exConTab[which(exConTab$id.to == t),]$type.to %>% unique()) %>% unlist()
txtColsTo <- lapply(typLabsTo,
                  function(t)
                    stCols$pal[
                      which(stCols$breaks == 
                              supertype(t))]) %>% unlist()

txtLabsFrom <- exConTab$id.from %>% levels() %>% unlist() %>% as.character()
typLabsFrom <- lapply(txtLabsFrom,function(t) exConTab[which(exConTab$id.from == t),]$type.from %>% unique()) %>% unlist()
txtColsFrom <- lapply(typLabsFrom,
                  function(t)
                    stCols$pal[
                      which(stCols$breaks == 
                              supertype(t))]) %>% unlist()


FBCol_Ex <- ggplot(exConTab) + 
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.5*max(exConTab$weightRelative),
                       limits=c(0,max(exConTab$weightRelative))) +
  geom_tile(aes(id.to,id.from,fill=weightRelative)) +
  theme_paper() + coord_fixed(ratio = 1) + 
  theme(axis.text.x = element_text(angle = 90,color=txtColsTo),
        axis.text.y = element_text(color=txtColsFrom)) +
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")

offset <- 0.5
for (g in 1:length(typesTo)){
  offset <- offset + length(which(grepl(typesTo[g],typLabsTo)))
  FBCol_Ex <- FBCol_Ex + geom_vline(xintercept = offset)
}

offset <- 0.5
for (g in 1:length(typesFrom)){
  offset <- offset + length(which(grepl(typesFrom[g],typLabsFrom)))
  FBCol_Ex <- FBCol_Ex + geom_hline(yintercept = offset)
}

print(FBCol_Ex)

ggsave("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_FB_ColNronNetwork\\hDeltasToOutputs.pdf",FBCol_Ex)
```


Look at the minimum path lengths between PFNs and outputs

Specify the input and output types and load the type-to-type table
```{r}
typesIn <- neuprint_search('PFN.*',field='type')$type %>% unique()
typesOut <- c(neuprint_search('FC.*',field='type')$type %>% unique(),
              neuprint_search('FS.*',field='type')$type %>% unique(),
              'PFR_b',
              neuprint_search('FR.*',field='type')$type %>% unique(),
              neuprint_search('PFL.*',field='type')$type %>% unique())
typesIDs <- 1:length(typesOut)

load("C:\\Users\\dantu\\Documents\\neuprintR-notebooks\\FBFigures\\T2T_FBCol_filtered.Rda")
```

Get the mimumim path lengths
```{r}
pathLengths <- matrix(,nrow=length(typesIn),ncol=length(typesOut))

for (i in 1:length(typesIn)){
  outIDs <- c()
  pl <- 0
  typesTo <- typesIn[i]
  while (length(outIDs) != length(typesIDs)){
    pl <- pl + 1
    typesTo <- T2T_FBCol_filtered %>% filter(type.from %in% typesTo) %>% select(type.to) %>% unique() %>% unlist()
    if (length(typesTo) == 0){
      break
    }
    throughPaths <- lapply(typesTo, function(t) which(t == typesOut)) %>% unlist() %>% as.numeric()
    throughPaths <- setdiff(throughPaths,outIDs)
    pathLengths[i,throughPaths] <- pl
    outIDs <- c(outIDs,throughPaths)
    if (pl > 100)
      break
  }
}
rownames(pathLengths) <- typesIn
colnames(pathLengths) <- typesOut
```
```{r}
pathLengths <- pathLengths %>% as.data.frame()
pathLengths$type.from <- rownames(pathLengths)
pathLengths <- melt(pathLengths, id.vars=c('type.from'),variable.name='type.to',value.name='pathlength')
pathLengths <- pathLengths[which(!is.na(pathLengths$pathlength)),]
```
```{r}
pathLengths_ToPlt <- pathLengths
pathLengths_ToPlt$type.from <- factor(pathLengths_ToPlt$type.from, levels = pathLengths_ToPlt$type.from %>% unique() %>% sort() %>% rev())
plPlt <- ggplot(pathLengths_ToPlt) + geom_tile(aes(x=type.to,y=type.from,fill=as.factor(pathlength))) + 
  coord_fixed(ratio=1) + theme_paper() + scale_fill_manual(values = paletteer_c("oompaBase::greyscale", 6),name='pathlength') + 
  xlab('postsynaptic type') + ylab('presynaptic type') +
    geom_vline(xintercept = 10.5) + 
    geom_vline(xintercept = 17.5) +
    geom_vline(xintercept = 18.5) +
    geom_vline(xintercept = 20.5) 
print(plPlt)
#ggsave("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_FB_ColNronNetwork\\InToOutPathLengths.pdf",plPlt)
```

Show different path lengths
Get the mimumim path lengths
```{r}
plMax <- 3

# Step through the different pathways
for (pl in 1:plMax){
  pathLengths <- matrix(0,nrow=length(typesIn),ncol=length(typesOut))
  
  # Step through the input types
  for (i in 1:length(typesIn)){
    typesTo <- typesIn[i]
    
    plNow <- 0
    # Step through the different path lengths
    while (plNow < pl){
      typesTo <- T2T_FBCol_filtered %>% filter(type.from %in% typesTo) %>% select(type.to) %>% unique() %>% unlist()
      plNow <- plNow + 1
    }
    if (length(typesTo) == 0){
      next
    }
    throughPaths <- lapply(typesTo, function(t) which(t == typesOut)) %>% unlist() %>% as.numeric()
    pathLengths[i,throughPaths] <- 1
  }
  rownames(pathLengths) <- typesIn
  colnames(pathLengths) <- typesOut
  
  pathLengths <- pathLengths %>% as.data.frame()
  pathLengths$type.from <- rownames(pathLengths)
  pathLengths <- melt(pathLengths, id.vars=c('type.from'),variable.name='type.to',value.name=paste0('pathlength-',pl))
  pathLengths <- pathLengths[which(!is.na(pathLengths$pathlength)),]
  
  if (pl == 1){
    pathLengths_ToPlt <- pathLengths
  }
  else {
    pathLengths_ToPlt <- left_join(pathLengths_ToPlt,pathLengths)
  }
}
pathLengths_ToPlt$type.from <- factor(pathLengths_ToPlt$type.from, levels = pathLengths_ToPlt$type.from %>% unique() %>% sort() %>% rev())
```
```{r}
plPlt <- ggplot(melt(pathLengths_ToPlt)) + geom_tile(aes(x=type.to,y=type.from,fill=as.factor(value))) + 
  coord_fixed(ratio=1) + theme_paper() + scale_fill_manual(values = c('white','black'),guide=FALSE) + 
  xlab('postsynaptic type') + ylab('presynaptic type') +
    geom_vline(xintercept = 10.5, color= 'gray') + 
    geom_vline(xintercept = 17.5, color= 'gray') +
    geom_vline(xintercept = 18.5, color= 'gray') +
    geom_vline(xintercept = 20.5, color= 'gray') +
  facet_grid(cols = vars(variable)) + 
  theme(axis.text.x = element_text(angle=90))
print(plPlt)
#ggsave("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_FB_ColNronNetwork\\PathLengths.pdf",plPlt)
```


Look at relative strength of paths
Load the type-to-type table and get the FB columnar types
```{r}
load("C:\\Users\\turnerevansd\\Documents\\FIBSEM\\neuprintR-notebooks\\FBFigures\\T2T_FBCol_filtered.Rda")
FBColTypes <- c(T2T_FBCol_filtered$type.from, T2T_FBCol_filtered$type.to) %>% unique()
```

Specify the input and output types
```{r}
typesIn <- neuprint_search('PFN.*',field='type')$type %>% unique()
typesOut <- c(neuprint_search('FC.*',field='type')$type %>% unique(),
              neuprint_search('FS.*',field='type')$type %>% unique(),
             'PFR_b',
             neuprint_search('FR.*',field='type')$type %>% unique(),
             neuprint_search('PFL.*',field='type')$type %>% unique())
```

Step through the pathways, populating a matrix with the relative strengths of the pathways as we go
```{r}
plMax <- 1

# Step through the paths
for (pl in 1:plMax){
  
  # Create an empty matrix to hold the relative strengths for each path
  pathLengths <- matrix(0,nrow=length(typesIn),ncol=length(typesOut))
  
  # Step through the input types
  for (i in 1:length(typesIn)){
    
    # Step though the output types
    for (j in 1:length(typesOut)){
      
      # Get the pathways
      pwsNow <- get_type2typePath(type.from = getTypesTable(typesIn[i]),
                                  type.to = getTypesTable(typesOut[j]),
                                  ROI='FB',
                                  n_steps = pl,
                                  renaming=identity)
      
      # Filter the pathways so that only columnar connections are considered
      if (pl == 2){
        pwsNow <- pwsNow %>% filter(type_N1 %in% FBColTypes)
      }
      if (pl == 3){
        pwsNow <- pwsNow %>% filter(type_N1 %in% FBColTypes,
                                    type_N2 %in% FBColTypes)
      }
      if (pl == 4){
        pwsNow <- pwsNow %>% filter(type_N1 %in% FBColTypes,
                                    type_N2 %in% FBColTypes,
                                    type_N3 %in% FBColTypes)
      }
      
      # If there are no pathways, move on to the next combination
      if (nrow(pwsNow) == 0){
        next
      }
      
      # Step through the pathways, multiplying the weights together
      totPws <- 0
      for (r in 1:nrow(pwsNow)){
        if (pl == 1){
          if (nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type.from,
                           type.to == pwsNow[r,]$type.to)) == 0){
            next
          }
          pathLengths[i,j] <- pwsNow[r,]$weightRelative_N1
        }
        if (pl == 2){
          if ((nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type.from,
                           type.to == pwsNow[r,]$type_N1)) == 0) |
              (nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type_N1,
                           type.to == pwsNow[r,]$type.to)) == 0))
            {
            next
          }
          if (is.na(pathLengths[i,j])){
            pathLengths[i,j] <- pwsNow[r,]$weightRelative_N2
          } else {
            pathLengths[i,j] <- pathLengths[i,j] +
            pwsNow[r,]$weightRelative_N1*pwsNow[r,]$weightRelative_N2
          }
        }
        if (pl == 3){
          if ((nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type.from,
                           type.to == pwsNow[r,]$type_N1)) == 0) |
              (nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type_N1,
                           type.to == pwsNow[r,]$type_N2)) == 0) |
              (nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type_N2,
                           type.to == pwsNow[r,]$type_to)) == 0))
            {
            next
          }
          if (is.na(pathLengths[i,j])){
            pathLengths[i,j] <- pwsNow[r,]$weightRelative_N1*pwsNow[r,]$weightRelative_N2*pwsNow[r,]$weightRelative_N3
          } else {
            pathLengths[i,j] <- pathLengths[i,j] +
            pwsNow[r,]$weightRelative_N1*pwsNow[r,]$weightRelative_N2*pwsNow[r,]$weightRelative_N3
          }
        }
        if (pl == 4){
          if ((nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type.from,
                           type.to == pwsNow[r,]$type_N1)) == 0) |
              (nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type_N1,
                           type.to == pwsNow[r,]$type_N2)) == 0) |
              (nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type_N2,
                           type.to == pwsNow[r,]$type_N3)) == 0) |
              (nrow(T2T_FBCol_filtered %>% 
                    filter(type.from == pwsNow[r,]$type_N3,
                           type.to == pwsNow[r,]$type.to)) == 0) )
            {
            next
          }
          if (is.na(pathLengths[i,j])){
            pathLengths[i,j] <- pwsNow[r,]$weightRelative_N1*pwsNow[r,]$weightRelative_N2*pwsNow[r,]$weightRelative_N3*pwsNow[r,]$weightRelative_N4
          } else {
            pathLengths[i,j] <- pathLengths[i,j] +
            pwsNow[r,]$weightRelative_N1*pwsNow[r,]$weightRelative_N2*pwsNow[r,]$weightRelative_N3*pwsNow[r,]$weightRelative_N4
          }
        }
      }
    }
  }
      
  rownames(pathLengths) <- typesIn
  colnames(pathLengths) <- typesOut 
  
  pathLengths <- pathLengths %>% as.data.frame()
  pathLengths$type.from <- rownames(pathLengths)
  pathLengths <- melt(pathLengths, id.vars=c('type.from'),variable.name='type.to',value.name='pathlength')
  
  pathLengths_ToPlt <- pathLengths
  pathLengths_ToPlt$type.from <- factor(pathLengths_ToPlt$type.from, levels = pathLengths_ToPlt$type.from %>% unique() %>% sort() %>% rev())
  plPlt <- ggplot(pathLengths_ToPlt) + geom_tile(aes(x=type.to,y=type.from,fill=pathlength)) + 
    coord_fixed(ratio=1) + theme_paper() + scale_fill_gradient(low='white',high='black',limits=c(0,0.4),name = "relative strength") + 
    xlab('postsynaptic type') + ylab('presynaptic type') +
    geom_vline(xintercept = 10.5) + 
    geom_vline(xintercept = 17.5) +
    geom_vline(xintercept = 18.5) +
    geom_vline(xintercept = 20.5) 
  print(plPlt)
  
  ggsave(paste0("C:\\Users\\turnerevansd\\Dropbox (HHMI)\\FIBSEM CX Paper Jan 2020\\Figures\\FirstDraftFigs\\FB\\FIGURE_FB_ColNronNetwork\\InToOutPathLengths-",pl,".pdf"),plPlt)
}

```

