---
title: "FBt synapses plot"
output: html_notebook
---

Notebook used to make the synapse distribution plot of FB tangentials (figure 40 figure supplement 2)
```{r message=FALSE, warning=FALSE}
#library(neuprintr)
#library(tidyverse)
#library(neuprintrExtra)
#library(nat)
#library(paletteer)
```

## Preparing the environment
```{r message=FALSE}
source(file.path("..","Outputs","outputFunctions-core.R"))
source(file.path("..","Outputs","outputFunctions-display.R"))
source(file.path("..","R","paperTheme.R"))
```

## Collecting the synapses
We first get a table of FBt neurons and add a column that denotes their layer. We also filter for only the types innervating the right side of the brain:
```{r}
FBt <- neuprint_search("FB[1-9].*",field = "type") %>% 
  mutate(databaseType=type,
         layer=gsub("FB","",str_extract(type,"FB[1-9]"))) %>% cxRetyping() %>% filter(grepl("_R",type))
head(FBt)
```

We define the ROIs we will consider in this figure:
```{r}
outsideRegions <- c("LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)","GA(R)")
```

We then collect the FBt input and output synapses and label them by layers:
```{r,warning=FALSE}
FBtInSyn <- collectSynapses(FBt,outsideRegions,polarity="post")
FBtOutSyn <- collectSynapses(FBt,outsideRegions,polarity="pre")

FBtInSyn <- FBtInSyn %>% 
  mutate(layer=gsub("FB","",str_extract(type,"FB[1-9]")))

FBtOutSyn <- FBtOutSyn %>% 
 mutate(layer=gsub("FB","",str_extract(type,"FB[1-9]")))

head(FBtInSyn)
```

We then define a palette to be used to label the layers:
```{r}
FBtPalette <- paletteer_d("RColorBrewer::YlGnBu")
FBLayersPalette <- FBtPalette
names(FBLayersPalette) <- paste0("FBl",1:9)
names(FBtPalette) <- as.character(1:9)

#write_csv(FBtInSyn,"FBtInputSynapses.csv")
#write_csv(FBtOutSyn,"FBtOutputSynapses.csv")
#write.csv(as.data.frame(as.character(FBtPalette)),"FBtPalette.csv")
```

And generate renderings (note that the display in the final figure was generated using NeuTu rather than this code):
```{r}
displaySynapses3D(synapses=FBtInSyn,
                 ROIs=c("FB","LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)"),
                 saveName = "FBtInSpheres",
                 synapsePalette = FBtPalette,
                 synapseCluster = "layer",
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2,
                 saveFolder = ".",
                 windowSize = c(3000,3000)
                 )

```


```{r}
displaySynapses3D(synapses=FBtOutSyn,
                 ROIs=c("FB","LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)"),
                 saveName = "FBtOutSpheres",
                 synapsePalette = FBtPalette,
                 synapseCluster = "layer",
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2,
                 saveFolder = ".",
                 windowSize = c(3000,3000)
                 )
```
Also generate and save the legend:
```{r}
legendSource <- cowplot::get_legend(ggplot(FBt) +
                                      geom_point(aes(x=0,y=0,color=layer)) + 
                                      theme_paper_map() + scale_color_manual(name="FB layer",values=FBtPalette))
```

```{r}
save_plot("legend.svg",legendSource,base_height = 3,base_width = 1)
```

