---
title: "FBt synapses plot"
output: html_notebook
---

Notebook used to make the synapse distribution plot of FB tangentials (figure 40 figure supplement 2)
```{r message=FALSE, warning=FALSE}
#library(neuprintr)
#library(tidyverse)
#library(neuprintrExtra)
#library(nat)
library(paletteer)
```

## Preparing the environment
```{r message=FALSE}
source(file.path("..","Outputs","outputFunctions-core.R"))
source(file.path("..","Outputs","outputFunctions-display.R"))
source(file.path("..","R","paperTheme.R"))
```

## Collecting the synapses
We first get a table of FBt neurons and add a column that denotes their layer. We also filter for only the types innervating the right side of the brain:
```{r}
FBt <- neuprint_search("FB[1-9].*",field = "type") %>% 
  mutate(databaseType=type,
         layer=gsub("FB","",str_extract(type,"FB[1-9]"))) %>% cxRetyping() %>% filter(grepl("_R",type))
head(FBt)
```

We define the ROIs we will consider in this figure:
```{r}
outsideRegions <- c("LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)","GA(R)")
```

We then collect the FBt input and output synapses and label them by layers:
```{r}
FBtInSyn <- collectSynapses(FBt,outsideRegions,polarity="post")
FBtOutSyn <- collectSynapses(FBt,outsideRegions,polarity="pre")

FBtInSyn <- FBtInSyn %>% 
  mutate(layer=gsub("FB","",str_extract(type,"FB[1-9]")))

FBtOutSyn <- FBtOutSyn %>% 
 mutate(layer=gsub("FB","",str_extract(type,"FB[1-9]")))

head(FBtInSyn)
```

We then define a palette to be used to label the layers:
```{r}
FBtPalette <- paletteer_d("RColorBrewer::YlGnBu")#paletteer_d("Polychrome::palette36")[3:11]
FBLayersPalette <- FBtPalette
names(FBLayersPalette) <- paste0("FBl",1:9)
names(FBtPalette) <- as.character(1:9)
```

We then define the ROI colors to be used:
```{r}
#FBRoi <- roiH
#FBRoi$level0[FBRoi$level2=="FB"] <- as.character(FBRoi$level4[FBRoi$level2=="FB"])
#FBRoi$level2 <- as.character(FBRoi$level4)
#displayAnatomies(
#                 ROIs=paste0("FBl",1:9),
#                 saveName = "FBLayers",
#                 roiPal = FBLayersPalette,
#                 roiRef = FBRoi,
#                 alphaRois=0.3
#                 )
```


```{r}
displaySynapses3D(synapses=FBtInSyn,
                 ROIs=c("FB","LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)"),
                 saveName = "FBtInSpheres",
                 synapsePalette = FBtPalette,
                 synapseCluster = "layer",
                 type="s",size=0.2,
                 specular="black",
                  saveFolder = ".",
                 alphaRois = 0.04,
                 windowSize = c(3000,3000)
                 )

displaySynapses3D(synapses=FBtInSyn,
                 ROIs=c("FB","LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)"),
                 saveName = "FBtIn",
                 synapsePalette = FBtPalette,
                 synapseCluster = "layer",
                 specular="black",
                  saveFolder = ".",
                 alphaRois = 0.04,
                 windowSize = c(3000,3000)
                 )
```


```{r}
displaySynapses3D(synapses=FBtOutSyn,
                 ROIs=c("FB","LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)"),
                 saveName = "FBtOutSpheres",
                 synapsePalette = FBtPalette,
                 synapseCluster = "layer",
                 type="s",size=0.2,
                 specular="black",
                  saveFolder = ".",
                 alphaRois = 0.04,
                 windowSize = c(3000,3000)
                 )

displaySynapses3D(synapses=FBtOutSyn,
                 ROIs=c("FB","LAL(R)","CRE(R)","SMP(R)","SIP(R)","SLP(R)"),
                 saveName = "FBtOut",
                 synapsePalette = FBtPalette,
                 synapseCluster = "layer",
                 specular="black",
                  saveFolder = ".",
                 alphaRois = 0.04,
                 windowSize = c(3000,3000)
                 )
```
Also generate and save the legend:
```{r}
legendSource <- cowplot::get_legend(ggplot(FBt) +
                                      geom_point(aes(x=0,y=0,color=layer)) + 
                                      theme_paper_map() + scale_color_manual(name="FB layer",values=FBtPalette))
```

```{r}
save_plot("legend.svg",legendSource,base_height = 3,base_width = 1)
```

