---
title: "Notebook assigning columns to PB-FB-XX (ie PFX) and Delta0 neurons"
output:
  html_document:
    df_print: paged
---

### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="FB"  

# Directory to save data to.
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save plots to.
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/ColumnarSynapseLocs/"


```


### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}

source("FB_SynapseDistribution_Utils.r")
source("FB_LayerOutline_Utils.r")

```


# Load pre-processed data and remove variables that won't be used
```{r}

load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
rm(list=c("roiEigen","Mesh_FB_Points","Mesh_FB_L1_Points", "Mesh_FB_L2_Points","Mesh_FB_L3_Points", "Mesh_FB_L4_Points",
          "Mesh_FB_L5_Points", "Mesh_FB_L6_Points","Mesh_FB_L7_Points", "Mesh_FB_L8_Points", "Mesh_FB_L9_Points"))

```


# Get PB glomeruli or columns (Some columns are mixed and are named _L1/2 for example)
```{r}


# Assign side (pb or fb column half)
FBC_SynsAll$Side=NA
FBC_SynsAll$Side[grepl("_R",FBC_SynsAll$bodyname)]<-"R"
FBC_SynsAll$Side[grepl("_L",FBC_SynsAll$bodyname)]<-"L"

# Assign PB glom
FBC_SynsAll$PBglom=NA
RightColumns=str_extract(FBC_SynsAll$bodyname, "_R(\\d+)")
LeftColumns=str_extract(FBC_SynsAll$bodyname, "_L(\\d+)")
FBC_SynsAll$PBglom[which(!is.na(RightColumns))]=RightColumns[which(!is.na(RightColumns))]
FBC_SynsAll$PBglom[which(!is.na(LeftColumns))]=LeftColumns[which(!is.na(LeftColumns))]
FBC_SynsAll$PBglom=sapply(FBC_SynsAll$PBglom, substring, 2, 3)

# Assign FB glom
FBC_SynsAll$FBcol=NA
FBC_SynsAll$FBcol=str_extract(FBC_SynsAll$bodyname, "_C(\\d+)")
FBC_SynsAll$FBcol=sapply(FBC_SynsAll$FBcol, substring, 2, 3)


# Manually change PB glom of one neuron (PFNp_a)
FBC_SynsAll$PBglom[FBC_SynsAll$bodyid == 5813128416] = NA # development error. 


```


# Get the line that bisects each FB layer in the XZ (horizontal) plane
```{r}

Mid_L1=Get_Mid(Outline_L1_XZ)
Mid_L2=Get_Mid(Outline_L2_XZ)
Mid_L3=Get_Mid(Outline_L3_XZ)
Mid_L4=Get_Mid(Outline_L4_XZ)
Mid_L5=Get_Mid(Outline_L5_XZ)
Mid_L6=Get_Mid(Outline_L6_XZ)
Mid_L7=Get_Mid(Outline_L7_XZ)
Mid_L8=Get_Mid(Outline_L8_XZ)


```



# Get synapse distribution information from FX neurons and plot the data for review
```{r}


# Make plotting directories
Fx_Dir=paste(PlotDir,"FX_Plots_All","/",sep="")
Fx_Dir_Dist=paste(Fx_Dir,"FX_MeasureWidth","/",sep="")
Fx_Dir_SynScatter=paste(Fx_Dir,"FX_SynScatter","/",sep="")
Fx_Dir_Crosses=paste(Fx_Dir,"FX_Crosses","/",sep="")
if (!dir.exists(Fx_Dir)){dir.create(Fx_Dir)}
if (!dir.exists(Fx_Dir_Dist)){dir.create(Fx_Dir_Dist)}
if (!dir.exists(Fx_Dir_SynScatter)){dir.create(Fx_Dir_SynScatter)}
if (!dir.exists(Fx_Dir_Crosses)){dir.create(Fx_Dir_Crosses)}

# Get all FX neurons (FC, FS, FR)
FX_SynsAll=subset(FBC_SynsAll, !(is.na(FBcol)) & startsWith(type,"F"))
FX_SynsAll$FBcol=factor(FX_SynsAll$FBcol, levels=sort(unique(FX_SynsAll$FBcol)) )


# Get synapse distributions per layer
FX_Distribution=Get_SynLayerDistribution(FX_SynsAll, 25, Fx_Dir_Dist) # 25 is good here, needs to match PFX/Delta0 threshold below.


# Plot distribution of all synapses in entire FB and by layer
PlotSyns_byColumn(FX_SynsAll, "FX All", "FX_All", Fx_Dir, TRUE, TRUE)
PlotSyns_byLayer(FX_SynsAll, "FX All", "FX_All_Layers", "FBcol", Fx_Dir_SynScatter, TRUE, TRUE)


# Make the same plots but per neuron type 
FX_Types=unique(FX_SynsAll$type)
for (ttt in 1:length(FX_Types)){
  SubData=subset(FX_SynsAll, type == FX_Types[ttt])
  PlotSyns_byColumn(SubData, FX_Types[ttt], paste("FX_",FX_Types[ttt],sep=""), Fx_Dir_SynScatter, TRUE, FALSE)
}
for (ttt in 1:length(FX_Types)){
  SubData=subset(FX_SynsAll, type == FX_Types[ttt])
  PlotSyns_byLayer(SubData, FX_Types[ttt], paste("FX_",FX_Types[ttt],"_Layers",sep=""), "FBcol", Fx_Dir_SynScatter, FALSE, FALSE)
}
remove(SubData)


```



# For each layer, define mean column position based on FX data and plot for review.
# Here, FB column positions are defined for each layer using the FX neurons that innervate
# every column of that layer. This criteria cleans up the column positions by excluding neuron
# types that happen to have a few neurons with synapses in a layer but don't innervate all columns.
```{r}


# Get average X/Z position of each column in each layer
FX_Column_Positions = as.data.frame(FX_Distribution %>% group_by(FBcol, Layer, type) %>% 
                                      summarise(X_Mean = mean(X_Mean), Y_Mean=mean(Y_Mean), Z_Mean = mean(Z_Mean),
                                                Cross_XL_X = mean(Cross_XL_X), Cross_XL_Z = mean(Cross_XL_Z),
                                                Cross_XR_X = mean(Cross_XR_X), Cross_XR_Z = mean(Cross_XR_Z),
                                                Cross_YU_X = mean(Cross_YU_X), Cross_YU_Z = mean(Cross_YU_Z),
                                                Cross_YD_X = mean(Cross_YD_X), Cross_YD_Z = mean(Cross_YD_Z)))
 
                          
# Plot the distribution of FX column positions for all FX neuron types and each FX type individually 
PlotColumn_Aves(FX_Column_Positions, "FX_Columns_All", Fx_Dir_Crosses, FALSE)
PlotColumn_Types(FX_Column_Positions, "FX_Columns", Fx_Dir_Crosses, FALSE) 


# Subset FX column positions to include only those neurons that innervate all columns in a layer
FX_ColumnsInnervatedPerLayer= FX_Column_Positions %>% group_by(type, Layer) %>% summarise(n=n())
FX_ColumnsInnervatedPerLayer= subset(FX_ColumnsInnervatedPerLayer, n==9) 


# Get just those layers where the FX neuron types innervates all columns
FX_Column_Positions= inner_join(FX_Column_Positions, FX_ColumnsInnervatedPerLayer, by = c("type","Layer"))


# Replot data
PlotColumn_Aves(FX_Column_Positions, "FX_Columns_All_Clean", Fx_Dir_Crosses, FALSE)
PlotColumn_Types(FX_Column_Positions, "FX_Columns_Clean", Fx_Dir_Crosses, FALSE) 


# Subset FX_Distribution based on neurons that innervate all columns of a layer
FX_Distribution_Columns= inner_join(FX_Distribution, FX_ColumnsInnervatedPerLayer, by = c("type","Layer"))



```



# Get PB-FB-XX (ie PFX)  synapse distribution data
```{r}

# Make PB-FB-X  plotting directory
PFX_Dir=paste(PlotDir,"PFX_Plots_All","/",sep="")
PFX_Dir_Dist=paste(PFX_Dir,"PFX_MeasureWidth","/",sep="")
PFX_Dir_Mapping=paste(PFX_Dir,"PFX_Mapping","/",sep="")
PFX_Dir_MapGraph=paste(PFX_Dir,"PFX_MapGraph","/",sep="")
PFX_Dir_Crosses=paste(PFX_Dir,"PFX_Crosses","/",sep="")
if (!dir.exists(PFX_Dir)){dir.create(PFX_Dir)}
if (!dir.exists(PFX_Dir_Dist)){dir.create(PFX_Dir_Dist)}
if (!dir.exists(PFX_Dir_Mapping)){dir.create(PFX_Dir_Mapping)}
if (!dir.exists(PFX_Dir_MapGraph)){dir.create(PFX_Dir_MapGraph)}
if (!dir.exists(PFX_Dir_Crosses)){dir.create(PFX_Dir_Crosses)}

# Get PB-FB-X neuron synapse locations per layer
PFX_SynsAll=subset(FBC_SynsAll, !(is.na(PBglom)) & startsWith(type,"PF"))
PFX_Distribution=Get_SynLayerDistribution(PFX_SynsAll, 25, PFX_Dir_Dist) # 25 is good here, as some types have low synapse counts


# Subset PFX data to include only layers innervated by all neurons of a type
PFX_NamedBodies=subset(NamedBodies, startsWith(bodytype,"PF")) 
PFX_NeuronsPerType = PFX_NamedBodies %>% group_by(bodytype) %>% summarise(NeuronsPerType=n())
colnames(PFX_NeuronsPerType)[1]="type"
PFX_NeuronsOfTypePerLayer= PFX_Distribution %>% group_by(type, Layer) %>% summarise(NeuronsPerLayer=n())
PFX_NeuronsOfTypePerLayer=merge(PFX_NeuronsOfTypePerLayer, PFX_NeuronsPerType)
PFX_NeuronsOfTypePerLayer$PercentInLayer=PFX_NeuronsOfTypePerLayer$NeuronsPerLayer/PFX_NeuronsOfTypePerLayer$NeuronsPerType*100 
PFX_NeuronsOfTypePerLayer = subset(PFX_NeuronsOfTypePerLayer, PercentInLayer>90) #PFNp_a has less than 100- 4 bodies dont innervate pb glom. PFNp_b has one neuron missing.
PFX_Distribution_Filt=inner_join(PFX_Distribution, PFX_NeuronsOfTypePerLayer, by = c("type","Layer"))
remove(PFX_Distribution)



#PFX_Distribution2=subset(PFX_Distribution, X_HW_Orth<2000)

#hist(PFX_Distribution2$X_HW_Orth ,100)


ggplot() + geom_point(data = subset(PFX_Distribution,Layer=="L1"), aes(x=X_Mean, y=Z_Mean)) +
  geom_path(data=Outline_FB_XZ, aes(x=c1, y=c2), size = 1) + xlim(c(-9000, 9000)) +  coord_fixed(ratio = 1)


```



# Get Delta0 synapse distribution data
```{r}


# Make plotting directory
D0_Dir=paste(PlotDir,"D0_Plots_All","/",sep="")
D0_Dir_Dist=paste(D0_Dir,"D0_MeasureWidth","/",sep="")
D0_Dir_Mapping=paste(D0_Dir,"D0_Mapping","/",sep="")
D0_Dir_Crosses=paste(D0_Dir,"D0_Crosses","/",sep="")
if (!dir.exists(D0_Dir)){dir.create(D0_Dir)}
if (!dir.exists(D0_Dir_Dist)){dir.create(D0_Dir_Dist)}
if (!dir.exists(D0_Dir_Mapping)){dir.create(D0_Dir_Mapping)}
if (!dir.exists(D0_Dir_Crosses)){dir.create(D0_Dir_Crosses)}

# Get Delta0 neuron synapse locations per layer
D0_SynsAll=subset(FBC_SynsAll, startsWith(type,"Delta0")) # Delta12s are included here and need to be identified
D0_Distribution=Get_SynLayerDistribution(D0_SynsAll, 25, D0_Dir_Dist) # 25 is good here, as some types have low synapse counts



# Subset D0 data to include only layers innervated by all neurons of a type
D0_NamedBodies=subset(NamedBodies, startsWith(bodytype,"Delta0")) 
D0_NeuronsPerType = D0_NamedBodies %>% group_by(bodytype) %>% summarise(NeuronsPerType=n())
colnames(D0_NeuronsPerType)[1]="type"
D0_NeuronsOfTypePerLayer= D0_Distribution %>% group_by(type, Layer) %>% summarise(NeuronsPerLayer=n())
D0_NeuronsOfTypePerLayer=merge(D0_NeuronsOfTypePerLayer, D0_NeuronsPerType)
D0_NeuronsOfTypePerLayer$PercentInLayer=D0_NeuronsOfTypePerLayer$NeuronsPerLayer/D0_NeuronsOfTypePerLayer$NeuronsPerType*100 
D0_NeuronsOfTypePerLayer = subset(D0_NeuronsOfTypePerLayer, PercentInLayer==100) #Delta0L is missing synapses at the moment
D0_Distribution_Filt=inner_join(D0_Distribution, D0_NeuronsOfTypePerLayer, by = c("type","Layer"))


```




# Find delta12 neurons, assign them names with columns for Shin-ya, and remove them from D0_Distribution_Filt
```{r}

# Make delta12 directory
D12_Dir=paste(PlotDir,"D12_Plots_All","/",sep="")
if (!dir.exists(D12_Dir)){dir.create(D12_Dir)}

# Find the delta12s based on width of synapse cloud
D12s=D0_SynsAll %>% group_by(bodyid) %>% summarize (XXX=sd(X), YYY=sd(Y), ZZZ=sd(Z))
hist(D12s$XXX,100)
D12s=subset(D12s, XXX>2500) #2500 is good
D12s=mutate(D12s, name=neuprint_get_meta(bodyid)$name, type=neuprint_get_meta(bodyid)$type)

# Check if there are any neurons named delta12 that weren't detected
D12s_withname=subset(NamedBodies, startsWith(bodyname, "Delta12"))
sum(D12s_withname$bodyid %in% D12s$bodyid)/length(D12s_withname$bodyid)
D12s_withname$bodyid[!D12s_withname$bodyid %in% D12s$bodyid]
print(paste("1342539738 is borderline?"))

# Make plots of all detected D12s
for (nnn in 1:length(D12s$bodyid)){
  Temp_Syns=subset(FBC_SynsAll, bodyid == D12s$bodyid[nnn])
  P1=ggplot() + geom_point(data=Temp_Syns, aes(x=X, y=Z)) + 
    geom_path(data=Outline_FB_XZ, aes(x=c1, y=c2), size = 1) + xlim(c(-9000, 9000)) +  coord_fixed(ratio = 1) +
    ggtitle(paste(D12s$type[nnn],D12s$name[nnn]))
  P2=ggplot() + geom_point(data=Temp_Syns, aes(x=X, y=-Y)) + 
    geom_path(data=Outline_FB_XY, aes(x=c1, y=c2), size = 1) + xlim(c(-9000, 9000)) +  coord_fixed(ratio = 1)
  P12=ggarrange(P2,P1)
  ggsave(paste(D12_Dir, D12s$type[nnn], "_", D12s$name, "_", D12s$bodyid[nnn] , ".png",sep=""), plot = P12, 
         device='png', scale = 1, width = 8, height = 5, units ="in", dpi = 500, limitsize = TRUE,  bg = "transparent")
}

# Give them a new name and save data
D12s$name_new = paste(D12s$type, "_C0",sep="")
save(D12s, file = paste(D12_Dir,"D12.Rdata",sep=""))
write.xlsx(D12s,  paste(D12_Dir,"D12.xlsx",sep=""), sheetName = "Sheet1", col.names = TRUE, row.names = TRUE, append = FALSE)


# Exclude these neurons from D0_Distribution_Filt
D0_Distribution_Filt=subset(D0_Distribution_Filt, !(bodyid %in% D12s$bodyid))


```



# Assign the PB-FB-XX neurons to columns defined by the closet FX column for each layer.
# Plot the PB-FB glomerulus->column pattern for each PB-FB-XX neuron
```{r}


# Assign column names based on closest neuron
PFX_Distribution_Columns = Assign_FB_Columns(PFX_Distribution_Filt, FX_Distribution_Columns, PFX_Dir_Mapping)
PFX_Distribution_Columns$PBglom = factor(PFX_Distribution_Columns$PBglom, levels= c("L9","L8","L7","L6","L5","L4","L3","L2","L1",
                                                                    "R1","R2","R3","R4","R5","R6","R7","R8","R9")) 
remove(PFX_Distribution_Filt)

# Get number of neurons going from each glom to each column
PFX_GlomToColumn_All=PFX_Distribution_Columns %>% group_by(bodyid, type, PBglom, FBcol) %>% summarise(Num_layers = n(), FBcol_Con= mean(FBcol_Con))
PFX_GlomToColumn_All=PFX_GlomToColumn_All %>% group_by(type, PBglom, FBcol) %>% summarise(Num_Neurons = n(), FBcol_Con= mean(FBcol_Con))


# Plot PB->FB mapping as a graph
Plot_PBglom_FBcol_Mapping(PFX_GlomToColumn_All, PFX_Dir_MapGraph, "ALL")


# Manually update mappings to correct what we think are errors
PFX_GlomToColumn_Sym=PFX_GlomToColumn_All
UpdateMapping=data.frame(type = character(), PBglom =  character(), FBcol=  character(), FBcol_New =  character() )
UpdateMapping=rbind(UpdateMapping,
                    data.frame(type = "PFGs", PBglom = "L8", FBcol= "C9", FBcol_New = "C8" ),
                    data.frame(type = "PFGs", PBglom = "L7", FBcol= "C8", FBcol_New = "C7" ),
                    data.frame(type = "PFL1", PBglom = "R6", FBcol= "C2", FBcol_New = "C3" ),
                    data.frame(type = "PFL1", PBglom = "R5", FBcol= "C3", FBcol_New = "C4" ),
                    data.frame(type = "PFNa", PBglom = "L7", FBcol= "C7", FBcol_New = "C6" ),
                    data.frame(type = "PFNd", PBglom = "R8", FBcol= "C3", FBcol_New = "C2" ),
                    data.frame(type = "PFNd", PBglom = "L5", FBcol= "C5", FBcol_New = "C4" ),
                    data.frame(type = "PFNp_a", PBglom = "L4", FBcol= "C4", FBcol_New = "C3" ),
                    data.frame(type = "PFNp_a", PBglom = "L3", FBcol= "C1", FBcol_New = "C2" ),
                    data.frame(type = "PFNp_c", PBglom = "L9", FBcol= "C8", FBcol_New = "C9" ),
                    data.frame(type = "PFR_a", PBglom = "L8", FBcol= "C9", FBcol_New = "C8" ),
                    data.frame(type = "PFNp_b", PBglom = "R2", FBcol= "C8", FBcol_New = "C9"),
                    data.frame(type = "PFNp_b", PBglom = "L6", FBcol= "C6", FBcol_New = "C5"),
                    data.frame(type = "PFL3", PBglom = "L3", FBcol= "C6", FBcol_New = "C5" ),
                    data.frame(type = "PFL3", PBglom = "R1", FBcol= "C8", FBcol_New = "C7" ))



# Create new mapping with corrections from UpdateMapping  
N_Count=0
for (rrr in 1:length(UpdateMapping$type)){
  Row_Ind=which(as.character(PFX_GlomToColumn_Sym$type) == as.character(UpdateMapping$type[rrr]) &
                as.character(PFX_GlomToColumn_Sym$PBglom) == as.character(UpdateMapping$PBglom[rrr]) &
                as.character(PFX_GlomToColumn_Sym$FBcol) == as.character(UpdateMapping$FBcol[rrr]) )
  PFX_GlomToColumn_Sym$FBcol[Row_Ind] = as.character(UpdateMapping$FBcol_New[rrr])
  N_Count=N_Count+length(Row_Ind)
}
PFX_GlomToColumn_Sym = PFX_GlomToColumn_Sym %>% group_by(type, PBglom, FBcol) %>% summarise(Num_Neurons = sum(Num_Neurons),  FBcol_Con = mean(FBcol_Con))

# Plot NEW PB->FB mapping as a graph
Plot_PBglom_FBcol_Mapping(PFX_GlomToColumn_Sym, PFX_Dir_MapGraph, "SYM")

# Get number of neurons mapped from glom to cols
PFX_NeuonrsPerTypeWithMappings=PFX_GlomToColumn_All %>% group_by(type) %>% summarize(Num = sum(Num_Neurons))


```




# Now that we have the columns for PFX neurons (in PFX_Distribution_Columns), assign them to PFX_SynsAll and plot the crosses
```{r}


# Get subset of mapping information
PFX_Distribution_Columns_Mapping=PFX_Distribution_Columns[c("bodyid","PBglom","FBcol")]


# Update PFX_SynsAll
Temp_ColNames=colnames(PFX_SynsAll)
PFX_SynsAll=PFX_SynsAll[!colnames(PFX_SynsAll)=="FBcol"]
PFX_SynsAll=inner_join(PFX_SynsAll, PFX_Distribution_Columns_Mapping, by=c("bodyid","PBglom"))
PFX_SynsAll=PFX_SynsAll[Temp_ColNames]


# Get average X/Z position of each column in each layer
PFX_Column_Positions = as.data.frame(PFX_Distribution_Columns %>% group_by(FBcol, Layer, type) %>% 
                                      summarise(X_Mean = mean(X_Mean), Y_Mean=mean(Y_Mean), Z_Mean = mean(Z_Mean),
                                                Cross_XL_X = mean(Cross_XL_X), Cross_XL_Z = mean(Cross_XL_Z),
                                                Cross_XR_X = mean(Cross_XR_X), Cross_XR_Z = mean(Cross_XR_Z),
                                                Cross_YU_X = mean(Cross_YU_X), Cross_YU_Z = mean(Cross_YU_Z),
                                                Cross_YD_X = mean(Cross_YD_X), Cross_YD_Z = mean(Cross_YD_Z)))


# Plot the distribution of PB-FB-XX column positions for all neurons and each type individually 
PlotColumn_Aves(PFX_Column_Positions, "PFX_Columns_All", PFX_Dir_Crosses, FALSE)
PlotColumn_Types(PFX_Column_Positions, "PFX_Columns", PFX_Dir_Crosses, FALSE) 






```


# Assign columns to Delta0s, plot crosses, and save names for Shin-ya
```{r}


# Assign column names based on closest neuron
D0_Distribution_Columns = Assign_FB_Columns(D0_Distribution_Filt, FX_Distribution_Columns, D0_Dir_Mapping)
D0_Distribution_Columns$PBglom = factor(D0_Distribution_Columns$PBglom, levels= c("L9","L8","L7","L6","L5","L4","L3","L2","L1",
                                                                    "R1","R2","R3","R4","R5","R6","R7","R8","R9")) 
#remove(D0_Distribution_Filt)



# Get subset of mapping information
D0_Distribution_Columns_Mapping=D0_Distribution_Columns[c("bodyid","FBcol")]


# Update D0_SynsAll
Temp_ColNames=colnames(D0_SynsAll)
D0_SynsAll=D0_SynsAll[!colnames(D0_SynsAll)=="FBcol"]
D0_SynsAll=inner_join(D0_SynsAll, D0_Distribution_Columns_Mapping, by=c("bodyid"))
D0_SynsAll=D0_SynsAll[Temp_ColNames]


# Get average X/Z position of each column in each layer
D0_Column_Positions = as.data.frame(D0_Distribution_Columns %>% group_by(FBcol, Layer, type) %>% 
                                      summarise(X_Mean = mean(X_Mean), Y_Mean=mean(Y_Mean), Z_Mean = mean(Z_Mean),
                                                Cross_XL_X = mean(Cross_XL_X), Cross_XL_Z = mean(Cross_XL_Z),
                                                Cross_XR_X = mean(Cross_XR_X), Cross_XR_Z = mean(Cross_XR_Z),
                                                Cross_YU_X = mean(Cross_YU_X), Cross_YU_Z = mean(Cross_YU_Z),
                                                Cross_YD_X = mean(Cross_YD_X), Cross_YD_Z = mean(Cross_YD_Z)))


# Plot the distribution of PB-FB-XX column positions for all neurons and each type individually 
PlotColumn_Aves(D0_Column_Positions, "D0_Columns_All", D0_Dir_Crosses, FALSE)
PlotColumn_Types(D0_Column_Positions, "D0_Columns", D0_Dir_Crosses, FALSE) 



# Give them a new name and save data
D0_Names=distinct(D0_SynsAll[c("bodyid","type","bodyname","FBcol")])
D0_Names$bodyid=as.factor(D0_Names$bodyid)
D0_Names$new_name=paste(D0_Names$bodyname, "_", D0_Names$FBcol,sep="")  
write.xlsx(D0_Names,  paste(D0_Dir,"D0_Names.xlsx",sep=""), sheetName = "Sheet1", col.names = TRUE, row.names = TRUE, append = FALSE)



```



# Save the entire workspace to a file for later script to use.
```{r}
# Save entire workspace to file
save.image(file=paste(SaveDir,'All_Data.Rdata',sep=""))
```



# How many columns do delta0s have?
# Make plots of mean synapse locations to see if columns pop out
```{r}


Plot_NeuronSynMeanPos<- function(Plot_Syns, LayerToPlot){
  col_vector=GetColorMap("FBcol")
  eval(parse( text= paste("Outline=Outline_", as.character(LayerToPlot),"_XZ",sep="") ))
  
  # Make scatter plot
  p_1=ggplot() + geom_point(data=subset(Plot_Syns, Layer==LayerToPlot), aes(x=X_Mean, y=Z_Mean, color=FBcol), shape=16, alpha=0.3) + 
    geom_path(data=Outline, aes(x=c1, y=c2), size = 1) + xlim(c(-9000, 9000)) +  coord_fixed(ratio = 1) +
    theme_void() + guides(fill=FALSE) + theme(legend.position = "none") +
    scale_color_manual(values=col_vector)  +  theme(
      panel.background = element_rect(fill = "transparent"), # bg of the panel
      plot.background = element_rect(fill = "transparent", color = NA), # bg of the plot
      panel.grid.major = element_blank(), # get rid of major grid
      panel.grid.minor = element_blank(), # get rid of minor grid
      legend.background = element_rect(fill = "transparent"), # get rid of legend bg
      legend.box.background = element_rect(fill = "transparent") # get rid of legend panel bg
    )
  
  # Make 2D histogram
  p_2=ggplot() + geom_hex(data=subset(Plot_Syns, Layer==LayerToPlot), aes(x=X_Mean, y=Z_Mean), bins = 20) +
    geom_path(data=Outline, aes(x=c1, y=c2), size = 1) + xlim(c(-9000, 9000)) +  coord_fixed(ratio = 1) +
    theme_void() + guides(fill=FALSE) + theme(legend.position = "none") +
    scale_color_manual(values=col_vector)  +  theme(
      panel.background = element_rect(fill = "transparent"), # bg of the panel
      plot.background = element_rect(fill = "transparent", color = NA), # bg of the plot
      panel.grid.major = element_blank(), # get rid of major grid
      panel.grid.minor = element_blank(), # get rid of minor grid
      legend.background = element_rect(fill = "transparent"), # get rid of legend bg
      legend.box.background = element_rect(fill = "transparent") # get rid of legend panel bg
    )
  pp=ggarrange(p_1, p_2)
  
  return(p_1)
}


# Plot FX mean positions
FX_L1=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L1")
FX_L2=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L2")
FX_L3=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L3")
FX_L4=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L4")
FX_L5=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L5")
FX_L6=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L6")
FX_L7=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L7")
FX_L8=Plot_NeuronSynMeanPos(FX_Distribution_Columns, "L8") + ggtitle("FX Neurons")
FX_All=ggarrange(FX_L8,FX_L7,FX_L6,FX_L5,FX_L4,FX_L3,FX_L2,FX_L1, nrow = 8, ncol = 1)
ggsave(paste(PlotDir, "FX_MeanSynPositions" , ".png",sep=""), plot = FX_All, 
         device='png', scale = 1, width = 4, height = 10, units ="in", dpi = 500, limitsize = TRUE,  bg = "transparent")


# Plot PFX mean positions
PFX_L1=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L1")
PFX_L2=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L2")
PFX_L3=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L3")
PFX_L4=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L4")
PFX_L5=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L5")
PFX_L6=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L6")
PFX_L7=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L7")
PFX_L8=Plot_NeuronSynMeanPos(PFX_Distribution_Columns, "L8") + ggtitle("PFX Neurons")
PFX_All=ggarrange(PFX_L8,PFX_L7,PFX_L6,PFX_L5,PFX_L4,PFX_L3,PFX_L2,PFX_L1, nrow = 8, ncol = 1)
ggsave(paste(PlotDir, "PFX_MeanSynPositions" , ".png",sep=""), plot = PFX_All, 
         device='png', scale = 1, width = 4, height = 10, units ="in", dpi = 500, limitsize = TRUE,  bg = "transparent")


# Plot delta0 mean positions
D0_L1=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L1")
D0_L2=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L2")
D0_L3=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L3")
D0_L4=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L4")
D0_L5=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L5")
D0_L6=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L6")
D0_L7=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L7")
D0_L8=Plot_NeuronSynMeanPos(D0_Distribution_Columns, "L8") + ggtitle("D0 Neurons")
D0_All=ggarrange(D0_L8,D0_L7,D0_L6,D0_L5,D0_L4,D0_L3,D0_L2,D0_L1, nrow = 8, ncol = 1)
ggsave(paste(PlotDir, "D0_MeanSynPositions" , ".png",sep=""), plot = D0_All, 
         device='png', scale = 1, width = 4, height = 10, units ="in", dpi = 500, limitsize = TRUE,  bg = "transparent")

# Plot all types
PP_All=ggarrange(FX_All, PFX_All, D0_All,ncol = 3, nrow = 1)
ggsave(paste(PlotDir, "AllTypes_MeanSynPositions" , ".png",sep=""), plot = PP_All, 
         device='png', scale = 1, width = 12, height = 10, units ="in", dpi = 500, limitsize = TRUE,  bg = "transparent")






```




























