---
title: "Notebook for plotting PB-FB-XX columnar neuron arbor width and inter-column distance"
output:
  html_document:
    df_print: paged
---

### Load libraries
```{r message=FALSE, warning=FALSE}
library(neuprintrExtra)
library(neuprintr)
library(ggraph)
library(stringr)
library(zoo)
library(robustbase)
library(numbers)
library(dplyr)
library(tidyr)
library(tibble)
```

# Make directories where figures will be saved to
```{r}

# Directory where synapse location data is stored (output of FB_GetAndSave_Synapses.Rmd)
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save main plots to
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/Figure_ColumnWidth/"
if (!dir.exists(PlotDir)){dir.create(PlotDir)}

# Directory where synapse distribution plots will be saved to
Distribution_Dir=paste(PlotDir,"Syn_Distribution_Examples","/",sep="")
if (!dir.exists(Distribution_Dir)){dir.create(Distribution_Dir)}

```

# Connect to neuprint server
```{r}
neuprint_login()
```

# Get general functions
```{r}

source("FB_LayerOutline_Utils.r")
source("FB_Analysis_Utils.r")
source("FB_ColumnWidthCompute.r")

```

# Load pre-processed synapse location data and remove variables that won't be used
```{r}

load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
rm(list=c("roiEigen","Mesh_FB_Points","Mesh_FB_L1_Points", "Mesh_FB_L2_Points","Mesh_FB_L3_Points", "Mesh_FB_L4_Points",
          "Mesh_FB_L5_Points", "Mesh_FB_L6_Points","Mesh_FB_L7_Points", "Mesh_FB_L8_Points", "Mesh_FB_L9_Points","origin"))

# Assign Side, PB glom, and FB col info
FBC_SynsAll=Assign_FBcol_PBglom(FBC_SynsAll, "name", "Side", "PBglom", "FBcol")

```

# Compute the line that approximately bisects each FB layer in the XZ (horizontal) plane, shown in yellow below.
# The width of each neuron's arbor will be measured tangent to this line to account for the FB's curvature. 
```{r}

Mid_L1=Get_Mid(Outline_L1_XZ)
Mid_L2=Get_Mid(Outline_L2_XZ)
Mid_L3=Get_Mid(Outline_L3_XZ)
Mid_L4=Get_Mid(Outline_L4_XZ)
Mid_L5=Get_Mid(Outline_L5_XZ)
Mid_L6=Get_Mid(Outline_L6_XZ)
Mid_L7=Get_Mid(Outline_L7_XZ)
Mid_L8=Get_Mid(Outline_L8_XZ)

```


# Measure each neuron's arbor width (i.e. the width of its synapse distribution 
# along a direction tangent to the bisecting line computed above)
```{r message=FALSE, warning=FALSE}

# Measure the width of each neurons synapse distribution 
SynThresh=25 # 25 is good here, as some types have low synapse counts, making it hard to measure the distribution's width
PFX_SynsAll=subset(FBC_SynsAll, !(is.na(PBglom)) & startsWith(type,"PF"))
PFX_Distribution=Get_SynLayerDistribution(PFX_SynsAll, SynThresh, Distribution_Dir) 

# Subset PFX_Distribution based on neurons that innervate all 9 columns of a layer
PFX_ColumnsInnervatedPerLayer= PFX_Distribution %>% group_by(type, Layer) %>%  
  summarise(n = n_distinct(FBcol)) %>% subset(n==9)
PFX_Distribution_Columns= inner_join(PFX_Distribution, PFX_ColumnsInnervatedPerLayer, by = c("type","Layer"))
remove(PFX_Distribution)

```


# Make a histogram showing the distribution of arbor widths for each supertype
```{r message=FALSE, warning=FALSE}

# Group neurons into supertypes
PFX_Distribution_Columns$supertype2 =NA
PFX_Distribution_Columns$supertype2 [startsWith(as.character(PFX_Distribution_Columns$type),"PFN")]="PFN"
PFX_Distribution_Columns$supertype2 [startsWith(as.character(PFX_Distribution_Columns$type),"PFG")]="PFGs"
PFX_Distribution_Columns$supertype2 [startsWith(as.character(PFX_Distribution_Columns$type),"PFR")]="PFR"
PFX_Distribution_Columns$supertype2 [startsWith(as.character(PFX_Distribution_Columns$type),"PFL")]="PFL"

# Plot the data
P_Hist = ggplot(PFX_Distribution_Columns, aes(x=X_HW_Orth*2/LayerLength, group = supertype2 , color = supertype2 )) + 
  geom_freqpoly(aes(y = stat(ncount)), binwidth=1/9/5, size=1) +
  scale_x_continuous( limits = c(0, 4/9), expand = c(0,0) , 
        breaks = c(0, signif(1/9, digits=2), signif(2/9, digits=2), signif(3/9, digits=2), signif(4/9, digits=2))) +
  theme_classic() + theme(text = element_text(size=12)) + scale_color_CX_supertype() +
  xlab("arbor width (fraction of layer)") + ylab("normalized proportion")
P_Hist
ggsave(paste(PlotDir, "PbFbXx_SynapseWidth", ".png",sep=""), plot = P_Hist, device='png',
       scale = 1, width = 4, height = 2, units ="in", dpi = 500, limitsize = TRUE,  bg = "transparent")

```


# Make a histogram showing the distribution of distances between neurons in adjacent columns
```{r message=FALSE, warning=FALSE}

# Get dataframe with just the information need
InterColumnDistance = PFX_Distribution_Columns[c("X_Mean","Y_Mean","Z_Mean","type","Layer","FBcol","Side","bodyid")]
InterColumnDistance = within(InterColumnDistance,  ID <- paste(type, Layer, FBcol,Side,bodyid,sep="_"))
InterColumnDistance = InterColumnDistance[c("X_Mean","Y_Mean","Z_Mean","ID")]

# Convert to matrix and use dist() to calculate all pairwise distances
InterColumnDistance= InterColumnDistance %>% 
  column_to_rownames("ID") %>% #make the ID the rownames. 
  dist() %>% 
  as.matrix() %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "ID.x") %>% #capture the row IDs
  gather(key = ID.y, value = dist, -ID.x) %>% 
  filter(ID.x < ID.y) %>% 
  as_tibble()

# Parse column names to get back Layer, Column, and type information on the neuron pairs
InterColumnDistance=Assign_FBcol_PBglom(InterColumnDistance, "ID.x", "Side.X", "Layer.X", "FBcol.X")
InterColumnDistance=Assign_FBcol_PBglom(InterColumnDistance, "ID.y", "Side.Y", "Layer.Y", "FBcol.Y")
InterColumnDistance$type.X=str_split_fixed(InterColumnDistance$ID.x, "_", Inf)[,1]
InterColumnDistance$type.Y=str_split_fixed(InterColumnDistance$ID.y, "_", Inf)[,1]

# Only consider distances between neuron pairs of the same type and between adjacent columns
InterColumnDistance=subset(InterColumnDistance, type.X==type.Y & Layer.X == Layer.Y)
InterColumnDistance=subset(InterColumnDistance, (FBcol.X == "C1" & FBcol.Y == "C2") | 
                                                (FBcol.X == "C2" & FBcol.Y == "C3") |
                                                (FBcol.X == "C3" & FBcol.Y == "C4") |
                                                (FBcol.X == "C4" & FBcol.Y == "C5") |
                                                (FBcol.X == "C5" & FBcol.Y == "C6") |
                                                (FBcol.X == "C6" & FBcol.Y == "C7") |
                                                (FBcol.X == "C7" & FBcol.Y == "C8") |
                                                (FBcol.X == "C8" & FBcol.Y == "C9") )

# Get layer lengths and normalize the distances bewteen neurons
LayerLengths=unique(PFX_Distribution_Columns[c("Layer","LayerLength")])
colnames(LayerLengths)[colnames(LayerLengths) == "Layer"]="Layer.X"
LayerLengths$Layer.X=as.character(LayerLengths$Layer.X)
InterColumnDistance=inner_join(InterColumnDistance, LayerLengths, by = "Layer.X")
InterColumnDistance$Distance_Norm=InterColumnDistance$dist/InterColumnDistance$LayerLength

# Group neurons into supertypes
InterColumnDistance$supertype2 =NA
InterColumnDistance$supertype2 [startsWith(as.character(InterColumnDistance$type.X),"PFN")]="PFN"
InterColumnDistance$supertype2 [startsWith(as.character(InterColumnDistance$type.X),"PFG")]="PFGs"
InterColumnDistance$supertype2 [startsWith(as.character(InterColumnDistance$type.X),"PFR")]="PFR"
InterColumnDistance$supertype2 [startsWith(as.character(InterColumnDistance$type.X),"PFL")]="PFL"

# Plot the data
P_Hist = ggplot(InterColumnDistance, aes(x=Distance_Norm, group = supertype2 , color = supertype2 )) + 
  geom_freqpoly(aes(y = stat(ncount)), binwidth=1/9/5, size=1) +
  scale_x_continuous( limits = c(0, 4/9), expand = c(0,0) , 
        breaks = c(0, signif(1/9, digits=2), signif(2/9, digits=2), signif(3/9, digits=2), signif(4/9, digits=2))) +
  theme_classic() + theme(text = element_text(size=12)) + scale_color_CX_supertype() +
  xlab("inter-column distance (fraction of layer)") + ylab("normalized proportion")
P_Hist
ggsave(paste(PlotDir, "PFX_InterColumnDistance", ".png",sep=""), plot = P_Hist, device='png',
       scale = 1, width = 4, height = 2, units ="in", dpi = 500, limitsize = TRUE,  bg = "transparent")

```

