---
title: "Notebook for getting FB synapses, performing PCA, and saving the data."
output:
  html_document:
    df_print: paged
---

# Load libraries
```{r message=FALSE, warning=FALSE}
library(neuprintrExtra)
library(neuprintr)
library(ggraph)
library(dplyr)
library(nat)
library(alphahull)
```

# Make a directory to save the data to.
```{r}

SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"
if (!dir.exists(SaveDir)){dir.create(SaveDir)}

```

# Connect to neuprint server.
```{r}
neuprint_login()
```

# Get general functions
```{r}

source("../R/SynapsePCAUtils.r")
source("FB_Analysis_Utils.r")

```


# Get information on all FB columnar neurons
```{r warning=FALSE}

# Get all FB bodies
NamedBodies=getNeuronsInRoiTable("FB",0)

# Exclude bodies that are not columnar
FB_Columnar_Type=c("PF","vDelta","hDelta","FR","FS","FC")
Logica=startsWith(NamedBodies$type, FB_Columnar_Type[1]) | startsWith(NamedBodies$type, FB_Columnar_Type[2]) |
       startsWith(NamedBodies$type, FB_Columnar_Type[3]) | startsWith(NamedBodies$type, FB_Columnar_Type[4]) |
       startsWith(NamedBodies$type, FB_Columnar_Type[5]) | startsWith(NamedBodies$type, FB_Columnar_Type[6]) 
IncludedTypes=unique(NamedBodies$type[Logica])
ColumnarBodies=subset(NamedBodies, NamedBodies$type %in% IncludedTypes)

```


# Get synapse locations for all columnar neurons and all layers
```{r warning=FALSE}

# Get synapses in layers 1-9
SynLocs_L1=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl1","L1") 
SynLocs_L2=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl2","L2") 
SynLocs_L3=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl3","L3") 
SynLocs_L4=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl4","L4") 
SynLocs_L5=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl5","L5") 
SynLocs_L6=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl6","L6") 
SynLocs_L7=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl7","L7") 
SynLocs_L8=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl8","L8") 
SynLocs_L9=Get_FBlayer_ColumnarSyns(ColumnarBodies$bodyid, "FBl9","L9") 

# Bind layer data into single data frame
FBC_SynsAll = do.call("rbind", list(SynLocs_L1, SynLocs_L2, SynLocs_L3, SynLocs_L4, SynLocs_L5, 
                                    SynLocs_L6, SynLocs_L7, SynLocs_L8, SynLocs_L9))
FBC_SynsAll$Layer=as.factor(FBC_SynsAll$Layer)

# Get meshes
Mesh_FB= neuprint_ROI_mesh("FB")
Mesh_FB_L1= neuprint_ROI_mesh("FBl1")
Mesh_FB_L2= neuprint_ROI_mesh("FBl2")
Mesh_FB_L3= neuprint_ROI_mesh("FBl3")
Mesh_FB_L4= neuprint_ROI_mesh("FBl4")
Mesh_FB_L5= neuprint_ROI_mesh("FBl5")
Mesh_FB_L6= neuprint_ROI_mesh("FBl6")
Mesh_FB_L7= neuprint_ROI_mesh("FBl7")
Mesh_FB_L8= neuprint_ROI_mesh("FBl8")
Mesh_FB_L9= neuprint_ROI_mesh("FBl9")

# Save synapse locations for later loading
save(FBC_SynsAll, Mesh_FB, Mesh_FB_L1, Mesh_FB_L2, Mesh_FB_L3, Mesh_FB_L4, Mesh_FB_L5,
     Mesh_FB_L6, Mesh_FB_L7, Mesh_FB_L8, Mesh_FB_L9, file = paste(SaveDir,"FBColumnarSynapses_Raw.RData",sep=""))

# Remove layer-specific variables
rm(list = c('SynLocs_L1','SynLocs_L2','SynLocs_L3','SynLocs_L4','SynLocs_L5','SynLocs_L6','SynLocs_L7','SynLocs_L8','SynLocs_L9'))

```


# Get each FB layer's ROI mesh
```{r}

Mesh_FB_Points=MeshPoints(Mesh_FB)
Mesh_FB_L1_Points=MeshPoints(Mesh_FB_L1)
Mesh_FB_L2_Points=MeshPoints(Mesh_FB_L2)
Mesh_FB_L3_Points=MeshPoints(Mesh_FB_L3)
Mesh_FB_L4_Points=MeshPoints(Mesh_FB_L4)
Mesh_FB_L5_Points=MeshPoints(Mesh_FB_L5)
Mesh_FB_L6_Points=MeshPoints(Mesh_FB_L6)
Mesh_FB_L7_Points=MeshPoints(Mesh_FB_L7)
Mesh_FB_L8_Points=MeshPoints(Mesh_FB_L8)
Mesh_FB_L9_Points=MeshPoints(Mesh_FB_L9)

```


# Center synapses and mesh points at new origin
```{r}

# Get new origin
origin = getCOM(Mesh_FB_Points)

# Reset orgin of all layers
Mesh_FB_Points = resetOrigin(Mesh_FB_Points, origin)
Mesh_FB_L1_Points = resetOrigin(Mesh_FB_L1_Points, origin)
Mesh_FB_L2_Points = resetOrigin(Mesh_FB_L2_Points, origin)
Mesh_FB_L3_Points = resetOrigin(Mesh_FB_L3_Points, origin)
Mesh_FB_L4_Points = resetOrigin(Mesh_FB_L4_Points, origin)
Mesh_FB_L5_Points = resetOrigin(Mesh_FB_L5_Points, origin)
Mesh_FB_L6_Points = resetOrigin(Mesh_FB_L6_Points, origin)
Mesh_FB_L7_Points = resetOrigin(Mesh_FB_L7_Points, origin)
Mesh_FB_L8_Points = resetOrigin(Mesh_FB_L8_Points, origin)
Mesh_FB_L9_Points = resetOrigin(Mesh_FB_L9_Points, origin)

# Reset origin of all synapses 
FBC_SynsAll = resetOrigin(FBC_SynsAll, origin)

```


# Perform PCA. Then rotate the PCs so that FB layers are mostly in x/y plane.
# Then project synapses locations into new reference frame.
```{r}

# Get eigenvectors
roiEigen = covPCA(Mesh_FB_Points)

# Rotate PCs
RotMat=makeRotMatYZ(-33) # 33 for paper
roiEigen$vectors= roiEigen$vectors %*% RotMat
RotMat=makeRotMatXY(-3) # -3 for paper
roiEigen$vectors= roiEigen$vectors %*% RotMat

# Project meshes into PCA space
Mesh_FB_Points = changeBasis(Mesh_FB_Points, roiEigen)
Mesh_FB_L1_Points = changeBasis(Mesh_FB_L1_Points, roiEigen)
Mesh_FB_L2_Points = changeBasis(Mesh_FB_L2_Points, roiEigen)
Mesh_FB_L3_Points = changeBasis(Mesh_FB_L3_Points, roiEigen)
Mesh_FB_L4_Points = changeBasis(Mesh_FB_L4_Points, roiEigen)
Mesh_FB_L5_Points = changeBasis(Mesh_FB_L5_Points, roiEigen)
Mesh_FB_L6_Points = changeBasis(Mesh_FB_L6_Points, roiEigen)
Mesh_FB_L7_Points = changeBasis(Mesh_FB_L7_Points, roiEigen)
Mesh_FB_L8_Points = changeBasis(Mesh_FB_L8_Points, roiEigen)
Mesh_FB_L9_Points = changeBasis(Mesh_FB_L9_Points, roiEigen)

# Project synapses into PCA space
FBC_SynsAll=changeBasis_df(FBC_SynsAll, roiEigen)

```


# Add the instance name of the pre and post neurons to FBC_SynsAll
```{r}

BodyId_And_Names=NamedBodies[c("bodyid","name")]
BodyId_And_PartnerNames=NamedBodies[c("bodyid","name")]
colnames(BodyId_And_PartnerNames)<-c("partner","partnername")
FBC_SynsAll=merge(FBC_SynsAll, BodyId_And_Names, by="bodyid")
FBC_SynsAll=merge(FBC_SynsAll, BodyId_And_PartnerNames, by="partner")

```


# Plot data in new and old reference frame
```{r message=FALSE}

# Make scatter plot new projection
ggplot(Mesh_FB_Points, aes(x=X, y=-Y)) + geom_point(size=1, alpha = 0.05) +  xlab("x=PC1") + ylab("y=PC2") + coord_fixed(ratio = 1) 
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=X, y=-Y), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L1_Points, aes(x=X, y=-Y), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=X, y=-Y), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=X, y=-Y), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=X, y=-Y), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=X, y=-Y), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=-Y), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=X, y=-Y), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=X, y=-Y), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=X, y=-Y), colour= "steelblue2",  size=1, alpha = 0.01) + coord_fixed(ratio = 1) 

# Make scatter plot of original space
ggplot(Mesh_FB_Points, aes(x=x, y=-z)) + geom_point(size=1, alpha = 0.05) +  xlab("x=PC1") + ylab("y=PC2") + coord_fixed(ratio = 1) 
ggplot() + geom_point(data=Mesh_FB_Points, aes(x=x, y=-z), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L1_Points, aes(x=x, y=-z), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L2_Points, aes(x=x, y=-z), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L3_Points, aes(x=x, y=-z), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L4_Points, aes(x=x, y=-z), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L5_Points, aes(x=x, y=-z), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L6_Points, aes(x=x, y=-z), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L7_Points, aes(x=x, y=-z), colour= "steelblue2",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L8_Points, aes(x=x, y=-z), colour= "slateblue4",  size=1, alpha = 0.01) + 
           geom_point(data=Mesh_FB_L9_Points, aes(x=x, y=-z), colour= "steelblue2",  size=1, alpha = 0.01) + coord_fixed(ratio = 1) 

```


# Get rid of original reference frame (the lowercase x,y,z data)
```{r}

# Meshes
Mesh_FB_Points=Mesh_FB_Points[ , !(names(Mesh_FB_Points) %in% c("x","y","z"))]
Mesh_FB_L1_Points=Mesh_FB_L1_Points[ , !(names(Mesh_FB_L1_Points) %in% c("x","y","z"))]
Mesh_FB_L2_Points=Mesh_FB_L2_Points[ , !(names(Mesh_FB_L2_Points) %in% c("x","y","z"))]
Mesh_FB_L3_Points=Mesh_FB_L3_Points[ , !(names(Mesh_FB_L3_Points) %in% c("x","y","z"))]
Mesh_FB_L4_Points=Mesh_FB_L4_Points[ , !(names(Mesh_FB_L4_Points) %in% c("x","y","z"))]
Mesh_FB_L5_Points=Mesh_FB_L5_Points[ , !(names(Mesh_FB_L5_Points) %in% c("x","y","z"))]
Mesh_FB_L6_Points=Mesh_FB_L6_Points[ , !(names(Mesh_FB_L6_Points) %in% c("x","y","z"))]
Mesh_FB_L7_Points=Mesh_FB_L7_Points[ , !(names(Mesh_FB_L7_Points) %in% c("x","y","z"))]
Mesh_FB_L8_Points=Mesh_FB_L8_Points[ , !(names(Mesh_FB_L8_Points) %in% c("x","y","z"))]
Mesh_FB_L9_Points=Mesh_FB_L9_Points[ , !(names(Mesh_FB_L9_Points) %in% c("x","y","z"))]

# Synapses
FBC_SynsAll=FBC_SynsAll[ , !(names(FBC_SynsAll) %in% c("x","y","z"))]

```


# Get outlines of each layer
```{r}

# Get XY outlines of each layer, with Y direction reversed so dorsal is up
alpha=155
Outline_FB_XY=MeshOutline(Mesh_FB_Points, "XY", alpha_rad=alpha)
Outline_L1_XY=MeshOutline(Mesh_FB_L1_Points, "XY", alpha_rad=alpha)
Outline_L2_XY=MeshOutline(Mesh_FB_L2_Points, "XY", alpha_rad=alpha)
Outline_L3_XY=MeshOutline(Mesh_FB_L3_Points, "XY", alpha_rad=alpha)
Outline_L4_XY=MeshOutline(Mesh_FB_L4_Points, "XY", alpha_rad=alpha)
Outline_L5_XY=MeshOutline(Mesh_FB_L5_Points, "XY", alpha_rad=alpha)
Outline_L6_XY=MeshOutline(Mesh_FB_L6_Points, "XY", alpha_rad=alpha)
Outline_L7_XY=MeshOutline(Mesh_FB_L7_Points, "XY", alpha_rad=alpha)
Outline_L8_XY=MeshOutline(Mesh_FB_L8_Points, "XY", alpha_rad=alpha)
Outline_L9_XY=MeshOutline(Mesh_FB_L9_Points, "XY", alpha_rad=alpha)

# Get XZ outlines of each layer, with Y direction reversed so dorsal is up
Outline_FB_XZ=MeshOutline(Mesh_FB_Points, "XZ", alpha_rad=alpha)
Outline_L1_XZ=MeshOutline(Mesh_FB_L1_Points, "XZ", alpha_rad=alpha)
Outline_L2_XZ=MeshOutline(Mesh_FB_L2_Points, "XZ", alpha_rad=alpha)
Outline_L3_XZ=MeshOutline(Mesh_FB_L3_Points, "XZ", alpha_rad=alpha)
Outline_L4_XZ=MeshOutline(Mesh_FB_L4_Points, "XZ", alpha_rad=alpha)
Outline_L5_XZ=MeshOutline(Mesh_FB_L5_Points, "XZ", alpha_rad=alpha)
Outline_L6_XZ=MeshOutline(Mesh_FB_L6_Points, "XZ", alpha_rad=alpha)
Outline_L7_XZ=MeshOutline(Mesh_FB_L7_Points, "XZ", alpha_rad=alpha)
Outline_L8_XZ=MeshOutline(Mesh_FB_L8_Points, "XZ", alpha_rad=alpha)
Outline_L9_XZ=MeshOutline(Mesh_FB_L9_Points, "XZ", alpha_rad=alpha)

# Check that each layer's outline has been computed correctly. 
# Mesh shapes may be updated in the future and new values for alpha_rad may need to chosen above. 
ggplot() + geom_point(data=Mesh_FB_L1_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L1_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L2_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L2_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L3_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L3_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L4_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L4_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L5_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L5_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L6_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L6_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L7_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L7_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L8_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L8_XZ, aes(x=c1, y=c2), size = 1) 

ggplot() + geom_point(data=Mesh_FB_L9_Points, aes(x=X, y=Z), colour= 'blueviolet',  size=1, alpha = 0.05) + 
  coord_fixed(ratio = 1) +  theme_void() + guides(color=FALSE) +
  geom_path(data=Outline_L9_XZ, aes(x=c1, y=c2), size = 1) 

```


# Save data for later loading in other notebooks
```{r}

save(NamedBodies, FB_Columnar_Type, ColumnarBodies, FBC_SynsAll, Mesh_FB_Points, Mesh_FB_L1_Points, Mesh_FB_L2_Points, Mesh_FB_L3_Points, Mesh_FB_L4_Points,
     Mesh_FB_L5_Points, Mesh_FB_L6_Points, Mesh_FB_L7_Points, Mesh_FB_L8_Points, Mesh_FB_L9_Points,
     roiEigen, origin, Outline_FB_XY,  Outline_L1_XY,  Outline_L2_XY,  Outline_L3_XY,  Outline_L4_XY,  Outline_L5_XY,  
     Outline_L6_XY,    Outline_L7_XY,  Outline_L8_XY,  Outline_L9_XY,  Outline_FB_XZ,  Outline_L1_XZ,  Outline_L2_XZ,
     Outline_L3_XZ,    Outline_L4_XZ,  Outline_L5_XZ,  Outline_L6_XZ,  Outline_L7_XZ,  Outline_L8_XZ,  Outline_L9_XZ,
     file = paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))

```

