---
title: "Notebook for plotting whether left and right PB-FB types target distinct neurons/types in FB (i.e. lateralization)"
output:
  html_document:
    df_print: paged
---

# Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
library(dtplyr)
library(neuprintrExtra)
library("xlsx")
library(tidyselect)
library(paletteer)
library(quantmod)
library(prismatic)
library(svglite)
options(nat.plotengine = 'rgl')
```

# Make directories where figures will be saved to
```{r}

# Home directory
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save plots to
PlotDir=paste(SaveDir, "/Figure_Lateralization/",sep="")
if (!dir.exists(PlotDir)){dir.create(PlotDir)}

```

# Connect to neuprint server
```{r}
neuprint_login()
```

# Get general functions
```{r}

source("FB_Analysis_Utils.r")

```

# Get all FB bodies and columnar types
```{r message=FALSE, warning=FALSE}

NamedBodies=getNeuronsInRoiTable("FB",0)
Columnar_Types=sort(unique( NamedBodies$type[startsWith(NamedBodies$type, "PF" )     | startsWith(NamedBodies$type, "FR" ) | 
                                             startsWith(NamedBodies$type, "FS" )     | startsWith(NamedBodies$type, "FC" ) | 
                                             startsWith(NamedBodies$type, "vDelta" ) | startsWith(NamedBodies$type, "hDelta")] ))
FBBodyCount=NamedBodies %>% group_by(type) %>% summarize(NumofNeurons=n())
FBColumnarBodyCount=subset(FBBodyCount, type %in% Columnar_Types)

```


# Get connectivity matrices for all PFX types
```{r}

# Get input and output tables
PFX_Types=unique(NamedBodies$type[startsWith(NamedBodies$type, "PF" )])
PFX_Bag=neuronBag(PFX_Types, slctROI="FB")
PFX_FB_Outputs_All=PFX_Bag[["outputs_raw"]]

# Subset data on outputs that are FB columnar types
PFX_FB_Outputs_All=subset(PFX_FB_Outputs_All, databaseType.to %in% Columnar_Types)

# Assign PBglom, FBcol, and Side from neuron names
PFX_FB_Outputs_All=Assign_FBcol_PBglom(PFX_FB_Outputs_All, "name.from", "Side.from", "PBglom.from", "FBcol.from")
PFX_FB_Outputs_All=Assign_FBcol_PBglom(PFX_FB_Outputs_All, "name.to", "Side.to", "PBglom.to", "FBcol.to")

```


# Compute various metrics indicitive of lateralization (i.e. where the left and right
# PB-FB-XX populations target either distinct downstream neurons or distinct neuron types)
```{r message=FALSE, warning=FALSE}

# Get unique pre-post pairs
Pre_Post=distinct(PFX_FB_Outputs_All[c("type.from","type.to")])

# Compute relative weight from left and right PB-FB-XX populations onto single downstream neurons
Scatter=PFX_FB_Outputs_All %>% group_by(Side.from, type.from, type.to, to) %>% summarise(weightRelative= sum(weightRelative))
Scatter_L=subset(Scatter, Side.from=="L")
colnames(Scatter_L)[colnames(Scatter_L) == "weightRelative"]="weightRelative_L"
Scatter_R=subset(Scatter, Side.from=="R")
colnames(Scatter_R)[colnames(Scatter_R) == "weightRelative"]="weightRelative_R"
Scatter_All=full_join(Scatter_L, Scatter_R, by=c("to", "type.from","type.to"))
Scatter_All$weightRelative_L[is.na(Scatter_All$weightRelative_L)]=0
Scatter_All$weightRelative_R[is.na(Scatter_All$weightRelative_R)]=0
rm(list=c("Scatter","Scatter_L","Scatter_R"))
Scatter_All=Scatter_All[c("type.from","type.to","to","weightRelative_R","weightRelative_L")]
Scatter_All=left_join(Scatter_All, distinct(PFX_FB_Outputs_All[c("to","FBcol.to")]), by="to")


# Loop over every Pre/Post connection pair and compute:
# 1) Lateralization (the proportjon of downstream neurons that receive input from the left or the right PB but not both)
# 2) PostProportion (the proportjon of neurons in a downstream neuron type targeted by a PB-FB-XX neuron type)
ConnectivityCriteria=data.frame(type.from=character(),type.to=character(),ColFromNum=numeric(),
                                PreProportion=numeric(),PostProportion=numeric(), Lateralization=numeric(), AverageWeight=numeric())
for (ppp in 1:length(Pre_Post$type.from)){

  # Consider only this pre-post type
  Temp_PFX_Out = subset(PFX_FB_Outputs_All, type.from == Pre_Post$type.from[ppp] & type.to == Pre_Post$type.to[ppp])
  Temp_Scatter = subset(Scatter_All, type.from == Pre_Post$type.from[ppp] & type.to == Pre_Post$type.to[ppp])

  # Calculate Lateralization and PostProportion
  PreNum=length(unique(Temp_PFX_Out$from))
  PostNum=length(unique(Temp_PFX_Out$to))
  FBColfromNum=length(unique(Temp_PFX_Out$FBcol.from))
  PreNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$type == Pre_Post$type.from[ppp]]
  PostNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$type == Pre_Post$type.to[ppp]]
  AverageWeight=mean((Temp_Scatter$weightRelative_L + Temp_Scatter$weightRelative_R)*PostNum/PostNum_All)
  Lateralization=1-sum(Temp_Scatter$weightRelative_R > 0 & Temp_Scatter$weightRelative_L > 0)/PostNum_All
  PostProportion=PostNum/PostNum_All
  PreProportion=PreNum/PreNum_All
  
  # Add this data to ConnectivityCriteria
  ConnectivityCriteria=rbind(ConnectivityCriteria, 
  data.frame(type.from=Pre_Post$type.from[ppp],type.to=Pre_Post$type.to[ppp],ColFromNum=FBColfromNum,
             PreProportion=PreProportion,PostProportion=PostProportion,Lateralization=Lateralization, AverageWeight=AverageWeight))
  
}


```


# Plot the amount of lateralization as a function of the proportion of postsynaptic neurons targeted and
# by the strength of the type-to-type connection. This shows that left/right lateralized connectivity
# matrices are from types with inconsistent and weak neuron-to-neuron connection matrices. 
```{r message=FALSE, warning=FALSE}

# remove PFLs
ConnectivityCriteria=subset(ConnectivityCriteria, !startsWith(as.character(type.from),"PFL"))

# Make supertype factor
ConnectivityCriteria$PresynapticClass =NA
ConnectivityCriteria$PresynapticClass [startsWith(as.character(ConnectivityCriteria$type.from),"PFGs")]="PFGs"
ConnectivityCriteria$PresynapticClass [startsWith(as.character(ConnectivityCriteria$type.from),"PFNa")]="PFNa"
ConnectivityCriteria$PresynapticClass [startsWith(as.character(ConnectivityCriteria$type.from),"PFNd")]="PFNd"
ConnectivityCriteria$PresynapticClass [startsWith(as.character(ConnectivityCriteria$type.from),"PFNm")]="PFNm (a/b)"
ConnectivityCriteria$PresynapticClass [startsWith(as.character(ConnectivityCriteria$type.from),"PFNp")]="PFNp (a/b/c/d/e)"
ConnectivityCriteria$PresynapticClass [startsWith(as.character(ConnectivityCriteria$type.from),"PFNv")]="PFNv"
ConnectivityCriteria$PresynapticClass [startsWith(as.character(ConnectivityCriteria$type.from),"PFR")]="PFR (a/b)"

# Make scatter plot (note that some jitter is added to resolve overlapping points)
ScatterColors <- paletteer_d("Polychrome::palette36")
ScatterColors = ScatterColors[c(5,17,8,6,11,33,1)]
P1=ggplot() + geom_point(data=ConnectivityCriteria, aes(x=PostProportion, y=Lateralization, size=AverageWeight, color=PresynapticClass),
                         alpha=0.8, shape=16, position= position_jitter(width = 0.025, height = 0.025)) +
  scale_color_manual(values=ScatterColors, drop=FALSE)  + theme_classic() + theme(aspect.ratio = 1) +
  xlab("Connection consistency")
P1
ggsave(paste(PlotDir, "Proportion_Vs_Lateralization_byWeight.png",sep=""),
         plot = P1, device='png', scale = 1, width =7, height = 6, units ="in", dpi = 500, limitsize = TRUE)


```



# For pre/post connections that are consistent, make scatter plot showing, for each downstream neuron,
# how much input it receives from the left and right PB-FB-XX populations. Dots along the x/y axes 
# represent neurons that receive input from the left or right PB-FB-XX populations (but not both).
```{r message=FALSE, warning=FALSE}

# Subset Scatter_All on consistent connections (where most neurons in both populatons are involved)
Scatter_All_Consistent = subset(Scatter_All, !startsWith(type.from,"PFL"))
Scatter_All_Consistent = left_join(Scatter_All_Consistent, ConnectivityCriteria, by=c("type.from","type.to"))
Scatter_All_Consistent = subset(Scatter_All_Consistent, ColFromNum>7 & (PreProportion>0.6 | PostProportion>0.6) )

# Make supertype factor
Scatter_All_Consistent$PresynapticClass =NA
Scatter_All_Consistent$PresynapticClass [startsWith(as.character(Scatter_All_Consistent$type.from),"PFGs")]="PFGs"
Scatter_All_Consistent$PresynapticClass [startsWith(as.character(Scatter_All_Consistent$type.from),"PFNa")]="PFNa"
Scatter_All_Consistent$PresynapticClass [startsWith(as.character(Scatter_All_Consistent$type.from),"PFNd")]="PFNd"
Scatter_All_Consistent$PresynapticClass [startsWith(as.character(Scatter_All_Consistent$type.from),"PFNm")]="PFNm (a/b)"
Scatter_All_Consistent$PresynapticClass [startsWith(as.character(Scatter_All_Consistent$type.from),"PFNp")]="PFNp (a/b/c/d/e)"
Scatter_All_Consistent$PresynapticClass [startsWith(as.character(Scatter_All_Consistent$type.from),"PFNv")]="PFNv"
Scatter_All_Consistent$PresynapticClass [startsWith(as.character(Scatter_All_Consistent$type.from),"PFR")]="PFR (a/b)"

# Make scatter plot for each supertype
ScatterColors <- paletteer_d("Polychrome::palette36")
ScatterColors = ScatterColors[c(5,17,8,6,11,33,1)]
LIM=max( c(Scatter_All_Consistent$weightRelative_L, Scatter_All_Consistent$weightRelative_R))
P1=ggplot() + geom_point(data=Scatter_All_Consistent, aes(x=weightRelative_L, y=weightRelative_R, color=PresynapticClass),alpha=0.8, shape=16) +
  scale_color_manual(values=ScatterColors, drop=FALSE)  + theme_classic() + theme(aspect.ratio = 1) + xlim(0,0.4) + ylim(0,0.4) + 
    xlab("relative weight from left PB") + ylab("relative weight from right PB")
P1
ggsave(paste(PlotDir, "SingleNeuron_Left_Vs_Right.png",sep=""),
         plot = P1, device='png', scale = 1, width =12, height = 6, units ="in", dpi = 500, limitsize = TRUE)

```



# Make scatter plot showing, for each posynaptic neuron type, the relative weight from the 
# left and right PB-FB-XX populations. If the left and right PB-FB-XX populations were to target
# distinct downstream types, then we would expect to see points along the diagonal. 
```{r message=FALSE, warning=FALSE}

# Average Left/Right PB input by postsynaptic type. Need to multiple by PostProportion because not all
# postsynaptic neurons of a type receive input from the presynaptic type in question, and averaging
# would miss these 0 weights.
Scatter_All_Consistent_bytype=Scatter_All_Consistent %>% group_by(type.from, type.to, PresynapticClass) %>%
  summarise(weightRelative_R=mean(weightRelative_R*PostProportion), weightRelative_L=mean(weightRelative_L*PostProportion))

P1=ggplot() + geom_point(data=Scatter_All_Consistent_bytype, aes(x=weightRelative_L, y=weightRelative_R, color=PresynapticClass),alpha=0.8, shape=16) +
  scale_color_manual(values=ScatterColors, drop=FALSE)  + theme_classic() + theme(aspect.ratio = 1) + xlim(0,0.2) + ylim(0,0.2) +
  xlab("relative weight from left PB") + ylab("relative weight from right PB")
P1
ggsave(paste(PlotDir, "NeuronType_Left_Vs_Right.png",sep=""),
         plot = P1, device='png', scale = 1, width =5, height = 4, units ="in", dpi = 500, limitsize = TRUE)

```


