---
title: "Notebook analyzing MBON to CX connections"
output:
  html_document:
    df_print: paged
---


### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
library(dtplyr)
library(neuprintrExtra)
library("xlsx")
library(tidyselect)
library(reshape2)
library(scales)
library(cowplot)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose save/plot directories
```{r}

# Directory to save data to.
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/MB_Analysis/"

# Create save/plot directory if they dont exists yet
if (!dir.exists(SaveDir)){dir.create(SaveDir)}

```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}

#source("../inputOutputRegionsVis.r")
#source("../R/connectivityMatricesTools.R")

```


# Get all MBONs from right MB
```{r}

# Get list of MBONS
MB_NamedBodies=getNeuronsInRoiTable("MB(R)",0)
MB_NamedBodies=subset(MB_NamedBodies, startsWith(name,"MBON"))
MBONs_Types_Table=getTypesTable(unique(MB_NamedBodies$type))

```




# ####################################################################################################################
# ######### Figure 0: Replicate MB Paper's MBON-->CX results #########################################################
# ####################################################################################################################


# A list of direct CX targets from the MB paper
```{r}

CXTypes <- supertype(read_csv("C:\\Users\\labadmin\\Dropbox\\FIBSEM CX Paper Jan 2020\\CX-cell-types060920"))$n.type

MB_Paper_Direct_Types=c("FB1C", "FB1H", "FB2A","FB2C","FB2L","FB4A","FB4C","FB4D","FB4F_b",
                        "FB4G","FB4H","FB4I","FB4J","FB4L","FB4M","FB4N","FB4O",
                        "FB4P_a","FB4P_b","FB4R","FB4X","FB4Y","FB5A","FB5AB","FB5C","FB5D",
                        "FB5E","FB5H","FB5I","FB5J","FB5K","FB5L","FB5M","FB5V","FB5X",
                        "FB6A","FB6P","FB6Q","FB6R","FB6T","FB6V","FB8F_a",
                        "LCNOp","LCNOpm","LNO2")

```


# Target list from the MB paper, using their criteria, to make sure we can mostly replicate their analysis.
# We get the exact same list as Li et al, with the exceptions of ER1_a(ring)_R which receives 10 synapses from MBON26(B'2d)_R.
# Perhaps their threshold was >10 instead of >=10 (as they report)?
```{r}

# MB paper's criteria
Li_DownBag=neuronBag(MBONs_Types_Table, by.roi=FALSE, omitInputs=TRUE, omitOutputs=FALSE)
Li_Direct=Li_DownBag$outputs_raw
Li_Direct=subset(Li_Direct, databaseType.to %in% CXTypes)
Li_Direct=subset(Li_Direct, weight>10) 

sort(unique(Li_Direct$type.to)) %in% MB_Paper_Direct_Types

sort(unique(Li_Direct$type.to))
MB_Paper_Direct_Types


```



# ####################################################################################################################
# ######### Figure 1: MBON to CX direct connections ##################################################################
# ####################################################################################################################
CD's Notes: 
1) MBON05 has no branches ipsilateral to the cell body, only contralateral. 
   FB4R only has dendrites ipsilateral to cell body. 
   Therefore, only MBON05_L (not MBON05_R) makes synapses onto FB4R_R.
2) MBON09 has bilateral branches, but only makes contact with ipsilateral FB4R, i.e., MBON09_R onto FB4R_R.
3) MBON21 has bilateral branches, and synapses onto FB4R bilaterally.
4) MBON04 has bilateral branches, but more contralaterally relative to the name 
   (although the *_L cell body is just off to the midline on the right side).
5) MBON12R and MBON13R only have branches ipsilateral to the cell body.
6) MBON03 has bilateral branches, but more contralaterally relative to the name.
7) MBON22 has ipsilateral branches in the calyx and bilateral branches in SIP/SMP.
8) MBON30 has bilateral branches, but more ipsilateral to the cell body.


# Get MBON to CX direct connections
```{r}

# Questions and to-do:
# SHOULD I average by databaseType.from and .to? 
# If not, I need to cluster by type, no lateralized type, orthewise L/R pairs end up apart in graphs
# CD has MBON12 and MBON13 going to FB5J. I don't. Why? 
# Look at antomy of every MBON, can we just take those from the right hemi?
# Understand CD's criteria and replicate
# How to average across just those ROIs where a neuron receives input (ROI level matters)
# Should I only include ROI outside the CX in computing weight relative, as CD does?



# Get first layer lateralized outputs
DownBag_L1=neuronBag(MBONs_Types_Table, by.roi=TRUE, omitInputs=TRUE, omitOutputs=FALSE)
DownBag_L1=lateralize_types(DownBag_L1) # Lateralize to take into account projections that may be missing from the volume


# Compute weight relative by summing ROIs not in the CX and not on the left side of the brain, which deals with polarity and lateralization issues.
# Polarity, since most FBt types receive a lot of input in the CX, the roi-independent relative weight can be very low.
# Lateralization, since some CX targets could have  dendrites on the left or dendrites on the right or both. So it makes sense to use all MBONs (L and R)
#   and just look at their targets in right ROIs (which should be more complete).
roiH <- getRoiTree()
outsideRegions <- unique(selectRoiSet(exceptions=sapply(as.character(unique(roiH$level1[grepl(roiH$level1,pattern="(R)")])),
                  function(i) return(1),USE.NAMES = TRUE,simplify=FALSE), exceptionLevelMatch = 1)$roi[roiH$level1!="CX" & roiH$side4!="Left"])
DownBag_L1 <- combineRois(DownBag_L1, outsideRegions, newRoi="NonCX") # Sum synapses across all non-CX ROIs on the right side
                                  

# Recompute type-to-type table
DownTypes_L1=getTypesTable(unique(c(DownBag_L1$outputs_raw$databaseType.from,
                                    DownBag_L1$outputs_raw$databaseType.to))) %>% lateralize_types()
Downstream_T2T_L1=getTypeToTypeTable(DownBag_L1$outputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0,
                                     singleNeuronThresholdN = 3, pThresh = 1, typesTable = DownTypes_L1, oldTable = NULL) # No t-test type-to-type tables 


# Restrict to just 'strong' CX targets.
MB2CX_Direct=subset(Downstream_T2T_L1, databaseType.to %in% CXTypes  & weightRelative>0.01 & weight>10)
MB2CX_Direct_Exclude=subset(Downstream_T2T_L1, databaseType.to %in% CXTypes & !(weightRelative>0.01 & weight>10) )



```



# Function to go from lateralized type-to-type weights back to unlateralized
```{r}

UnLateralize() <- function(Data){
  Data %>% group_by(databaseType.to) %>% summarize()
}


```


# Make MB paper style graph of MBON to CX direct connections
```{r}


# Average over left/right pairs
Graph_Data=MB2CX_Direct %>% group_by(databaseType.from, databaseType.to) %>%
  summarize(weightRelative=mean(weightRelative), outputContribution=mean(outputContribution), weight=mean(weight)) 

colnames(Graph_Data)=c("type.from","type.to","weightRelative","outputContribution","weight")
Graph_Data$roi="All"


# Cluster the FB neurons by their input vectors
Graph_Data_Clust=connectivityCluster(inputsTable = Graph_Data, outputsTable = NULL) %>% setClusters(h = 0.8, k = NULL)
Graph_Data_Clust=Graph_Data_Clust$inputsTable %>% arrange(cluster.to)



# Now sort inputs (MBONs) by which cluster they project most strongly to
PreOrder=Graph_Data_Clust %>% group_by(type.from) %>% filter(weightRelative == max(weightRelative))
PreOrder=PreOrder[c("type.from","cluster.to")]
colnames(PreOrder)=c("type.from","cluster.from")
Graph_Data_Clust=merge(Graph_Data_Clust,PreOrder, by="type.from")

  

P0=plotConnectivity(Graph_Data_Clust, slctROI = NULL, grouping = "type", connectionMeasure = "weightRelative",
  xaxis = c("outputs"), facetInputs = NULL, facetOutputs = NULL, theme = theme_minimal(),
  cmax = NULL, replacementLabels = NULL, orderIn = NULL, orderOut = NULL,
  legendName = NULL, showTable = "inputs") + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        #axis.ticks = element_blank(),
        aspect.ratio = 1)  
ggsave(paste(SaveDir, "MB_Direct_Clust.pdf",sep=""),
        plot = P0, device='pdf', scale = 1, width =8, height = 6, units ="in", dpi = 500, limitsize = TRUE)



P0=plotConnectivity(MB2CX_Direct, slctROI = NULL, grouping = "type", connectionMeasure = "weightRelative",
  xaxis = c("outputs"), facetInputs = NULL, facetOutputs = NULL, theme = theme_minimal(),
  cmax = NULL, replacementLabels = NULL, 
  orderIn = NULL, 
  orderOut = NULL,
  legendName = NULL, showTable = "inputs") + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        #axis.ticks = element_blank(),
        aspect.ratio = 1)  
ggsave(paste(SaveDir, "MB_Direct.pdf",sep=""),
        plot = P0, device='pdf', scale = 1, width =8, height = 6, units ="in", dpi = 500, limitsize = TRUE)



# Get node sizes
PostSize=Graph_Data_Clust %>% group_by(type.to) %>% summarize(Syns=sum(weight))
colnames(PostSize)=c("name","Size")
PreSize=Graph_Data_Clust %>% group_by(type.from) %>% summarize(Syns=sum(weight))
colnames(PreSize)=c("name","Size")
AllSize=rbind(PostSize, PreSize)
AllSize$name[startsWith(AllSize$name,"MBON")]=substr(AllSize$name[startsWith(AllSize$name,"MBON")], 5, 6)



Lout=2
if (Lout==1){
  
  # Pre Nodes
  MBON_Nodes=data.frame(name=sort(unique(Graph_Data_Clust$type.from) %>% as.character()))
  MBON_Nodes$name=substr(MBON_Nodes$name,5, 6)
  MBON_Nodes$x=0
  MBON_Nodes$y=(seq(from = 1, to = length(MBON_Nodes$name), by = 1)*1.8)
  
  # Post Nodes
  CX_Nodes=data.frame(name=rev(sort(unique(Graph_Data_Clust$type.to) %>% as.character()))) 
  L1to4=grepl("1",CX_Nodes$name) | grepl("2",CX_Nodes$name) | grepl("3",CX_Nodes$name) | grepl("4",CX_Nodes$name)
  CX_Nodes$x=NA
  CX_Nodes$x[L1to4]=-1
  CX_Nodes$x[!L1to4]=1
  CX_Nodes$y=NA
  CX_Nodes$y[L1to4]=rev(seq(from = 1, to = sum(L1to4), by = 1))
  CX_Nodes$y[!L1to4]=rev(seq(from = 1, to = sum(!L1to4), by = 1))
  
} else if (Lout==2){
  
  # Pre Nodes
  MBON_Nodes=data.frame(name=(unique(Graph_Data_Clust$type.from) %>% as.character()))
  MBON_Nodes$name=substr(MBON_Nodes$name,5, 6)
  MBON_Nodes$x=0
  MBON_Nodes$y=(seq(from = 1, to = length(MBON_Nodes$name), by = 1))
  MBON_Nodes$y=(MBON_Nodes$y-mean(MBON_Nodes$y))*1.2
  
  # Post Nodes
  CX_Nodes=data.frame(name=rev((unique(Graph_Data_Clust$type.to) %>% as.character()))) 
  CX_Nodes$x=1
  CX_Nodes$y=rev(seq(from = 1, to = length(CX_Nodes$name), by = 1))
  CX_Nodes$y=CX_Nodes$y-mean(CX_Nodes$y)
}


# edges
EDGES=Graph_Data_Clust[c("type.from","type.to","weightRelative")]
colnames(EDGES)=c("from","to","weight")
EDGES$from[startsWith(EDGES$from,"MBON")]=substr(EDGES$from[startsWith(EDGES$from,"MBON")], 5, 6)


# nodes
NODES=rbind(MBON_Nodes, CX_Nodes)
NODES=merge(NODES, AllSize, by="name")


# Node Colors
TransmitterColor=c("#F26629","#20B685","#3668AC") #ACH, GLU
NODES$COLORZ="Black"
NODES$COLORZ[NODES$name %in% c("12","13","15","21","22","23","24","26","27","29","33","35")]=TransmitterColor[1]
NODES$COLORZ[NODES$name %in% c("01 ","03","04","05","06","30","34")]=TransmitterColor[2]
NODES$COLORZ[NODES$name %in% c("09","11")]=TransmitterColor[3]


# Node fills
NODES$FILLZ=NODES$COLORZ
NODES$FILLZ[NODES$name %in% c("21","22","23","24","26","27","29","33","35")]="white"


#Edge colors
EDGES$COLORZ="black"
EDGES$COLORZ[EDGES$from %in% c("12","13","15","21","22","23","24","26","27","29","33","35")]=TransmitterColor[1]
EDGES$COLORZ[EDGES$from %in% c("01 ","03","04","05","06","30","34")]=TransmitterColor[2]
EDGES$COLORZ[EDGES$from %in% c("09","11")]=TransmitterColor[3]
EDGES$COLORZ=factor(EDGES$COLORZ, levels=unique(EDGES$COLORZ))
col_vector=levels(EDGES$COLORZ)



# Make graph
graph = tbl_graph(NODES, EDGES)



P1=ggraph(graph,layout="manual",x=NODES$x,y=NODES$y) + 
  geom_edge_fan( aes(width=weight, color=COLORZ),
                 arrow = arrow(length = unit(2, 'mm'),ends = "last", type = "closed"),
                 end_cap = circle(0.66, 'cm'), alpha=1,strength=1, n=2, linemitre=1) +
  geom_node_point(aes(size = Size), color=NODES$COLORZ, fill=NODES$FILLZ) + scale_size(range = c(7,12)) +
  geom_node_text(aes(label=name),angle=0,size=3, nudge_x = NODES$x*0.08, color='black' ) +
  theme_classic() + 
  theme(legend.text=element_text(size=6),legend.title=element_text(size=6),
        axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),axis.title.y=element_blank()) +
  scale_edge_width(range = c(1,6)) + scale_edge_color_manual(values=col_vector)
print(P1)
ggsave(paste(SaveDir, "Graph_V1.pdf",sep=""),
        plot = P1, device='pdf', scale = 1, width =8, height = 13, units ="in", dpi = 500, limitsize = TRUE)



```



# Plot threshold dependence
```{r}


# For each MBON with direct connections to the CX plot the max relative weight
All_MB2CX_Direct=Downstream_T2T_L1 %>% 
  subset(databaseType.to %in% CXTypes & !databaseType.from=="MBON15-like") %>%
  group_by(databaseType.from, databaseType.to) %>%
  summarize(weightRelative=mean(weightRelative), outputContribution=mean(outputContribution), weight=mean(weight)) 
MBON_Direct_byThresh_Plot=All_MB2CX_Direct %>% group_by(databaseType.from) %>% summarize(weightRelative=max(weightRelative))


P1a=ggplot(data=MBON_Direct_byThresh_Plot, aes(x=databaseType.from, y=weightRelative)) + 
  geom_bar(stat="identity", color="black", fill='black', width=0.850) + theme_classic()  + 
  theme(axis.text.x = element_text(angle = 90)) + scale_y_continuous(breaks = seq(from=0, to=0.12, by=0.01), lim=c(0,0.12) )
  ggsave(paste(SaveDir, "MBON_by_Thrsh.pdf",sep=""),
         plot = P1a, device='pdf', scale = 1, width =6, height = 3.5, units ="in", dpi = 500, limitsize = TRUE)

  
  
# Loop over different relative weight thresholds and compute the number of direction MBON-->CX targets
Threshes=seq(from=0.001, to=0.2, by=0.001)
Num_of_Cx_Types=data.frame(thresh=numeric(), NumofCxTypes=numeric())
for (ttt in 1:length(Threshes)){
  Temp_All_MB2CX_Direct=All_MB2CX_Direct %>% subset(weightRelative>Threshes[ttt] & weight > 0)
  if (length(Temp_All_MB2CX_Direct$databaseType.from)>0){
    Num_of_Cx_Types[ttt,1]=Threshes[ttt]
    Num_of_Cx_Types[ttt,2]=length(unique(Temp_All_MB2CX_Direct$databaseType.to))
  }
}

P2=ggplot(data=Num_of_Cx_Types, aes(x=thresh, y=NumofCxTypes)) +
  geom_line() + theme_classic() + 
  theme(axis.text.x = element_text(angle = 90)) + scale_x_continuous(breaks = seq(from=0, to=0.12, by=0.01), lim=c(0,0.12) )
  ggsave(paste(SaveDir, "NumOfCxTypes_by_Thrsh.pdf",sep=""),
         plot = P2, device='pdf', scale = 1, width =4, height = 3.5, units ="in", dpi = 500, limitsize = TRUE)
  
  
  
# Make a scatter plot of weight vs relative weight for each connection
P3=ggplot(data=All_MB2CX_Direct, aes(x=weight, y=weightRelative)) + geom_point(size=1, shape=1) +
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(breaks = seq(from=0, to=0.12, by=0.01), lim=c(0,0.12) ) + 
  scale_x_continuous(breaks = seq(from=0, to=150, by=10), lim=c(0,150) )

ggsave(paste(SaveDir, "Thresh_Scatter.pdf",sep=""),
         plot = P3, device='pdf', scale = 1, width =4, height = 3.5, units ="in", dpi = 500, limitsize = TRUE)

  

```



# ####################################################################################################################
# ######### Figure 2: MBON to CX indirect connections ################################################################
# ####################################################################################################################


# Get indirect connections
```{r}


# Get strong connections from MBONs to non-CX neurons
MB2NonCX=subset(Downstream_T2T_L1, !(databaseType.to %in% CXTypes)  & weightRelative>0.01 & weight>10)


# Get type table
L2_Types=sort(unique(MB2NonCX$databaseType.to))
L2_Types=L2_Types[is.na(as.numeric(L2_Types))]
L2_Types=L2_Types[! (startsWith(L2_Types,"(") | startsWith(L2_Types,"Ascending") | startsWith(L2_Types, "MBON"))]
L2_Types_Table=getTypesTable(L2_Types)


# Get second layer lateralized outputs
DownBag_L2=neuronBag(L2_Types_Table, by.roi=TRUE, omitInputs=TRUE, omitOutputs=FALSE)
DownBag_L2=lateralize_types(DownBag_L2) # Lateralize to take into account projections that may be missing from the volume


# Compute weight relative by summing ROIs not in the CX and not on the left side of the brain, which deals with polarity and lateralization issues.
# Polarity, since most FBt types receive a lot of input in the CX, the roi-independent relative weight can be very low.
# Lateralization, since some CX targets could have  dendrites on the left or dendrites on the right or both. So it makes sense to use all MBONs (L and R)
#   and just look at their targets in right ROIs (which should be more complete).
DownBag_L2 <- combineRois(DownBag_L2, outsideRegions, newRoi="NonCX") # Sum synapses across all non-CX ROIs on the right side
           
                       
# Recompute type-to-type table
DownTypes_L2=getTypesTable(unique(c(DownBag_L2$outputs_raw$databaseType.from,
                                    DownBag_L2$outputs_raw$databaseType.to))) %>% lateralize_types()
Downstream_T2T_L2=getTypeToTypeTable(DownBag_L2$outputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0,
                                     singleNeuronThresholdN = 3, pThresh = 1, typesTable = DownTypes_L2, oldTable = NULL) # No t-test type-to-type tables 




```



# Get just indirect connections to the CX and plot
```{r}


# Get first and second layer of projections
L2_to_Cx=subset(Downstream_T2T_L2, databaseType.to %in% CXTypes  & weightRelative>0.01 & weight>10)
L1_to_L2=subset(MB2NonCX, databaseType.to %in% L2_to_Cx$databaseType.from & weightRelative>0.01 & weight>10
                & !startsWith(type.to,"MBON") & !databaseType.from=="MBON15-like")


# Average over left and right 
L2_to_Cx_Ave=L2_to_Cx %>% group_by(databaseType.from, databaseType.to) %>%  
  summarize(weightRelative=mean(weightRelative), outputContribution=mean(outputContribution), weight=mean(weight))
colnames(L2_to_Cx_Ave)=c("type.from","type.to","weightRelative","outputContribution","weight")
L2_to_Cx_Ave$roi="R"


L1_to_L2_Ave=L1_to_L2 %>% group_by(databaseType.from, databaseType.to) %>%  
  summarize(weightRelative=mean(weightRelative), outputContribution=mean(outputContribution), weight=mean(weight)) 
colnames(L1_to_L2_Ave)=c("type.from","type.to","weightRelative","outputContribution","weight")
L1_to_L2_Ave$roi="R"



P2=plotConnectivity(L1_to_L2_Ave, slctROI = NULL, grouping = "type", connectionMeasure = "weightRelative",
  xaxis = c("outputs"), facetInputs = NULL, facetOutputs = NULL, theme = theme_minimal(),
  cmax = NULL, replacementLabels = NULL, orderIn = NULL, orderOut = NULL,
  legendName = NULL, showTable = "inputs")
P2 = P2 +   coord_fixed(ratio = 1) +
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        text = element_text(size=6)) 
print(P2)
ggsave(paste(SaveDir, "L1_to_L2_Ave.Pdf",sep=""),
        plot = P2, device='pdf', scale = 1, width =8, height = 6, units ="in", dpi = 500, limitsize = TRUE)



P2=plotConnectivity(L2_to_Cx_Ave, slctROI = NULL, grouping = "type", connectionMeasure = "weightRelative",
  xaxis = c("outputs"), facetInputs = NULL, facetOutputs = NULL, theme = theme_minimal(),
  cmax = NULL, replacementLabels = NULL, orderIn = NULL, orderOut = NULL,
  legendName = NULL, showTable = "inputs")
P2 = P2 + coord_fixed(ratio = 1) + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        text = element_text(size=6)) 
print(P2)
ggsave(paste(SaveDir, "L2_to_Cx_Ave.Pdf",sep=""),
        plot = P2, device='pdf', scale = 1, width =8, height = 6, units ="in", dpi = 500, limitsize = TRUE)



# Construct pathway object
MBON2CX_Indirect=tableChain2path(L1_to_L2, L2_to_Cx)
MBON2CX_Indirect=subset(MBON2CX_Indirect, !is.na(type_N1) )
MBON2CX_Indirect_Ave=MBON2CX_Indirect %>% group_by(databaseType.from, databaseType.to, databaseType_N1) %>%
  summarize(weightRelative_N1=mean(weightRelative_N1), weightRelative_N2=mean(weightRelative_N2), weightRelative_path=mean(weightRelative_path))


sort(unique(MBON2CX_Indirect_Ave$databaseType.to))


```


# Plot the number of pathways from MBONs to the various FB layers
```{r}

library(prismatic)
library(paletteer)


# Group my projections to FB layer
MBON2CX_Indirect_Ave_FBlayer=subset(MBON2CX_Indirect_Ave, startsWith(databaseType.to,"FB"))
MBON2CX_Indirect_Ave_FBlayer$FBlayer=paste("L", substr(MBON2CX_Indirect_Ave_FBlayer$databaseType.to,3,3), sep="")
MBON2CX_Indirect_Ave_FBlayer=MBON2CX_Indirect_Ave_FBlayer %>% group_by(databaseType.from, FBlayer) %>%
  summarize(NumOfPaths=n(), NumOfFBt=length(unique(databaseType.to)), PathwayWeight=sum(weightRelative_N1*weightRelative_N2))
MBON2CX_Indirect_Ave_FBlayer$FBlayer=factor(MBON2CX_Indirect_Ave_FBlayer$FBlayer, levels=c("L1","L2","L3","L4","L5","L6","L7","L8","L9"))


ggplot(MBON2CX_Indirect_Ave_FBlayer) +
  geom_tile(aes(databaseType.from,FBlayer,fill=NumOfPaths)) + scale_y_discrete(drop=FALSE) +
  scale_fill_paletteer_c("ggthemes::Blue", limits=c(0,15), breaks = c(0,5,10,15), oob=squish, na.value="gray50") +
  theme_classic() + theme(axis.text.x = element_text(angle = 90))  + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA, size = 0.5), #add black border
        panel.spacing = unit(0, "lines"))  + coord_fixed(ratio = 1)

  
ggplot(MBON2CX_Indirect_Ave_FBlayer) +
  geom_tile(aes(databaseType.from,FBlayer,fill=NumOfFBt)) + scale_y_discrete(drop=FALSE) +
  scale_fill_paletteer_c("ggthemes::Blue", limits=c(0,14), breaks = c(0,7,14), oob=squish, na.value="gray50") +
  theme_classic() + theme(axis.text.x = element_text(angle = 90))  + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA, size = 0.5), #add black border
        panel.spacing = unit(0, "lines"))  + coord_fixed(ratio = 1)


ggplot(MBON2CX_Indirect_Ave_FBlayer) +
  geom_tile(aes(databaseType.from,FBlayer,fill=PathwayWeight)) + scale_y_discrete(drop=FALSE) +
  scale_fill_paletteer_c("ggthemes::Blue", limits=c(0,0.05), breaks = c(0,0.025,0.05), oob=squish, na.value="gray50") +
  theme_classic() + theme(axis.text.x = element_text(angle = 90))  + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA, size = 0.5), #add black border
        panel.spacing = unit(0, "lines"))  + coord_fixed(ratio = 1)


```



# Use CD's code from CX_ContextualAnalysisUtils.R to get the MBON info larry provided
```{r}

#source("../CX_ContextualAnalysisUtils.R")

# Read tables of PN to MBON with input modality percentages and return a data frame
getPN2MBONinputTable <- function(){
  PN2MBON_InputPc <- read.csv('C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FIGURE_MB/PN2MBON.csv', header = FALSE)
  PN2ATMBON_InputPc <- read.csv('C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FIGURE_MB/PN2ATMBON.csv', header = FALSE)
  PNtypes <- c('UniGlom', 'MultiGlom', 'ThermoHygro', 'Visual')
  colnames(PN2MBON_InputPc) <- PNtypes
  colnames(PN2ATMBON_InputPc) <- PNtypes
  MBONtypeNames <- c('MBON01', 'MBON02', 'MBON03', 'MBON04', 'MBON05', 'MBON06', 'MBON07', 'MBON09', 'MBON11', 'MBON12', 'MBON13', 'MBON14', 'MBON15', 'MBON16', 'MBON17', 'MBON18', 'MBON19a', 'MBON19b', 'MBON20', 'MBON21', 'MBON22', 'MBON23')
  atypicalMBONtypeNames <- c('MBON10', 'MBON24', 'MBON25', 'MBON26', 'MBON27', 'MBON29', 'MBON30', 'MBON31', 'MBON32', 'MBON33', 'MBON34', 'MBON35', 'MBON28')
  allMBONtypeNames <- c(MBONtypeNames,atypicalMBONtypeNames)
  rownames(PN2MBON_InputPc) <- MBONtypeNames
  rownames(PN2ATMBON_InputPc) <- atypicalMBONtypeNames
  PN2allMBON_InputPct <- rbind(PN2MBON_InputPc,PN2ATMBON_InputPc)
  PN2allMBON_InputPct <- PN2allMBON_InputPct %>% mutate(Olfactory = UniGlom + MultiGlom) # add a column for the sum of UniGlom and MultiGlom as Olfactory
  PN2allMBON_InputPct <- PN2allMBON_InputPct %>% mutate(MBON = allMBONtypeNames) # add a column for matching MBON type names
  
  PN2allMBON_InputPct[[17,"MBON"]] <- "MBON19" # combine the 2 MBON19 types
  PN2allMBON_InputPct[[18,"MBON"]] <- "MBON19"
  
  return(PN2allMBON_InputPct)
}
```



# Make graphs of visual and thermo/hygro indirect pathways
```{r}



PN2allMBON_InputPct=getPN2MBONinputTable()



```





# Make plots of non-FBt pathways
```{r}

NonFBt_Types=sort(unique(MBON2CX_Indirect_Ave$databaseType.to)) 
NonFBt_Types=NonFBt_Types[!startsWith(NonFBt_Types, "FB")]


ExRPaths=subset(MBON2CX_Indirect_Ave, startsWith(databaseType.to,"ExR"))
LalNoPaths=subset(MBON2CX_Indirect_Ave, startsWith(databaseType.to,"LC") | startsWith(databaseType.to,"GLN") | startsWith(databaseType.to,"LNO"))


```


