---
title: "Notebook plotting offsets in connectivity between PB-FB-XX neurons and other columnar neurons"
output:
  html_document:
    df_print: paged
---

### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# The region of interest.
ROI="FB"  

# Directory to save data to.
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save plots to.
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/OffsetConnectivity/"


# Create save/plot directory if they dont exists yet
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}
```


### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}

source("FB_SynapseDistribution_Utils.r")
source("FB_LayerOutline_Utils.r")
source("../InputOutputByTypeUtils.r", chdir = TRUE)
source("../neuprintQueryUtils.r", chdir = TRUE)
source("../visualizeConnectivityTables.r", chdir = TRUE)
library("xlsx")

```


# Load pre-processed data and remove variables that won't be used
```{r}

load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
rm(list=c("roiEigen","Mesh_FB_Points","Mesh_FB_L1_Points", "Mesh_FB_L2_Points","Mesh_FB_L3_Points", "Mesh_FB_L4_Points",
          "Mesh_FB_L5_Points", "Mesh_FB_L6_Points","Mesh_FB_L7_Points", "Mesh_FB_L8_Points", "Mesh_FB_L9_Points","origin"))

```


# Get PB glomeruli and FB columns
```{r}


# Assign side (pb or fb column half)
FBC_SynsAll$Side=NA
FBC_SynsAll$Side[grepl("_R",FBC_SynsAll$bodyname)]<-"R"
FBC_SynsAll$Side[grepl("_L",FBC_SynsAll$bodyname)]<-"L"

# Assign PB glomeruli
FBC_SynsAll$PBglom=NA
RightColumns=str_extract(FBC_SynsAll$bodyname, "_R(\\d+)")
LeftColumns=str_extract(FBC_SynsAll$bodyname, "_L(\\d+)")
FBC_SynsAll$PBglom[which(!is.na(RightColumns))]=RightColumns[which(!is.na(RightColumns))]
FBC_SynsAll$PBglom[which(!is.na(LeftColumns))]=LeftColumns[which(!is.na(LeftColumns))]
FBC_SynsAll$PBglom=sapply(FBC_SynsAll$PBglom, substring, 2, 3)

# Assign FB columns of FX, PFX, and Delta0
FBC_SynsAll$FBcol=NA
FBC_SynsAll$FBcol=str_extract(FBC_SynsAll$bodyname, "_C(\\d+)")
FBC_SynsAll$FBcol=sapply(FBC_SynsAll$FBcol, substring, 2, 3)

# Assign column to Delta6s
Delta6_Temp=subset(FBC_SynsAll, startsWith(bodyname, "Delta6"))[c("bodyid","bodyname","FBcol")]
Delta6_Temp$FBcol=str_extract(Delta6_Temp$bodyname, "_(\\d+)")
Delta6_Temp$FBcol=paste("C",sapply(Delta6_Temp$FBcol, substring, 2, 3),sep="")
Delta6_Temp=distinct(Delta6_Temp)
for (nnn in 1:length(Delta6_Temp$bodyid)){
  FBC_SynsAll$FBcol[FBC_SynsAll$bodyid == Delta6_Temp$bodyid[nnn]]=Delta6_Temp$FBcol[nnn]
}

rm(list=c("LeftColumns","RightColumns","Delta6_Temp"))
```



# Plot connectivity of PB-FB-XX neurons to check for offsets predicted from PB glom to FB col mappings
```{r}


# Get input and output tables
Columnar_Types=unique( FBC_SynsAll$type[ startsWith(FBC_SynsAll$type, "PF" ) | startsWith(FBC_SynsAll$type, "F" ) | startsWith(FBC_SynsAll$type, "Delta" )] )
PFX_Types=unique( FBC_SynsAll$type[startsWith(FBC_SynsAll$type, "PF" )] )
PFX_Bag=buildInputsOutputsByType(PFX_Types, slctROI="FB")
PFX_FB_Outputs_All=PFX_Bag[["outputs_raw"]]
PFX_FB_Inputs_All=PFX_Bag[["inputs_raw"]]


# Subset data on columnar types
PFX_FB_Outputs_All=subset(PFX_FB_Outputs_All, databaseType.to %in% Columnar_Types)
PFX_FB_Inputs_All=subset(PFX_FB_Inputs_All, databaseType.from %in% Columnar_Types)


# Get FB columns and PB glomeruli
Glom_And_Col_From=distinct(FBC_SynsAll[c("bodyid","Side","PBglom","FBcol")])
colnames(Glom_And_Col_From)= c("from","Side.from","PBglom.from","FBcol.from")
Glom_And_Col_To=distinct(FBC_SynsAll[c("bodyid","Side","PBglom","FBcol")])
colnames(Glom_And_Col_To)= c("to","Side.to","PBglom.to","FBcol.to")


# Add column, glomerlus, and side information to inputs/output tables
PFX_FB_Outputs=merge(PFX_FB_Outputs_All, Glom_And_Col_From, by="from", all.x=TRUE)
PFX_FB_Outputs=merge(PFX_FB_Outputs, Glom_And_Col_To, by="to", all.x=TRUE)
PFX_FB_Inputs=merge(PFX_FB_Inputs_All, Glom_And_Col_From, by="from", all.x=TRUE)
PFX_FB_Inputs=merge(PFX_FB_Inputs, Glom_And_Col_To, by="to", all.x=TRUE)


# Order input table
PFX_FB_Inputs$PBglom.to=factor(PFX_FB_Inputs$PBglom.to, levels = rev(c("R9","L1","R8","L2","R7","L3","R6","L4","R5","L5","R4","L6","R3","L7","R2","L8","R1","L9")))
PFX_FB_Inputs$FBcol.from=factor(PFX_FB_Inputs$FBcol.from, levels = rev(c("C14","C13","C12","C11","C10","C9","C8","C7","C6","C5","C4","C3","C2","C1")))
PFX_FB_Inputs$name.from=factor(PFX_FB_Inputs$name.from, levels = unique((PFX_FB_Inputs$name.from)[order(PFX_FB_Inputs$FBcol.from)]) )
PFX_FB_Inputs$name.to=factor(PFX_FB_Inputs$name.to, levels = unique((PFX_FB_Inputs$name.to)[order(PFX_FB_Inputs$FBcol.to)]) )


# Order ouput table
PFX_FB_Outputs$PBglom.from=factor(PFX_FB_Outputs$PBglom.from, levels = rev(c("R9","L1","R8","L2","R7","L3","R6","L4","R5","L5","R4","L6","R3","L7","R2","L8","R1","L9")))
PFX_FB_Outputs$FBcol.to=factor(PFX_FB_Outputs$FBcol.to, levels = rev(c("C14","C13","C12","C11","C10","C9","C8","C7","C6","C5","C4","C3","C2","C1")))
PFX_FB_Outputs$name.to=factor(PFX_FB_Outputs$name.to, levels = unique((PFX_FB_Outputs$name.to)[order(PFX_FB_Outputs$FBcol.to)]) )
PFX_FB_Outputs$name.from=factor(PFX_FB_Outputs$name.from, levels = unique((PFX_FB_Outputs$name.from)[order(PFX_FB_Outputs$FBcol.from)]) )

# Create output folder
PFX_Dir=paste(PlotDir,"PFX_Plots_All","/",sep="")
PFX_Dir_Connectivity=paste(PFX_Dir,"PFX_ConnectivityOffsets","/",sep="")
if (!dir.exists(PFX_Dir)){dir.create(PFX_Dir)}
if (!dir.exists(PFX_Dir_Connectivity)){dir.create(PFX_Dir_Connectivity)}


for (nnn in 1:length(PFX_Types)){
  Temp_Type=PFX_Types[nnn]

    
  # Output table for this neuron
  Temp_OutputTable=subset(PFX_FB_Outputs, databaseType.from == Temp_Type)
  Temp_OutputTable=subset(Temp_OutputTable, type.to %in% Columnar_Types)  

  # Filter output table by neuron types that innervate all columns
  Temp_GoodTypes_Output=Temp_OutputTable %>% group_by(FBcol.to, type.to) %>% summarize(n=n()) %>% group_by(type.to) %>% summarize(NumOfCol=n())
  Temp_GoodTypes_Output=subset(Temp_GoodTypes_Output, NumOfCol==9)
  Temp_OutputTable=subset(Temp_OutputTable, type.to %in% Temp_GoodTypes_Output$type.to & !is.na(FBcol.to) & !is.na(PBglom.from))
  
  # Compute mean by input/output cell type and input PBglom and output FBcol
  Temp_OutputTable_Sum=Temp_OutputTable %>% group_by(type.from, type.to, PBglom.from, FBcol.to) %>% summarise(weight=mean(weight))
  
  # Make output plots  
  if (length(Temp_OutputTable$weight)>0){
   
    # Plot all matrices
    OutputsPlot = plotConnectivityMatrix(Temp_OutputTable_Sum, byGroup = "Glom_to_Col", connectionMeasure = "weight")
    OutputsPlot = OutputsPlot + facet_grid(reorder(type.from, desc(type.from)) ~ type.to, switch="both") + 
      ggtitle(paste("Outputs from ", Temp_Type, " in FB")) +  coord_fixed(ratio = 1) 
    ggsave(paste(PFX_Dir_Connectivity, Temp_Type,"_Outputs_inFB.png",sep=""),
           plot = OutputsPlot, device='png', scale = 1, width = 10, height = 10, units ="in", dpi = 500, limitsize = TRUE)
    
    # Plot matrices one-by-one for each downstream cell type
    Temp_Downstream_Types=unique(Temp_OutputTable_Sum$type.to)
    for (ttt in 1:length(Temp_Downstream_Types)){
      Temp_OutputTable_Sum_Subset=subset(Temp_OutputTable_Sum, type.to == Temp_Downstream_Types[ttt])
      
      OutputsPlot_Sub = plotConnectivityMatrix(Temp_OutputTable_Sum_Subset, byGroup = "Glom_to_Col", connectionMeasure = "weight")
      OutputsPlot_Sub = OutputsPlot_Sub + facet_grid(reorder(type.from, desc(type.from)) ~ type.to, switch="both") + 
        ggtitle(paste("Outputs from ", Temp_Type, " in FB")) +  coord_fixed(ratio = 1) 
      ggsave(paste(PFX_Dir_Connectivity, Temp_Type,"_OutoutTo_", Temp_Downstream_Types[ttt], "_inFB.png",sep=""),
             plot = OutputsPlot_Sub, device='png', scale = 1, width = 4, height = 5, units ="in", dpi = 500, limitsize = TRUE)
    }
    
  }
  
  
  
  # Inpute table for this neuron
  Temp_InputTable=subset(PFX_FB_Inputs, databaseType.to == Temp_Type)
  Temp_InputTable=subset(Temp_InputTable, type.from %in% Columnar_Types) 
  
  # Filter input table by neuron types that innervate all columns
  Temp_GoodTypes_Input=Temp_InputTable %>% group_by(FBcol.from, type.from) %>% summarize(n=n()) %>% group_by(type.from) %>% summarize(NumOfCol=n())
  Temp_GoodTypes_Input=subset(Temp_GoodTypes_Input, NumOfCol==9)
  Temp_InputTable=subset(Temp_InputTable, type.from %in% Temp_GoodTypes_Input$type.from & !is.na(FBcol.from) &  !is.na(PBglom.to))

  # Compute mean by input/output cell type and input PBglom and output FBcol
  Temp_InputTable_Sum=Temp_InputTable %>% group_by(type.from, type.to, PBglom.to, FBcol.from) %>% summarise(weight=mean(weight))
  
  # Make input plots  
  if (length(Temp_InputTable$weight)>0){
    InputsPlot = plotConnectivityMatrix(Temp_InputTable_Sum, byGroup = "Col_to_Glom", connectionMeasure = "weight")
    InputsPlot = InputsPlot + facet_grid(reorder(type.from, desc(type.from)) ~ type.to, switch="both") +
      ggtitle(paste("Inputs to ", Temp_Type, " in FB")) +  coord_fixed(ratio = 1) 
    ggsave(paste(PFX_Dir_Connectivity, Temp_Type,"_Inputs_inFB.png",sep=""),
           plot = InputsPlot, device='png', scale = 1, width = 10, height = 10, units ="in", dpi = 500, limitsize = TRUE)
    
    # Plot matrices one-by-one for each upstream cell type
    Temp_Upstream_Types=unique(Temp_InputTable_Sum$type.from)
    for (ttt in 1:length(Temp_Upstream_Types)){
      Temp_InputTable_Sum_Subset=subset(Temp_InputTable_Sum, type.from == Temp_Upstream_Types[ttt])
      
      InputsPlot_Sub = plotConnectivityMatrix(Temp_InputTable_Sum_Subset, byGroup = "Col_to_Glom", connectionMeasure = "weight")
      InputsPlot_Sub = InputsPlot_Sub + facet_grid(reorder(type.from, desc(type.from)) ~ type.to, switch="both") + 
        ggtitle(paste("Inputs to ", Temp_Type, " in FB")) +  coord_fixed(ratio = 1) 
      ggsave(paste(PFX_Dir_Connectivity, Temp_Type,"_InputFrom_", Temp_Upstream_Types[ttt], "_inFB.png",sep=""),
             plot = InputsPlot_Sub, device='png', scale = 1, width = 7.5, height = 5, units ="in", dpi = 500, limitsize = TRUE)
    }
    
  }
  
}


  
  




```



# Look for lateralized output patterns, where PB-FB-XX neurons from right bridge target neurons that neurons from left bridge do not
```{r}


# Make directory
PFX_Dir_Lat=paste(PFX_Dir,"PFX_Left_VS_Right","/",sep="")
if (!dir.exists(PFX_Dir_Lat)){dir.create(PFX_Dir_Lat)}


# Plot all outputs and look for lateralization
PFX_FB_Outputs_Lat=subset(PFX_FB_Outputs, startsWith(type.to, "Delta" ) & !type.to=="Delta?" & !is.na(PBglom.from))
PFX_FB_Outputs_Lat$to=as.character(PFX_FB_Outputs_Lat$to)
PFX_FB_Outputs_Lat$from=as.character(PFX_FB_Outputs_Lat$from)

# Get upstream and downstream types
UpTypes   = unique(PFX_FB_Outputs_Lat$type.from)
DownTypes = unique(PFX_FB_Outputs_Lat$type.to)

# Get the total number of cells for all upstream and downstream types
Number_of_Ups= subset(NamedBodies, bodytype %in% UpTypes) %>% group_by(bodytype) %>% summarize(N=n())
Number_of_Downs= subset(NamedBodies, bodytype %in% DownTypes) %>% group_by(bodytype) %>% summarize(N=n())


# Loop over all upstream/downstream pairs and plot matricies
for (upup in 1:length(UpTypes)){
  for (downdown in 1:length(DownTypes)){
    
    # Get connectivity matrix from upstream type to downstream type
    Temp_Lat=subset(PFX_FB_Outputs_Lat, type.from == UpTypes[upup] & type.to == DownTypes[downdown] & weight>3) 
    
    if (length(Temp_Lat$to>0)){
      # Get number of upstream/downstream neurons as a percent of the total
      Temp_TotalUps=Number_of_Ups[Number_of_Ups$bodytype == UpTypes[upup],]$N
      Temp_TotalDowns=Number_of_Downs[Number_of_Downs$bodytype == DownTypes[downdown],]$N
      Temp_NowUps=length(unique(subset(Temp_Lat, type.from == UpTypes[upup] )$from))
      Temp_NowDowns=length(unique(subset(Temp_Lat, type.to == DownTypes[downdown] )$to))
      
      # Average by PB glom
      Temp_Lat_Sum=Temp_Lat %>% group_by(PBglom.from, Side.from, to, name.to) %>% summarize(weight = mean(weight))
      
      
      
      if (Temp_NowUps/Temp_TotalUps>0.35 & Temp_NowDowns/Temp_TotalDowns >0.35){
        
        PP <- ggplot(Temp_Lat_Sum) + 
          theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
          scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                               midpoint =0.5*max(Temp_Lat_Sum$weight), limits=c(0,max(Temp_Lat_Sum$weight))) +
          geom_tile(aes(to,PBglom.from,fill=weight)) +
          facet_grid(rows = vars(Side.from), scales="free_y") +
          ggtitle(paste(Temp_Lat$type.from[1]," to ",Temp_Lat$type.to[1],sep=""))
        
        ggsave(paste(PFX_Dir_Lat, Temp_Lat$type.from[1],"_to_",Temp_Lat$type.to[1], "_inFB.png",sep=""),
               plot = PP, device='png', scale = 1, width = 7.5, height = 5, units ="in", dpi = 500, limitsize = TRUE)
      }
    }
  }
}
















```




