---
title: "Notebook plotting connectivity of PB-FB-XX outputs in FB to look for lateralized downstream connections"
output:
  html_document:
    df_print: paged
---


### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
library(dtplyr)
library(neuprintrExtra)
library("xlsx")
library(tidyselect)
library(paletteer)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# Directory to save data to.
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save plots to.
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/Section2/"

# Create save/plot directory if they dont exists yet
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}


```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}

source("FB_SynapseDistribution_Utils.r")
source("FB_LayerOutline_Utils.r")
source("FB_ConnectivityOffsetPlotting_Utils.r")
source("../visualizeConnectivityTables.r", chdir = TRUE)
source("../inputOutputRegionsVis.r")

```


# Get all FB bodies and columnar types
```{r}

NamedBodies=getNeuronsInRoiTable("FB",0)
Columnar_Types=sort(unique( NamedBodies$type[ startsWith(NamedBodies$type, "PF" ) | startsWith(NamedBodies$type, "FR" ) | 
               startsWith(NamedBodies$type, "FS" ) | startsWith(NamedBodies$type, "FC" ) |
               startsWith(NamedBodies$type, "vDelta" ) | startsWith(NamedBodies$type, "hDelta" )] ))

FBBodyCount=NamedBodies %>% group_by(type) %>% summarize(NumofNeurons=n())
FBColumnarBodyCount=subset(FBBodyCount, type %in% Columnar_Types)

```


# Look for lateralized output patterns, where PB-FB-XX neurons of a single neuron type
# target distinct downstream neurons depending on  whether the PB-FB-XX neurons come 
# from the right bridge or left bridge.
```{r}



# Get unique pre-post pairs
Pre_Post=distinct(PFX_FB_Outputs_All[c("type.from","type.to")])


# Make to/from names
PFX_FB_Outputs_All$from_name = paste(PFX_FB_Outputs_All$FBcol.from, PFX_FB_Outputs_All$from, sep="__")
PFX_FB_Outputs_All$to_name   = paste(PFX_FB_Outputs_All$FBcol.to, PFX_FB_Outputs_All$to, sep="__")


# Compute percent input from left and right PB types
Scatter = PFX_FB_Outputs_All %>% group_by(to, Side.from, type.from, type.to) %>% summarise(weightRelative= sum(weightRelative))
Scatter_L=subset(Scatter, Side.from=="L")
colnames(Scatter_L)[colnames(Scatter_L) == "weightRelative"]="weightRelative_L"
Scatter_R=subset(Scatter, Side.from=="R")
colnames(Scatter_R)[colnames(Scatter_R) == "weightRelative"]="weightRelative_R"
Scatter_All=full_join(Scatter_L, Scatter_R, by=c("to", "type.from","type.to"))
Scatter_All$weightRelative_L[is.na(Scatter_All$weightRelative_L)]=0
Scatter_All$weightRelative_R[is.na(Scatter_All$weightRelative_R)]=0
rm(list=c("Scatter","Scatter_L","Scatter_R"))


# Plot every PB-FB-XX to FB columnar type connectivity matrix and look for asymmetric connectivities
ColColors=GetColorMap("FBcol")
ColColors=c(ColColors[1],ColColors)
Delta6Colors <- paletteer_d("Polychrome::dark")
Detlta6Colors = Delta6Colors[c(1,2,3,4,5,6,8,9,11,7,17,18,20,1)]
for (ppp in 1:length(Pre_Post$type.from)){
  print(ppp)
  
  # Subset data and name neurons by column/glom and bodyid
  Temp_PFX_Out=subset(PFX_FB_Outputs_All, type.from == Pre_Post$type.from[ppp] & type.to == Pre_Post$type.to[ppp])
  Temp_Scatter = subset(Scatter_All, type.from == Pre_Post$type.from[ppp] & type.to == Pre_Post$type.to[ppp])
  Temp_Scatter = merge(Temp_Scatter, Temp_PFX_Out[c("to","FBcol.to")], by="to")
  

  # Calculate number of pre and post neurons
  PreNum=length(unique(Temp_PFX_Out$from))
  PostNum=length(unique(Temp_PFX_Out$to))
  PreNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$type == Pre_Post$type.from[ppp]]
  PostNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$type == Pre_Post$type.to[ppp]]
  FBColtoNum=length(unique(Temp_PFX_Out$FBcol.to))

  
  if (FBColtoNum>4 & PreNum/PreNum_All>0.25 & PostNum/PostNum_All >0.25){
    
    if (Temp_PFX_Out$type.from[1] == Temp_PFX_Out$type.to[1]){
      Prefix="Recurrent"
    } else {
      Prefix=""
    }
    
    XXX=unique(Temp_PFX_Out$to_name)
    YYY=unique(Temp_PFX_Out$from_name)
    P1 <- ggplot(Temp_PFX_Out) + 
      theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
      scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                           midpoint =0.5*max(Temp_PFX_Out$weightRelative), limits=c(0,max(Temp_PFX_Out$weightRelative))) +
      geom_tile(aes(to_name,from_name,fill=weightRelative)) + scale_x_discrete(breaks  = XXX, labels = substr(XXX,1,6))  + 
      scale_y_discrete(breaks  = YYY, labels = substr(YYY,1,6))
                    
    
    if (Temp_PFX_Out$type.to[1] %in% PFX_Types){
      P1 = P1 + facet_grid(rows = vars(Side.from), cols=vars(Side.to), scales="free")
    } else {
      P1 = P1 + facet_grid(rows = vars(Side.from), scales="free_y")
    }
    
    P1 = P1 +ggtitle(paste(Temp_PFX_Out$type.from[1], "(", as.character(PreNum), " of ", as.character(PreNum_All), ") to ",
                           Temp_PFX_Out$type.to[1], "(", as.character(PostNum), " of ", as.character(PostNum_All), ") to ", sep=""))
    

     
    if (Temp_PFX_Out$type.to[1] %in% PFX_Types | startsWith(Temp_PFX_Out$type.to[1], "Delta0")){
      Temp_Scatter$FBcol.to=factor(Temp_Scatter$FBcol.to, levels = rev(c("C9","C8","C7","C6","C5","C4","C3","C2","C1","C0")))
    } else if (startsWith(Temp_PFX_Out$type.to[1], "Delta6")) {
      Temp_Scatter$FBcol.to=factor(Temp_Scatter$FBcol.to, levels = rev(c("DC14","DC13","DC12","DC11","DC10","DC09","DC08","DC07","DC06","DC05","DC04","DC03","DC02","DC01")))
    }
    
    P2=ggplot() + geom_point(data=Temp_Scatter, aes(x=weightRelative_L, y=weightRelative_R, color=FBcol.to)) +
      ggtitle(paste(Temp_PFX_Out$type.from[1]," to ",Temp_PFX_Out$type.to[1],sep="")) + theme_bw()
    
    if (Temp_PFX_Out$type.to[1] %in% PFX_Types | startsWith(Temp_PFX_Out$type.to[1], "Delta0")){
      P2 = P2 + scale_color_manual(values=ColColors, drop=FALSE)
    } else if (startsWith(Temp_PFX_Out$type.to[1], "Delta6")) {
      P2 = P2 + scale_color_manual(values=Detlta6Colors, drop=FALSE)
    }
    
    P3=ggarrange(P1,P2,nrow=1, ncol=2)
    
    ggsave(paste(PFX_Dir_Lat, Prefix, Temp_PFX_Out$type.from[1],"_to_",Temp_PFX_Out$type.to[1], "_inFB.png",sep=""),
           plot = P3, device='png', scale = 1, width =15, height = 5, units ="in", dpi = 500, limitsize = TRUE)
    
  }
}









# Make scatter plot of all R vs L weights
pcCols <- paletteer_d("Polychrome::palette36")
PFXs_ThatOutput=unique(PFX_FB_Outputs_All$type.from)
for (ppp in 1:length(PFXs_ThatOutput)){
  
  Scatter_Temp=subset(Scatter_All, type.from==PFXs_ThatOutput[ppp])
  
  
  
  ggplot() + geom_point(data=Scatter_Temp, aes(x=weightRelative_L, y=weightRelative_R, color=type.to)) + 
    scale_color_manual(values=pcCols, drop=FALSE)
  
}


hist(Scatter_All$weightRelative_L-Scatter_All$weightRelative_R,100) +ylim(c(0,200))





# Plot PFNd to PFNd connectivity
Temp_PFX_Out=subset(PFX_FB_Outputs_All, type.from == "PFNd" & type.to == "PFNd" & weightRelative >0.005)
Temp_PFX_Out$from_name = paste(Temp_PFX_Out$PBglom.from, Temp_PFX_Out$from, sep="__")
Temp_PFX_Out$to_name   = paste(Temp_PFX_Out$PBglom.to, Temp_PFX_Out$to, sep="__")
  

PP <- ggplot(Temp_PFX_Out) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.5*max(Temp_PFX_Out$weightRelative), limits=c(0,max(Temp_PFX_Out$weightRelative))) +
  geom_tile(aes(to_name,from_name,fill=weightRelative)) +
  facet_grid(rows = vars(Side.from), cols=vars(Side.to), scales="free") +
  ggtitle(paste(Temp_PFX_Out$type.from[1]," to ",Temp_PFX_Out$type.to[1],sep=""))

ggsave(paste(PFX_Dir_Lat, "Asym_", Temp_PFX_Out$type.from[1],"_to_",Temp_PFX_Out$type.to[1], "_inFB.png",sep=""),
       plot = PP, device='png', scale = 1, width = 7.5, height = 5, units ="in", dpi = 500, limitsize = TRUE)






```