---
title: "Notebook analyzing the dFB sleep-wake circuit, including how it connects to sleep neurons in the EB"
output:
  html_document:
    df_print: paged
---

# Command to clear environment is: rm(list = ls(all.names = TRUE))
# Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
library(dtplyr)
library(neuprintrExtra)
library("xlsx")
library(tidyselect)
library(reshape2)
library(scales)
library(cowplot)
library(paletteer)
library(prismatic)
options(nat.plotengine = 'rgl')
```

# Configurable inputs: choose save/plot directories
```{r}

# Directory to save plots to.
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/Sleep/"
if (!dir.exists(PlotDir)){dir.create(PlotDir)}

```

# Connect to neuprint server.
```{r}
neuprint_login()
```

# Get general functions
```{r}
source("FB_SleepSection_Utils.r")
```

# Get neurons in the dFB sleep-wake circuit
```{r message=FALSE, warning=FALSE}

# Get meta information on all neurons likely to be contained in 23E10 (based on EM-LM matches)
dFB23E10_Types=c("FB7A","FB7K", "FB6A", "FB6C_a", "FB6C_b", "FB6E", "FB6G", "FB6I", "FB6Z")
dFB23E10_MetaAll=getTypesTable(dFB23E10_Types)

# Get meta information on PPL1 dopamine neurons (FB7B and FB6H) with connections to 23E10 neurons
# FB5H is also a PPL1 DAN but does not talk directly with the sleep-wake neurons
dFBdan_Types=c("FB6H","FB7B")
dFBdan_Meta=getTypesTable(dFBdan_Types)

# Neuron types in sleep-wake circuit
SleepWakeTypes=c(dFB23E10_Types,dFBdan_Types)
SleepWakeTypes_Meta=getTypesTable(SleepWakeTypes)

```


# ####################################################################################################################
# ######### Section 1: Connectivity of 23E10 and PPL1 circuit ########################################################
# ####################################################################################################################


# Plot similarity between 23E10 neurons to show that there a multiple distinct types
```{r message=FALSE, warning=FALSE}

# Get all upstream and downstream partners of 23E10 neurons in the FB
dFB23E10_Bag=neuronBag(dFB23E10_MetaAll, slctROI="FB")
dFB23E10_Outputs=dFB23E10_Bag[["outputs_raw"]]
dFB23E10_Inputs=dFB23E10_Bag[["inputs_raw"]]

# Compute input and output connectivity vectors, then concatenate
dFB23E10_Thresh=0.008 # relative weight threshold to binarize connectivity (0.008 is a good)
dFB23E10_Outputs_Vectors= connectivityMatrix(subset(dFB23E10_Outputs, weightRelative>dFB23E10_Thresh),"FB", allToAll=FALSE, from="from",to="to")
dFB23E10_Inputs_Vectors=t(connectivityMatrix(subset(dFB23E10_Inputs,  weightRelative>dFB23E10_Thresh),"FB", allToAll=FALSE, from="from",to="to"))
dFB23E10_Outputs_Vectors=dFB23E10_Outputs_Vectors[order(rownames(dFB23E10_Outputs_Vectors)),]
dFB23E10_Inputs_Vectors=dFB23E10_Inputs_Vectors[order(rownames(dFB23E10_Inputs_Vectors)),]
dFB23E10_InputsOutputs_Vectors=cbind(dFB23E10_Outputs_Vectors, dFB23E10_Inputs_Vectors)

# Compute cosine similarity between the input/output connectivity vectors
dFB23E10_Similarity=Connectivity_VectorsDistance(dFB23E10_InputsOutputs_Vectors, "cosine", dFB23E10_MetaAll)

# Plot cosine similarity 
dFB23E10_Similarity$plotname=paste(dFB23E10_Similarity$type,  as.character(dFB23E10_Similarity$bodyid),sep="__")
dFB23E10_Similarity$plotname2=paste(dFB23E10_Similarity$type2, as.character(dFB23E10_Similarity$bodyid2),sep="__")
dFB23E10_Similarity$type=factor(dFB23E10_Similarity$type, levels=sort(unique(dFB23E10_Similarity$type)))
dFB23E10_Similarity$type2=factor(dFB23E10_Similarity$type2, levels=sort(unique(dFB23E10_Similarity$type2),decreasing = TRUE))

P1=ggplot(dFB23E10_Similarity) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="gray50", high="black", 
                        midpoint=0.5,limits=c(0,1),oob=squish,breaks = c(0,0.5,1)) +
  geom_tile(aes(plotname,plotname2,fill=Similarity))  + 
  facet_grid(rows=vars(type2),cols=vars(type), scales = "free", space = "free") + 
  theme(strip.background = element_blank(), 
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5), 
        panel.spacing = unit(0, "lines"), axis.ticks = element_blank(), aspect.ratio = 1) 
P1
ggsave(paste(PlotDir, "SleepWake_23e10_SimilarityCosine.png",sep=""),
       plot = P1, device='png', scale = 1, width =12, height = 8, units ="in", dpi = 500, limitsize = TRUE)

```


# Look at neuron-to-neuron connectivity of dFB 23E10 and PPL1 dopamine neurons
```{r message=FALSE, warning=FALSE}

# Get upstream and downstream partners of sleep-wake types in FB
SW_Bag=neuronBag(SleepWakeTypes_Meta, slctROI="FB")
SW_N2N_Output=SW_Bag$outputs_raw

# Get neuron-to-neuron connectivity table involving just sleep-wake types, thresholded 0.0005
SleepWake_N2N_InputOutput=subset(SW_N2N_Output, type.to %in% SleepWakeTypes)
SleepWake_N2N_InputOutput=subset(SleepWake_N2N_InputOutput, weightRelative > 0.0005) 

# Plot neuron-to-neuron connectivity matrix
SleepWake_N2N_InputOutput$fromname=paste(SleepWake_N2N_InputOutput$type.from,  as.character(SleepWake_N2N_InputOutput$from),sep="__")
SleepWake_N2N_InputOutput$toname=paste(SleepWake_N2N_InputOutput$type.to, as.character(SleepWake_N2N_InputOutput$to),sep="__")
SleepWake_N2N_InputOutput$type.from=factor(SleepWake_N2N_InputOutput$type.from, levels=sort(unique(SleepWake_N2N_InputOutput$type.from), decreasing=TRUE))
SleepWake_N2N_InputOutput$type.to=factor(SleepWake_N2N_InputOutput$type.to, levels=sort(unique(SleepWake_N2N_InputOutput$type.to)))

P2=ggplot(SleepWake_N2N_InputOutput) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                        midpoint=0.05,limits=c(0,0.1),oob=squish,breaks = c(0,0.05,0.1)) +
  geom_tile(aes(toname,fromname,fill=weightRelative))  + 
  facet_grid(rows=vars(type.from),cols=vars(type.to), scales = "free", space = "free") + 
  theme(strip.background = element_blank(), 
        panel.border = element_rect(colour = "grey50", fill = NA, size = 0.5), 
        panel.spacing = unit(0, "lines"), axis.ticks = element_blank(), aspect.ratio = 1) 
P2
ggsave(paste(PlotDir, "SleepWake_N2N.png",sep=""),
       plot = P2, device='png', scale = 1, width =12, height = 8, units ="in", dpi = 500, limitsize = TRUE)

```


# Now look at type-to-type connectivity of dFB sleep-wake types
```{r message=FALSE, warning=FALSE}

# Compute type-to-type connections without using t-test significance criteria.
# Because many FB tangential types are composed of two neurons, the t-test can occasionally
# filter out strong connetions involving two neurons with variable weights.
SleepWake_T2T_Output=getTypeToTypeTable(SW_N2N_Output, majorOutputThreshold = 0.8, singleNeuronThreshold = 0.0, 
                                        singleNeuronThresholdN = 3, pThresh = 1, typesTable = NULL, oldTable = NULL)
SleepWake_T2T_Output=subset(SleepWake_T2T_Output, type.to %in% SleepWakeTypes & !type.to=="FB07?")

# Group presynaptic 23E10 types by FB layer
SleepWake_T2T_Output$InputGrouping=NA
SleepWake_T2T_Output$InputGrouping[startsWith(SleepWake_T2T_Output$type.from,"FB6")]=6
SleepWake_T2T_Output$InputGrouping[startsWith(SleepWake_T2T_Output$type.from,"FB7")]=7
SleepWake_T2T_Output$InputGrouping=factor(SleepWake_T2T_Output$InputGrouping, levels=c(7,6))

# Divide postsynaptic neurons into groups according to which layer provides their strongest input
OutputGrouping = SleepWake_T2T_Output %>% group_by(type.to) %>% filter(weightRelative == max(weightRelative)) 
OutputGrouping = OutputGrouping[c("type.from","type.to")]                                                                            
OutputGrouping$OutputGrouping=NA
OutputGrouping$OutputGrouping[startsWith(OutputGrouping$type.from,"FB6")]=6
OutputGrouping$OutputGrouping[startsWith(OutputGrouping$type.from,"FB7")]=7
OutputGrouping = OutputGrouping[c("type.to","OutputGrouping")]
SleepWake_T2T_Output=merge(SleepWake_T2T_Output,OutputGrouping, by = "type.to")
SleepWake_T2T_Output$OutputGrouping=factor(SleepWake_T2T_Output$OutputGrouping,levels=c(6,7))

# Plot type-to-type connectivity matrix
P3=ggplot(subset(SleepWake_T2T_Output,weightRelative>0.01)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", midpoint =0.1, limits=c(0,0.2),oob=squish) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) + ggtitle("23E10 Outputs") + 
  facet_grid(rows=vars(InputGrouping), cols=vars(OutputGrouping),scales = "free", space = "free") +
  theme(strip.background = element_blank(), panel.border = element_rect(colour = "grey50", fill = NA), 
        panel.spacing = unit(0, "lines"), aspect.ratio = 1)  
P3
ggsave(paste(PlotDir, "SleepWake_T2T_Sorted.png",sep=""),
         plot = P3, device='png', scale = 1, width =12, height = 5, units ="in", dpi = 500, limitsize = TRUE)

# Plot the same type-to-type connectivity matrix as a network graph
GraphTable=subset(SleepWake_T2T_Output, weightRelative >0.01 & !(type.from == type.to))
P4=Plot_SleepWake_Graph(GraphTable, PlotDir)
P4

```


# ####################################################################################################################
# ######### Section 2: Analysis of upstream/downstream pathways to/from sleep-wake types #############################
# ####################################################################################################################


# Get pathways to and from sleep-wake types that involve at most one intermediate neuron (i.e. 1-hop and 2-hop pathways).
# As mentioend above, this is done without using the t-test significant criteria, which filters out some strong but
# variable FBt connections involving 2-3 neurons.  
```{r message=FALSE, warning=FALSE}

################## Get downstream pathways ################## 

# Get first layer outputs (i.e. those neurons directly downstream of sleep-wake types)
DownBag1=neuronBag(SleepWakeTypes_Meta, by.roi=FALSE, omitInputs=TRUE, omitOutputs=FALSE)
SW_Downstream_Raw1=getTypeToTypeTable(DownBag1$outputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0.01, singleNeuronThresholdN = 3,
                                      pThresh = 1, typesTable = NULL, oldTable = NULL)

# Get second layer outputs (i.e. those neurons two "hops" downstream of sleep-wake types)
DownType1=getTypesTable(unique(SW_Downstream_Raw1$type.to))
DownBag2=neuronBag(DownType1, by.roi=FALSE, omitInputs=TRUE, omitOutputs=FALSE)
SW_Downstream_Raw2=getTypeToTypeTable(DownBag2$outputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0.01, singleNeuronThresholdN = 3,
                                      pThresh = 1, typesTable = NULL, oldTable = NULL)  

# Create pathway objects
SW_Downstream_Raw=list(SW_Downstream_Raw1, SW_Downstream_Raw2)
SW_Downstream=tableChain2path(SW_Downstream_Raw)
remove(DownBag1, SW_Downstream_Raw1, DownType1, DownBag2, SW_Downstream_Raw2, SW_Downstream_Raw)

################## Get upstream pathways ##################

# Get first layer inputs (i.e. those neurons directly upstream of sleep-wake types)
UpBag1=neuronBag(SleepWakeTypes_Meta, by.roi=FALSE, omitInputs=FALSE, omitOutputs=TRUE)
SW_Upstream_Raw1=getTypeToTypeTable(UpBag1$inputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0.01, singleNeuronThresholdN = 3,
                                    pThresh = 1, typesTable = NULL, oldTable = NULL)

# Get second layer inputs (i.e. those neurons two "hops" upstream of sleep-wake types)
UpType1=getTypesTable(unique(SW_Upstream_Raw1$type.from))
UpBag2=neuronBag(UpType1, by.roi=FALSE, omitInputs=FALSE, omitOutputs=TRUE)
SW_Upstream_Raw2=getTypeToTypeTable(UpBag2$inputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0.01, singleNeuronThresholdN = 3,
                                    pThresh = 1, typesTable = NULL, oldTable = NULL)  

# Get pathway objects
SW_Upstream_Raw=list(SW_Upstream_Raw1, SW_Upstream_Raw2)
SW_Upstream=tableChain2path(SW_Upstream_Raw)
SW_Upstream=subset(SW_Upstream, databaseType.to %in% SleepWakeTypes_Meta$type)
remove(UpBag1, SW_Upstream_Raw1, UpType1, UpBag2, SW_Upstream_Raw2, SW_Upstream_Raw)

```


# Pick a pathway weight threshold for input and output pathways (0.005 for figures)
```{r message=FALSE, warning=FALSE}
PathwayThresh=0.005
```


# Plot pathways downstream of sleep-wake types.
# Note that some downstream types belong to Unknown Types (i.e. neurons not assigned types yet).
# Future databse versions may assign names to these bodies, in which case, they can be grouped into new SuperTypes.
```{r message=FALSE, warning=FALSE}

# Plot 1-step pathways
UnknownDownTypes=Plot_DownStream_Pathways(SW_Downstream, PathwayThresh, 1, PlotDir)

# Plot 2-step pathways
UnknownDownTypes=Plot_DownStream_Pathways(SW_Downstream, PathwayThresh, 2, PlotDir)

```


# Plot pathways upstream of sleep-wake types.
# Note that some upstream types belong to Unknown Types (i.e. neurons not assigned types yet).
# Future databse versions may assign names to these bodies, in which case, they can be grouped into new SuperTypes.
```{r message=FALSE, warning=FALSE}

# Plot 1-step upstream pathways
UnknownUpTypes=Plot_UpStream_Pathways(SW_Upstream, PathwayThresh, 1, PlotDir)

# Plot 2-step upstream pathways
UnknownUpTypes=Plot_UpStream_Pathways(SW_Upstream, PathwayThresh, 2, PlotDir)
  
```


# ####################################################################################################################
# ######### Section 3: Make network graph of core sleep circuit ######################################################
# ####################################################################################################################


# Get connections among a group of hand-picked neuron types known to be involved in sleep-wake control along with
# some neuron types that are strongly connected to known sleep-wake types (e.g. PFGs) or those that participate in
# in direct connetions from EB to FB (e.g. hDeltaK). This plot is meant to illustrator possible EB-FB sleep-wake
# pathways but does not include all connetions of each sleep-wake type or those that may also be involved (e.g ER5->EL).
```{r}

# Define core sleep pathway types connecting EB to FB
SleepWakeTypes_EbFb=c("FB6A","PFGs","hDeltaK","hDeltaF","ExR3","ExR1","ER5",
                      "PEN_b(PEN2)","ER3d_a","ER3d_b","ER3d_c","ER3d_d","FB8B",
                      "hDeltaD","FB7A","FB7B","FB7K", "FB6H", "OA-VPM3")
SleepWakeTypes_EbFb_Table=getTypesTable(SleepWakeTypes_EbFb)

# Get connection table just between these types (thresholded at 0.01 relative weight)
SW_EbFb_Bag=neuronBag(SleepWakeTypes_EbFb_Table, by.roi=TRUE)
SW_EbFb_N2N=SW_EbFb_Bag$inputs_raw
SW_EbFb_N2N_Sub=subset(SW_EbFb_N2N, type.to %in% SleepWakeTypes_EbFb & type.from %in% SleepWakeTypes_EbFb)
SW_EbFb_N2N_Sub=subset(SW_EbFb_N2N_Sub, weightRelative > 0.01)

# Compute type-to-type connectivity (without t-test significance criteria, as explained above)
SW_EbFb_T2T=getTypeToTypeTable(SW_EbFb_Bag$inputs_raw, majorOutputThreshold = 0.8, singleNeuronThreshold = 0.01, singleNeuronThresholdN = 3,
                                      pThresh = 1, typesTable = NULL, oldTable = NULL)
SW_EbFb_T2T_Sub=subset(SW_EbFb_T2T, type.to %in% SleepWakeTypes_EbFb & type.from %in% SleepWakeTypes_EbFb)
SW_EbFb_T2T_Sub=subset(SW_EbFb_T2T_Sub, weightRelative>0.01)


```


# Make network of EB-FB sleep-wake network
```{r}

Plot_EbFb_SleepWake_Graph(SW_EbFb_T2T_Sub, PlotDir)
 
```

