---
title: "Notebook analyzing FB sleep circuit"
output:
  html_document:
    df_print: paged
---


### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
library(dtplyr)
library(neuprintrExtra)
library("xlsx")
library(tidyselect)
library(reshape2)
library(scales)
library(cowplot)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose save/plot directories
```{r}

# Directory to save data to.
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save plots to.
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/Sleep/Plots/"

# Create save/plot directory if they dont exists yet
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}


```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}

source("FB_SynapseDistribution_Utils.r")
source("FB_LayerOutline_Utils.r")
source("FB_ConnectivityOffsetPlotting_Utils.r")
source("../visualizeConnectivityTables.r", chdir = TRUE)
source("../inputOutputRegionsVis.r")
source("../R/connectivityMatricesTools.R")

```


# Get all FB bodies and columnar types
```{r}

NamedBodies=getNeuronsInRoiTable("FB",0)
NamedBodies_Meta=neuprint_get_meta(NamedBodies$bodyid)
Columnar_Types=sort(unique( NamedBodies$type[ startsWith(NamedBodies$type, "PF" ) | startsWith(NamedBodies$type, "FR" ) | 
               startsWith(NamedBodies$type, "FS" ) | startsWith(NamedBodies$type, "FC" ) |
               startsWith(NamedBodies$type, "vDelta" ) | startsWith(NamedBodies$type, "hDelta" )] ))
Tangential_Types=sort(unique( NamedBodies$type[ startsWith(NamedBodies$type, "FB" ) |
                                                  startsWith(NamedBodies$type, "ExR") | startsWith(NamedBodies$type, "OA")]))
FBBodyCount=NamedBodies %>% group_by(type) %>% summarize(NumofNeurons=n())
FBColumnarBodyCount=subset(FBBodyCount, type %in% Columnar_Types)

```


# Get neurons of interest: the cell types in 23E10 and the two dFB PPL1 DANs
```{r}

# Bodyids of neurons with 23E10-like morphologies (including FB7B and FB6H, the putative dopamine neurons). Important to keep
# bodyid information in case names change in the future.
dFB23E10_Like=c(294800293,  297183251,  327203386,  327730878,  329289084,  420842989,  422191200,  422876942,  452029745,  513788774,
           762222901,  915960391,  915964590,  916288456,  916292026,  946308203,  946641212,  946645313,  946978006,  979065964,
           1105955480, 5813019588, 5813020684, 5813020735, 5813026514, 5813049824, 5813050747, 5813055834, 5813057169, 5813058367,
           5813058368, 5813061177, 5813061495, 5813069331, 5813071027, 5813071028, 5813081818, 948346463, 5813020698)
dFB23E10_Like_Meta=neuprint_get_meta(dFB23E10_Like)


# FB7B (1 neuron per hemisphere) and FB6H (1 neurons per hemisphere) are the best candidates 
# for dFB PPL1 dopamine neurons, and also have a 23E10-like anatomy. 
dFBdan_Types=c("FB6H","FB7B")
dFBdan=c(5813020698, 948346463, 915960391, 5813020684) 
dFBdan_Meta=neuprint_get_meta(dFBdan)


# Include only the nine cell types found in 23E10
dFB23E10_Types=c("FB7A","FB7K", "FB6A", "FB6C_a", "FB6C_b", "FB6E", "FB6G", "FB6I", "FB6Z")
dFB23E10_Meta=subset(dFB23E10_Like_Meta, type %in% dFB23E10_Types)
dFB23E10_MetaAll=subset(NamedBodies, type %in% dFB23E10_Types) # Get meta data for all 23E10-like types to make sure there are 39 neurons.

# Cell types in sleep/wake circuit
SleepWakeAllTypes=c(dFB23E10_Types,dFBdan_Types)


# Circadian neurons
DN1=neuprint_search(".*DN1.*")


```


# ####################################################################################################################
# ######### Figure 1: Plot of 23E10 and PPL1 circuit #################################################################
# ####################################################################################################################


# Function for computing distance and returning data frame for plotting
```{r}

# Compute distance or correlation matrices on a connetivity table matrix
Connectivity_VectorsDistance <- function(connectTable_Vectors, Method, MetaNames){
  
  # Compute similarity matrix
  if (Method=='binary'){
     Sim=1-bin_dist(connectTable_Vectors,0)
  } else if (Method=='cosine') {
     Sim = 1-cos_dist(connectTable_Vectors)
  } 

  # Convert to data frame
  Sim <- as.matrix(Sim)
  Sim=melt(Sim)
  colnames(Sim) <- c("bodyid", "bodyid2", "Similarity")
  
  # Assign names
  Names=distinct(MetaNames[c("bodyid","name","type")])
  Sim=inner_join(Sim,Names, by="bodyid")
  colnames(Names)=c("bodyid2","name2","type2")
  Sim=inner_join(Sim,Names, by="bodyid2")
  return(Sim)
}


```



# Plot similarity between 23E10 types, to show that there a multiple distinct types
```{r}


# Get upstream and downstream partners of 23E10 neurons
dFB23E10_Bag=create_neuronBag(dFB23E10_Meta, slctROI="FB")
dFB23E10_Outputs=dFB23E10_Bag[["outputs_raw"]]
dFB23E10_Inputs=dFB23E10_Bag[["inputs_raw"]]


# Compute input and output vectors, then concatenate
dFB23E10_Thresh=0.008 #0.008 good threshold
#dFB23E10_Outputs$from=as.character(dFB23E10_Outputs$from)
#dFB23E10_Outputs$to=as.character(dFB23E10_Outputs$to)
dFB23E10_Outputs_Vectors= connectivityMatrix(subset(dFB23E10_Outputs, weightRelative>dFB23E10_Thresh),"FB", allToAll=FALSE, from="from",to="to")
dFB23E10_Inputs_Vectors=t(connectivityMatrix(subset(dFB23E10_Inputs,  weightRelative>dFB23E10_Thresh),"FB", allToAll=FALSE, from="from",to="to"))
dFB23E10_Outputs_Vectors=dFB23E10_Outputs_Vectors[order(rownames(dFB23E10_Outputs_Vectors)),]
dFB23E10_Inputs_Vectors=dFB23E10_Inputs_Vectors[order(rownames(dFB23E10_Inputs_Vectors)),]
dFB23E10_InputsOutputs_Vectors=cbind(dFB23E10_Outputs_Vectors, dFB23E10_Inputs_Vectors)


# Compute cosine distance
MetaNames=dFB23E10_Meta[c("bodyid","name","type")]
dFB23E10_Distance=Connectivity_VectorsDistance(dFB23E10_InputsOutputs_Vectors, "cosine", MetaNames)


# Plot similarity
dFB23E10_Distance$plotname=paste(dFB23E10_Distance$type,  as.character(dFB23E10_Distance$bodyid),sep="__")
dFB23E10_Distance$plotname2=paste(dFB23E10_Distance$type2, as.character(dFB23E10_Distance$bodyid2),sep="__")
dFB23E10_Distance$bodyid=as.character(dFB23E10_Distance$bodyid)
dFB23E10_Distance$bodyid2=as.character(dFB23E10_Distance$bodyid2)
dFB23E10_Distance$type=factor(dFB23E10_Distance$type, levels=sort(unique(dFB23E10_Distance$type)))
dFB23E10_Distance$type2=factor(dFB23E10_Distance$type2, levels=sort(unique(dFB23E10_Distance$type2),decreasing = TRUE))


P1=ggplot(dFB23E10_Distance) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="white", mid="gray50", high="black", 
                        midpoint=0.5,limits=c(0,1),oob=squish,breaks = c(0,0.5,1)) +
  geom_tile(aes(plotname,plotname2,fill=Similarity))  + 
  facet_grid(rows=vars(type2),cols=vars(type), scales = "free", space = "free") + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        axis.ticks = element_blank(),
        aspect.ratio = 1) 
 ggsave(paste(PlotDir, "FIGURE_", "23e10_SimilarityCosine.pdf",sep=""),
         plot = P1, device='pdf', scale = 1, width =12, height = 8, units ="in", dpi = 500, limitsize = TRUE)


```


# Get connectivity bag of entire FB
```{r}

# Get upstream and downstream partners of all FB neurons
FB_Bag=create_neuronBag(NamedBodies_Meta, slctROI="FB")
FB_T2T_Output=FB_Bag$outputs
FB_N2N_Output=FB_Bag$outputs_raw

```


# look at neuron-to-neuron connectivity of dFB 23E10 and PPL1 dopamine neurons
```{r}


# Get type-to-type table and subset on 23E10-like neurons and their upstream/downstream connections
SleepWake_N2N_InputOutput=subset(FB_N2N_Output, type.from %in% SleepWakeTypes & type.to %in% SleepWakeTypes)
SleepWake_N2N_InputOutput=subset(SleepWake_N2N_InputOutput, weightRelative > 0.0005) #0.0005

# Plot matrix
SleepWake_N2N_InputOutput$fromname=paste(SleepWake_N2N_InputOutput$type.from,  as.character(SleepWake_N2N_InputOutput$from),sep="__")
SleepWake_N2N_InputOutput$toname=paste(SleepWake_N2N_InputOutput$type.to, as.character(SleepWake_N2N_InputOutput$to),sep="__")
SleepWake_N2N_InputOutput$type.from=factor(SleepWake_N2N_InputOutput$type.from, levels=sort(unique(SleepWake_N2N_InputOutput$type.from), decreasing=TRUE))
SleepWake_N2N_InputOutput$type.to=factor(SleepWake_N2N_InputOutput$type.to, levels=sort(unique(SleepWake_N2N_InputOutput$type.to)))


P1=ggplot(SleepWake_N2N_InputOutput) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                        midpoint=0.05,limits=c(0,0.1),oob=squish,breaks = c(0,0.05,0.1)) +
  geom_tile(aes(toname,fromname,fill=weightRelative))  + 
  facet_grid(rows=vars(type.from),cols=vars(type.to), scales = "free", space = "free") + 
  theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA, size = 0.5), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        axis.ticks = element_blank(),
        aspect.ratio = 1) 
 ggsave(paste(PlotDir, "FIGURE_", "SleepWake_N2N.pdf",sep=""),
         plot = P1, device='pdf', scale = 1, width =12, height = 8, units ="in", dpi = 500, limitsize = TRUE)



```


# Now look at type-to-type connectivity of dFB 23E10 and PPL1 dopamine neurons
```{r}


# Get type-to-type table and subset on 23E10-like neurons and their upstream/downstream connections
SleepWake_T2T_Output=subset(FB_T2T_Output, type.from %in% SleepWakeTypes & type.to %in% SleepWakeTypes & !type.to=="FB07?")


# Group presynaptic 23E10 types by FB layer
SleepWake_T2T_Output$InputGrouping=NA
SleepWake_T2T_Output$InputGrouping[startsWith(SleepWake_T2T_Output$type.from,"FB6")]=6
SleepWake_T2T_Output$InputGrouping[startsWith(SleepWake_T2T_Output$type.from,"FB7")]=7
SleepWake_T2T_Output$InputGrouping=factor(SleepWake_T2T_Output$InputGrouping, levels=c(7,6))


# Divide postsynaptic neurons into groups targetted by layer 6 or layer 7 neurons
OutputGrouping = SleepWake_T2T_Output %>% group_by(type.to) %>% filter(weightRelative == max(weightRelative)) 
OutputGrouping = OutputGrouping[c("type.from","type.to")]                                                                            
OutputGrouping$OutputGrouping=NA
OutputGrouping$OutputGrouping[startsWith(OutputGrouping$type.from,"FB6")]=6
OutputGrouping$OutputGrouping[startsWith(OutputGrouping$type.from,"FB7")]=7
OutputGrouping = OutputGrouping[c("type.to","OutputGrouping")]
SleepWake_T2T_Output=merge(SleepWake_T2T_Output,OutputGrouping, by = "type.to")
SleepWake_T2T_Output$OutputGrouping=factor(SleepWake_T2T_Output$OutputGrouping,levels=c(6,7))


# Make plot of sorted 23E10 output matrix
P2b=ggplot(subset(SleepWake_T2T_Output,weightRelative>0.01)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.1, limits=c(0,0.2),oob=squish) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) + ggtitle("23E10 Outputs") + 
  facet_grid(rows=vars(InputGrouping), cols=vars(OutputGrouping),scales = "free", space = "free") +
   theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        #axis.ticks = element_blank(),
        aspect.ratio = 1)  
ggsave(paste(PlotDir, "23e10_TypeToType_Outputs_Sorted.pdf",sep=""),
         plot = P2b, device='pdf', scale = 1, width =12, height = 5, units ="in", dpi = 500, limitsize = TRUE)



```


# Make graph of type-to-type sleep-wake network
```{r}

# Load libraries
require(visNetwork, quietly = TRUE)
library(paletteer)

# Get input data
GraphTable=SleepWake_T2T_Output

# remove self connections
GraphTable=subset(GraphTable, !(type.from == type.to) )


# Set node node
IDs_Type=sort(unique(c(unique(GraphTable$type.from),unique(GraphTable$type.to))))
NODES=data.frame(name=IDs_Type)


# Set node positions
NODES$name=NODES$name[c(1,3,7,4,8,2,5,9,11,6,10)]
NODES$angle=NA
NODES$x=NA
NODES$y=NA

Diff=pi/(4)
NODES$angle[c(1,2,3,4,5)]=seq(from = 0, to = pi , by = Diff)
NODES$x=cos(NODES$angle)*200
NODES$y=sin(NODES$angle)*100

NODES$x[6]=-125
NODES$y[6]=0

NODES$x[7]=125
NODES$y[7]=0

NODES$x[8]=0
NODES$y[8]=-200/1.2

NODES$x[9]=100
NODES$y[9]=-300/1.3

NODES$x[10]=0
NODES$y[10]=-100/1.2

NODES$x[11]=-100
NODES$y[11]=-300/1.3

# NODES
NODES$y=-NODES$y
NODES$COLORZ="dodgerblue3"
NODES$COLORZ[NODES$name == "FB6H" | NODES$name == "FB7B"]="magenta3"

# edges
EDGES=GraphTable[c("type.from","type.to","weightRelative")]

# Threshold
EDGES=subset(EDGES,weightRelative >0.01)

# edges
colnames(EDGES)=c("from","to","weight")
EDGES$from=as.character(EDGES$from)
EDGES$to=as.character(EDGES$to)
EDGES$COLORZ="Sleep to Sleep"
EDGES$COLORZ[EDGES$from == "FB6H" | EDGES$from == "FB7B"]="Wake to sleep"
EDGES$COLORZ[EDGES$to   == "FB6H" | EDGES$to   == "FB7B"]="Sleep to Wake"
EDGES$COLORZ=factor(EDGES$COLORZ,levels=c("Sleep to Wake", "Wake to sleep", "Sleep to Sleep"))


# Make ggraph object
graph = tbl_graph(NODES, EDGES)

# colors
pcCols <- paletteer_d("Polychrome::palette36")
col_vector=c(pcCols[15],pcCols[13],"gray50")

# Make plot and save
P1=ggraph(graph,layout="manual",x=NODES$x,y=NODES$y) + 
  geom_edge_fan( aes(width=weight, color=COLORZ), 
                 arrow = arrow(length = unit(2, 'mm'),ends = "last", type = "closed"), end_cap = circle(1, 'cm'), alpha=1,strength=1) +
  geom_node_point(color=NODES$COLORZ, size=20) +
  geom_node_text(aes(label=name),angle=0,size=2, nudge_y = c(rep(0.06,18),rep(-0.06,9)), color='black' ) +
  theme_classic() + 
  theme(legend.text=element_text(size=6),legend.title=element_text(size=6),
        axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),axis.title.y=element_blank()) +
  scale_edge_width(range = c(0.5,2)) + scale_edge_color_manual(values=col_vector)
ggsave(paste(PlotDir, "FIGURE_SleepWake_N2N_Graph.pdf",sep=""), plot = P1, device='pdf', scale = 1, width = 8.2, height = 8, units ="in", dpi = 500, limitsize = TRUE)


```



# ####################################################################################################################
# ######### Figure 2: Plot of upstream/downstream of 23E10 and PPL1 circuit ##########################################
# ####################################################################################################################




# Now look at upstream and downstream connections of 23E10 and PPL1 neurons
```{r}


# Get type-to-type table and subset on 23E10-like neurons and their upstream/downstream connections
SleepWakeAll_T2T_InputOutput=subset(FB_T2T_Output, type.from %in% SleepWakeTypes | type.to %in% SleepWakeTypes)
SleepWakeAll_T2T_Input=subset(SleepWakeAll_T2T_InputOutput, type.to %in% SleepWakeTypes)
SleepWakeAll_T2T_Output=subset(SleepWakeAll_T2T_InputOutput, type.from %in% SleepWakeTypes & !type.to=="FB07?")


###################################### Plots of 23E10 Inputs ###################################################

# Plot and save un-sorted type-to-type connectivity matrices for 23E10 inputs
P1=ggplot(subset(SleepWakeAll_T2T_Input,weightRelative>0.01)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.15, limits=c(0,0.3),oob=squish) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) + ggtitle("23E10 Inputs")
ggsave(paste(PlotDir, "23e10_TypeToType_Inputs.png",sep=""),
         plot = P1, device='png', scale = 1, width =8, height = 10, units ="in", dpi = 500, limitsize = TRUE)

# Divide presynaptic neurons into groups that target FB layer 6 and those that target layer 7
InputGrouping = SleepWakeAll_T2T_Input %>% group_by(type.from) %>% filter(weightRelative == max(weightRelative)) 
InputGrouping = InputGrouping[c("type.from","type.to")]                                                                            
InputGrouping$InputGrouping=NA
InputGrouping$InputGrouping[startsWith(InputGrouping$type.to,"FB6")]=6
InputGrouping$InputGrouping[startsWith(InputGrouping$type.to,"FB7")]=7
InputGrouping = InputGrouping[c("type.from","InputGrouping")]
SleepWakeAll_T2T_Input=merge(SleepWakeAll_T2T_Input,InputGrouping, by = "type.from")
SleepWakeAll_T2T_Input$InputGrouping=factor(SleepWakeAll_T2T_Input$InputGrouping,levels=c(7,6))

# Group postsynaptic 23E10 types by FB layer
SleepWakeAll_T2T_Input$OutputGrouping=NA
SleepWakeAll_T2T_Input$OutputGrouping[startsWith(SleepWakeAll_T2T_Input$type.to,"FB6")]=6
SleepWakeAll_T2T_Input$OutputGrouping[startsWith(SleepWakeAll_T2T_Input$type.to,"FB7")]=7
SleepWakeAll_T2T_Input$OutputGrouping=factor(SleepWakeAll_T2T_Input$OutputGrouping, levels=c(7,6))

# Make plot with sorted 23E10 input matrix (NEED TO FIX)
P1b=ggplot(subset(SleepWakeAll_T2T_Input,weightRelative>0.01)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.1, limits=c(0,0.2),oob=squish) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) + ggtitle("23E10 Inputs") + 
  facet_grid(rows=vars(InputGrouping), cols=vars(OutputGrouping),scales = "free", space = "free") +
   theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "black", fill = NA), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        #axis.ticks = element_blank(),
        aspect.ratio = 1)  
ggsave(paste(PlotDir, "SleepWake_InputsAll_Sorted.pdf",sep=""),
         plot = P1b, device='pdf', scale = 1, width =8, height = 10, units ="in", dpi = 500, limitsize = TRUE)




###################################### Plots of 23E10 Outputs ###################################################


# Plot and save un-sorted type-to-type connectivity matrices for 23E10 outputs
P2=ggplot(subset(SleepWakeAll_T2T_Output,weightRelative>0.01)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.1, limits=c(0,0.2),oob=squish) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) + ggtitle("23E10 Outputs")
ggsave(paste(PlotDir, "23e10_TypeToType_Outputs.png",sep=""),
         plot = P2, device='png', scale = 1, width =12, height = 5, units ="in", dpi = 500, limitsize = TRUE)


# Group presynaptic 23E10 types by FB layer
SleepWakeAll_T2T_Output$InputGrouping=NA
SleepWakeAll_T2T_Output$InputGrouping[startsWith(SleepWakeAll_T2T_Output$type.from,"FB6")]=6
SleepWakeAll_T2T_Output$InputGrouping[startsWith(SleepWakeAll_T2T_Output$type.from,"FB7")]=7
SleepWakeAll_T2T_Output$InputGrouping=factor(SleepWakeAll_T2T_Output$InputGrouping, levels=c(7,6))


# Divide postsynaptic neurons into groups targetted by layer 6 or layer 7 neurons
OutputGrouping = SleepWakeAll_T2T_Output %>% group_by(type.to) %>% filter(weightRelative == max(weightRelative)) 
OutputGrouping = OutputGrouping[c("type.from","type.to")]                                                                            
OutputGrouping$OutputGrouping=NA
OutputGrouping$OutputGrouping[startsWith(OutputGrouping$type.from,"FB6")]=6
OutputGrouping$OutputGrouping[startsWith(OutputGrouping$type.from,"FB7")]=7
OutputGrouping = OutputGrouping[c("type.to","OutputGrouping")]
SleepWakeAll_T2T_Output=merge(SleepWakeAll_T2T_Output,OutputGrouping, by = "type.to")
SleepWakeAll_T2T_Output$OutputGrouping=factor(SleepWakeAll_T2T_Output$OutputGrouping,levels=c(6,7))


# Make plot of sorted 23E10 output matrix
P2b=ggplot(subset(SleepWakeAll_T2T_Output,weightRelative>0.01)) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.1, limits=c(0,0.2),oob=squish) +
  geom_tile(aes(type.to,type.from,fill=weightRelative)) + ggtitle("23E10 Outputs") + 
  facet_grid(rows=vars(InputGrouping), cols=vars(OutputGrouping),scales = "free", space = "free") +
   theme(strip.background = element_blank(), #remove background for facet labels
        panel.border = element_rect(colour = "grey50", fill = NA), #add black border
        panel.spacing = unit(0, "lines"),#remove space between facets
        #axis.ticks = element_blank(),
        aspect.ratio = 1)  
ggsave(paste(PlotDir, "SleepWake_OutputsAll_Sorted.pdf",sep=""),
         plot = P2b, device='pdf', scale = 1, width =12, height = 5, units ="in", dpi = 500, limitsize = TRUE)




```



# Try some pathway tracing out of dFB sleep/wake circuit
```{r include=FALSE}



#Start=neuprint_search("FB6A.*")
Start=subset(NamedBodies, type %in% SleepWakeTypes)
Steps=3

# Trace downstream pathways
CurrentLayer=Start
for (nnn in 1:Steps){
  print(nnn)
  bag <- create_neuronBag(CurrentLayer,by.roi=FALSE,omitInputs=TRUE,selfRef=FALSE)  
  Out=bag$outputs
  Out$Step=nnn
  
  Out=subset(Out,weightRelative >0.005)
  Out=subset(Out, grepl("\\D", Out$type.to))
  Out=subset(Out, !(type.to %in% Out$type.from)) # no within-layer connections

  if (nnn==1){
    Pathway=Out
  } else {
    Out=subset(Out, !(type.to %in% Pathway$type.from) ) # no backward connections
    Pathway=rbind(Pathway,Out)
  }
  
  TempBodies=subset(bag$outputs_raw, type.to %in% Out$type.to)
  CurrentLayer=neuprint_get_meta(unique(TempBodies$to))
}


```


```{r include=FALSE}


Graph=subset(Pathway,Step<3)
Graph=subset(Graph, outputContribution >0)

A=unique(c(Graph$type.from, Graph$type.to))
Exclude=c("FB07?","TuBu")

Graph=subset(Graph,!(type.to %in% Exclude | type.from %in% Exclude))
Graph=subset(Graph, (startsWith(type.to,"E") & Step ==2) | Step==1)


# Set node layers
A=distinct(Graph[c("type.from","Step")])
A2=distinct(Graph[c("type.to","Step")])
A2=subset(A2, !type.to %in% A$type.from)
A2$Step=A2$Step+1
colnames(A)=c("name","Step")
colnames(A2)=c("name","Step")
NODES=rbind(A,A2)

NODES=NODES[order(NODES$name),]


NODES$x=NA
NODES$y=NA

#
l1nodes=sum(NODES$Step==1)
NODES$x[NODES$Step==1]=0
NODES$y[NODES$Step==1]=seq(from=-l1nodes/2,l1nodes/2,by=1)*1500

l2nodes=sum(NODES$Step==2)
NODES$x[NODES$Step==2]=40
NODES$y[NODES$Step==2]=seq(from=-l2nodes/2,l2nodes/2,by=1)*500

l3nodes=sum(NODES$Step==3)
NODES$x[NODES$Step==3]=80
NODES$y[NODES$Step==3]=seq(from=-l3nodes/2,l3nodes/2-1,by=1)*500

#l4nodes=sum(NODES$Step==4)
#NODES$x[NODES$Step==4]=160
#NODES$y[NODES$Step==4]=seq(from=-l4nodes/2,l4nodes/2-1,by=1)*500


# edges
EDGES=Graph[c("type.from","type.to","outputContribution")]


# edges
colnames(EDGES)=c("from","to","weight")
EDGES$from=as.character(EDGES$from)
EDGES$to=as.character(EDGES$to)


# Make ggraph object
plotgraph = tbl_graph(NODES, EDGES)




# Make plot and save
P1=ggraph(plotgraph,layout="manual",x=NODES$x,y=NODES$y) + 
  geom_edge_fan( aes(width=weight,colour=EDGES$from), 
                 arrow = arrow(length = unit(2, 'mm'),ends = "last", type = "closed"), end_cap = circle(0, 'cm'), alpha=1,strength=1) +
  geom_node_point(size=1) +
  geom_node_text(aes(label=name),angle=0,size=2, nudge_x = 3, color='red' ) +
  theme_classic() + 
  theme(legend.text=element_text(size=6),legend.title=element_text(size=6),
        axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),axis.title.y=element_blank()) +
  scale_edge_width(range = c(0,1)) + scale_edge_color_hue(guide='none')

ggsave(paste(PlotDir, "Graph.pdf",sep=""), plot = P1, device='pdf', scale = 1, width = 5, height = 10, units ="in", dpi = 300, limitsize = TRUE)



# Make plot and save (decent auto layouts: dh)
P1=ggraph(plotgraph,layout = "dh") + 
  geom_edge_fan( aes(width=weight,colour=EDGES$from), 
                 arrow = arrow(length = unit(2, 'mm'),ends = "last", type = "closed"), end_cap = circle(0, 'cm'), alpha=1,strength=1) +
  geom_node_point(size=1) +
  geom_node_text(aes(label=name),angle=0,size=2, nudge_x = 3, color='red' ) +
  theme_classic() + 
  theme(legend.text=element_text(size=6),legend.title=element_text(size=6),
        axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),axis.title.y=element_blank()) +
  scale_edge_width(range = c(0,1)) + scale_edge_color_hue(guide='none')

ggsave(paste(PlotDir, "Graph2.pdf",sep=""), plot = P1, device='pdf', scale = 1, width = 5, height = 10, units ="in", dpi = 300, limitsize = TRUE)



```
































































