---
title: "Notebook plotting offsets in connectivity between PB-FB-XX neurons and other columnar neurons"
output:
  html_document:
    df_print: paged
---


### Command to clear environment is: rm(list = ls(all.names = TRUE))
### Command to update is remotes::update_packages('neuprintr')
### Load libraries
```{r message=FALSE, warning=FALSE}
library(nat)
library(neuprintr)
library(tidyverse)
library(dplyr)
library(matlib)
library(RColorBrewer)
library(ggraph)
library(robustbase)
require(alphahull)
library(zoo)
library(ggpubr)
library(ggraph)
library(igraph)
library(tidygraph)
library(xlsx)
library(dtplyr)
library(neuprintrExtra)
library("xlsx")
library(tidyselect)
options(nat.plotengine = 'rgl')
```

### Configurable inputs: choose ROI and save/plot directories
```{r}

# Directory to save data to.
SaveDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/"

# Directory to save plots to.
PlotDir="C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/Section2/"

# Create save/plot directory if they dont exists yet
if (!dir.exists(SaveDir)){dir.create(SaveDir)}
if (!dir.exists(PlotDir)){dir.create(PlotDir)}


```

### Connect to neuprint server.
```{r}
neuprint_login()
```

### Get general functions
```{r}

source("FB_SynapseDistribution_Utils.r")
source("FB_LayerOutline_Utils.r")
source("FB_ConnectivityOffsetPlotting_Utils.r")
source("../visualizeConnectivityTables.r", chdir = TRUE)
source("../inputOutputRegionsVis.r")
source("../GetNeuronsInRoi.r")


```


# Get all FB bodies and columnar types
```{r}

NamedBodies = Get_AllNeurons_InRoi("FB", FALSE)
NamedBodies = ComputeRelativeSynapseCounts(NamedBodies)
Columnar_Types=sort(unique( NamedBodies$bodytype[ startsWith(NamedBodies$bodytype, "PF" ) | startsWith(NamedBodies$bodytype, "FR" ) | 
               startsWith(NamedBodies$bodytype, "FS" ) | startsWith(NamedBodies$bodytype, "FC" ) |
               startsWith(NamedBodies$bodytype, "vDelta" ) | startsWith(NamedBodies$bodytype, "hDelta" )] ))

FBBodyCount=NamedBodies %>% group_by(bodytype) %>% summarize(NumofNeurons=n())
FBColumnarBodyCount=subset(FBBodyCount, bodytype %in% Columnar_Types)

```


# Load pre-processed synapse location data and remove variables that won't be used
# NOTE: Need to rebuild this periodically in case types/names get changed
```{r}

load(paste(SaveDir,"FBColumnarSynapses_PostPCA.RData",sep=""))
rm(list=c("roiEigen","Mesh_FB_Points","Mesh_FB_L1_Points", "Mesh_FB_L2_Points","Mesh_FB_L3_Points", "Mesh_FB_L4_Points",
          "Mesh_FB_L5_Points", "Mesh_FB_L6_Points","Mesh_FB_L7_Points", "Mesh_FB_L8_Points", "Mesh_FB_L9_Points","origin"))

# Assign Side, PB glom, and FB col info
FBC_SynsAll=Assign_FBcol_PBglom(FBC_SynsAll, "bodyname", "Side", "PBglom", "FBcol", "bodyid")


```




# ##################################################################################################################
# ######### Figure 1: Intra-FB connectivity motifs #################################################################
# ##################################################################################################################



# Plot intra-FB connectivity matrices and assign to motifs
```{r}
source("FB_ConnectivityOffsetPlotting_Utils.r")


# Other plotting directories
PFX_Dir_Connectivity=paste(PlotDir,"Columnar_Motifs","/",sep="")
if (!dir.exists(PFX_Dir_Connectivity)){dir.create(PFX_Dir_Connectivity)}


# Get columnar output connectivity table
PFX_Bag=create_neuronBag(Columnar_Types, slctROI="FB")
PFX_FB_Outputs_All=PFX_Bag[["outputs_raw"]]


# Subset data on columnar types
PFX_FB_Outputs_All=subset(PFX_FB_Outputs_All, databaseType.to %in% Columnar_Types)


# Assign PBglom, FBcol, and Side from neuron names
PFX_FB_Outputs_All=Assign_FBcol_PBglom(PFX_FB_Outputs_All, "name.from", "Side.from", "PBglom.from", "FBcol.from", "from")
PFX_FB_Outputs_All=Assign_FBcol_PBglom(PFX_FB_Outputs_All, "name.to", "Side.to", "PBglom.to", "FBcol.to", "to")


# Order ouput table
PFX_FB_Outputs_All$PBglom.from=factor(PFX_FB_Outputs_All$PBglom.from, levels = rev(c("R9","L1","R8","L2","R7","L3","R6","L4","R5","L5","R4","L6","R3","L7","R2","L8","R1","L9")))
PFX_FB_Outputs_All$FBcol.from=factor(PFX_FB_Outputs_All$FBcol.from, levels = rev(c("C12","C11","C10","C9","C8","C7","C6","C5","C4","C3","C2","C1","C0")))
PFX_FB_Outputs_All$PBglom.to=factor(PFX_FB_Outputs_All$PBglom.to, levels = rev(c("R9","L1","R8","L2","R7","L3","R6","L4","R5","L5","R4","L6","R3","L7","R2","L8","R1","L9")))
PFX_FB_Outputs_All$FBcol.to=factor(PFX_FB_Outputs_All$FBcol.to, levels = rev(c("C12","C11","C10","C9","C8","C7","C6","C5","C4","C3","C2","C1","C0")))


# Get the number of columns for each neuron type
ColumnarBodies=subset(NamedBodies, bodytype %in% Columnar_Types)
ColumnarBodies=All=Assign_FBcol_PBglom(ColumnarBodies, "bodyname", "Side", "PBglom", "FBcol", "bodyid") 
ColumnCounts=ColumnarBodies %>% group_by(bodytype) %>% summarize(Columns = length(unique(FBcol)))
ColumnCounts$Columns[ !(startsWith(ColumnCounts$bodytype,"hDelta"))]=9

ColumnCounts_from=ColumnCounts
colnames(ColumnCounts_from)<-c("type.from","ColNum.from")
ColumnCounts_to=ColumnCounts_from
colnames(ColumnCounts_to)<-c("type.to","ColNum.to")
PFX_FB_Outputs_All=inner_join(PFX_FB_Outputs_All, ColumnCounts_to, by="type.to")
PFX_FB_Outputs_All=inner_join(PFX_FB_Outputs_All, ColumnCounts_from, by="type.from")


# Map all neurons into 9 column space (C0 to C9)
PFX_FB_Outputs_All$FBcol.from9=PFX_FB_Outputs_All$FBcol.from
PFX_FB_Outputs_All$FBcol.from9=as.numeric(sapply(PFX_FB_Outputs_All$FBcol.from9, substring, 2, 4))
PFX_FB_Outputs_All$FBcol.from9=round(PFX_FB_Outputs_All$FBcol.from9/PFX_FB_Outputs_All$ColNum.from*9)
PFX_FB_Outputs_All$FBcol.from9=paste("C",PFX_FB_Outputs_All$FBcol.from9,sep="")
PFX_FB_Outputs_All$FBcol.from9=factor(PFX_FB_Outputs_All$FBcol.from9, levels = rev(c("C9","C8","C7","C6","C5","C4","C3","C2","C1","C0")))

PFX_FB_Outputs_All$FBcol.to9=PFX_FB_Outputs_All$FBcol.to
PFX_FB_Outputs_All$FBcol.to9=as.numeric(sapply(PFX_FB_Outputs_All$FBcol.to9, substring, 2, 4))
PFX_FB_Outputs_All$FBcol.to9=round(PFX_FB_Outputs_All$FBcol.to9/PFX_FB_Outputs_All$ColNum.to*9)
PFX_FB_Outputs_All$FBcol.to9=paste("C",PFX_FB_Outputs_All$FBcol.to9,sep="")
PFX_FB_Outputs_All$FBcol.to9=factor(PFX_FB_Outputs_All$FBcol.to9, levels = rev(c("C9","C8","C7","C6","C5","C4","C3","C2","C1","C0")))


# Loop over all Pre-Post pairs, map each pair into a 9 column space, and convert that matrix to a vector to be saved
Pre_Post=distinct(PFX_FB_Outputs_All[c("type.from","type.to")])
Vectors=matrix(data=NA,nrow=length(Pre_Post$type.from),ncol=100)
for (ppp in 1:length(Pre_Post$type.from)){
  print(ppp)
  
  # Average across columns and plot (using all columns)
  Temp_PFX_Out=subset(PFX_FB_Outputs_All, (type.from==Pre_Post$type.from[ppp]) & (type.to==Pre_Post$type.to[ppp]))
  
  
  # Subset data and name neurons by column/glom and bodyid for a fully connected 9 column scheme
  Temp_ColumnTable9=Temp_PFX_Out %>% group_by(FBcol.from9,FBcol.to9) %>% summarize(weightRelative=mean(weightRelative))
  
  # Turn dataframe into a matrix, where implicitly missing connections have 0 weight. Store as vector.
  all <- Temp_ColumnTable9 %>% expand(FBcol.from9, FBcol.to9) %>% distinct()
  Temp_ColumnTable9_Full = Temp_ColumnTable9 %>% dplyr::right_join(all, by = c("FBcol.from9", "FBcol.to9"))
  Temp_ColumnTable9_Full$weightRelative[is.na( Temp_ColumnTable9_Full$weightRelative)]=0
  TempMatrix <- reshape2::acast(Temp_ColumnTable9_Full, FBcol.from9 ~ FBcol.to9, value.var="weightRelative")
  TempVector = c(TempMatrix)
  Vectors[ppp,]=TempVector
}


# define a function for doing PCA on Vectors
motifPCA <- function(PCA_In, Norm, Pre_Post){
  
  # Binarize or normalize data
  if (Norm=="Binary"){
    PCA_In[PCA_In>0.001]=1 #0.001
    #PCA_In[PCA_In<=0.001]=0
  } 
  
  # calculate covariance matrix across dimensions 
  cov = data.frame(cov(PCA_In))
  
  # calculate eigenvectors and values (columns contain PCs, ranked from most variance accounted for to least)
  covEigen = eigen(cov) 
  
  # Project into PC space
  NewData=PCA_In %*% covEigen$vectors
  
  # Make dataframe
  PCA_Out=cbind(Pre_Post,as.data.frame(NewData))
  
  return(PCA_Out)
}


## Perform PCA
Columnar_PC_Motifs=motifPCA(Vectors, "Binary", Pre_Post)


# Make supertypes
Columnar_PC_Motifs$Motif=NA
hDeltaTypes=Columnar_Types[startsWith(Columnar_Types,'hDelta')]
VDeltaTypes=Columnar_Types[!startsWith(Columnar_Types,'hDelta') ]
Columnar_PC_Motifs$Motif[ (Columnar_PC_Motifs$type.from %in% hDeltaTypes) & (Columnar_PC_Motifs$type.to %in% hDeltaTypes)] = "H to H"
Columnar_PC_Motifs$Motif[ (Columnar_PC_Motifs$type.from %in% VDeltaTypes) & (Columnar_PC_Motifs$type.to %in% VDeltaTypes)] = "V to V"
Columnar_PC_Motifs$Motif[ (Columnar_PC_Motifs$type.from %in% VDeltaTypes) & (Columnar_PC_Motifs$type.to %in% hDeltaTypes)] = "V to H"
Columnar_PC_Motifs$Motif[ (Columnar_PC_Motifs$type.from %in% hDeltaTypes) & (Columnar_PC_Motifs$type.to %in% VDeltaTypes)] = "H to V"
Columnar_PC_Motifs$Motif=factor(Columnar_PC_Motifs$Motif, levels=unique(Columnar_PC_Motifs$Motif))

# Get colors
pcCols <- paletteer_d("Polychrome::palette36")
pcCols=pcCols[c(26,6,32,25)]

# Loop over and plot every neurons matrix along with its place in the PCA space
for (ppp in 1:length(Pre_Post$type.from)){
  print(ppp)
  
  # Average across columns and plot (using all columns)
  Temp_PFX_Out=subset(PFX_FB_Outputs_All, (type.from==Pre_Post$type.from[ppp]) & (type.to==Pre_Post$type.to[ppp]))
  
  
  # Average across columns and plot (using all columns)
  Temp_ColumnTable=Temp_PFX_Out %>% group_by(FBcol.from,FBcol.to) %>% summarize(weightRelative=mean(weightRelative))
  
  # Calculate number of pre and post neurons
  PreNum=length(unique(Temp_PFX_Out$from))
  PostNum=length(unique(Temp_PFX_Out$to))
  PreNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$bodytype == Pre_Post$type.from[ppp]]
  PostNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$bodytype == Pre_Post$type.to[ppp]]
  FBColtoNum=length(unique(Temp_PFX_Out$FBcol.to))
  
  P1=ggplot(Temp_ColumnTable) + 
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                         midpoint =0.5*max(Temp_ColumnTable$weightRelative), limits=c(0,max(Temp_ColumnTable$weightRelative))) +
    geom_tile(aes(FBcol.to,FBcol.from,fill=weightRelative)) + ylab(Pre_Post$type.from[ppp]) + xlab(Pre_Post$type.to[ppp])
  
  
  # Do the same, but for a fully connected 9 column scheme
  Temp_ColumnTable9=Temp_PFX_Out %>% group_by(FBcol.from9,FBcol.to9) %>% summarize(weightRelative=mean(weightRelative))
  
  # Turn dataframe into a matrix, where implicitly missing connections have 0 weight. Store as vector.
  all <- Temp_ColumnTable9 %>% expand(FBcol.from9, FBcol.to9) %>% distinct()
  Temp_ColumnTable9_Full = Temp_ColumnTable9 %>% dplyr::right_join(all, by = c("FBcol.from9", "FBcol.to9"))
  Temp_ColumnTable9_Full$weightRelative[is.na( Temp_ColumnTable9_Full$weightRelative)]=0
  
  P2=ggplot(Temp_ColumnTable9_Full) + 
    theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                         midpoint =0.5*max(Temp_ColumnTable9_Full$weightRelative), limits=c(0,max(Temp_ColumnTable9_Full$weightRelative))) +
    geom_tile(aes(FBcol.to9,FBcol.from9,fill=weightRelative)) + ylab(Pre_Post$type.from[ppp]) + xlab(Pre_Post$type.to[ppp])
  

  # Plot PCA space
  CCC=pcCols[which(Columnar_PC_Motifs$Motif[ppp] == levels(Columnar_PC_Motifs$Motif))]
  P3=ggplot()  + geom_point(data=Columnar_PC_Motifs,aes(x=V1, y=V2, color=Motif),alpha=0.5,size=2) + 
    geom_point(data=Columnar_PC_Motifs[ppp,],aes(x=V1, y=V2),color="red", fill=CCC, alpha=1,size=5,shape = 21) +
    xlab("PC 1") + ylab("PC 2") + coord_fixed() +  theme_classic() + theme(text = element_text(size=12)) +
    xlim(-4,4) + ylim(0,8) + scale_color_manual(values=pcCols)

  P4=ggarrange(P1,P2,P3,nrow=1,ncol=3)
  ggsave(paste(PFX_Dir_Connectivity, Pre_Post$type.from[ppp],"_to_", Pre_Post$type.to[ppp], "_", as.character(ppp),"_inFB.png",sep=""), plot = P4, device='png', scale = 1, width =15, height = 3.5, units ="in", dpi = 250, limitsize = TRUE)
  
}


# Make plot with all examples shown

CCC1=pcCols[which(Columnar_PC_Motifs$Motif[11] == levels(Columnar_PC_Motifs$Motif))]
CCC2=pcCols[which(Columnar_PC_Motifs$Motif[23] == levels(Columnar_PC_Motifs$Motif))]
CCC3=pcCols[which(Columnar_PC_Motifs$Motif[47] == levels(Columnar_PC_Motifs$Motif))]
CCC4=pcCols[which(Columnar_PC_Motifs$Motif[14] == levels(Columnar_PC_Motifs$Motif))]
CCC5=pcCols[which(Columnar_PC_Motifs$Motif[10] == levels(Columnar_PC_Motifs$Motif))]
CCC6=pcCols[which(Columnar_PC_Motifs$Motif[142] == levels(Columnar_PC_Motifs$Motif))]

P3=ggplot()  + geom_point(data=Columnar_PC_Motifs,aes(x=V1, y=V2, color=Motif),alpha=0.5,size=2) + 
  geom_point(data=Columnar_PC_Motifs[11,],aes(x=V1, y=V2),color="red", fill=CCC1, alpha=1,size=5,shape = 21) +
  geom_point(data=Columnar_PC_Motifs[23,],aes(x=V1, y=V2),color="red", fill=CCC2, alpha=1,size=5,shape = 21) +
  geom_point(data=Columnar_PC_Motifs[47,],aes(x=V1, y=V2),color="red", fill=CCC3, alpha=1,size=5,shape = 21) +
  geom_point(data=Columnar_PC_Motifs[14,],aes(x=V1, y=V2),color="red", fill=CCC4, alpha=1,size=5,shape = 21) +
  geom_point(data=Columnar_PC_Motifs[10,],aes(x=V1, y=V2),color="red", fill=CCC5, alpha=1,size=5,shape = 21) +
  geom_point(data=Columnar_PC_Motifs[142,],aes(x=V1, y=V2),color="red", fill=CCC6, alpha=1,size=5,shape = 21) +
  xlab("PC 1") + ylab("PC 2") + coord_fixed() +  theme_classic() + theme(text = element_text(size=12)) +
  xlim(-4,4) + ylim(0,8) + scale_color_manual(values=pcCols)


ggsave(paste(PFX_Dir_Connectivity, "PCA_Scatter_Examples.pdf",sep=""), plot = P3, device='pdf', scale = 1, width =6, height = 4, units ="in", dpi = 250, limitsize = TRUE)




  
  



```


















# ##################################################################################################################
# ######### Figure 2: ??? ###############################################################################
# ##################################################################################################################
























# Plot connectivity of PB-FB-XX neurons to check for offsets predicted from PB glom to FB col mappings
```{r}


# Get input and output tables
PFX_Types=unique(NamedBodies$bodytype[startsWith(NamedBodies$bodytype, "PF" )])
PFX_Bag=create_neuronBag(PFX_Types, slctROI="FB")
PFX_FB_Outputs_All=PFX_Bag[["outputs_raw"]]
PFX_FB_Inputs_All=PFX_Bag[["inputs_raw"]]


# Subset data on columnar types
PFX_FB_Outputs_All=subset(PFX_FB_Outputs_All, databaseType.to %in% Columnar_Types)
PFX_FB_Inputs_All=subset(PFX_FB_Inputs_All, databaseType.from %in% Columnar_Types)


# Assign PBglom, FBcol, and Side from neuron names
PFX_FB_Outputs_All=Assign_FBcol_PBglom(PFX_FB_Outputs_All, "name.from", "Side.from", "PBglom.from", "FBcol.from", "from")
PFX_FB_Outputs_All=Assign_FBcol_PBglom(PFX_FB_Outputs_All, "name.to", "Side.to", "PBglom.to", "FBcol.to", "to")
PFX_FB_Inputs_All=Assign_FBcol_PBglom(PFX_FB_Inputs_All, "name.from", "Side.from", "PBglom.from", "FBcol.from", "from")
PFX_FB_Inputs_All=Assign_FBcol_PBglom(PFX_FB_Inputs_All, "name.to", "Side.to", "PBglom.to", "FBcol.to", "to")


# Order input table
PFX_FB_Inputs_All$PBglom.to=factor(PFX_FB_Inputs_All$PBglom.to, levels = rev(c("R9","L1","R8","L2","R7","L3","R6","L4","R5","L5","R4","L6","R3","L7","R2","L8","R1","L9")))
PFX_FB_Inputs_All$FBcol.from=factor(PFX_FB_Inputs_All$FBcol.from, levels = rev(c("C9","C8","C7","C6","C5","C4","C3","C2","C1","C0",
                                                                         "DC14","DC13","DC12","DC11","DC10","DC09","DC08","DC07","DC06","DC05","DC04","DC03","DC02","DC01")))
PFX_FB_Inputs_All$name.from=factor(PFX_FB_Inputs_All$name.from, levels = unique((PFX_FB_Inputs_All$name.from)[order(PFX_FB_Inputs_All$FBcol.from)]) )
PFX_FB_Inputs_All$name.to=factor(PFX_FB_Inputs_All$name.to, levels = unique((PFX_FB_Inputs_All$name.to)[order(PFX_FB_Inputs_All$FBcol.to)]) )


# Order ouput table
PFX_FB_Outputs_All$PBglom.from=factor(PFX_FB_Outputs_All$PBglom.from, levels = rev(c("R9","L1","R8","L2","R7","L3","R6","L4","R5","L5","R4","L6","R3","L7","R2","L8","R1","L9")))
PFX_FB_Outputs_All$FBcol.to=factor(PFX_FB_Outputs_All$FBcol.to, levels = rev(c("C9","C8","C7","C6","C5","C4","C3","C2","C1","C0",
                                                                         "DC14","DC13","DC12","DC11","DC10","DC09","DC08","DC07","DC06","DC05","DC04","DC03","DC02","DC01")))
PFX_FB_Outputs_All$name.to=factor(PFX_FB_Outputs_All$name.to, levels = unique((PFX_FB_Outputs_All$name.to)[order(PFX_FB_Outputs_All$FBcol.to)]) )
PFX_FB_Outputs_All$name.from=factor(PFX_FB_Outputs_All$name.from, levels = unique((PFX_FB_Outputs_All$name.from)[order(PFX_FB_Outputs_All$FBcol.from)]) )


# Plot connectivity matrices with PBgloms and FBcols arranged to show mapping
Plot_Connectivity_Mappings(PFX_Types, PFX_FB_Outputs_All, PFX_FB_Inputs_All, PFX_Dir_Connectivity)


```



# Look for lateralized output patterns, where PB-FB-XX neurons of a single neuron type
# target distinct downstream neurons depending on  whether the PB-FB-XX neurons come 
# from the right bridge or left bridge.
```{r}



# Get unique pre-post pairs
Pre_Post=distinct(PFX_FB_Outputs_All[c("type.from","type.to")])


# Make to/from names
PFX_FB_Outputs_All$from_name = paste(PFX_FB_Outputs_All$FBcol.from, PFX_FB_Outputs_All$from, sep="__")
PFX_FB_Outputs_All$to_name   = paste(PFX_FB_Outputs_All$FBcol.to, PFX_FB_Outputs_All$to, sep="__")


# Compute percent input from left and right PB types
Scatter = PFX_FB_Outputs_All %>% group_by(to, Side.from, type.from, type.to) %>% summarise(weightRelative= sum(weightRelative))
Scatter_L=subset(Scatter, Side.from=="L")
colnames(Scatter_L)[colnames(Scatter_L) == "weightRelative"]="weightRelative_L"
Scatter_R=subset(Scatter, Side.from=="R")
colnames(Scatter_R)[colnames(Scatter_R) == "weightRelative"]="weightRelative_R"
Scatter_All=full_join(Scatter_L, Scatter_R, by=c("to", "type.from","type.to"))
Scatter_All$weightRelative_L[is.na(Scatter_All$weightRelative_L)]=0
Scatter_All$weightRelative_R[is.na(Scatter_All$weightRelative_R)]=0
rm(list=c("Scatter","Scatter_L","Scatter_R"))


# Plot every PB-FB-XX to FB columnar type connectivity matrix and look for asymmetric connectivities
ColColors=GetColorMap("FBcol")
ColColors=c(ColColors[1],ColColors)
Delta6Colors <- paletteer_d("Polychrome::dark")
Detlta6Colors = Delta6Colors[c(1,2,3,4,5,6,8,9,11,7,17,18,20,1)]
for (ppp in 1:length(Pre_Post$type.from)){
  print(ppp)
  
  # Subset data and name neurons by column/glom and bodyid
  Temp_PFX_Out=subset(PFX_FB_Outputs_All, type.from == Pre_Post$type.from[ppp] & type.to == Pre_Post$type.to[ppp])
  Temp_Scatter = subset(Scatter_All, type.from == Pre_Post$type.from[ppp] & type.to == Pre_Post$type.to[ppp])
  Temp_Scatter = merge(Temp_Scatter, Temp_PFX_Out[c("to","FBcol.to")], by="to")
  

  # Calculate number of pre and post neurons
  PreNum=length(unique(Temp_PFX_Out$from))
  PostNum=length(unique(Temp_PFX_Out$to))
  PreNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$bodytype == Pre_Post$type.from[ppp]]
  PostNum_All=FBColumnarBodyCount$NumofNeurons[FBColumnarBodyCount$bodytype == Pre_Post$type.to[ppp]]
  FBColtoNum=length(unique(Temp_PFX_Out$FBcol.to))

  
  if (FBColtoNum>4 & PreNum/PreNum_All>0.25 & PostNum/PostNum_All >0.25){
    
    if (Temp_PFX_Out$type.from[1] == Temp_PFX_Out$type.to[1]){
      Prefix="Recurrent"
    } else {
      Prefix=""
    }
    
    XXX=unique(Temp_PFX_Out$to_name)
    YYY=unique(Temp_PFX_Out$from_name)
    P1 <- ggplot(Temp_PFX_Out) + 
      theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
      scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                           midpoint =0.5*max(Temp_PFX_Out$weightRelative), limits=c(0,max(Temp_PFX_Out$weightRelative))) +
      geom_tile(aes(to_name,from_name,fill=weightRelative)) + scale_x_discrete(breaks  = XXX, labels = substr(XXX,1,6))  + 
      scale_y_discrete(breaks  = YYY, labels = substr(YYY,1,6))
                    
    
    if (Temp_PFX_Out$type.to[1] %in% PFX_Types){
      P1 = P1 + facet_grid(rows = vars(Side.from), cols=vars(Side.to), scales="free")
    } else {
      P1 = P1 + facet_grid(rows = vars(Side.from), scales="free_y")
    }
    
    P1 = P1 +ggtitle(paste(Temp_PFX_Out$type.from[1], "(", as.character(PreNum), " of ", as.character(PreNum_All), ") to ",
                           Temp_PFX_Out$type.to[1], "(", as.character(PostNum), " of ", as.character(PostNum_All), ") to ", sep=""))
    

     
    if (Temp_PFX_Out$type.to[1] %in% PFX_Types | startsWith(Temp_PFX_Out$type.to[1], "Delta0")){
      Temp_Scatter$FBcol.to=factor(Temp_Scatter$FBcol.to, levels = rev(c("C9","C8","C7","C6","C5","C4","C3","C2","C1","C0")))
    } else if (startsWith(Temp_PFX_Out$type.to[1], "Delta6")) {
      Temp_Scatter$FBcol.to=factor(Temp_Scatter$FBcol.to, levels = rev(c("DC14","DC13","DC12","DC11","DC10","DC09","DC08","DC07","DC06","DC05","DC04","DC03","DC02","DC01")))
    }
    
    P2=ggplot() + geom_point(data=Temp_Scatter, aes(x=weightRelative_L, y=weightRelative_R, color=FBcol.to)) +
      ggtitle(paste(Temp_PFX_Out$type.from[1]," to ",Temp_PFX_Out$type.to[1],sep="")) + theme_bw()
    
    if (Temp_PFX_Out$type.to[1] %in% PFX_Types | startsWith(Temp_PFX_Out$type.to[1], "Delta0")){
      P2 = P2 + scale_color_manual(values=ColColors, drop=FALSE)
    } else if (startsWith(Temp_PFX_Out$type.to[1], "Delta6")) {
      P2 = P2 + scale_color_manual(values=Detlta6Colors, drop=FALSE)
    }
    
    P3=ggarrange(P1,P2,nrow=1, ncol=2)
    
    ggsave(paste(PFX_Dir_Lat, Prefix, Temp_PFX_Out$type.from[1],"_to_",Temp_PFX_Out$type.to[1], "_inFB.png",sep=""),
           plot = P3, device='png', scale = 1, width =15, height = 5, units ="in", dpi = 500, limitsize = TRUE)
    
  }
}









# Make scatter plot of all R vs L weights
pcCols <- paletteer_d("Polychrome::palette36")
PFXs_ThatOutput=unique(PFX_FB_Outputs_All$type.from)
for (ppp in 1:length(PFXs_ThatOutput)){
  
  Scatter_Temp=subset(Scatter_All, type.from==PFXs_ThatOutput[ppp])
  
  
  
  ggplot() + geom_point(data=Scatter_Temp, aes(x=weightRelative_L, y=weightRelative_R, color=type.to)) + 
    scale_color_manual(values=pcCols, drop=FALSE)
  
}


hist(Scatter_All$weightRelative_L-Scatter_All$weightRelative_R,100) +ylim(c(0,200))





# Plot PFNd to PFNd connectivity
Temp_PFX_Out=subset(PFX_FB_Outputs_All, type.from == "PFNd" & type.to == "PFNd" & weightRelative >0.005)
Temp_PFX_Out$from_name = paste(Temp_PFX_Out$PBglom.from, Temp_PFX_Out$from, sep="__")
Temp_PFX_Out$to_name   = paste(Temp_PFX_Out$PBglom.to, Temp_PFX_Out$to, sep="__")
  

PP <- ggplot(Temp_PFX_Out) + 
  theme_classic() + theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(low="thistle", mid="blueviolet", high="black", 
                       midpoint =0.5*max(Temp_PFX_Out$weightRelative), limits=c(0,max(Temp_PFX_Out$weightRelative))) +
  geom_tile(aes(to_name,from_name,fill=weightRelative)) +
  facet_grid(rows = vars(Side.from), cols=vars(Side.to), scales="free") +
  ggtitle(paste(Temp_PFX_Out$type.from[1]," to ",Temp_PFX_Out$type.to[1],sep=""))

ggsave(paste(PFX_Dir_Lat, "Asym_", Temp_PFX_Out$type.from[1],"_to_",Temp_PFX_Out$type.to[1], "_inFB.png",sep=""),
       plot = PP, device='png', scale = 1, width = 7.5, height = 5, units ="in", dpi = 500, limitsize = TRUE)






```




# Look for evidence of PI motifs by plotting inputs to PFLs
```{r}


######## Part 1: Get the data ######################################################


# Get full input/output connectivity tables for all FB columnar types
Bag=buildInputsOutputsByType(Columnar_Types, slctROI="FB")
FB_ColumnarInputs_All=Bag[["inputs_raw"]]


# Subset data on columnar types
FB_ColumnarInputs_All=subset(FB_ColumnarInputs_All, databaseType.from %in% Columnar_Types)


# Assign PBglom, FBcol, and Side from neuron names
FB_ColumnarInputs_All=Assign_FBcol_PBglom(FB_ColumnarInputs_All, "name.from", "Side.from", "PBglom.from", "FBcol.from", "from")
FB_ColumnarInputs_All=Assign_FBcol_PBglom(FB_ColumnarInputs_All, "name.to", "Side.to", "PBglom.to", "FBcol.to", "to")


# Give each neuron a unique name
FB_ColumnarInputs_All$from_name = paste(FB_ColumnarInputs_All$FBcol.from, as.character(FB_ColumnarInputs_All$from), sep="__")
FB_ColumnarInputs_All$to_name   = paste(FB_ColumnarInputs_All$FBcol.to, as.character(FB_ColumnarInputs_All$to), sep="__")



######## Part 2: Look at inputs (and inputs to inputs) to PFLn ######################################################


# Get a list of neuron types that give significant input to PFLn
PFL_Type="PFL3"
PFLn_Inputs=subset(FB_ColumnarInputs_All, type.to == PFL_Type)
PFLn_InputsPerColumn=PFLn_Inputs %>% group_by(type.from, FBcol.from) %>% summarise(n=n()) %>%
  group_by(type.from) %>% summarize(Columns = n())
PFLn_InputsPerColumn_Filt = subset(PFLn_InputsPerColumn, (startsWith(type.from, "Delta6")  & Columns >= 4) | 
                                                         (!startsWith(type.from, "Delta6") & Columns >= 4 ) )

# Get the network
PFLn_Network_Types=c(unique( PFLn_InputsPerColumn_Filt$type.from ), PFL_Type)
PFLn_Input_Network=subset(FB_ColumnarInputs_All,  type.to %in% PFLn_Network_Types)
PFLn_Input_Network=subset(PFLn_Input_Network, weight > 3)


# Plot the full matrix
P1=Plot_ColCol_Matix(PFLn_Input_Network)
ggsave(paste(PFX_Dir_PI, PFL_Type, ".png",sep=""),
           plot = P1, device='png', scale = 1, width =15, height = 15, units ="in", dpi = 500, limitsize = TRUE)


P2=Plot_ColCol_Matix(subset(PFLn_Input_Network, type.from %in% Columnar_Types[startsWith(Columnar_Types,"Delta0")] ))
ggsave(paste(PFX_Dir_PI, PFL_Type, "Delta0_Outputs.png",sep=""),
       plot = P2, device='png', scale = 1, width =15, height = 15, units ="in", dpi = 500, limitsize = TRUE)


P2=Plot_ColCol_Matix(subset(PFLn_Input_Network, type.from %in% Columnar_Types[startsWith(Columnar_Types,"Delta6")] ))
ggsave(paste(PFX_Dir_PI, PFL_Type, "Delta6_Outputs.png",sep=""),
       plot = P2, device='png', scale = 1, width =15, height = 15, units ="in", dpi = 500, limitsize = TRUE)


P3=Plot_ColCol_Matix(subset(PFLn_Input_Network, type.from %in% Columnar_Types[!startsWith(Columnar_Types,"Delta6")] &
                              type.from %in% Columnar_Types[!startsWith(Columnar_Types,"Delta0")]))
ggsave(paste(PFX_Dir_PI, PFL_Type, "NonDelta_Outputs.png",sep=""),
       plot = P3, device='png', scale = 1, width =15, height = 15, units ="in", dpi = 500, limitsize = TRUE)



InputsPlot_Sub = plotConnectivityMatrix(PFLn_Input_Network, byGroup = "type", connectionMeasure = "weightRelative")
ggsave(paste(PFX_Dir_PI, PFL_Type, "_Type.png",sep=""),
       plot = InputsPlot_Sub, device='png', scale = 1, width =15, height = 15, units ="in", dpi = 500, limitsize = TRUE)


### Need to look at INPUTS TO INPUTS, because we're likely missing something
### Need to loop over PFN to PFL pathways and compute relative strengths



```








Load the libraries
```{r}
library(nat)
library(neuprintr)
library(tidyverse)
library(tidygraph)
library(ggraph)
library(gridExtra)
library(paletteer)
library(visNetwork) 
source("../pathways.R")
source("../R/supertypeUtils.R", chdir = TRUE)
source("../visualizeConnectivityTables.R")
source("../neuprintQueryUtils.R", chdir = TRUE)
source("../colorCodeLookup.R")
source("../FBNetworkVisUtils.R")
options(nat.plotengine = 'rgl')
```

Connect to neuprint
```{r}
neuprint_login()
```

Get a connection table (type to type)
```{r}
nronTypes <- c("PFN","Delta0","Delta6","PFR_a","PFG","FC","PFL","^FR","FS","PFR_b")
ROI = "FB"
  
# Get the connection table
conTab <- getConnectionTable_forSubset(getBodyIdsForList(nronTypes)$bodyid,
                                         getBodyIdsForList(nronTypes)$bodyid,
                                         ROI)

typeToType_Clean <- getTypeToTypeTable(conTab)



# try a different method of getting type to type
conTab_New=conTab
conTab_New=Assign_FBcol_PBglom(conTab_New, "name.from", "Side.from", "PBglom.from", "FBcol.from", "from")
conTab_New=Assign_FBcol_PBglom(conTab_New, "name.to", "Side.to", "PBglom.to", "FBcol.to", "to")
conTab_New=subset(conTab_New, weight>=6)

Column_Counts=conTab_New %>% group_by(type.from, type.to, FBcol.to) %>% summarize() %>% group_by(type.from, type.to) %>% summarize(NumOfCols=n())
Column_Counts_Filt=subset(Column_Counts, NumOfCols>=8)


typeToType_Clean = subset(typeToType_Clean, type.to %in% Column_Counts_Filt$type.to & type.from %in% Column_Counts_Filt$type.from)


```


Specify an x and y lookup table of the location for each neuron type
```{r}
xyLookup <- xyLookupTableInner()
```


Create a dynamic visualization of the FB network data
```{r}
# Get the table of nodes (types)
nodes = data.frame(name = unique(c(typeToType_Clean$type.from,typeToType_Clean$type.to)))
nodes$id <- 1:nrow(nodes)
nodes$superType <- nodes$name %>% as.character %>% supertype()

# Position the nodes according to the lookup table
nodes$x <- sapply(nodes$name, function(x) xyLookup$x[match(x,xyLookup$type)])
nodes$y <- sapply(nodes$name, function(x) xyLookup$y[match(x,xyLookup$type)])

# Get the edges from the connection table
edges <- typeToType_Clean[which((typeToType_Clean$type.from %in% nodes$name) & (typeToType_Clean$type.to %in% nodes$name)),] %>%
  mutate(to = sapply(type.to, function(f) which(f == nodes$name)),
         from = sapply(type.from, function(f) which(f == nodes$name)))
edges$superType <- edges$type.from %>% as.character %>% supertype()
  
# Specify colors for the supertypes
sTs <- xyLookup$type %>% as.character() %>% supertype() %>% unique() %>% sort()
pcCols <- paletteer_d("Polychrome::palette36")
sTCols <- c(pcCols[35],pcCols[32],pcCols[9],pcCols[3],pcCols[8],pcCols[17],pcCols[7],pcCols[26],pcCols[1])

# Set the node properties for the visulization
vis.nodes <- nodes[,c("name","id")]
vis.nodes$type.name <- nodes$name %>% as.character()
vis.nodes$title <- nodes$name %>% as.character()
vis.nodes$label <- ""
vis.nodes$font.size <- 12
vis.nodes$x <- nodes$y*500
vis.nodes$y <- nodes$x*500
vis.nodes$size <- 10
vis.nodes$color.background <- sTCols[match(nodes$superType,as.factor(sTs))]
vis.nodes$color.highlight <- sTCols[match(nodes$superType,as.factor(sTs))]
vis.nodes$color.border <- "black"
vis.nodes$color.highlight.border <- "orange"
vis.nodes$group <- as.character(nodes$superType)

# Set the link properties for the visualization
vis.links <- edges[,c("to","from")]
vis.links$width <- edges$weightRelative*20
vis.links$arrows <- "to"
vis.links$smooth <- TRUE
vis.links$color <- sTCols[match(edges$superType,as.factor(sTs))]

# Create the visualization
v <- visNetwork(vis.nodes, vis.links, width="100%", height="800px",main= "inputs -> outputs") %>% 
  visNodes(fixed = TRUE) %>% 
  visOptions(highlightNearest = list(enabled = TRUE, hover = TRUE, degree = 1,algorithm="hierarchical"), selectedBy = "type.name") 

# Set a color for each group (need to do this for the legend)
for (st in 1:length(sTs)){
  v <- v %>% visGroups(groupname = sTs[st], color = sTCols[st])
}

# Add a legend and the ability to select multiple nodes
v <- v %>% visLegend(width=0.2, main="super type",ncol=3) %>% visInteraction(multiselect = TRUE)

# Save the plot
visSave(v, "C:/Users/labadmin/Documents/Cx_EM_Analysis/BradData/FB_Analysis/OffsetConnectivity/PFX_Plots_All/PFX_PI/AllColumnarConnections.html", selfcontained = TRUE, background = "white")
```











