---
title: "validation-Figure3"
output: html_notebook
---

This notebook generates the plots related to the first "validation" figure (figure 3), which compares connectivity in the EB in two different versions of the dataset.

## Preparing the environment:

- Path to the folder where the plots will be saved if need be (by default in a folder created for that in the validation folder)
```{r}
validationFolder <- file.path("validationFigures-figure3")
if (!dir.exists(validationFolder)) dir.create(validationFolder)
```

- Loading some local functions
```{r}
source("validationFunctions.R")
source(file.path("..","R","paperTheme.R"))
```

## Preparing the data

We want to compare two version of the dataset. One is the recent one used throughout this paper (v1.1), the other one corresponds to a stage where the EB wasn't densely proofread yet (v0.9, which has been added to newprint). Those two variables can be passed as the `dataset` argument in most `neuprintr` functions:
```{r}
newD <- "hemibrain:v1.1"
oldD <- "hemibrain:v0.9"
```

We first collect information about the EB innervation of neurons in the new dataset:
```{r}
ebNeurons <- neuprint_bodies_in_ROI("EB",all_segments = FALSE,dataset=newD)
ebInfo <- filter(getRoiInfo(ebNeurons$bodyid,dataset=newD),roi=="EB")
ebInfo[is.na(ebInfo)] <- 0
head(ebInfo)
```

We then select neurons with at least 200 upstream or downstream synapses to be used in the comparisons of inputs (or outputs):
```{r}
ebIns <- filter(ebInfo,upstream>200)
ebOuts <- filter(ebInfo,downstream>200)
```

We then run `getCompConnectionTable`, defined in **validationFunctions.R**. This gathers modified connection tables in both versions of the dataset, for an "input" and an "output" set of bodyids and returns a table of comparisons. A few notes on variables in that table:
- `side` specify if the connection is to be used for inputs or outputs comparisons
- `known_synapses` refers to the number of synapses made onto (or received from) traced partners (rather than fragments)
- `knownWeightRelative` and `knownOutputContribution` are similar to `weightRelative` and `outputContribution` except that they are relative to the synapses made to traced partners rather than relative to all the neuron's synapses
- `old` and `new` are `knownWeightRelative.old/new` if `side` is "inputs", `knownOutputContribution.old/new` is it's "outputs". Similarly, `bodyid` is the postsynaptic partner if `side` is "inputs" and the presynaptic partner otherwise 
- `known_synapses_ratio` is the fraction increase in the number of synapses to traced partners between the old and the new dataset for the neuron defined in `bodyid`
The function also computes completedness statistics we won't be using here.
```{r}
EBAges <- getCompConnectionTable(ebIns$bodyid,ebOuts$bodyid,"EB",newD,oldD)
head(EBAges)
```

The bodyid of the EPG used as an example in the figure:
```{r}
exampleEPG <- 789126240
```

## Plotting the increase in synapses to known partners (panel B)
We select neurons with at least a 10% change and get a condensed version of the table for plotting:
```{r}
EBAges_filtered <- filter(EBAges,known_synapses_ratio>0.1)
EBAges_summary <-distinct(EBAges_filtered,bodyid,side,databaseType,supertype2,known_synapses_ratio) 
head(EBAges_summary)
```

We then plot the results, separating inputs and outputs:
```{r}
synChangeEB <- ggplot(EBAges_summary,aes(x=databaseType,
                                         y=known_synapses_ratio*100,
                                         color=supertype2)) +
  geom_jitter(width=0.25,size=0.4) + 
     scale_color_CX_supertype(name="supertype") +
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.background.x = element_rect(color="black")) + 
  facet_grid(.~side,scales="free_x") + 
  xlab("") + ylab("known synapses change (%)") +
  ylim(c(0,120))+ggforce::geom_mark_circle(aes(filter = (bodyid == exampleEPG & side=="inputs")),color="black",expand=0.03)
synChangeEB
```
And save it:
```{r}
save_plot(file.path(validationFolder,"EBCounts.svg"),synChangeEB,base_width=6.5,base_height=2.25)
```

## Linear fits of connectivity between the two dataset (panels C and D)
We used the `getFit` function, a convenience function defined in **validationFunctions.R** to run linear fits on a dataframe between `predictor` and `predicted` grouped according to `groups`. We use it on our comparison table, between the `old` and `new` variable:
```{r}
EBFits <- getFit(EBAges,
                 groups = c("bodyid","databaseType","supertype2","side"),
                 predicted="new",predictor="old")
head(EBFits)
```
We also combine it with the original table to get metadata we need for plots:
```{r}
EBFits <- left_join(EBFits,
                    distinct(EBAges,bodyid,databaseType,supertype2,side,known_synapses_ratio,known_synapses.old,known_synapses.new),
                    by=c("bodyid","databaseType","supertype2","side"))
```

### Example fit (panel C)
We use one EPG neuron as an example, showing the relative weight in the old vs the new dataset, overlaying the liner fit (we use ggplot's `geom_smooth` for that) and annotating with the fit statistics:
```{r}
fitValsEPG <- filter(EBFits,bodyid==exampleEPG & side=="Inputs")
EBCompExample <- ggplot(filter(EBAges_filtered,bodyid==exampleEPG & side=="inputs"),aes(x=old,y=new)) +
  geom_point(aes(color=supertype2.from),size=0.4) + 
  geom_smooth(formula=y~x,method="lm",color="grey70",alpha=0.1) + 
  geom_abline(linetype=2,lwd=0.2) + theme_paper()  +
  scale_color_CX_supertype(name="Supertype") + xlab("relative weight in the old dataset") +
  coord_fixed() +
  ylab("relative weight in the new dataset") + 
  annotate(geom="text",x=0.015,y=0.002,label=paste0("s= ",format(fitValsEPG$estimate,digits = 3),"\n r\u00b2= ",format(fitValsEPG$adj.r.squared,digits=3)))

EBCompExample
```
Then save it:
```{r}
save_plot(file.path(validationFolder,"EBExampleFit.svg"),EBCompExample,base_width=3,base_height=3)
```

### Fits results (panel D)
We plot the estimated slope (with error bars) for all the fits run:
```{r}
EBSlopes <- ggplot(filter(EBFits,paste(bodyid,side) %in% paste(EBAges_summary$bodyid,EBAges_summary$side)),
                   aes(x=databaseType,y=estimate,
                       ymin=estimate-std.error,ymax=estimate+std.error,color=supertype2)) +
  geom_pointrange(size=0.4/20,position=position_jitter(width=0.2)) + scale_color_CX_supertype(name="supertype") +
  facet_grid(.~side,scales = "free_x") + 
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.background.x = element_rect(color="black")) +
  xlab("") +ylab("slope estimate") + 
  ggforce::geom_mark_circle(aes(filter = (bodyid == exampleEPG & side=="inputs")),color="black",expand=0.03) + 
  geom_hline(yintercept = 1,lty=2)
EBSlopes
```

And save it:
```{r}
save_plot(file.path(validationFolder,"EBSlopes.svg"),EBSlopes,base_width=6.5,base_height=2.25)
```

##  Influence of the amount of proofreading on the fit results (figure supplement 1)
We quantify how the slope and r^2 of the fits vary as the function of:
- the increase in synapse numbers between the two dataset 
- the absolute number of synapses the neuron of interest has

### Increase to slope (panel A)
```{r}
incSlope <-  ggplot(filter(EBFits,paste(bodyid,side) %in% 
                             paste(EBAges_summary$bodyid,EBAges_summary$side)),
                    aes(x=known_synapses_ratio*100,y=estimate,ymin=estimate-std.error,ymax=estimate+std.error,color=supertype2)) + 
  geom_pointrange(size=0.2/3) +
  scale_color_CX_supertype(name="supertype") + 
  facet_grid(.~side,scales = "free_x") + 
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.background.x = element_rect(color="black")) +
  xlab("known synapse increase") +ylab("slope estimate") + geom_hline(yintercept=1,lty=2)
incSlope
```
```{r}
save_plot(file.path(validationFolder,"SI-panelA.svg"),incSlope,base_width=4,base_height=2)
```

### Increase to r^2 (panel B)

```{r}
incRS <-  ggplot(filter(EBFits,paste(bodyid,side) %in% paste(EBAges_summary$bodyid,EBAges_summary$side)),
                 aes(x=known_synapses_ratio*100,y=adj.r.squared,color=supertype2)) + 
  geom_point(size=1) + scale_color_CX_supertype(name="supertype") + 
  facet_grid(.~side,scales = "free_x") +
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.background.x = element_rect(color="black")) +
  xlab("known synapse increase") +ylab("adjusted r\u00b2") + geom_hline(yintercept=1,lty=2)
incRS
```

```{r}
save_plot(file.path(validationFolder,"SI-panelB.svg"),incRS,base_width=4,base_height=2)
```

### Absolute to slope (panel C)
```{r}
nSlope <-  ggplot(filter(EBFits,paste(bodyid,side) %in% paste(EBAges_summary$bodyid,EBAges_summary$side)),
                  aes(x=known_synapses.new,y=estimate,ymin=estimate-std.error,ymax=estimate+std.error,color=supertype2)) + 
  geom_pointrange(size=0.2/3) + 
  scale_color_CX_supertype(name="supertype") + 
  facet_grid(.~side,scales = "free_x") + 
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.background.x = element_rect(color="black")) +
  xlab("# synapses") +ylab("slope estimate")  + geom_hline(yintercept=1,lty=2)
nSlope
```
```{r}
save_plot(file.path(validationFolder,"SI-panelC.svg"),nSlope,base_width=4,base_height=2)
```

### Absolute to r^2 (panel D)

```{r}
nRS <-  ggplot(filter(EBFits,paste(bodyid,side) %in% paste(EBAges_summary$bodyid,EBAges_summary$side)),
               aes(x=known_synapses.new,y=adj.r.squared,color=supertype2)) + 
  geom_point(size=1) + 
  scale_color_CX_supertype(name="Supertype") + 
  facet_grid(.~side,scales = "free_x") + 
  theme_paper(axis.text.x = element_text(angle = 90,hjust = 1,vjust=0.5),strip.background.x = element_rect(color="black")) +
  xlab("# synapses") +ylab("adjusted r\u00b2") +geom_hline(yintercept=1,lty=2)
nRS
```
```{r}
save_plot(file.path(validationFolder,"SI-panelD.svg"),nRS,base_width=4,base_height=2)
```
