---
title: "Pathways to DNs, figure 63"
output: html_notebook
---
## Preparing the environment
Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source("outputFunctions-core.R")
source(file.path("..","R","paperTheme.R"))
```
This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure63-OutputsToDN"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
## Known types in the output graph
knownTypesTable <- readRDS(file.path(dataFolder,"known-table.rds"))
## The table of pathway weights
CXoutFull <- readRDS(file.path(dataFolder,"pathwayWeightsTable.rds"))
## The full outputs graph (and bilateral graph)
CX_outGraph <- readRDS(file.path(dataFolder,"output_graph.rds"))
CX_outGraphBi <- readRDS(file.path(dataFolder,"output_graph_FullBilateral.rds"))
## Metadata about the main targets
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
```

## Preparing some data
A palette to be used in network graphs:
```{r}
customGraphPalette <- supertype3Palette[names(supertype3Palette) %in% filter(mainFFConns, Path_weight>0.005)$supertype3.to]
extraPal <- p36[!p36 %in% customSupertypePalette & !p36 %in% customGraphPalette]
extraLevs <- unique(mainFFConns$supertype2.to[mainFFConns$supertype3.to=="Terra incognita"])
extraPal <- extraPal[1:length(extraLevs)]
names(extraPal) <- extraLevs
customGraphPalette <- c(customGraphPalette,extraPal)
```

## DN in the strong targets network (panel A)
We select from the pathway weight table all DN types that receive at least 0.005% pathway weight from the CX. We also customize the supertypes to the most common CX output types present in that table and label the DN neurons with the VNC neuropil they putatively innervate: 
```{r}

CXoutFFEndpointDNs <- filter(CXoutFull,(supertype3.to == "DN" | 
                                           startsWith(type.to,"DN?")) & 
                                fullCXwr>0.0005) %>%
   mutate(supertype.to=knownTypesTable$supertype[match(type.to,knownTypesTable$type)], 
          supertype.from=CXOutputNeurons$supertype[match(databaseType.from,
                                                         CXOutputNeurons$databaseType)],
          customSupertype = case_when(supertype.from=="PFL" ~ databaseType.from,
                                      grepl("ExR[7-8]",supertype.from) ~ as.character(supertype.from),
                                      supertype.from=="FR2" ~ as.character(supertype.from),
                                      TRUE ~ "Other"),
          target.to = case_when(type.to %in% c("DNa01_R","DNa01_L",
                                               "MDN_R","MDN_L") ~ "legs",
                                type.to %in% c("DN?_1406000196",
                                               "DNa09_R","DNa09_L") ~ "wing",
                                type.to %in% c("DNa03_R","DNa03_L") ~ "tectulum",
                                type.to %in% c("DNp15_R","DNp16/17_R","DNb02_R",
                                               "DNp15_L","DNp16/17_L","DNb02_L") ~ "neck+halteres",
                                type.to %in% c("DNp18_R","DNp18_L",
                                               "DN?_5813078116",
                                               "DNa04_R","DNa04_L") ~ "neck+wings+halteres",
                                type.to %in% c("DNa02_R","DNb01_2_R",
                                               "DNb01_1_R","DNb01_1_L",
                                               "DNp32_R","DNa02_L",
                                               "DNb01_2_L","DNp32_L") ~ "mixed",
                                TRUE ~ "?"
          )     
   )
head(CXoutFFEndpointDNs)
```
```{r}
moreDNsPlot <- ggplot(CXoutFFEndpointDNs,aes(x=type.to,y=Path_weight)) +
   geom_col(aes(fill=customSupertype))+ 
   scale_fill_manual(name="source type",values=c(customSupertypePalette,"Other"="grey90"))+
   ylab("total pathway weight") + 
   xlab("descending neuron") +
   facet_grid(.~target.to,scale="free_x",space="free_x",switch = "x") + 
   theme_paper(axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5),
               strip.text.x = element_text(angle=60),
               strip.background.x = element_rect(fill="grey90"))  

moreDNsPlot
```
```{r}
save_plot(file.path(outputsFolder,"DNWeights.svg"),moreDNsPlot,base_width = 7,base_height=4.5)
```

## PFL neurons to DN graph (panel B)
We built this network manually (from neurons found using the `getSubgraph` function) for custom positioning of the nodes:
```{r}
# This is the code we would run to make a graph with the neurons of interest, this could be plotted for exploration 
#PFLsToDN<- getLocalSubgraph(c("ExR8_R","ExR7_R","ExR7_L","PFL3_L*","PFL2_R","PFL3_R*","LAL112_R"),c("DNa01_R","DNa02_R","DNa03_R","DNa04_R","DNb01_2_R","DN?_5813078378","MDN_R","LAL111_R"),CX_outGraphBi,order=1) 

PFL_toDNs_Half <- as_tbl_graph(induced_subgraph(CX_outGraphBi,c("PFL2_L","PFL2_R",
                                               "PFL3_L*","PFL3_R*",
                                               "LAL121_L",
                                               "AOTU019_L",
                                               "PS013_R",
                                               "LAL018_R",
                                               "LAL014_R",
                                               "LAL046_R",
                                               "LAL040_L",
                                               "LAL010_R",
                                               "CRE015_R",
                                               "DNa03_R",
                                               "DNa02_R",
                                               "DNa01_R",
                                               "DNa04_R",
                                               "ExR7_R",
                                               "LAL013_R",
                                               "DNb01_2_R","DN?_5813078378",
                                               "PS211_R",
                                               "ExR7_L",
                                               "ExR8_R",
                                               "PS077_R",
                                               "MBON27_L"))) %N>% mutate(x=case_when(
                                                  type%in% c("PFL3_L*") ~ 1,
                                                  type %in% c("PFL3_R*") ~ 2.2,
                                                  type=="MBON27_L"~1.4,
                                                  type %in% c("PFL2_L","ExR7_L") ~ 1.6,
                                                  type %in% c("PFL2_R","DNa01_R","ExR7_R") ~ 1.8,
                                                  type %in% c("LAL121_L","AOTU019_L","LAL040_L") ~ 2,
                                                  type %in% c("CRE015_R","DNb01_2_R") ~ 0.8,
                                                  type == "LAL018_R" ~ 1,
                                                  type %in% c("DNa02_R","ExR8_R") ~ 1.1,
                                                  type == "LAL014_R" ~ 1.4,
                                                  type %in% c("LAL046_R","PS077_R") ~ 1.2,
                                                  type == "LAL010_R" ~ 1.6,
                                                  type == "LAL013_R" ~ 1.7,
                                                  type == "DNa04_R" ~ 0.93,
                                                  type == "DNa03_R" ~ 1.3,
                                                  type %in% c("DN?_5813078378","PS013_R","PS211_R") ~ 0.6
                                                  ),
                                                  y=case_when(
                                                     type %in% c("PFL2_L","PFL2_R","PFL3_L*","PFL3_R*") ~ 3,
                                                     type %in% c("PS013_R","PS013_L","LAL046_R","LAL046_L","LAL121_R","CRE015_R") ~ 2.2,
                                                     type %in% c("LAL046_R","LAL014_R","LAL121_L") ~ 2,
                                                     type %in% c("LAL018_R","LAL010_R","PS211_R") ~ 1.8,
                                                     type %in% c("AOTU019_L") ~ 2.6,
                                                     type == "LAL040_L" ~ 1.2,
                                                     type %in% c("ExR7_R","ExR7_L","MBON27_L","ExR8_R","PS077_R") ~ 0.3,
                                                     type == "LAL013_R" ~ 0.5,
                                                     type %in% c("DNb01_2_R","DN?_5813078378","DNa03_R","DNa03_L","DNa02_R","DNa02_L","DNa01_R","DNa04_R")~1
                                                  )) %>% selectSupertypeSet(default_level = 1) %>%
   customOutputSupertype() %>% 
   mutate(customSupertype=case_when(customSupertype=="MBON27" ~ "MBON",TRUE ~ customSupertype)) %E>%
   mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)])
PFL_toDNs_Half
```
Then plot it:
```{r}
PFL2DNsHalfPlot <- ggraph(PFL_toDNs_Half,layout="manual",x=x,y=y) + 
   geom_vline(xintercept = 2,lty=2,color="grey50")+
   geom_edge_fan(aes(color=customSupertype.from,width=weightRelative),
                 end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                 arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
   geom_node_point(aes(color=customSupertype),size=4)+
   geom_node_text(aes(label=type))+
   theme_paper_map()+scale_color_manual(values=c(customGraphPalette,customSupertypePalette))+
   scale_edge_color_manual(values=c(customGraphPalette,customSupertypePalette)) +
   scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="relative weight") +
   guides(color="none",edge_color="none") 

PFL2DNsHalfPlot 
```
```{r}
save_plot(file.path(outputsFolder,"PFLtoDN_NGraph.svg"),PFL2DNsHalfPlot,nrow=1,ncol=2)
```

## Bodyids for renderings
### Panel C
LAL121_R
```{r}
filter(mainFFTargetsNeurons,type %in% c("LAL121_R"))$bodyid
```
AOTU019_R
```{r}
filter(mainFFTargetsNeurons,type %in% c("AOTU019_R"))$bodyid
```
PFL3_L*:
```{r}
filter(CXNeurons,type %in% c("PFL3_L*"))$bodyid
```

### Panel D
LAL018_R:
```{r}
filter(mainFFTargetsNeurons,type %in% c("LAL018_R"))$bodyid
```
PS013_R:
```{r}
filter(mainFFTargetsNeurons,type %in% c("PS013_R"))$bodyid
```
DNa04_R:
```{r}
filter(mainFFTargetsNeurons,type =="DNa04_R")$bodyid
```
### Panel E
LAL010_R:
```{r}
filter(mainFFTargetsNeurons,type %in% c("LAL010_R"))$bodyid
```
DNa02_R:
```{r}
filter(mainFFTargetsNeurons,type %in%"DNa02_R")$bodyid
```

## Other pathways to DN (figure supplement 1)
### ExR8 to DNp15 16/17 (panels C, D, E)
#### Network graph
Generate the graph:
```{r}
pathsToDNp15<- getLocalSubgraph(c("ExR8_R","ExR8_L"),c("DNp15_R","DNp16/17_R"),
                                CX_outGraphBi,order=1) %>% selectSupertypeSet(default_level = 1) %>%
   customOutputSupertype() %>% 
   mutate(customSupertype=case_when(customSupertype=="MBON27" ~ "MBON",TRUE ~ customSupertype)) %E>%
   mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)])
```
And plot it: 
```{r}
pathsToDNp15Plot <- ggraph(pathsToDNp15,layout="sugiyama") +
   geom_edge_fan(aes(color=customSupertype.from,width=weightRelative),
                 end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                 arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
   geom_node_point(aes(color=customSupertype),size=4)+
   geom_node_text(aes(label=type))+
   theme_paper_map()+
   scale_color_manual(values=c(customGraphPalette,customSupertypePalette))+
   scale_edge_color_manual(values=c(customGraphPalette,customSupertypePalette)) +
   scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="relative weight") +
   guides(color="none",edge_color="none") + 
   coord_cartesian(clip="off") + theme(legend.position = c(0.05,0.9))
pathsToDNp15Plot
```
Save it:
```{r}
save_plot(file.path(outputsFolder,"ExR2DNP_NGraph.svg"),pathsToDNp15Plot,nrow=0.5,ncol=0.5)
```

#### Bodyids for renderings (panel D and E)
PS235_R:
```{r}
filter(mainFFTargetsNeurons,type %in% c("PS235_R"))$bodyid
```
ExR8:
```{r}
filter(CXOutputNeurons,type =="ExR8_R")$bodyid
```

DNp15:
```{r}
DNp15Id <- neuprint_search("DNp15_R")
DNp15Id$bodyid
```

### FR to DNp32 path network graph (panel F)
Generate the graph:
```{r}
pathsToDNp32<- getLocalSubgraph(c("FR2_R","FR2_L"),c("DNp32_R"),CX_outGraphBi,order=1) %>%
   selectSupertypeSet(default_level = 1) %>%
   customOutputSupertype() %>% 
   mutate(customSupertype=case_when(customSupertype=="MBON27" ~ "MBON",TRUE ~ customSupertype)) %E>%
   mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)])
```
And plot it: 
```{r}
pathsToDNp32Plot <- ggraph(pathsToDNp32,layout="sugiyama") +
   geom_edge_fan(aes(color=customSupertype.from,width=weightRelative),
                 end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                 arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
   geom_node_point(aes(color=supertype2),size=4)+geom_node_text(aes(label=type))+
   theme_paper_map()+
   scale_color_manual(values=c(customGraphPalette,customSupertypePalette))+
   scale_edge_color_manual(values=c(customGraphPalette,customSupertypePalette)) +
   scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="relative weight") +
   guides(color="none",edge_color="none") + theme(legend.position=c(0.6,0.5))

pathsToDNp32Plot
```
```{r}
save_plot(file.path(outputsFolder,"FR2DNp_NGraph.svg"),pathsToDNp32Plot,nrow=0.5,ncol=0.5)
```

### Paths to MDN (panels A,B)
#### Network graph
We built this network manually (from neurons found using the `getSubgraph` function) for custom positioning of the nodes. One first has to build two half networks for both sides of the brain (this is because MDN neurons innervate both side of the brain, and we want to distinguish the two innervated regions on the right and the left):
```{r}
# This is the code we would run to make a graph with the neurons of interest, this could be plotted for exploration 
#pathsToMDN<- getLocalSubgraph(c("PFL2_L","PFL2_R","PFL3_R*","ExR6_L"),c("MDN_L","MDN_R"),CX_outGraph,order=1)

pathsToMDNManual_left <- as_tbl_graph(induced_subgraph(CX_outGraphBi,
                                                       c("PFL2_L","PFL2_R",
                                                         "MBON30_R",
                                                         "PFL3_L*",
                                                         "MDN_R","MDN_L",
                                                         "LAL160_R","LAL161_R",
                                                         "LAL040_R"))) 

pathsToMDNManual_right <- as_tbl_graph(induced_subgraph(CX_outGraphBi,
                                                        c("PFL2_L","PFL2_R",
                                                          "PS010_R","MDN_L"))) %N>%
   mutate(type=case_when(type=="MDN_L" ~ "MDN_L_c",
                         TRUE ~type),
          name=type)
```  
We then join the two graphs:
```{r}
pathsToMDNManual <- graph_join(pathsToMDNManual_left,pathsToMDNManual_right) %N>%
   mutate(x=case_when(type %in% c("PFL2_L") ~ 0.3,
                      type %in% c("LAL160_R","LAL161_R","LAL040_R") ~ 1,
                      type %in% c("PFL2_R") ~ 0.5,
                      type %in% c("PS010_R") ~ 0.5,
                      type == "MBON30_R" ~ 0.7,
                      type %in% c("PFL3_L*") ~ 0.9,
                      type %in% c("MDN_L") ~ 1.3,
                      type == "MDN_R" ~ 1.15,
                      type == "MDN_L_c" ~ 0.85),
          y=case_when(type %in% c("PFL2_L","PFL2_R","PFL3_L*","MBON30_R") ~ 3,
                      type %in% c("MDN_L","MDN_L_c") ~ 1.1,
                      type == "MDN_R" ~0.9,
                      type == "PS010_R" ~ 2,
                      type %in% c("LAL160_R") ~ 2,
                      type %in% c("LAL161_R") ~ 1.7,
                      type == "LAL040_R" ~ 2.5)) %>% 
   selectSupertypeSet(default_level = 1) %>%
   customOutputSupertype()  %>% mutate(customSupertype=case_when(customSupertype=="MDN" ~ "DN",
                                                                 customSupertype=="MBON30" ~ "MBON",
                                                                 TRUE ~ customSupertype)) %E>%
   mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)])
```
Then plot the graph:
```{r}
MDNsPlot <- ggraph(pathsToMDNManual,layout="manual",x=x,y=y) + 
   geom_vline(xintercept = 1,lty=2,color="grey50")+
   geom_edge_fan(aes(color=customSupertype.from,width=weightRelative),
                 end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                 arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
   geom_node_point(aes(color=customSupertype),size=4)+
   geom_node_text(aes(label=type),nudge_y = 0.1)+
   theme_paper_map()+
   scale_color_manual(values=c(customGraphPalette,customSupertypePalette))+
   scale_edge_color_manual(values=c(customGraphPalette,customSupertypePalette)) +
   scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="relative weight") +
   guides(color="none",edge_color="none") + theme(legend.position=c(0.85,0.9))

MDNsPlot
```
```{r}
save_plot(file.path(outputsFolder,"PathsToMDN_NGraph.svg"),MDNsPlot,nrow=0.6,ncol=0.7)
```

#### Bodyids for renderings
PS010_R:
```{r}
ps10Id <- neuprint_search("PS010_R")
ps10Id$bodyid
```
LAL160_R and LAL161_R:
```{r}
filter(mainFFTargetsNeurons,type %in% c("LAL160_R","LAL161_R"))$bodyid
```
PFL2_R:
```{r}
filter(CXOutputNeurons,type =="PFL2_R")$bodyid
```

