---
title: "PFL3 weight distribution per column, figure 64"
output: html_notebook
---

## Preparing the environment
Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure64-PFL3"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```
Loading some data generated in "Outputs-Core.Rmd":
```{r}
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
```

## PFL3 outputs connectivity matrix at glomerulus resolution
We first get the connection information about PFL3_L direct partners:
```{r}
PFLBag <- neuronBag(filter(CXNeurons,type == "PFL3_L*"),selfRef = T,
                    slctROI=outsideRegions,omitInputs = T,renaming = cxRetyping) %>%
  combineRois(outsideRegions,"Outside")
```
We then use the `plotGlomMat` function (defined in "outputFunctions-display.R"). It takes as input a `neuronBag` object, a neuron of interest, a feature to group on (glomerulus or column), and a table of targets to restrict the plot to, and plot the connectivity per glomerulus (or column):
```{r}
PFL3Glom <- plotGlomMat(PFLBag,
                        "PFL3_L*",
                        grouping="gl",
                        targetFilt=mainFFTargets)
PFL3Glom
```
```{r}
save_plot(file.path(outputsFolder,"outputs-Figure10-PFL3.svg"),PFL3Glom,base_height = 11/5,base_width = 13)
```
