---
title: "Paths to MBONs and PPLs figure"
output: html_notebook
---
## Preparing the environment
```{r}
library(dplyr)
```
Loading some local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source("outputFunctions-core.R")
source(file.path("..","R","paperTheme.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure61-OutputsToMBONsAndPPL"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
## Known types in the output graph
knownTypesTable <- readRDS(file.path(dataFolder,"known-table.rds"))
## The graph of the outputs reduced to strong targets
CX_outGraphRed <- readRDS(file.path(dataFolder,"output_graph_reduced.rds"))

## The graph of the outputs extended to both sides
CX_outGraphBi <- readRDS(file.path(dataFolder,"output_graph_FullBilateral.rds"))

## Metadata about the strongest targest
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
## The table of pathway weights
CXoutFull <- readRDS(file.path(dataFolder,"pathwayWeightsTable.rds"))
```

## Preparing some data
A palette to be used in network graphs:
```{r}
customGraphPalette <- supertype3Palette[names(supertype3Palette) %in% filter(mainFFConns,
                                                                             Path_weight>0.005)$supertype3.to]

extraPal <- p36[!p36 %in% customSupertypePalette & !p36 %in% customGraphPalette]
extraLevs <- unique(mainFFConns$supertype2.to[mainFFConns$supertype3.to=="Terra incognita"])
extraPal <- extraPal[1:length(extraLevs)]
names(extraPal) <- extraLevs
customGraphPalette <- c(customGraphPalette,extraPal)
```

## MBONs and PPLs in the strong target network (panel A)
We select from the pathway weight table all MBON, PPL or antennal lobe types that receive at least 0.05% pathway weight from the CX. We also customize the supertypes to the most common CX output types present in that table: 
```{r}
CXoutFFEndpointMBONPPLs <- filter(CXoutFull,(supertype3.to == "MBON" | 
                                                 supertype1.to=="PPL" | 
                                                 supertype3.to == "Antennal lobe") & 
                                      fullCXwr>0.0005) %>%
    mutate(supertype.to=knownTypesTable$supertype[match(type.to,knownTypesTable$type)],
           supertype.from=CXOutputNeurons$supertype[match(databaseType.from,
                                                          CXOutputNeurons$databaseType)],
           customSupertype = case_when(supertype.from=="PFL" ~ databaseType.from,
                                       supertype.from=="PFR" ~ databaseType.from,
                                       grepl("ExR[7-8]",supertype.from) ~ as.character(supertype.from),
                                       grepl("FB[8-9]",supertype.from) ~ "FB8-9",
                                       supertype.from %in% c("FR1","FR2","FS1","FS2","FC1") ~ as.character(supertype.from),
                                       TRUE ~ "Other")
           )
head(CXoutFFEndpointMBONPPLs)
```
Then generate the plot:
```{r}
moreMBONPPLPlot <- ggplot(CXoutFFEndpointMBONPPLs,aes(x=type.to,y=Path_weight)) +
    geom_col(aes(fill=customSupertype))+ 
    scale_fill_manual(name="source type",
                      values=c(customSupertypePalette,"Other"="grey90"))+
    theme_paper(axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5),
                strip.background.x = element_rect(colour="black")) +  
    ylab("total pathway weight") + xlab("target type") + 
    facet_grid(.~supertype3.to,scale="free_x",space="free_x") 

moreMBONPPLPlot
```
```{r}
save_plot(file.path(outputsFolder,"MBONsPPLTargets.svg"),moreMBONPPLPlot,nrow=0.6,ncol=0.8)
```

## Network graph (panel B)
We manually select origin and target plots (they have been chosen by looking at the graphs converging on the strong targets as seen in panel A) and generate the local subgraph. `getLocalSubgraph` takes as input origin and target neurons and a graph object, and for each neurons group generates a neighborhood of side `order` and returns the intersection of the two neighborhoods (defined in "outputFunctions-display"). We also do some retyping to ease the mapping of existing palettes in the plot:
```{r}
graphToMBONs<- getLocalSubgraph(c("PFR_b_L*",
                                  "FS1A_L","FS1B_L",
                                  "ExR7_R","FS2_L","FR1_L","FR2_L","FB8F_a_R"),
                                c("mALD1_L","PPL102_L","PPL103_R","PPL104_R","PPL105_R","PPL107_R",
                                  "MBON13_R","MBON20_R","MBON23_R","MBON27_R","MBON30_R"),
                                CX_outGraphBi,
                                order=1)%>% 
    selectSupertypeSet(default_level = 1)  %>%
    customOutputSupertype(extraTypes = filter(knownTypesTable,supertype != "CX")$type)  %E>% 
    mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)],weight=weightRelative) %>% filter(weightRelative > 0.005)
```
We then generate the plot with `ggraph`: 
```{r}
set.seed(20)
graphToMBONsPlot <- ggraph(graphToMBONs,layout="dh") +
    geom_edge_fan(aes(color=customSupertype.from,width=weightRelative),
                  end_cap = circle(3, "mm"),linejoin = "mitre",linemitre=3,
                   arrow =arrow(length = unit(1, 'mm'),type = "closed")) +
    geom_node_point(aes(color=customSupertype),size=4)+
    geom_node_text(aes(label=type))+theme_paper_map()+
    scale_color_manual(values=c(customGraphPalette,customSupertypePalette))+
    scale_edge_color_manual(name="supertype",values=c(customGraphPalette,customSupertypePalette)) +
    scale_edge_width(range=c(0.2,3),limits=c(0.001,NA),name="relative weight") + 
    guides(edge_color="none") + 
    coord_cartesian(clip = "off")+ 
    theme(legend.position=c(0.9,0.5))

graphToMBONsPlot
```

Save the plot:
```{r}
save_plot(file.path(outputsFolder,"MBON-PPLs-NGraph.svg"),graphToMBONsPlot,nrow=1.3,ncol=1.4)
```

## Bodyids for anatomy plots
### FR2 to PPL107 (panel C)
```{r}
## FR2_L
filter(CXNeurons,type=="FR2_L")$bodyid
```
```{r}
##PPL107_R
filter(mainFFTargetsNeurons,type=="PPL107_R")$bodyid
```
```{r}
## CRE054_R
filter(mainFFTargetsNeurons,type=="CRE054_R")$bodyid
```

### FB8 loop (panel E)
```{r}
## FB8F_a
filter(CXNeurons,type=="FB8F_a_R")$bodyid
```
```{r}
##PPL105_R
filter(mainFFTargetsNeurons,type=="PPL105_R")$bodyid
```
```{r}
## MBON23_R
mb23 <- getTypesTable("MBON23") %>% cxRetyping()
filter(mb23,type=="MBON23_R")$bodyid
```

### FR1 to MBON30 (panel D)
```{r}
## FR1_L
filter(CXNeurons,type=="FR1_L")$bodyid
```
```{r}
## MBON30_R
filter(mainFFTargetsNeurons,type=="MBON30_R")$bodyid
```
```{r}
## PPL102_L
filter(mainFFTargetsNeurons,type=="PPL102_L")$bodyid
```

## Pathways to MBON27 and oviIN (figure supplement 1)
### Network graph (panel A)
We generate a more detailed subgraph for oviIN and MBON27:
```{r}
FCFStoOviMBON27<- getLocalSubgraph(c("FC2B_L","FS1A_L","FS1A_R","FS1B_L","FS1B_R"),
                                   c("oviIN_R","MBON27_R"),CX_outGraphRed,order=1) %>%
    selectSupertypeSet(default_level = 1) %>%
    customOutputSupertype(extraTypes = filter(knownTypesTable,supertype != "CX")$type)  %E>% 
    mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)]) 
```
Then plot it: 
```{r}
FCFStoOviPlot <- standardGraph(FCFStoOviMBON27,layout="sugiyama",
                               pal=c(customGraphPalette,customSupertypePalette))+
    coord_cartesian(clip="off") 
FCFStoOviPlot
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"FCFStoOviINGraph.svg"),FCFStoOviPlot,nrow=1,ncol=1.3)
```


### Bodyid for renderings:
```{r}
## FS1 Neurons
CXNeurons$bodyid[match( c("FS1A_L","FS1A_R","FS1B_L"),CXNeurons$type)]
```
```{r}
## FC2B
CXNeurons$bodyid[match( c("FC2B_L"),CXNeurons$type)]
```
```{r}
## oviIN_R
filter(mainFFTargetsNeurons,type=="oviIN_R")$bodyid
```
```{r}
## MBON27_R
filter(mainFFTargetsNeurons,type=="MBON27_R")$bodyid
```
