---
title: "Type by type analysis figures: used for figure 74"
output: html_notebook
---

This notebook generates the network graphs used to guide the schematic of figure 74 (including the graph shown as figure supplement 1)
## Preparing the environment
```{r}
library(readr)
```


Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source(file.path("..","R","paperTheme.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure74-localNetworks"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```
Loading some data generated in "Outputs-Core.Rmd":
```{r}
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
## Metadata about the main targets
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
## Graph of the outputs reduced to the main partners
CX_outGraphRed <- readRDS(file.path(dataFolder,"output_graph_reduced.rds"))
```

## Preparing the data
Tweaking the metadata, and creating a custom palette for the network graphs to come:
```{r}
mainFFTargetsS <- mainFFTargets %>% 
   rename(type=type.to,databaseType=databaseType.to) %>% 
   supertype() %>% selectSupertypeSet(default_level = 3,
                                      exceptions=list("Terra incognita"=2))

customGraphPalette <- supertype3Palette[names(supertype3Palette) %in%
                                           filter(mainFFConns,
                                                  Path_weight>0.005)$supertype3.to]

extraPal <- p36[!p36 %in% customSupertypePalette & !p36 %in% customGraphPalette]
extraLevs <- unique(mainFFConns$supertype2.to[mainFFConns$supertype3.to=="Terra incognita"])
extraPal <- extraPal[1:length(extraLevs)]
names(extraPal) <- extraLevs
customGraphPalette <- c(customGraphPalette,extraPal,"Source"="red")
```

## PFL neurons
Throughout this script, we'll use the the `plotSubgraph` function, which takes a contributing type and a graph as an input, together with the metadata tables about the strong targets, and reduces the graph to the strong target of the type of interest, with the contributing type in red. For example for PFL1 (figure supplement 1):
```{r}
PFL1Graph <- plotSubgraph("PFL1_L*",
                          graph=CX_outGraphRed,
                          pal=customGraphPalette,
                          conns=mainFFConns,
                          targets=mainFFTargetsS) + coord_cartesian(clip="off")
PFL1Graph
```
Save the figure supplement:
```{r}
save_plot(file.path(outputsFolder,"outputs-Figure74-SI1.svg"),PFL1Graph,base_height = 7,base_width = 8.5)
```
Extracting the graph and different nodes to be used in the SI video:
```{r}
PFL1Raw <- plotSubgraph_subgraph("PFL1_L*",
                                 graph=CX_outGraphRed,
                                 conns=mainFFConns,
                                 targets=mainFFTargetsS) 

contraWed <- PFL1Raw %N>% filter(type %in% c("LAL138_R",filter(.E(),type.from=="LAL138_R")$type.to)) %>% as_tibble()

crissCross <- PFL1Raw %>% convert(to_local_neighborhood,which(.N()$type %in% c("LAL086_R","LAL087_R")),mode="out",order=4) %N>% as_tibble()

ipsiWed <- PFL1Raw %N>% filter(!(type %in% c(contraWed$type,crissCross$type,"PFL1_L*"))) %>% as_tibble() 
```

Then finding bodyids (on the side of the brain with the most instances)
```{r}
PFL1_RNeurons <-  filter(CXNeurons,type=="PFL1_R*")
PFL1_LNeurons <- filter(CXNeurons,type=="PFL1_L*")

## Both for outputs of PFL1_R*
contraWedNeurons <-  getTypesTable(contraWed$databaseType) %>%
  cxRetyping() %>%
  filter(type %in% lrInvert(contraWed$type))

crissCrossNeurons <- getTypesTable(crissCross$databaseType) %>%
  cxRetyping() %>%
  filter(type %in% lrInvert(crissCross$type))

## For PFL1_L*
ipsiWedNeurons <- getTypesTable(ipsiWed$databaseType) %>%
  cxRetyping() %>%
  filter(type %in% ipsiWed$type)
```

```{r}
write_csv(PFL1_RNeurons,"PFL1_R.csv")
write_csv(PFL1_LNeurons,"PFL1_L.csv")

write_csv(contraWedNeurons,"contraLateral_wedge.csv")
write_csv(ipsiWedNeurons,"ipsi_wedgePLP.csv")
write_csv(crissCrossNeurons,"interHemisphericMotifs.csv")
```


We proceed to run the same for most CX output neurons:
```{r}
PFL2Graph <- plotSubgraph(c("PFL2_L","PFL2_R"),
                          graph=CX_outGraphRed,
                          conns=mainFFConns,
                          pal=customGraphPalette,
                          targets=mainFFTargetsS) + coord_cartesian(clip="off")
PFL2Graph
```

```{r}

PFL3Graph <- plotSubgraph(c("PFL3_L*"),graph=CX_outGraphRed,influenceThreshold = 0.01,
                          conns=mainFFConns,
                          pal=customGraphPalette,
                          targets=mainFFTargetsS) + coord_cartesian(clip="off")
PFL3Graph
```
Selection of types for video:
```{r}
DNTypes <- c("DNb01_2_R",paste0("DNa0",2:4,"_R"),"DNa03_L"))
LALTypes <- c(DNTypes,"LAL010_R","LAL046_R","LAL194_R","LAL195_R","AOTU42_R","AOTU019_R")

DNsGroup <- filter(mainFFTargetsNeurons,
                   type.to %in% c("DNb01_2_R",paste0("DNa0",2:4,"_R"),"DNa03_L"))
```



## FS neurons

```{r}
FS1Graph <- plotSubgraph(c("FS1A_L","FS1B_L"),graph=CX_outGraphRed,
                         conns=mainFFConns,
                         targets=mainFFTargetsS,
                         pal=customGraphPalette,
                         layout="stress") + coord_cartesian(clip="off")
FS1Graph
```

```{r}
FS2Graph <- plotSubgraph(c("FS2_L","FS2_R"),graph=CX_outGraphRed,
                         conns=mainFFConns,
                         pal=customGraphPalette,
                         targets=mainFFTargetsS,
                         layout="stress") + coord_cartesian(clip="off")
FS2Graph
```

```{r}
FS3Graph <- plotSubgraph(c("FS3_L"),graph=CX_outGraphRed,layout="stress",influenceThreshold = 0.001,
                         conns=mainFFConns,
                         targets=mainFFTargetsS,
                         pal=customGraphPalette) + coord_cartesian(clip="off")
FS3Graph
```
```{r}
FS4AGraph <- plotSubgraph(c("FS4A_L"),graph=CX_outGraphRed,layout="stress",influenceThreshold = 0.001,
                          conns=mainFFConns,
                          pal=customGraphPalette,
                          targets=mainFFTargetsS) + coord_cartesian(clip="off")
FS4AGraph
```
```{r}
FS4BGraph <- plotSubgraph(c("FS4B_L"),graph=CX_outGraphRed,layout="stress",influenceThreshold = 0.001,
                          conns=mainFFConns,
                          pal=customGraphPalette,
                          targets=mainFFTargetsS) + coord_cartesian(clip="off")
FS4BGraph
```
```{r}
FS4CGraph <- plotSubgraph(c("FS4C_L"),graph=CX_outGraphRed,layout="stress",influenceThreshold = 0.001,
                          conns=mainFFConns,
                          pal=customGraphPalette,
                          targets=mainFFTargetsS) + coord_cartesian(clip="off")
FS4CGraph
```


## FC neurons
```{r}
FCGraph <- plotSubgraph(c("FC1C_L","FC1E_L","FC2A_L","FC2B_L","FC2C_L"),graph=CX_outGraphRed,layout="stress",
                        conns=mainFFConns,
                        pal=customGraphPalette,
                        targets=mainFFTargetsS) + coord_cartesian(clip="off")
FCGraph
```



## PFR neurons
```{r}
PFRGraph <- plotSubgraph(c("PFR_b_L*"),graph=CX_outGraphRed,layout="stress",
                         conns=mainFFConns,
                         pal=customGraphPalette,
                         targets=mainFFTargetsS) + coord_cartesian(clip="off")
PFRGraph
```

## FR neurons
```{r}
FRGraph <- plotSubgraph(c("FR1_L","FR2_L"),graph=CX_outGraphRed,layout="stress",
                        conns=mainFFConns,
                        pal=customGraphPalette,
                        targets=mainFFTargetsS) + coord_cartesian(clip="off")
FRGraph
```

## ExR7/8 neurons

```{r}
ExR8Graph <- plotSubgraph(c("ExR8_R","ExR7_R","ExR7_L"),graph=CX_outGraphRed,layout="stress",
                          conns=mainFFConns,
                          pal=customGraphPalette,
                          targets=mainFFTargetsS) + coord_cartesian(clip="off")
ExR8Graph
```
## ExR2-6 neurons
```{r}
ExR26Graph <- plotSubgraph(c("ExR2_R","ExR3_R","ExR2_R","ExR6_R"),graph=CX_outGraphRed,
                           conns=mainFFConns,
                           pal=customGraphPalette,
                           targets=mainFFTargetsS,layout="stress") + coord_cartesian(clip="off")
ExR26Graph
```




