---
title: "Breakdown of synapse locations (figure 59 supplement 3 to 5)"
output: html_notebook
---

## Prepare the environment
Loading output display functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source(file.path("..","R","paperTheme.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- file.path("figure59-OutputsModularity","synapseLocSupplement")
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```
Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder <- "data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
## The CX outputs synapses
CXOutSyn <- readRDS(file.path(dataFolder,"CX-outsideSynapses.rds"))
## The synapses of the main output targets
CXTargetsSyn <- readRDS(file.path(dataFolder,"CX-targets-synapses.rds"))
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
## Metadata about the targets
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
```

## Preparing the data
We enrich the data frame of the synapses of the main targets by some metadata, mostly to know which CX output neuron contributes the most to each target:
```{r}
CXTargetsSyn <- mutate(CXTargetsSyn,
                       type=mainFFTargetsNeurons$type[match(bodyid,mainFFTargetsNeurons$bodyid)],
                       mainContributor=mainFFConns$mainContributor[match(type,mainFFConns$type.to)],
                       mainContributor_data=mainFFConns$mainContributor_data[match(type,mainFFConns$type.to)])


CXTargetsSyn <- mutate(CXTargetsSyn,
                       customContributor=CXOutputNeurons$customSupertype[match(mainContributor,
                                                                               CXOutputNeurons$type)])
```

Throughout this notebook, we'll use the `displaySynapses3D` function, defined in "outputFunctions-display" repeatedly. It takes as inputs a synapses data frame, a choice of ROIs to render a variable (of the synapses data frame) to cluster the synapses upon (here the supertype or the main contributor), and information about the palette to use and the file where to save the results. The function saves two views of the rendering. We also generate a legend panel for each type.  Note that the display in the final figure was generated using NeuTu rather than this code.

## PFLs
### Their synapses
```{r}
displaySynapses3D(synapses=filter(CXOutSyn,
                                 customSupertype %in% c("PFL1","PFL2","PFL3")),
                 ROIs = c("LAL(R)","CRE(R)"),
                 saveName = "PFLs",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customSupertype",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```

### Synapses of their main targets

```{r}
displaySynapses3D(synapses=filter(CXTargetsSyn,customContributor %in% c("PFL1","PFL2","PFL3")),
                 ROIs = c("LAL(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "PFLTargets",
                 synapsePalette = customSupertypePalette,
                 saveFolder = outputsFolder,
                 synapseCluster = "customContributor",
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)

```

### Legend
```{r}
legendSourcePF <- cowplot::get_legend(ggplot(filter(CXOutputNeurons,
                                                    customSupertype %in% c("PFL1","PFL2","PFL3")),
                                             aes(x=1,y=customSupertype)) +
                                         geom_point(aes(color=customSupertype)) + 
                                         theme_paper_map() +
                                         scale_color_manual(name="type",values=customSupertypePalette))
```

```{r}
save_plot(file.path(outputsFolder,"legendPFLSyns.svg"),legendSourcePF,nrow=0.3,ncol=0.1)
```


## FSs
### Their synapses
```{r}
displaySynapses3D(synapses=filter(CXOutSyn,
                                 customSupertype %in% c("FS1","FS2","FS3","FS4")),
                 ROIs = c("CRE(R)","SMP(R)"),
                 saveName = "FSs",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customSupertype",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```
### Synapses of their main targets
```{r}
displaySynapses3D(synapses=filter(CXTargetsSyn,
                                 customContributor %in% c("FS1","FS2","FS3","FS4")),
                 ROIs = c("LAL(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "FSTargets",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customContributor",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)

```

### Legend
```{r}
legendSourceFS <- cowplot::get_legend(ggplot(filter(CXOutputNeurons,
                                                    customSupertype %in% c("FS1","FS2","FS3","FS4")),
                                             aes(x=1,y=customSupertype)) +
                                         geom_point(aes(color=customSupertype)) + 
                                         theme_paper_map() +
                                         scale_color_manual(name="type",
                                                            values=customSupertypePalette))
```

```{r}
save_plot(file.path(outputsFolder,"legendFSSyns.svg"),legendSourceFS,nrow=0.3,ncol=0.1)
```

## FCs
### Their synapses
```{r}
displaySynapses3D(synapses=filter(CXOutSyn,
                                 customSupertype %in% c("FC1","FC2")),
                 ROIs = c("CRE(R)","SMP(R)"),
                 saveName = "FCs",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customSupertype",
                 saveFolder=outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```
### Synapses of their main targets
```{r}
displaySynapses3D(synapses=filter(CXTargetsSyn,
                                 customContributor %in% c("FC1","FC2")),
                 ROIs = c("LAL(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "FCTargets",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customContributor",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```
### Legend
```{r}
legendSourceFC <- cowplot::get_legend(ggplot(filter(CXOutputNeurons,
                                                    customSupertype %in% c("FC1","FC2")),
                                             aes(x=1,y=customSupertype)) +
                                         geom_point(aes(color=customSupertype)) + 
                                         theme_paper_map() +
                                         scale_color_manual(name="type",
                                                            values=customSupertypePalette))
```

```{r}
save_plot(file.path(outputsFolder,"legendFCSyns.svg"),legendSourceFC,nrow=0.3,ncol=0.1)
```

## PFR neurons
### Their synapses
```{r}
displaySynapses3D(synapses=filter(CXOutSyn,
                                 customSupertype %in% c("PFR_b","PFR_a")),
                 ROIs = c("CRE(R)"),
                 saveName = "PFRs",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customSupertype",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```

### Synapses of their main targets
```{r}
displaySynapses3D(synapses=filter(CXTargetsSyn,
                                 customContributor %in% c("PFR_b","PFR_a")),
                 ROIs = c("LAL(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "PFRTargets",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customContributor",
                 saveFolder=outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```

### Legend
```{r}
legendSourcePFR <- cowplot::get_legend(ggplot(filter(CXOutputNeurons,
                                                     customSupertype %in% c("PFR_a","PFR_b")),
                                              aes(x=1,y=customSupertype)) +
                                          geom_point(aes(color=customSupertype)) + 
                                          theme_paper_map() +
                                          scale_color_manual(name="type",
                                                             values=customSupertypePalette))
```

```{r}
save_plot(file.path(outputsFolder,"legendPFRSyns.svg"),legendSourcePFR,nrow=0.3,ncol=0.1)
```

## ExRs
### Their synapses
```{r}
displaySynapses3D(synapses=filter(CXOutSyn,
                                 customSupertype %in% c("ExR1","ExR2-6","ExR7","ExR8")),
                 ROIs = c("BU(R)","LAL(R)","SPS(R)","WED(R)","CRE(R)"),
                 saveName = "ExRs",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customSupertype",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```

### Synapses of their main targets
```{r}
displaySynapses3D(synapses=filter(CXTargetsSyn,
                                 customContributor %in% c("ExR1","ExR2-6","ExR7","ExR8")),
                 ROIs = c("LAL(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "ExRTargets",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customContributor",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```

### Legend
```{r}
legendSourceExR <- cowplot::get_legend(ggplot(filter(CXOutputNeurons,
                                                     customSupertype %in% c("ExR1","ExR2-6","ExR7","ExR8")),
                                              aes(x=1,y=customSupertype)) +
                                          geom_point(aes(color=customSupertype)) +
                                          theme_paper_map() +
                                          scale_color_manual(name="type",
                                                             values=customSupertypePalette))
```

```{r}
save_plot(file.path(outputsFolder,"legendExRSyns.svg"),legendSourceExR,nrow=0.3,ncol=0.1)
```

## FRs
### Their synapses
```{r}
displaySynapses3D(synapses=filter(CXOutSyn,
                                 customSupertype %in% c("FR1","FR2")),
                 ROIs = c("CRE(R)"),
                 saveName = "FRs",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customSupertype",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```
### Synapses of their main targets

```{r}
displaySynapses3D(synapses=filter(CXTargetsSyn,
                                 customContributor %in% c("FR1","FR2")),
                 ROIs = c("LAL(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "FRTargets",
                 synapsePalette = customSupertypePalette,
                 synapseCluster = "customContributor",
                 saveFolder = outputsFolder,
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2)
```
### Legend
```{r}
legendSourceFR <- cowplot::get_legend(ggplot(filter(CXOutputNeurons,
                                                    customSupertype %in% c("FR1","FR2")),
                                             aes(x=1,y=customSupertype)) + 
                                         geom_point(aes(color=customSupertype)) + 
                                         theme_paper_map() +
                                         scale_color_manual(name="type",
                                                            values=customSupertypePalette))
```

```{r}
save_plot(file.path(outputsFolder,"legendFRSyns.svg"),legendSourceFR,nrow=0.3,ncol=0.1)
```
