---
title: "Visual PNs outputs, figure 62"
output: html_notebook
---

## Preparing the environment

Loading some local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source("outputFunctions-core.R")
source(file.path("..","R","paperTheme.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure62-OutputsToVisual"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
## Known types in the output graph
knownTypesTable <- readRDS(file.path(dataFolder,"known-table.rds"))
## The table of pathway weights
CXoutFull <- readRDS(file.path(dataFolder,"pathwayWeightsTable.rds"))
## The full outputs graph (and bilateral graph)
CX_outGraph <- readRDS(file.path(dataFolder,"output_graph.rds"))
CX_outGraphBi <- readRDS(file.path(dataFolder,"output_graph_FullBilateral.rds"))
## Metadata about the main targets
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
```

## Preparing some data
A palette to be used in network graphs:
```{r}
customGraphPalette <- supertype3Palette[names(supertype3Palette) %in% filter(mainFFConns,
                                                                             Path_weight>0.005)$supertype3.to]
extraPal <- p36[!p36 %in% customSupertypePalette & !p36 %in% customGraphPalette]
extraLevs <- unique(mainFFConns$supertype2.to[mainFFConns$supertype3.to=="Terra incognita"])
extraPal <- extraPal[1:length(extraLevs)]
names(extraPal) <- extraLevs
customGraphPalette <- c(customGraphPalette,extraPal,customSupertypePalette)
```

## Visual PNs in the strong targets network (panel A)
We select from the pathway weight table all visual PN types that receive at least 0.05% pathway weight from the CX. We also customize the supertypes to the most common CX output types present in that table: 
```{r}

CXoutFFEndpointVPNs <- filter(CXoutFull,(supertype3.to == "Visual PNs") & 
                                fullCXwr>0.0005) %>%
  mutate(supertype.to=knownTypesTable$supertype[match(type.to,
                                                      knownTypesTable$type)],
         supertype.from=CXOutputNeurons$supertype[match(databaseType.from,
                                                        CXOutputNeurons$databaseType)],
         customSupertype = case_when(supertype.from %in% c("PFL") ~ databaseType.from,
                                     grepl("ExR8",supertype.from) ~ as.character(supertype.from),
                                     type.from %in% c("PFR_b_L*") ~ databaseType.from,
                                     TRUE ~ "Other")
  )
head(CXoutFFEndpointVPNs)
```
Then generate the plot:
```{r}
moreVPNsPlot <- ggplot(CXoutFFEndpointVPNs,aes(x=type.to,y=Path_weight)) + 
  geom_col(aes(fill=customSupertype))+ 
  scale_fill_manual(name="source type",
                    values=c(customSupertypePalette,"Other"="grey90"))+
  theme_paper(axis.text.x = element_text(angle=90,hjust = 1,vjust=0.5),
              strip.text.x = element_text(angle=60),
              strip.background.x = element_rect(fill="grey90")) +  
  ylab("total pathway weight") + xlab("target type") 
  
moreVPNsPlot
```
And save it:
```{r}
save_plot(file.path(outputsFolder,"VPNTargets.svg"),moreVPNsPlot,nrow=0.5,ncol=0.6)
```

## PFL3 to LC33 (panels B and C)
### Network graph
We use `getLocalSubgraph` to extract all neurons in PFL3 to LC33 pathways in 2 steps or less. We also do some retyping to ease the mapping of existing palettes in the plot: 
```{r}
PFLtoLC33 <- getLocalSubgraph(c("PFL3_L*"),c("LC33_R"),
                              CX_outGraph,order=1) %>% 
    selectSupertypeSet(default_level = 1)  %>%
    customOutputSupertype(extraTypes = filter(knownTypesTable,supertype != "CX")$type)  %E>% 
    mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)],weight=weightRelative) %>% filter(weightRelative > 0.005)
PFLtoLC33
```

We then generate the plot using `standardGraph`, defined in **outputFunctions-display.R**, which is a shortcut for calling `ggraph` with our standard set of parameters
```{r}
PFLtoLC33Plot <- standardGraph(PFLtoLC33,pal = customGraphPalette,layout="stress")
PFLtoLC33Plot
```


And save it: 
```{r}
save_plot(file.path(outputsFolder,"PFL3-LC33-NGraph.svg"),PFLtoLC33Plot,nrow=0.4,ncol=0.6)
```

### Bodyids for renderings
LC33 neurons connected to PFL3:
```{r}
specialLC33 <- c(1260197431,5813022538,1418186940)
```
Other LC33 neurons:
```{r}
filter(mainFFTargetsNeurons,type=="LC33_R" & !bodyid %in% specialLC33)$bodyid
```
PFL3 neurons:
```{r}
filter(CXNeurons,type=="PFL3_L*")$bodyid
```
LAL141_R:
```{r}
filter(mainFFTargetsNeurons,type=="LAL141_R")$bodyid
```

### Details of PFL3 to LC33 connectivity (figure supplement 2)
Gathering output connectivity for PFL3, reorder them by FB column:
```{r}
PFL3Bag <- neuronBag(filter(CXNeurons,type=="PFL3_L*"),
                     selfRef = T,
                     slctROI=outsideRegions,omitInputs = T,renaming = cxRetyping) %>%
  combineRois(outsideRegions,"Outside")

orderPFL3Name <- c("PFL3(PB12c)_R2_C1_irreg","PFL3(PB12c)_R1_C2_irreg",
                   "PFL3(PB12c)_L1_C3","PFL3(PB12c)_L2_C4",
                   "PFL3(PB12c)_L3_C5","PFL3(PB12c)_L4_C6",
                   "PFL3(PB12c)_L5_C7","PFL3(PB12c)_L6_C8","PFL3(PB12c)_L7_C9")
PFL3s <- PFL3Bag$names %>% 
  mutate(name=factor(name,levels=orderPFL3Name)) %>% 
  arrange(name)
orderPFL3BI <- PFL3s$bodyid
```
Then plot the PFL3 to PF3 direct connectivity:
```{r}
PFL32LC33Mat <- plotConnectivity(filter(PFL3Bag$outputs_raw,type.to=="LC33_R")
                                 ,grouping="neuron",
                                 orderIn = orderPFL3BI,xaxis="outputs",
                                 replacementLabels = "name",
                                 legendName="relative weight",theme=theme_paper()) + 
  xlab("postsynaptic neuron") + ylab("presynaptic neuron")
PFL32LC33Mat
```
Save the plot:
```{r}
save_plot(file.path(outputsFolder,"PFL3toLC33Mat.svg"),PFL32LC33Mat,nrow=0.6,ncol=0.5)
```

Retype 1260197431 5813022538 and 1418186940 (the LC33 strongly connected to PFL3) for a look at the shared outputs between those neurons and PFL3 neurons. To do that we create a `specialRenaming` function, that can be used as argument to the `neuronBag` function (which we run for LC33 outputs):
```{r}
specialRenaming <- function(connections,postfix=c("raw", "to", "from")){
  connections <- redefineTypeByBodyId(connections,sets=list(1566597156,1655997973),
                                      nameModifiers=c("_1_R","_2_R"),
                                      postfix=postfix,redefinePartners=T)
  connections <- redefineTypeByBodyId(connections,sets=list(c(1260197431,5813022538,1418186940)),
                                      nameModifiers=c("_b_R"),postfix=postfix,redefinePartners=T)
  connections <- cxRetyping(connections,postfix=postfix)
}

LC33Bag <- neuronBag("LC33",omitInputs=TRUE,renaming=specialRenaming) %>% combineRois(outsideRegions,"Outside")
```

We then plot the special LC33 outputs matrix side by side with the PFL3 outputs matrix:
```{r}
PFLLCOutMat <- plotConnectivity(filter(rbind(PFL3Bag$outputs_raw,
                                             filter(LC33Bag$outputs_raw,
                                                    type.from=="LC33_b_R")),
                                       supertype2.to != "Unassigned"),
                                facetInputs="type.from",facetOutputs="supertype2.to",
                                grouping="neuron",replacementLabels = "name",
                                legendName="relative weight",theme=theme_paper_grid_rects(),
                                switch="x") + 
  xlab("presynaptic neuron") + ylab("postsynaptic neuron")+ 
  theme(strip.text.y = element_text(angle=0),
        axis.text.x = element_blank(),axis.text.y=element_blank())
PFLLCOutMat
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"PFL3andLC33Shared.svg"),PFLLCOutMat,nrow=2.8,ncol=0.8)
```

## The LC10 connection (panels D and E)
### Network graph
For display purposes, we use a manual graph layout, so we build the graph directly from the neurons we found in the network and assign x/y positions: 
```{r}
PFL3ToLC10<-as_tbl_graph(induced_subgraph(CX_outGraphBi,
                                          c("PFL3_L*","PFL3_R*","LC10_R",
                                            "AOTU042_L","AOTU019_R"))) %N>% 
  mutate(x=case_when(type %in% c("LC10_R")~0.3,
                     type=="PFL3_L*"~0.6,
                     type %in% c("AOTU042_L","AOTU019_R") ~1,
                     type=="PFL3_R*"~1.4),
         y=case_when(type == "LC10_R"~0.7,
                     type=="AOTU019_R"~0.7,type=="AOTU042_L"~0.3,
                     type %in%c("PFL3_L*","PFL3_R*") ~1)) %>% 
    selectSupertypeSet(default_level = 1)  %>%
    customOutputSupertype(extraTypes = filter(knownTypesTable,supertype != "CX")$type)  %E>% 
    mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)],weight=weightRelative) %>% filter(weightRelative > 0.005)

## How we found the neurons in the graph
#getLocalSubgraph(c("PFL3_L*","PFL3_R*","LC10_R"),c("LC10_R"),CX_outGraphBi,order=1) 
```
We then plot the graph:
```{r}
PFL3ToLC10Plot <- standardGraph(PFL3ToLC10,
                                pal=customGraphPalette,
                                layout="manual",x=x,y=y) + 
  geom_vline(xintercept = 1,lty=2,color="grey50")
PFL3ToLC10Plot
```


Then save it:
```{r}
save_plot(file.path(outputsFolder,"PFL3-LC10-NGraph.svg"),PFL3ToLC10Plot,nrow=0.4,ncol=0.6)
```

### Bodyids for renderings
Getting the LC10 connection tables to assess the importance of their connectivity:
```{r}
LC10Bag <- neuronBag("LC10",by.roi=FALSE,renaming=customRetyping)
```

All connected LC10 neurons, ordered by connection strength with AOTU42:
```{r}
LC10Body <- arrange(filter(LC10Bag$inputs_raw,type.from=="AOTU042_L"),desc(weightRelative))
head(LC10Body)
```
Strongly connected LC10 neurons:
```{r}
LC10Body$to[1:10]
```
Example weakly connected LC10 neurons:
```{r}
LC10Body$to[300:310]
```
Example unconnected LC10:
```{r}
LC10Other <- filter(LC10Bag$names,!(bodyid %in% LC10Body$from))
LC10Other$bodyid[1:2]
```
PFL3_R neurons:
```{r}
(getTypesTable("PFL3") %>% customRetyping() %>% filter(type=="PFL3_R*"))$bodyid
```

## PFL1 to LC27 connection (panels F and G)
### Network graph
We proceed the same way we did for panels B and C:
```{r}
PFL1ToLC27 <- getLocalSubgraph(c("PFL1_L*"),c("LC27_R"),CX_outGraphBi,order=2) %>% 
    selectSupertypeSet(default_level = 1)  %>%
    customOutputSupertype(extraTypes = filter(knownTypesTable,supertype != "CX")$type)  %E>% 
    mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)],weight=weightRelative) %>% filter(weightRelative > 0.005)
PFL1ToLC27
```

```{r}
PFL1ToLC27Plot <- standardGraph(PFL1ToLC27,pal=customGraphPalette,layout="stress")
PFL1ToLC27Plot
```


Save the graph:
```{r}
save_plot(file.path(outputsFolder,"PFL1-LC27-NGraph.svg"),PFL1ToLC27Plot,nrow=0.4,ncol=0.5)
```

### Bodyids used for renderings
LC27 neurons:
```{r}
LC27Body <- neuprint_search("LC27",field="type")
LC27Body$bodyid[1:10]
```
LAL047:
```{r}
filter(mainFFTargetsNeurons,type %in% c("LAL047_R"))$bodyid
```
PLP077:
```{r}
filter(mainFFTargetsNeurons,type %in% c("PLP077_L"))$bodyid
```
PFL1:
```{r}
filter(CXOutputNeurons,type=="PFL1_L*")$bodyid
```

## ExR8 to VCH/DCH connection (panels H and I)
We build the network graph the same way:
```{r}
ExR8toCH<- getLocalSubgraph(c("ExR8_R"),c("VCH_L","DCH_L"),CX_outGraphBi,order=1) %>% 
    selectSupertypeSet(default_level = 1)  %>%
    customOutputSupertype(extraTypes = filter(knownTypesTable,supertype != "CX")$type)  %E>% 
    mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)],weight=weightRelative) %>% filter(weightRelative > 0.005)
ExR8toCH
```

```{r}
ExR8toCHPlot <- standardGraph(ExR8toCH,pal=customGraphPalette,layout="stress")
ExR8toCHPlot
```

And save the plot:
```{r}
save_plot(file.path(outputsFolder,"ExR8-CH-NGraph.svg"),ExR8toCHPlot,nrow=0.5,ncol=0.5)
```

### Bodyids for renderings
ExR8
```{r}
filter(CXNeurons,type=="ExR8_R")$bodyid
```
CH
```{r}
filter(mainFFTargetsNeurons,type%in% c("DCH_L","VCH_L"))$bodyid
```
PS047:
```{r}
filter(mainFFTargetsNeurons,type=="PS047_R")$bodyid
```

## PFR_b to LT/MC connection (figure supplement 1)
### Network graph:
```{r}
PFRbToLTMC <- getLocalSubgraph(c("PFR_b_L*"),
                               c("LT85_R","MC62_R","LC29_R"),CX_outGraphBi,order=2) %>% 
    selectSupertypeSet(default_level = 1)  %>%
    customOutputSupertype(extraTypes = filter(knownTypesTable,supertype != "CX")$type)  %E>% 
    mutate(customSupertype.from = .N()$customSupertype[match(type.from,.N()$type)],weight=weightRelative) %>% filter(weightRelative > 0.005)
```

```{r}
PFRbToLTMCPlot <- standardGraph(PFRbToLTMC,pal=customGraphPalette,layout="stress") +
  scale_y_continuous(trans="reverse")

PFRbToLTMCPlot
```
```{r}
save_plot(file.path(outputsFolder,"PFRb-Visual-NGraph.svg"),PFRbToLTMCPlot,nrow=0.5,ncol=1)
```

### Bodyids for renderings:
MBON20:
```{r}
filter(mainFFTargetsNeurons,type=="MBON20_R")$bodyid
```
LT85:
```{r}
LT85Body <- getTypesTable("LT85")
LT85Body$bodyid
```
MC62:
```{r}
MC62Body <- getTypesTable("MC62")
MC62Body$bodyid[1:5]
```
mALD1:
```{r}
filter(mainFFTargetsNeurons,type=="mALD1_L")$bodyid
```
