---
title: "Connectivity of the GA/GAs/ROB/RUB (figure 56)"
output: html_notebook
---

## Preparing the environment

Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
source("outputFunctions-core.R")
source(file.path("..","R","paperTheme.R"))
source(file.path("..","R","table2ggraphUtils.R"))
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure56-GAROBRUB"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```

Loading some data generated in "Outputs-Core.Rmd":
```{r}
# Basic metadata:
load(file.path(dataFolder,"outputsBasics.RData"))
# Pathway of normalized weights to the CX table
CXInfluence <- readRDS(file.path(dataFolder,"cx-influence.rds"))

# The network graph reduced to the most important targets
CX_outGraphRed <- readRDS(file.path(dataFolder,"output_graph_reduced.rds"))

# Metadata about the main targets
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
```



## The synapses labeled by their target influence (panel A)
We're mainly going to use the `CXInfluence` object, which quantifies how much of the pathways coming out of the central complex are actually ending on other CX types (see the "Outputs-Core" notebook, line 257).

For all CX output neurons, we're going to label their synapses by the fraction the postsynaptic neuron contributes to pathways ending in the central complex.
For all neurons in the graph, we calculate their total path weight contributions to CX neurons (`totalOC` for total output contribution). 
```{r}
CXInfluenceFullSummary <- group_by(CXInfluence,type.from) %>% 
  summarize(totalOC=sum(Path_weight)) %>% 
  ungroup() 
## If the target is itself a central complex neuron, then this means 100% of the circuit post-synaptic to this synapse ends in the central complex
CXInfluenceFullSummary$totalOC[CXInfluenceFullSummary$type.from %in% CXNeurons$type] <- 1
```

We then read the synapses (generated in "Outputs-Core.Rmd"), and create a data frame of the neurons directly post-synaptic to those:
```{r}
CXOutSyn <- readRDS(file.path(dataFolder,"CX-outsideSynapses.rds"))

allTargets <- neuprint_get_meta(CXOutSyn$partner) %>% 
  mutate(databaseType=type) %>% 
  customRetyping() %>% 
  supertype() %>% 
  selectSupertypeSet(default_level = 1) %>%  
  customOutputSupertype(postfix="raw")
head(allTargets)
```

We then add the output contribution to the synapses data frame, discretize it and create a palette for plotting: 
```{r}
CXOutSyn <- mutate(CXOutSyn,
                   partnerType=allTargets$type[match(partner,allTargets$bodyid)],
                   totalOC=CXInfluenceFullSummary$totalOC[match(partnerType,CXInfluenceFullSummary$type.from)]) %>%
  na.omit() %>%
  mutate(colLevs = cut(totalOC,breaks=seq(0,1,length.out=100),labels=1:99))
            

cPal <- paletteer_c("viridis::plasma",n=100)
names(cPal) <- 1:99

head(CXOutSyn)
```

Rendering (and saving) the synapses (note that the display in the final figure was generated using NeuTu rather than this code):
```{r}
displaySynapses3D(synapses=CXOutSyn,
                 ROIs=c("EB","FB","PB","NO","LAL(R)","BU(R)","CRE(R)","SMP(R)","WED(R)","SLP(R)","SIP(R)","SPS(R)","IPS(R)"),
                 saveName = "allOuts-CX2CXLab",
                 synapsePalette = cPal,
                 synapseCluster = "colLevs",
                 saveFolder = outputsFolder,
                 windowSize = c(3000,3000),
                 type="s",
                 specular="black",
                 diffuse="black",
                 ambient="black",
                 lwd=0,
                 size=0.2
                 )

```

We then create the legend for this panel:
```{r}
legendSource <- cowplot::get_legend(ggplot(data.frame(x=1,y=1,c=0.5),aes(x=1,y=1)) +
                                      geom_point(aes(color=c)) + theme_paper_map() +
                                      scale_color_paletteer_c("viridis::plasma",limits=c(0,1),
                                                              name="CX to CX fraction"))
```
Saving the legend:
```{r}
save_plot(file.path(outputsFolder,"legend_CX2CX.svg"),legendSource,ncol = 0.2,nrow=0.5)
```

## Composition and importance of the CX to CX connections in those neuropils (panel B)
In this figure we restrict our analysis to a few CX types innervating those regions:
```{r}
localNeuropileNeurons <- c("EL","EPG","PEG","ER6","ExR1","ExR2","ExR3","ExR5","ExR6","PFR_a","PFR_b","FR1","FR2")
```

We summarize the influence of those types exert by supertype:
```{r}
CXInfluenceLocal <- filter(CXInfluence,databaseType.from %in% localNeuropileNeurons) %>% 
  group_by(supertype3.to,type.from,supertype3.from) %>%
  summarize(Path_weight=sum(Path_weight)) %>% 
  ungroup()
head(CXInfluenceLocal)
```
Generate panel B from this table. `supertype3Palette` is a custom palette defined in "outputFunctions-display.R" to be used throughout the section: 
```{r}
backCXCompositionLocal <- ggplot(CXInfluenceLocal,aes(x=type.from,y=Path_weight)) + 
  geom_col(aes(fill=supertype3.to)) + 
  scale_fill_manual(name="target supertype",values=supertype3Palette)+ 
  theme_paper() + 
  theme(strip.text.x=element_blank(),axis.text.x = element_text(angle=90,hjust =1,vjust=0.5))+
  facet_grid(.~supertype3.from,scales = "free",space="free") + 
  ylab("normalized pathway weight") + 
  xlab("CX output type")

backCXCompositionLocal
```
Save the plot:
```{r}
save_plot(file.path(outputsFolder,"outputs-CXInfluenceCompositionLocal.svg"),backCXCompositionLocal,ncol=0.5,nrow=6,base_width = 8.5,base_height = 11/35)
```

## Connectivity matrix of the main GA types (panel D)
Since the Gall is a badly defined region, we can't easily collect neurons that go to the Gall based in the EM ROI. 
We therefore select a subset of neurons that we consider as arborizing in the gall and get all their connections in regions outside of the CX (on the right side of the brain):
```{r}
gallSlctTypes <-   c("EPG","PEG","EL","PFGs","ER6","EPGt")
gallSlctIDs <- getTypesTable(gallSlctTypes)

GABag <- neuronBag(gallSlctIDs,
                   slctROI=outsideRegions,
                   omitInputs = T,renaming = cxRetyping) %>% 
  combineRois(outsideRegions,"Outside")
```

We then filter the raw connection table to just those types, and get neurons orders by column for the plot to come:
```{r}
GAConnections <- filter(GABag$outputs_raw,databaseType.to %in% gallSlctTypes)%>% 
  mutate(glomerulus.from=factor(gsub("_","",str_extract(name.from,"_[L|R][1-9]")),
                                levels=c(paste0("L",1:9),paste0("R",9:1))),
         glomerulus.to=factor(gsub("_","",str_extract(name.to,"_[L|R][1-9]")),
                              levels=c(paste0("L",1:9),paste0("R",9:1)))) %>%
  arrange(type.from,glomerulus.from)

orderIn <- unique(GAConnections$from)

GAConnections <- arrange(GAConnections,type.to,glomerulus.to)

orderOut <- unique(GAConnections$to)
```

Finally we plot the connectivity matrix:
```{r}
GAMatPlot <-  plotConnectivity(GAConnections, 
                              grouping =  "bodyid",
                              facetInputs = "type.from",
                              facetOutputs = "type.to",
                              orderIn = orderIn,
                              orderOut = orderOut,
                              legendName = "relative weight",
                              theme = theme_paper_rects(strip.placement="outside"),
                              switch = "both",
                              flipy_facet=T
                              ) + theme(
                                strip.text.x=element_text(angle=90),
                                strip.text.y.left=element_text(angle=0),
                                axis.text.x=element_blank(),
                                axis.text.y=element_blank(),
                                axis.ticks.x=element_blank(),
                                axis.ticks.y=element_blank()
                              )
GAMatPlot
```

And save it:
```{r}
save_plot(file.path(outputsFolder,"connectivityMatrixSelect.svg"),GAMatPlot,nrow=0.7,ncol=0.6)
```

## Connectivity graphs in the EB and GA (panel F)
We use the same palette as in the EB section:
```{r}
EBPalTable <- full_join(read.csv(file.path("..","colormaps",paste0("colorMap_RingNeurons.csv"))),
                    read.csv(file.path("..","colormaps",paste0("colorMap_columnar.csv"))))
                    
EBPal <- EBPalTable$hex
names(EBPal) <- EBPalTable$Type
```

### In the GA (panel Fi)

Generate the graph from the type to type connection table and filter it:
```{r}
GAgraph <- makeGraph(GABag$outputs) %N>% 
  filter(databaseType %in% c("EPG","PEG","EL","ER6")) %E>%
  filter(weightRelative > 0.05)
GAgraph
```

Plot it using `standardGraph` (defined in **outputsFunctions-display.R**):
```{r}
GAGraphPlot <- standardGraph(GAgraph,colP = "databaseType",
                             pal=EBPal,loop=T,widthLimits = c(0.05,NA),
                             widthRange = c(0.2,2))

GAGraphPlot
```

```{r}
save_plot(file.path(outputsFolder,"GAGraph.svg"),GAGraphPlot,nrow=0.45,ncol = 0.6)
```

## In the EB (panel Fii)

We select the types of interest, and get their connectivity in the EB:
```{r}
EBBag <- neuronBag(gallSlctIDs %>% filter(databaseType %in% c("PEG","ER6","EL","EPG")),
                   slctROI="EB",
                   omitInputs = T,renaming = cxRetyping) 
```

Generate a graph object and filter it:
```{r}
EBgraph <- makeGraph(EBBag$outputs) %N>% 
  filter(databaseType %in% c("EPG","PEG","EL","ER6")) %E>%
  filter(weightRelative > 0.05)
EBgraph
```

Then generate the graph:
```{r}
EBGraphPlot <- standardGraph(EBgraph,colP = "databaseType",
                             pal=EBPal,loop=T,
                             layout="sugiyama",
                             widthLimits = c(0.05,NA),widthRange = c(0.2,2)) + coord_flip()
EBGraphPlot
```

```{r}
save_plot(file.path(outputsFolder,"EBGraph.svg"),EBGraphPlot,nrow=0.6,ncol = 0.7)
```


## Connectivity in the GA (figure supplement 1, panel A)

We first collect connection tables of all the types innervating the Gall in the gall:
```{r}
gaTable = getTypesInRoiTable("GA(R)", minTypePercentage = 0.5)
```

We then filter the raw connection table to just GA neurons:
```{r}
allGAneurons <-  unique(c(gaTable$outputs$databaseType.from,gaTable$inputs$databaseType.to))
myConnections <- filter(gaTable$inputs_raw,databaseType.to %in% allGAneurons & databaseType.from %in% allGAneurons)
```

And plot the resulting connectivity matrix:
```{r}
conMatPlot <-  plotConnectivity(myConnections, 
                              grouping =  "bodyid",
                              facetInputs = "type.from",
                              facetOutputs = "type.to",
                              legendName = "relative weight",
                              theme = theme_paper_rects(strip.placement="outside"),
                              switch = "both",
                              flipy_facet=T
                              ) + theme(
                                strip.text.x=element_text(angle=90),
                                strip.text.y.left=element_text(angle=0),
                                axis.text.x=element_blank(),
                                axis.text.y=element_blank(),
                                axis.ticks.x=element_blank(),
                                axis.ticks.y=element_blank()
                              )
conMatPlot
```

Then save it:
```{r}
save_plot(file.path(outputsFolder,"connectivityMatrixGA.svg"),conMatPlot,nrow=1.3,ncol=1)
```



### PFR connectivity (figure supplement 2)
#### Intra PFR connectivity (panel A)
We want to plot the connections of PFR neurons between themselves. We first collect their connectivity out of the central complex:
```{r}
PFRBag <- neuronBag(filter(CXOutputNeurons,customSupertype %in% c("PFR_a","PFR_b")),
                    selfRef=T,
                    slctROI=outsideRegions,omitInputs = T,
                    renaming = cxRetyping) %>% 
  combineRois(outsideRegions,"Outside")
```

We then reformat the connection table, restricting it to PFR to PFR interactions, and ordering it by glomerulus of origin:
```{r}
PFRTab <- filter(PFRBag$outputs_raw,supertype2.to=="PFR") %>% 
  mutate(glomerulus.from=factor(gsub("_","",str_extract(name.from,"_[L|R][1-9]_")),
                                levels=c(paste0("L",9:1),paste0("R",1:9))),
         glomerulus.to=factor(gsub("_","",str_extract(name.to,"_[L|R][1-9]_")),
                              levels=c(paste0("L",9:1),paste0("R",1:9)))) %>%
  arrange(glomerulus.from)

orderIn <- unique(PFRTab$from)

PFRTab <- arrange(PFRTab,glomerulus.to)

orderOut <- unique(PFRTab$to)
```

Finally we can plot the matrix:
```{r}
PFRConnPlot <- plotConnectivity(PFRTab,slctROI = "Outside",
                                grouping = "neuron",
                                orderIn=orderIn,orderOut=orderOut,
                                facetInputs = "type.from",facetOutputs = "type.to",
                                xaxis = "outputs",
                                theme = theme_paper_grid_rects(strip.placement = "outside"),
                                replacementLabels = "glomerulus",
                                legendName = "relative weight",
                                switch="both") +
  xlab("postsynaptic neuron, PB glomerulus") + 
  ylab("presynaptic neuron, PB glomerulus") 
 

PFRConnPlot
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"PFRMat.svg"),PFRConnPlot,nrow = 1,ncol=1,base_height = 11/4,base_width=8.5/2)
```

#### PFR outputs network (panel B)
We first add supertypes to the data frame about all the main targets and define a color palette (based off the one used above but adding "terra incognita" types present in the actual graph) to be used in network graphs:
```{r}
mainFFTargetsS <- mainFFTargets %>% 
  rename(type=type.to,databaseType=databaseType.to) %>% 
  supertype() %>% 
  selectSupertypeSet(default_level = 3,
                     exceptions=list("Terra incognita"=2))

customGraphPalette <- supertype3Palette[names(supertype3Palette) %in% filter(mainFFConns, 
                                                                             Path_weight>0.005)$supertype3.to]

extraPal <- p36[!p36 %in% customSupertypePalette & !p36 %in% customGraphPalette]
extraLevs <- unique(mainFFConns$supertype2.to[mainFFConns$supertype3.to=="Terra incognita"])
extraPal <- extraPal[1:length(extraLevs)]
names(extraPal) <- extraLevs

customGraphPalette <- c(customGraphPalette,extraPal,"Source"="red")
head(mainFFTargetsS)
```

We then use the `plotSubgraph` function (defined in "outputFunctions-display.R") to display the network constituted by all the main targets of PFR_L neurons:
```{r}
PFRGraph <- plotSubgraph(c("PFR_b_L*","PFR_a_L*"),
                         pal=customGraphPalette,
                         conns=mainFFConns,
                         targets=mainFFTargetsS,
                         graph=CX_outGraphRed,
                         layout="stress") +
  coord_cartesian(clip="off")
PFRGraph
```
And save it: 
```{r}
save_plot(file.path(outputsFolder,"PFRGraphOut.svg"),PFRGraph,base_height = 5,base_width=7)
```

### FR connectivity: figure supplement 3
#### Intra FR connectivity (panel A)
We want to plot the connections of FR neurons between themselves. We first collect their connectivity out of the central complex:
```{r}
FRBag <- neuronBag(filter(CXOutputNeurons,customSupertype %in% c("FR1","FR2")),
                   selfRef = T,
                   slctROI=outsideRegions,
                   omitInputs = T,renaming = cxRetyping) %>% 
  combineRois(outsideRegions,"Outside")
```
We then reformat the connection table, restricting it to FR to FR interactions, and ordering it by column of origin:
```{r}
FRTab <- filter(FRBag$outputs_raw,supertype2.to=="FR") %>% 
    mutate(column.from=factor(gsub("_","",str_extract(name.from,"_C[1-9]")),levels=paste0("C",9:1)),
           column.to=factor(gsub("_","",str_extract(name.to,"_C[1-9]")),levels=paste0("C",9:1))) %>%
  arrange(column.from)

orderIn <- unique(FRTab$from)

FRTab <- arrange(FRTab,column.to)

orderOut <- unique(FRTab$to)
```

Finally we can plot the matrix:
```{r}
FRConnPlot <-  plotConnectivity(FRTab,
                                slctROI = "Outside",
                                grouping = "neuron",
                                orderIn=orderIn,orderOut=orderOut,
                                facetInputs = "type.from",facetOutputs = "type.to",
                                xaxis = "outputs",
                                theme = theme_paper_grid_rects(strip.placement="outside"),
                                replacementLabels = "column",
                                legendName = "relative weight",
                                switch="both") + 
  xlab("postsynaptic neuron, FB column") + ylab("presynaptic neuron, FB column")
FRConnPlot
```
And we save the plot:
```{r}
save_plot(file.path(outputsFolder,"FRMat.svg"),FRConnPlot,nrow = 1,ncol=1,base_height = 11/4,base_width=8.5/2)
```

#### Direct targets of FR neurons connectivity matrix (panel B)
We reformat the neuron to neuron connectivity table for FR neurons, excluding connections between FR neurons and labeling it by column:
```{r}
restrictedConnectivity <- filter(FRBag$outputs_raw,
                                 supertype2.to != "FR" & type.to %in% FRBag$outputs$type.to) %>% 
  mutate(column=factor(gsub("_","",str_extract(name.from,"_C[1-9]")),levels=paste0("C",9:1))) %>%
  arrange(column) %>%
  mutate(label.from=column,
         label.to=name.to)
```

We then generate the plot:
```{r}
FROutputs <- plotConnectivity(restrictedConnectivity,
                              slctROI="Outside",
                              grouping="neuron",
                              xaxis="outputs",
                              facetInputs="databaseType.from",
                              facetOutputs="supertype2.to",
                              theme=theme_paper_grid_rects(strip.placement="outside"),
                              replacementLabels = "label",
                              legendName = "relative weight",
                              switch="both")+
  theme(strip.text.x=element_blank())+xlab("postsynaptic neuron")+ylab("presynaptic neuron, FB column")
FROutputs
```
And save the plot:
```{r}
save_plot(file.path(outputsFolder,"FRMatOut.svg"),
          FROutputs,nrow = 1,ncol=1,base_height = 11/3,base_width=8.5)
```

#### FR outputs network (panel C)
We generate the graph in the same way we generated the graph for the PFR neurons:
```{r}
FRGraph <- plotSubgraph(c("FR1_L","FR2_L"),
                        pal=customGraphPalette,
                        conns=mainFFConns,
                        targets=mainFFTargetsS,
                        graph=CX_outGraphRed,layout="stress") + 
  coord_cartesian(clip="off")
FRGraph
```
And save it:
```{r}
save_plot(file.path(outputsFolder,"FRGraphOut.svg"),FRGraph,base_height = 4,base_width=6)
```

