---
title: "FS4A weight distribution per column, figure 65"
output: html_notebook
---
Loading local functions:
```{r message=FALSE}
source("outputFunctions-display.R")
```

This is a folder where the figures will be saved if needed:
```{r}
outputsFolder <- "figure65-FS4A"
if (!dir.exists(outputsFolder)) dir.create(outputsFolder)
```

Where the data has been saved (by "Outputs-Core.Rmd"):
```{r}
dataFolder="data"
```
Loading some data generated in "Outputs-Core.Rmd":
```{r}
## General outputs metadata
load(file.path(dataFolder,"outputsBasics.RData"))
load(file.path(dataFolder,"mainTargetsAndConns.Rdata"))
```

## FS4A outputs connectivity matrix at glomerulus resolution (panel A)
We first get the connection information about FS4A direct partners:
```{r}
FSBag <- neuronBag(filter(CXOutputNeurons,customSupertype %in% c("FS4")),
                   selfRef = T,slctROI=outsideRegions,
                   omitInputs = T,renaming = cxRetyping) %>%
  combineRois(outsideRegions,"Outside")
```
We then use the `plotGlomMat` function (defined in "outputFunctions-display.R"). It takes as input a `neuronBag` object, a neuron of interest, a feature to group on (glomerulus or column), and a table of targets to restrict the plot to, and plot the connectivity per glomerulus (or column):
```{r}
FS4ACol <- plotGlomMat(FSBag,"FS4A_L",
                       grouping="col",targetFilt=mainFFTargets)
FS4ACol
```

```{r}
save_plot(file.path(outputsFolder,"outputs-FS4A.svg"),FS4ACol,base_height = 11/5,base_width = 8.5)
```

## Bodyids for rendering
SMP297_R:
```{r}
filter(mainFFTargetsNeurons,type %in% c("SMP297_R"))$bodyid
```
FS4A_L:
```{r}
filter(CXOutputNeurons,type %in% c("FS4A_L"))$bodyid
```

SMP304_R
```{r}
filter(mainFFTargetsNeurons,type %in% c("SMP304_R"))$bodyid
```

